### 2021-02-22 demonstration_romain.tex
ajout de la démonstration de Romain en anglais
La démonstration n'est pas terminée, et ce qui est déjà écrit est bien sûr sujet à des modifications ultérieures.

\documentclass{article}
\title{New theoretical lower bounds of weak Schur numbers using regular Schur numbers}
\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage[top=1cm]{geometry}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]

\begin{document}
\maketitle
\section{Introduction, context and notations}
We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.
\begin{definition}
A subset $A$ of $\mathbb{N}$ is said to be sum-free when :
\[ \forall (a,b) \in A^2 \text{, } a+b \notin A
\]
\end{definition}
\begin{definition}
A subset $B$ of $\mathbb{N}$ is said to be weakly sum-free when :
\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B
\]
\end{definition}
Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free subsets. Given $m$ and $n$ two integers, we are interested in partitioning the set of integers from 1 to $m$ in $n$ weakly sum-free subsets.
\begin{notation}
We denote by $[\![1,n]\!]$ the set of integers $\{1, 2, ..., n\}$
\end{notation}
Schur proved in [1] that given a number of subsets $n$, there exists a value of $m$ such that there exists no partition of $[\![1,p]\!]$ for any $p \geqslant m$. This observation leads to the following definition.
\begin{definition}
Let $n \in \mathbb{N}^*$, there exists an integer that we note S(n) (\textit{respectively WS(n)}) such that $[\![1,S(n) + 1]\!]$ (respectively $[\![1,WS(n) + 1]\!]$) can not be partitioned in $n$ sum-free subsets (respectively in $n$ weakly sum-free subsets) while $[\![1,S(n)]\!]$ (respectively $[\![1,WS(n)]\!]$) can be. S(n) is called the n\textsuperscript{th} Schur number and WS(n) the n\textsuperscript{th} weak Schur number.
\end{definition}
The values of both Schur and weak Schur numbers are known only for small values of $n$, and our goal is to improve the lower bounds on weak Schur numbers for $n \geqslant 5$. At the time being, the best lower bounds for weak Schur numbers are established by Rowley in [2]. He greatly improved the former best values with a purely theoretical and constructive approach. More precisely, he managed to build interesting weakly sum-free partitions with sum-free partitions. With this, he found the following lower bounds :
\[ WS(n+1) \geqslant 4S(n) + 2
\]
\[
WS(n+2) \geqslant 13S(n) + 8
\]
Actually, Rowley's construction can be generalised to find a lower bound for $WS(n+m)$ for all $(n,m) \in (\mathbb{N}^*)^2$. This result and its demonstration are detailled in the next part.
\section{A new theoretical lower bound for WS(n+m)}
The following theorem, inspired by Rowley's work, was found and proved by Romain Ageron.
\begin{theorem}
Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$. If there exists a partition of $r$ weakly sum-free subsets of $[\![1,n]\!]$ and a partition of $s$ sum-free subsets of $[\![1,p]\!]$ then there exists a partition of $r+s$ weakly sum-free subsets of $[\![1,p(n+\left \lfloor \frac{n}{2} \right \rfloor + 1)+n]\!]$
\end{theorem}
In particular, if we choose $n = WS(r)$ and $p = WS(s)$ in the last theorem, the next corollary follows.
\begin{corollary}
$ \forall (n,m) \in (\mathbb{N}^*)^2 \text{, } WS(n+m) \geqslant S(m) \left (WS(n) + \left \lfloor \frac{WS(n)}{2} \right \rfloor +1 \right) + WS(n)$
\end{corollary}
\textsc{Proof :} Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$,  $N = p(n+\left \lfloor \frac{n}{2} \right \rfloor + 1)+n$, $\alpha = \left \lfloor \frac{n}{2} \right \rfloor > 0$ and $\beta = n + \alpha + 1$. We denote by $f$ the projection of the equivalence relation induced by the partition of $[\![1,n]\!]$ and $g$ the one induced by the partition of $[\![1,p]\!]$. Each equivalence class is represented by a single integer, therefore :
\[ f : [\![1,n]\!] \longrightarrow [\![1,r]\!] \text{ and } \forall (x,y) \in [\![1,n]\!]^2, \left\{
    \begin{array}{ll}
        x \neq y \\
        f(x) = f(y)
    \end{array}
\right.
\Longrightarrow f(x+y) \neq f(x)
\]
\[g : [\![1,p]\!] \longrightarrow [\![1,s]\!] \text{ and } \forall (x,y) \in [\![1,n]\!]^2 \text{, } f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
\]
Let us start by parting the integers of $[\![1,N]\!]$ in two subsets $\mathcal{A}$ and $\mathcal{B}$ where $\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]\}$ and $\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}$.\\
\\
First, \underline{$\mathcal{A} \cap \mathcal{B} = \varnothing$} : \\
Suppose there exists $x \in \mathcal{A} \cap \mathcal{B} = \varnothing$. Then there are $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]$ and $(b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ such that $x = a\beta + u = b\beta +v$. By definition of $\alpha$ and  $\beta$ we have $u \in [\![\alpha + 1,n]\!] \subset [\![0,\beta - 1]\!]$. From there, we distinguish two cases :
\begin{itemize}
\item If $v \in [\![0,\alpha]\!]$ then $v \in [\![0,\beta - 1]\!]$ and $v \neq u$ because $v < \alpha + 1 \leqslant u$
\item If $v \in [\![-\alpha,-1]\!]$, we note $\tilde{v} = \beta + v$ and thus have $x = (b-1)\beta + \tilde{v}$ with $\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]$ and $\tilde{v} \neq u$ because $u < n+1 = \beta - \alpha \leqslant \tilde{v}$.
\end{itemize}
In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of $x$ by $\beta$.\\
\\
Then, we have \underline{$\mathcal{A} \cup \mathcal{B} = [\![1,N]\!]$}:
\begin{itemize}
\item On one hand : $1 = \text{min($\mathcal{A}$)} \leqslant \text{max($\mathcal{A}$)} = p\beta + n = N$ and $1 \leqslant \beta - \alpha = \text{min($\mathcal{B}$)} \leqslant \text{max($\mathcal{B}$)} = p\beta + \alpha \leqslant N$, which gives $\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]$.
\item On the other hand, let $x \in  [\![1,N]\!]$. If $x \leqslant \alpha$, we directly have $x \in \mathcal{A}$, let us then suppose that $x > \alpha$ and write $x = a\beta + u$ the euclidean division of $x$ by $\beta$. We have $x \leqslant N$, thus $a \leqslant p$. We distinguish three cases : \\
- If $u \in [\![0,\alpha]\!]$ then we necessarily have $a \geqslant 1$ because $x > \alpha$, and so $x \in \mathcal{B}$.\\
- If $u \in [\![\alpha + 1,n]\!]$, then $x \in \mathcal{A}$. \\
- If $u \in [\![n + 1,\beta - 1]\!]$ then $x = (a+1)\beta - (\beta - u)$ with $-\alpha \leqslant \beta - u \leqslant 0$ and so $x \in \mathcal{B}$ \\
In any case, $x \in \mathcal{A} \cup \mathcal{B}$ and we can thus conclude that $[\![1,N]\!] \subset \mathcal{A} \cup \mathcal{B}$.
\end{itemize}
\end{document}

### 2021-02-23 extension/schur_5/find_partitions.py
generation de partitions Schur 5

@@ -1,0 +1,170 @@
+import argparse
+import pickle
+
+
+def main(seeds, stop=None):
+    if stop is None:
+        stop = 3 * 10 ** 9
+
+    stack = seeds.copy()
+    partitions = set(seeds)
+    i = 0
+
+    while stack:
+        partition = stack.pop()
+        for neighbour in neighbours(partition):
+            if neighbour not in partitions:
+                partitions.add(neighbour)
+                stack.append(neighbour)
+
+        i += 1
+        if i % 10_000 == 0:
+            print("partitions found : {} -- nodes in stack : {}".format(
+                len(partitions), len(stack)
+            ))
+        if len(partitions) >= stop:
+            break
+
+    print("\n", len(partitions), " partitions found", sep="")
+    save_partitions(partitions)
+
+
+def save_partitions(partitions):
+    partitions = sorted(partitions, reverse=True)
+    with open("partitions", 'wb') as file:
+        pickle.dump(partitions, file)
+
+
+def neighbours(partition):
+    subsets, word, mins = from_int(partition)
+    for i, subset in enumerate(subsets):
+        choices = set(range(1, 161))
+        choices.difference_update(subset)
+        choices.difference_update(compute_sums(subset))
+        choices.difference_update(compute_difs(subset))
+
+        for n in choices:
+            j = word[n]
+            if j != 4 and n == mins[j][0] and (i > j or mins[j][1] > mins[j + 1][0]):
+                yield reorder(word, n, i)
+            else:
+                yield partition + (i - j) * (5 ** n)
+
+
+def reorder(word, n, i):
+    j = word[n]
+    word[n] = i
+
+    order = [None] * 5
+    count = 0
+    for p in range(1, 161):
+        k = word[p]
+        if order[k] is None:
+            order[k] = count
+            if count == 4:
+                break
+            count += 1
+
+    pow_5 = 1
+    acc = 0
+    for p in range(1, 161):
+        pow_5 *= 5
+        acc += order[word[p]] * pow_5
+
[…]

### 2021-02-23 extension/schur_5/read_partitions.py

@@ -1,0 +1,7 @@
+import pickle
+
+
+def read_partitions():
+    with open("partitions", 'rb') as file:
+        partitions = pickle.load(file)
+    return partitions

### 2021-02-23 demonstration_romain.tex

@@
 \end{notation}
-Schur proved in [1] that given a number of subsets $n$, there exists a value of $m$ such that there exists no partition of $[\![1,p]\!]$ for any $p \geqslant m$.
+Schur proved in \hyperlink{label1}{\textbf{[1]}} that given a number of subsets $n$, there exists a value of $m$ such that there exists no partition of $[\![1,p]\!]$ in $n$ sum-free subsets for any $p \geqslant m$.
 This observation leads to the following definition.
@@
 The values of both Schur and weak Schur numbers are known only for small values of $n$, and our goal is to improve the lower bounds on weak Schur numbers for $n \geqslant 5$.
-At the time being, the best lower bounds for weak Schur numbers are established by Rowley in [2].
+At the time being, the best lower bounds for weak Schur numbers are established by Rowley in \hyperlink{label2}{\textbf{[2]}}.
 He greatly improved the former best values with a purely theoretical and constructive approach.
@@
 - If $u \in [\![\alpha + 1,n]\!]$, then $x \in \mathcal{A}$. \\
-- If $u \in [\![n + 1,\beta - 1]\!]$ then $x = (a+1)\beta - (\beta - u)$ with $-\alpha \leqslant \beta - u \leqslant 0$ and so $x \in \mathcal{B}$ \\
+- If $u \in [\![n + 1,\beta - 1]\!]$ then $x = (a+1)\beta - (\beta - u)$ with $-\alpha \leqslant \beta - u \leqslant 0$.
+Furthermore, $a \leqslant p - 1$, else we would have $x > N$, and so $x \in \mathcal{B}$ \\
 In any case, $x \in \mathcal{A} \cup \mathcal{B}$ and we can thus conclude that $[\![1,N]\!] \subset \mathcal{A} \cup \mathcal{B}$.
 \end{itemize}
+This first partition of $[\![1,N]\!]$ will help us to define our final partition by the projection of its equivalence relation.
+We thereby define $h : [\![1,N]\!] \longrightarrow [\![1,r+s]\!]$ as such :\\
+- If $x \in \mathcal{A}$ then $h(x) = f(x \text{ mod } \beta)$ (well defined because $x \text{ mod } \beta \in [\![1,N]\!]$)\\
+- If $x \in \mathcal{B}$ then $x = a\beta + u$ with a unique $(a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ and we define $h(x) = r + g(a)$\\
+The fact that $(\mathcal{A}, \mathcal{B})$ is a partition of $[\![1,N]\!]$ ensures that this definition of $h$ is valid. We then have to verify that $h$ induces weakly sum-free subsets.\\
+\\
+\underline{The classes of equivalence $h(x)$ for $x \in \mathcal{A}$ are weakly sum-free :}
+\\
+\\
+Let $(x,y) \in \mathcal{A}^2$ such that $h(x) = h(y)$, $x \neq y$ and $x + y \leqslant N$
+\begin{itemize}
+\item If $(x,y) \in [\![1,\alpha]\!]^2$ :\\
+We have $x + y \leqslant 2\alpha \leqslant n$ and $x + y = 0\beta + x + y$, therefore $x + y \in \mathcal{A}$.
+Then, by definition : $h(x) = f(x)$, $h(y) = f(y)$ and $h(x+y) = f(x+y)$, which gives us, thanks to the property verified by $f$, that $h(x+y) \neq h(x)$.
+\item If $(x,y) \in [\![1,\alpha]\!] \times ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )$ :\\
+We write $y = a\beta + u$ with $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]$.
+Then $x+y = a\beta + x + u = (a+1)\beta + x + u - \beta$, and if $x + u > n$ it follows that $a \leqslant p-1$ since $x+y \leqslant N$, and $-\alpha \leqslant x + u - \beta \leqslant -1$.
+Therefore $x+y \in \mathcal{B}$ and $h(x+y) \neq h(x) = f(x)$ by definition of h.
+On the contrary, if $x - u \leqslant n$, then $x+y \in \mathcal{A}$ and $h(x+y) = f(x+u)$ because $x+u$ is actually the remainder of the euclidean division of $x+y$ by $\beta$.
+Moreover, $h(x) = f(x)$, $x < u$ and, with our initial hypothesis, $h(x) = h(y) = f(u)$.
+The property verified by $f$ gives us $f(x+u) \neq f(x)$ which can be rewritten as $h(x+y) \neq h(x)$.
+\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] ) \times [\![1,\alpha]\!]$ : \\
+This case is handled exactly like the previous one by swaping the roles of $x$ and $y$.
+\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )^2$ : \\
+We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![0,p]\!] \times [\![\alpha + 1,n]\!]$.
+Then $x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta$ with $a+b \leqslant p-1$ (else we would have $x+y > N$ because $u+v > n$) and $-\alpha \leqslant u + v - \beta \leqslant \alpha$, therefore $x+y \in \mathcal{B}$ and by definition $h(x+y) \neq h(x)$.
+\end{itemize}
+In any case, $h(x+y) \neq h(x)$ and the classes of equivalence $h(x)$ for $x \in \mathcal{A}$ are weakly sum-free.\\
+\\
+\underline{The classes of equivalence $h(x)$ for $x \in \mathcal{B}$ are weakly sum-free :}
+\\
+\\
+Let $(x,y) \in \mathcal{B}^2$ such that $h(x) = h(y)$, $x \neq y$ and $x + y \leqslant N$.\\
+We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![1,p]\!] \times [\![-\alpha,\alpha]\!]$.
+We have $h(x) = r + g(a)$ and $h(y) = r + g(b)$, therefore $g(a) = g(b)$.
+We also have $x+y = (a+b)\beta + u +v$.\\
+If $u + v \in [\![-\alpha,\alpha]\!]$, then $x+y \in \mathcal{B}$ and $h(x+y) = g(a+b)$, hence we can deduce that $h(x+y) \neq h(x)$ because of the property verified by $g$.
+On the contrary, if $u+v \notin [\![-\alpha,\alpha]\!]$, then necessarily $x+y \in \mathcal{A}$.
+Suppose $x+y \in \mathcal{B}$, then $x+y = c\beta + w$ with $(c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$.
+Thus, $c\beta + w = (a+b)\beta + u + v$ and $(a+b-c)\beta = w-u-v$.
+Furthermore $a+b-c \neq 0$, else we would have $u+v = w \in [\![-\alpha,\alpha]\!]$.
+This finally leads to the following inequality :
+\[\beta \leqslant |a+b-c|\beta = |w-u-v| \leqslant |w| + |u| + |v| \leqslant 3\alpha \leqslant n + \alpha < \beta
+\]
+which is absurd.
+We can therefore conclude that $x+y \in \mathcal{A}$ and by definition of $h$, $h(x+y) \neq h(x)$, proving that the classes of equivalence $h(x)$ for $x \in \mathcal{B}$ are weakly sum-free.\\
+\\
+Finally, we have showed that every classe of equivalence induced by $h$ is weakly sum-free, which ends the proof.
+\section{References}
+\hypertarget{label1}{\textbf{[1]}} Schur, I.. "Über Kongruenz x ... (mod. p.).." Jahresbericht der Deutschen Mathematiker-Vereinigung 25 (1917): 114-116. \url{http://eudml.org/doc/145475} \\
+\hypertarget{label2}{\textbf{[2]}} F. Rowley, New Lower Bounds for Weak Schur Partitions, arXiv 2011.11292, \url{https://arxiv.org/pdf/2011.11292.pdf}
 \end{document}

### 2021-02-23 extension/schur_5/read_partitions.py
=format plus pratique dans read_partitions

@@ -1,7 +1,20 @@
 import pickle
 
 
+def from_int(int_repr):
+    partition = [[] for _ in range(5)]
+    for n in range(1, 161):
+        int_repr //= 5
+        i = int_repr % 5
+        partition[i].append(n)
+    return partition
+
+
 def read_partitions():
     with open("partitions", 'rb') as file:
-        partitions = pickle.load(file)
+        int_reprs = pickle.load(file)
+    partitions = []
+    for int_repr in int_reprs:
+        partition = from_int(int_repr)
+        partitions.append(partition)
     return partitions

### 2021-02-24 extension/schur_5/find_partitions.py
=la version precedente calculer des partitions weak schur et non schur + un peu plus rapide

@@ -39,9 +39,7 @@ def neighbours(partition):
     subsets, word, mins = from_int(partition)
     for i, subset in enumerate(subsets):
         choices = set(range(1, 161))
-        choices.difference_update(subset)
-        choices.difference_update(compute_sums(subset))
-        choices.difference_update(compute_difs(subset))
+        choices.difference_update(compute_forbidden(subset))
 
         for n in choices:
             j = word[n]
@@ -75,36 +73,30 @@ def reorder(word, n, i):
     return acc
 
 
-def compute_difs(subset):
-    difs = set()
-    for a in subset:
-        for b in subset:
-            if a < b:
-                difs.add(b - a)
-    return difs
-
-
-def compute_sums(subset):
-    sums = set()
-    for a in subset:
-        for b in subset:
-            if a > b:
-                continue
-            tot = a + b
-            if tot <= 160:
-                sums.add(tot)
-    return sums
+def compute_forbidden(subset):
+    forbidden = set(subset)
+    for i, a in enumerate(subset):
+        if a % 2 == 0:
+            forbidden.add(a // 2)
+        for j in range(i):
+            forbidden.add(a - subset[j])
+        for j in range(i, len(subset)):
+            tot = a + subset[j]
+            if tot > 160:
+                break
+            forbidden.add(tot)
+    return forbidden
 
 
 def from_int(partition):
-    subsets = [set() for _ in range(5)]
+    subsets = [[] for _ in range(5)]
     word = [None] * 161
     mins = [[] for _ in range(5)]
 
     for n in range(1, 161):
         partition //= 5
         i = partition % 5
-        subsets[i].add(n)
+        subsets[i].append(n)
         word[n] = i
         mini = mins[i]
         if len(mini) < 2:

### 2021-02-24 extension/viewing.py
bug fix (quand on change de partition avec la souris sur le tableau)

@@ -83,6 +83,12 @@ class Viewing:
             for n in subset:
                 self.canvas.itemconfig(self.squares[n], fill=color)
 
+        for line in range(1, 45):
+            for text_id in self.canvas.find_withtag(f"L{line}"):
+                self.canvas.itemconfig(text_id, fill='black')
+                self.canvas.itemconfig(text_id, font=self.font)
+        self.on_enter()
+
     def draw_square(self, n):
         side = self.side + self.width
         mid = side // 2 - self.width // 2
@@ -123,8 +129,11 @@ class Viewing:
                     yield a
                     yield b
 
-    def find_text_ids(self, event):
-        square_id = event.widget.find_withtag('current')[0]
+    def find_text_ids(self):
+        try:
+            square_id = self.canvas.find_withtag('current')[0]
+        except:
+            return
         n = self.squares.index(square_id)
         line = (n + 1) // 4
 
@@ -144,23 +153,23 @@ class Viewing:
         self.root.grid_columnconfigure(2, weight=1)
         self.root.grid_columnconfigure(3, weight=2)
 
-    def next(self, _):
+    def next(self, *args):
         self.i += 1
         self.display()
 
-    def on_enter(self, event):
+    def on_enter(self, *args):
         font = (self.font[0], self.font[1], 'bold')
 
-        for text_id in self.find_text_ids(event):
+        for text_id in self.find_text_ids():
             self.canvas.itemconfig(text_id, fill='yellow')
             self.canvas.itemconfig(text_id, font=font)
 
-    def on_leave(self, event):
-        for text_id in self.find_text_ids(event):
+    def on_leave(self, *args):
+        for text_id in self.find_text_ids():
             self.canvas.itemconfig(text_id, fill='black')
             self.canvas.itemconfig(text_id, font=self.font)
 
-    def previous(self, _):
+    def previous(self, *args):
         self.i -= 1
         self.display()
 

### 2021-02-25 extension/schur_5/find_partitions.py
correction du cassage de symetrie

@@ -37,13 +37,15 @@ def save_partitions(partitions):
 
 def neighbours(partition):
     subsets, word, mins = from_int(partition)
+
     for i, subset in enumerate(subsets):
         choices = set(range(1, 161))
         choices.difference_update(compute_forbidden(subset))
 
         for n in choices:
             j = word[n]
-            if j != 4 and n == mins[j][0] and (i > j or mins[j][1] > mins[j + 1][0]):
+            if j != 4 and ((i > j and n <= mins[i - 1][0]) or
+                    (n == mins[j][0] and mins[j][1] > mins[j + 1][0])):
                 yield reorder(word, n, i)
             else:
                 yield partition + (i - j) * (5 ** n)
@@ -158,5 +160,5 @@ if __name__ == "__main__":
     args = argparse.ArgumentParser(description="test setup")
     args.add_argument('--stop', type=int)
     args = args.parse_args()
-
+    
     main(PARTITIONS, args.stop)

### 2021-02-26 extension/schur_5/check_partitions.py
lecture des partitions schur 5

@@ -1,0 +1,42 @@
+from load_partitions import load_partitions
+
+
+def is_partition(partition):
+    occurences = [1] + [0] * 160
+    for subset in partition:
+        for num in subset:
+            occurences[num] += 1
+    return all(map(lambda n_occu: n_occu == 1, occurences))
+
+
+def is_sum_free(subset):
+    list_subset = sorted(subset)
+    set_subset = set(subset)
+    maxi = list_subset[-1]
+    for i, num in enumerate(list_subset):
+        if 2 * num > maxi:
+            break
+        for j in range(i, len(list_subset)):
+            add = num + list_subset[j]
+            if add > maxi:
+                break
+            if add in set_subset:
+                return False
+    return True
+
+
+def is_sum_free_partition(partition):
+    return is_partition(partition) and all(map(is_sum_free, partition))
+
+
+def main():
+    c = 0
+    for partition in load_partitions():
+        minis = list(map(min, partition))
+        assert minis == sorted(minis)
+        assert is_sum_free_partition(partition)
+    print(c, "partitions")
+
+
+if __name__ == '__main__':
+    main()

### 2021-02-26 extension/schur_5/load_partitions.py

@@ -1,0 +1,60 @@
+import heapq
+import os
+import pickle
+import tqdm
+
+
+def from_int(int_repr):
+    partition = [[] for _ in range(5)]
+    for n in range(1, 161):
+        int_repr //= 5
+        i = int_repr % 5
+        partition[i].append(n)
+    return partition
+
+
+def read_file(filename):
+    if isinstance(filename, int):
+        filename = "{:05d}".format(filename)
+
+    with open("./partitions/all_partitions/" + filename, 'rb') as file:
+        partitions = pickle.load(file)
+    return map(from_int, partitions)
+
+
+def load_partitions():
+    _, _, groups = next(os.walk("./partitions/all_partitions/"))
+    for group in tqdm.tqdm(groups):
+        for partition in read_file(group):
+            yield partition
+
+
+def select_partitions(necessary_condition=None, fitness_function=None,
+                      max_size=10_000):
+    if necessary_condition is None:
+        necessary_condition = lambda _: True
+    if fitness_function is None:
+        fitness_function = lambda _: 0
+        stop_early = True
+    else:
+        stop_early = False
+
+    heap = []
+    counter = 0
+
+    for partition in load_partitions():
+        if not necessary_condition(partition):
+            continue
+
+        counter += 1
+        fitness = fitness_function(partition)
+        item = (fitness, counter, partition)
+
+        if len(heap) < max_size:
+            heapq.heappush(heap, item)
+        else:
+            if stop_early:
+                break
+            heapq.heappushpop(heap, item)
+
+    return heap

### 2021-02-26 extension/schur_5/read_partitions.py

@@ -1,20 +1,0 @@
-import pickle
-
-
-def from_int(int_repr):
-    partition = [[] for _ in range(5)]
-    for n in range(1, 161):
-        int_repr //= 5
-        i = int_repr % 5
-        partition[i].append(n)
-    return partition
-
-
-def read_partitions():
-    with open("partitions", 'rb') as file:
-        int_reprs = pickle.load(file)
-    partitions = []
-    for int_repr in int_reprs:
-        partition = from_int(int_repr)
-        partitions.append(partition)
-    return partitions

### 2021-04-06 article/article.tex
article initial commit

\documentclass{article}
\title{New lower bounds for Schur and weak Schur numbers}
\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage[english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{computational theorem}{Computational Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]

\begin{document}
\maketitle

\section{Abstract}

\section{Introduction, context and notations}

We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.

\begin{definition}
A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} when :
\[ \forall (a,b) \in A^2 \text{, } a+b \notin A\]
\end{definition}

\begin{definition}
A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} when:
\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B\]
\end{definition}

Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free
subsets. Given \(m\) and \(n\) two integers, we are interested in partitioning the set of integers from 1 to \(m\) into
\(n\) weakly sum-free subsets.

\begin{notation}
We denote by \([\![1,n]\!]\) the set of integers \(\{1, 2, ..., n\}\).
\end{notation}

Schur proved in \hyperlink{label1}{\textbf{[1]}} that given a number of subsets \(n\), there exists a value of \(m\)
such that there exists no partition of \([\![1,p]\!]\) into \(n\) sum-free subsets for any \(p \geqslant m\). A similar
property holds for weakly sum-free subsets (reference necessaire). These observations lead to the following definitions.

\begin{definition}
Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we note \(S(n)\) (\textit{resp. \(WS(n)\)}) such that
\([\![1,S(n)]\!]\) (resp. \([\![1,WS(n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(WS(n)\) the \(n\)\textsuperscript{th} weak
Schur number}.
\end{definition}

\begin{notation}
For a partition of \([\![1, n]\!]\) in \(k\) subsets, we generally note these subsets \(A_1, ..., A_k\). We also note \(m_i = \text{min}(A_i)\). 
By ordering the subsets, we mean assuming that \(m_1 < ... < m_k\). However, if not specified we do not make this hypothesis since we 
do not always consider partitions in which every subset plays a symmetric role.
\end{notation}

\section{Schur numbers}

\section{Weak Schur numbers}

\section{About the construction of lower bounds for weak Schur numbers using a computer}

In this section, we first reframe the question of the existence of (weakly) sum-free partitions as a boolean
satisfiability (SAT) problem. We then provide evidence which indicates that the main assumption made by papers which
found the previous best known lower bounds for weak Schur numbers may not be correct. Finally, we obtain stronger
results than those previously known for \(WS(5)\) while gaining several orders of magnitude in computation time by 
giving additional information to the SAT solver without losing in generality. In this section, we assume that the subsets are ordered.

\subsection{Reformulation as a SAT problem}

We encode the existence of (weakly) sum-free partitions as propositional formulae like in \hyperlink{label3}{\textbf{[3]}} and then use 
SAT solvers to determine whether these formulae are satisfiable.

\begin{definition}
A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a negative literal) where \(v\) 
takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a conjunction of clauses: it 
is a propositional formula in \textit{conjonctive normal form} (CNF).
\end{definition}

\begin{definition}
An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A literal \(l\) is 
\textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\) 
(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A clause is \textit{satisfied} 
by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is \textit{satisfied} by an assignment 
\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an assignment that satisfies it; 
otherwise it is \textit{unsatisfiable}.
\end{definition}

\subsection{Search space previously used in computer search for lower bound may not contain the optimal partitions}

Rowley's new lower bound for \(WS(6)\) (642)  \hyperlink{label2}{\textbf{[2]}} was a quite significant improvement upon the former 
best known lower bound (582). This previous lower bound was found using a computer with Monte-Carlo methods and by making the 
assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small values of \(n\).
Therefore, one may wonder whether the limiting factor is the assumption or the methods used to search for partitions. It appears that 
the latter is correct.

\begin{computational theorem}
There is no weakly sum-free partition of \([\![1,583]\!]\) in 6 parts such that:
\begin{itemize}
\item \(m_5 \ge 66\)
\item \(m_6 \ge 186\)
\item \([\![210,349]\!] \subset A_6\)
\end{itemize}  
\end{computational theorem}

This result was obtained in 8 hours with the SAT solver plingeling \hyperlink{label5}{\textbf{[5]}} on a 2.60 GHz Intel i7 processor PC.
However, simply encoding the existence of such a partition as explained in the previous subsection would not result in a reasonable 
computation time. In order to help the SAT solver, we add additional information in the propositional formula. We did not quantify the 
speedup, but it most likely allows us to gain several order of magnitude in computation time as we explain in the next subsection.

\par
Every weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets starts with the following sequence 1121222133. Then 11 is always 
either in subset 1 or 3, 12 is always in subset 3 and so. For every integer in \([\![1,65]\!]\), we computed in which subset it can appear. 
By using this constraints, we could then compute for every integer in \([\![1,185]\!]\), in which subset it can appear in a weakly sum-free 
partition of  \([\![1,185]\!]\) which starts with a  weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets. Adding these constraints to the 
formula corresponding to the above theorem gives additional information to the SAT solver without losing in generality.

\subsection{Weak Schur number five}

\section{Conclusions and future work}

\section{Acknowledgments}

\section{References}

\hypertarget{label1}{\textbf{[1]}} Schur, I. 1917. Uber die Kongruenz \(x^m + y^m = z^m~(\text{mod}~p)\). Jahresbericht der 
Deutschen Mathematikervereinigung 25:114–117.: 114-116. \url{http://eudml.org/doc/145475}

\hypertarget{label2}{\textbf{[2]}} Rowley, F. 2020. New Lower Bounds for Weak Schur Partitions. arXiv 2011.11292, 
\url{https://arxiv.org/pdf/2011.11292.pdf}

\hypertarget{label3}{\textbf{[3]}} Heule, M.J.H. 2017. Schur Number Five. arXiv 1711.08076, \url{https://arxiv.org/pdf/1711.08076.pdf}

\hypertarget{label4}{\textbf{[4]}} S. Eliahou, J.M. Marín, M.P. Revuelta and M.I. Sanz 2012. Weak Schur numbers and the search for G.W. 
Walker’s lost partitions. Computers \& Mathematics with Applications Vol. 63, \url{https://www.sciencedirect.com/science/article/pii/S0898122111009722}

\hypertarget{label5}{\textbf{[5]}} Bierem, A. 2017. CaDiCaL, Lingeling, Plingeling, Treengeling, YalSAT Entering the SAT Competition 2017. 
Proceedinfs of SAT Competition 2017 -- Solver and Benchmark Descriptions \url{http://fmv.jku.at/papers/Biere-SAT-Competition-2017-solvers.pdf}

\end{document}

### 2021-04-06 article/article.tex
Add files via upload

@@
 
+\qquad In this section, we use Rowley's constructions [7] in a Schur context.
+To improve lower bounds for Ramsay's numbers, Rowley introduces partitions verifying some properties which can be extended using method which generalizes Abbott-Hanson's [8] construction.
+Rolwey named these partitions "templates", and we will keep this name in the entire article.
+Finding suitable templates and applying his method to these will allow us to find new lower bounds for Schur methods.
+
+\subsection{Definition of SE\(_+\)}
+
+\begin{definition}
+Let \( n \in \mathbb{N}^*\), there exists a greatest integer that we note \(SE_+(n)\) (resp.
+\(SE_-(n)\)) such that \( [\![1, SE_+(n)]\!]\) (resp.
+\( [\![1, SE_-(n)]\!]\)) can be partitionned (resp.
+can not be partionned) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
+\[
+\forall k \in [\![1, n-1]\!], \forall (x,y) \in A_k^2, x+y > SE_+(n)
+\Longrightarrow x+y-SE_+(n) \notin A_k
+\]
+\end{definition}
+We notice that in general, unlike regular Schur numbers, we don't have \(SE_+(n) + 1 \neq SE_-(n)\)
+
+\begin{theorem}
+Let \(n \in [\![2, +\infty]\!]\), we have :
+\[
+2S(n-1)+1 \leqslant SE_+(n) \leqslant S(n)
+\]
+\end{theorem}
+
+\subsection{}
+
+\subsection{}
+
 \section{Weak Schur numbers}
+
+In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the integer \(WE_+(n)\) to build suitable templates.
+
+\subsection{Lower bound for Weak Schur numbers using Schur and Weak Schur numbers}
+
+The following theorem, inspired by Rowley's work, was found and proved by Romain Ageron.
+\begin{theorem}
+Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$.
+If there exists a partition of $r$ weakly sum-free subsets of $[\![1,n]\!]$ and a partition of $s$ sum-free subsets of $[\![1,p]\!]$ then there exists a partition of $r+s$ weakly sum-free subsets of $[\![1,p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n]\!]$
+\end{theorem}
+In particular, if we choose $n = WS(r)$ and $p = WS(s)$ in the last theorem, the next corollary follows.
+\begin{corollary}
+$ \forall (n,m) \in (\mathbb{N}^*)^2 \text{, } WS(n+m) \geqslant S(m) \left (WS(n) + \left \lceil \frac{WS(n)}{2} \right \rceil +1 \right) + WS(n)$
+\end{corollary}
+\textsc{Proof :} Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$,  $N = p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n$, $\alpha = \left \lceil \frac{n}{2} \right \rceil > 0$ and $\beta = n + \alpha + 1$.
+We denote by $f$ the projection of the equivalence relation induced by the partition of $[\![1,n]\!]$ and $g$ the one induced by the partition of $[\![1,p]\!]$.
+Each equivalence class is represented by a single integer, therefore :
+\[ f : [\![1,n]\!] \longrightarrow [\![1,r]\!] \text{ and } \forall (x,y) \in [\![1,n]\!]^2, \left\{
+    \begin{array}{ll}
+        x \neq y \\
+        f(x) = f(y)
+    \end{array}
+\right.
+\Longrightarrow f(x+y) \neq f(x)
+\]
+\[g : [\![1,p]\!] \longrightarrow [\![1,s]\!] \text{ and } \forall (x,y) \in [\![1,n]\!]^2 \text{, } f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
+\]
+Let us start by parting the integers of $[\![1,N]\!]$ in two subsets $\mathcal{A}$ and $\mathcal{B}$ where $\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]\}$ and $\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}$.\\
+\\
+First, \underline{$\mathcal{A} \cap \mathcal{B} = \varnothing$} : \\
+Suppose there exists $x \in \mathcal{A} \cap \mathcal{B} = \varnothing$.
+Then there are $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]$ and $(b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ such that $x = a\beta + u = b\beta +v$.
+By definition of $\alpha$ and  $\beta$ we have $u \in [\![\alpha + 1,n]\!] \subset [\![0,\beta - 1]\!]$.
+From there, we distinguish two cases :
+\begin{itemize}
+\item If $v \in [\![0,\alpha]\!]$ then $v \in [\![0,\beta - 1]\!]$ and $v \neq u$ because $v < \alpha + 1 \leqslant u$
+\item If $v \in [\![-\alpha,-1]\!]$, we note $\tilde{v} = \beta + v$ and thus have $x = (b-1)\beta + \tilde{v}$ with $\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]$ and $\tilde{v} \neq u$ because $u < n+1 = \beta - \alpha \leqslant \tilde{v}$.
+\end{itemize}
+In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of $x$ by $\beta$.\\
+\\
+Then, we have \underline{$\mathcal{A} \cup \mathcal{B} = [\![1,N]\!]$}:
+\begin{itemize}
+\item On one hand : $1 = \text{min($\mathcal{A}$)} \leqslant \text{max($\mathcal{A}$)} = p\beta + n = N$ and $1 \leqslant \beta - \alpha = \text{min($\mathcal{B}$)} \leqslant \text{max($\mathcal{B}$)} = p\beta + \alpha \leqslant N$, which gives $\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]$.
+\item On the other hand, let $x \in  [\![1,N]\!]$.
+If $x \leqslant \alpha$, we directly have $x \in \mathcal{A}$, let us then suppose that $x > \alpha$ and write $x = a\beta + u$ the euclidean division of $x$ by $\beta$.
+We have $x \leqslant N$, thus $a \leqslant p$.
+We distinguish three cases : \\
+- If $u \in [\![0,\alpha]\!]$ then we necessarily have $a \geqslant 1$ because $x > \alpha$, and so $x \in \mathcal{B}$.\\
+- If $u \in [\![\alpha + 1,n]\!]$, then $x \in \mathcal{A}$. \\
+- If $u \in [\![n + 1,\beta - 1]\!]$ then $x = (a+1)\beta - (\beta - u)$ with $-\alpha \leqslant \beta - u \leqslant 0$.
+Furthermore, $a \leqslant p - 1$, else we would have $x > N$, and so $x \in \mathcal{B}$ \\
+In any case, $x \in \mathcal{A} \cup \mathcal{B}$ and we can thus conclude that $[\![1,N]\!] \subset \mathcal{A} \cup \mathcal{B}$.
+\end{itemize}
+This first partition of $[\![1,N]\!]$ will help us to define our final partition by the projection of its equivalence relation.
+We thereby define $h : [\![1,N]\!] \longrightarrow [\![1,r+s]\!]$ as such :\\
+- If $x \in \mathcal{A}$ then $h(x) = f(x \text{ mod } \beta)$ (well defined because $x \text{ mod } \beta \in [\![1,N]\!]$)\\
+- If $x \in \mathcal{B}$ then $x = a\beta + u$ with a unique $(a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ and we define $h(x) = r + g(a)$\\
+The fact that $(\mathcal{A}, \mathcal{B})$ is a partition of $[\![1,N]\!]$ ensures that this definition of $h$ is valid. We then have to verify that $h$ induces weakly sum-free subsets.\\
+\\
+\underline{The classes of equivalence $h(x)$ for $x \in \mathcal{A}$ are weakly sum-free :}
+\\
+\\
+Let $(x,y) \in \mathcal{A}^2$ such that $h(x) = h(y)$, $x \neq y$ and $x + y \leqslant N$
+\begin{itemize}
+\item If $(x,y) \in [\![1,\alpha]\!]^2$ :\\
+We have $x + y \leqslant 2\alpha \leqslant n$ and $x + y = 0\beta + x + y$, therefore $x + y \in \mathcal{A}$.
+Then, by definition : $h(x) = f(x)$, $h(y) = f(y)$ and $h(x+y) = f(x+y)$, which gives us, thanks to the property verified by $f$, that $h(x+y) \neq h(x)$.
+\item If $(x,y) \in [\![1,\alpha]\!] \times ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )$ :\\
+We write $y = a\beta + u$ with $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]$.
+Then $x+y = a\beta + x + u = (a+1)\beta + x + u - \beta$, and if $x + u > n$ it follows that $a \leqslant p-1$ since $x+y \leqslant N$, and $-\alpha \leqslant x + u - \beta \leqslant -1$.
+Therefore $x+y \in \mathcal{B}$ and $h(x+y) \neq h(x) = f(x)$ by definition of h.
+On the contrary, if $x - u \leqslant n$, then $x+y \in \mathcal{A}$ and $h(x+y) = f(x+u)$ because $x+u$ is actually the remainder of the euclidean division of $x+y$ by $\beta$.
+Moreover, $h(x) = f(x)$, $x < u$ and, with our initial hypothesis, $h(x) = h(y) = f(u)$.
+The property verified by $f$ gives us $f(x+u) \neq f(x)$ which can be rewritten as $h(x+y) \neq h(x)$.
+\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] ) \times [\![1,\alpha]\!]$ : \\
+This case is handled exactly like the previous one by swaping the roles of $x$ and $y$.
+\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )^2$ : \\
+We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![0,p]\!] \times [\![\alpha + 1,n]\!]$.
+Then $x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta$ with $a+b \leqslant p-1$ (else we would have $x+y > N$ because $u+v > n$) and $-\alpha \leqslant u + v - \beta \leqslant \alpha$, therefore $x+y \in \mathcal{B}$ and by definition $h(x+y) \neq h(x)$.
+\end{itemize}
+In any case, $h(x+y) \neq h(x)$ and the classes of equivalence $h(x)$ for $x \in \mathcal{A}$ are weakly sum-free.\\
+\\
+\underline{The classes of equivalence $h(x)$ for $x \in \mathcal{B}$ are weakly sum-free :}
+\\
+\\
+Let $(x,y) \in \mathcal{B}^2$ such that $h(x) = h(y)$, $x \neq y$ and $x + y \leqslant N$.\\
+We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![1,p]\!] \times [\![-\alpha,\alpha]\!]$.
+We have $h(x) = r + g(a)$ and $h(y) = r + g(b)$, therefore $g(a) = g(b)$.
+We also have $x+y = (a+b)\beta + u +v$.\\
+If $u + v \in [\![-\alpha,\alpha]\!]$, then $x+y \in \mathcal{B}$ and $h(x+y) = g(a+b)$, hence we can deduce that $h(x+y) \neq h(x)$ because of the property verified by $g$.
+On the contrary, if $u+v \notin [\![-\alpha,\alpha]\!]$, then necessarily $x+y \in \mathcal{A}$.
+Suppose $x+y \in \mathcal{B}$, then $x+y = c\beta + w$ with $(c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$.
+Thus, $c\beta + w = (a+b)\beta + u + v$ and $(a+b-c)\beta = w-u-v$.
+Furthermore $a+b-c \neq 0$, else we would have $u+v = w \in [\![-\alpha,\alpha]\!]$.
+This finally leads to the following inequality :
+\[\beta \leqslant |a+b-c|\beta = |w-u-v| \leqslant |w| + |u| + |v| \leqslant 3\alpha \leqslant n + \alpha < \beta
+\]
+which is absurd.
+We can therefore conclude that $x+y \in \mathcal{A}$ and by definition of $h$, $h(x+y) \neq h(x)$, proving that the classes of equivalence $h(x)$ for $x \in \mathcal{B}$ are weakly sum-free.\\
+\\
+Finally, we have showed that every classe of equivalence induced by $h$ is weakly sum-free, which ends the proof.
 

### 2021-04-06 article/article.tex
redaction sat

--- 2021-04-06 article/article.tex
@@
 
-\subsection{Search space previously used in computer search for lower bound may not contain the optimal partitions}
+We then encode the existence of a partition of \([\![1,n]\!]\) in \(k\)  weakly sum-free subsets as follows: for every integer 
+\(i \in [\![1,n]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!], x^{(i)}_c = 1 \iff i \in A_c\). 
+The corresponding clauses are:
+
+\begin{itemize}
+\item \textbf{sumfree:} \(\forall c \in  [\![1,k]\!], \forall (i, j) \in [\![1,n]\!]^2, (i \neq j ~ \text{and} ~ i + j \leq n) \implies \lnot x^{(i)}_c 
+\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
+\item \textbf{union:} \(\forall i \in [\![1,n]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
+\item \textbf{disjoint:} \(\forall i \in [\![1,n]\!],\forall (c_1, c_2) \in  [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
+\end{itemize}
+
+In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the subsets, that is by 
+enforcing that \(m_1 < ... < m_k\). The correspond clauses are: \linebreak
+\textbf{symmetry breaking:}  \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!], x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
+
+\subsection{The search space previously used in computer search for lower bound may not contain the optimal partitions}
 

### 2021-04-06 article/article.tex
avancement sat

@@
 \begin{definition}
-A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} when :
+A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} when:
 \[ \forall (a,b) \in A^2 \text{, } a+b \notin A\]
@@
 
-\qquad In this section, we use Rowley's constructions [7] in a Schur context.
-To improve lower bounds for Ramsay's numbers, Rowley introduces partitions verifying some properties which can be extended using method which generalizes Abbott-Hanson's [8] construction.
-Rolwey named these partitions "templates", and we will keep this name in the entire article.
-Finding suitable templates and applying his method to these will allow us to find new lower bounds for Schur methods.
+\qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's numbers, Rowley 
+introduces partitions verifying some properties which can be extended using method which generalizes Abbott-Hanson's [8] construction. 
+Rolwey named these partitions "templates", and we will keep this name in the entire article. Finding suitable templates and applying his 
+method to these will allow us to find new lower bounds for Schur methods.
 
@@
 \begin{definition}
-Let \( n \in \mathbb{N}^*\), there exists a greatest integer that we note \(SE_+(n)\) (resp.
-\(SE_-(n)\)) such that \( [\![1, SE_+(n)]\!]\) (resp.
-\( [\![1, SE_-(n)]\!]\)) can be partitionned (resp.
-can not be partionned) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
+Let \( n \in \mathbb{N}^*\), there exists a greatest integer that we note \(SE_+(n)\) (resp. \(SE_-(n)\)) such that \( [\![1, SE_+(n)]\!]\) 
+(resp. \( [\![1, SE_-(n)]\!]\)) can be partitionned (resp. can not be partionned) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
 \[
@@
 
-In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the integer \(WE_+(n)\) to build suitable templates.
+In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the integer \(WE_+(n)\) 
+to build suitable templates.
 
@@
 \begin{theorem}
-Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$.
-If there exists a partition of $r$ weakly sum-free subsets of $[\![1,n]\!]$ and a partition of $s$ sum-free subsets of $[\![1,p]\!]$ then there exists a partition of $r+s$ weakly sum-free subsets of $[\![1,p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n]\!]$
+Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$. If there exists a partition of $r$ weakly sum-free subsets of $[\![1,n]\!]$ and a partition of $s$ sum-free 
+subsets of $[\![1,p]\!]$ then there exists a partition of $r+s$ weakly sum-free subsets of $[\![1,p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n]\!]$
 \end{theorem}
@@
 In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the subsets, that is by 
-enforcing that \(m_1 < ... < m_k\). The correspond clauses are: \linebreak
+enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
 \textbf{symmetry breaking:}  \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!], x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
 
-\subsection{The search space previously used in computer search for lower bound may not contain the optimal partitions}
+\subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
 
 Rowley's new lower bound for \(WS(6)\) (642)  \hyperlink{label2}{\textbf{[2]}} was a quite significant improvement upon the former 
-best known lower bound (582). This previous lower bound was found using a computer with Monte-Carlo methods and by making the 
+best known lower bound (582). This previous lower bound was found using a computer (often with Monte-Carlo) methods and by making the 
 assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small values of \(n\).
@@
 Every weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets starts with the following sequence 1121222133. Then 11 is always 
-either in subset 1 or 3, 12 is always in subset 3 and so. For every integer in \([\![1,65]\!]\), we computed in which subset it can appear. 
+either in subset 1 or 3, 12 is always in subset 3 and so on. For every integer in \([\![1,65]\!]\), we computed in which subset it can appear. 
 By using this constraints, we could then compute for every integer in \([\![1,185]\!]\), in which subset it can appear in a weakly sum-free 
@@
 
+\par
+The above theorem shows that the previous lower bound for \(WS(6)\) is optimal in the search space considered by the papers which found it. 
+Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geq 590\) which does not have a template-like structure 
+would be extremely interesting since it could give indications on a new search space for improving lower bounds with a computer. More generally, 
+it questions the search space previously used for finding lower bounds for \(WS(n)\) with a computer. In particular, to our knowledge every paper 
+that found the lower bound \(WS(5) \geq 196\) used this assumption [reference necessaire]. Therefore one may wonder if this actually a good lower 
+bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has to verify.
+
 \subsection{Weak Schur number five}
+As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
+we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same method as the previous subsection.
 

### 2021-04-07 article/article.tex
remarkgit add .git add .git add .git add .git add .git add .git add .git add .

@@
 \newtheorem{theorem}{Theorem}[section]
-\newtheorem{computational theorem}{Computational Theorem}[section]
+\newtheorem{computational theorem}{Computational Theorem}[theorem]
 \newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{remark}{Remark}[section]
 
@@
 
+\begin{remark}
+The performance of
+\end{remark}
+
 \subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
@@
 As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
-we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same method as the previous subsection.
+we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same type of methods as in the
+ previous subsection.
+
+\par
+First
+
+\begin{computational theorem}
+If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). 
+\end{computational theorem}
+
+More precisely, we verified the following results using the glucose SAT solver [reference].
+
+\begin{tabular}{| c | *{21}{ p{2mm} |}}
+	\hline
+	\(m_4\)                   &   4   &   5   &   6  &   7   &   8   &   9   &  10  &  11  &  12  &  13  &  14  &  15  &  16  &  17  &  18  &  19  &  20  &  21  &  22  &  23  &  24  \\ 
+	\hline
+	\(WS(4 | m_4) + 1\) &  55  &  59  &  60  &  59  &  59  &  60  &  60  &  60  &  60  &  64  &  63  &  64  &  61  &  64  &  63  &  65  &  65  &  65  &  65  &  66  &  67  \\
+	\hline
+	\(max~m_5\)           &        &       &        &        &       &        &       &        &        &       &        &       &        &       &        &        &       &        &       &        &  53  \\
+	\hline
+\end{tabular}
 

### 2021-04-07 article/article.tex
local
label SAT

@@
 \subsection{Reformulation as a SAT problem}
+\label{SAT}
 
@@
 \begin{remark}
-The performance of
+For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary significantly according to the problem. 
+For instance, we used two different SAT solvers in the next two next subsections.
 \end{remark}
@@
 \par
-First
+\hyperlink{label4}{\textbf{[4]}} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of \([\![1,197]\!]\) with  
+\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only assuming \(m_5 = 67\) even after several 
+weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5 seconds with the SAT solver glucose 
+on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here but in the rest of this subsection, we used the parallel version of glucose). 
+The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free subsets starts with a partition of 
+\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among the 3 partitions of \([\![1,23]\!]\) in 
+3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two different subsets. We hardcoded 
+this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation time.
 
@@
 
-More precisely, we verified the following results using the glucose SAT solver [reference].
+More precisely, we verified the following results.
 

### 2021-04-07 article/article.tex
local

--- 2021-04-07 article/article.tex
@@
 
-\subsection{}
+\begin{remark}
+\(SE_+\) and \(S\) have the same asymptotic growth rate.
+\end{remark}
 
+\subsection{Inequaties on SE_+}
+
+The main result on \(SE_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(SE_+\).
+
+\begin{theorem}
+Let \(n, k \in \mathbb{N}^*\), we have \\
+\[ S(n+k) \geq SE_+(k+1)S(n) \]
+\end{theorem}
+
+Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
+hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
+a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
+inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
 \subsection{}

### 2021-04-07 article/article.tex
ajout tableau de données schur

--- 2021-04-07 article/article.tex
@@
 
+\usepackage[table]{xcolor}
+
 \newtheorem{definition}{Definition}[section]
@@
 \newtheorem{theorem}{Theorem}[section]
-\newtheorem{computational theorem}{Computational Theorem}[theorem]
+\newtheorem{computational theorem}{Computational Theorem}[section]
 \newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{remark}{Remark}[section]
 
@@
 
-\begin{remark}
-\(SE_+\) and \(S\) have the same asymptotic growth rate.
-\end{remark}
+\subsection{}
 
-\subsection{Inequaties on SE_+}
+\subsection{New lower bounds for Schur numbers}
 
-The main result on \(SE_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(SE_+\).
+The previous inequalities gives new lower bounds for \(S(n)\) for
+\( n \in [\![9,+\infty]\!] \backslash \{13\} \). We compute the lower
+bounds values for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the values for \( n = 8\) and \(n = 13\) were already obtained thanks to the first one, found by Rowley.
+The best lower bounds are highlighted.\\
+\\
+\begin{center}
+\begin{tabular}{|*{5}{c|}}
+    \hline
+	 & 8 & 9 & 10 & 11 \\
+	\hline
+	\(33S(n-3) + 6 \) & \cellcolor{yellow} 5286 & 17694 & 55446 & 174444\\
+	\hline
+	\(111S(n-4) + 43 \) & 4927 & \cellcolor{yellow} 17803 & 59539 & 186523\\
+	\hline
+	\(380S(n-5) + 148 \) & 5088 & 16868 & \cellcolor{yellow} 60948 & \cellcolor{yellow} 203828 \\
+	\hline
+	\(1140S(n-6) + 528 \) & 5088 & 15348 & 50688 & 182928\\
+	\hline
+	\hline
+	& 12 & 13 & 14 & 15 \\
+	\hline
+	\(33S(n-3) + 6 \) & 587505 & \cellcolor{yellow} 2011290 & 6726330 & 21072090\\
+	\hline
+	\(111S(n-4) + 43 \) & 586789 & 1976176 & 6765271 & 22624951 \\
+	\hline
+	\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\
+	\hline
+	\(1140S(n-6) + 528 \) & 611568 & 1915728 & 6026568 & 20295948 \\
+	\hline
+\end{tabular}
+\end{center}
 
-\begin{theorem}
-Let \(n, k \in \mathbb{N}^*\), we have \\
-\[ S(n+k) \geq SE_+(k+1)S(n) \]
-\end{theorem}
-
-Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
-hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
-a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
-inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
-\subsection{}
+Except for 8, 9 and 13, the best lower bounds are obtained thanks to the third inequality \( 380S(n-5) + 148 \leqslant S(n) \).
+The table doesn't go any further, but the same inequality allows to improve the lower bounds for every \( n \in [\![15,+\infty]\!] \).
 
@@
 
-\begin{remark}
-The performance of
-\end{remark}
-
 \subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
@@
 As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
-we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same type of methods as in the
- previous subsection.
-
-\par
-First
-
-\begin{computational theorem}
-If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). 
-\end{computational theorem}
-
-More precisely, we verified the following results using the glucose SAT solver [reference].
-
-\begin{tabular}{| c | *{21}{ p{2mm} |}}
-	\hline
-	\(m_4\)                   &   4   &   5   &   6  &   7   &   8   &   9   &  10  &  11  &  12  &  13  &  14  &  15  &  16  &  17  &  18  &  19  &  20  &  21  &  22  &  23  &  24  \\ 
-	\hline
-	\(WS(4 | m_4) + 1\) &  55  &  59  &  60  &  59  &  59  &  60  &  60  &  60  &  60  &  64  &  63  &  64  &  61  &  64  &  63  &  65  &  65  &  65  &  65  &  66  &  67  \\
-	\hline
-	\(max~m_5\)           &        &       &        &        &       &        &       &        &        &       &        &       &        &       &        &        &       &        &       &        &  53  \\
-	\hline
-\end{tabular}
+we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same method as the previous subsection.
 

### 2021-04-07 article/article.tex
truc

--- 2021-04-07 article/article.tex
@@
 a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
-inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
+inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperlink{SAT}{SAT section}. \\
+
+The special case \(k \in {1, 2} \) provides Rowley's inequalities \hyperlink{label2}{\textbf{[2]}}, \(S(n+1) \geq 4S(n)+2\) and \(S(n+2) \geq 13S(n)+8\). 
+In this case, \(SE_+(2) = 4 = S(2)\) and \(SE_+(3) = 13 = S(3)\). We found other inequalities as well.
+
 \subsection{}

### 2021-04-07 article/article.tex
fichiers

--- 2021-04-07 article/article.tex
@@
 
-\section{Abstract}
+\include{intro.tex}
 
-\section{Introduction, context and notations}
+\include{schur.tex}
 
-We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.
+\include{weakschur.tex}
 
-\begin{definition}
-A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} when:
-\[ \forall (a,b) \in A^2 \text{, } a+b \notin A\]
-\end{definition}
-
-\begin{definition}
-A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} when:
-\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B\]
-\end{definition}
-
-Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free
-subsets. Given \(m\) and \(n\) two integers, we are interested in partitioning the set of integers from 1 to \(m\) into
-\(n\) weakly sum-free subsets.
-
-\begin{notation}
-We denote by \([\![1,n]\!]\) the set of integers \(\{1, 2, ..., n\}\).
-\end{notation}
-
-Schur proved in \hyperlink{label1}{\textbf{[1]}} that given a number of subsets \(n\), there exists a value of \(m\)
-such that there exists no partition of \([\![1,p]\!]\) into \(n\) sum-free subsets for any \(p \geqslant m\). A similar
-property holds for weakly sum-free subsets (reference necessaire). These observations lead to the following definitions.
-
-\begin{definition}
-Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we note \(S(n)\) (\textit{resp. \(WS(n)\)}) such that
-\([\![1,S(n)]\!]\) (resp. \([\![1,WS(n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
-subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(WS(n)\) the \(n\)\textsuperscript{th} weak
-Schur number}.
-\end{definition}
-
-\begin{notation}
-For a partition of \([\![1, n]\!]\) in \(k\) subsets, we generally note these subsets \(A_1, ..., A_k\). We also note \(m_i = \text{min}(A_i)\). 
-By ordering the subsets, we mean assuming that \(m_1 < ... < m_k\). However, if not specified we do not make this hypothesis since we 
-do not always consider partitions in which every subset plays a symmetric role.
-\end{notation}
-
-\section{Schur numbers}
-
-\qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's numbers, Rowley 
-introduces partitions verifying some properties which can be extended using method which generalizes Abbott-Hanson's [8] construction. 
-Rolwey named these partitions "templates", and we will keep this name in the entire article. Finding suitable templates and applying his 
-method to these will allow us to find new lower bounds for Schur methods.
-
-\subsection{Definition of SE\(_+\)}
-
-\begin{definition}
-Let \( n \in \mathbb{N}^*\), there exists a greatest integer that we note \(SE_+(n)\) (resp. \(SE_-(n)\)) such that \( [\![1, SE_+(n)]\!]\) 
-(resp. \( [\![1, SE_-(n)]\!]\)) can be partitionned (resp. can not be partionned) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
-\[
-\forall k \in [\![1, n-1]\!], \forall (x,y) \in A_k^2, x+y > SE_+(n)
-\Longrightarrow x+y-SE_+(n) \notin A_k
-\]
-\end{definition}
-We notice that in general, unlike regular Schur numbers, we don't have \(SE_+(n) + 1 \neq SE_-(n)\)
-
-\begin{theorem}
-Let \(n \in [\![2, +\infty]\!]\), we have :
-\[
-2S(n-1)+1 \leqslant SE_+(n) \leqslant S(n)
-\]
-\end{theorem}
-
-\subsection{}
-
-\subsection{New lower bounds for Schur numbers}
-
-The previous inequalities gives new lower bounds for \(S(n)\) for
-\( n \in [\![9,+\infty]\!] \backslash \{13\} \). We compute the lower
-bounds values for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the values for \( n = 8\) and \(n = 13\) were already obtained thanks to the first one, found by Rowley.
-The best lower bounds are highlighted.\\
-\\
-\begin{center}
-\begin{tabular}{|*{5}{c|}}
-    \hline
-	 & 8 & 9 & 10 & 11 \\
-	\hline
-	\(33S(n-3) + 6 \) & \cellcolor{yellow} 5286 & 17694 & 55446 & 174444\\
-	\hline
-	\(111S(n-4) + 43 \) & 4927 & \cellcolor{yellow} 17803 & 59539 & 186523\\
-	\hline
-	\(380S(n-5) + 148 \) & 5088 & 16868 & \cellcolor{yellow} 60948 & \cellcolor{yellow} 203828 \\
-	\hline
-	\(1140S(n-6) + 528 \) & 5088 & 15348 & 50688 & 182928\\
-	\hline
-	\hline
-	& 12 & 13 & 14 & 15 \\
-	\hline
-	\(33S(n-3) + 6 \) & 587505 & \cellcolor{yellow} 2011290 & 6726330 & 21072090\\
-	\hline
-	\(111S(n-4) + 43 \) & 586789 & 1976176 & 6765271 & 22624951 \\
-	\hline
-	\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\
-	\hline
-	\(1140S(n-6) + 528 \) & 611568 & 1915728 & 6026568 & 20295948 \\
-	\hline
-\end{tabular}
-\end{center}
-
-Except for 8, 9 and 13, the best lower bounds are obtained thanks to the third inequality \( 380S(n-5) + 148 \leqslant S(n) \).
-The table doesn't go any further, but the same inequality allows to improve the lower bounds for every \( n \in [\![15,+\infty]\!] \).
-
-\section{Weak Schur numbers}
-
-In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the integer \(WE_+(n)\) 
-to build suitable templates.
-
-\subsection{Lower bound for Weak Schur numbers using Schur and Weak Schur numbers}
-
-The following theorem, inspired by Rowley's work, was found and proved by Romain Ageron.
-\begin{theorem}
-Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$. If there exists a partition of $r$ weakly sum-free subsets of $[\![1,n]\!]$ and a partition of $s$ sum-free 
-subsets of $[\![1,p]\!]$ then there exists a partition of $r+s$ weakly sum-free subsets of $[\![1,p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n]\!]$
-\end{theorem}
-In particular, if we choose $n = WS(r)$ and $p = WS(s)$ in the last theorem, the next corollary follows.
-\begin{corollary}
-$ \forall (n,m) \in (\mathbb{N}^*)^2 \text{, } WS(n+m) \geqslant S(m) \left (WS(n) + \left \lceil \frac{WS(n)}{2} \right \rceil +1 \right) + WS(n)$
-\end{corollary}
-\textsc{Proof :} Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$,  $N = p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n$, $\alpha = \left \lceil \frac{n}{2} \right \rceil > 0$ and $\beta = n + \alpha + 1$.
-We denote by $f$ the projection of the equivalence relation induced by the partition of $[\![1,n]\!]$ and $g$ the one induced by the partition of $[\![1,p]\!]$.
-Each equivalence class is represented by a single integer, therefore :
-\[ f : [\![1,n]\!] \longrightarrow [\![1,r]\!] \text{ and } \forall (x,y) \in [\![1,n]\!]^2, \left\{
-    \begin{array}{ll}
-        x \neq y \\
-        f(x) = f(y)
-    \end{array}
-\right.
-\Longrightarrow f(x+y) \neq f(x)
-\]
-\[g : [\![1,p]\!] \longrightarrow [\![1,s]\!] \text{ and } \forall (x,y) \in [\![1,n]\!]^2 \text{, } f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
-\]
-Let us start by parting the integers of $[\![1,N]\!]$ in two subsets $\mathcal{A}$ and $\mathcal{B}$ where $\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]\}$ and $\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}$.\\
-\\
-First, \underline{$\mathcal{A} \cap \mathcal{B} = \varnothing$} : \\
-Suppose there exists $x \in \mathcal{A} \cap \mathcal{B} = \varnothing$.
-Then there are $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]$ and $(b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ such that $x = a\beta + u = b\beta +v$.
-By definition of $\alpha$ and  $\beta$ we have $u \in [\![\alpha + 1,n]\!] \subset [\![0,\beta - 1]\!]$.
-From there, we distinguish two cases :
-\begin{itemize}
-\item If $v \in [\![0,\alpha]\!]$ then $v \in [\![0,\beta - 1]\!]$ and $v \neq u$ because $v < \alpha + 1 \leqslant u$
-\item If $v \in [\![-\alpha,-1]\!]$, we note $\tilde{v} = \beta + v$ and thus have $x = (b-1)\beta + \tilde{v}$ with $\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]$ and $\tilde{v} \neq u$ because $u < n+1 = \beta - \alpha \leqslant \tilde{v}$.
-\end{itemize}
-In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of $x$ by $\beta$.\\
-\\
-Then, we have \underline{$\mathcal{A} \cup \mathcal{B} = [\![1,N]\!]$}:
-\begin{itemize}
-\item On one hand : $1 = \text{min($\mathcal{A}$)} \leqslant \text{max($\mathcal{A}$)} = p\beta + n = N$ and $1 \leqslant \beta - \alpha = \text{min($\mathcal{B}$)} \leqslant \text{max($\mathcal{B}$)} = p\beta + \alpha \leqslant N$, which gives $\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]$.
-\item On the other hand, let $x \in  [\![1,N]\!]$.
-If $x \leqslant \alpha$, we directly have $x \in \mathcal{A}$, let us then suppose that $x > \alpha$ and write $x = a\beta + u$ the euclidean division of $x$ by $\beta$.
-We have $x \leqslant N$, thus $a \leqslant p$.
-We distinguish three cases : \\
-- If $u \in [\![0,\alpha]\!]$ then we necessarily have $a \geqslant 1$ because $x > \alpha$, and so $x \in \mathcal{B}$.\\
-- If $u \in [\![\alpha + 1,n]\!]$, then $x \in \mathcal{A}$. \\
-- If $u \in [\![n + 1,\beta - 1]\!]$ then $x = (a+1)\beta - (\beta - u)$ with $-\alpha \leqslant \beta - u \leqslant 0$.
-Furthermore, $a \leqslant p - 1$, else we would have $x > N$, and so $x \in \mathcal{B}$ \\
-In any case, $x \in \mathcal{A} \cup \mathcal{B}$ and we can thus conclude that $[\![1,N]\!] \subset \mathcal{A} \cup \mathcal{B}$.
-\end{itemize}
-This first partition of $[\![1,N]\!]$ will help us to define our final partition by the projection of its equivalence relation.
-We thereby define $h : [\![1,N]\!] \longrightarrow [\![1,r+s]\!]$ as such :\\
-- If $x \in \mathcal{A}$ then $h(x) = f(x \text{ mod } \beta)$ (well defined because $x \text{ mod } \beta \in [\![1,N]\!]$)\\
-- If $x \in \mathcal{B}$ then $x = a\beta + u$ with a unique $(a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ and we define $h(x) = r + g(a)$\\
-The fact that $(\mathcal{A}, \mathcal{B})$ is a partition of $[\![1,N]\!]$ ensures that this definition of $h$ is valid. We then have to verify that $h$ induces weakly sum-free subsets.\\
-\\
-\underline{The classes of equivalence $h(x)$ for $x \in \mathcal{A}$ are weakly sum-free :}
-\\
-\\
-Let $(x,y) \in \mathcal{A}^2$ such that $h(x) = h(y)$, $x \neq y$ and $x + y \leqslant N$
-\begin{itemize}
-\item If $(x,y) \in [\![1,\alpha]\!]^2$ :\\
-We have $x + y \leqslant 2\alpha \leqslant n$ and $x + y = 0\beta + x + y$, therefore $x + y \in \mathcal{A}$.
-Then, by definition : $h(x) = f(x)$, $h(y) = f(y)$ and $h(x+y) = f(x+y)$, which gives us, thanks to the property verified by $f$, that $h(x+y) \neq h(x)$.
-\item If $(x,y) \in [\![1,\alpha]\!] \times ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )$ :\\
-We write $y = a\beta + u$ with $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]$.
-Then $x+y = a\beta + x + u = (a+1)\beta + x + u - \beta$, and if $x + u > n$ it follows that $a \leqslant p-1$ since $x+y \leqslant N$, and $-\alpha \leqslant x + u - \beta \leqslant -1$.
-Therefore $x+y \in \mathcal{B}$ and $h(x+y) \neq h(x) = f(x)$ by definition of h.
-On the contrary, if $x - u \leqslant n$, then $x+y \in \mathcal{A}$ and $h(x+y) = f(x+u)$ because $x+u$ is actually the remainder of the euclidean division of $x+y$ by $\beta$.
-Moreover, $h(x) = f(x)$, $x < u$ and, with our initial hypothesis, $h(x) = h(y) = f(u)$.
-The property verified by $f$ gives us $f(x+u) \neq f(x)$ which can be rewritten as $h(x+y) \neq h(x)$.
-\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] ) \times [\![1,\alpha]\!]$ : \\
-This case is handled exactly like the previous one by swaping the roles of $x$ and $y$.
-\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )^2$ : \\
-We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![0,p]\!] \times [\![\alpha + 1,n]\!]$.
-Then $x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta$ with $a+b \leqslant p-1$ (else we would have $x+y > N$ because $u+v > n$) and $-\alpha \leqslant u + v - \beta \leqslant \alpha$, therefore $x+y \in \mathcal{B}$ and by definition $h(x+y) \neq h(x)$.
-\end{itemize}
-In any case, $h(x+y) \neq h(x)$ and the classes of equivalence $h(x)$ for $x \in \mathcal{A}$ are weakly sum-free.\\
-\\
-\underline{The classes of equivalence $h(x)$ for $x \in \mathcal{B}$ are weakly sum-free :}
-\\
-\\
-Let $(x,y) \in \mathcal{B}^2$ such that $h(x) = h(y)$, $x \neq y$ and $x + y \leqslant N$.\\
-We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![1,p]\!] \times [\![-\alpha,\alpha]\!]$.
-We have $h(x) = r + g(a)$ and $h(y) = r + g(b)$, therefore $g(a) = g(b)$.
-We also have $x+y = (a+b)\beta + u +v$.\\
-If $u + v \in [\![-\alpha,\alpha]\!]$, then $x+y \in \mathcal{B}$ and $h(x+y) = g(a+b)$, hence we can deduce that $h(x+y) \neq h(x)$ because of the property verified by $g$.
-On the contrary, if $u+v \notin [\![-\alpha,\alpha]\!]$, then necessarily $x+y \in \mathcal{A}$.
-Suppose $x+y \in \mathcal{B}$, then $x+y = c\beta + w$ with $(c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$.
-Thus, $c\beta + w = (a+b)\beta + u + v$ and $(a+b-c)\beta = w-u-v$.
-Furthermore $a+b-c \neq 0$, else we would have $u+v = w \in [\![-\alpha,\alpha]\!]$.
-This finally leads to the following inequality :
-\[\beta \leqslant |a+b-c|\beta = |w-u-v| \leqslant |w| + |u| + |v| \leqslant 3\alpha \leqslant n + \alpha < \beta
-\]
-which is absurd.
-We can therefore conclude that $x+y \in \mathcal{A}$ and by definition of $h$, $h(x+y) \neq h(x)$, proving that the classes of equivalence $h(x)$ for $x \in \mathcal{B}$ are weakly sum-free.\\
-\\
-Finally, we have showed that every classe of equivalence induced by $h$ is weakly sum-free, which ends the proof.
-
-\section{About the construction of lower bounds for weak Schur numbers using a computer}
-
-In this section, we first reframe the question of the existence of (weakly) sum-free partitions as a boolean
-satisfiability (SAT) problem. We then provide evidence which indicates that the main assumption made by papers which
-found the previous best known lower bounds for weak Schur numbers may not be correct. Finally, we obtain stronger
-results than those previously known for \(WS(5)\) while gaining several orders of magnitude in computation time by 
-giving additional information to the SAT solver without losing in generality. In this section, we assume that the subsets are ordered.
-
-\subsection{Reformulation as a SAT problem}
-
-We encode the existence of (weakly) sum-free partitions as propositional formulae like in \hyperlink{label3}{\textbf{[3]}} and then use 
-SAT solvers to determine whether these formulae are satisfiable.
-
-\begin{definition}
-A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a negative literal) where \(v\) 
-takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a conjunction of clauses: it 
-is a propositional formula in \textit{conjonctive normal form} (CNF).
-\end{definition}
-
-\begin{definition}
-An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A literal \(l\) is 
-\textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\) 
-(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A clause is \textit{satisfied} 
-by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is \textit{satisfied} by an assignment 
-\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an assignment that satisfies it; 
-otherwise it is \textit{unsatisfiable}.
-\end{definition}
-
-We then encode the existence of a partition of \([\![1,n]\!]\) in \(k\)  weakly sum-free subsets as follows: for every integer 
-\(i \in [\![1,n]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!], x^{(i)}_c = 1 \iff i \in A_c\). 
-The corresponding clauses are:
-
-\begin{itemize}
-\item \textbf{sumfree:} \(\forall c \in  [\![1,k]\!], \forall (i, j) \in [\![1,n]\!]^2, (i \neq j ~ \text{and} ~ i + j \leq n) \implies \lnot x^{(i)}_c 
-\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
-\item \textbf{union:} \(\forall i \in [\![1,n]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
-\item \textbf{disjoint:} \(\forall i \in [\![1,n]\!],\forall (c_1, c_2) \in  [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
-\end{itemize}
-
-In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the subsets, that is by 
-enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
-\textbf{symmetry breaking:}  \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!], x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
-
-\subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
-
-Rowley's new lower bound for \(WS(6)\) (642)  \hyperlink{label2}{\textbf{[2]}} was a quite significant improvement upon the former 
-best known lower bound (582). This previous lower bound was found using a computer (often with Monte-Carlo) methods and by making the 
-assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small values of \(n\).
-Therefore, one may wonder whether the limiting factor is the assumption or the methods used to search for partitions. It appears that 
-the latter is correct.
-
-\begin{computational theorem}
-There is no weakly sum-free partition of \([\![1,583]\!]\) in 6 parts such that:
-\begin{itemize}
-\item \(m_5 \ge 66\)
-\item \(m_6 \ge 186\)
-\item \([\![210,349]\!] \subset A_6\)
-\end{itemize}  
-\end{computational theorem}
-
-This result was obtained in 8 hours with the SAT solver plingeling \hyperlink{label5}{\textbf{[5]}} on a 2.60 GHz Intel i7 processor PC.
-However, simply encoding the existence of such a partition as explained in the previous subsection would not result in a reasonable 
-computation time. In order to help the SAT solver, we add additional information in the propositional formula. We did not quantify the 
-speedup, but it most likely allows us to gain several order of magnitude in computation time as we explain in the next subsection.
-
-\par
-Every weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets starts with the following sequence 1121222133. Then 11 is always 
-either in subset 1 or 3, 12 is always in subset 3 and so on. For every integer in \([\![1,65]\!]\), we computed in which subset it can appear. 
-By using this constraints, we could then compute for every integer in \([\![1,185]\!]\), in which subset it can appear in a weakly sum-free 
-partition of  \([\![1,185]\!]\) which starts with a  weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets. Adding these constraints to the 
-formula corresponding to the above theorem gives additional information to the SAT solver without losing in generality.
-
-\par
-The above theorem shows that the previous lower bound for \(WS(6)\) is optimal in the search space considered by the papers which found it. 
-Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geq 590\) which does not have a template-like structure 
-would be extremely interesting since it could give indications on a new search space for improving lower bounds with a computer. More generally, 
-it questions the search space previously used for finding lower bounds for \(WS(n)\) with a computer. In particular, to our knowledge every paper 
-that found the lower bound \(WS(5) \geq 196\) used this assumption [reference necessaire]. Therefore one may wonder if this actually a good lower 
-bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has to verify.
-
-\subsection{Weak Schur number five}
-As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
-we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same method as the previous subsection.
+\include{sat.tex}
 

### 2021-04-07 article/intro.tex
fichiers

\section{Abstract}

\section{Introduction, context and notations}

We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.

\begin{definition}
A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} when:
\[ \forall (a,b) \in A^2 \text{, } a+b \notin A\]
\end{definition}

\begin{definition}
A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} when:
\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B\]
\end{definition}

Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free
subsets. Given \(m\) and \(n\) two integers, we are interested in partitioning the set of integers from 1 to \(m\) into
\(n\) weakly sum-free subsets.

\begin{notation}
We denote by \([\![1,n]\!]\) the set of integers \(\{1, 2, ..., n\}\).
\end{notation}

Schur proved in \hyperlink{label1}{\textbf{[1]}} that given a number of subsets \(n\), there exists a value of \(m\)
such that there exists no partition of \([\![1,p]\!]\) into \(n\) sum-free subsets for any \(p \geqslant m\). A similar
property holds for weakly sum-free subsets (reference necessaire). These observations lead to the following definitions.

\begin{definition}
Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we note \(S(n)\) (\textit{resp. \(WS(n)\)}) such that
\([\![1,S(n)]\!]\) (resp. \([\![1,WS(n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(WS(n)\) the \(n\)\textsuperscript{th} weak
Schur number}.
\end{definition}

\begin{notation}
For a partition of \([\![1, n]\!]\) in \(k\) subsets, we generally note these subsets \(A_1, ..., A_k\). We also note \(m_i = \text{min}(A_i)\). 
By ordering the subsets, we mean assuming that \(m_1 < ... < m_k\). However, if not specified we do not make this hypothesis since we 
do not always consider partitions in which every subset plays a symmetric role.
\end{notation}

### 2021-04-07 article/schur.tex
fichiers

\section{Schur numbers}

\qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's numbers, Rowley 
introduces partitions verifying some properties which can be extended using method which generalizes Abbott-Hanson's [8] construction. 
Rolwey named these partitions "templates", and we will keep this name in the entire article. Finding suitable templates and applying his 
method to these will allow us to find new lower bounds for Schur methods.

\subsection{Definition of SE\(_+\)}

\begin{definition}
	Let \( n \in \mathbb{N}^*\), there exists a greatest integer that we note \(SE_+(n)\) (resp. \(SE_-(n)\)) such that \( [\![1, SE_+(n)]\!]\) 
	(resp. \( [\![1, SE_-(n)]\!]\)) can be partitionned (resp. can not be partionned) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
	\[
	\forall k \in [\![1, n-1]\!], \forall (x,y) \in A_k^2, x+y > SE_+(n)
	\Longrightarrow x+y-SE_+(n) \notin A_k
	\]
\end{definition}
We notice that in general, unlike regular Schur numbers, we don't have \(SE_+(n) + 1 \neq SE_-(n)\)

\begin{theorem}
	Let \(n \in [\![2, +\infty]\!]\), we have :
	\[
	2S(n-1)+1 \leqslant SE_+(n) \leqslant S(n)
	\]
\end{theorem}

\begin{remark}
	\(SE_+\) and \(S\) have the same asymptotic growth rate.
\end{remark}

\subsection{Inequaties on SE_+}

The main result on \(SE_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(SE_+\).

\begin{theorem}
	Let \(n, k \in \mathbb{N}^*\), we have \\
	\[ S(n+k) \geq SE_+(k+1)S(n) \]
\end{theorem}

Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.

\subsection{New lower bounds for Schur numbers}

The previous inequalities gives new lower bounds for \(S(n)\) for
\( n \in [\![9,+\infty]\!] \backslash \{13\} \). We compute the lower
bounds values for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the values for \( n = 8\) and \(n = 13\) were already obtained thanks to the first one, found by Rowley. The best lower bounds are highlighted.\\
\\
\begin{center}
\begin{tabular}{|*{5}{c|}}
    \hline
	 & 8 & 9 & 10 & 11 \\
	\hline
	\(33S(n-3) + 6 \) & \cellcolor{yellow} 5286 & 17694 & 55446 & 174444\\
	\hline
	\(111S(n-4) + 43 \) & 4927 & \cellcolor{yellow} 17803 & 59539 & 186523\\
	\hline
	\(380S(n-5) + 148 \) & 5088 & 16868 & \cellcolor{yellow} 60948 & \cellcolor{yellow} 203828 \\
	\hline
	\(1140S(n-6) + 528 \) & 5088 & 15348 & 50688 & 182928\\
	\hline
	\hline
	& 12 & 13 & 14 & 15 \\
	\hline
	\(33S(n-3) + 6 \) & 587505 & \cellcolor{yellow} 2011290 & 6726330 & 21072090\\
	\hline
	\(111S(n-4) + 43 \) & 586789 & 1976176 & 6765271 & 22624951 \\
	\hline
	\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\
	\hline
	\(1140S(n-6) + 528 \) & 611568 & 1915728 & 6026568 & 20295948 \\
	\hline
\end{tabular}
\end{center}

Except for 8, 9 and 13, the best lower bounds are obtained thanks to the third inequality \( 380S(n-5) + 148 \leqslant S(n) \). The table doesn't go any further, but the same inequality allows to improve the lower bounds for every \( n \in [\![15,+\infty]\!] \).

### 2021-04-07 article/article.tex
kaboom

--- 2021-04-07 article/article.tex
@@
 
-\begin{remark}
-\(SE_+\) and \(S\) have the same asymptotic growth rate.
-\end{remark}
-
-\subsection{Inequaties on SE_+}
-
-The main result on \(SE_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(SE_+\).
-
-\begin{theorem}
-Let \(n, k \in \mathbb{N}^*\), we have \\
-\[ S(n+k) \geq SE_+(k+1)S(n) \]
-\end{theorem}
-
-Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
-hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
-a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
-inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperlink{SAT}{SAT section}. \\
-
-The special case \(k \in {1, 2} \) provides Rowley's inequalities \hyperlink{label2}{\textbf{[2]}}, \(S(n+1) \geq 4S(n)+2\) and \(S(n+2) \geq 13S(n)+8\). 
-In this case, \(SE_+(2) = 4 = S(2)\) and \(SE_+(3) = 13 = S(3)\). We found other inequalities as well.
+\subsection{}
 
@@
 
+\begin{notation}
+Let \(P\) be a predicate. We denote
+\end{notation}
+
 \par
@@
 3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two different subsets. We hardcoded 
-this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation time.
+this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation time. We also give the stronger 
+following result.
 
@@
 
-More precisely, we verified the following results.
+More precisely, we verified the following results (\(max~m_5\) is the greatest value of \(m_5\) for which we have not verified that \(WS(5 | m_5) \leq 196\)).
 

### 2021-04-07 article/sat.tex

\section{About the construction of lower bounds for weak Schur numbers using a computer}

In this section, we first reframe the question of the existence of (weakly) sum-free partitions as a boolean
satisfiability (SAT) problem. We then provide evidence which indicates that the main assumption made by papers which
found the previous best known lower bounds for weak Schur numbers may not be correct. Finally, we obtain stronger
results than those previously known for \(WS(5)\) while gaining several orders of magnitude in computation time by 
giving additional information to the SAT solver without losing in generality. In this section, we assume that the subsets are ordered.

\subsection{Reformulation as a SAT problem}

We encode the existence of (weakly) sum-free partitions as propositional formulae like in \hyperlink{label3}{\textbf{[3]}} and then use 
SAT solvers to determine whether these formulae are satisfiable.

\begin{definition}
	A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a negative literal) where \(v\) 
	takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a conjunction of clauses: it 
	is a propositional formula in \textit{conjonctive normal form} (CNF).
\end{definition}

\begin{definition}
	An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A literal \(l\) is 
	\textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\) 
	(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A clause is \textit{satisfied} 
	by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is \textit{satisfied} by an assignment 
	\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an assignment that satisfies it; 
	otherwise it is \textit{unsatisfiable}.
\end{definition}

We then encode the existence of a partition of \([\![1,n]\!]\) in \(k\)  weakly sum-free subsets as follows: for every integer 
\(i \in [\![1,n]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!], x^{(i)}_c = 1 \iff i \in A_c\). 
The corresponding clauses are:

\begin{itemize}
	\item \textbf{sumfree:} \(\forall c \in  [\![1,k]\!], \forall (i, j) \in [\![1,n]\!]^2, (i \neq j ~ \text{and} ~ i + j \leq n) \implies \lnot x^{(i)}_c 
	\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
	\item \textbf{union:} \(\forall i \in [\![1,n]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
	\item \textbf{disjoint:} \(\forall i \in [\![1,n]\!],\forall (c_1, c_2) \in  [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
\end{itemize}

In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the subsets, that is by 
enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
\textbf{symmetry breaking:}  \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!], x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)

\begin{remark}
	The performance of
\end{remark}

\subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}

Rowley's new lower bound for \(WS(6)\) (642)  \hyperlink{label2}{\textbf{[2]}} was a quite significant improvement upon the former 
best known lower bound (582). This previous lower bound was found using a computer (often with Monte-Carlo) methods and by making the 
assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small values of \(n\).
Therefore, one may wonder whether the limiting factor is the assumption or the methods used to search for partitions. It appears that 
the latter is correct.

\begin{computational theorem}
	There is no weakly sum-free partition of \([\![1,583]\!]\) in 6 parts such that:
	\begin{itemize}
		\item \(m_5 \ge 66\)
		\item \(m_6 \ge 186\)
		\item \([\![210,349]\!] \subset A_6\)
	\end{itemize}  
\end{computational theorem}

This result was obtained in 8 hours with the SAT solver plingeling \hyperlink{label5}{\textbf{[5]}} on a 2.60 GHz Intel i7 processor PC.
However, simply encoding the existence of such a partition as explained in the previous subsection would not result in a reasonable 
computation time. In order to help the SAT solver, we add additional information in the propositional formula. We did not quantify the 
speedup, but it most likely allows us to gain several order of magnitude in computation time as we explain in the next subsection.

\par
Every weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets starts with the following sequence 1121222133. Then 11 is always 
either in subset 1 or 3, 12 is always in subset 3 and so on. For every integer in \([\![1,65]\!]\), we computed in which subset it can appear. 
By using this constraints, we could then compute for every integer in \([\![1,185]\!]\), in which subset it can appear in a weakly sum-free 
partition of  \([\![1,185]\!]\) which starts with a  weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets. Adding these constraints to the 
formula corresponding to the above theorem gives additional information to the SAT solver without losing in generality.

\par
The above theorem shows that the previous lower bound for \(WS(6)\) is optimal in the search space considered by the papers which found it. 
Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geq 590\) which does not have a template-like structure 
would be extremely interesting since it could give indications on a new search space for improving lower bounds with a computer. More generally, 
it questions the search space previously used for finding lower bounds for \(WS(n)\) with a computer. In particular, to our knowledge every paper 
that found the lower bound \(WS(5) \geq 196\) used this assumption [reference necessaire]. Therefore one may wonder if this actually a good lower 
bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has to verify.

\subsection{Weak Schur number five}
As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same type of methods as in the
previous subsection.

\par
First

\begin{computational theorem}
	If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). 
\end{computational theorem}

More precisely, we verified the following results using the glucose SAT solver [reference].

\begin{tabular}{| c | *{21}{ p{2mm} |}}
	\hline
	\(m_4\)                   &   4   &   5   &   6  &   7   &   8   &   9   &  10  &  11  &  12  &  13  &  14  &  15  &  16  &  17  &  18  &  19  &  20  &  21  &  22  &  23  &  24  \\ 
	\hline
	\(WS(4 | m_4) + 1\) &  55  &  59  &  60  &  59  &  59  &  60  &  60  &  60  &  60  &  64  &  63  &  64  &  61  &  64  &  63  &  65  &  65  &  65  &  65  &  66  &  67  \\
	\hline
	\(max~m_5\)           &        &       &        &        &       &        &       &        &        &       &        &       &        &       &        &        &       &        &       &        &  53  \\
	\hline
\end{tabular}

### 2021-04-07 article/weakschur.tex

--- 2021-02-23 demonstration_romain.tex
@@
-\documentclass{article}
-\title{New theoretical lower bounds of weak Schur numbers using regular Schur numbers}
-\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{setspace}
-\usepackage[top=1cm]{geometry}
-\usepackage{graphicx}
-\usepackage[hyphens]{url}
-\usepackage{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
+\section{Weak Schur numbers}
 
-\newtheorem{definition}{Definition}[section]
-\newtheorem{notation}[definition]{Notation}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
+In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the integer \(WE_+(n)\) 
+to build suitable templates.
 
-\begin{document}
-\maketitle
-\section{Introduction, context and notations}
-We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.
-\begin{definition}
-A subset $A$ of $\mathbb{N}$ is said to be sum-free when :
-\[ \forall (a,b) \in A^2 \text{, } a+b \notin A
-\]
-\end{definition}
-\begin{definition}
-A subset $B$ of $\mathbb{N}$ is said to be weakly sum-free when :
-\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B
-\]
-\end{definition}
-Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free subsets.
-Given $m$ and $n$ two integers, we are interested in partitioning the set of integers from 1 to $m$ in $n$ weakly sum-free subsets.
-\begin{notation}
-We denote by $[\![1,n]\!]$ the set of integers $\{1, 2, ..., n\}$
-\end{notation}
-Schur proved in \hyperlink{label1}{\textbf{[1]}} that given a number of subsets $n$, there exists a value of $m$ such that there exists no partition of $[\![1,p]\!]$ in $n$ sum-free subsets for any $p \geqslant m$.
-This observation leads to the following definition.
-\begin{definition}
-Let $n \in \mathbb{N}^*$, there exists an integer that we note S(n) (\textit{respectively WS(n)}) such that $[\![1,S(n) + 1]\!]$ (respectively $[\![1,WS(n) + 1]\!]$) can not be partitioned in $n$ sum-free subsets (respectively in $n$ weakly sum-free subsets) while $[\![1,S(n)]\!]$ (respectively $[\![1,WS(n)]\!]$) can be.
-S(n) is called the n\textsuperscript{th} Schur number and WS(n) the n\textsuperscript{th} weak Schur number.
-\end{definition}
-The values of both Schur and weak Schur numbers are known only for small values of $n$, and our goal is to improve the lower bounds on weak Schur numbers for $n \geqslant 5$.
-At the time being, the best lower bounds for weak Schur numbers are established by Rowley in \hyperlink{label2}{\textbf{[2]}}.
-He greatly improved the former best values with a purely theoretical and constructive approach.
-More precisely, he managed to build interesting weakly sum-free partitions with sum-free partitions.
-With this, he found the following lower bounds :
-\[ WS(n+1) \geqslant 4S(n) + 2
-\]
-\[
-WS(n+2) \geqslant 13S(n) + 8
-\]
-Actually, Rowley's construction can be generalised to find a lower bound for $WS(n+m)$ for all $(n,m) \in (\mathbb{N}^*)^2$. This result and its demonstration are detailled in the next part.
-\section{A new theoretical lower bound for WS(n+m)}
+\subsection{Lower bound for Weak Schur numbers using Schur and Weak Schur numbers}
+
 The following theorem, inspired by Rowley's work, was found and proved by Romain Ageron.
 \begin{theorem}
-Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$.
-If there exists a partition of $r$ weakly sum-free subsets of $[\![1,n]\!]$ and a partition of $s$ sum-free subsets of $[\![1,p]\!]$ then there exists a partition of $r+s$ weakly sum-free subsets of $[\![1,p(n+\left \lfloor \frac{n}{2} \right \rfloor + 1)+n]\!]$
+	Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$. If there exists a partition of $r$ weakly sum-free subsets of $[\![1,n]\!]$ and a partition of $s$ sum-free 
+	subsets of $[\![1,p]\!]$ then there exists a partition of $r+s$ weakly sum-free subsets of $[\![1,p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n]\!]$
 \end{theorem}
@@
 \begin{corollary}
-$ \forall (n,m) \in (\mathbb{N}^*)^2 \text{, } WS(n+m) \geqslant S(m) \left (WS(n) + \left \lfloor \frac{WS(n)}{2} \right \rfloor +1 \right) + WS(n)$
+	$ \forall (n,m) \in (\mathbb{N}^*)^2 \text{, } WS(n+m) \geqslant S(m) \left (WS(n) + \left \lceil \frac{WS(n)}{2} \right \rceil +1 \right) + WS(n)$
 \end{corollary}
-\textsc{Proof :} Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$,  $N = p(n+\left \lfloor \frac{n}{2} \right \rfloor + 1)+n$, $\alpha = \left \lfloor \frac{n}{2} \right \rfloor > 0$ and $\beta = n + \alpha + 1$.
+\textsc{Proof :} Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$,  $N = p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n$, $\alpha = \left \lceil \frac{n}{2} \right \rceil > 0$ and $\beta = n + \alpha + 1$.
 We denote by $f$ the projection of the equivalence relation induced by the partition of $[\![1,n]\!]$ and $g$ the one induced by the partition of $[\![1,p]\!]$.
@@
 Finally, we have showed that every classe of equivalence induced by $h$ is weakly sum-free, which ends the proof.
-\section{References}
-\hypertarget{label1}{\textbf{[1]}} Schur, I.. "Über Kongruenz x ... (mod. p.).." Jahresbericht der Deutschen Mathematiker-Vereinigung 25 (1917): 114-116. \url{http://eudml.org/doc/145475} \\
-\hypertarget{label2}{\textbf{[2]}} F. Rowley, New Lower Bounds for Weak Schur Partitions, arXiv 2011.11292, \url{https://arxiv.org/pdf/2011.11292.pdf}
-\end{document}

### 2021-04-07 article/schur.tex
modif math mode

@@
+\documentclass{article}
+\title{New lower bounds for Schur and weak Schur numbers}
+\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}
+
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+\usepackage[english]{babel}
+\usepackage[hyphens]{url}
+\usepackage{hyperref}
+\usepackage[utf8]{inputenc}
+
+\usepackage[table]{xcolor}
+
+\newtheorem{definition}{Definition}[section]
+\newtheorem{notation}[definition]{Notation}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{computational theorem}{Computational Theorem}[section]
+\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{remark}{Remark}[section]
+
+\begin{document}
 \section{Schur numbers}
@@
 
-\subsection{Inequaties on SE_+}
+\subsection{Inequaties on \(SE_+\)}
 
@@
 \end{center}
-
 Except for 8, 9 and 13, the best lower bounds are obtained thanks to the third inequality \( 380S(n-5) + 148 \leqslant S(n) \).
 The table doesn't go any further, but the same inequality allows to improve the lower bounds for every \( n \in [\![15,+\infty]\!] \).
+\end{document}

### 2021-04-07 article/sat.tex

@@
 \begin{remark}
-	The performance of
+For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary significantly according to the problem.
+For instance, we used two different SAT solvers in the next two next subsections.
 \end{remark}
@@
 
+\begin{notation}
+Let \(P\) be a predicate. We denote
+\end{notation}
+
 \par
-First
+\hyperlink{label4}{\textbf{[4]}} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of \([\![1,197]\!]\) with
+\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only assuming \(m_5 = 67\) even after several
+weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5 seconds with the SAT solver glucose
+on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here but in the rest of this subsection, we used the parallel version of glucose).
+The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free subsets starts with a partition of
+\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among the 3 partitions of \([\![1,23]\!]\) in
+3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two different subsets. We hardcoded
+this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation time. We also give the stronger
+following result.
 
@@
 
-More precisely, we verified the following results using the glucose SAT solver [reference].
+More precisely, we verified the following results (\(max~m_5\) is the greatest value of \(m_5\) for which we have not verified that \(WS(5 | m_5) \leq 196\)).
 

### 2021-04-07 article/schur.tex
commit avant pull

--- 2021-04-07 article/schur.tex
@@
 	Let \(n, k \in \mathbb{N}^*\), we have \\
-	\[ S(n+k) \geq SE_+(k+1)S(n) \]
+	\[ S(n+k) \geqslant SE_+(k+1)S(n) \]
 \end{theorem}
@@
 inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
+Here are the best inequalities on Schur numbers so far :
+\[ S(n+1) \geq 3S(n) + 1 \\
+ S(n+2) \geq 9S(n) + 4 \\
+ S(n+3) \geq 33S(n) + 6 \\
+ S(n+4) \geq 111S(n) + 43 \\
+ S(n+5) \geq 380S(n) + 148 \\
+ S(n+6) \geq 1140S(n) + 528 \]
 
@@
 \end{center}
-
 Except for 8, 9 and 13, the best lower bounds are obtained thanks to the third inequality \( 380S(n-5) + 148 \leqslant S(n) \).

### 2021-04-07 article/weakschur.tex
Update weakschur.tex
ajout WE+

@@
 Finally, we have showed that every classe of equivalence induced by $h$ is weakly sum-free, which ends the proof.
+
+\begin{remark}
+This formula includes the results of Rowley \hyperlink{label2}{\textbf{[2]}} as a special case.
+For \(n>2\), this formula does not give new lower bounds but in the same way as we introduced \(SE_+\)\hyperref[SE]{(Definition 3.1)}, we will define \(WE_+\) and find inequalities between \(WE_+\),\(WS\) and \(S\)
+\end{remark}
+
+\subsection{Definition of \(WE_+\)}
+
+\begin{definition}
+Let \( n \in \mathbb{N}^*\), let\( b \in \mathbb{N}^*\) there exists a greatest integer that we note \(WE_b^+(n)\) such that \( [\![1, b+WE_b^+(n)]\!]\) can be partitionned into \(n\) weakly-sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
+\\\\
+\underline{\(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
+\\\\
+\underline{For \(A_n\) (the special subset):} \quad \(\forall (x,y) \in A_n^2,\)
+\\
+\[if \quad x+y>b+2WE_b^+(n),\quad x+y-2WE_b^+(n)\notin A_n\]
+\\
+\underline{For the others subsets:}\quad \(\forall (x,y) \in A_k^2\)
+\\
+\[
+(Id+WE_b^+(n)\mathbf{1}_{ [\![0,b]\!]})(x+y[WE_b^+(n)]) \notin A_k
+\]
+
+\end{definition}
+
+\begin{Theorem}
+Let \( n \in \mathbb{N}^*\), let\( (a,b) \in (\mathbb{N}^*)^2\) such as \(a>b\). If there exist a partition of  
+\end{Theorem}

### 2021-04-07 article/weakschur.tex
Ajout tableau de valeurs WS

@@
 \end{Theorem}
+
+\subsection{New lower bounds for Weak Schur numbers}
+Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \).
+The first two inequalities are due to Rowley, they are detailed in [2].
+The best lower bound for each integer is highlighted.\\
+\\
+\begin{center}
+\begin{tabular}{|*{5}{c|}}
+    \hline
+	 & 8 & 9 & 10 & 11 \\
+	\hline
+	\(4S(n-1) + 2 \) & 6722 & 21146 & \cellcolor{yellow} 71214 & \cellcolor{yellow} 243794\\
+	\hline
+	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6976 & 21848 & 68726 & 231447\\
+	\hline
+	\(42S(n-3) + 24 \) & 6744 & \cellcolor{yellow} 22536 & 70584 & 222036 \\
+	\hline
+	\(127S(n-4) + 68 \) & 5656 & 20388 & 68140 & 213428\\
+	\hline
+	\hline
+	& 12 & 13 & 14 & 15 \\
+	\hline
+	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815314 & 2554194 & 8045162 & \cellcolor{yellow} 27061154\\
+	\hline
+	\(13S(n-2) + 8 \) & 792332 & \cellcolor{yellow}2649772 & 8301132 & 26146778 \\
+	\hline
+	\(42S(n-3) + 24 \) & 747750 & 2559840 & \cellcolor{yellow} 8560800 &  25886224 \\
+	\hline
+	\(127S(n-4) + 68 \) & 671390 & 2261049 & 7740464 & 25886224 \\
+	\hline
+\end{tabular}
+\end{center}
+With \( S(9) \geqslant 17803 \), we found a new lower bound for
+\(WS(10)\) using Rowley's inequality. Moreover, the third inequality
+gives new lower bounds for \(WS(9)\) and \(WS(14)\). However, the last
+inequality doesn't give any better lower bound, even beyond \( n = 15 \)
+: the best bounds are always provided by the first three.

### 2021-04-07 article/schur.tex
inequality on SE

@@
 \begin{theorem}
+	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
+	and a partition of $n$ sum-free subsets of $[\![1,s]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,rs]\!]$
+\end{theorem}
+
+Setting $r = SE_+(k+1)$ and $s = S(n)$ yields the following corollary.
+
+\begin{corollary}
 	Let \(n, k \in \mathbb{N}^*\), we have \\
 	\[ S(n+k) \geqslant SE_+(k+1)S(n) \]
+\end{corollary}
+
+Using a SAT solvers, we are able to exhibit SF-template,
+hence providing lower bound on \(SE_+\). Moreover, when using 
+a SF-template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
+inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
+Here are the best inequalities on Schur numbers so far :
+\[ S(n+1) \geqslant 3S(n) + 1 \]
+\[ S(n+2) \geqslant 9S(n) + 4 \]
+\[ S(n+3) \geqslant 33S(n) + 6 \]
+\[ S(n+4) \geqslant 111S(n) + 43 \]
+\[ S(n+5) \geqslant 380S(n) + 148 \]
+\[ S(n+6) \geqslant 1140S(n) + 528 \]
+
+The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second and third ones were found by Rowley (reference nécessaire), 
+and the other ones are new. \\
+
+We also have a similar theorem where only \(SE_+\) is involved.
+
+\begin{theorem}
+	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
+	and \(SF\)-template of \(n\) color and lenght \(s\), then there exists \(SF\)-template of \((n+k)\) and lenght \(rs\).
 \end{theorem}
 
-Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
-hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
-a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
-inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
-Here are the best inequalities on Schur numbers so far :
-\[ S(n+1) \geq 3S(n) + 1 \\
- S(n+2) \geq 9S(n) + 4 \\
- S(n+3) \geq 33S(n) + 6 \\
- S(n+4) \geq 111S(n) + 43 \\
- S(n+5) \geq 380S(n) + 148 \\
- S(n+6) \geq 1140S(n) + 528 \]
+And the associated inequality :
+
+\begin{corollary}
+	Let \(n, k \in \mathbb{N}^*\), we have \\
+	\[ SE_+(n+k) \geqslant SE_+(k+1)SE_+(n) \]
+\end{corollary}
 

### 2021-04-07 article/schur.tex

@@
 
-The previous inequalities gives new lower bounds for \(S(n)\) for
+The previous inequalities give new lower bounds for \(S(n)\) for
 \( n \in [\![9,+\infty]\!] \backslash \{13\} \). We compute the lower
-bounds values for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the values for \( n = 8\) and \(n = 13\) were already obtained thanks to the first one, found by Rowley.
+bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n = 8\) and \(n = 13\) were already obtained thanks to the first one, found by Rowley.
 The best lower bounds are highlighted.\\

### 2021-04-07 article/sat.tex
fin sat

@@
 
+\begin{remark}
+Using a parallel SAT solver usually reduces the computation time, especially when trying to show that a formula is unsatisfiable. However, most of the 
+parallel SAT solver do not have a deterministic behaviour and it can results in a strong variation of running times.
+\end{remark}
+
 \subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
@@
 Rowley's new lower bound for \(WS(6)\) (642)  \hyperlink{label2}{\textbf{[2]}} was a quite significant improvement upon the former
-best known lower bound (582). This previous lower bound was found using a computer (often with Monte-Carlo) methods and by making the
+best known lower bound (582) \hyperlink{label7}{\textbf{[7]}}. This previous lower bound was found using a computer (often with Monte-Carlo methods) and by making the
 assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small values of \(n\).
-Therefore, one may wonder whether the limiting factor is the assumption or the methods used to search for partitions. It appears that
-the latter is correct.
+Therefore, one may wonder whether the limiting factor are the assumptions or the methods used to search for partitions. It appears that the search space
+induced by these assumptions does not contain the optimal partitions.
 
@@
 computation time. In order to help the SAT solver, we add additional information in the propositional formula. We did not quantify the
-speedup, but it most likely allows us to gain several order of magnitude in computation time as we explain in the next subsection.
+speedup, but it most likely allowed us to gain several order of magnitude in computation time as we explain in the next subsection.
 
@@
 \begin{notation}
-Let \(P\) be a predicate. We denote
+Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(WS(n | P)\) the greatest number \(N\) such that there exists a partition of  
+\([\![1,N]\!]\) in n weakly sum-free subsets which verifies P.
 \end{notation}
@@
 \(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only assuming \(m_5 = 67\) even after several
-weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5 seconds with the SAT solver glucose
-on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here but in the rest of this subsection, we used the parallel version of glucose).
+weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5 seconds with the SAT solver glucose  \hyperlink{label6}{\textbf{[6]}}
+on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here for the sake of comparison but in the rest of this subsection, we used the parallel version of glucose).
 The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free subsets starts with a partition of
@@
 \begin{computational theorem}
-If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\).
+If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). \\
+NB : on doit finir d'obtenir les valeurs.
 \end{computational theorem}
@@
 \end{tabular}
+
+To obtain these results, we once again provided additionnal information to the SAT solver. We also gave other types of information to the SAT solver.
+(pas encore fini)

### 2021-04-07 article/schur.tex

--- 2021-04-07 article/schur.tex
@@
 inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
-Here are the best inequalities on Schur numbers so far :
-\[ S(n+1) \geq 3S(n) + 1 \\
- S(n+2) \geq 9S(n) + 4 \\
- S(n+3) \geq 33S(n) + 6 \\
- S(n+4) \geq 111S(n) + 43 \\
- S(n+5) \geq 380S(n) + 148 \\
- S(n+6) \geq 1140S(n) + 528 \]
 

### 2021-04-07 article/schur.tex
definition template

--- 2021-04-07 article/schur.tex
@@
 \begin{definition}
-	Let \( n \in \mathbb{N}^*\), there exists a greatest integer that we note \(SE_+(n)\) (resp. \(SE_-(n)\)) such that \( [\![1, SE_+(n)]\!]\) 
-	(resp. \( [\![1, SE_-(n)]\!]\)) can be partitionned (resp. can not be partionned) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
+	We call SF-template of \(k\) colors and lenght \(n\) a partition of \( [\![1,n]\!]\) into \(k\) sum-free subsets \(A_1, A_2, ..., A_k\) which verify :
 	\[
-	\forall k \in [\![1, n-1]\!], \forall (x,y) \in A_k^2, x+y > SE_+(n)
-	\Longrightarrow x+y-SE_+(n) \notin A_k
+	\forall i \in [\![1, k-1]\!], \forall (x,y) \in A_i^2, x+y > n
+	\Longrightarrow x+y-n \notin A_i
 	\]
+	We note \(SE_+(k)\) the maximal lenght for a SF-template of \(k\) colors. 
 \end{definition}
-We notice that in general, unlike regular Schur numbers, we don't have \(SE_+(n) + 1 \neq SE_-(n)\)
 
@@
 The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second and third ones were found by Rowley (reference nécessaire), 
-and the other ones are new. \\
+while the other ones are new. \\
 

### 2021-04-07 article/weakschur.tex

@@
 \subsection{New lower bounds for Weak Schur numbers}
+Having found suitable templates, which can be found in the appendix,  with a SAT solver, we can claim that for all \(n \in \mathbb{N}^*\):
+\[
+4S(n) + 1 \leqslant WS(n+1)
+\]
+\[
+13S(n) + 8 \leqslant WS(n+2)
+\]
+\[
+42S(n) + 24 \leqslant WS(n+3)
+\]
+\[
+127S(n) + 68 \leqslant WS(n+4)
+\]
+The first two inequalities are due to Rowley, they are detailed in [2].
 Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \).
-The first two inequalities are due to Rowley, they are detailed in [2].
 The best lower bound for each integer is highlighted.\\
@@
 inequality doesn't give any better lower bound, even beyond \( n = 15 \)
-: the best bounds are always provided by the first three.
+: the best bounds are always provided by the first three. We highly suspect that these values can be improved by investigating the search
+space further, which would provide new, more effective templates. One
+may try to go over this search space using a Monte-Carlo method, as in
+(ref Eliahou) or (ref Bouzy). This could be the suject of a future work.

### 2021-04-07 article/weakschur.tex
theoreme schur et modification WS+

@@
 \subsection{Definition of \(WE_+\)}
+\begin{definition}
+Let \( (n,k,b) \in (\mathbb{N}^*)^3\), Let \((A_1,....,A_k)\) a partition of  \([\![1, n]\!]\). This partition is said to be a (n,k,b)-weakly-sum-free template when:
+\\\\
+\underline{\(\forall i \in [\![1, k]\!], \quad A_i\) is weakly-sum-free}
+\\\\
+\underline{\(\forall i \in [\![1, k]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
+\\\\
+\underline{For \(A_k\) (the special subset):} \quad \(\forall (x,y) \in A_k^2,\)
+\\
+\[if \quad x+y>b+2(n-b),\quad x+y-2(n-b)\notin A_k\]
+\\
+\underline{For the others subsets:}\quad \(\forall i \in [\![0,k-1]\!], \forall(x,y) \in A_i^2\)
+\\
+\[
+(Id+(n-b)\mathbf{1}_{ [\![0,b]\!]})(x+y[n-b]) \notin A_i
+\]
+\end{definition}
+\\\\
+\begin{definition}
+Let \( (k,b) \in (\mathbb{N}^*)^2\), if there exist n such as there exist a partition of k subsets of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template, we note: 
+\\\\\(WS_b^+=\max \{n\in \mathbb{N}^*\)/ there exists a partition of k-subsets of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template \}
+\\\\
+If this n does not exist, we set \(WS_b^+= 0\)
+\end{definition}
 
 \begin{definition}
-Let \( n \in \mathbb{N}^*\), let\( b \in \mathbb{N}^*\) there exists a greatest integer that we note \(WE_b^+(n)\) such that \( [\![1, b+WE_b^+(n)]\!]\) can be partitionned into \(n\) weakly-sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
-\\\\
-\underline{\(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
-\\\\
-\underline{For \(A_n\) (the special subset):} \quad \(\forall (x,y) \in A_n^2,\)
-\\
-\[if \quad x+y>b+2WE_b^+(n),\quad x+y-2WE_b^+(n)\notin A_n\]
-\\
-\underline{For the others subsets:}\quad \(\forall (x,y) \in A_k^2\)
-\\
-\[
-(Id+WE_b^+(n)\mathbf{1}_{ [\![0,b]\!]})(x+y[WE_b^+(n)]) \notin A_k
-\]
-
+Let \( n \in \mathbb{N}^*\), we define \(WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{WS_b^+(n)\}\) 
 \end{definition}
 
-\begin{Theorem}
-Let \( n \in \mathbb{N}^*\), let\( (a,b) \in (\mathbb{N}^*)^2\) such as \(a>b\). If there exist a partition of  
-\end{Theorem}
+\subsection{Lower bound for Weak schur numbers using Schur and Weak Schur template numbers}
+
+\begin{theorem}
+Let \((n,k,b) \in (\mathbb{N}*)^3\), let \( (m,p) \in (\mathbb{N}^*)^2\).
+If there exists a partition of p sum-free subsets of \([\![1,m]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template, then there exists a partition of (k+p-1) weakly sum-free subsets of \([\![1, b+c+m \times n]\!]\) with c=\(min A_n\bigcap [\![b+1, n]\!]\)-b-1
+\end{theorem}
 

### 2021-04-07 article/schur.tex
taux de croissance
version finale 07/04

@@
 \qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's numbers, Rowley 
-introduces partitions verifying some properties which can be extended using method which generalizes Abbott-Hanson's [8] construction. 
-Rolwey named these partitions "templates", and we will keep this name in the entire article. Finding suitable templates and applying his 
-method to these will allow us to find new lower bounds for Schur methods.
+introduces partitions verifying some properties which can be extended using a method which generalizes Abbott-Hanson's [8] construction. 
+Rolwey named these partitions "templates", and we will keep this name in the entire article. We find suitable templates and use them
+ to find new lower bounds for Schur numbers.
 
@@
 
-\subsection{Inequaties on \(SE_+\)}
+\subsection{Inequalities on \(SE_+\)}
 
@@
 	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
-	and a partition of $n$ sum-free subsets of $[\![1,s]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,rs]\!]$
+	and a partition of $n$ sum-free subsets of $[\![1,s]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,rs]\!]$.
 \end{theorem}
@@
 \end{center}
-Except for 8, 9 and 13, the best lower bounds are obtained thanks to the third inequality \( 380S(n-5) + 148 \leqslant S(n) \).
-The table doesn't go any further, but the same inequality allows to improve the lower bounds for every \( n \in [\![15,+\infty]\!] \).
+Except for 8, 9 and 13, the best lower bounds are obtained thanks to
+the third inequality \( 380S(n-5) + 148 \leqslant S(n) \). The table
+doesn't go any further, but the same inequality allows to improve the
+lower bounds for every \( n \in [\![15,+\infty]\!] \).
+
+\begin{corollary}
+The growth rate for Schur (and Ramsey) numbers satisfies \(\gamma = \sqrt[5]{380} \geqslant 3.28 \).
+\end{corollary}
+\textsc{Proof :} It is a mere consequence of the inequality \(380S(n-5) + 148 \leqslant S(n) \). As for Ramsey's 
+numbers growth rate, a lower bound can be found using Schur's one, thanks to \(S(n) \leqslant R_n(3)-2 \) 
+(see \hyperlink{label1}{\textbf{[1]}}).

### 2021-04-08 article/intro.tex
notations :'(

@@
 Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free
-subsets. Given \(m\) and \(n\) two integers, we are interested in partitioning the set of integers from 1 to \(m\) into
+subsets. Given \(p\) and \(n\) two integers, we are interested in partitioning the set of integers from 1 to \(p\) into
 \(n\) weakly sum-free subsets.
@@
 \begin{notation}
-We denote by \([\![1,n]\!]\) the set of integers \(\{1, 2, ..., n\}\).
+We denote by \([\![1,p]\!]\) the set of integers \(\{1, 2, ..., p\}\).
 \end{notation}
 
-Schur proved in \hyperlink{label1}{\textbf{[1]}} that given a number of subsets \(n\), there exists a value of \(m\)
-such that there exists no partition of \([\![1,p]\!]\) into \(n\) sum-free subsets for any \(p \geqslant m\). A similar
+Schur proved in \hyperlink{label1}{\textbf{[1]}} that given a number of subsets \(n\), there exists a value of \(p\)
+such that there exists no partition of \([\![1,q]\!]\) into \(n\) sum-free subsets for any \(q \geqslant p\). A similar
 property holds for weakly sum-free subsets (reference necessaire). These observations lead to the following definitions.
@@
 \begin{notation}
-For a partition of \([\![1, n]\!]\) in \(k\) subsets, we generally note these subsets \(A_1, ..., A_k\). We also note \(m_i = \text{min}(A_i)\). 
-By ordering the subsets, we mean assuming that \(m_1 < ... < m_k\). However, if not specified we do not make this hypothesis since we 
+For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally note these subsets \(A_1, ..., A_n\). We also note \(m_i = \text{min}(A_i)\). 
+By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do not make this hypothesis since we 
 do not always consider partitions in which every subset plays a symmetric role.

### 2021-04-08 article/sat.tex
notations :'(

@@
 
-We then encode the existence of a partition of \([\![1,n]\!]\) in \(k\)  weakly sum-free subsets as follows: for every integer
-\(i \in [\![1,n]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!], x^{(i)}_c = 1 \iff i \in A_c\).
+We then encode the existence of a partition of \([\![1,p]\!]\) in \(k\)  weakly sum-free subsets as follows: for every integer
+\(i \in [\![1,p]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!], x^{(i)}_c = 1 \iff i \in A_c\).
 The corresponding clauses are:
@@
 \begin{itemize}
-\item \textbf{sumfree:} \(\forall c \in  [\![1,k]\!], \forall (i, j) \in [\![1,n]\!]^2, (i \neq j ~ \text{and} ~ i + j \leq n) \implies \lnot x^{(i)}_c
+\item \textbf{sumfree:} \(\forall c \in  [\![1,k]\!], \forall (i, j) \in [\![1,p]\!]^2, (i \neq j ~ \text{and} ~ i + j \leq n) \implies \lnot x^{(i)}_c
 \lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
-\item \textbf{union:} \(\forall i \in [\![1,n]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
-\item \textbf{disjoint:} \(\forall i \in [\![1,n]\!],\forall (c_1, c_2) \in  [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
+\item \textbf{union:} \(\forall i \in [\![1,p]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
+\item \textbf{disjoint:} \(\forall i \in [\![1,p]\!],\forall (c_1, c_2) \in  [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
 \end{itemize}
@@
 \begin{itemize}
-	\item \(m_5 \ge 66\)
-	\item \(m_6 \ge 186\)
+	\item \(m_5 \geqslant 66\)
+	\item \(m_6 \geqslant 186\)
 	\item \([\![210,349]\!] \subset A_6\)
@@
 The above theorem shows that the previous lower bound for \(WS(6)\) is optimal in the search space considered by the papers which found it.
-Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geq 590\) which does not have a template-like structure
+Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geqslant 590\) which does not have a template-like structure
 would be extremely interesting since it could give indications on a new search space for improving lower bounds with a computer. More generally,
 it questions the search space previously used for finding lower bounds for \(WS(n)\) with a computer. In particular, to our knowledge every paper
-that found the lower bound \(WS(5) \geq 196\) used this assumption [reference necessaire]. Therefore one may wonder if this actually a good lower
+that found the lower bound \(WS(5) \geqslant 196\) used this assumption [reference necessaire]. Therefore one may wonder if this actually a good lower
 bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has to verify.
@@
 \subsection{Weak Schur number five}
-As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection,
+As explained in the previous subsection, the search space used for showing that  \(WS(5) \geqslant 196\) may not contain optimal solution. In this subsection,
 we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same type of methods as in the 
@@
 \begin{notation}
-Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(WS(n | P)\) the greatest number \(N\) such that there exists a partition of  
-\([\![1,N]\!]\) in n weakly sum-free subsets which verifies P.
+Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(WS(n | P)\) the greatest number \(p\) such that there exists a partition of  
+\([\![1,p]\!]\) in n weakly sum-free subsets which verifies P.
 \end{notation}

### 2021-04-08 article/schur.tex
notations :'(

@@
 introduces partitions verifying some properties which can be extended using a method which generalizes Abbott-Hanson's [8] construction. 
-Rolwey named these partitions "templates", and we will keep this name in the entire article. We find suitable templates and use them
+Rowley named these partitions "templates", and we will keep this name in the entire article. We find suitable templates and use them
  to find new lower bounds for Schur numbers.
 
-\subsection{Definition of SE\(_+\)}
+\subsection{Definition of S\(_+\)}
 
 \begin{definition}
-	We call SF-template of \(k\) colors and lenght \(n\) a partition of \( [\![1,n]\!]\) into \(k\) sum-free subsets \(A_1, A_2, ..., A_k\) which verify :
+	We call SF-template of \(n\) colors and lenght \(p\) a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
 	\[
-	\forall i \in [\![1, k-1]\!], \forall (x,y) \in A_i^2, x+y > n
-	\Longrightarrow x+y-n \notin A_i
+	\forall i \in [\![1, n-1]\!], \forall (x,y) \in A_i^2, x+y > p
+	\Longrightarrow x+y-p \notin A_i
 	\]
-	We note \(SE_+(k)\) the maximal lenght for a SF-template of \(k\) colors. 
+	We note \(S_+(n)\) the maximal lenght for a SF-template of \(n\) colors. 
 \end{definition}
@@
 	\[
-	2S(n-1)+1 \leqslant SE_+(n) \leqslant S(n)
+	2S(n-1)+1 \leqslant S_+(n) \leqslant S(n)
 	\]
@@
 \begin{remark}
-	\(SE_+\) and \(S\) have the same asymptotic growth rate.
+	\(S_+\) and \(S\) have the same asymptotic growth rate.
 \end{remark}
 
-\subsection{Inequalities on \(SE_+\)}
+\subsection{Inequalities on \(S_+\)}
 
-The main result on \(SE_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(SE_+\).
+The main result on \(S_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(S_+\).
 
 \begin{theorem}
-	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
-	and a partition of $n$ sum-free subsets of $[\![1,s]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,rs]\!]$.
+	Let $(n,k), (p,q) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(p\),
+	and a partition of $n$ sum-free subsets of $[\![1,q]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,pq]\!]$.
 \end{theorem}
 
-Setting $r = SE_+(k+1)$ and $s = S(n)$ yields the following corollary.
+Setting $p = S_+(k+1)$ and $q = S(n)$ yields the following corollary.
 
@@
 	Let \(n, k \in \mathbb{N}^*\), we have \\
-	\[ S(n+k) \geqslant SE_+(k+1)S(n) \]
+	\[ S(n+k) \geqslant S_+(k+1)S(n) \]
 \end{corollary}
@@
 Using a SAT solvers, we are able to exhibit SF-template,
-hence providing lower bound on \(SE_+\). Moreover, when using 
+hence providing lower bound on \(S_+\). Moreover, when using 
 a SF-template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
-inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
+inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(S_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
 Here are the best inequalities on Schur numbers so far :
@@
 
-The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second and third ones were found by Rowley (reference nécessaire), 
-while the other ones are new. \\
+The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second one are due to Abott (référence nécessaire) 
+and the third one to Rowley (reference nécessaire). The other ones are new. \\
 
-We also have a similar theorem where only \(SE_+\) is involved.
+We also have a similar theorem where only \(S_+\) is involved.
 
 \begin{theorem}
-	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
-	and \(SF\)-template of \(n\) color and lenght \(s\), then there exists \(SF\)-template of \((n+k)\) and lenght \(rs\).
+	Let $(n,k), (p,q) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(p\),
+	and \(SF\)-template of \(n\) color and lenght \(q\), then there exists \(SF\)-template of \((n+k)\) and lenght \(pq\).
 \end{theorem}
@@
 	Let \(n, k \in \mathbb{N}^*\), we have \\
-	\[ SE_+(n+k) \geqslant SE_+(k+1)SE_+(n) \]
+	\[ S_+(n+k) \geqslant S_+(k+1)S_+(n) \]
 \end{corollary}
@@
 The previous inequalities give new lower bounds for \(S(n)\) for
-\( n \in [\![9,+\infty]\!] \backslash \{13\} \). We compute the lower
+\( n \geqslant 9 \). We compute the lower
 bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n = 8\) and \(n = 13\) were already obtained thanks to the first one, found by Rowley.
@@
     \hline
-	 & 8 & 9 & 10 & 11 \\
+	\(n\) & 8 & 9 & 10 & 11 \\
 	\hline
@@
 	\hline
-	& 12 & 13 & 14 & 15 \\
+	\(n\) & 12 & 13 & 14 & 15 \\
 	\hline
@@
 Except for 8, 9 and 13, the best lower bounds are obtained thanks to
-the third inequality \( 380S(n-5) + 148 \leqslant S(n) \). The table
+the third inequality \( S(n+5) \geqslant 380S(n) + 148\). The table
 doesn't go any further, but the same inequality allows to improve the
-lower bounds for every \( n \in [\![15,+\infty]\!] \).
+lower bounds for every \( n \geqslant 15 \).
 
 \begin{corollary}
-The growth rate for Schur (and Ramsey) numbers satisfies \(\gamma = \sqrt[5]{380} \geqslant 3.28 \).
+The growth rate for Schur (and Ramsey) numbers satisfies \(\gamma \geqslant \sqrt[5]{380} \approx 3.28 \).
 \end{corollary}
-\textsc{Proof :} It is a mere consequence of the inequality \(380S(n-5) + 148 \leqslant S(n) \). As for Ramsey's 
+\textsc{Proof :} It is a mere consequence of the inequality \( S(n+5) \geqslant 380S(n) + 148\). As for Ramsey's 
 numbers growth rate, a lower bound can be found using Schur's one, thanks to \(S(n) \leqslant R_n(3)-2 \) 

### 2021-04-08 article/weakschur.tex
version finale 07/04
notations :'(

@@
 
-In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the integer \(WE_+(n)\) 
+In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the integer \(WS_+(n)\) 
 to build suitable templates.
@@
 \begin{theorem}
-	Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$. If there exists a partition of $r$ weakly sum-free subsets of $[\![1,n]\!]$ and a partition of $s$ sum-free 
-	subsets of $[\![1,p]\!]$ then there exists a partition of $r+s$ weakly sum-free subsets of $[\![1,p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n]\!]$
+	Let $(p,q), (n,k) \in (\mathbb{N}^*)^2$. If there exists a partition of $[\![1,q]\!]$ into $n$ weakly sum-free subsets and a partition of $[\![1,p]\!]$ into $k$ sum-free 
+	subsets then there exists a partition of $[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]$ into $n+k$ weakly sum-free subsets.
 \end{theorem}
-In particular, if we choose $n = WS(r)$ and $p = WS(s)$ in the last theorem, the next corollary follows.
+In particular, if we choose $q = WS(n)$ and $p = S(k)$ in the last theorem, the next corollary follows.
 \begin{corollary}
-	$ \forall (n,m) \in (\mathbb{N}^*)^2 \text{, } WS(n+m) \geqslant S(m) \left (WS(n) + \left \lceil \frac{WS(n)}{2} \right \rceil +1 \right) + WS(n)$
+	$ \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } WS(n+k) \geqslant S(k) \left (WS(n) + \left \lceil \frac{WS(n)}{2} \right \rceil +1 \right) + WS(n)$
 \end{corollary}
-\textsc{Proof :} Let $(n,p), (r,s) \in (\mathbb{N}^*)^2$,  $N = p(n+\left \lceil \frac{n}{2} \right \rceil + 1)+n$, $\alpha = \left \lceil \frac{n}{2} \right \rceil > 0$ and $\beta = n + \alpha + 1$.
-We denote by $f$ the projection of the equivalence relation induced by the partition of $[\![1,n]\!]$ and $g$ the one induced by the partition of $[\![1,p]\!]$.
+\textsc{Proof :} Let $(p,q), (n,k) \in (\mathbb{N}^*)^2$,  $N = p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q$, $\alpha = \left \lceil \frac{q}{2} \right \rceil > 0$ and $\beta = q + \alpha + 1$. 
+We denote by $f$ the projection of the equivalence relation induced by the partition of $[\![1,q]\!]$ and $g$ the one induced by the partition of $[\![1,p]\!]$.
 Each equivalence class is represented by a single integer, therefore :
-\[ f : [\![1,n]\!] \longrightarrow [\![1,r]\!] \text{ and } \forall (x,y) \in [\![1,n]\!]^2, \left\{
+\[ f : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2, \left\{
 \begin{array}{ll}
@@
 \]
-\[g : [\![1,p]\!] \longrightarrow [\![1,s]\!] \text{ and } \forall (x,y) \in [\![1,n]\!]^2 \text{, } f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
+\[g : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
 \]
-Let us start by parting the integers of $[\![1,N]\!]$ in two subsets $\mathcal{A}$ and $\mathcal{B}$ where $\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]\}$ and $\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}$.\\
+Let us start by parting the integers of $[\![1,N]\!]$ in two subsets $\mathcal{A}$ and $\mathcal{B}$ where $\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\}$ and $\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}$.\\
 \\
 First, \underline{$\mathcal{A} \cap \mathcal{B} = \varnothing$} : \\
-Suppose there exists $x \in \mathcal{A} \cap \mathcal{B} = \varnothing$.
-Then there are $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]$ and $(b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ such that $x = a\beta + u = b\beta +v$.
-By definition of $\alpha$ and  $\beta$ we have $u \in [\![\alpha + 1,n]\!] \subset [\![0,\beta - 1]\!]$.
+By contradiction, suppose there exists $x \in \mathcal{A} \cap \mathcal{B} \neq \varnothing $.
+Then there are $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]$ and $(b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ such that $x = a\beta + u = b\beta +v$.
+By definition of $\alpha$ and  $\beta$ we have $u \in [\![\alpha + 1,q]\!] \subset [\![0,\beta - 1]\!]$.
 From there, we distinguish two cases :
@@
 	\item If $v \in [\![0,\alpha]\!]$ then $v \in [\![0,\beta - 1]\!]$ and $v \neq u$ because $v < \alpha + 1 \leqslant u$
-	\item If $v \in [\![-\alpha,-1]\!]$, we note $\tilde{v} = \beta + v$ and thus have $x = (b-1)\beta + \tilde{v}$ with $\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]$ and $\tilde{v} \neq u$ because $u < n+1 = \beta - \alpha \leqslant \tilde{v}$.
+	\item If $v \in [\![-\alpha,-1]\!]$, we note $\tilde{v} = \beta + v$ and thus have $x = (b-1)\beta + \tilde{v}$ with $\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]$ and $\tilde{v} \neq u$ because $u < q+1 = \beta - \alpha \leqslant \tilde{v}$.
 \end{itemize}
@@
 \begin{itemize}
-	\item On one hand : $1 = \text{min($\mathcal{A}$)} \leqslant \text{max($\mathcal{A}$)} = p\beta + n = N$ and $1 \leqslant \beta - \alpha = \text{min($\mathcal{B}$)} \leqslant \text{max($\mathcal{B}$)} = p\beta + \alpha \leqslant N$, which gives $\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]$.
-	\item On the other hand, let $x \in  [\![1,N]\!]$.
-If $x \leqslant \alpha$, we directly have $x \in \mathcal{A}$, let us then suppose that $x > \alpha$ and write $x = a\beta + u$ the euclidean division of $x$ by $\beta$.
-We have $x \leqslant N$, thus $a \leqslant p$.
-We distinguish three cases : \\
+	\item On the one hand : $1 = \text{min($\mathcal{A}$)} \leqslant \text{max($\mathcal{A}$)} = p\beta + q = N$ and 
+	$1 \leqslant \beta - \alpha = \text{min($\mathcal{B}$)} \leqslant \text{max($\mathcal{B}$)} = p\beta + \alpha \leqslant N$, 
+	which gives $\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]$.
+	\item On the other hand, let $x \in  [\![1,N]\!]$. If $x \leqslant \alpha$, we directly have $x \in \mathcal{A}$, let us then suppose that $x > \alpha$ and write $x = a\beta + u$ 
+	the euclidean division of $x$ by $\beta$. We have $x \leqslant N$, thus $a \leqslant p$. We distinguish three cases : \\
 	- If $u \in [\![0,\alpha]\!]$ then we necessarily have $a \geqslant 1$ because $x > \alpha$, and so $x \in \mathcal{B}$.\\
-	- If $u \in [\![\alpha + 1,n]\!]$, then $x \in \mathcal{A}$. \\
-	- If $u \in [\![n + 1,\beta - 1]\!]$ then $x = (a+1)\beta - (\beta - u)$ with $-\alpha \leqslant \beta - u \leqslant 0$.
+	- If $u \in [\![\alpha + 1,q]\!]$, then $x \in \mathcal{A}$. \\
+	- If $u \in [\![q + 1,\beta - 1]\!]$ then $x = (a+1)\beta - (\beta - u)$ with $-\alpha \leqslant \beta - u \leqslant 0$. 
 	Furthermore, $a \leqslant p - 1$, else we would have $x > N$, and so $x \in \mathcal{B}$ \\
@@
 This first partition of $[\![1,N]\!]$ will help us to define our final partition by the projection of its equivalence relation. 
-We thereby define $h : [\![1,N]\!] \longrightarrow [\![1,r+s]\!]$ as such :\\
+We thereby define $h : [\![1,N]\!] \longrightarrow [\![1,n+k]\!]$ as such :\\
 - If $x \in \mathcal{A}$ then $h(x) = f(x \text{ mod } \beta)$ (well defined because $x \text{ mod } \beta \in [\![1,N]\!]$)\\
-- If $x \in \mathcal{B}$ then $x = a\beta + u$ with a unique $(a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ and we define $h(x) = r + g(a)$\\
+- If $x \in \mathcal{B}$ then $x = a\beta + u$ with a unique $(a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ and we define $h(x) = n + g(a)$\\
 The fact that $(\mathcal{A}, \mathcal{B})$ is a partition of $[\![1,N]\!]$ ensures that this definition of $h$ is valid. We then have to verify that $h$ induces weakly sum-free subsets.\\
@@
 	\item If $(x,y) \in [\![1,\alpha]\!]^2$ :\\
-	We have $x + y \leqslant 2\alpha \leqslant n$ and $x + y = 0\beta + x + y$, therefore $x + y \in \mathcal{A}$.
+	We have $x + y \leqslant 2\alpha \leqslant q$ and $x + y = 0\beta + x + y$, therefore $x + y \in \mathcal{A}$. 
 	Then, by definition : $h(x) = f(x)$, $h(y) = f(y)$ and $h(x+y) = f(x+y)$, which gives us, thanks to the property verified by $f$, that $h(x+y) \neq h(x)$.
 	\item If $(x,y) \in [\![1,\alpha]\!] \times ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )$ :\\
-	We write $y = a\beta + u$ with $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,n]\!]$.
-Then $x+y = a\beta + x + u = (a+1)\beta + x + u - \beta$, and if $x + u > n$ it follows that $a \leqslant p-1$ since $x+y \leqslant N$, and $-\alpha \leqslant x + u - \beta \leqslant -1$.
-Therefore $x+y \in \mathcal{B}$ and $h(x+y) \neq h(x) = f(x)$ by definition of h.
-On the contrary, if $x - u \leqslant n$, then $x+y \in \mathcal{A}$ and $h(x+y) = f(x+u)$ because $x+u$ is actually the remainder of the euclidean division of $x+y$ by $\beta$.
-Moreover, $h(x) = f(x)$, $x < u$ and, with our initial hypothesis, $h(x) = h(y) = f(u)$.
-The property verified by $f$ gives us $f(x+u) \neq f(x)$ which can be rewritten as $h(x+y) \neq h(x)$.
+	We write $y = a\beta + u$ with $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]$. Then $x+y = a\beta + x + u = (a+1)\beta + x + u - \beta$, 
+	and if $x + u > q$ it follows that $a \leqslant p-1$ since $x+y \leqslant N$, and $-\alpha \leqslant x + u - \beta \leqslant -1$. 
+	Therefore $x+y \in \mathcal{B}$ and $h(x+y) \neq h(x) = f(x)$ by definition of h. On the contrary, if $x - u \leqslant n$, 
+	then $x+y \in \mathcal{A}$ and $h(x+y) = f(x+u)$ because $x+u$ is actually the remainder of the euclidean division of $x+y$ by $\beta$. 
+	Moreover, $h(x) = f(x)$, $x < u$ and, with our initial hypothesis, $h(x) = h(y) = f(u)$. The property verified by $f$ gives us $f(x+u) \neq f(x)$ which can be rewritten as $h(x+y) \neq h(x)$.
 	\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] ) \times [\![1,\alpha]\!]$ : \\
@@
 	\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )^2$ : \\
-	We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![0,p]\!] \times [\![\alpha + 1,n]\!]$.
-Then $x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta$ with $a+b \leqslant p-1$ (else we would have $x+y > N$ because $u+v > n$) and $-\alpha \leqslant u + v - \beta \leqslant \alpha$, therefore $x+y \in \mathcal{B}$ and by definition $h(x+y) \neq h(x)$.
+	We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![0,p]\!] \times [\![\alpha + 1,q]\!]$. Then $x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta$ 
+	with $a+b \leqslant p-1$ (else we would have $x+y > N$ because $u+v > q$) and $-\alpha \leqslant u + v - \beta \leqslant \alpha$, therefore $x+y \in \mathcal{B}$ and by definition $h(x+y) \neq h(x)$.
 \end{itemize}
@@
 We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![1,p]\!] \times [\![-\alpha,\alpha]\!]$. 
-We have $h(x) = r + g(a)$ and $h(y) = r + g(b)$, therefore $g(a) = g(b)$.
-We also have $x+y = (a+b)\beta + u +v$.\\
+We have $h(x) = q + g(a)$ and $h(y) = q + g(b)$, therefore $g(a) = g(b)$. We also have $x+y = (a+b)\beta + u +v$.\\
 If $u + v \in [\![-\alpha,\alpha]\!]$, then $x+y \in \mathcal{B}$ and $h(x+y) = g(a+b)$, hence we can deduce that $h(x+y) \neq h(x)$ because of the property verified by $g$.
@@
 This finally leads to the following inequality :
-\[\beta \leqslant |a+b-c|\beta = |w-u-v| \leqslant |w| + |u| + |v| \leqslant 3\alpha \leqslant n + \alpha < \beta
+\[\beta \leqslant |a+b-c|\beta = |w-u-v| \leqslant |w| + |u| + |v| \leqslant 3\alpha \leqslant q + \alpha < \beta
 \]
@@
 \begin{remark}
-This formula includes the results of Rowley \hyperlink{label2}{\textbf{[2]}} as a special case.
-For \(n>2\), this formula does not give new lower bounds but in the same way as we introduced \(SE_+\)\hyperref[SE]{(Definition 3.1)}, we will define \(WE_+\) and find inequalities between \(WE_+\),\(WS\) and \(S\)
+This formula includes the results of Rowley \hyperlink{label2}{\textbf{[2]}} as a special case. For \(n>2\), 
+this formula does not give new lower bounds but in the same way as we introduced \(S_+\)\hyperref[SE]{(Definition 3.1)}, 
+we will define \(WS_+\) and find inequalities between \(WS_+\),\(WS\) and \(S\)
 \end{remark}
 
-\subsection{Definition of \(WE_+\)}
+\subsection{Definition of \(WS_+\)}
 \begin{definition}
-Let \( (n,k,b) \in (\mathbb{N}^*)^3\), Let \((A_1,....,A_k)\) a partition of  \([\![1, n]\!]\). This partition is said to be a (n,k,b)-weakly-sum-free template when:
+Let \( (p,k,b) \in (\mathbb{N}^*)^3\), Let \((A_1,....,A_k)\) a partition of  \([\![1, p]\!]\). 
+This partition is said to be a b-weakly-sum-free template (b-WSF-template) of \(k\) colors and lenght \(p\) when:
 \\\\
@@
 \\
-\[if \quad x+y>b+2(n-b),\quad x+y-2(n-b)\notin A_k\]
+\[if \quad x+y>b+2(p-b),\quad x+y-2(p-b)\notin A_k\]
 \\
@@
 \[
-(Id+(n-b)\mathbf{1}_{ [\![0,b]\!]})(x+y[n-b]) \notin A_i
+(Id+(p-b)\mathbf{1}_{ [\![0,b]\!]})(x+y ~\text{mod}~ (p-b)) \notin A_i
 \]
@@
 \begin{definition}
-Let \( (k,b) \in (\mathbb{N}^*)^2\), if there exist n such as there exist a partition of k subsets of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template, we note: 
-\\\\\(WS_b^+=\max \{n\in \mathbb{N}^*\)/ there exists a partition of k-subsets of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template \}
+Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note: 
+\\\\\(WS_b^+=\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a \(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
 \\\\
-If this n does not exist, we set \(WS_b^+= 0\)
+If this \(p\) does not exist, we set \(WS_b^+= 0\)
 \end{definition}
@@
 \begin{theorem}
-Let \((n,k,b) \in (\mathbb{N}*)^3\), let \( (m,p) \in (\mathbb{N}^*)^2\).
-If there exists a partition of p sum-free subsets of \([\![1,m]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, n]\!]\) which is a (n,k,b)-weakly-sum-free template, then there exists a partition of (k+p-1) weakly sum-free subsets of \([\![1, b+c+m \times n]\!]\) with c=\(min A_n\bigcap [\![b+1, n]\!]\)-b-1
+Let \((p,k,b) \in (\mathbb{N}^*)^3\), let \( (q,n) \in (\mathbb{N}^*)^2\). If there exists a partition of \(n\)
+ sum-free subsets of \([\![1,q]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, p]\!]\) which is a \(b\)-WSF of \(k\) colors and lenght \(p\), 
+ then there exists a partition of \([\![1, b+c+q \times p]\!]\) into \((k+n-1)\) weakly sum-free subsets with c=\(min A_p\bigcap [\![b+1, p]\!] -b-1\).
 \end{theorem}
@@
     \hline
-	 & 8 & 9 & 10 & 11 \\
+	n & 8 & 9 & 10 & 11 \\
 	\hline
@@
 	\hline
-	& 12 & 13 & 14 & 15 \\
+	n & 12 & 13 & 14 & 15 \\
 	\hline

### 2021-04-08 article/schur.tex
¯\_(ツ)_/¯

@@
 
-\begin{theorem}
+\begin{remark}
+	SF-templates include Abott and Hanson's construction [reference necessaire] as a special case.
+\end{remark}
+
+\begin{proposition}
 	Let \(n \in [\![2, +\infty]\!]\), we have :
@@
 	\]
-\end{theorem}
+\end{proposition}
+
+\textsc{Proof :} The lower bound comes from Abott and Hanson's construction. The upper bound comes 
+from the fact that a SF-template of length \(p\) with \(n\) colors is also a partition of 
+\([\![1, p]\!]\) into \(n\) sum-free subsets.
 
@@
 
-\subsection{Inequalities on \(S_+\)}
+\subsection{Inequalities using \(S_+\)}
 
@@
 \( n \geqslant 9 \). We compute the lower
-bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n = 8\) and \(n = 13\) were already obtained thanks to the first one, found by Rowley.
+bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n = 8\) and \(n = 13\) were obtained thanks to the first one, found by Rowley.
 The best lower bounds are highlighted.\\

### 2021-04-08 article/weakschur.tex
¯\_(ツ)_/¯

@@
 
-The following theorem, inspired by Rowley's work, was found and proved by Romain Ageron.
+Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction [refenrece]. Here we 
+give a general lower bound for weak Schur numbers as a function of both regular and weak Schur numbers.
+The following theorem, inspired by Rowley's inequalities for \(WS(n+1)\) and \(WS(n+2)\), was found and proved 
+by Romain Ageron.
+
 \begin{theorem}
@@
 \end{definition}
-\\\\
+
 \begin{definition}
@@
 \subsection{New lower bounds for Weak Schur numbers}
-Having found suitable templates, which can be found in the appendix,  with a SAT solver, we can claim that for all \(n \in \mathbb{N}^*\):
+Having found suitable templates, which can be found in the appendix,  with a SAT solver, we claim that for all \(n \in \mathbb{N}^*\):
 \[
@@
 \end{center}
+
 With \( S(9) \geqslant 17803 \), we found a new lower bound for
@@
 space further, which would provide new, more effective templates. One
-may try to go over this search space using a Monte-Carlo method, as in
-(ref Eliahou) or (ref Bouzy). This could be the suject of a future work.
+may try to go over this search space using a Monte-Carlo method, as in (ref Bouzy), 
+but with a different search space (as we explain in \hyperref[SAT]{SAT section}). 
+This could be the suject of a future work.

### 2021-04-08 article/weakschur.tex
corollaire theoreme ws

@@
  sum-free subsets of \([\![1,q]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, p]\!]\) which is a \(b\)-WSF of \(k\) colors and lenght \(p\), 
- then there exists a partition of \([\![1, b+c+q \times p]\!]\) into \((k+n-1)\) weakly sum-free subsets with c=\(min A_p\bigcap [\![b+1, p]\!] -b-1\).
+ then there exists a partition of \([\![1, b+q \times p]\!]\) into \((k+n-1)\) weakly sum-free subsets.
 \end{theorem}
+
+In particular, if we choose \(q = S(n)\) and \(p = WS^+(k)\) in the last theorem, the next corollary follows.
+
+\begin{corollary}
+	\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let \text{ } b_{max}=max \{b\in \mathbb{N}^*/WS^+(k+1)=WS_b^+(k+1)\},\)
+	\[ WS(n+k) \geqslant S(n) WS^+(k+1)+b_{max}\]
+\end{corollary}
+
+\begin{remark}
+There exists a \(c(b) \geqslant \text{min}(A_{k+1} \backslash [\![1,b]\) - b - 1\) such that \(c(b)\) numbers can be added at the end of the extended partition.Therefore, we can get a better lower bound by finding a couple \((b,c(b))\) which maximizes the sum  \(b+c(b)\) such that \(WS^+(k+1)=WS_b^+(k+1)\).
+Hence we have:
+	\[ WS(n+k) \geqslant S(n) WS^+(k+1)+b+c(b)\]
+
+\end{remark}
 

### 2021-04-08 article/article.tex
environnement remark
¯\_(ツ)_/¯
formatage code

--- 2021-04-07 article/article.tex
@@
 \newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{remark}{Remark}[section]
+\newtheorem{proposition}{Proposition}[section]
 
@@
 
-\hypertarget{label1}{\textbf{[1]}} Schur, I. 1917. Uber die Kongruenz \(x^m + y^m = z^m~(\text{mod}~p)\). Jahresbericht der 
+\hypertarget{label1}{\textbf{[1]}} Schur, I. 1917. Uber die Kongruenz \(x^m + y^m = z^m~(\text{mod}~p)\). Jahresbericht
+der
 Deutschen Mathematikervereinigung 25:114–117.: 114-116. \url{http://eudml.org/doc/145475}
@@
 
-\hypertarget{label3}{\textbf{[3]}} Heule, M.J.H. 2017. Schur Number Five. arXiv 1711.08076, \url{https://arxiv.org/pdf/1711.08076.pdf}
+\hypertarget{label3}{\textbf{[3]}} Heule, M.J.H. 2017. Schur Number Five. arXiv 1711.08076,
+\url{https://arxiv.org/pdf/1711.08076.pdf}
 
-\hypertarget{label4}{\textbf{[4]}} S. Eliahou, J.M. Marín, M.P. Revuelta and M.I. Sanz 2012. Weak Schur numbers and the search for G.W. 
-Walker’s lost partitions. Computers \& Mathematics with Applications Vol. 63, \url{https://www.sciencedirect.com/science/article/pii/S0898122111009722}
+\hypertarget{label4}{\textbf{[4]}} S. Eliahou, J.M. Marín, M.P. Revuelta and M.I. Sanz 2012. Weak Schur numbers and the
+search for G.W.
+Walker’s lost partitions. Computers \& Mathematics with Applications Vol. 63,
+\url{https://www.sciencedirect.com/science/article/pii/S0898122111009722}
 
-\hypertarget{label5}{\textbf{[5]}} Bierem, A. 2017. CaDiCaL, Lingeling, Plingeling, Treengeling, YalSAT Entering the SAT Competition 2017. 
-Proceedinfs of SAT Competition 2017 -- Solver and Benchmark Descriptions \url{http://fmv.jku.at/papers/Biere-SAT-Competition-2017-solvers.pdf}
+\hypertarget{label5}{\textbf{[5]}} Bierem, A. 2017. CaDiCaL, Lingeling, Plingeling, Treengeling, YalSAT Entering the SAT
+Competition 2017.
+Proceedinfs of SAT Competition 2017 -- Solver and Benchmark Descriptions
+\url{http://fmv.jku.at/papers/Biere-SAT-Competition-2017-solvers.pdf}
+
+\hypertarget{label6}{\textbf{[6]}} Gilles Audemard, Laurent Simon, 2015.
+\url{https://www.labri.fr/perso/lsimon/glucose/}
+
+\hypertarget{label7}{\textbf{[7]}} Eliahou S., Fonlupt C., Fromentin J., Marion-Poty V., Robilliard D., Teytaud F. 2013.
+Investigating Monte-Carlo Methods on the Weak Schur Problem.
+In Evolutionary Computation in Combinatorial Optimization, 2013.
+\url{https://link.springer.com/chapter/10.1007/978-3-642-37198-1_17}
 

### 2021-04-08 article/sat.tex
formatage code

@@
 results than those previously known for \(WS(5)\) while gaining several orders of magnitude in computation time by
-giving additional information to the SAT solver without losing in generality. In this section, we assume that the subsets are ordered.
+giving additional information to the SAT solver without losing in generality. In this section, we assume that the
+subsets are ordered.
 
@@
 
-We encode the existence of (weakly) sum-free partitions as propositional formulae like in \hyperlink{label3}{\textbf{[3]}} and then use
+We encode the existence of (weakly) sum-free partitions as propositional formulae like in
+\hyperlink{label3}{\textbf{[3]}} and then use
 SAT solvers to determine whether these formulae are satisfiable.
@@
 \begin{definition}
-A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a negative literal) where \(v\)
-takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a conjunction of clauses: it
+A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a
+negative literal) where \(v\)
+takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a
+conjunction of clauses: it
 is a propositional formula in \textit{conjonctive normal form} (CNF).
@@
 \begin{definition}
-An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A literal \(l\) is
+An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A
+literal \(l\) is
 \textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\)
-(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A clause is \textit{satisfied}
-by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is \textit{satisfied} by an assignment
-\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an assignment that satisfies it;
+(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A
+clause is \textit{satisfied}
+by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is
+\textit{satisfied} by an assignment
+\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an
+assignment that satisfies it;
 otherwise it is \textit{unsatisfiable}.
@@
 
-We then encode the existence of a partition of \([\![1,p]\!]\) in \(k\)  weakly sum-free subsets as follows: for every integer
-\(i \in [\![1,p]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!], x^{(i)}_c = 1 \iff i \in A_c\).
+We then encode the existence of a partition of \([\![1,p]\!]\) in \(k\) weakly sum-free subsets as follows: for every
+integer
+\(i \in [\![1,p]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!],
+x^{(i)}_c = 1 \iff i \in A_c\).
 The corresponding clauses are:
@@
 \begin{itemize}
-\item \textbf{sumfree:} \(\forall c \in  [\![1,k]\!], \forall (i, j) \in [\![1,p]\!]^2, (i \neq j ~ \text{and} ~ i + j \leq n) \implies \lnot x^{(i)}_c
+\item \textbf{sumfree:} \(\forall c \in [\![1,k]\!], \forall (i, j) \in [\![1,p]\!]^2, (i \neq j ~ \text{and} ~ i + j
+\leq n) \implies \lnot x^{(i)}_c
 \lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
 \item \textbf{union:} \(\forall i \in [\![1,p]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
-\item \textbf{disjoint:} \(\forall i \in [\![1,p]\!],\forall (c_1, c_2) \in  [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
+\item \textbf{disjoint:} \(\forall i \in [\![1,p]\!],\forall (c_1, c_2) \in [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg
+x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
 \end{itemize}
 
-In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the subsets, that is by
+In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the
+subsets, that is by
 enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
-\textbf{symmetry breaking:}  \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!], x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
+\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!],
+x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
 
 \begin{remark}
-For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary significantly according to the problem.
+For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary
+significantly according to the problem.
 For instance, we used two different SAT solvers in the next two next subsections.
@@
 \begin{remark}
-Using a parallel SAT solver usually reduces the computation time, especially when trying to show that a formula is unsatisfiable. However, most of the 
+Using a parallel SAT solver usually reduces the computation time, especially when trying to show that a formula is
+unsatisfiable. However, most of the
 parallel SAT solver do not have a deterministic behaviour and it can results in a strong variation of running times.
@@
 \subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
-
-Rowley's new lower bound for \(WS(6)\) (642)  \hyperlink{label2}{\textbf{[2]}} was a quite significant improvement upon the former
-best known lower bound (582) \hyperlink{label7}{\textbf{[7]}}. This previous lower bound was found using a computer (often with Monte-Carlo methods) and by making the
-assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small values of \(n\).
-Therefore, one may wonder whether the limiting factor are the assumptions or the methods used to search for partitions. It appears that the search space
+Rowley's new lower bound for \(WS(6)\) (642) \hyperlink{label2}{\textbf{[2]}} was a quite significant improvement upon
+the former
+best known lower bound (582) \hyperlink{label7}{\textbf{[7]}}. This previous lower bound was found using a computer
+(often with Monte-Carlo methods) and by making the
+assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small
+values of \(n\).
+Therefore, one may wonder whether the limiting factor are the assumptions or the methods used to search for partitions.
+It appears that the search space
 induced by these assumptions does not contain the optimal partitions.
@@
 
-This result was obtained in 8 hours with the SAT solver plingeling \hyperlink{label5}{\textbf{[5]}} on a 2.60 GHz Intel i7 processor PC.
-However, simply encoding the existence of such a partition as explained in the previous subsection would not result in a reasonable
-computation time. In order to help the SAT solver, we add additional information in the propositional formula. We did not quantify the
-speedup, but it most likely allowed us to gain several order of magnitude in computation time as we explain in the next subsection.
+This result was obtained in 8 hours with the SAT solver plingeling \hyperlink{label5}{\textbf{[5]}} on a 2.60 GHz Intel
+i7 processor PC.
+However, simply encoding the existence of such a partition as explained in the previous subsection would not result in a
+reasonable
+computation time. In order to help the SAT solver, we add additional information in the propositional formula. We did
+not quantify the
+speedup, but it most likely allowed us to gain several order of magnitude in computation time as we explain in the next
+subsection.
 
 \par
-Every weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets starts with the following sequence 1121222133. Then 11 is always
-either in subset 1 or 3, 12 is always in subset 3 and so on. For every integer in \([\![1,65]\!]\), we computed in which subset it can appear.
-By using this constraints, we could then compute for every integer in \([\![1,185]\!]\), in which subset it can appear in a weakly sum-free
-partition of  \([\![1,185]\!]\) which starts with a  weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets. Adding these constraints to the
+Every weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets starts with the following sequence 1121222133. Then 11
+is always
+either in subset 1 or 3, 12 is always in subset 3 and so on. For every integer in \([\![1,65]\!]\), we computed in which
+subset it can appear.
+By using this constraints, we could then compute for every integer in \([\![1,185]\!]\), in which subset it can appear
+in a weakly sum-free
+partition of \([\![1,185]\!]\) which starts with a weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets. Adding
+these constraints to the
 formula corresponding to the above theorem gives additional information to the SAT solver without losing in generality.
@@
 \par
-The above theorem shows that the previous lower bound for \(WS(6)\) is optimal in the search space considered by the papers which found it.
-Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geqslant 590\) which does not have a template-like structure
-would be extremely interesting since it could give indications on a new search space for improving lower bounds with a computer. More generally,
-it questions the search space previously used for finding lower bounds for \(WS(n)\) with a computer. In particular, to our knowledge every paper
-that found the lower bound \(WS(5) \geqslant 196\) used this assumption [reference necessaire]. Therefore one may wonder if this actually a good lower
-bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has to verify.
+The above theorem shows that the previous lower bound for \(WS(6)\) is optimal in the search space considered by the
+papers which found it.
+Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geqslant 590\) which does
+not have a template-like structure
+would be extremely interesting since it could give indications on a new search space for improving lower bounds with a
+computer. More generally,
+it questions the search space previously used for finding lower bounds for \(WS(n)\) with a computer. In particular, to
+our knowledge every paper
+that found the lower bound \(WS(5) \geqslant 196\) used this assumption [reference necessaire]. Therefore one may wonder
+if this actually a good lower
+bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has
+to verify.
 
 \subsection{Weak Schur number five}
-As explained in the previous subsection, the search space used for showing that  \(WS(5) \geqslant 196\) may not contain optimal solution. In this subsection,
-we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same type of methods as in the 
+As explained in the previous subsection, the search space used for showing that \(WS(5) \geqslant 196\) may not contain
+optimal solution. In this subsection,
+we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the
+same type of methods as in the
 previous subsection.
@@
 \begin{notation}
-Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(WS(n | P)\) the greatest number \(p\) such that there exists a partition of  
+Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(WS(n | P)\) the greatest number \(p\) such that
+there exists a partition of
 \([\![1,p]\!]\) in n weakly sum-free subsets which verifies P.
@@
 \par
-\hyperlink{label4}{\textbf{[4]}} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of \([\![1,197]\!]\) with
-\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only assuming \(m_5 = 67\) even after several
-weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5 seconds with the SAT solver glucose  \hyperlink{label6}{\textbf{[6]}}
-on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here for the sake of comparison but in the rest of this subsection, we used the parallel version of glucose).
-The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free subsets starts with a partition of
-\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among the 3 partitions of \([\![1,23]\!]\) in
-3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two different subsets. We hardcoded
-this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation time. We also give the stronger
+\hyperlink{label4}{\textbf{[4]}} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of
+\([\![1,197]\!]\) with
+\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only
+assuming \(m_5 = 67\) even after several
+weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5
+seconds with the SAT solver glucose \hyperlink{label6}{\textbf{[6]}}
+on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here for the sake of comparison but in the rest of
+this subsection, we used the parallel version of glucose).
+The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free
+subsets starts with a partition of
+\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among
+the 3 partitions of \([\![1,23]\!]\) in
+3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two
+different subsets. We hardcoded
+this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation
+time. We also give the stronger
 following result.
@@
 
-More precisely, we verified the following results (\(max~m_5\) is the greatest value of \(m_5\) for which we have not verified that \(WS(5 | m_5) \leq 196\)).
+More precisely, we verified the following results (\(max~m_5\) is the greatest value of \(m_5\) for which we have not
+verified that \(WS(5 | m_5) \leq 196\)).
 
@@
 	\hline
-	\(WS(4 | m_4) + 1\) &  55  &  59  &  60  &  59  &  59  &  60  &  60  &  60  &  60  &  64  &  63  &  64  &  61  &  64  &  63  &  65  &  65  &  65  &  65  &  66  &  67  \\
+\(WS(4 | m_4) + 1\) & 55 & 59 & 60 & 59 & 59 & 60 & 60 & 60 & 60 & 64 & 63 & 64 & 61 & 64 & 63 & 65 & 65 & 65 & 65 & 66
+& 67 \\
 	\hline
@@
 
-To obtain these results, we once again provided additionnal information to the SAT solver. We also gave other types of information to the SAT solver.
+To obtain these results, we once again provided additionnal information to the SAT solver. We also gave other types of
+information to the SAT solver.
 (pas encore fini)

### 2021-04-08 article/schur.tex
formatage code

@@
 
-\qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's numbers, Rowley 
-introduces partitions verifying some properties which can be extended using a method which generalizes Abbott-Hanson's [8] construction. 
-Rowley named these partitions "templates", and we will keep this name in the entire article. We find suitable templates and use them
+\qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's
+numbers, Rowley
+introduces partitions verifying some properties which can be extended using a method which generalizes Abbott-Hanson's
+[8] construction.
+Rowley named these partitions "templates", and we will keep this name in the entire article. We find suitable templates
+and use them
  to find new lower bounds for Schur numbers.
@@
 \begin{definition}
-	We call SF-template of \(n\) colors and lenght \(p\) a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
+We call SF-template of \(n\) colors and lenght \(p\) a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets \(A_1,
+A_2, ..., A_n\) which verify :
 	\[
@@
 	\]
-	We note \(S_+(n)\) the maximal lenght for a SF-template of \(n\) colors. 
+	We note \(S^+(n)\) the maximal lenght for a SF-template of \(n\) colors.
 \end{definition}
@@
 	\[
-	2S(n-1)+1 \leqslant S_+(n) \leqslant S(n)
+	2S(n-1)+1 \leqslant S^+(n) \leqslant S(n)
 	\]
@@
 \begin{remark}
-	\(S_+\) and \(S\) have the same asymptotic growth rate.
+	\(S^+\) and \(S\) have the same asymptotic growth rate.
 \end{remark}
 
-\subsection{Inequalities using \(S_+\)}
+\subsection{Inequalities using \(S^+\)}
 
-The main result on \(S_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(S_+\).
+The main result on \(S^+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(S^+\).
 
 \begin{theorem}
-	Let $(n,k), (p,q) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(p\),
-	and a partition of $n$ sum-free subsets of $[\![1,q]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,pq]\!]$.
+	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template of \(k+1\) colors and lenght \(p\),
+and a partition of \(n\) sum-free subsets of \([\![1,q]\!]\) then there exists a partition of \(n+k\) sum-free subsets
+of \([\![1,pq]\!]\).
 \end{theorem}
 
-Setting $p = S_+(k+1)$ and $q = S(n)$ yields the following corollary.
+Setting \(p = S^+(k+1)\) and \(q = S(n)\) yields the following corollary.
 
@@
 	Let \(n, k \in \mathbb{N}^*\), we have \\
-	\[ S(n+k) \geqslant S_+(k+1)S(n) \]
+	\[ S(n+k) \geqslant S^+(k+1)S(n) \]
 \end{corollary}
@@
 Using a SAT solvers, we are able to exhibit SF-template,
-hence providing lower bound on \(S_+\). Moreover, when using 
+hence providing lower bound on \(S^+\). Moreover, when using
 a SF-template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
-inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(S_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
+inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(S^+(k+1)\). Further details can be found in the
+\hyperref[SAT]{SAT section}.
 Here are the best inequalities on Schur numbers so far :
@@
 
-The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second one are due to Abott (référence nécessaire) 
+The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second one are due to
+Abott (référence nécessaire)
 and the third one to Rowley (reference nécessaire). The other ones are new. \\
 
-We also have a similar theorem where only \(S_+\) is involved.
+We also have a similar theorem where only \(S^+\) is involved.
 
 \begin{theorem}
-	Let $(n,k), (p,q) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(p\),
+	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template of \(k+1\) colors and lenght \(p\),
 	and \(SF\)-template of \(n\) color and lenght \(q\), then there exists \(SF\)-template of \((n+k)\) and lenght \(pq\).
@@
 	Let \(n, k \in \mathbb{N}^*\), we have \\
-	\[ S_+(n+k) \geqslant S_+(k+1)S_+(n) \]
+	\[ S^+(n+k) \geqslant S^+(k+1)S^+(n) \]
 \end{corollary}
@@
 \( n \geqslant 9 \). We compute the lower
-bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n = 8\) and \(n = 13\) were obtained thanks to the first one, found by Rowley.
-The best lower bounds are highlighted.\\
+bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n =
+8\) and \(n = 13\) were obtained thanks to the first one, found by Rowley. The best lower bounds are highlighted.\\
 \\
@@
 	\hline
-	\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\
-	\hline
+\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\	\hline
 	\(1140S(n-6) + 528 \) & 611568 & 1915728 & 6026568 & 20295948 \\

### 2021-04-08 article/weakschur.tex
formatage code

--- 2021-04-08 article/weakschur.tex
@@
 
-In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the integer \(WS_+(n)\) 
+In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the
+integer \(WS^+(n)\)
 to build suitable templates.
@@
 \begin{theorem}
-	Let $(p,q), (n,k) \in (\mathbb{N}^*)^2$. If there exists a partition of $[\![1,q]\!]$ into $n$ weakly sum-free subsets and a partition of $[\![1,p]\!]$ into $k$ sum-free 
-	subsets then there exists a partition of $[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]$ into $n+k$ weakly sum-free subsets.
+Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
+subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free
+subsets then there exists a partition of \([\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]\) into \(n+k\)
+weakly sum-free subsets.
 \end{theorem}
-In particular, if we choose $q = WS(n)$ and $p = S(k)$ in the last theorem, the next corollary follows.
+In particular, if we choose \(q = WS(n)\) and \(p = S(k)\) in the last theorem, the next corollary follows.
 \begin{corollary}
-	$ \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } WS(n+k) \geqslant S(k) \left (WS(n) + \left \lceil \frac{WS(n)}{2} \right \rceil +1 \right) + WS(n)$
+\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } WS(n+k) \geqslant S(k) \left (WS(n) + \left \lceil \frac{WS(n)}{2}
+\right \rceil +1 \right) + WS(n)\)
 \end{corollary}
-\textsc{Proof :} Let $(p,q), (n,k) \in (\mathbb{N}^*)^2$,  $N = p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q$, $\alpha = \left \lceil \frac{q}{2} \right \rceil > 0$ and $\beta = q + \alpha + 1$. 
-We denote by $f$ the projection of the equivalence relation induced by the partition of $[\![1,q]\!]$ and $g$ the one induced by the partition of $[\![1,p]\!]$.
-Each equivalence class is represented by a single integer, therefore :
+\textsc{Proof :} Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\), \(N = p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q\),
+\(\alpha = \left \lceil \frac{q}{2} \right \rceil > 0\) and \(\beta = q + \alpha + 1\).
+We denote by \(f\) the projection of the equivalence relation induced by the partition of \([\![1,q]\!]\) and \(g\) the
+one induced by the partition of \([\![1,p]\!]\). Each equivalence class is represented by a single integer, therefore :
 \[ f : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2, \left\{
@@
 \]
-\[g : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
+\[g : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } f(x) = f(y)
+\Longrightarrow f(x+y) \neq f(x)
 \]
-Let us start by parting the integers of $[\![1,N]\!]$ in two subsets $\mathcal{A}$ and $\mathcal{B}$ where $\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\}$ and $\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}$.\\
+Let us start by parting the integers of \([\![1,N]\!]\) in two subsets \(\mathcal{A}\) and \(\mathcal{B}\) where
+\(\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\}\) and
+\(\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}\).\\
 \\
-First, \underline{$\mathcal{A} \cap \mathcal{B} = \varnothing$} : \\
-By contradiction, suppose there exists $x \in \mathcal{A} \cap \mathcal{B} \neq \varnothing $.
-Then there are $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]$ and $(b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ such that $x = a\beta + u = b\beta +v$.
-By definition of $\alpha$ and  $\beta$ we have $u \in [\![\alpha + 1,q]\!] \subset [\![0,\beta - 1]\!]$.
+First, \underline{\(\mathcal{A} \cap \mathcal{B} = \varnothing\)} : \\
+By contradiction, suppose there exists \(x \in \mathcal{A} \cap \mathcal{B} \neq \varnothing \). Then there are \((a,u)
+\in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\) and \((b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\) such that \(x
+= a\beta + u = b\beta +v\). By definition of \(\alpha\) and \(\beta\) we have \(u \in [\![\alpha + 1,q]\!] \subset
+[\![0,\beta - 1]\!]\).
 From there, we distinguish two cases :
 \begin{itemize}
-	\item If $v \in [\![0,\alpha]\!]$ then $v \in [\![0,\beta - 1]\!]$ and $v \neq u$ because $v < \alpha + 1 \leqslant u$
-	\item If $v \in [\![-\alpha,-1]\!]$, we note $\tilde{v} = \beta + v$ and thus have $x = (b-1)\beta + \tilde{v}$ with $\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]$ and $\tilde{v} \neq u$ because $u < q+1 = \beta - \alpha \leqslant \tilde{v}$.
+\item If \(v \in [\![0,\alpha]\!]\) then \(v \in [\![0,\beta - 1]\!]\) and \(v \neq u\) because \(v < \alpha + 1
+\leqslant u\)
+\item If \(v \in [\![-\alpha,-1]\!]\), we note \(\tilde{v} = \beta + v\) and thus have \(x = (b-1)\beta + \tilde{v}\)
+with \(\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]\) and \(\tilde{v} \neq u\) because \(u
+< q+1 = \beta - \alpha \leqslant \tilde{v}\).
 \end{itemize}
-In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of $x$ by $\beta$.\\
+In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of \(x\) by
+\(\beta\).\\
 \\
-Then, we have \underline{$\mathcal{A} \cup \mathcal{B} = [\![1,N]\!]$}:
+Then, we have \underline{\(\mathcal{A} \cup \mathcal{B} = [\![1,N]\!]\)}:
 \begin{itemize}
-	\item On the one hand : $1 = \text{min($\mathcal{A}$)} \leqslant \text{max($\mathcal{A}$)} = p\beta + q = N$ and 
-	$1 \leqslant \beta - \alpha = \text{min($\mathcal{B}$)} \leqslant \text{max($\mathcal{B}$)} = p\beta + \alpha \leqslant N$, 
-	which gives $\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]$.
-	\item On the other hand, let $x \in  [\![1,N]\!]$. If $x \leqslant \alpha$, we directly have $x \in \mathcal{A}$, let us then suppose that $x > \alpha$ and write $x = a\beta + u$ 
-	the euclidean division of $x$ by $\beta$. We have $x \leqslant N$, thus $a \leqslant p$. We distinguish three cases : \\
-	- If $u \in [\![0,\alpha]\!]$ then we necessarily have $a \geqslant 1$ because $x > \alpha$, and so $x \in \mathcal{B}$.\\
-	- If $u \in [\![\alpha + 1,q]\!]$, then $x \in \mathcal{A}$. \\
-	- If $u \in [\![q + 1,\beta - 1]\!]$ then $x = (a+1)\beta - (\beta - u)$ with $-\alpha \leqslant \beta - u \leqslant 0$. 
-	Furthermore, $a \leqslant p - 1$, else we would have $x > N$, and so $x \in \mathcal{B}$ \\
-	In any case, $x \in \mathcal{A} \cup \mathcal{B}$ and we can thus conclude that $[\![1,N]\!] \subset \mathcal{A} \cup \mathcal{B}$.
+	\item On the one hand : \(1 = \text{min}(\mathcal{A}) \leqslant \text{max}(\mathcal{A}) = p\beta + q = N\) and
+\(1 \leqslant \beta - \alpha = \text{min}(\mathcal{B}) \leqslant \text{max}(\mathcal{B}) = p\beta + \alpha \leqslant
+N\),
+	which gives \(\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]\).
+\item On the other hand, let \(x \in [\![1,N]\!]\). If \(x \leqslant \alpha\), we directly have \(x \in \mathcal{A}\),
+let us then suppose that \(x > \alpha\) and write \(x = a\beta + u\)
+the euclidean division of \(x\) by \(\beta\). We have \(x \leqslant N\), thus \(a \leqslant p\). We distinguish three
+cases : \\
+- If \(u \in [\![0,\alpha]\!]\) then we necessarily have \(a \geqslant 1\) because \(x > \alpha\), and so \(x \in
+\mathcal{B}\).\\
+	- If \(u \in [\![\alpha + 1,q]\!]\), then \(x \in \mathcal{A}\). \\
+- If \(u \in [\![q + 1,\beta - 1]\!]\) then \(x = (a+1)\beta - (\beta - u)\) with \(-\alpha \leqslant \beta - u
+\leqslant 0\).
+	Furthermore, \(a \leqslant p - 1\), else we would have \(x > N\), and so \(x \in \mathcal{B}\) \\
+In any case, \(x \in \mathcal{A} \cup \mathcal{B}\) and we can thus conclude that \([\![1,N]\!] \subset \mathcal{A} \cup
+\mathcal{B}\).
 \end{itemize}
-This first partition of $[\![1,N]\!]$ will help us to define our final partition by the projection of its equivalence relation. 
-We thereby define $h : [\![1,N]\!] \longrightarrow [\![1,n+k]\!]$ as such :\\
-- If $x \in \mathcal{A}$ then $h(x) = f(x \text{ mod } \beta)$ (well defined because $x \text{ mod } \beta \in [\![1,N]\!]$)\\
-- If $x \in \mathcal{B}$ then $x = a\beta + u$ with a unique $(a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$ and we define $h(x) = n + g(a)$\\
-The fact that $(\mathcal{A}, \mathcal{B})$ is a partition of $[\![1,N]\!]$ ensures that this definition of $h$ is valid. We then have to verify that $h$ induces weakly sum-free subsets.\\
+This first partition of \([\![1,N]\!]\) will help us to define our final partition by the projection of its equivalence
+relation.
+We thereby define \(h : [\![1,N]\!] \longrightarrow [\![1,n+k]\!]\) as such :\\
+- If \(x \in \mathcal{A}\) then \(h(x) = f(x \text{ mod } \beta)\) (well defined because \(x \text{ mod } \beta \in
+[\![1,N]\!]\))\\
+- If \(x \in \mathcal{B}\) then \(x = a\beta + u\) with a unique \((a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\)
+and we define \(h(x) = n + g(a)\)\\
+The fact that \((\mathcal{A}, \mathcal{B})\) is a partition of \([\![1,N]\!]\) ensures that this definition of \(h\) is
+valid. We then have to verify that \(h\) induces weakly sum-free subsets.\\
 \\
-\underline{The classes of equivalence $h(x)$ for $x \in \mathcal{A}$ are weakly sum-free :}
+\underline{The classes of equivalence \(h(x)\) for \(x \in \mathcal{A}\) are weakly sum-free :}
 \\
 \\
-Let $(x,y) \in \mathcal{A}^2$ such that $h(x) = h(y)$, $x \neq y$ and $x + y \leqslant N$
+Let \((x,y) \in \mathcal{A}^2\) such that \(h(x) = h(y)\), \(x \neq y\) and \(x + y \leqslant N\)
 \begin{itemize}
-	\item If $(x,y) \in [\![1,\alpha]\!]^2$ :\\
-	We have $x + y \leqslant 2\alpha \leqslant q$ and $x + y = 0\beta + x + y$, therefore $x + y \in \mathcal{A}$. 
-	Then, by definition : $h(x) = f(x)$, $h(y) = f(y)$ and $h(x+y) = f(x+y)$, which gives us, thanks to the property verified by $f$, that $h(x+y) \neq h(x)$.
-	\item If $(x,y) \in [\![1,\alpha]\!] \times ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )$ :\\
-	We write $y = a\beta + u$ with $(a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]$. Then $x+y = a\beta + x + u = (a+1)\beta + x + u - \beta$, 
-	and if $x + u > q$ it follows that $a \leqslant p-1$ since $x+y \leqslant N$, and $-\alpha \leqslant x + u - \beta \leqslant -1$. 
-	Therefore $x+y \in \mathcal{B}$ and $h(x+y) \neq h(x) = f(x)$ by definition of h. On the contrary, if $x - u \leqslant n$, 
-	then $x+y \in \mathcal{A}$ and $h(x+y) = f(x+u)$ because $x+u$ is actually the remainder of the euclidean division of $x+y$ by $\beta$. 
-	Moreover, $h(x) = f(x)$, $x < u$ and, with our initial hypothesis, $h(x) = h(y) = f(u)$. The property verified by $f$ gives us $f(x+u) \neq f(x)$ which can be rewritten as $h(x+y) \neq h(x)$.
-	\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] ) \times [\![1,\alpha]\!]$ : \\
-	This case is handled exactly like the previous one by swaping the roles of $x$ and $y$.
-	\item If $(x,y) \in ( \mathcal{A} \text{ \textbackslash} \text{ } [\![1,\alpha]\!] )^2$ : \\
-	We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![0,p]\!] \times [\![\alpha + 1,q]\!]$. Then $x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta$ 
-	with $a+b \leqslant p-1$ (else we would have $x+y > N$ because $u+v > q$) and $-\alpha \leqslant u + v - \beta \leqslant \alpha$, therefore $x+y \in \mathcal{B}$ and by definition $h(x+y) \neq h(x)$.
+	\item If \((x,y) \in [\![1,\alpha]\!]^2\) :\\
+	We have \(x + y \leqslant 2\alpha \leqslant q\) and \(x + y = 0\beta + x + y\), therefore \(x + y \in \mathcal{A}\).
+Then, by definition : \(h(x) = f(x)\), \(h(y) = f(y)\) and \(h(x+y) = f(x+y)\), which gives us, thanks to the property
+verified by \(f\), that \(h(x+y) \neq h(x)\).
+	\item If \((x,y) \in [\![1,\alpha]\!] \times ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] )\) :\\
+We write \(y = a\beta + u\) with \((a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\). Then \(x+y = a\beta + x + u =
+(a+1)\beta + x + u - \beta\),
+and if \(x + u > q\) it follows that \(a \leqslant p-1\) since \(x+y \leqslant N\), and \(-\alpha \leqslant x + u -
+\beta \leqslant -1\).
+Therefore \(x+y \in \mathcal{B}\) and \(h(x+y) \neq h(x) = f(x)\) by definition of h. On the contrary, if \(x - u
+\leqslant n\),
+then \(x+y \in \mathcal{A}\) and \(h(x+y) = f(x+u)\) because \(x+u\) is actually the remainder of the euclidean division
+of \(x+y\) by \(\beta\).
+Moreover, \(h(x) = f(x)\), \(x < u\) and, with our initial hypothesis, \(h(x) = h(y) = f(u)\). The property verified by
+\(f\) gives us \(f(x+u) \neq f(x)\) which can be rewritten as \(h(x+y) \neq h(x)\).
+	\item If \((x,y) \in ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] ) \times [\![1,\alpha]\!]\) : \\
+	This case is handled exactly like the previous one by swaping the roles of \(x\) and \(y\).
+	\item If \((x,y) \in ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] )^2\) : \\
+We write \(x = a\beta + u\) and \(y = b\beta + v\) with \((a,u)\) and \((b,v)\) in \([\![0,p]\!] \times [\![\alpha +
+1,q]\!]\). Then \(x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta\)
+with \(a+b \leqslant p-1\) (else we would have \(x+y > N\) because \(u+v > q\)) and \(-\alpha \leqslant u + v - \beta
+\leqslant \alpha\), therefore \(x+y \in \mathcal{B}\) and by definition \(h(x+y) \neq h(x)\).
 \end{itemize}
-In any case, $h(x+y) \neq h(x)$ and the classes of equivalence $h(x)$ for $x \in \mathcal{A}$ are weakly sum-free.\\
+In any case, \(h(x+y) \neq h(x)\) and the classes of equivalence \(h(x)\) for \(x \in \mathcal{A}\) are weakly
+sum-free.\\
 \\
-\underline{The classes of equivalence $h(x)$ for $x \in \mathcal{B}$ are weakly sum-free :}
+\underline{The classes of equivalence \(h(x)\) for \(x \in \mathcal{B}\) are weakly sum-free :}
 \\
 \\
-Let $(x,y) \in \mathcal{B}^2$ such that $h(x) = h(y)$, $x \neq y$ and $x + y \leqslant N$.\\
-We write $x = a\beta + u$ and $y = b\beta + v$ with $(a,u)$ and $(b,v)$ in $[\![1,p]\!] \times [\![-\alpha,\alpha]\!]$. 
-We have $h(x) = q + g(a)$ and $h(y) = q + g(b)$, therefore $g(a) = g(b)$. We also have $x+y = (a+b)\beta + u +v$.\\
-If $u + v \in [\![-\alpha,\alpha]\!]$, then $x+y \in \mathcal{B}$ and $h(x+y) = g(a+b)$, hence we can deduce that $h(x+y) \neq h(x)$ because of the property verified by $g$.
-On the contrary, if $u+v \notin [\![-\alpha,\alpha]\!]$, then necessarily $x+y \in \mathcal{A}$.
-Suppose $x+y \in \mathcal{B}$, then $x+y = c\beta + w$ with $(c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]$.
-Thus, $c\beta + w = (a+b)\beta + u + v$ and $(a+b-c)\beta = w-u-v$.
-Furthermore $a+b-c \neq 0$, else we would have $u+v = w \in [\![-\alpha,\alpha]\!]$.
-This finally leads to the following inequality :
+Let \((x,y) \in \mathcal{B}^2\) such that \(h(x) = h(y)\), \(x \neq y\) and \(x + y \leqslant N\).\\
+We write \(x = a\beta + u\) and \(y = b\beta + v\) with \((a,u)\) and \((b,v)\) in \([\![1,p]\!] \times
+[\![-\alpha,\alpha]\!]\).
+We have \(h(x) = q + g(a)\) and \(h(y) = q + g(b)\), therefore \(g(a) = g(b)\). We also have \(x+y = (a+b)\beta + u
++v\).\\
+If \(u + v \in [\![-\alpha,\alpha]\!]\), then \(x+y \in \mathcal{B}\) and \(h(x+y) = g(a+b)\), hence we can deduce that
+\(h(x+y) \neq h(x)\) because of the property verified by \(g\). On the contrary, if \(u+v \notin
+[\![-\alpha,\alpha]\!]\), then necessarily \(x+y \in \mathcal{A}\). Suppose \(x+y \in \mathcal{B}\), then \(x+y = c\beta
++ w\) with \((c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\). Thus, \(c\beta + w = (a+b)\beta + u + v\) and
+\((a+b-c)\beta = w-u-v\). Furthermore \(a+b-c \neq 0\), else we would have \(u+v = w \in [\![-\alpha,\alpha]\!]\). This
+finally leads to the following inequality :
 \[\beta \leqslant |a+b-c|\beta = |w-u-v| \leqslant |w| + |u| + |v| \leqslant 3\alpha \leqslant q + \alpha < \beta
 \]
-which is absurd.
-We can therefore conclude that $x+y \in \mathcal{A}$ and by definition of $h$, $h(x+y) \neq h(x)$, proving that the classes of equivalence $h(x)$ for $x \in \mathcal{B}$ are weakly sum-free.\\
+which is absurd. We can therefore conclude that \(x+y \in \mathcal{A}\) and by definition of \(h\), \(h(x+y) \neq
+h(x)\), proving that the classes of equivalence \(h(x)\) for \(x \in \mathcal{B}\) are weakly sum-free.\\
 \\
-Finally, we have showed that every classe of equivalence induced by $h$ is weakly sum-free, which ends the proof.
+Finally, we have showed that every classe of equivalence induced by \(h\) is weakly sum-free, which ends the proof.
 
@@
 This formula includes the results of Rowley \hyperlink{label2}{\textbf{[2]}} as a special case. For \(n>2\),
-this formula does not give new lower bounds but in the same way as we introduced \(S_+\)\hyperref[SE]{(Definition 3.1)}, 
-we will define \(WS_+\) and find inequalities between \(WS_+\),\(WS\) and \(S\)
+this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition 3.1)},we will define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
 \end{remark}
 
-\subsection{Definition of \(WS_+\)}
+\subsection{Definition of \(WS^+\)}
 \begin{definition}
@@
 \begin{definition}
-Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note: 
-\\\\\(WS_b^+=\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a \(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
+Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\)
+subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note:
+\\\\\(WS_b^+=\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
+\(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
 \\\\
@@
 Let \((p,k,b) \in (\mathbb{N}^*)^3\), let \( (q,n) \in (\mathbb{N}^*)^2\). If there exists a partition of \(n\)
- sum-free subsets of \([\![1,q]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, p]\!]\) which is a \(b\)-WSF of \(k\) colors and lenght \(p\), 
- then there exists a partition of \([\![1, b+c+q \times p]\!]\) into \((k+n-1)\) weakly sum-free subsets with c=\(min A_p\bigcap [\![b+1, p]\!] -b-1\).
+sum-free subsets of \([\![1,q]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, p]\!]\) which is a
+\(b\)-WSF of \(k\) colors and lenght \(p\),
+ then there exists a partition of \([\![1, b+q \times p]\!]\) into \((k+n-1)\) weakly sum-free subsets.
 \end{theorem}
 
+In particular, if we choose \(q = S(n)\) and \(p = WS^+(k)\) in the last theorem, the next corollary follows.
+
+\begin{corollary}
+\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(k+1)=WS_b^+(k+1)\},\)	\[ WS(n+k) \geqslant S(n) WS^+(k+1)+b_{max}\]
+\end{corollary}
+
+\begin{remark}
+There exists a \(c(b) \geqslant \text{min}(A_{k+1} \backslash [\![1,b] - b - 1\) such that \(c(b)\) numbers can be
+added at the end of the extended partition.Therefore, we can get a better lower bound by finding a couple \((b,c(b))\)
+which maximizes the sum \(b+c(b)\) such that \(WS^+(k+1)=WS_b^+(k+1)\). Hence we have:
+	\[ WS(n+k) \geqslant S(n) WS^+(k+1)+b+c(b)\]
+
+\end{remark}
+
 \subsection{New lower bounds for Weak Schur numbers}
-Having found suitable templates, which can be found in the appendix,  with a SAT solver, we claim that for all \(n \in \mathbb{N}^*\):
+Having found suitable templates, which can be found in the appendix, with a SAT solver, we claim that for all \(n \in
+\mathbb{N}^*\):
 \[
@@
 \]
-The first two inequalities are due to Rowley, they are detailed in [2].
-Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \).
-The best lower bound for each integer is highlighted.\\
+The first two inequalities are due to Rowley, they are detailed in [2]. Like in 3.3, we compute the lower bounds given
+by the previous inequalities for \( n \in [\![8,15]\!] \). The best lower bound for each integer is highlighted.\\
 \\
@@
 inequality doesn't give any better lower bound, even beyond \( n = 15 \)
-: the best bounds are always provided by the first three. We highly suspect that these values can be improved by investigating the search
+: the best bounds are always provided by the first three. We highly suspect that these values can be improved by
+investigating the search
 space further, which would provide new, more effective templates. One

### 2021-04-08 article/article.tex
Le pouvoir de BibTeX ᕕ( ᐛ )ᕗ

--- 2021-04-07 article/article.tex
@@
 
-\section{References}
-
-\hypertarget{label1}{\textbf{[1]}} Schur, I. 1917. Uber die Kongruenz \(x^m + y^m = z^m~(\text{mod}~p)\). Jahresbericht der 
-Deutschen Mathematikervereinigung 25:114–117.: 114-116. \url{http://eudml.org/doc/145475}
-
-\hypertarget{label2}{\textbf{[2]}} Rowley, F. 2020. New Lower Bounds for Weak Schur Partitions. arXiv 2011.11292, 
-\url{https://arxiv.org/pdf/2011.11292.pdf}
-
-\hypertarget{label3}{\textbf{[3]}} Heule, M.J.H. 2017. Schur Number Five. arXiv 1711.08076, \url{https://arxiv.org/pdf/1711.08076.pdf}
-
-\hypertarget{label4}{\textbf{[4]}} S. Eliahou, J.M. Marín, M.P. Revuelta and M.I. Sanz 2012. Weak Schur numbers and the search for G.W. 
-Walker’s lost partitions. Computers \& Mathematics with Applications Vol. 63, \url{https://www.sciencedirect.com/science/article/pii/S0898122111009722}
-
-\hypertarget{label5}{\textbf{[5]}} Bierem, A. 2017. CaDiCaL, Lingeling, Plingeling, Treengeling, YalSAT Entering the SAT Competition 2017. 
-Proceedinfs of SAT Competition 2017 -- Solver and Benchmark Descriptions \url{http://fmv.jku.at/papers/Biere-SAT-Competition-2017-solvers.pdf}
+\bibliography{biblio}
+\bibliographystyle{plain}
 

### 2021-04-08 article/intro.tex
formatage code
Le pouvoir de BibTeX ᕕ( ᐛ )ᕗ

@@
 
-Schur proved in \hyperlink{label1}{\textbf{[1]}} that given a number of subsets \(n\), there exists a value of \(p\)
+Schur proved in \cite{Schur1917} that given a number of subsets \(n\), there exists a value of \(p\)
 such that there exists no partition of \([\![1,q]\!]\) into \(n\) sum-free subsets for any \(q \geqslant p\). A similar
 property holds for weakly sum-free subsets (reference necessaire). These observations lead to the following definitions.
-
 \begin{definition}
@@
 \([\![1,S(n)]\!]\) (resp. \([\![1,WS(n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
-subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(WS(n)\) the \(n\)\textsuperscript{th} weak
+subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(WS(n)\) the
+\(n\)\textsuperscript{th} weak
 Schur number}.
@@
 \begin{notation}
-For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally note these subsets \(A_1, ..., A_n\). We also note \(m_i = \text{min}(A_i)\). 
-By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do not make this hypothesis since we 
+For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally note these subsets \(A_1, ..., A_n\). We also note
+\(m_i = \text{min}(A_i)\).
+By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do not make this
+hypothesis since we
 do not always consider partitions in which every subset plays a symmetric role.

### 2021-04-08 article/sat.tex
Le pouvoir de BibTeX ᕕ( ᐛ )ᕗ

@@
 We encode the existence of (weakly) sum-free partitions as propositional formulae like in
-\hyperlink{label3}{\textbf{[3]}} and then use
+\cite{Heule2017} and then use
 SAT solvers to determine whether these formulae are satisfiable.
@@
 \subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
-Rowley's new lower bound for \(WS(6)\) (642) \hyperlink{label2}{\textbf{[2]}} was a quite significant improvement upon
+Rowley's new lower bound for \(WS(6)\) (642) \cite{RowleyWS} was a quite significant improvement upon
 the former
-best known lower bound (582) \hyperlink{label7}{\textbf{[7]}}. This previous lower bound was found using a computer
+best known lower bound (582) \cite{EliahouBook}. This previous lower bound was found using a computer
 (often with Monte-Carlo methods) and by making the
@@
 
-This result was obtained in 8 hours with the SAT solver plingeling \hyperlink{label5}{\textbf{[5]}} on a 2.60 GHz Intel
+This result was obtained in 8 hours with the SAT solver plingeling \cite{Lingeling2017} on a 2.60 GHz Intel
 i7 processor PC.
@@
 \par
-\hyperlink{label4}{\textbf{[4]}} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of
+\cite{ELIAHOU2012175} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of
 \([\![1,197]\!]\) with
@@
 weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5
-seconds with the SAT solver glucose \hyperlink{label6}{\textbf{[6]}}
+seconds with the SAT solver glucose \cite{Glucose}
 on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here for the sake of comparison but in the rest of

### 2021-04-08 article/schur.tex
Le pouvoir de BibTeX ᕕ( ᐛ )ᕗ

@@
 
-\qquad In this section, we use Rowley's constructions [7] in a Schur context. To improve lower bounds for Ramsay's
+\qquad In this section, we use Rowley's constructions \cite{RowleyRamsey} in a Schur context. To improve lower bounds for Ramsay's
 numbers, Rowley
 introduces partitions verifying some properties which can be extended using a method which generalizes Abbott-Hanson's
-[8] construction.
+\cite{AbbottHanson} construction.
 Rowley named these partitions "templates", and we will keep this name in the entire article. We find suitable templates
@@
 
-The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second one are due to
-Abott (référence nécessaire)
-and the third one to Rowley (reference nécessaire). The other ones are new. \\
+The first inequality comes from the original Schur's paper \cite{Schur1917}. The second one are due to
+Abott \cite{AbbottHanson}
+and the third one to Rowley \cite{RowleyRamsey}. The other ones are new. \\
 
@@
 numbers growth rate, a lower bound can be found using Schur's one, thanks to \(S(n) \leqslant R_n(3)-2 \)
-(see \hyperlink{label1}{\textbf{[1]}}).
+(see \cite{Schur1917}).

### 2021-04-08 article/intro.tex

@@
 \section{Abstract}
+
+\qquad This paper offers new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
+Rowley's "templates"-based approach for Ramsey numbers in 2020. Finding suitable templates allows us to apply Rowley's construction 
+to get explicit partitions improving lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
+the principle that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding
+the previous lower bound \(WS(6) \geqslant 582\) is impossible with such a method upon imposing certain conditions on the good
+5-subsets partition. The new lower bounds includes \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
 

### 2021-04-08 weak_schur_sat/check_assumption/utils.py
espace de recherche non otpimal (SAT)

@@ -1,0 +1,62 @@
+def load_pos(k, file):
+    cnf = []
+    with open(file) as f:
+        for i, line in enumerate(f.readlines()):
+            clause = ""
+            for c in map(int, line.strip().split()):
+                clause += f"{k * i + c} "
+            cnf.append(clause[:-1])
+    return cnf
+
+
+def weakly_sum_free(k, n):
+    cnf = []
+    for c in range(k):
+        for i in range(1, n + 1):
+            for j in range(i + 1, n + 1):
+                tot = i + j
+                if tot > n:
+                    break
+                no_sum = f"-{i * k - c} -{j * k - c} -{tot * k - c}"
+                cnf.append(no_sum)
+    return cnf
+
+
+def use_all(k, n):
+    cnf = []
+    for i in range(n):
+        use_i = " ".join(map(str, range(k * i + 1, k * (i + 1) + 1)))
+        cnf.append(use_i)
+    return cnf
+
+
+def disjoint(k, n):
+    cnf = []
+    for i in range(1, n + 1):
+        for c1 in range(k):
+            for c2 in range(c1 + 1, k):
+                cnf.append(f"-{k * i - c1} -{k * i - c2}")
+    return cnf
+
+
+def break_symmetries(k):
+    cnf = ["1"]
+    if k >= 3:
+        cnf.append(f"-{k + 3}")
+        cnf.append(f"{k + 2} -{2 * k + 3}")
+    if k >= 4:
+        clause= ""
+        for i in range(2, 9):
+            cnf.append(clause + f"-{k * i + 4}")
+            clause += f"{k * i + 3} "
+    if k >= 5:
+        clause= ""
+        for i in range(2, 24):
+            cnf.append(clause + f"-{k * i + 5}")
+            clause += f"{k * i + 4} "
+    if k >= 6:
+        clause= ""
+        for i in range(2, 67):
+            cnf.append(clause + f"-{k * i + 6}")
+            clause += f"{k * i + 5} "
+    return cnf

### 2021-04-08 article/article.tex

@@
 
+\par
+These new results come from Rowley's approach for Ramsey graphs which is relatively new. Therefore, it would not surprise us
+if lower bounds are later improved using better templates. Moreover, studying specifically \(S_+(n)\) and \(WS_+(n)\) numbers might be
+of interest as they are closely related to Schur and weak Schur numbers.
+
+\par
+The fifth section gives new insight on the method that was formerly used to achieve new lower bounds. The principle behind it
+might have discarded many interesting partititions of the search space and lowered the highest value that can be reached within it.
+However, algorithms based on randomness such as Monte-Carlo algorithms may appear very useful if used in a search space with more
+potential. For example, such an algorithm could be used to find better templates and improve inequalities and lower bounds for high values
+of \(n\). This could be the subject fo a future work. Nevertheless, it would not help for the smallest values.
+
 \section{Acknowledgments}
+
+\par
+We would first like to address warm thanks to Fred Rowley who kindly answered our many questions and with who it was a pleasure
+to exchange. A great thank-you to Marijn Heule who also took the time to respond to our requests. Finally, last but not least, we would
+like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised us during the whole research and writing.
 

### 2021-04-08 article/schur.tex

@@
 \end{corollary}
+
+\textsc{Proof :} We denote by \(f\) the projection of the equivalence relation induced by the \(SF\)-template of lenght \(p\) 
+and \(g\) the one induced by the sum-free partition of \([\![1,q]\!]\). Each equivalence class is represented by a single integer, therefore :
+
+\[ f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!] \text{ and } \forall (x,y) \in [\![1,p]\!]^2, \left\{
+\begin{array}{ll}
+	f(x) = f(y) \leqslant k \\
+	x + y > p
+\end{array}
+\right.
+\Longrightarrow f(x+y-p) \neq f(x)
+\]
+with also the sum-free condition : \[ \forall (x,y) \in [\![1,p]\!]^2 \text{, } f(x) = f(y)
+\Longrightarrow f(x+y) \neq f(x) \]
+
+\[g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } g(x) = g(y)
+\Longrightarrow g(x+y) \neq g(x)
+\]
+
+We now define \(h : [\![1,pq]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
+\( \forall x \in [\![1,pq]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q]\!] \) and \( u \in [\![0,p-1]\!] \).
+This decomposition if of course unique. If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1) \) \(h(x) = k + g(\alpha) \). 
+Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.
+
+Let \(x,y \in [\![1,pq]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq\). We write \(x = \alpha p - u\) and \(y = \beta p - v\). \\
+We simply need \(h(x+y) \neq h(x)\). \\
+
+We first examine the case where \(h(x) \leqslant k\). We assume \(h(x+y) \leqslant k\), otherwise we are fine. 
+Thus by definition of \(h\), we have \(h(x) = f(p-u) = f(p-v) = h(y)\).
+\begin{itemize}
+\item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
+We have \(f(p-u) = f(p-v)  \leqslant k\) and \(p-u + p-v > p\), the extra condition on \(f\) provides \(f(p-u-v) \neq f(p-u)\).
+We assumed \(h(x+y) \leqslant k\) hence \(h(x+y) = f(p-u-v)\). Since \(h(x) = f(p-u)\), we have at last \(h(x+y) \neq h(x)\).
+\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
+We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f((p-u + p-v))\). Since \(f(p-u+p-v) \neq f(p-u)\),
+we get \(h(x+y) \neq h(x)\).
+\end{itemize}
+
+We now assume \(h(x) > k\) (and also \(h(x+y) > k\) otherwise the expected result is trivial). 
+Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(alpha) = g(\beta\). We have the two same cases as before.
+
+\begin{itemize}
+\item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
+Since \(g(alpha) = g(\beta)\), the sum-free condition garanties \(g\alpha) \neq g(\alpha+\beta)\), 
+thus \(h(x+y) = k + g(\alpha + \beta) \neq k + g(\alpha) = h(x)\).
+\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
+Because of the assumption \(h(x) > k\), we necessarily have \(f(p-u) = k+1 = f(p-v)\). 
+Then \(f(p-(u+v-p)) = f(p-u + p-v) \leqslant k \) with the sum-free condition on \(f\), 
+hence \(h(x+y) = f(p-(u+v-p)) \) by construction of \(h\). Thus \(h(x+y) \leqslant k < h(x)\).
+\end{itemize}
 

### 2021-04-08 article/weakschur.tex

@@
 
-In this section, we generalize Rowley's constructions in [2]. We then introduce, by analogy with the third section, the
+In this section, we generalize Rowley's constructions in \cite{RowleyWS}. We then introduce, by analogy with the third section, the
 integer \(WS^+(n)\)
@@
 
-Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction [refenrece]. Here we
+Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction \cite{AbbottHanson}. Here we
 give a general lower bound for weak Schur numbers as a function of both regular and weak Schur numbers.
@@
 \begin{remark}
-This formula includes the results of Rowley \hyperlink{label2}{\textbf{[2]}} as a special case. For \(n>2\),
+This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\),
 this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition 3.1)},we will define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
@@
 space further, which would provide new, more effective templates. One
-may try to go over this search space using a Monte-Carlo method, as in (ref Bouzy),
+may try to go over this search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP},
 but with a different search space (as we explain in \hyperref[SAT]{SAT section}).

### 2021-04-08 article/schur.tex
preuve 3.1 v2

@@
 
-We now assume \(h(x) > k\) (and also \(h(x+y) > k\) otherwise the expected result is trivial). 
-Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(alpha) = g(\beta\). We have the two same cases as before.
+We now assume \(h(x) > k\). Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta\). 
+We have the two same cases as before.
 
@@
 \item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
-Since \(g(alpha) = g(\beta)\), the sum-free condition garanties \(g\alpha) \neq g(\alpha+\beta)\), 
+We assume \(h(x+y) > k\) otherwise the expected result is trivial.
+Since \(g(\alpha) = g(\beta)\), the sum-free condition garanties \(g\alpha) \neq g(\alpha+\beta)\), 
 thus \(h(x+y) = k + g(\alpha + \beta) \neq k + g(\alpha) = h(x)\).

### 2021-04-09 article/schur.tex
longueur des lignes

@@
 
-\qquad In this section, we use Rowley's constructions \cite{RowleyRamsey} in a Schur context. To improve lower bounds for Ramsay's
+\qquad In this section, we use Rowley's constructions \cite{RowleyRamsey} in a Schur context. To improve lower bounds
+for Ramsay's
 numbers, Rowley
@@
 
-\textsc{Proof :} We denote by \(f\) the projection of the equivalence relation induced by the \(SF\)-template of lenght \(p\) 
-and \(g\) the one induced by the sum-free partition of \([\![1,q]\!]\). Each equivalence class is represented by a single integer, therefore :
+\textsc{Proof :} We denote by \(f\) the projection of the equivalence relation induced by the \(SF\)-template of lenght
+\(p\)
+and \(g\) the one induced by the sum-free partition of \([\![1,q]\!]\). Each equivalence class is represented by a
+single integer, therefore :
 
@@
 We now define \(h : [\![1,pq]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
-\( \forall x \in [\![1,pq]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q]\!] \) and \( u \in [\![0,p-1]\!] \).
-This decomposition if of course unique. If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1) \) \(h(x) = k + g(\alpha) \). 
+\( \forall x \in [\![1,pq]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q]\!] \) and \( u \in
+[\![0,p-1]\!] \).
+This decomposition if of course unique. If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \).
 Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.
 
-Let \(x,y \in [\![1,pq]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq\). We write \(x = \alpha p - u\) and \(y = \beta p - v\). \\
+Let \(x,y \in [\![1,pq]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq\). We write \(x = \alpha p - u\) and \(y =
+\beta p - v\). \\
 We simply need \(h(x+y) \neq h(x)\). \\
@@
 \item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
-We have \(f(p-u) = f(p-v)  \leqslant k\) and \(p-u + p-v > p\), the extra condition on \(f\) provides \(f(p-u-v) \neq f(p-u)\).
-We assumed \(h(x+y) \leqslant k\) hence \(h(x+y) = f(p-u-v)\). Since \(h(x) = f(p-u)\), we have at last \(h(x+y) \neq h(x)\).
+We have \(f(p-u) = f(p-v) \leqslant k\) and \(p-u + p-v > p\), the extra condition on \(f\) provides \(f(p-u-v) \neq
+f(p-u)\).
+We assumed \(h(x+y) \leqslant k\) hence \(h(x+y) = f(p-u-v)\). Since \(h(x) = f(p-u)\), we have at last \(h(x+y) \neq
+h(x)\).
 \item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
-We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f((p-u + p-v))\). Since \(f(p-u+p-v) \neq f(p-u)\),
-we get \(h(x+y) \neq h(x)\).
+We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f((p-u + p-v))\). Since \(f(p-u+p-v) \neq
+f(p-u)\),we get \(h(x+y) \neq h(x)\).
 \end{itemize}
@@
 \( n \geqslant 9 \). We compute the lower
-bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n =
-8\) and \(n = 13\) were obtained thanks to the first one, found by Rowley. The best lower bounds are highlighted.\\
+bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n
+=8\) and \(n = 13\) were obtained thanks to the first one, found by Rowley. The best lower bounds are highlighted.\\
 \\
@@
 	\hline
-\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\	\hline
+\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\\hline
 	\(1140S(n-6) + 528 \) & 611568 & 1915728 & 6026568 & 20295948 \\

### 2021-04-09 article/schur.tex
preuve 3.1 v3

--- 2021-04-08 article/schur.tex
@@
 \item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
-We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f((p-u + p-v))\). Since \(f(p-u+p-v) \neq f(p-u)\),
+We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f(p-u + p-v)\). Since \(f(p-u+p-v) \neq f(p-u)\),
 we get \(h(x+y) \neq h(x)\).
@@
 
-We now assume \(h(x) > k\). Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta\). 
+We now assume \(h(x) > k\). Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). 
 We have the two same cases as before.
@@
 We assume \(h(x+y) > k\) otherwise the expected result is trivial.
-Since \(g(\alpha) = g(\beta)\), the sum-free condition garanties \(g\alpha) \neq g(\alpha+\beta)\), 
+Since \(g(\alpha) = g(\beta)\), the sum-free condition garanties \(g(\alpha) \neq g(\alpha+\beta)\), 
 thus \(h(x+y) = k + g(\alpha + \beta) \neq k + g(\alpha) = h(x)\).

### 2021-04-09 article/schur.tex

--- 2021-04-09 article/schur.tex
@@
 \item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
-We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f((p-u + p-v))\). Since \(f(p-u+p-v) \neq
-f(p-u)\),we get \(h(x+y) \neq h(x)\).
+We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f(p-u + p-v)\). Since \(f(p-u+p-v) \neq f(p-u)\),
+we get \(h(x+y) \neq h(x)\).
 \end{itemize}
 
-We now assume \(h(x) > k\). Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta\). 
+We now assume \(h(x) > k\). Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). 
 We have the two same cases as before.

### 2021-04-09 article/weakschur.tex

@@
 
-In this section, we generalize Rowley's constructions in \cite{RowleyWS}. We then introduce, by analogy with the third section, the
+In this section, we generalize Rowley's constructions in \cite{RowleyWS}. We then introduce, by analogy with the third
+section, the
 integer \(WS^+(n)\)
@@
 
-Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction \cite{AbbottHanson}. Here we
+Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction \cite{AbbottHanson}. Here
+we
 give a general lower bound for weak Schur numbers as a function of both regular and weak Schur numbers.
@@
 \item If \(v \in [\![-\alpha,-1]\!]\), we note \(\tilde{v} = \beta + v\) and thus have \(x = (b-1)\beta + \tilde{v}\)
-with \(\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]\) and \(\tilde{v} \neq u\) because \(u
-< q+1 = \beta - \alpha \leqslant \tilde{v}\).
+with \(\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]\) and \(\tilde{v} \neq u\) because
+\(u< q+1 = \beta - \alpha \leqslant \tilde{v}\).
 \end{itemize}
-In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of \(x\) by
-\(\beta\).\\
+In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of \(x\)
+by\(\beta\).\\
 \\
@@
 	Furthermore, \(a \leqslant p - 1\), else we would have \(x > N\), and so \(x \in \mathcal{B}\) \\
-In any case, \(x \in \mathcal{A} \cup \mathcal{B}\) and we can thus conclude that \([\![1,N]\!] \subset \mathcal{A} \cup
-\mathcal{B}\).
+In any case, \(x \in \mathcal{A} \cup \mathcal{B}\) and we can thus conclude that \([\![1,N]\!] \subset \mathcal{A}
+\cup\mathcal{B}\).
 \end{itemize}
@@
 [\![1,N]\!]\))\\
-- If \(x \in \mathcal{B}\) then \(x = a\beta + u\) with a unique \((a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\)
-and we define \(h(x) = n + g(a)\)\\
+- If \(x \in \mathcal{B}\) then \(x = a\beta + u\) with a unique \((a,u) \in [\![1,p]\!] \times
+[\![-\alpha,\alpha]\!]\)and we define \(h(x) = n + g(a)\)\\
 The fact that \((\mathcal{A}, \mathcal{B})\) is a partition of \([\![1,N]\!]\) ensures that this definition of \(h\) is
@@
 \leqslant n\),
-then \(x+y \in \mathcal{A}\) and \(h(x+y) = f(x+u)\) because \(x+u\) is actually the remainder of the euclidean division
-of \(x+y\) by \(\beta\).
+then \(x+y \in \mathcal{A}\) and \(h(x+y) = f(x+u)\) because \(x+u\) is actually the remainder of the euclidean
+divisionof \(x+y\) by \(\beta\).
 Moreover, \(h(x) = f(x)\), \(x < u\) and, with our initial hypothesis, \(h(x) = h(y) = f(u)\). The property verified by
@@
 \(h(x+y) \neq h(x)\) because of the property verified by \(g\). On the contrary, if \(u+v \notin
-[\![-\alpha,\alpha]\!]\), then necessarily \(x+y \in \mathcal{A}\). Suppose \(x+y \in \mathcal{B}\), then \(x+y = c\beta
-+ w\) with \((c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\). Thus, \(c\beta + w = (a+b)\beta + u + v\) and
+[\![-\alpha,\alpha]\!]\), then necessarily \(x+y \in \mathcal{A}\). Suppose \(x+y \in \mathcal{B}\), then \(x+y =
+c\beta+ w\) with \((c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\). Thus, \(c\beta + w = (a+b)\beta + u + v\) and
 \((a+b-c)\beta = w-u-v\). Furthermore \(a+b-c \neq 0\), else we would have \(u+v = w \in [\![-\alpha,\alpha]\!]\). This
@@
 This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\),
-this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition 3.1)},we will define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
+this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
+3.1)},we will define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
 \end{remark}
@@
 \begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(k+1)=WS_b^+(k+1)\},\)	\[ WS(n+k) \geqslant S(n) WS^+(k+1)+b_{max}\]
+\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(k+1)=WS_b^+(k+1)\},\) \[
+WS(n+k) \geqslant S(n) WS^+(k+1)+b_{max}\]
 \end{corollary}

### 2021-04-09 article/schur.tex
Ajout intuition tableau

--- 2021-04-09 article/schur.tex
@@
 
+The idea lying beneath this inequality is similar to Abbott and Hanson's
+contruction. We build a table where every column is colored according
+to a SF-template partition of order \(n+1\) and where there are
+\(S^+(n)\) rows. The resulting coloring of the table gives a sum-free
+partitions thnaks to the properties of the SF-template. We give the
+following table for \(n = 2\) to make the intuition cleared. This
+intuition will be formalised in the proof.
+\begin{center}
+\(\overset{S^+(3)}{S^+(2) \left \updownarrow\overleftrightarrow{\begin{tabular}{|*{7}{c|}}
+	\hline
+	\cellcolor{red} 1 & \cellcolor{blue} 2 & \cellcolor{blue} 3 & \cellcolor{green} 4 & \cellcolor{red} 5 & \cellcolor{green} 6 & \cellcolor{blue} 7 \\
+	\hline
+	\cellcolor{red} 8 & \cellcolor{blue} 9 & \cellcolor{blue} 10 & \cellcolor{green} 11 & \cellcolor{red} 12 & \cellcolor{green} 13 & \cellcolor{blue} 14\\
+	\hline
+	\cellcolor{red} 15 & \cellcolor{blue} 16 & \cellcolor{blue} 17 & \cellcolor{green} 18 & \cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{blue} 21 \\
+	\hline
+	\cellcolor{red} 22 & \cellcolor{blue} 23 & \cellcolor{blue} 24 & \cellcolor{green} 25 & \cellcolor{red} 26 & \cellcolor{green} 27 & \cellcolor{blue} 28 \\
+	\hline
+\end{tabular}}
+\right.}\)
+\end{center}
+
 \subsection{New lower bounds for Schur numbers}

### 2021-04-09 article/schur.tex
exemple template

--- 2021-04-09 article/schur.tex
@@
 \end{corollary}
+
+See below an example of such a construction. \\
+It is quite similar to Abott and Hanson construction \cite{AbbottHanson}. They extend vertically a sum-free partition,
+and horizontally an other sum-free partition. This way each "block" acts like a security zone for the other one.
+Here, the horizontal partition is no longer to the side of the vertical one, but occupies the column of the special color
+of the \(SF\)-template, i.e the one without the extra condition.
 
@@
 
-The first inequality comes from the original Schur's paper \cite{Schur1917}. The second one are due to
+The first inequality comes from the original Schur's paper \cite{Schur1917}. The second one is due to
 Abott \cite{AbbottHanson}
@@
 \end{corollary}
+
+\textsc{Proof :} The idea is the same as in the previous theorem. The only difference is the \(SF\) property inherited 
+from the second \(SF\)-template.
 

### 2021-04-09 article/weakschur.tex
lemme+tableau

@@
 \subsection{Definition of \(WS^+\)}
+
+We will now define notations and results, we will use in the following theorem.
+
+\begin{notation}
+
+Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\pi_{a,b}\) the projection:
+\[ \pi_{a,b}:x->(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a}))\]
+\end{notation}
+
+We will note  the projection \(\pi\) and not \(\pi_{a,b}\) when there is no doubt about the a and b we use.
+
+\begin{Proposition}
+Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
+\end{Proposition}
+
+\textsc{Proof :}Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)
+
+\\\\if \(x+\pi(y)< a:\)we remark that \(\pi(y)>b\) and therefore \(x+\pi(y)>b\):
+
+\begin{align*}
+ \\\pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
+& =x+ \pi(y)
+\end{align*}
+
+\\if \(x+\pi(y\geqslant a\):
+\begin{align*}
+ \\\pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
+& = x+\pi(y) - a +a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
+& = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
+& = x+\pi(y)
+\end{align*}
+
+\begin{Proposition}
+Let (x,y)\(\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
+\end{Proposition}
+
+\textsc{Proof :}Let (x,y)\(\in (\mathbb{N}^*)^2\),
+
+\begin{align*}
+ \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})((Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a})+(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{y mod a})\text{ mod a}) \\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ ((x mod a) + (y mod a)) mod a})\\
+& =(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ x+y mod a})\\
+& =\pi(x+y)
+\end{align*}
+
+\begin{notation}
+
+Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\lambda_{a,b}\) the projection:
+\[ \lambda_{a,b}:x->1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
+\end{notation}
+
+We will note  the projection \(\lambda\) and not \(\lambda_{a,b}\) when there is no doubt about the a and b we use.
+
+\begin{remark}
+In the following theorem, \(\lambda\) is the function which return the line number of an element x.
+\end{remark}
+
+\begin{Proposition}
+Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
+\end{Proposition}
+\textsc{Proof :}Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\),
+\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(\text{x mod a})+\mathbf{1}_{ [\![0,b]\!]}(\text{x mod a})\)
+
+\\\\if x mod a \(>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+\text{x mod a}=x\)
+
+\\\\if x mod a \(\leqslant b\):
+\(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)
 \begin{definition}
@@
 \end{corollary}
+
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
+\hline
+  & & & & & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
+\hline
+   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
+\hline
+\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
+\hline
+...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
+\hline
+\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
+\hline
+...&...&...&...&...&...&...&...&...&...&...&...&...\\
+\hline
+\end{tabular}
 

### 2021-04-09 article/weakschur.tex
correction

@@
 subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note:
-\\\\\(WS_b^+=\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
+\\\\\(WS_b^+=-b+\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
 \(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
@@
 \begin{theorem}
-Let \((p,k,b) \in (\mathbb{N}^*)^3\), let \( (q,n) \in (\mathbb{N}^*)^2\). If there exists a partition of \(n\)
-sum-free subsets of \([\![1,q]\!]\) and a partition of k subsets \((A_1,....,A_k)\) of \([\![1, p]\!]\) which is a
-\(b\)-WSF of \(k\) colors and lenght \(p\),
- then there exists a partition of \([\![1, b+q \times p]\!]\) into \((k+n-1)\) weakly sum-free subsets.
+Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \(k\)
+sum-free subsets of \([\![1,p]\!]\) and a partition of n subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
+\(b\)-WSF of \(n\) colors and lenght \(q\),
+ then there exists a partition of \([\![1, b+q \times (p-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
 \end{theorem}
 
-In particular, if we choose \(q = S(n)\) and \(p = WS^+(k)\) in the last theorem, the next corollary follows.
+In particular, if we choose \(p = S(k)\) and \(q = WS^+(n)\) in the last theorem, the next corollary follows.
 
 \begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(k+1)=WS_b^+(k+1)\},\) \[
-WS(n+k) \geqslant S(n) WS^+(k+1)+b_{max}\]
+\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(n+1)=WS_b^+(n+1)\},\) \[
+WS(n+k) \geqslant S(k) WS^+(n+1)+b_{max}\]
 \end{corollary}

### 2021-04-09 article/weakschur.tex
synthaxe
correction

@@
 
-\begin{Proposition}
+\begin{proposition}
 Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
-\end{Proposition}
+\end{proposition}
 
@@
 
-\begin{Proposition}
+\begin{proposition}
 Let (x,y)\(\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
-\end{Proposition}
+\end{proposition}
 
@@
 
-\begin{Proposition}
+\begin{proposition}
 Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
-\end{Proposition}
+\end{proposition}
 \textsc{Proof :}Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\),
@@
 \(b\)-WSF of \(n\) colors and lenght \(q\),
- then there exists a partition of \([\![1, b+q \times (p-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
+ then there exists a partition of \([\![1, b+p \times (q-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
 \end{theorem}

### 2021-04-09 article/weakschur.tex
modification \

@@
 
-\\\\if \(x+\pi(y)< a:\)we remark that \(\pi(y)>b\) and therefore \(x+\pi(y)>b\):
+if \(x+\pi(y)< a:\)we remark that \(\pi(y)>b\) and therefore \(x+\pi(y)>b\):
 
 \begin{align*}
- \\\pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
+ \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
 & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
@@
 \begin{align*}
- \\\pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
+ \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
 & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\

### 2021-04-09 article/schur.tex

@@
 and a partition of \(n\) sum-free subsets of \([\![1,q]\!]\) then there exists a partition of \(n+k\) sum-free subsets
-of \([\![1,pq]\!]\).
+of \([\![1,pq+m_{k+1}-1]\!]\). \(m_{k+1}\) is the first number colored with the \(k+1\)-th color in the \(SF\)-template.
 \end{theorem}
@@
 	Let \(n, k \in \mathbb{N}^*\), we have \\
-	\[ S(n+k) \geqslant S^+(k+1)S(n) \]
+	\[ S(n+k) \geqslant S^+(k+1)S(n) + m_{k+1} - 1 \]
 \end{corollary}
 
-See below an example of such a construction. \\
-It is quite similar to Abott and Hanson construction \cite{AbbottHanson}. They extend vertically a sum-free partition,
-and horizontally an other sum-free partition. This way each "block" acts like a security zone for the other one.
-Here, the horizontal partition is no longer to the side of the vertical one, but occupies the column of the special color
-of the \(SF\)-template, i.e the one without the extra condition.
+The idea lying beneath this inequality is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. 
+They extend vertically a sum-free partition, and horizontally an other sum-free partition. This way each "block" 
+acts like a security zone for the other one. Here, the horizontal partition is no longer to the side of the 
+vertical one, but occupies the column of the special color of the \(SF\)-template, i.e the one without the 
+extra condition. We give the following table for \(p = 7, q = 4, n = 2 ~\textrm{and}~ k = 2\) to make the intuition clear. \\
+
+This shows the inequality \(S(2+2) \geqslant S^+(3)S(2)\), with the extra constant. 
+We prooved \(S^+(3) = 9\).The special color is blue.
+
+\(\overset{SF\textrm{-template}}{\textrm{Sum-free partition} \left \updownarrow\overleftrightarrow{\begin{tabular}{|*{9}{c|}}
+	\hline
+	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
+	\hline
+	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
+	\hline
+	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
+	\hline
+	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{red} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36\\
+	\hline
+	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 & & & & &\\
+	\hline
+\end{tabular}}
+\right.}\)
+ \\
+
+\begin{center}
+\(SF\)-template with 3 colors (it is actually maximal)\\
+\begin{tabular}{|*{9}{c|}}
+	\hline 
+	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
+	\hline
+\end{tabular} \\
+
+Sum-free partition (\(S(2)\) actually) \\
+\begin{tabular}{|*{4}{c|}}
+	\hline 
+	\cellcolor{blue} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{blue} 4 \\
+	\hline
+\end{tabular}
+\end{center}
+
+To compare, here is a classic Abbott and Hanson partition : \(S(2+2) \geqslant S(2)(2S(2)+1)+S(2) \). \\
+
+\begin{center}
+\begin{tabular}{|*{9}{c|}}
+	\hline
+	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{blue} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
+	\hline
+	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{yellow} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
+	\hline
+	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{yellow} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
+	\hline
+	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{blue} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36 \\
+	\hline
+	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 & & & & &\\
+	\hline
+\end{tabular}
+\end{center}
 
@@
 We now define \(h : [\![1,pq]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
-\( \forall x \in [\![1,pq]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q]\!] \) and \( u \in
+\( \forall x \in [\![1,pq + m_{k+1}-1]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q]\!] \) and \( u \in
 [\![0,p-1]\!] \).

### 2021-04-09 article/intro.tex
valeurs + precision

@@
 \qquad This paper offers new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
-Rowley's "templates"-based approach for Ramsey numbers in 2020. Finding suitable templates allows us to apply Rowley's construction 
+Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction 
 to get explicit partitions improving lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
@@
 the previous lower bound \(WS(6) \geqslant 582\) is impossible with such a method upon imposing certain conditions on the good
-5-subsets partition. The new lower bounds includes \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
+5-subsets partition. The new lower bounds includes\(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
 

### 2021-04-09 article/schur.tex
tableaux abbot

@@
 
-This shows the inequality \(S(2+2) \geqslant S^+(3)S(2)\), with the extra constant. 
-We prooved \(S^+(3) = 9\).The special color is blue.
+This shows the inequality \(S(2+2) \geqslant S^+(3)S(2) + 4\). The special color is blue and is first used
+to color 5, hence \(4 = m_{3} - 1\). 
+We prooved \(S^+(3) = 9\). The special color is blue.
 
-\(\overset{SF\textrm{-template}}{\textrm{Sum-free partition} \left \updownarrow\overleftrightarrow{\begin{tabular}{|*{9}{c|}}
+\begin{center}
+\(\overset{S^+(3)}{\left. \overleftrightarrow{\begin{tabular}{|*{9}{c|}}
 	\hline
@@
 \end{tabular}}
-\right.}\)
- \\
+\right \updownarrow S(2)}\)
+\end{center}
 
 \begin{center}
-\(SF\)-template with 3 colors (it is actually maximal)\\
+\(S^+(3)\)\\
 \begin{tabular}{|*{9}{c|}}
@@
 
-Sum-free partition (\(S(2)\) actually) \\
+\(S(2)\) \\
 \begin{tabular}{|*{4}{c|}}
@@
 \Longrightarrow f(x+y) \neq f(x) \]
+Moreover, by definition of \(m_{k+1}\), if \(x < m_{k+1}\), \(f(x) \leqslant k\).
 
@@
 
-We now define \(h : [\![1,pq]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
-\( \forall x \in [\![1,pq + m_{k+1}-1]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q]\!] \) and \( u \in
+We now define \(h : [\![1,pq+m_{k+1}-1]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
+\( \forall x \in [\![1,pq + m_{k+1}-1]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q+1]\!] \) and \( u \in
 [\![0,p-1]\!] \).
-This decomposition if of course unique. If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \).
+This decomposition if of course unique. \\
+If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \). \\
+If \(\alpha = q+1\), we have a problem plugging it into \(g\). Hopefully, this issue never arises : if 
+\(\alpha = q+1\), we have \(u > p - m_{k+1}\) since \(x \in [\![1,pq + m_{k+1}-1]\!]\), hence \(p-u < m_{k+1}\) and \(f(p-u) \leqslant k\). \\
 Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.
 
-Let \(x,y \in [\![1,pq]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq\). We write \(x = \alpha p - u\) and \(y =
+Let \(x,y \in [\![1,pq + m_{k+1}-1]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq+m_{k+1}-1\). We write \(x = \alpha p - u\) and \(y =
 \beta p - v\). \\

### 2021-04-09 article/article.tex
Ajout annexe et templates

@@
 
+\appendix
+\renewcommand{\arraystretch}{1}
+\section{SF-templates}
+\begin{center}
+SF-template partitionning \([\![1, 111]\!]\) into 5 subsets
+\begin{tabular}{|*{2}{c|}}
+	\hline
+	1 & 1, 5, 18, 12, 14 ,21, 23, 30, 32, 36, 39, 43, 45, 52, 103 \\
+	 & 106, 110 \\
+	\hline
+	2 & 2, 6, 7, 10, 15, 18, 26, 29, 34, 37, 38, 42, 46, 51, 54 \\
+	& 101, 104, 109 \\
+	\hline
+	3 & 3, 4, 9, 11, 17, 19, 25, 27, 33, 35, 40, 41, 47, 48, 55 \\
+	& 100, 107, 108 \\
+	\hline
+	4 & 13, 16, 20, 22, 24, 28, 31, 58, 61, 67, 88, 94, 97 \\
+	\hline
+	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70\\
+	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85\\
+	& 86, 87, 89, 90, 91, 92, 93, 95, 96, 98, 99, 102, 105, 111 \\
+	\hline
+\end{tabular}
+\end{center}
+\begin{center}
+SF-template partitionning \([\![1, 380]\!]\) into 6 subsets
+\begin{tabular}{|*{2}{c|}}
+	\hline
+	1 & 1, 5, 8, 11, 15, 17, 29, 33, 36, 39, 43, 57, 61, 88, 92 \\
+	& 106, 110, 113, 116, 120, 132, 134, 138, 141, 144, 148, 150, 154, 157, 160 \\
+	& 164, 178, 182, 185, 188, 341, 344, 347, 351, 365, 369, 372, 375, 379\\
+	\hline
+	2 & 2, 9, 13, 16, 20, 23, 24, 27, 28, 31, 34, 35, 38, 42, 45\\
+	& 49, 53, 60, 67, 71, 78, 82, 89, 96, 100, 104, 107, 111, 114, 115\\
+	& 118, 121, 122, 125, 126, 129, 133, 136, 140, 147, 158, 162, 165, 169, 172\\
+	& 176, 183, 187, 194, 201, 328, 335, 342, 346, 353, 357, 360, 364, 367, 371\\
+	\hline
+	3 & 3, 4, 12, 14, 19, 25, 30, 32, 40, 41, 47, 48, 58, 91, 101\\
+	& 102, 108, 109, 117, 119, 124, 130, 135, 137, 145, 146, 152, 153, 161, 163\\
+	& 168, 179, 181, 190, 339, 348, 350, 361, 366, 368, 376, 377\\
+	\hline
+	4 & 6, 7, 10, 18, 21, 22, 26, 37, 46, 50, 51, 54, 65, 70, 79\\
+	& 84, 95, 98, 99, 103, 112, 123, 127, 128, 131, 139, 142, 143, 151, 155\\
+	& 156, 159, 167, 170, 171, 175, 186, 343, 354, 358, 359, 362, 370, 373, 374\\
+	& 378\\
+	\hline
+	5 & 44, 52, 55, 56, 59, 62, 63, 64, 66, 68, 69, 72, 73, 74, 75\\
+	& 76, 77, 80, 81, 83, 85, 86, 87, 90, 93, 94, 97, 105, 189, 196\\
+	& 197, 200, 203, 206, 207, 209, 214, 219, 231, 298, 310, 315, 320, 322, 323\\
+	& 326, 329, 332, 333, 340\\
+	\hline
+	6 & 149, 166, 173, 174, 177, 180, 184, 191, 192, 193, 195, 198, 199, 202, 204\\
+	& 205, 208, 210, 211, 212, 213, 215, 216, 217, 218, 220, 221, 222, 223, 224\\
+	& 225, 226, 227, 228, 229, 230, 232, 233, 234, 235, 236, 237, 238, 239, 240\\
+	& 241, 242, 243, 244, 245, 246, 247, 248, 249, 250, 251, 252, 253, 254, 255\\
+	& 256, 257, 258, 259, 260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270\\
+	& 271, 272, 273, 274, 275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285\\
+	& 286, 287, 288, 289, 290, 291, 292, 293, 294, 295, 296, 297, 299, 300, 301\\
+	& 302, 303, 304, 305, 306, 307, 308, 309, 311, 312, 313, 314, 316, 317, 318\\
+	& 319, 321, 324, 325, 327, 330, 331, 334, 336, 337, 338, 345, 349, 352, 355\\
+	& 356, 363, 380\\
+	\hline
+
+\end{tabular}
+\end{center}
+\section{WSF-templates}
+\begin{center}
+WSF-template partitionning \([\![1, 42]\!]\) into 4 subsets
+\begin{tabular}{|*{2}{c|}}
+	\hline
+	1 & 1, 2, 4, 8, 11, 22, 25 & \textbf{(66)}\\
+	\hline
+	2 & 5, 6, 7, 19, 21, 23, 36\\
+	\hline
+	3 & 9, 10, 12, 13, 14, 15, 16, 17, 18, 20\\
+	\hline
+	4 & 24, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 37, 38, 39, 40\\
+	& 41, 42\\
+	\hline
+\end{tabular}
+\end{center}
+This template produces the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
+by placing 66 in the first subset.
+
 \end{document}

### 2021-04-09 article/schur.tex
tableaux section 3

@@
 
-Using a SAT solvers, we are able to exhibit SF-template,
-hence providing lower bound on \(S^+\). Moreover, when using
-a SF-template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
-inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(S^+(k+1)\). Further details can be found in the
-\hyperref[SAT]{SAT section}.
+Using a SAT solvers, we are able to exhibit SF-template, hence providing lower bound on \(S^+\). 
+We seek templates providing the best lower bound possible, but also the best additive constant (\(m_{k+1}\) with the previous notation). 
+Further details can be found in the\hyperref[SAT]{SAT section}. \\
+
 Here are the best inequalities on Schur numbers so far :

### 2021-04-09 article/article.tex
Correction petite erreur
Format A4
Déplacement de l'abstract

@@
 
+\usepackage[a4paper, total={6in, 8in}]{geometry}
+
 \begin{document}
+
 \maketitle
+
+\begin{abstract}
+
+This paper offers new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
+Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction 
+to get explicit partitions improving lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
+the principle that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding
+the previous lower bound \(WS(6) \geqslant 582\) is impossible with such a method upon imposing certain conditions on the good
+5-subsets partition. The new lower bounds includes\(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
+
+\end{abstract}
 
@@
 	\hline
-	1 & 1, 2, 4, 8, 11, 22, 25 & \textbf{(66)}\\
+	1 & 1, 2, 4, 8, 11, 22, 25, \textbf{(66)}\\
 	\hline

### 2021-04-09 article/article.tex

@@
 the previous lower bound \(WS(6) \geqslant 582\) is impossible with such a method upon imposing certain conditions on the good
-5-subsets partition. The new lower bounds includes\(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
+5-subsets partition. The new lower bounds includes \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
 
@@
 \par
-The fifth section gives new insight on the method that was formerly used to achieve new lower bounds. The principle behind it
+The fourth section gives new insight on the method that was formerly used to achieve new lower bounds. The principle behind it
 might have discarded many interesting partititions of the search space and lowered the highest value that can be reached within it.

### 2021-04-09 article/weakschur.tex
modification \
tableaux accolades
theoreme weak schur

@@
 
-\\if \(x+\pi(y\geqslant a\):
+if \(x+\pi(y\geqslant a\):
 \begin{align*}
@@
 
-\\\\if x mod a \(>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+\text{x mod a}=x\)
+if x mod a \(>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+\text{x mod a}=x\)
 
-\\\\if x mod a \(\leqslant b\):
+if x mod a \(\leqslant b\):
 \(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)
@@
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
-\hline
-  & & & & & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
+\cline{4-9}
+   \multicolumn{5}{c|}{} & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
 \hline
@@
 \end{tabular}
+
+\textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b
+
+We denote by \(g\) the projection of the equivalence relation induced by the partition of \([\![1,q]\!]\) and \(h\) the
+one induced by the partition of \([\![1,p]\!]\). Each equivalence class is represented by a single integer, therefore :
+\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
+\]
+\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
+\Longrightarrow h(x+y) \neq h(x)
+\]
+
+Let \( f : [\![1,b+p \time a]\!] \longrightarrow [\![1,n]\!] \) such as:
+\\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
+\\\\-if \( x \in [\![1,b+p \time a]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
+\\\\-if \( x \in [\![1,b+p \time a]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{L}): f(x)=n-1+h(\lambda(x))\)
+\\\\
+f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+p \time a]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)
+
+We have parted the integers of \(\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{L}\).
+
+We have to verify that f induces weakly-sum-free templates:\\
+\\
+\underline{if (x,y) \(\in (\mathcal{T})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\\x+y\(<\)a+b since b\(<\)a and g(x)=f(x)=f(y)=g(y). 
+\\Hence f(x+y)=g(x+y)\(\neq\)g(x)=f(x)
+\\\\
+\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{C}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+We distinguish two cases:
+
+\begin{itemize}
+\item If x+\(\pi(y)\leqslant a+b\)
+\\g(x)=f(x)=f(y)=g(\(\pi(y)\). Hence g(x)\(\neq g(x+\pi(y))=g(\pi(x+y))\) (qv previous proposition)
+\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
+\\else, \(f(x+y)=g(\pi(x+y))\neq g(x)=f(x)\)
+\item If x+\(\pi(y)> a+b\), x+y\(>\)a+b and by definition of g, \(g(\pi(x+y))\neq g(x)\)
+\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
+\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
+\end{itemize}
+
+\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{L}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\\Then, f(x)=f(y)=n. We distinguish two cases:
+
+\begin{itemize}
+\item If \(\lambda(y)=\lambda(x+y)\),
+\\\(g(x)=g(\pi(y))=n \text{ since } g(y)=g(\pi(y))\)
+\\Therefore \(g(\pi(x+y))=g(x+\pi(y)) \neq g(x)=n\)(qv previous proposition)
+\\Hence \(f(x+y)=g(\pi(x+y))\neq n\)
+\item If  \(\lambda(y)\neq \lambda(x+y)\), \(\lambda(y)+1= \lambda(x+y)\)\\
+n=f(y)=n-1+h(\(\lambda(y)\)). Hence h(\(\lambda(y)\))=1.
+\\Moreover h(1)=1, therefore \(h(\lambda(y)+1) \neq 1\)
+\\if \(\pi(x+y) \in A_n\), \(f(x+y)=n-1+h(\lambda(x+y))>n\)
+\end{itemize}
+
+\underline{if (x,y) \(\in (\mathcal{C})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases:
+
+\begin{itemize}
+\item If \(\pi(x)+\pi(y)>q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) (qv previous proposition)
+\\Hence \(g(\pi(x+y))= g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))\) 
+\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
+\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
+\item If  \(\pi(x)+\pi(y)\leqslant q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) since g is sum-free for x\(>b\)
+\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
+\\else, \(f(x+y)=g(\pi(x+y))=g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))=f(x)\)
+
+\end{itemize}
+
+\underline{if (x,y) \(\in \mathcal{C} \times \mathcal{L} \), \(f(x)\neq f(y)\)}\\
+
+\underline{if (x,y) \(\in (\mathcal{L})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\\Let r(x)=\(\pi(x)-a\) and r(y)=\(\pi(y)-a\),
+\\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
+\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases:
+
+\begin{itemize}
+\item If \(r(x)+r(y) \in [\![b-a+1,b]\!]\), \(h(\lambda(x))=f(x)+1-n=f(y)+1-n=h(\lambda(y))\)
+Hence, \(h(\lambda(x)+\lambda(y)) \neq h(\lambda(x))\).
+\begin{align*}
+ \\\lambda(x+y) & =1+\left\lfloor\dfrac{a(\lambda(x)+\lambda(y))+r(x)+r(y)-b-1}{a}\right\rfloor+1\\
+& = \lambda(x)+\lambda(y)+\left\lfloor\dfrac{r(x)+r(y)-b-1}{a}\right\rfloor+1 \\
+& = \lambda(x)+\lambda(y) -1 +1 \text{ since } r(x)+r(y) \in [\![b-a+1,b]\!] \\
+& =\lambda(x)+\lambda(y)
+\end{align*}
+
+\begin{align*}
+ \\\text{if f(x+y)\(\geqslant\)n, }f(x+y) & =n-1+h(\lambda(x+y))\\
+& =n-1+h(\lambda(x)+\lambda(y)) \\
+& \neq n-1+h(\lambda(x))\\
+& =f(x)
+\end{align*}
+
+\item If \(r(x)+r(y)>b\), \(\pi(x)+\pi(y)>2a+b\)
+\\Since g is a b-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
+\\Therefore, \(g(\pi(x+y)) \neq n\) ie \(x+y \in \mathcal{C}\)
+\\Hence \(f(x+y) <n\leqslant f(x)\)
+\item If \(r(x)+r(y)\leqslant b-a,\), \(\pi(x)+\pi(y)\leqslant b+a\)
+\\Since g is sum-free for x\(>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
+\\Hence, \(f(x+y) <n\leqslant f(x)\)
+\end{itemize}
 

### 2021-04-09 article/weakschur.tex
tableaux 5

@@
 \renewcommand{\arraystretch}{2}
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
-\cline{4-9}
+\begin{center}
+\[
+\begin{array}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
+\cline{6-9}
    \multicolumn{5}{c|}{} & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
@@
 \hline
-\end{tabular}
-
-\textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b
-
+\end{array}
+\]
+\end{center}
+\textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
 We denote by \(g\) the projection of the equivalence relation induced by the partition of \([\![1,q]\!]\) and \(h\) the
@@
 
-Let \( f : [\![1,b+p \time a]\!] \longrightarrow [\![1,n]\!] \) such as:
+Let \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such as:
 \\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
-\\\\-if \( x \in [\![1,b+p \time a]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
-\\\\-if \( x \in [\![1,b+p \time a]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{L}): f(x)=n-1+h(\lambda(x))\)
+\\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
+\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{L}): f(x)=n-1+h(\lambda(x))\)
 \\\\
-f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+p \time a]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)
+f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)
 

### 2021-04-09 article/article.tex
explication intuitive + valuers

--- 2021-04-09 article/article.tex
@@
 The fifth section gives new insight on the method that was formerly used to achieve new lower bounds. The principle behind it
-might have discarded many interesting partititions of the search space and lowered the highest value that can be reached within it.
+might have discarded many interesting partitions of the search space and lowered the highest value that can be reached within it.
 However, algorithms based on randomness such as Monte-Carlo algorithms may appear very useful if used in a search space with more
@@
 	\hline
-	1 & 1, 2, 4, 8, 11, 22, 25 & \textbf{(66)}\\
+	1 & 1, 2, 4, 8, 11, 22, 25\\
 	\hline
@@
 \end{center}
-This template produces the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
-by placing 66 in the first subset.
 

### 2021-04-09 article/weakschur.tex
explication intuitive + valuers

--- 2021-04-09 article/weakschur.tex
@@
 \end{theorem}
+
 In particular, if we choose \(q = WS(n)\) and \(p = S(k)\) in the last theorem, the next corollary follows.
+
 \begin{corollary}
@@
 \end{corollary}
+
+\begin{remark}
+In the above ineqality, a "\(+1\)" can be added to the lower bound if \(WS(n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less 
+clear and it is never useful in practice.
+\end{remark}
+
+We first give an intuitive explanation of the above theorem. Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
+subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\) and let's try to build a colouring of \([\![1, ap + q]\!]\) 
+into \(n + k\) weakly sum-free subsets. Let \(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\). \\
+
+First, put the integers of \([\![1, ap + q]\!]\) in the following table (with \(a\) columns and \(p + 1\) lines) and divide it into 3 blocks (the columns are numbered from \(-l\) to \(+q\)):
+
+\begin{itemize}
+	\item \(\mathcal{T}\) (the "tail"): the integers from 1 to \(q\). NB: this is line number 0.
+	\item \(\mathcal{L}\) (the "lines"): the integers in columns \(-l\) to \(+r\) (excluding  \(\mathcal{T}\)).
+	\item \(\mathcal{C}\) (the "columns"): the integers in the last \(w\) columns (excluding  \(\mathcal{T}\)).
+\end{itemize}
+
+Note that with this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the sum of the columns modulo \(a\).
+
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
+\hline
+  & & & & & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} ...&\cellcolor{green}\(r\)&\(r+1\)&...&\(b - 1\)&\(b\) \\
+\hline
+   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
+\hline
+\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
+\hline
+...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
+\hline
+\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
+\hline
+...&...&...&...&...&...&...&...&...&...&...&...&...\\
+\hline
+\end{tabular}
+
+\underline{\textbf{\(\mathcal{T}\) block}} \\
+We color this block using the weakly sum-free colouring of \([\![1,q]\!]\) with colors \(1, ..., n\).
+
+\underline{\textbf{\(\mathcal{L}\) block}} \\
+In this block,  we use the colors \(n + 1, ..., n + k\). We colour an integer \(x\) according to its line number (written \(\lambda(x)\)).
+For every \(x \in \mathcal{L}\), we colour \(x\) with \(n + c\) where \(c\) is the colour of \(\lambda(x)\) in the sum-free colouring of  \([\![1,p]\!]\).
+Let \((x, y) \in \mathcal(L)^2\). The cases are twofold.
+
+\begin{itemize}
+	\item \underline{\(\lambda(x+y) = \lambda(x) + \lambda(y)\)} \\
+	In this case, we use the sum-free property of the colouring of \([\![1,p]\!]\) (in block \(\mathcal{C}\), we only use colours \(1, ..., n\)).
+
+	\item \underline{\(\lambda(x+y) \neq \lambda(x) + \lambda(y)\)} \\
+	In this case, we do not have information about the colour of \(\lambda(x+y)\). Thereby, we want to have \(x+y \in \mathcal{C}\).
+	A simple solution is to limit the horizontal movement, that is if the sum changes line, not to move too far so that it stays in \(\mathcal{C}\). 
+	There, the maximal displacement to the left (resp. to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left 
+	is then expressed as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written as
+	 \(\text{max}(l, r) \leqslant w\).
+\end{itemize}
+
+\underline{\textbf{\(\mathcal{C}\) block}} \\
+In this block,  we use colors \(1, ..., n\). We colour an integer \(x\) according to its column number (written \(\tilde{\pi}(x)\), it is linked to the 
+projection on the first line, written \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\)). A simple solution is to colour \(x\) with the same colour 
+as \(\tilde{\pi}(x)\) in the weakly sum-free colouring of \([\![1,q]\!]\). As long as \(2b \leqslant a + r\) (not going two far to the right) and there 
+is no \(x \in \tilde{\pi}(\mathcal{C})\) such that \(2x \in \tilde{\pi}(\mathcal{C})\) (so that we do not have a sum in \(\mathcal{C}\) when 
+taking two numbers in the same column), the colours \(1, ..., n\) are sum-free. \\
+
+In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem. \\
+
 \textsc{Proof :} Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\), \(N = p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q\),
@@
 \end{corollary}
-
-\renewcommand{\arraystretch}{2}
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
-\hline
-  & & & & & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
-\hline
-   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
-\hline
-\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
-\hline
-...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
-\hline
-\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
-\hline
-...&...&...&...&...&...&...&...&...&...&...&...&...\\
-\hline
-\end{tabular}
 

### 2021-04-09 article/article.tex

--- 2021-04-09 article/article.tex
@@
 \par
-The fourth section gives new insight on the method that was formerly used to achieve new lower bounds. The principle behind it
-might have discarded many interesting partititions of the search space and lowered the highest value that can be reached within it.
+The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak Schur numbers. The principle behind it
+might have discarded many interesting partitions of the search space and lowered the highest value that can be reached within it.
 However, algorithms based on randomness such as Monte-Carlo algorithms may appear very useful if used in a search space with more

### 2021-04-09 article/schur.tex

@@
 \begin{center}
-\(\overset{S^+(3)}{\left. \overleftrightarrow{\begin{tabular}{|*{9}{c|}}
+\[
+\begin{array}{|*{9}{c|}}
+	\multicolumn{9}{c}{\overset{S^+(3)}{\overbrace{\rule{6cm}{0pt}}}} \\
 	\hline
-	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
+	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9 \\
 	\hline
@@
 	\hline
-	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 & & & & &\\
-	\hline
-\end{tabular}}
-\right \updownarrow S(2)}\)
+	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 \\
+	\cline{1-4}
+\end{array}
+\]
 \end{center}
@@
 \begin{center}
-\(S^+(3)\)\\
-\begin{tabular}{|*{9}{c|}}
+\[
+S^+(3) 
+\begin{array}{|*{9}{c|}}
 	\hline 
@@
 	\hline
-\end{tabular} \\
-
-\(S(2)\) \\
-\begin{tabular}{|*{4}{c|}}
+\end{array}  \]
+\[
+S(2) 
+\begin{array}{|*{4}{c|}}
 	\hline 
@@
 	\hline
-\end{tabular}
+\end{array}
+\]
 \end{center}
 
-To compare, here is a classic Abbott and Hanson partition : \(S(2+2) \geqslant S(2)(2S(2)+1)+S(2) \). \\
-
+To compare, here is a classic Abbott and Hanson partition : \(S(2+2) \geqslant S(2)(2S(2)+1)+S(2) \). 
 \begin{center}
-\begin{tabular}{|*{9}{c|}}
+\[
+\begin{array}{|*{9}{c|}}
+	\multicolumn{4}{c}{\overset{S(2)}{\overbrace{\rule{2.6cm}{0pt}}}} \\
 	\hline
@@
 	\hline
-	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 & & & & &\\
-	\hline
-\end{tabular}
+	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 \\
+	\cline{1-4}
+\end{array}
+\]
 \end{center}
@@
 This decomposition if of course unique. \\
+
 If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \). \\
@@
 \(\alpha = q+1\), we have \(u > p - m_{k+1}\) since \(x \in [\![1,pq + m_{k+1}-1]\!]\), hence \(p-u < m_{k+1}\) and \(f(p-u) \leqslant k\). \\
-Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.
+
+Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.\\
 
 Let \(x,y \in [\![1,pq + m_{k+1}-1]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq+m_{k+1}-1\). We write \(x = \alpha p - u\) and \(y =
-\beta p - v\). \\
-We simply need \(h(x+y) \neq h(x)\). \\
+\beta p - v\). We simply need \(h(x+y) \neq h(x)\). \\
 

### 2021-04-09 article/weakschur.tex

--- 2021-04-09 article/weakschur.tex
@@
 \end{corollary}
+
+\begin{remark}
+In the above ineqality, a "\(+1\)" can be added to the lower bound if \(WS(n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less
+clear and it is never useful in practice.
+\end{remark}
+
+We first give an intuitive explanation of the above theorem. Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
+subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\) and let's try to build a colouring of \([\![1, ap + q]\!]\)
+into \(n + k\) weakly sum-free subsets. Let \(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\). \\
+
+First, put the integers of \([\![1, ap + q]\!]\) in the following table (with \(a\) columns and \(p + 1\) lines) and divide it into 3 blocks (the columns are numbered from \(-l\) to \(+q\)):
+
+\begin{itemize}
+	\item \(\mathcal{T}\) (the "tail"): the integers from 1 to \(q\). NB: this is line number 0.
+	\item \(\mathcal{L}\) (the "lines"): the integers in columns \(-l\) to \(+r\) (excluding  \(\mathcal{T}\)).
+	\item \(\mathcal{C}\) (the "columns"): the integers in the last \(w\) columns (excluding  \(\mathcal{T}\)).
+\end{itemize}
+
+Note that with this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the sum of the columns modulo \(a\).
+
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
+\hline
+  & & & & & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} ...&\cellcolor{green}\(r\)&\(r+1\)&...&\(b - 1\)&\(b\) \\
+\hline
+   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
+\hline
+\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
+\hline
+...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
+\hline
+\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
+\hline
+...&...&...&...&...&...&...&...&...&...&...&...&...\\
+\hline
+\end{tabular}
+
+\underline{\textbf{\(\mathcal{T}\) block}} \\
+We color this block using the weakly sum-free colouring of \([\![1,q]\!]\) with colors \(1, ..., n\).
+
+\underline{\textbf{\(\mathcal{L}\) block}} \\
+In this block,  we use the colors \(n + 1, ..., n + k\). We colour an integer \(x\) according to its line number (written \(\lambda(x)\)).
+For every \(x \in \mathcal{L}\), we colour \(x\) with \(n + c\) where \(c\) is the colour of \(\lambda(x)\) in the sum-free colouring of  \([\![1,p]\!]\).
+Let \((x, y) \in \mathcal(L)^2\). The cases are twofold.
+
+\begin{itemize}
+	\item \underline{\(\lambda(x+y) = \lambda(x) + \lambda(y)\)} \\
+	In this case, we use the sum-free property of the colouring of \([\![1,p]\!]\) (in block \(\mathcal{C}\), we only use colours \(1, ..., n\)).
+
+	\item \underline{\(\lambda(x+y) \neq \lambda(x) + \lambda(y)\)} \\
+	In this case, we do not have information about the colour of \(\lambda(x+y)\). Thereby, we want to have \(x+y \in \mathcal{C}\).
+	A simple solution is to limit the horizontal movement, that is if the sum changes line, not to move too far so that it stays in \(\mathcal{C}\).
+	There, the maximal displacement to the left (resp. to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left
+	is then expressed as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written as
+	 \(\text{max}(l, r) \leqslant w\).
+\end{itemize}
+
+\underline{\textbf{\(\mathcal{C}\) block}} \\
+In this block,  we use colors \(1, ..., n\). We colour an integer \(x\) according to its column number (written \(\tilde{\pi}(x)\), it is linked to the
+projection on the first line, written \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\)). A simple solution is to colour \(x\) with the same colour
+as \(\tilde{\pi}(x)\) in the weakly sum-free colouring of \([\![1,q]\!]\). As long as \(2b \leqslant a + r\) (not going two far to the right) and there
+is no \(x \in \tilde{\pi}(\mathcal{C})\) such that \(2x \in \tilde{\pi}(\mathcal{C})\) (so that we do not have a sum in \(\mathcal{C}\) when
+taking two numbers in the same column), the colours \(1, ..., n\) are sum-free. \\
+
+In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem. \\
+
 \textsc{Proof :} Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\), \(N = p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q\),

### 2021-04-09 article/article.tex
corrections de légers problèmes

@@
 Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction
-to get explicit partitions improving lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
+to get explicit partitions improving lower bounds. We also developed a new method to improve weak Schur lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
 the principle that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding
-the previous lower bound \(WS(6) \geqslant 582\) is impossible with such a method upon imposing certain conditions on the good
+the previous lower bound \(WS(6) \geqslant 582\) is impossible with such an assumption upon imposing certain conditions on the good
 5-subsets partition. The new lower bounds includes \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
@@
 These new results come from Rowley's approach for Ramsey graphs which is relatively new. Therefore, it would not surprise us
-if lower bounds are later improved using better templates. Moreover, studying specifically \(S_+(n)\) and \(WS_+(n)\) numbers might be
+if lower bounds are later improved using better templates. Moreover, studying specifically \(S^+(n)\) and \(WS^+(n)\) numbers might be
 of interest as they are closely related to Schur and weak Schur numbers.
@@
 \par
-We would first like to address warm thanks to Fred Rowley who kindly answered our many questions and with who it was a pleasure
-to exchange. A great thank-you to Marijn Heule who also took the time to respond to our requests. Finally, last but not least, we would
-like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised us during the whole research and writing.
+We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised 
+us during the whole research and writing. Finally, last but not least, we would like to address warm thanks 
+to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange.
 

### 2021-04-09 article/weakschur.tex
tableau+modif pi
corrections de légers problèmes

@@
 \renewcommand{\arraystretch}{2}
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
-\hline
-  & & & & & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} ...&\cellcolor{green}\(r\)&\(r+1\)&...&\(b - 1\)&\(b\) \\
+\begin{center}
+\[
+\begin{array}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
+\cline{6-9}
+   \multicolumn{5}{c|}{} & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
 \hline
@@
 \hline
-\end{tabular}
+\end{array}
+\]
+\end{center}
 
@@
 
-We will now define notations and results, we will use in the following theorem.
+We will now define functions and results, that will be used in the following theorem.
 
-\begin{notation}
+\begin{definition}
 
 Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\pi_{a,b}\) the projection:
-\[ \pi_{a,b}:x->(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a}))\]
-\end{notation}
+\[ \pi_{a,b}:x \longmapsto (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a}))\]
+\end{definition}
 
@@
 
-\begin{notation}
+\begin{definition}
 
 Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\lambda_{a,b}\) the projection:
-\[ \lambda_{a,b}:x->1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
-\end{notation}
+\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
+\end{definition}
 
@@
 \begin{remark}
-In the following theorem, \(\lambda\) is the function which return the line number of an element x.
+In the following theorem, \(\lambda\) is the function which maps an element x to its line number.
 \end{remark}
@@
 \(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)
+
 \begin{definition}
@@
 \[
-(Id+(p-b)\mathbf{1}_{ [\![0,b]\!]})(x+y ~\text{mod}~ (p-b)) \notin A_i
+x+y>p \implies \pi(x+y) \notin A_i
 \]
@@
 
-\renewcommand{\arraystretch}{2}
-\begin{center}
-\[
-\begin{array}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
-\cline{6-9}
-   \multicolumn{5}{c|}{} & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
-\hline
-   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
-\hline
-\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
-\hline
-...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
-\hline
-\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
-\hline
-...&...&...&...&...&...&...&...&...&...&...&...&...\\
-\hline
-\end{array}
-\]
-\end{center}
 \textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\

### 2021-04-09 article/article.tex
premiere version (pas de relecture + mise en page)

@@
 
-This paper offers new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
+This paper provides new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
 Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction
-to get explicit partitions improving lower bounds. We also developed a new method to improve weak Schur lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
-the principle that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding
-the previous lower bound \(WS(6) \geqslant 582\) is impossible with such an assumption upon imposing certain conditions on the good
-5-subsets partition. The new lower bounds includes \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
+to get explicit partitions improving lower bounds as well as the growth rate of Schur numbers and Ramsey numbers \(R_n(3)\). 
+We also developed a new method to improve lower bounds on weak Schur numbers. Furthermore, this paper tries to analyze former 
+works on the subject based on the principle that good partitions into \(n+1\) subsets start with good partitions 
+into \(n\) subsets. We show that exceeding the previous lower bound \(WS(6) \geqslant 582\) is impossible with such an assumption upon 
+imposing certain conditions on the good 5-subsets partition. The new lower bounds includes \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), 
+\(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
 
@@
 \par
-These new results come from Rowley's approach for Ramsey graphs which is relatively new. Therefore, it would not surprise us
-if lower bounds are later improved using better templates. Moreover, studying specifically \(S^+(n)\) and \(WS^+(n)\) numbers might be
-of interest as they are closely related to Schur and weak Schur numbers.
+These new results come from an extension of Rowley's template-based approach for Ramsey graphs and Schur numbers which is relatively new. 
+Therefore, we would not be surprised if lower bounds are later improved using better templates. Moreover, studying specifically \(S^+(n)\) and 
+\(WS^+(n)\) might be of interest as they are closely related to Schur and weak Schur numbers.
 
 \par
-The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak Schur numbers. The principle behind it
-might have discarded many interesting partitions of the search space and lowered the highest value that can be reached within it.
-However, algorithms based on randomness such as Monte-Carlo algorithms may appear very useful if used in a search space with more
-potential. For example, such an algorithm could be used to find better templates and improve inequalities and lower bounds for high values
-of \(n\). This could be the subject fo a future work. Nevertheless, it would not help for the smallest values.
+The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak Schur numbers. The assumption behind it
+might have removed the optimal partitions from the search space and thus lowered the highest value that can be reached within it.
+However, algorithms based on randomness such as Monte-Carlo algorithms may prove to be very useful if used in a search space with more
+potential. For instance, such an algorithm could be used to find better templates and improve inequalities and lower bounds for high values
+of \(n\). This could be the subject of a future work.
 
@@
 We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised 
-us during the whole research and writing. Finally, last but not least, we would like to address warm thanks 
+us during the whole research and writing. Last but not least, we would like to address warm thanks 
 to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange.
@@
 \renewcommand{\arraystretch}{1}
+
 \section{SF-templates}
+
+\begin{center}
+SF-template partitionning \([\![1, 33]\!]\) into 4 subsets \\
+\begin{tabular}{|*{2}{c|}}
+	\hline
+	1 & 1, 6, 9, 13, 16, 20, 24, 27, 31 \\
+	\hline
+	2 & 2, 5, 14, 15, 25, 26 \\
+	\hline
+	3 & 3, 4, 10, 11, 12, 28, 29, 30 \\
+	\hline
+	4 & 7, 8, 17, 18, 19, 21, 22, 23, 32, 33 \\
+	\hline
+\end{tabular}
+\end{center}
+
 \begin{center}
@@
 \end{center}
+
 \begin{center}
@@
 \end{center}
+
 \section{WSF-templates}
+
 \begin{center}
@@
 	\hline
-	1 & 1, 2, 4, 8, 11, 22, 25, \textbf{(66)}\\
+	1 & 1, 2, 4, 8, 11, 22, 25, \(\mathbf{(N+1)}\)\\
 	\hline
@@
 \end{center}
-This template produces the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
-by placing 66 in the first subset.
+
+This template provides the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
+by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.
 

### 2021-04-09 article/intro.tex
Abstract comme il faut
Déplacement de l'abstract
premiere version (pas de relecture + mise en page)

--- 2021-04-08 article/intro.tex
@@
-\section{Abstract}
-
 \section{Introduction, context and notations}
@@
 property holds for weakly sum-free subsets (reference necessaire). These observations lead to the following definitions.
+
 \begin{definition}
-Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we note \(S(n)\) (\textit{resp. \(WS(n)\)}) such that
+Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we denote \(S(n)\) (\textit{resp. \(WS(n)\)}) such that
 \([\![1,S(n)]\!]\) (resp. \([\![1,WS(n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
@@
 \begin{notation}
-For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally note these subsets \(A_1, ..., A_n\). We also note
+For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We also denote
 \(m_i = \text{min}(A_i)\).
@@
 \end{notation}
+
+\begin{definition}
+We sometimes refer to a partitition as a colouring. The colouring associated to a partition \(A_1, ..., A_n\) of 
+\([\![1, p]\!]\) is the function \(f\) that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition associated to 
+a colouring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall i \in [\![1, n]\!], A_i = f^{-1}(i)\).
+\end{definition}

### 2021-04-09 article/sat.tex
nouvelle valeur de max m_5
valeurs + precision
explication intuitive + valuers
corrections de légers problèmes
premiere version (pas de relecture + mise en page)

@@
 \par
-Every weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets starts with the following sequence 1121222133. Then 11
-is always
+For every weakly sum-free colouring \(f\) of \([\![1,65]\!]\) with 4 colors, the sequence \(f(1), f(2), f(3), ...\) always 
+starts with the following subsequence 1121222133. Then 11 is always
 either in subset 1 or 3, 12 is always in subset 3 and so on. For every integer in \([\![1,65]\!]\), we computed in which
@@
 our knowledge every paper
-that found the lower bound \(WS(5) \geqslant 196\) used this assumption [reference necessaire]. Therefore one may wonder
+that found the lower bound \(WS(5) \geqslant 196\) used this assumption. Therefore one may wonder
 if this actually a good lower
@@
 this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation
-time. We also give the stronger
-following result.
+time. We also give the stronger following result.
 
 \begin{computational theorem}
-If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). \\
-NB : on doit finir d'obtenir les valeurs.
+If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). NB : on doit finir d'obtenir les valeurs.
 \end{computational theorem}
@@
 	\hline
-\(max~m_5\) & & & & & & & & & & & & & & & & & & & & & 53 \\
+	\(max~m_5\) & 49 & 51 & 54 & 53 & 54 & 54 & & & & & & & & & & & & 59 & 61 & 58 & 53 \\
 	\hline
@@
 
-To obtain these results, we once again provided additionnal information to the SAT solver. We also gave other types of
-information to the SAT solver.
-(pas encore fini)
+In the above table, we only made real efforts (trying different additionnal information) for \(m_4 = 24\). In this case, the value \(m_5 \leqslant 53\) 
+was obtained after 7 hours of runtime.
+To obtain these results, we once again provided additionnal information to the SAT solver. We added two different types information. 
+The first one is the same above. The second one is maximum length of a sequence using only a certain subset of the colors. For instance, 
+if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3. \\

### 2021-04-09 article/schur.tex
corrections de légers problèmes
premiere version (pas de relecture + mise en page)

@@
 
-\qquad In this section, we use Rowley's constructions \cite{RowleyRamsey} in a Schur context. To improve lower bounds
-for Ramsay's
-numbers, Rowley
-introduces partitions verifying some properties which can be extended using a method which generalizes Abbott-Hanson's
-\cite{AbbottHanson} construction.
-Rowley named these partitions "templates", and we will keep this name in the entire article. We find suitable templates
-and use them
- to find new lower bounds for Schur numbers.
+\qquad In this section, we use Rowley's constructions \cite{RowleyRamsey} in the context of Schur numbers. To improve lower bounds
+for Ramsay's numbers, Rowley introduces partitions verifying some properties which can be extended using a method which generalizes 
+Abbott and Hanson's  construction \cite{AbbottHanson}. Rowley named these partitions "templates", and we will keep this name in the 
+entire article. We find suitable templates and use them to find new lower bounds for Schur numbers.
 
-\subsection{Definition of S\(_+\)}
+\subsection{Definition of \(S^+\)}
 
@@
 \begin{remark}
-	SF-templates include Abott and Hanson's construction [reference necessaire] as a special case.
+	Here, \(n\) is the "special" color: it has less constraints than the other colors. However, please note that \(n\) 
+	is not necessarily the last color by order of appearance.
+\end{remark}
+
+\begin{remark}
+	\(SF\)-templates include Abott and Hanson's construction \cite{AbbottHanson} as a special case.
 \end{remark}
@@
 acts like a security zone for the other one. Here, the horizontal partition is no longer to the side of the 
-vertical one, but occupies the column of the special color of the \(SF\)-template, i.e the one without the 
-extra condition. We give the following table for \(p = 7, q = 4, n = 2 ~\textrm{and}~ k = 2\) to make the intuition clear. \\
+vertical one, but it occupies the column of the special color of the \(SF\)-template, i.e the one without the 
+extra condition. We give the following example for \(p = 7, q = 4, n = 2 ~\textrm{and}~ k = 2\). \\
 
@@
 
-\textsc{Proof :} We denote by \(f\) the projection of the equivalence relation induced by the \(SF\)-template of lenght
-\(p\)
-and \(g\) the one induced by the sum-free partition of \([\![1,q]\!]\). Each equivalence class is represented by a
-single integer, therefore :
+\textsc{Proof :} We denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\)
+and \(g\) the one associated to the sum-free partition of \([\![1,q]\!]\).
 
@@
 
-Using a SAT solvers, we are able to exhibit SF-template, hence providing lower bound on \(S^+\). 
-We seek templates providing the best lower bound possible, but also the best additive constant (\(m_{k+1}\) with the previous notation). 
-Further details can be found in the\hyperref[SAT]{SAT section}. \\
+\begin{definition}
+A SF-template with \(n\) colors is said to be symmetric if the partition in \(n\) sum-free subsets derived (with the additive constant) from this template is symmetric. 
+A sum-free partition \(A_1, ..., A_n\) of \([\![1, p]\!]\) is said to be symmetric if for all \( x \in [\![1, p]\!]\), \(x\) and \(p + 1 - x\) belong to the same subset 
+(except if \(x = p + 1 - x\)).
+\end{definition}
 
-Here are the best inequalities on Schur numbers so far :
+Using a SAT solver, we exhibited SF-templates, hence providing lower bound on \(S^+\) and inequalities 
+of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
+\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5, we looked for symmetric SF-templates, 
+we assumed that the special color was the last color to appear and we constrained the \(m_c\)'s out of being too small.
+
+Here are the best inequalities on Schur numbers so far (the templates corresponding to the third, fourth and fifth 
+inequalities can be found in the appendix):
 \[ S(n+1) \geqslant 3S(n) + 1 \]
@@
 and the third one to Rowley \cite{RowleyRamsey}. The other ones are new. \\
+
+The first 3 inequalities are optimal. The fourth one is optimal among symmetric SF-templates whose special color is 
+the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
+likely not optimal but should not be too far from the optimal SF-template. 
+Finally, the sixth one is obtained by combining (see below) the SF-template of length 380 and the one of length 3. Although we 
+could not find a better SF-template with 7 colors, this one definetely very far from the optimal value. One may try to seek better 
+templates by constraining less the search space and by using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. 
+This could be the suject of a future work.\\
 
@@
 \begin{corollary}
-The growth rate for Schur (and Ramsey) numbers satisfies \(\gamma \geqslant \sqrt[5]{380} \approx 3.28 \).
+The growth rate for Schur numbers (and Ramsey numbers \(R_n(3)\))  satisfies \(\gamma \geqslant \sqrt[5]{380} \approx 3.28 \).
 \end{corollary}

### 2021-04-09 article/weakschur.tex
premiere version (pas de relecture + mise en page)

@@
 \begin{remark}
+This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers.
+\end{remark}
+
+\begin{remark}
 In the above ineqality, a "\(+1\)" can be added to the lower bound if \(WS(n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less
@@
 
-Note that with this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the sum of the columns modulo \(a\).
+Like for SF-templates, \(\mathcal{L}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with 
+this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the 
+sum of the columns modulo \(a\).
 
@@
 \cline{6-9}
-   \multicolumn{5}{c|}{} & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
+   \multicolumn{5}{c|}{} & \cellcolor{green} 1 & \cellcolor{green} 2 & \cellcolor{blue} ... &\cellcolor{green} r & r + 1 & ... & b - 1 &  b \\
 \hline
-   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
+   \cellcolor{red} a - l & \cellcolor{red} a- l + 1 & \cellcolor{red} ...
+& \cellcolor{red} a - 1 & \cellcolor{red} a & \cellcolor{red} a + 1 & \cellcolor{red} ...
+&\cellcolor{red} a + r - 1 & \cellcolor{red} a + r & a + r + 1 & ...
+& a + b - 1 & a+ b \\
 \hline
-\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
+\cellcolor{yellow} 2 a - l &\cellcolor{yellow}...&\cellcolor{yellow}...&\cellcolor{yellow}...&\cellcolor{yellow} 2 a &\cellcolor{yellow} ...
+&\cellcolor{yellow} ...
+&\cellcolor{yellow} ...
+&\cellcolor{yellow} 2 a + r & ...
+& ...
+& ...
+& 2 a + b \\
 \hline
@@
 \hline
-...&...&...&...&...&...&...&...&...&...&...&...&...\\
+p a - l & ... & ... & ... &p a & ... & ... & .... & p a + r & ... & ... & ... & p a + b\\
 \hline
@@
 \(\alpha = \left \lceil \frac{q}{2} \right \rceil > 0\) and \(\beta = q + \alpha + 1\).
-We denote by \(f\) the projection of the equivalence relation induced by the partition of \([\![1,q]\!]\) and \(g\) the
-one induced by the partition of \([\![1,p]\!]\). Each equivalence class is represented by a single integer, therefore :
+We denote by \(f\) the colouring associated to the partition of \([\![1,q]\!]\) and \(g\) the
+one associated to the partition of \([\![1,p]\!]\).
 \[ f : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2, \left\{
@@
 
+\begin{remark}
+\(\pi\) is the projection on the first line mentioned in the intuitive explanation.
+\end{remark}
+
 \begin{proposition}
@@
 \begin{remark}
-In the following theorem, \(\lambda\) is the function which maps an element x to its line number.
+In the following theorem, \(\lambda\) is the function which maps an element x to its line number, as mentioned in the intuitive explanation.
 \end{remark}
@@
 \begin{definition}
-Let \( (p,k,b) \in (\mathbb{N}^*)^3\), Let \((A_1,....,A_k)\) a partition of  \([\![1, p]\!]\).
-This partition is said to be a b-weakly-sum-free template (b-WSF-template) of \(k\) colors and lenght \(p\) when:
+Let \( (p,n,b) \in (\mathbb{N}^*)^3\), Let \((A_1,...,A_n)\) a partition of  \([\![1, p]\!]\).
+This partition is said to be a b-weakly-sum-free template (b-WSF-template) of \(n\) colors and lenght \(p\) when:
 \\\\
-\underline{\(\forall i \in [\![1, k]\!], \quad A_i\) is weakly-sum-free}
+\underline{\(\forall i \in [\![1, n]\!], \quad A_i\) is weakly-sum-free}
 \\\\
-\underline{\(\forall i \in [\![1, k]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
+\underline{\(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
 \\\\
-\underline{For \(A_k\) (the special subset):} \quad \(\forall (x,y) \in A_k^2,\)
+\underline{For \(A_n\) (the special subset):} \quad \(\forall (x,y) \in A_n^2,\)
 \\
-\[if \quad x+y>b+2(p-b),\quad x+y-2(p-b)\notin A_k\]
+\[if \quad x+y>b+2(p-b),\quad x+y-2(p-b)\notin A_n\]
 \\
-\underline{For the others subsets:}\quad \(\forall i \in [\![0,k-1]\!], \forall(x,y) \in A_i^2\)
+\underline{For the others subsets:}\quad \(\forall i \in [\![0,n-1]\!], \forall(x,y) \in A_i^2,\)
 \\
@@
 \end{definition}
+
+\begin{remark}
+	Please note that the special color \(n\) is not necessarily the last color by order of appearance.
+\end{remark}
 
@@
 \textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
-We denote by \(g\) the projection of the equivalence relation induced by the partition of \([\![1,q]\!]\) and \(h\) the
-one induced by the partition of \([\![1,p]\!]\). Each equivalence class is represented by a single integer, therefore :
+We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
+one associated to the partition of \([\![1,p]\!]\).
 \[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
@@
 
-Let \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such as:
+Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such that:
 \\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
@@
 
+\begin{corollary}
+The general lower bound for weak Schur numbers in function of both regular and weak Schur numbers can be seen as a particular 
+case of WSF-template in the same way Abott and Hanson's construction can be seen as a particular case of SF-template.
+\end{corollary}
+
 \subsection{New lower bounds for Weak Schur numbers}
@@
 \mathbb{N}^*\):
+
 \[
@@
 \]
-The first two inequalities are due to Rowley, they are detailed in [2]. Like in 3.3, we compute the lower bounds given
-by the previous inequalities for \( n \in [\![8,15]\!] \). The best lower bound for each integer is highlighted.\\
+
+The first two inequalities were found by Rowley, they are detailed in [2]. The third inequality is optimal and was found with a SAT solver. 
+As for the fourth inequality, it is not useful since by comibing the first inequality with \(S(n) \geqslant 33 S(n-3) + 6\) provides a 
+better inequality. It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of 
+5 colors which start with a good \(WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates 
+as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates 
+with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. 
+This could be the suject of a future work.
+
+Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \). The best lower bound 
+for each integer is highlighted.\\
 \\
@@
 
-With \( S(9) \geqslant 17803 \), we found a new lower bound for
-\(WS(10)\) using Rowley's inequality. Moreover, the third inequality
-gives new lower bounds for \(WS(9)\) and \(WS(14)\). However, the last
-inequality doesn't give any better lower bound, even beyond \( n = 15 \)
-: the best bounds are always provided by the first three. We highly suspect that these values can be improved by
-investigating the search
-space further, which would provide new, more effective templates. One
-may try to go over this search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP},
-but with a different search space (as we explain in \hyperref[SAT]{SAT section}).
-This could be the suject of a future work.
+With \( S(9) \geqslant 17803 \), we found a new lower bound for \(WS(10)\) using Rowley's inequality. 
+Moreover, the third inequality gives new lower bounds for \(WS(9)\) and \(WS(14)\).

### 2021-04-09 article/schur.tex
petit oubli

@@
 of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
-\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5, we looked for symmetric SF-templates, 
-we assumed that the special color was the last color to appear and we constrained the \(m_c\)'s out of being too small.
+\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5,in order to reduce the search space we 
+looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
+the \(m_c\)'s out of being too small. Further details about the encoding as a SAT problem can be found in the
+\hyperref[SAT]{SAT section}. \\
 

### 2021-04-11 article/sat.tex
ajout des valeurs

@@
 this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation
-time. We also give the stronger following result.
+time. Since \(WS(4) = 66\), we have \(m_5 \leqslant 67\). We give the stronger following result.
 
 \begin{computational theorem}
-If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). NB : on doit finir d'obtenir les valeurs.
+If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leqslant 59\).
 \end{computational theorem}
@@
 
-\begin{tabular}{| c | *{21}{ p{2mm} |}}
+\renewcommand{\arraystretch}{1.5}
+\setlength{\tabcolsep}{3pt}
+
+\begin{center}
+\begin{tabular}{| c | *{21}{c |}}
 	\hline
@@
 	\hline
-	\(max~m_5\) & 49 & 51 & 54 & 53 & 54 & 54 & & & & & & & & & & & & 59 & 61 & 58 & 53 \\
+	\(max~m_5\) & 49 & 51 & 54 & 53 & 54 & 54 & 55 & 55 & 55 & 55 & 55 & 56 & 57 & 57 & 59 & 59 & 59 & 59 & 59 & 58 & 53 \\
 	\hline
 \end{tabular}
+\end{center}
 
-In the above table, we only made real efforts (trying different additionnal information) for \(m_4 = 24\). In this case, the value \(m_5 \leqslant 53\) 
-was obtained after 7 hours of runtime.
+For \(m_4 = 24\), the value \(m_5 \leqslant 53\) was obtained after 7 hours of runtime, and for  \(m_4 = 22\), the 
+value \(m_5 \leqslant 59\) was obtained after 11 hours of runtime. All the other values took between 1 minutes and 2 hours.
 To obtain these results, we once again provided additionnal information to the SAT solver. We added two different types information. 
-The first one is the same above. The second one is maximum length of a sequence using only a certain subset of the colors. For instance, 
+The first one is the same as previously: we compute the subsets in which the first numbers can appear. The second type of 
+information is the maximum length of a sequence using only a certain subset of the colors. For instance, 
 if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3. \\

### 2021-04-12 weak_schur_sat/bound_m5/find_pos.py
borne sup m_5

@@ -1,0 +1,112 @@
+import subprocess
+import sys
+import tqdm
+
+
+def is_solution(answer):
+    for line in answer.splitlines():
+        if line[0] != 's':
+            continue
+        return line[2] == 'S'
+    print(answer)
+    raise RuntimeError
+
+
+def weakly_sum_free(k, n):
+    cnf = []
+    for c in range(k):
+        for i in range(1, n + 1):
+            for j in range(i + 1, n + 1):
+                tot = i + j
+                if tot > n:
+                    break
+                no_sum = f"-{i * k - c} -{j * k - c} -{tot * k - c}"
+                cnf.append(no_sum)
+    return cnf
+
+
+def use_all(k, n):
+    cnf = []
+    for i in range(n):
+        use_i = " ".join(map(str, range(k * i + 1, k * (i + 1) + 1)))
+        cnf.append(use_i)
+    return cnf
+
+
+def disjoint(k, n):
+    cnf = []
+    for i in range(1, n + 1):
+        for c1 in range(k):
+            for c2 in range(c1 + 1, k):
+                cnf.append(f"-{k * i - c1} -{k * i - c2}")
+    return cnf
+
+
+def break_symmetries(k):
+    cnf = ["1"]
+    if k >= 3:
+        cnf.append(f"-{k + 3}")
+        cnf.append(f"{k + 2} -{2 * k + 3}")
+    if k >= 4:
+        clause= ""
+        for i in range(2, 9):
+            cnf.append(clause + f"-{k * i + 4}")
+            clause += f"{k * i + 3} "
+    if k >= 5:
+        clause= ""
+        for i in range(2, 24):
+            cnf.append(clause + f"-{k * i + 5}")
+            clause += f"{k * i + 4} "
+    if k >= 6:
+        clause= ""
+        for i in range(2, 67):
+            cnf.append(clause + f"-{k * i + 6}")
+            clause += f"{k * i + 5} "
+    return cnf
+
+
+def search_space(k, n, i, c_i, m_4):
+    cnf = [f"{k * (i - 1) + c_i}"]
+    for j in range(1, m_4):
+        cnf.append(f"-{k * (j - 1) + 4}")
+    cnf.append(f"{k * (m_4 - 1) + 4}")
+    return cnf
+
+
+def weak_schur_cnf(k, n, i, c_i, m_4):
+    cnf = weakly_sum_free(k, n)
[…]

### 2021-04-12 weak_schur_sat/bound_m5/m5_m4.py

@@ -1,0 +1,121 @@
+from sys import argv
+
+
+def get_max_len(m_4):
+    if m_4 >= 22:
+        return 17
+    if m_4 >= 10:
+        return 18
+    if m_4 == 9:
+        return 21
+    return None
+
+
+def load_pos(k, file):
+    cnf = []
+    with open(file) as f:
+        for i, line in enumerate(f.readlines()):
+            clause = ""
+            for c in map(int, line.strip().split()):
+                clause += f"{k * i + c} "
+            cnf.append(clause[:-1])
+    return cnf
+
+
+def sum_free(k, n):
+    cnf = []
+    for c in range(k):
+        for i in range(1, n + 1):
+            for j in range(i + 1, n + 1):
+                tot = i + j
+                if tot > n:
+                    break
+                no_sum = f"-{i * k - c} -{j * k - c} -{tot * k - c}"
+                cnf.append(no_sum)
+    return cnf
+
+
+def use_all(k, n):
+    cnf = []
+    for i in range(n):
+        use_i = " ".join(map(str, range(k * i + 1, k * (i + 1) + 1)))
+        cnf.append(use_i)
+    return cnf
+
+
+def disjoint(k, n):
+    cnf = []
+    for i in range(1, n + 1):
+        for c1 in range(k):
+            for c2 in range(c1 + 1, k):
+                cnf.append(f"-{k * i - c1} -{k * i - c2}")
+    return cnf
+
+
+def break_symmetries(k):
+    cnf = ["1"]
+    if k >= 3:
+        cnf.append(f"-{k + 3}")
+        cnf.append(f"{k + 2} -{2 * k + 3}")
+    if k >= 4:
+        clause= ""
+        for i in range(1, 9):
+            cnf.append(clause + f"-{k * i + 4}")
+            clause += f"{k * i + 3} "
+    if k >= 5:
+        clause= ""
+        for i in range(1, 24):
+            cnf.append(clause + f"-{k * i + 5}")
+            clause += f"{k * i + 4} "
+    if k >= 6:
+        clause= ""
+        for i in range(1, 67):
+            cnf.append(clause + f"-{k * i + 6}")
+            clause += f"{k * i + 5} "
+    return cnf
+
+
+def search_space(n, m_4, lim):
+    try:
+        cnf = load_pos(5, "sghts")
[…]

### 2021-04-12 weak_schur_sat/bound_m5/max_len.py

@@ -1,0 +1,90 @@
+from sys import argv
+
+
+def max_len(k, n, d):
+    cnf = []
+    for c in range(k):
+        for i in range(1, d + 1):
+            for j in range(d + 1, n + d + 1):
+                tot = i + j
+                if tot > n + d:
+                    break
+                no_sum = f"-{i * k - c} -{j * k - c} -{tot * k - c}"
+                cnf.append(no_sum)
+    return cnf
+
+
+def weakly_sum_free(k, n):
+    cnf = []
+    for c in range(k):
+        for i in range(1, n + 1):
+            for j in range(i + 1, n + 1):
+                tot = i + j
+                if tot > n:
+                    break
+                no_sum = f"-{i * k - c} -{j * k - c} -{tot * k - c}"
+                cnf.append(no_sum)
+    return cnf
+
+
+def use_all(k, n):
+    cnf = []
+    for i in range(n):
+        use_i = " ".join(map(str, range(k * i + 1, k * (i + 1) + 1)))
+        cnf.append(use_i)
+    return cnf
+
+
+def disjoint(k, n):
+    cnf = []
+    for i in range(1, n + 1):
+        for c1 in range(k):
+            for c2 in range(c1 + 1, k):
+                cnf.append(f"-{k * i - c1} -{k * i - c2}")
+    return cnf
+
+
+def break_symmetries(k):
+    cnf = ["1"]
+    if k >= 3:
+        cnf.append(f"-{k + 3}")
+        cnf.append(f"{k + 2} -{2 * k + 3}")
+    if k >= 4:
+        clause= ""
+        for i in range(2, 9):
+            cnf.append(clause + f"-{k * i + 4}")
+            clause += f"{k * i + 3} "
+    if k >= 5:
+        clause= ""
+        for i in range(2, 24):
+            cnf.append(clause + f"-{k * i + 5}")
+            clause += f"{k * i + 4} "
+    if k >= 6:
+        clause= ""
+        for i in range(2, 67):
+            cnf.append(clause + f"-{k * i + 6}")
+            clause += f"{k * i + 5} "
+    return cnf
+
+
+def weak_schur_cnf(k, n, d):
+    cnf = []
+    cnf.extend(weakly_sum_free(k, d))
+    cnf.extend(use_all(k, n + d))
+    cnf.extend(disjoint(k, n + d))
[…]

### 2021-04-12 article/article.tex
rafinements + prop WS^+

@@
 Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction
-to get explicit partitions improving lower bounds as well as the growth rate of Schur numbers and Ramsey numbers \(R_n(3)\). 
+to get explicit partitions improving lower bounds as well as the growth rate of both Schur numbers and Ramsey numbers \(R_n(3)\). 
 We also developed a new method to improve lower bounds on weak Schur numbers. Furthermore, this paper tries to analyze former 

### 2021-04-12 article/schur.tex
rafinements + prop WS^+

@@
 
-The idea lying beneath this inequality is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. 
+\begin{remark}
+The following proposition can help improve the additive constant of a SF-template. Although it does not allow us to improve the SF-templates 
+we have found, the analogous of this proposition for WSF-templates (see next section) allows to improve one of them.
+\end{remark}
+
+\begin{proposition}
+Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a colouring associated to a SF-template of length \(p\) with \(k\) colors. Let 
+\(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a colouring \(g\) of \([\![1, b]\!]\) with \(k\) colors such that:
+\begin{itemize}
+	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in [\![1, p]\!]^2,(f(x) = f(y) \text{ and } (x + y) \mod p \leqslant b) 
+	\implies g((x + y) \mod p) \neq f(x)\)
+	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in [\![1, p]\!] \times  [\![1, b]\!], (f(x) = g(y) \text{ and } x + y \leqslant b) 
+	\implies g(x + y) \neq f(x)\)
+\end{itemize}
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n))\), we have\\
+\[ S(n+k) \geqslant S^+(k+1)S(n) + b\]
+\end{proposition}
+
+\begin{remark}
+This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
+column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
+intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the colouring of the last 
+row can be weakened.
+\end{remark}
+
+The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. 
 They extend vertically a sum-free partition, and horizontally an other sum-free partition. This way each "block" 
@@
 
-\textsc{Proof :} We denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\)
+\textsc{Proof of theorem:} We denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\)
 and \(g\) the one associated to the sum-free partition of \([\![1,q]\!]\).
@@
 of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
-\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5,in order to reduce the search space we 
+\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5, in order to reduce the search space we 
 looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
@@
 likely not optimal but should not be too far from the optimal SF-template. 
-Finally, the sixth one is obtained by combining (see below) the SF-template of length 380 and the one of length 3. Although we 
-could not find a better SF-template with 7 colors, this one definetely very far from the optimal value. One may try to seek better 
-templates by constraining less the search space and by using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. 
-This could be the suject of a future work.\\
+Finally, the sixth one is obtained by combining (see below) the SF-template of length 380 and the one of length 3. 
+Although we could not find a better SF-template with 7 colors, the last inequality is definetely very far from the 
+optimal value. One may try to seek better templates by constraining less the search space and by using 
+Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.\\
 

### 2021-04-12 article/weakschur.tex
petit oubli
rafinements + prop WS^+

@@
 	\item \(\mathcal{T}\) (the "tail"): the integers from 1 to \(q\). NB: this is line number 0.
-	\item \(\mathcal{L}\) (the "lines"): the integers in columns \(-l\) to \(+r\) (excluding  \(\mathcal{T}\)).
+	\item \(\mathcal{R}\) (the "rows"): the integers in columns \(-l\) to \(+r\) (excluding  \(\mathcal{T}\)).
 	\item \(\mathcal{C}\) (the "columns"): the integers in the last \(w\) columns (excluding  \(\mathcal{T}\)).
@@
 
-Like for SF-templates, \(\mathcal{L}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with 
+Like for SF-templates, \(\mathcal{R}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with 
 this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the 
@@
 
-\underline{\textbf{\(\mathcal{L}\) block}} \\
+\underline{\textbf{\(\mathcal{R}\) block}} \\
 In this block,  we use the colors \(n + 1, ..., n + k\). We colour an integer \(x\) according to its line number (written \(\lambda(x)\)).
-For every \(x \in \mathcal{L}\), we colour \(x\) with \(n + c\) where \(c\) is the colour of \(\lambda(x)\) in the sum-free colouring of  \([\![1,p]\!]\).
-Let \((x, y) \in \mathcal(L)^2\). The cases are twofold.
+For every \(x \in \mathcal{R}\), we colour \(x\) with \(n + c\) where \(c\) is the colour of \(\lambda(x)\) in the sum-free colouring of  \([\![1,p]\!]\).
+Let \((x, y) \in \mathcal{R}^2\). The cases are twofold.
 
@@
 this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
-3.1)},we will define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
+3.1)},we define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
 \end{remark}
@@
 
-We will now define functions and results, that will be used in the following theorem.
+In this subsection, we define the objects and proove the results needed for the general theorem regarding templates for 
+weak Schur numbers.
 
@@
 
+\begin{proposition}
+	Let \(n \in [\![2, +\infty]\!]\), we have :
+	\[
+	\frac{3}{2}WS(n-1)+1 \leqslant WS^+(n) \leqslant WS(n)
+	\]
+\end{proposition}
+
+\textsc{Proof :} The lower bound comes from the analogous of Abott and Hanson's construction for weak Schur numbers. 
+The upper bound comes from the fact that a WSF-template of length \(p\) with \(n\) colors is also a partition of
+\([\![1, p]\!]\) into \(n\) sum-free subsets.
+
+\begin{remark}
+	\(WS^+\) and \(WS\) have the same asymptotic growth rate.
+\end{remark}
+
 \subsection{Lower bound for Weak schur numbers using Schur and Weak Schur template numbers}
@@
 \begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(n+1)=WS_b^+(n+1)\},\) \[
+\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/ WS_b^+(n+1) = WS^+(n+1)\},\) \[
 WS(n+k) \geqslant S(k) WS^+(n+1)+b_{max}\]
 \end{corollary}
+
+\begin{remark}
+In the SF-template construction for Schur numbers, the additive constant comes from the fact that the special color does 
+not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_max\) can actually be replaced by \\
+\[\max \left\{ b + \min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ WS_b^+(n+1) = WS^+(n+1) \right\}\]
+\end{remark}
+
+\begin{remark}
+Acutally, like for SF-templates, the additive constant of a WSF-template (in the form given by the above remark) can be improved 
+by weakening the hypotheses made on the last row. The principle behind it is the same as in the analogous proposition for SF-templates.
+\end{remark}
+
+\begin{proposition}
+Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a b-WSF-template of length \(p\) with \(k\) colors. Let 
+\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of 
+\([\![b + 1, b + c]\!]\) with \(k\) colors such that:
+\begin{itemize}
+	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c) 
+	\implies g(\pi(x + y)) \neq f(x)\)
+	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c) 
+\implies g(\pi(x + y)) \neq f(x)\)
+\end{itemize}
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
+\[ WS(n+k) \geqslant WS^+(k+1) S(n) + b + c\]
+\end{proposition}
 
@@
 
-\begin{remark}
-There exists a \(c(b) \geqslant \text{min}(A_{k+1} \backslash [\![1,b] - b - 1\) such that \(c(b)\) numbers can be
-added at the end of the extended partition.Therefore, we can get a better lower bound by finding a couple \((b,c(b))\)
-which maximizes the sum \(b+c(b)\) such that \(WS^+(k+1)=WS_b^+(k+1)\). Hence we have:
-	\[ WS(n+k) \geqslant S(n) WS^+(k+1)+b+c(b)\]
-
-\end{remark}
-
 \begin{corollary}
@@
 \end{corollary}
+
+\begin{remark}
+The WSF-templates can actually be fine-tuned further. However, it gives only minor improvements (most likely only additive 
+constant) at the cost of dramatically increasing the size of the search space while. Therefore, it does not seem relevant to 
+use this sophistications given that we could not even find good WSF-templates with 5 colors using a computer (here good 
+means better than those obtain by combining smaller templates).
+
+\par These modifications work as follows. One may notice that the first row (excluding the "tail") has constraints that other rows 
+do not have because of the tail, especially if the special color appears in the tail as well. Thus allowing to have a colouring on the 
+first row different from the colouring of the other rows would weaken the constraints. Acutally, one may even go further by 
+noticing that on the one hand the first (ordered) color of the sum-free partition used for the extension procedure has more 
+more constraints than the other colors of the sum-free partition since the first row is of this color and is more constrained than 
+the other rows, but that on the other hand it has more degrees of freedom than the other colors of the sum-free partition since in 
+the sum-free partition there cannot be two consecutive numbers of this color. As a result, it removes  some constraints imposed
+ by the first row on the other rows.
+
+\par To sum up, one can look for a generalised WSF-template that uses a special colouring for the tail and the first row, a 
+colouring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a colouring for all 
+the other rows and a special colouring for the last numbers (as previously explained for the improvement of the additive 
+constant of WSF-templates).
+\end{remark}
+
+We also have a similar theorem where only \(WS^+\) is involved.
+
+\begin{theorem}
+	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template of \(k+1\) colors and lenght \(p\),
+	and \(WSF\)-template of \(n\) color and lenght \(q\), then there exists \(WSF\)-template of \((n+k)\) and lenght \(pq\).
+\end{theorem}
+
+And the associated inequality :
+
+\begin{corollary}
+	Let \(n, k \in \mathbb{N}^*\), we have \\
+	\[ WS^+(n+k) \geqslant S^+(k+1)WS^+(n) \]
+\end{corollary}
+
+\textsc{Proof :} The idea is the same as in the previous theorem. The only difference is the \(SF\) property inherited 
+from the second \(SF\)-template.
 
@@
 \[
-127S(n) + 68 \leqslant WS(n+4)
+132S(n) + 26 \leqslant WS(n+4)
 \]
@@
 The first two inequalities were found by Rowley, they are detailed in [2]. The third inequality is optimal and was found with a SAT solver. 
-As for the fourth inequality, it is not useful since by comibing the first inequality with \(S(n) \geqslant 33 S(n-3) + 6\) provides a 
-better inequality. It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of 
+It uses the first sophistication explained in the previous subsection in order to add the last number in the first color.  
+As for the fourth inequality, it was obtained by combining an optimal SF-template of length 33 with a WSF-template of length 4. 
+The best template we could get with a computer search gives the inequality \(WS(n+4) \geqslant 127 S(n) + 68\). 
+It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of 
 5 colors which start with a good \(WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates 
@@
 with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. 
-This could be the suject of a future work.
+This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in the
+\hyperref[SAT]{SAT section}. \\
 

### 2021-04-13 article/schur.tex
anglais

@@
 \qquad In this section, we use Rowley's constructions \cite{RowleyRamsey} in the context of Schur numbers. To improve lower bounds
-for Ramsay's numbers, Rowley introduces partitions verifying some properties which can be extended using a method which generalizes 
-Abbott and Hanson's  construction \cite{AbbottHanson}. Rowley named these partitions "templates", and we will keep this name in the 
-entire article. We find suitable templates and use them to find new lower bounds for Schur numbers.
+for Ramsay's numbers, Rowley introduces some sum-free partitions verifying some additional properties which can be extended using a 
+method which generalizes Abbott and Hanson's  construction \cite{AbbottHanson}. Rowley named these partitions "templates", and 
+we will keep this name in the entire article. We find suitable templates and use them to find new lower bounds for Schur numbers.
 
@@
 \begin{proposition}
-	Let \(n \in [\![2, +\infty]\!]\), we have :
+	Let \(n \in [\![2, +\infty]\!]\). Then
 	\[
@@
 	and a partition of \(n\) sum-free subsets of \([\![1,q]\!]\) then there exists a partition of \(n+k\) sum-free subsets
-	of \([\![1,pq+m_{k+1}-1]\!]\). \(m_{k+1}\) is the first number colored with the \(k+1\)-th color in the \(SF\)-template.
+	of \([\![1,pq+m_{k+1}-1]\!]\). \(m_{k+1}\) is the minimum of the special subset in the \(SF\)-template.
 \end{theorem}
@@
 \begin{corollary}
-	Let \(n, k \in \mathbb{N}^*\), we have \\
+	Let \(n, k \in \mathbb{N}^*\). Then
 	\[ S(n+k) \geqslant S^+(k+1)S(n) + m_{k+1} - 1 \]
@@
 The following proposition can help improve the additive constant of a SF-template. Although it does not allow us to improve the SF-templates 
-we have found, the analogous of this proposition for WSF-templates (see next section) allows to improve one of them.
+we have found, the analogous of this proposition for WSF-templates (see next section) allows us to improve one of them.
 \end{remark}
@@
 vertical one, but it occupies the column of the special color of the \(SF\)-template, i.e the one without the 
-extra condition. We give the following example for \(p = 7, q = 4, n = 2 ~\textrm{and}~ k = 2\). \\
+extra condition. We give the following example for \(p = 9, q = 4, n = 2 ~\textrm{and}~ k = 2\). \\
 
 This shows the inequality \(S(2+2) \geqslant S^+(3)S(2) + 4\). The special color is blue and is first used
-to color 5, hence \(4 = m_{3} - 1\). 
-We prooved \(S^+(3) = 9\). The special color is blue.
+to color 5, hence \(4 = m_{3} - 1\). The special color is blue.
 
@@
 
-To compare, here is a classic Abbott and Hanson partition : \(S(2+2) \geqslant S(2)(2S(2)+1)+S(2) \). 
+To comparison, here is an usual Abbott and Hanson partition : \(S(2+2) \geqslant S(2)(2S(2)+1)+S(2) \). 
 \begin{center}

### 2021-04-14 article/appendix.tex
modification organisation generale

--- 2021-04-09 article/weakschur.tex
@@
-\section{Weak Schur numbers}
+\appendix
+\renewcommand{\arraystretch}{1}
 
-In this section, we generalize Rowley's constructions in \cite{RowleyWS}. We then introduce, by analogy with the third
-section, the
-integer \(WS^+(n)\)
-to build suitable templates.
+\section{SF-templates}
 
-\subsection{Lower bound for Weak Schur numbers using Schur and Weak Schur numbers}
-
-Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction \cite{AbbottHanson}. Here
-we
-give a general lower bound for weak Schur numbers as a function of both regular and weak Schur numbers.
-The following theorem, inspired by Rowley's inequalities for \(WS(n+1)\) and \(WS(n+2)\), was found and proved
-by Romain Ageron.
-
-\begin{theorem}
-Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
-subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free
-subsets then there exists a partition of \([\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]\) into \(n+k\)
-weakly sum-free subsets.
-\end{theorem}
-
-In particular, if we choose \(q = WS(n)\) and \(p = S(k)\) in the last theorem, the next corollary follows.
-
-\begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } WS(n+k) \geqslant S(k) \left (WS(n) + \left \lceil \frac{WS(n)}{2}
-\right \rceil +1 \right) + WS(n)\)
-\end{corollary}
-
-\begin{remark}
-In the above ineqality, a "\(+1\)" can be added to the lower bound if \(WS(n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less
-clear and it is never useful in practice.
-\end{remark}
-
-We first give an intuitive explanation of the above theorem. Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
-subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\) and let's try to build a colouring of \([\![1, ap + q]\!]\)
-into \(n + k\) weakly sum-free subsets. Let \(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\). \\
-
-First, put the integers of \([\![1, ap + q]\!]\) in the following table (with \(a\) columns and \(p + 1\) lines) and divide it into 3 blocks (the columns are numbered from \(-l\) to \(+q\)):
-
-\begin{itemize}
-	\item \(\mathcal{T}\) (the "tail"): the integers from 1 to \(q\). NB: this is line number 0.
-	\item \(\mathcal{L}\) (the "lines"): the integers in columns \(-l\) to \(+r\) (excluding  \(\mathcal{T}\)).
-	\item \(\mathcal{C}\) (the "columns"): the integers in the last \(w\) columns (excluding  \(\mathcal{T}\)).
-\end{itemize}
-
-Note that with this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the sum of the columns modulo \(a\).
-
-\renewcommand{\arraystretch}{2}
 \begin{center}
-\[
-\begin{array}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
-\cline{6-9}
-   \multicolumn{5}{c|}{} & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
+SF-template partitionning \([\![1, 33]\!]\) into 4 subsets \\
+\begin{tabular}{|*{2}{c|}}
 	\hline
-   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
+	1 & 1, 6, 9, 13, 16, 20, 24, 27, 31 \\
 	\hline
-\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
+	2 & 2, 5, 14, 15, 25, 26 \\
 	\hline
-...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
+	3 & 3, 4, 10, 11, 12, 28, 29, 30 \\
 	\hline
-\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
+	4 & 7, 8, 17, 18, 19, 21, 22, 23, 32, 33 \\
 	\hline
-...&...&...&...&...&...&...&...&...&...&...&...&...\\
-\hline
-\end{array}
-\]
+\end{tabular}
 \end{center}
 
-\underline{\textbf{\(\mathcal{T}\) block}} \\
-We color this block using the weakly sum-free colouring of \([\![1,q]\!]\) with colors \(1, ..., n\).
+\begin{center}
+SF-template partitionning \([\![1, 111]\!]\) into 5 subsets
+\begin{tabular}{|*{2}{c|}}
+	\hline
+	1 & 1, 5, 18, 12, 14 ,21, 23, 30, 32, 36, 39, 43, 45, 52, 103 \\
+	 & 106, 110 \\
+	\hline
+	2 & 2, 6, 7, 10, 15, 18, 26, 29, 34, 37, 38, 42, 46, 51, 54 \\
+	& 101, 104, 109 \\
+	\hline
+	3 & 3, 4, 9, 11, 17, 19, 25, 27, 33, 35, 40, 41, 47, 48, 55 \\
+	& 100, 107, 108 \\
+	\hline
+	4 & 13, 16, 20, 22, 24, 28, 31, 58, 61, 67, 88, 94, 97 \\
+	\hline
+	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70\\
+	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85\\
+	& 86, 87, 89, 90, 91, 92, 93, 95, 96, 98, 99, 102, 105, 111 \\
+	\hline
+\end{tabular}
+\end{center}
 
-\underline{\textbf{\(\mathcal{L}\) block}} \\
-In this block,  we use the colors \(n + 1, ..., n + k\). We colour an integer \(x\) according to its line number (written \(\lambda(x)\)).
-For every \(x \in \mathcal{L}\), we colour \(x\) with \(n + c\) where \(c\) is the colour of \(\lambda(x)\) in the sum-free colouring of  \([\![1,p]\!]\).
-Let \((x, y) \in \mathcal(L)^2\). The cases are twofold.
+\begin{center}
+SF-template partitionning \([\![1, 380]\!]\) into 6 subsets
+\begin{tabular}{|*{2}{c|}}
+	\hline
+	1 & 1, 5, 8, 11, 15, 17, 29, 33, 36, 39, 43, 57, 61, 88, 92 \\
+	& 106, 110, 113, 116, 120, 132, 134, 138, 141, 144, 148, 150, 154, 157, 160 \\
+	& 164, 178, 182, 185, 188, 341, 344, 347, 351, 365, 369, 372, 375, 379\\
+	\hline
+	2 & 2, 9, 13, 16, 20, 23, 24, 27, 28, 31, 34, 35, 38, 42, 45\\
+	& 49, 53, 60, 67, 71, 78, 82, 89, 96, 100, 104, 107, 111, 114, 115\\
+	& 118, 121, 122, 125, 126, 129, 133, 136, 140, 147, 158, 162, 165, 169, 172\\
+	& 176, 183, 187, 194, 201, 328, 335, 342, 346, 353, 357, 360, 364, 367, 371\\
+	\hline
+	3 & 3, 4, 12, 14, 19, 25, 30, 32, 40, 41, 47, 48, 58, 91, 101\\
+	& 102, 108, 109, 117, 119, 124, 130, 135, 137, 145, 146, 152, 153, 161, 163\\
+	& 168, 179, 181, 190, 339, 348, 350, 361, 366, 368, 376, 377\\
+	\hline
+	4 & 6, 7, 10, 18, 21, 22, 26, 37, 46, 50, 51, 54, 65, 70, 79\\
+	& 84, 95, 98, 99, 103, 112, 123, 127, 128, 131, 139, 142, 143, 151, 155\\
+	& 156, 159, 167, 170, 171, 175, 186, 343, 354, 358, 359, 362, 370, 373, 374\\
+	& 378\\
+	\hline
+	5 & 44, 52, 55, 56, 59, 62, 63, 64, 66, 68, 69, 72, 73, 74, 75\\
+	& 76, 77, 80, 81, 83, 85, 86, 87, 90, 93, 94, 97, 105, 189, 196\\
+	& 197, 200, 203, 206, 207, 209, 214, 219, 231, 298, 310, 315, 320, 322, 323\\
+	& 326, 329, 332, 333, 340\\
+	\hline
+	6 & 149, 166, 173, 174, 177, 180, 184, 191, 192, 193, 195, 198, 199, 202, 204\\
+	& 205, 208, 210, 211, 212, 213, 215, 216, 217, 218, 220, 221, 222, 223, 224\\
+	& 225, 226, 227, 228, 229, 230, 232, 233, 234, 235, 236, 237, 238, 239, 240\\
+	& 241, 242, 243, 244, 245, 246, 247, 248, 249, 250, 251, 252, 253, 254, 255\\
+	& 256, 257, 258, 259, 260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270\\
+	& 271, 272, 273, 274, 275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285\\
+	& 286, 287, 288, 289, 290, 291, 292, 293, 294, 295, 296, 297, 299, 300, 301\\
+	& 302, 303, 304, 305, 306, 307, 308, 309, 311, 312, 313, 314, 316, 317, 318\\
+	& 319, 321, 324, 325, 327, 330, 331, 334, 336, 337, 338, 345, 349, 352, 355\\
+	& 356, 363, 380\\
+	\hline
 
-\begin{itemize}
-	\item \underline{\(\lambda(x+y) = \lambda(x) + \lambda(y)\)} \\
-	In this case, we use the sum-free property of the colouring of \([\![1,p]\!]\) (in block \(\mathcal{C}\), we only use colours \(1, ..., n\)).
+\end{tabular}
+\end{center}
 
-	\item \underline{\(\lambda(x+y) \neq \lambda(x) + \lambda(y)\)} \\
-	In this case, we do not have information about the colour of \(\lambda(x+y)\). Thereby, we want to have \(x+y \in \mathcal{C}\).
-	A simple solution is to limit the horizontal movement, that is if the sum changes line, not to move too far so that it stays in \(\mathcal{C}\).
-	There, the maximal displacement to the left (resp. to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left
-	is then expressed as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written as
-	 \(\text{max}(l, r) \leqslant w\).
-\end{itemize}
+\section{WSF-templates}
 
-\underline{\textbf{\(\mathcal{C}\) block}} \\
-In this block,  we use colors \(1, ..., n\). We colour an integer \(x\) according to its column number (written \(\tilde{\pi}(x)\), it is linked to the
-projection on the first line, written \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\)). A simple solution is to colour \(x\) with the same colour
-as \(\tilde{\pi}(x)\) in the weakly sum-free colouring of \([\![1,q]\!]\). As long as \(2b \leqslant a + r\) (not going two far to the right) and there
-is no \(x \in \tilde{\pi}(\mathcal{C})\) such that \(2x \in \tilde{\pi}(\mathcal{C})\) (so that we do not have a sum in \(\mathcal{C}\) when
-taking two numbers in the same column), the colours \(1, ..., n\) are sum-free. \\
+\begin{center}
+WSF-template partitionning \([\![1, 42]\!]\) into 4 subsets
+\begin{tabular}{|*{2}{c|}}
+	\hline
+	1 & 1, 2, 4, 8, 11, 22, 25, \(\mathbf{(N+1)}\)\\
+	\hline
+	2 & 5, 6, 7, 19, 21, 23, 36\\
+	\hline
+	3 & 9, 10, 12, 13, 14, 15, 16, 17, 18, 20\\
+	\hline
+	4 & 24, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 37, 38, 39, 40\\
+	& 41, 42\\
+	\hline
+\end{tabular}
+\end{center}
 
-In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem. \\
+This template provides the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
+by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.
+
+\section{Proof of theorem j'arrive pas a afficher le numero du theoreme avec un lien}
 
@@
 Finally, we have showed that every classe of equivalence induced by \(h\) is weakly sum-free, which ends the proof.
-
-\begin{remark}
-This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\),
-this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
-3.1)},we will define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
-\end{remark}
-
-\subsection{Definition of \(WS^+\)}
-
-We will now define functions and results, that will be used in the following theorem.
-
-\begin{definition}
-
-Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\pi_{a,b}\) the projection:
-\[ \pi_{a,b}:x \longmapsto (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a}))\]
-\end{definition}
-
-We will note  the projection \(\pi\) and not \(\pi_{a,b}\) when there is no doubt about the a and b we use.
-
-\begin{proposition}
-Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
-\end{proposition}
-
-\textsc{Proof :}Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)
-
-if \(x+\pi(y)< a:\)we remark that \(\pi(y)>b\) and therefore \(x+\pi(y)>b\):
-
-\begin{align*}
- \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
-& =x+ \pi(y)
-\end{align*}
-
-if \(x+\pi(y\geqslant a\):
-\begin{align*}
- \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
-& = x+\pi(y) - a +a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
-& = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
-& = x+\pi(y)
-\end{align*}
-
-\begin{proposition}
-Let (x,y)\(\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
-\end{proposition}
-
-\textsc{Proof :}Let (x,y)\(\in (\mathbb{N}^*)^2\),
-
-\begin{align*}
- \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})((Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a})+(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{y mod a})\text{ mod a}) \\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ ((x mod a) + (y mod a)) mod a})\\
-& =(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ x+y mod a})\\
-& =\pi(x+y)
-\end{align*}
-
-\begin{definition}
-
-Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\lambda_{a,b}\) the projection:
-\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
-\end{definition}
-
-We will note  the projection \(\lambda\) and not \(\lambda_{a,b}\) when there is no doubt about the a and b we use.
-
-\begin{remark}
-In the following theorem, \(\lambda\) is the function which maps an element x to its line number.
-\end{remark}
-
-\begin{proposition}
-Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
-\end{proposition}
-\textsc{Proof :}Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\),
-\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(\text{x mod a})+\mathbf{1}_{ [\![0,b]\!]}(\text{x mod a})\)
-
-if x mod a \(>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+\text{x mod a}=x\)
-
-if x mod a \(\leqslant b\):
-\(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)
-
-\begin{definition}
-Let \( (p,k,b) \in (\mathbb{N}^*)^3\), Let \((A_1,....,A_k)\) a partition of  \([\![1, p]\!]\).
-This partition is said to be a b-weakly-sum-free template (b-WSF-template) of \(k\) colors and lenght \(p\) when:
-\\\\
-\underline{\(\forall i \in [\![1, k]\!], \quad A_i\) is weakly-sum-free}
-\\\\
-\underline{\(\forall i \in [\![1, k]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
-\\\\
-\underline{For \(A_k\) (the special subset):} \quad \(\forall (x,y) \in A_k^2,\)
-\\
-\[if \quad x+y>b+2(p-b),\quad x+y-2(p-b)\notin A_k\]
-\\
-\underline{For the others subsets:}\quad \(\forall i \in [\![0,k-1]\!], \forall(x,y) \in A_i^2\)
-\\
-\[
-x+y>p \implies \pi(x+y) \notin A_i
-\]
-\end{definition}
-
-\begin{definition}
-Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\)
-subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note:
-\\\\\(WS_b^+=-b+\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
-\(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
-\\\\
-If this \(p\) does not exist, we set \(WS_b^+= 0\)
-\end{definition}
-
-\begin{definition}
-Let \( n \in \mathbb{N}^*\), we define \(WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{WS_b^+(n)\}\)
-\end{definition}
-
-\subsection{Lower bound for Weak schur numbers using Schur and Weak Schur template numbers}
-
-\begin{theorem}
-Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \(k\)
-sum-free subsets of \([\![1,p]\!]\) and a partition of n subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
-\(b\)-WSF of \(n\) colors and lenght \(q\),
- then there exists a partition of \([\![1, b+p \times (q-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
-\end{theorem}
-
-In particular, if we choose \(p = S(k)\) and \(q = WS^+(n)\) in the last theorem, the next corollary follows.
-
-\begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/WS^+(n+1)=WS_b^+(n+1)\},\) \[
-WS(n+k) \geqslant S(k) WS^+(n+1)+b_{max}\]
-\end{corollary}
-
-\textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
-We denote by \(g\) the projection of the equivalence relation induced by the partition of \([\![1,q]\!]\) and \(h\) the
-one induced by the partition of \([\![1,p]\!]\). Each equivalence class is represented by a single integer, therefore :
-\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
-\]
-\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
-\Longrightarrow h(x+y) \neq h(x)
-\]
-
-Let \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such as:
-\\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
-\\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
-\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{L}): f(x)=n-1+h(\lambda(x))\)
-\\\\
-f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)
-
-We have parted the integers of \(\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{L}\).
-
-We have to verify that f induces weakly-sum-free templates:\\
-\\
-\underline{if (x,y) \(\in (\mathcal{T})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
-\\x+y\(<\)a+b since b\(<\)a and g(x)=f(x)=f(y)=g(y).
-\\Hence f(x+y)=g(x+y)\(\neq\)g(x)=f(x)
-\\\\
-\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{C}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
-We distinguish two cases:
-
-\begin{itemize}
-\item If x+\(\pi(y)\leqslant a+b\)
-\\g(x)=f(x)=f(y)=g(\(\pi(y)\). Hence g(x)\(\neq g(x+\pi(y))=g(\pi(x+y))\) (qv previous proposition)
-\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
-\\else, \(f(x+y)=g(\pi(x+y))\neq g(x)=f(x)\)
-\item If x+\(\pi(y)> a+b\), x+y\(>\)a+b and by definition of g, \(g(\pi(x+y))\neq g(x)\)
-\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
-\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
-\end{itemize}
-
-\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{L}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
-\\Then, f(x)=f(y)=n. We distinguish two cases:
-
-\begin{itemize}
-\item If \(\lambda(y)=\lambda(x+y)\),
-\\\(g(x)=g(\pi(y))=n \text{ since } g(y)=g(\pi(y))\)
-\\Therefore \(g(\pi(x+y))=g(x+\pi(y)) \neq g(x)=n\)(qv previous proposition)
-\\Hence \(f(x+y)=g(\pi(x+y))\neq n\)
-\item If  \(\lambda(y)\neq \lambda(x+y)\), \(\lambda(y)+1= \lambda(x+y)\)\\
-n=f(y)=n-1+h(\(\lambda(y)\)). Hence h(\(\lambda(y)\))=1.
-\\Moreover h(1)=1, therefore \(h(\lambda(y)+1) \neq 1\)
-\\if \(\pi(x+y) \in A_n\), \(f(x+y)=n-1+h(\lambda(x+y))>n\)
-\end{itemize}
-
-\underline{if (x,y) \(\in (\mathcal{C})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
-\\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases:
-
-\begin{itemize}
-\item If \(\pi(x)+\pi(y)>q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) (qv previous proposition)
-\\Hence \(g(\pi(x+y))= g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))\)
-\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
-\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
-\item If  \(\pi(x)+\pi(y)\leqslant q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) since g is sum-free for x\(>b\)
-\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
-\\else, \(f(x+y)=g(\pi(x+y))=g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))=f(x)\)
-
-\end{itemize}
-
-\underline{if (x,y) \(\in \mathcal{C} \times \mathcal{L} \), \(f(x)\neq f(y)\)}\\
-
-\underline{if (x,y) \(\in (\mathcal{L})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
-\\Let r(x)=\(\pi(x)-a\) and r(y)=\(\pi(y)-a\),
-\\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
-\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases:
-
-\begin{itemize}
-\item If \(r(x)+r(y) \in [\![b-a+1,b]\!]\), \(h(\lambda(x))=f(x)+1-n=f(y)+1-n=h(\lambda(y))\)
-Hence, \(h(\lambda(x)+\lambda(y)) \neq h(\lambda(x))\).
-\begin{align*}
- \\\lambda(x+y) & =1+\left\lfloor\dfrac{a(\lambda(x)+\lambda(y))+r(x)+r(y)-b-1}{a}\right\rfloor+1\\
-& = \lambda(x)+\lambda(y)+\left\lfloor\dfrac{r(x)+r(y)-b-1}{a}\right\rfloor+1 \\
-& = \lambda(x)+\lambda(y) -1 +1 \text{ since } r(x)+r(y) \in [\![b-a+1,b]\!] \\
-& =\lambda(x)+\lambda(y)
-\end{align*}
-
-\begin{align*}
- \\\text{if f(x+y)\(\geqslant\)n, }f(x+y) & =n-1+h(\lambda(x+y))\\
-& =n-1+h(\lambda(x)+\lambda(y)) \\
-& \neq n-1+h(\lambda(x))\\
-& =f(x)
-\end{align*}
-
-\item If \(r(x)+r(y)>b\), \(\pi(x)+\pi(y)>2a+b\)
-\\Since g is a b-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
-\\Therefore, \(g(\pi(x+y)) \neq n\) ie \(x+y \in \mathcal{C}\)
-\\Hence \(f(x+y) <n\leqslant f(x)\)
-\item If \(r(x)+r(y)\leqslant b-a,\), \(\pi(x)+\pi(y)\leqslant b+a\)
-\\Since g is sum-free for x\(>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
-\\Hence, \(f(x+y) <n\leqslant f(x)\)
-\end{itemize}
-
-\begin{remark}
-There exists a \(c(b) \geqslant \text{min}(A_{k+1} \backslash [\![1,b] - b - 1\) such that \(c(b)\) numbers can be
-added at the end of the extended partition.Therefore, we can get a better lower bound by finding a couple \((b,c(b))\)
-which maximizes the sum \(b+c(b)\) such that \(WS^+(k+1)=WS_b^+(k+1)\). Hence we have:
-	\[ WS(n+k) \geqslant S(n) WS^+(k+1)+b+c(b)\]
-
-\end{remark}
-
-\subsection{New lower bounds for Weak Schur numbers}
-Having found suitable templates, which can be found in the appendix, with a SAT solver, we claim that for all \(n \in
-\mathbb{N}^*\):
-\[
-4S(n) + 1 \leqslant WS(n+1)
-\]
-\[
-13S(n) + 8 \leqslant WS(n+2)
-\]
-\[
-42S(n) + 24 \leqslant WS(n+3)
-\]
-\[
-127S(n) + 68 \leqslant WS(n+4)
-\]
-The first two inequalities are due to Rowley, they are detailed in [2]. Like in 3.3, we compute the lower bounds given
-by the previous inequalities for \( n \in [\![8,15]\!] \). The best lower bound for each integer is highlighted.\\
-\\
-\begin{center}
-\begin{tabular}{|*{5}{c|}}
-    \hline
-	n & 8 & 9 & 10 & 11 \\
-	\hline
-	\(4S(n-1) + 2 \) & 6722 & 21146 & \cellcolor{yellow} 71214 & \cellcolor{yellow} 243794\\
-	\hline
-	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6976 & 21848 & 68726 & 231447\\
-	\hline
-	\(42S(n-3) + 24 \) & 6744 & \cellcolor{yellow} 22536 & 70584 & 222036 \\
-	\hline
-	\(127S(n-4) + 68 \) & 5656 & 20388 & 68140 & 213428\\
-	\hline
-	\hline
-	n & 12 & 13 & 14 & 15 \\
-	\hline
-	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815314 & 2554194 & 8045162 & \cellcolor{yellow} 27061154\\
-	\hline
-	\(13S(n-2) + 8 \) & 792332 & \cellcolor{yellow}2649772 & 8301132 & 26146778 \\
-	\hline
-	\(42S(n-3) + 24 \) & 747750 & 2559840 & \cellcolor{yellow} 8560800 &  25886224 \\
-	\hline
-	\(127S(n-4) + 68 \) & 671390 & 2261049 & 7740464 & 25886224 \\
-	\hline
-\end{tabular}
-\end{center}
-
-With \( S(9) \geqslant 17803 \), we found a new lower bound for
-\(WS(10)\) using Rowley's inequality. Moreover, the third inequality
-gives new lower bounds for \(WS(9)\) and \(WS(14)\). However, the last
-inequality doesn't give any better lower bound, even beyond \( n = 15 \)
-: the best bounds are always provided by the first three. We highly suspect that these values can be improved by
-investigating the search
-space further, which would provide new, more effective templates. One
-may try to go over this search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP},
-but with a different search space (as we explain in \hyperref[SAT]{SAT section}).
-This could be the suject of a future work.

### 2021-04-14 article/article.tex
anglais
modification organisation generale

@@
 
-This paper provides new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
-Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction
+This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by continuing on
+Rowley's "templates"-based approach for Ramsey and Schur numbers. Finding suitable templates allows us to apply Rowley's construction
 to get explicit partitions improving lower bounds as well as the growth rate of both Schur numbers and Ramsey numbers \(R_n(3)\). 
@@
 into \(n\) subsets. We show that exceeding the previous lower bound \(WS(6) \geqslant 582\) is impossible with such an assumption upon 
-imposing certain conditions on the good 5-subsets partition. The new lower bounds includes \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), 
+imposing certain conditions on the good 5-subsets partition. The new lower bounds include \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), 
 \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
@@
 
-\include{intro.tex}
+\include{introduction.tex}
+
+\include{state_of_the_art.tex}
+
+\include{definitions_notations.tex}
 
@@
 
-\appendix
-\renewcommand{\arraystretch}{1}
-
-\section{SF-templates}
-
-\begin{center}
-SF-template partitionning \([\![1, 33]\!]\) into 4 subsets \\
-\begin{tabular}{|*{2}{c|}}
-	\hline
-	1 & 1, 6, 9, 13, 16, 20, 24, 27, 31 \\
-	\hline
-	2 & 2, 5, 14, 15, 25, 26 \\
-	\hline
-	3 & 3, 4, 10, 11, 12, 28, 29, 30 \\
-	\hline
-	4 & 7, 8, 17, 18, 19, 21, 22, 23, 32, 33 \\
-	\hline
-\end{tabular}
-\end{center}
-
-\begin{center}
-SF-template partitionning \([\![1, 111]\!]\) into 5 subsets
-\begin{tabular}{|*{2}{c|}}
-	\hline
-	1 & 1, 5, 18, 12, 14 ,21, 23, 30, 32, 36, 39, 43, 45, 52, 103 \\
-	 & 106, 110 \\
-	\hline
-	2 & 2, 6, 7, 10, 15, 18, 26, 29, 34, 37, 38, 42, 46, 51, 54 \\
-	& 101, 104, 109 \\
-	\hline
-	3 & 3, 4, 9, 11, 17, 19, 25, 27, 33, 35, 40, 41, 47, 48, 55 \\
-	& 100, 107, 108 \\
-	\hline
-	4 & 13, 16, 20, 22, 24, 28, 31, 58, 61, 67, 88, 94, 97 \\
-	\hline
-	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70\\
-	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85\\
-	& 86, 87, 89, 90, 91, 92, 93, 95, 96, 98, 99, 102, 105, 111 \\
-	\hline
-\end{tabular}
-\end{center}
-
-\begin{center}
-SF-template partitionning \([\![1, 380]\!]\) into 6 subsets
-\begin{tabular}{|*{2}{c|}}
-	\hline
-	1 & 1, 5, 8, 11, 15, 17, 29, 33, 36, 39, 43, 57, 61, 88, 92 \\
-	& 106, 110, 113, 116, 120, 132, 134, 138, 141, 144, 148, 150, 154, 157, 160 \\
-	& 164, 178, 182, 185, 188, 341, 344, 347, 351, 365, 369, 372, 375, 379\\
-	\hline
-	2 & 2, 9, 13, 16, 20, 23, 24, 27, 28, 31, 34, 35, 38, 42, 45\\
-	& 49, 53, 60, 67, 71, 78, 82, 89, 96, 100, 104, 107, 111, 114, 115\\
-	& 118, 121, 122, 125, 126, 129, 133, 136, 140, 147, 158, 162, 165, 169, 172\\
-	& 176, 183, 187, 194, 201, 328, 335, 342, 346, 353, 357, 360, 364, 367, 371\\
-	\hline
-	3 & 3, 4, 12, 14, 19, 25, 30, 32, 40, 41, 47, 48, 58, 91, 101\\
-	& 102, 108, 109, 117, 119, 124, 130, 135, 137, 145, 146, 152, 153, 161, 163\\
-	& 168, 179, 181, 190, 339, 348, 350, 361, 366, 368, 376, 377\\
-	\hline
-	4 & 6, 7, 10, 18, 21, 22, 26, 37, 46, 50, 51, 54, 65, 70, 79\\
-	& 84, 95, 98, 99, 103, 112, 123, 127, 128, 131, 139, 142, 143, 151, 155\\
-	& 156, 159, 167, 170, 171, 175, 186, 343, 354, 358, 359, 362, 370, 373, 374\\
-	& 378\\
-	\hline
-	5 & 44, 52, 55, 56, 59, 62, 63, 64, 66, 68, 69, 72, 73, 74, 75\\
-	& 76, 77, 80, 81, 83, 85, 86, 87, 90, 93, 94, 97, 105, 189, 196\\
-	& 197, 200, 203, 206, 207, 209, 214, 219, 231, 298, 310, 315, 320, 322, 323\\
-	& 326, 329, 332, 333, 340\\
-	\hline
-	6 & 149, 166, 173, 174, 177, 180, 184, 191, 192, 193, 195, 198, 199, 202, 204\\
-	& 205, 208, 210, 211, 212, 213, 215, 216, 217, 218, 220, 221, 222, 223, 224\\
-	& 225, 226, 227, 228, 229, 230, 232, 233, 234, 235, 236, 237, 238, 239, 240\\
-	& 241, 242, 243, 244, 245, 246, 247, 248, 249, 250, 251, 252, 253, 254, 255\\
-	& 256, 257, 258, 259, 260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270\\
-	& 271, 272, 273, 274, 275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285\\
-	& 286, 287, 288, 289, 290, 291, 292, 293, 294, 295, 296, 297, 299, 300, 301\\
-	& 302, 303, 304, 305, 306, 307, 308, 309, 311, 312, 313, 314, 316, 317, 318\\
-	& 319, 321, 324, 325, 327, 330, 331, 334, 336, 337, 338, 345, 349, 352, 355\\
-	& 356, 363, 380\\
-	\hline
-
-\end{tabular}
-\end{center}
-
-\section{WSF-templates}
-
-\begin{center}
-WSF-template partitionning \([\![1, 42]\!]\) into 4 subsets
-\begin{tabular}{|*{2}{c|}}
-	\hline
-	1 & 1, 2, 4, 8, 11, 22, 25, \(\mathbf{(N+1)}\)\\
-	\hline
-	2 & 5, 6, 7, 19, 21, 23, 36\\
-	\hline
-	3 & 9, 10, 12, 13, 14, 15, 16, 17, 18, 20\\
-	\hline
-	4 & 24, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 37, 38, 39, 40\\
-	& 41, 42\\
-	\hline
-\end{tabular}
-\end{center}
-
-This template provides the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
-by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.
+\include{appendix.tex}
 

### 2021-04-14 article/weakschur.tex
modification organisation generale

@@
 In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem. \\
-
-\textsc{Proof :} Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\), \(N = p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q\),
-\(\alpha = \left \lceil \frac{q}{2} \right \rceil > 0\) and \(\beta = q + \alpha + 1\).
-We denote by \(f\) the colouring associated to the partition of \([\![1,q]\!]\) and \(g\) the
-one associated to the partition of \([\![1,p]\!]\).
-\[ f : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2, \left\{
-\begin{array}{ll}
-	x \neq y \\
-	f(x) = f(y)
-\end{array}
-\right.
-\Longrightarrow f(x+y) \neq f(x)
-\]
-\[g : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } f(x) = f(y)
-\Longrightarrow f(x+y) \neq f(x)
-\]
-Let us start by parting the integers of \([\![1,N]\!]\) in two subsets \(\mathcal{A}\) and \(\mathcal{B}\) where
-\(\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\}\) and
-\(\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}\).\\
-\\
-First, \underline{\(\mathcal{A} \cap \mathcal{B} = \varnothing\)} : \\
-By contradiction, suppose there exists \(x \in \mathcal{A} \cap \mathcal{B} \neq \varnothing \). Then there are \((a,u)
-\in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\) and \((b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\) such that \(x
-= a\beta + u = b\beta +v\). By definition of \(\alpha\) and \(\beta\) we have \(u \in [\![\alpha + 1,q]\!] \subset
-[\![0,\beta - 1]\!]\).
-From there, we distinguish two cases :
-\begin{itemize}
-\item If \(v \in [\![0,\alpha]\!]\) then \(v \in [\![0,\beta - 1]\!]\) and \(v \neq u\) because \(v < \alpha + 1
-\leqslant u\)
-\item If \(v \in [\![-\alpha,-1]\!]\), we note \(\tilde{v} = \beta + v\) and thus have \(x = (b-1)\beta + \tilde{v}\)
-with \(\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]\) and \(\tilde{v} \neq u\) because
-\(u< q+1 = \beta - \alpha \leqslant \tilde{v}\).
-\end{itemize}
-In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of \(x\)
-by\(\beta\).\\
-\\
-Then, we have \underline{\(\mathcal{A} \cup \mathcal{B} = [\![1,N]\!]\)}:
-\begin{itemize}
-	\item On the one hand : \(1 = \text{min}(\mathcal{A}) \leqslant \text{max}(\mathcal{A}) = p\beta + q = N\) and
-\(1 \leqslant \beta - \alpha = \text{min}(\mathcal{B}) \leqslant \text{max}(\mathcal{B}) = p\beta + \alpha \leqslant
-N\),
-	which gives \(\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]\).
-\item On the other hand, let \(x \in [\![1,N]\!]\). If \(x \leqslant \alpha\), we directly have \(x \in \mathcal{A}\),
-let us then suppose that \(x > \alpha\) and write \(x = a\beta + u\)
-the euclidean division of \(x\) by \(\beta\). We have \(x \leqslant N\), thus \(a \leqslant p\). We distinguish three
-cases : \\
-- If \(u \in [\![0,\alpha]\!]\) then we necessarily have \(a \geqslant 1\) because \(x > \alpha\), and so \(x \in
-\mathcal{B}\).\\
-	- If \(u \in [\![\alpha + 1,q]\!]\), then \(x \in \mathcal{A}\). \\
-- If \(u \in [\![q + 1,\beta - 1]\!]\) then \(x = (a+1)\beta - (\beta - u)\) with \(-\alpha \leqslant \beta - u
-\leqslant 0\).
-	Furthermore, \(a \leqslant p - 1\), else we would have \(x > N\), and so \(x \in \mathcal{B}\) \\
-In any case, \(x \in \mathcal{A} \cup \mathcal{B}\) and we can thus conclude that \([\![1,N]\!] \subset \mathcal{A}
-\cup\mathcal{B}\).
-\end{itemize}
-This first partition of \([\![1,N]\!]\) will help us to define our final partition by the projection of its equivalence
-relation.
-We thereby define \(h : [\![1,N]\!] \longrightarrow [\![1,n+k]\!]\) as such :\\
-- If \(x \in \mathcal{A}\) then \(h(x) = f(x \text{ mod } \beta)\) (well defined because \(x \text{ mod } \beta \in
-[\![1,N]\!]\))\\
-- If \(x \in \mathcal{B}\) then \(x = a\beta + u\) with a unique \((a,u) \in [\![1,p]\!] \times
-[\![-\alpha,\alpha]\!]\)and we define \(h(x) = n + g(a)\)\\
-The fact that \((\mathcal{A}, \mathcal{B})\) is a partition of \([\![1,N]\!]\) ensures that this definition of \(h\) is
-valid. We then have to verify that \(h\) induces weakly sum-free subsets.\\
-\\
-\underline{The classes of equivalence \(h(x)\) for \(x \in \mathcal{A}\) are weakly sum-free :}
-\\
-\\
-Let \((x,y) \in \mathcal{A}^2\) such that \(h(x) = h(y)\), \(x \neq y\) and \(x + y \leqslant N\)
-\begin{itemize}
-	\item If \((x,y) \in [\![1,\alpha]\!]^2\) :\\
-	We have \(x + y \leqslant 2\alpha \leqslant q\) and \(x + y = 0\beta + x + y\), therefore \(x + y \in \mathcal{A}\).
-Then, by definition : \(h(x) = f(x)\), \(h(y) = f(y)\) and \(h(x+y) = f(x+y)\), which gives us, thanks to the property
-verified by \(f\), that \(h(x+y) \neq h(x)\).
-	\item If \((x,y) \in [\![1,\alpha]\!] \times ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] )\) :\\
-We write \(y = a\beta + u\) with \((a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\). Then \(x+y = a\beta + x + u =
-(a+1)\beta + x + u - \beta\),
-and if \(x + u > q\) it follows that \(a \leqslant p-1\) since \(x+y \leqslant N\), and \(-\alpha \leqslant x + u -
-\beta \leqslant -1\).
-Therefore \(x+y \in \mathcal{B}\) and \(h(x+y) \neq h(x) = f(x)\) by definition of h. On the contrary, if \(x - u
-\leqslant n\),
-then \(x+y \in \mathcal{A}\) and \(h(x+y) = f(x+u)\) because \(x+u\) is actually the remainder of the euclidean
-divisionof \(x+y\) by \(\beta\).
-Moreover, \(h(x) = f(x)\), \(x < u\) and, with our initial hypothesis, \(h(x) = h(y) = f(u)\). The property verified by
-\(f\) gives us \(f(x+u) \neq f(x)\) which can be rewritten as \(h(x+y) \neq h(x)\).
-	\item If \((x,y) \in ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] ) \times [\![1,\alpha]\!]\) : \\
-	This case is handled exactly like the previous one by swaping the roles of \(x\) and \(y\).
-	\item If \((x,y) \in ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] )^2\) : \\
-We write \(x = a\beta + u\) and \(y = b\beta + v\) with \((a,u)\) and \((b,v)\) in \([\![0,p]\!] \times [\![\alpha +
-1,q]\!]\). Then \(x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta\)
-with \(a+b \leqslant p-1\) (else we would have \(x+y > N\) because \(u+v > q\)) and \(-\alpha \leqslant u + v - \beta
-\leqslant \alpha\), therefore \(x+y \in \mathcal{B}\) and by definition \(h(x+y) \neq h(x)\).
-\end{itemize}
-In any case, \(h(x+y) \neq h(x)\) and the classes of equivalence \(h(x)\) for \(x \in \mathcal{A}\) are weakly
-sum-free.\\
-\\
-\underline{The classes of equivalence \(h(x)\) for \(x \in \mathcal{B}\) are weakly sum-free :}
-\\
-\\
-Let \((x,y) \in \mathcal{B}^2\) such that \(h(x) = h(y)\), \(x \neq y\) and \(x + y \leqslant N\).\\
-We write \(x = a\beta + u\) and \(y = b\beta + v\) with \((a,u)\) and \((b,v)\) in \([\![1,p]\!] \times
-[\![-\alpha,\alpha]\!]\).
-We have \(h(x) = q + g(a)\) and \(h(y) = q + g(b)\), therefore \(g(a) = g(b)\). We also have \(x+y = (a+b)\beta + u
-+v\).\\
-If \(u + v \in [\![-\alpha,\alpha]\!]\), then \(x+y \in \mathcal{B}\) and \(h(x+y) = g(a+b)\), hence we can deduce that
-\(h(x+y) \neq h(x)\) because of the property verified by \(g\). On the contrary, if \(u+v \notin
-[\![-\alpha,\alpha]\!]\), then necessarily \(x+y \in \mathcal{A}\). Suppose \(x+y \in \mathcal{B}\), then \(x+y =
-c\beta+ w\) with \((c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\). Thus, \(c\beta + w = (a+b)\beta + u + v\) and
-\((a+b-c)\beta = w-u-v\). Furthermore \(a+b-c \neq 0\), else we would have \(u+v = w \in [\![-\alpha,\alpha]\!]\). This
-finally leads to the following inequality :
-\[\beta \leqslant |a+b-c|\beta = |w-u-v| \leqslant |w| + |u| + |v| \leqslant 3\alpha \leqslant q + \alpha < \beta
-\]
-which is absurd. We can therefore conclude that \(x+y \in \mathcal{A}\) and by definition of \(h\), \(h(x+y) \neq
-h(x)\), proving that the classes of equivalence \(h(x)\) for \(x \in \mathcal{B}\) are weakly sum-free.\\
-\\
-Finally, we have showed that every classe of equivalence induced by \(h\) is weakly sum-free, which ends the proof.
 

### 2021-04-14 article/appendix.tex
commande \WS

@@
 
-This template provides the inequality \(WS(n+3) \geqslant 42S(n) + 24\)
+This template provides the inequality \(\WS (n+3) \geqslant 42S(n) + 24\)
 by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.

### 2021-04-14 article/article.tex
commande \WS

@@
 \usepackage[table]{xcolor}
+\usepackage[a4paper, total={6in, 8in}]{geometry}
 
@@
 
-\usepackage[a4paper, total={6in, 8in}]{geometry}
+\newcommand{\WS}{\mathit{WS}}
 
@@
 works on the subject based on the principle that good partitions into \(n+1\) subsets start with good partitions
-into \(n\) subsets. We show that exceeding the previous lower bound \(WS(6) \geqslant 582\) is impossible with such an assumption upon 
+into \(n\) subsets. We show that exceeding the previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption upon
 imposing certain conditions on the good 5-subsets partition. The new lower bounds include \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\),
-\(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).
+\(\WS (9) \geqslant 22536 \) and \(\WS (10) \geqslant 71214 \).
 
@@
 Therefore, we would not be surprised if lower bounds are later improved using better templates. Moreover, studying specifically \(S^+(n)\) and
-\(WS^+(n)\) might be of interest as they are closely related to Schur and weak Schur numbers.
+\(\WS^+(n)\) might be of interest as they are closely related to Schur and weak Schur numbers.
 

### 2021-04-14 article/definitions_notations.tex
modification organisation generale
commande \WS

--- 2021-04-09 article/intro.tex
@@
-\section{Introduction, context and notations}
+\section{Definitions and notations}
 
@@
 subsets. Given \(p\) and \(n\) two integers, we are interested in partitioning the set of integers from 1 to \(p\) into
-\(n\) weakly sum-free subsets.
+\(n\) (weakly) sum-free subsets.
 
@@
 \begin{definition}
-Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we denote \(S(n)\) (\textit{resp. \(WS(n)\)}) such that
-\([\![1,S(n)]\!]\) (resp. \([\![1,WS(n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
-subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(WS(n)\) the
+Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we denote \(S(n)\) (\textit{resp. \(\WS (n)\)}) such that
+\([\![1,S(n)]\!]\) (resp. \([\![1, \WS (n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
+subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(\WS (n)\) the
 \(n\)\textsuperscript{th} weak
@@
 For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We also denote
-\(m_i = \text{min}(A_i)\).
+\(m_i = \min(A_i)\).
 By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do not make this
@@
 We sometimes refer to a partitition as a colouring. The colouring associated to a partition \(A_1, ..., A_n\) of
-\([\![1, p]\!]\) is the function \(f\) that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition associated to 
-a colouring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall i \in [\![1, n]\!], A_i = f^{-1}(i)\).
+\([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition associated to
+a colouring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
 \end{definition}

### 2021-04-14 article/sat.tex
commande \WS

@@
 found the previous best known lower bounds for weak Schur numbers may not be correct. Finally, we obtain stronger
-results than those previously known for \(WS(5)\) while gaining several orders of magnitude in computation time by
+results than those previously known for \(\WS (5)\) while gaining several orders of magnitude in computation time by
 giving additional information to the SAT solver without losing in generality. In this section, we assume that the
@@
 enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
-\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1,WS(c - 1)+1]\!],
+\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1, \WS (c - 1)+1]\!],
 x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
@@
 \subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
-Rowley's new lower bound for \(WS(6)\) (642) \cite{RowleyWS} was a quite significant improvement upon
+Rowley's new lower bound for \(\WS (6)\) (642) \cite{RowleyWS} was a quite significant improvement upon
 the former
@@
 (often with Monte-Carlo methods) and by making the
-assumption that a good partition for \(WS(n+1)\) starts with a good partition for \(WS(n)\) which is true for small
+assumption that a good partition for \(\WS (n+1)\) starts with a good partition for \(\WS (n)\) which is true for small
 values of \(n\).
@@
 \par
-The above theorem shows that the previous lower bound for \(WS(6)\) is optimal in the search space considered by the
+The above theorem shows that the previous lower bound for \(\WS (6)\) is optimal in the search space considered by the
 papers which found it.
@@
 computer. More generally,
-it questions the search space previously used for finding lower bounds for \(WS(n)\) with a computer. In particular, to
+it questions the search space previously used for finding lower bounds for \(\WS (n)\) with a computer. In particular, to
 our knowledge every paper
-that found the lower bound \(WS(5) \geqslant 196\) used this assumption. Therefore one may wonder
+that found the lower bound \(\WS (5) \geqslant 196\) used this assumption. Therefore one may wonder
 if this actually a good lower
@@
 \subsection{Weak Schur number five}
-As explained in the previous subsection, the search space used for showing that \(WS(5) \geqslant 196\) may not contain
+As explained in the previous subsection, the search space used for showing that \(\WS (5) \geqslant 196\) may not contain
 optimal solution. In this subsection,
@@
 \begin{notation}
-Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(WS(n | P)\) the greatest number \(p\) such that
+Let \(P\) be a predicate over weakly sum-free partitions. We denote by \(\WS (n | P)\) the greatest number \(p\) such that
 there exists a partition of
@@
 assuming \(m_5 = 67\) even after several
-weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5
+weeks of runtime. By using the same method as above, we were able to verify that \(\WS (5 | m_5 = 67) = 196\) in 0.5
 seconds with the SAT solver glucose \cite{Glucose}
@@
 this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation
-time. Since \(WS(4) = 66\), we have \(m_5 \leqslant 67\). We give the stronger following result.
+time. Since \(\WS (4) = 66\), we have \(m_5 \leqslant 67\). We give the stronger following result.
 
@@
 More precisely, we verified the following results (\(max~m_5\) is the greatest value of \(m_5\) for which we have not
-verified that \(WS(5 | m_5) \leq 196\)).
+verified that \(\WS (5 | m_5) \leq 196\)).
 
@@
 	\hline
-	\(WS(4 | m_4) + 1\) & 55 & 59 & 60 & 59 & 59 & 60 & 60 & 60 & 60 & 64 & 63 & 64 & 61 & 64 & 63 & 65 & 65 & 65 & 65 & 66
+	\(\WS (4 | m_4) + 1\) & 55 & 59 & 60 & 59 & 59 & 60 & 60 & 60 & 60 & 64 & 63 & 64 & 61 & 64 & 63 & 65 & 65 & 65 & 65 & 66
 	& 67 \\

### 2021-04-14 article/weakschur.tex
commande \WS

@@
 section, the
-integer \(WS^+(n)\)
+integer \(\WS^+(n)\)
 to build suitable templates.
@@
 give a general lower bound for weak Schur numbers as a function of both regular and weak Schur numbers.
-The following theorem, inspired by Rowley's inequalities for \(WS(n+1)\) and \(WS(n+2)\), was found and proved
+The following theorem, inspired by Rowley's inequalities for \(\WS (n+1)\) and \(\WS (n+2)\), was found and proved
 by Romain Ageron.
@@
 
-In particular, if we choose \(q = WS(n)\) and \(p = S(k)\) in the last theorem, the next corollary follows.
+In particular, if we choose \(q = \WS (n)\) and \(p = S(k)\) in the last theorem, the next corollary follows.
 
 \begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } WS(n+k) \geqslant S(k) \left (WS(n) + \left \lceil \frac{WS(n)}{2}
-\right \rceil +1 \right) + WS(n)\)
+\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } \WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \frac{\WS (n)}{2}
+\right \rceil +1 \right) + \WS (n)\)
 \end{corollary}
@@
 \begin{remark}
-In the above ineqality, a "\(+1\)" can be added to the lower bound if \(WS(n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less
+In the above ineqality, a "\(+1\)" can be added to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less
 clear and it is never useful in practice.
@@
 this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
-3.1)},we define \(WS^+\) and find inequalities between \(WS^+\),\(WS\) and \(S\)
+3.1)},we define \(\WS^+\) and find inequalities between \(\WS^+\),\(\WS\) and \(S\)
 \end{remark}
 
-\subsection{Definition of \(WS^+\)}
+\subsection{Definition of \(\WS^+\)}
 
-In this subsection, we define the objects and proove the results needed for the general theorem regarding templates for 
+In this subsection, we define the objects and prove the results needed for the general theorem regarding templates for
 weak Schur numbers.
@@
 Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\)
-subsets which is a \(b\)-WS-template of \(k\) colors and lenght \(p\), we note:
-\\\\\(WS_b^+=-b+\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
+subsets which is a \(b\)-WSF-template of \(k\) colors and lenght \(p\), we note:
+\\\\\(\WS_b^+=-b+\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
 \(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
 \\\\
-If this \(p\) does not exist, we set \(WS_b^+= 0\)
+If this \(p\) does not exist, we set \(\WS_b^+= 0\)
 \end{definition}
@@
 \begin{definition}
-Let \( n \in \mathbb{N}^*\), we define \(WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{WS_b^+(n)\}\)
+Let \( n \in \mathbb{N}^*\), we define \(\WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{\WS_b^+(n)\}\)
 \end{definition}
@@
 	\[
-	\frac{3}{2}WS(n-1)+1 \leqslant WS^+(n) \leqslant WS(n)
+	\frac{3}{2} \WS (n-1)+1 \leqslant \WS^+(n) \leqslant \WS (n)
 	\]
@@
 \begin{remark}
-	\(WS^+\) and \(WS\) have the same asymptotic growth rate.
+	\(\WS^+\) and \(\WS\) have the same asymptotic growth rate.
 \end{remark}
@@
 
-In particular, if we choose \(p = S(k)\) and \(q = WS^+(n)\) in the last theorem, the next corollary follows.
+In particular, if we choose \(p = S(k)\) and \(q = \WS^+(n)\) in the last theorem, the next corollary follows.
 
 \begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/ WS_b^+(n+1) = WS^+(n+1)\},\) \[
-WS(n+k) \geqslant S(k) WS^+(n+1)+b_{max}\]
+\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\},\) \[
+\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}\]
 \end{corollary}
@@
 not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_max\) can actually be replaced by \\
-\[\max \left\{ b + \min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ WS_b^+(n+1) = WS^+(n+1) \right\}\]
+\[\max \left\{ b + \min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}\]
 \end{remark}
@@
 Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
-\[ WS(n+k) \geqslant WS^+(k+1) S(n) + b + c\]
+\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
 \end{proposition}
@@
 
-We also have a similar theorem where only \(WS^+\) is involved.
+We also have a similar theorem where only \(\WS^+\) is involved.
 
@@
 	Let \(n, k \in \mathbb{N}^*\), we have \\
-	\[ WS^+(n+k) \geqslant S^+(k+1)WS^+(n) \]
+	\[ \WS^+(n+k) \geqslant S^+(k+1) \WS^+(n) \]
 \end{corollary}
@@
 \[
-4S(n) + 1 \leqslant WS(n+1)
+\WS(n+1) \geqslant 4S(n) + 1 
 \]
 \[
-13S(n) + 8 \leqslant WS(n+2)
+\WS(n+2) \geqslant 13S(n) + 8
 \]
 \[
-42S(n) + 24 \leqslant WS(n+3)
+\WS(n+3) \geqslant 42S(n) + 24
 \]
 \[
-132S(n) + 26 \leqslant WS(n+4)
+\WS(n+4) \geqslant 132S(n) + 26
 \]
@@
 As for the fourth inequality, it was obtained by combining an optimal SF-template of length 33 with a WSF-template of length 4.
-The best template we could get with a computer search gives the inequality \(WS(n+4) \geqslant 127 S(n) + 68\). 
+The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
 It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of
-5 colors which start with a good \(WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates 
+5 colors which start with a good \(\WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates
 as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates
@@
 
-With \( S(9) \geqslant 17803 \), we found a new lower bound for \(WS(10)\) using Rowley's inequality. 
-Moreover, the third inequality gives new lower bounds for \(WS(9)\) and \(WS(14)\).
+With \( S(9) \geqslant 17803 \), we found a new lower bound for \(\WS(10)\) using Rowley's inequality.
+Moreover, the third inequality gives new lower bounds for \(\WS(9)\) and \(WS(14)\).

### 2021-04-14 article/appendix.tex
reorganisation sat / search space

@@
 by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.
+
+\section{Reformulation as a SAT problem}
+\label{SAT}
+
+In this section, we reframe the question of the existence of (weakly) sum-free partitions as a boolean
+satisfiability (SAT) problem. We encode the existence of (weakly) sum-free partitions as propositional formulae like in
+\cite{Heule2017} and then use SAT solvers to determine whether these formulae are satisfiable.
+
+\begin{definition}
+A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a
+negative literal) where \(v\)
+takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a
+conjunction of clauses: it
+is a propositional formula in \textit{conjonctive normal form} (CNF).
+\end{definition}
+
+\begin{definition}
+An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A
+literal \(l\) is
+\textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\)
+(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A
+clause is \textit{satisfied}
+by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is
+\textit{satisfied} by an assignment
+\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an
+assignment that satisfies it;
+otherwise it is \textit{unsatisfiable}.
+\end{definition}
+
+We then encode the existence of a partition of \([\![1,p]\!]\) in \(k\) weakly sum-free subsets as follows: for every
+integer
+\(i \in [\![1,p]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!],
+x^{(i)}_c = 1 \iff i \in A_c\).
+The corresponding clauses are:
+
+\begin{itemize}
+\item \textbf{weakly sum-free:} \(\forall c \in [\![1,k]\!], \forall (i, j) \in [\![1,p]\!]^2, (i \neq j ~ \text{and} ~ i + j
+\leq n) \implies \lnot x^{(i)}_c
+\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
+\item \textbf{union:} \(\forall i \in [\![1,p]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
+\item \textbf{disjoint:} \(\forall i \in [\![1,p]\!],\forall (c_1, c_2) \in [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg
+x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
+\end{itemize}
+
+In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the
+subsets, that is by
+enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
+\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1, \WS (c - 1)+1]\!],
+x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
+
+\begin{remark}
+For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary
+significantly according to the problem.
+For instance, we used two different SAT solvers in the next two next subsections.
+\end{remark}
+
+\begin{remark}
+Using a parallel SAT solver usually reduces the computation time, especially when trying to show that a formula is
+unsatisfiable. However, most of the
+parallel SAT solver do not have a deterministic behaviour and it can results in a strong variation of running times.
+\end{remark}
 

### 2021-04-14 article/search_space.tex
reorganisation sat / search space

--- 2021-04-14 article/sat.tex
@@
-\section{About the construction of lower bounds for weak Schur numbers using a computer}
+\section{Analysis of the former search space}
 
-In this section, we first reframe the question of the existence of (weakly) sum-free partitions as a boolean
-satisfiability (SAT) problem. We then provide evidence which indicates that the main assumption made by papers which
-found the previous best known lower bounds for weak Schur numbers may not be correct. Finally, we obtain stronger
-results than those previously known for \(\WS (5)\) while gaining several orders of magnitude in computation time by
-giving additional information to the SAT solver without losing in generality. In this section, we assume that the
-subsets are ordered.
+In this section, we first provide evidence which indicates that the main assumption made by papers which
+found the previous best known lower bounds for weak Schur numbers using a computer may not be correct. 
+This is done primarily by studying \(\WS(6)\). Then, in an effort to eliminate irrelevant search spaces, we 
+obtain stronger results than those previously known for \(\WS (5)\) while gaining several orders of magnitude 
+in computation time by giving additional information to the SAT solver without losing in generality. In this 
+section, we assume that the subsets are ordered.
 
-\subsection{Reformulation as a SAT problem}
-\label{SAT}
-
-We encode the existence of (weakly) sum-free partitions as propositional formulae like in
-\cite{Heule2017} and then use
-SAT solvers to determine whether these formulae are satisfiable.
-
-\begin{definition}
-A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a
-negative literal) where \(v\)
-takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a
-conjunction of clauses: it
-is a propositional formula in \textit{conjonctive normal form} (CNF).
-\end{definition}
-
-\begin{definition}
-An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A
-literal \(l\) is
-\textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\)
-(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A
-clause is \textit{satisfied}
-by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is
-\textit{satisfied} by an assignment
-\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an
-assignment that satisfies it;
-otherwise it is \textit{unsatisfiable}.
-\end{definition}
-
-We then encode the existence of a partition of \([\![1,p]\!]\) in \(k\) weakly sum-free subsets as follows: for every
-integer
-\(i \in [\![1,p]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!],
-x^{(i)}_c = 1 \iff i \in A_c\).
-The corresponding clauses are:
-
-\begin{itemize}
-\item \textbf{sumfree:} \(\forall c \in [\![1,k]\!], \forall (i, j) \in [\![1,p]\!]^2, (i \neq j ~ \text{and} ~ i + j
-\leq n) \implies \lnot x^{(i)}_c
-\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
-\item \textbf{union:} \(\forall i \in [\![1,p]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
-\item \textbf{disjoint:} \(\forall i \in [\![1,p]\!],\forall (c_1, c_2) \in [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg
-x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
-\end{itemize}
-
-In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the
-subsets, that is by
-enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
-\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1, \WS (c - 1)+1]\!],
-x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
-
-\begin{remark}
-For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary
-significantly according to the problem.
-For instance, we used two different SAT solvers in the next two next subsections.
-\end{remark}
-
-\begin{remark}
-Using a parallel SAT solver usually reduces the computation time, especially when trying to show that a formula is
-unsatisfiable. However, most of the
-parallel SAT solver do not have a deterministic behaviour and it can results in a strong variation of running times.
-\end{remark}
-
-\subsection{The search space previously used in computer search for lower bounds may not contain the optimal partitions}
-Rowley's new lower bound for \(\WS (6)\) (642) \cite{RowleyWS} was a quite significant improvement upon
-the former
-best known lower bound (582) \cite{EliahouBook}. This previous lower bound was found using a computer
-(often with Monte-Carlo methods) and by making the
-assumption that a good partition for \(\WS (n+1)\) starts with a good partition for \(\WS (n)\) which is true for small
-values of \(n\).
-Therefore, one may wonder whether the limiting factor are the assumptions or the methods used to search for partitions.
-It appears that the search space
-induced by these assumptions does not contain the optimal partitions.
+\subsection{Former assumption appears to be wrong}
+Rowley's new lower bound for \(\WS (6)\) (642) \cite{RowleyWS} was a significant improvement upon
+the former best known lower bound (582) \cite{EliahouBook}. This previous lower bound has been found 
+several times using a computer (often with Monte-Carlo methods) and by recursively making the assumption 
+that a good partition for \(\WS (n+1)\) starts with a good partition for \(\WS (n)\) which is true for small
+values of \(n\). Therefore, one may wonder whether the limiting factor are the assumptions or the 
+methods used to search for partitions. It appears that the search space induced by these assumptions does 
+not contain the optimal partitions.
 
@@
 information is the maximum length of a sequence using only a certain subset of the colors. For instance,
-if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3. \\
+if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3.
+
+\subsection{Conclusion on the search space}
+As explained in the first subsection, the recursive assumption that a good partition for\(\WS (n+1)\) starts with a good partition for 
+\(\WS (n)\) appears to be wrong. Given that no extensive search for \(\WS(5)\) has been conducted without making this assumption and 
+that the size of the considered partitions is reasonable (the current lower bound is 196 and \(S(5) = 160\) was verified), it seems worth 
+investigating this special case further. In a spirit of orientating this search, we then give necessary conditions on an hypothetical partition 
+of \([\![1,197]\!]\) in 5 weakly sum-free subsets. Finding partitions that exceeds the lower bounds found with a computer (even if they 
+do not exceed those obtained with templates) which are not as regular as those obtained with templates would be extremely interesing 
+since it could designate a new search space for finding lower bounds with a computer.

### 2021-04-14 article/weakschur.tex
reorganisation sat / search space

@@
 \begin{remark}
-In the above ineqality, a "\(+1\)" can be added to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is odd in the theorem). However, it makes the proof less
-clear and it is never useful in practice.
+In the above ineqality, a "\(+1\)" can be added to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is 
+odd in the theorem). However, it makes the proof less clear and it is never useful in practice.
 \end{remark}
 
-We first give an intuitive explanation of the above theorem. Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
-subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\) and let's try to build a colouring of \([\![1, ap + q]\!]\)
-into \(n + k\) weakly sum-free subsets. Let \(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\). \\
+We give here an intuitive explanation of the above theorem; a formal proof can be found in the appendix. 
+Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
+subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\) 
+and let's try to build a colouring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let 
+\(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\).
 
@@
 
-In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem. \\
+In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem.
 
@@
 this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
-3.1)},we define \(\WS^+\) and find inequalities between \(\WS^+\),\(\WS\) and \(S\)
+3.1)}, we define \(\WS^+\) and find inequalities between \(\WS^+\),\(\WS\) and \(S\).
 \end{remark}
@@
 
-\textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
+\textsc{Proof:} Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
 We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
@@
 \\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
-\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{L}): f(x)=n-1+h(\lambda(x))\)
+\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
 \\\\
@@
 
-We have parted the integers of \(\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{L}\).
+We have parted the integers of \(\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{R}\).
 
@@
 
-\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{L}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{R}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
 \\Then, f(x)=f(y)=n. We distinguish two cases:
@@
 
-\underline{if (x,y) \(\in \mathcal{C} \times \mathcal{L} \), \(f(x)\neq f(y)\)}\\
+\underline{if (x,y) \(\in \mathcal{C} \times \mathcal{R} \), \(f(x)\neq f(y)\)}\\
 
-\underline{if (x,y) \(\in (\mathcal{L})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if (x,y) \(\in (\mathcal{R})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
 \\Let r(x)=\(\pi(x)-a\) and r(y)=\(\pi(y)-a\),
@@
 \\Hence \(f(x+y) <n\leqslant f(x)\)
-\item If \(r(x)+r(y)\leqslant b-a,\), \(\pi(x)+\pi(y)\leqslant b+a\)
+\item If \(r(x)+r(y) \leqslant b - a\), \(\pi(x)+\pi(y)\leqslant b+a\)
 \\Since g is sum-free for x\(>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
@@
 This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in the
-\hyperref[SAT]{SAT section}. \\
+\hyperref[SAT]{SAT section}.
 
 Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \). The best lower bound
-for each integer is highlighted.\\
-\\
+for each integer is highlighted.
+
 \begin{center}
@@
 Moreover, the third inequality gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
+
+\subsection{Conclusion on WSF-templates}
+
+In this section, we first gave a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott 
+and Hanson's construction for sum-free partitions. We then  introduced WSF-templates and generalized this construction. This 
+allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant difference 
+between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds 
+obtained with WSF-templates (including Rowley's two inequalities). In the next section, we try to analyze this phenomenon.

### 2021-04-15 article/state_of_the_art.tex
Texte

\section{State of the art}

Before Rowley, the best lower bounds were obtained thanks to a random
tree search. Indeed, the postulate stating that every good weakly sum-
free partition into \(n+1\) colours starts with a weakly sum-free
partition into \(n\) colors leads to a recursive method. However,
these values were improved by Rowley using a theoretical and explicit
construction for special cases. It's interesting to notice that before
that there were no theoretical approach such as Abott and Hanson's
\cite{AbottHanson} for weak Schur.

### 2021-04-15 article/weakschur.tex
correction mode math

@@
 
-Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\pi_{a,b}\) the projection:
-\[ \pi_{a,b}:x \longmapsto (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a}))\]
+Let \((a,b) \in (\mathbb{N}^*)^2\),\(a>b\), \(n \in \mathbb{N}^*\), we will define \(\pi_{a,b}\) the projection:
+\[ \pi_{a,b}:x \longmapsto (Id+a\mathbf{1}_{ [\![0,b]\!]})(x \mod a))\]
 \end{definition}
 
-We will note  the projection \(\pi\) and not \(\pi_{a,b}\) when there is no doubt about the a and b we use.
+We will note  the projection \(\pi\) and not \(\pi_{a,b}\) when there is no doubt about the \(a\) and \(b\) we use.
 
@@
 \begin{proposition}
-Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
+Let x \(\in [\![1,b]\!]\), let  \(y \in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
 \end{proposition}
 
-\textsc{Proof :}Let x \(\in [\![1,b]\!]\), let y \(\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)
+\textsc{Proof :}Let  \(x\in [\![1,b]\!]\), let  \(y\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)
 
@@
 \begin{align*}
- \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
+ \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+y \mod a)\\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a)\text{ since } \pi(y)\=y \mod a \\
 & =x+ \pi(y)
@@
 
-if \(x+\pi(y\geqslant a\):
+if \(x+\pi(y)\geqslant a\):
 \begin{align*}
- \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x+y mod a})\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\text{ mod a) since } \pi(y)\text{=y mod a} \\
+ \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+y \mod a)\\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a)\text{ since } \pi(y)=y \mod a \\
 & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
@@
 \begin{proposition}
-Let (x,y)\(\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
+Let \((x,y)\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
 \end{proposition}
 
-\textsc{Proof :}Let (x,y)\(\in (\mathbb{N}^*)^2\),
+\textsc{Proof :}Let \((x,y)\in (\mathbb{N}^*)^2\),
 
@@
  \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})((Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{x mod a})+(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{y mod a})\text{ mod a}) \\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ ((x mod a) + (y mod a)) mod a})\\
-& =(Id+a\mathbf{1}_{ [\![0,b]\!]})(\text{ x+y mod a})\\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})((Id+a\mathbf{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathbf{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
+& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
+& =(Id+a\mathbf{1}_{ [\![0,b]\!]})( x+y \mod a)\\
 & =\pi(x+y)
@@
 
-Let (a,b) \(n \in (\mathbb{N}^*)^2\),\(a>b\), we will define \(\lambda_{a,b}\) the projection:
+Let \((a,b) \in (\mathbb{N}^*)^2\), \(a>b\), let \(n \in\mathbb{N}\) we will define \(\lambda_{a,b}\) the projection:
 \[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
@@
 
-We will note  the projection \(\lambda\) and not \(\lambda_{a,b}\) when there is no doubt about the a and b we use.
+We will note  the projection \(\lambda\) and not \(\lambda_{a,b}\) when there is no doubt about the \(a\) and \(b\) we use.
 
@@
 \begin{proposition}
-Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
+Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
 \end{proposition}
-\textsc{Proof :}Let (a,b)\(\in (\mathbb{N}^*)^2\), \(a>b\), let x \(\in \mathbb{N}^*\),
-\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(\text{x mod a})+\mathbf{1}_{ [\![0,b]\!]}(\text{x mod a})\)
+\textsc{Proof :}Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\),
+\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(\text{x mod a})+\mathbf{1}_{ [\![0,b]\!]}(x \mod a)\)
 
-if x mod a \(>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+\text{x mod a}=x\)
+if \(x \mod a>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)
 
-if x mod a \(\leqslant b\):
+if \(x \mod a \leqslant b\):
 \(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)
@@
 \begin{definition}
-Let \( n \in \mathbb{N}^*\), we define \(\WS^+(n)\)=\(\max_{b\in \mathbb{N}^*} \{\WS_b^+(n)\}\)
+Let \( n \in \mathbb{N}^*\), we define \(\WS^+(n)=\max_{b\in \mathbb{N}^*} \{\WS_b^+(n)\}\)
 \end{definition}
@@
 Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \(k\)
-sum-free subsets of \([\![1,p]\!]\) and a partition of n subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
+sum-free subsets of \([\![1,p]\!]\) and a partition of \(n\) subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
 \(b\)-WSF of \(n\) colors and lenght \(q\),
@@
 \begin{proposition}
-Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a b-WSF-template of length \(p\) with \(k\) colors. Let
+Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a \(b\)-WSF-template of length \(p\) with \(k\) colors. Let
 \(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of
@@
 
-\textsc{Proof:} Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
+\textsc{Proof:} Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let \(a=q-b\). \\
 We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
 one associated to the partition of \([\![1,p]\!]\).
-\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
+\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a \(b\)-WSF-template.}
 \]
@@
 Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such that:
-\\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
+\\\\-if  \(x\leqslant b \text{ (we will note }x \in \mathcal{T}): f(x)=g(x)\)
 \\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
@@
 \\\\
-f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)
+\(f\) is well defined because \(\pi\) is defined for \(x>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because \(h(\lambda(x))\leqslant k\)
 
@@
 \\
-\underline{if (x,y) \(\in (\mathcal{T})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
-\\x+y\(<\)a+b since b\(<\)a and g(x)=f(x)=f(y)=g(y).
-\\Hence f(x+y)=g(x+y)\(\neq\)g(x)=f(x)
+\underline{if (x,y) \(\in (\mathcal{T})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\\\(x+y<a+b\) since \(b<a\) and \(g(x)=f(x)=f(y)=g(y)\).
+\\Hence \(f(x+y)=g(x+y)\neq g(x)=f(x)\)
 \\\\
-\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{C}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in \mathcal{T} \times \mathcal{C}\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
 We distinguish two cases:
@@
 \begin{itemize}
-\item If x+\(\pi(y)\leqslant a+b\)
-\\g(x)=f(x)=f(y)=g(\(\pi(y)\). Hence g(x)\(\neq g(x+\pi(y))=g(\pi(x+y))\) (qv previous proposition)
+\item If \(x+\pi(y)\leqslant a+b\)
+\\\(g(x)=f(x)=f(y)=g(\pi(y)\). Hence \(g(x)\neq g(x+\pi(y))=g(\pi(x+y))\) (qv previous proposition)
 \\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
 \\else, \(f(x+y)=g(\pi(x+y))\neq g(x)=f(x)\)
-\item If x+\(\pi(y)> a+b\), x+y\(>\)a+b and by definition of g, \(g(\pi(x+y))\neq g(x)\)
+\item If \(x+\pi(y)> a+b\), \(x+y>a+b\) and by definition of \(g\), \(g(\pi(x+y))\neq g(x)\)
 \\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
@@
 
-\underline{if (x,y) \(\in \mathcal{T} \times \mathcal{R}\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
-\\Then, f(x)=f(y)=n. We distinguish two cases:
+\underline{if \((x,y) \in \mathcal{T} \times \mathcal{R}\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\\Then, \(f(x)=f(y)=n\). We distinguish two cases:
 
@@
 \item If  \(\lambda(y)\neq \lambda(x+y)\), \(\lambda(y)+1= \lambda(x+y)\)\\
-n=f(y)=n-1+h(\(\lambda(y)\)). Hence h(\(\lambda(y)\))=1.
-\\Moreover h(1)=1, therefore \(h(\lambda(y)+1) \neq 1\)
+\(n=f(y)=n-1+h(\lambda(y))\). Hence \(h(\lambda(y))=1\).
+\\Moreover \(h(1)=1\), therefore \(h(\lambda(y)+1) \neq 1\)
 \\if \(\pi(x+y) \in A_n\), \(f(x+y)=n-1+h(\lambda(x+y))>n\)
@@
 
-\underline{if (x,y) \(\in (\mathcal{C})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in (\mathcal{C})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
 \\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases:
@@
 \\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
-\item If  \(\pi(x)+\pi(y)\leqslant q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) since g is sum-free for x\(>b\)
+\item If  \(\pi(x)+\pi(y)\leqslant q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) since \(g\) is sum-free for \(x>b\)
 \\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
@@
 
-\underline{if (x,y) \(\in \mathcal{C} \times \mathcal{R} \), \(f(x)\neq f(y)\)}\\
+\underline{if \((x,y) \in \mathcal{C} \times \mathcal{R} \), \(f(x)\neq f(y)\)}\\
 
-\underline{if (x,y) \(\in (\mathcal{R})^2\) such that f(x)=f(y), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
-\\Let r(x)=\(\pi(x)-a\) and r(y)=\(\pi(y)-a\),
+\underline{if \((x,y) \in (\mathcal{R})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\\Let \(r(x)=\pi(x)-a\) and \(r(y)=\pi(y)-a\),
 \\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
@@
 \item If \(r(x)+r(y)>b\), \(\pi(x)+\pi(y)>2a+b\)
-\\Since g is a b-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
+\\Since \(g\) is a \(b\)-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
 \\Therefore, \(g(\pi(x+y)) \neq n\) ie \(x+y \in \mathcal{C}\)
@@
 \item If \(r(x)+r(y) \leqslant b - a\), \(\pi(x)+\pi(y)\leqslant b+a\)
-\\Since g is sum-free for x\(>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
+\\Since \(g\) is sum-free for \(x>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
 \\Hence, \(f(x+y) <n\leqslant f(x)\)

### 2021-04-15 article/state_of_the_art.tex
Texte
tableau state

@@
 
-Before Rowley, the best lower bounds were obtained thanks to a random
-tree search. Indeed, the postulate stating that every good weakly sum-
-free partition into \(n+1\) colours starts with a weakly sum-free
-partition into \(n\) colors leads to a recursive method. However,
-these values were improved by Rowley using a theoretical and explicit
-construction for special cases. It's interesting to notice that before
-that there were no theoretical approach such as Abott and Hanson's
-\cite{AbottHanson} for weak Schur.
+\[
+\begin{array}{|*{13}{c|}}
+    \hline
+    k & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
+    \hline
+    S(n) & & & & & & & & & & & & \\
+    \text{old} & 1 & 4 & 13 & 44 & 160 \cite{Heule2017} & 536 \cite{Fredricksen} & 1680 \cite{Fredricksen} & 
+    5041 \cite{ELIAHOU2012175} & 15124 \cite{ELIAHOU2012175} & 51120 \cite{AbbottHanson} & 172216 \cite{AbbottHanson} & 
+    575664 \cite{AbbottHanson} \\
+    \text{Rowley} & & & & & & & & 5286 & 17694 & 60320 & 201696 & 631840 \\
+    \text{new} & & & & & & & & & 17803 & 60948 & 203828 & 638548 \\
+    \hline
+    WS(n) & & & & & & & & & & & & \\
+    \text{old} & 2 & 8 & 23 & 66 & 196 \cite{ELIAHOU2012175} & 582 \cite{EliahouBook} & 1740 \cite{Malgache} & 5201 \cite{Malgache} & 
+    15596 \cite{Malgache} & 51520 & 172216 & 575664 \\
+    \text{Rowley} & & & & & & 642 & 2146 & 6976 & 21848 & 70778 & 241282 & 806786 \\
+    \text{new} & & & & & & & & & 22536 & 71214 & 243794 & 815314 \\
+    \hline
+\end{array}
+\]

### 2021-04-15 article/state_of_the_art.tex

@@
 \]
+Before Rowley, the best lower bounds were obtained thanks to a random
+tree search. Indeed, the postulate stating that every good weakly sum-
+free partition into \(n+1\) colours starts with a weakly sum-free
+partition into \(n\) colors leads to a recursive method. However,
+these values were improved by Rowley using a theoretical and explicit
+construction for special cases. It's interesting to notice that before
+that there were no theoretical approach such as Abbott and Hanson's
+\cite{AbbottHanson} for weak Schur.

### 2021-04-15 article/schur.tex
relecture démonstration schur

@@
 \begin{proposition}
-Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a colouring associated to a SF-template of length \(p\) with \(k\) colors. Let 
-\(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a colouring \(g\) of \([\![1, b]\!]\) with \(k\) colors such that:
+Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a colouring associated to a SF-template of length \(p\) with \(k+1\) colors. Let 
+\(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a colouring \(g\) of \([\![1, b]\!]\) with \(k+1\) colors such that:
 \begin{itemize}
-	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in [\![1, p]\!]^2,(f(x) = f(y) \text{ and } (x + y) \mod p \leqslant b) 
+	\item \(\forall (x, y) \in [\![1, p]\!]^2,(f(x) = f(y) \text{ and } (x + y) \mod p \leqslant b) 
 	\implies g((x + y) \mod p) \neq f(x)\)
-	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in [\![1, p]\!] \times  [\![1, b]\!], (f(x) = g(y) \text{ and } x + y \leqslant b) 
+	\item \(\forall (x, y) \in [\![1, p]\!] \times  [\![1, b]\!], (f(x) = g(y) \text{ and } x + y \leqslant b) 
 	\implies g(x + y) \neq f(x)\)
@@
 \begin{itemize}
-\item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
+\item If \(u+v < p\), then \(x+y = (\alpha+\beta)p - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
 We have \(f(p-u) = f(p-v) \leqslant k\) and \(p-u + p-v > p\), the extra condition on \(f\) provides \(f(p-u-v) \neq
@@
 h(x)\).
-\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
-We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (p-u-v)) = f(p-u + p-v)\). Since \(f(p-u+p-v) \neq f(p-u)\),
+\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1)p - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
+We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (u+v-p)) = f(p-u + p-v)\). Since \(f(p-u+p-v) \neq f(p-u)\),
 we get \(h(x+y) \neq h(x)\).
@@
 \begin{itemize}
-\item If \(u+v < p\), then \(x+y = (\alpha+\beta) - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
+\item If \(u+v < p\), then \(x+y = (\alpha+\beta)p - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
 We assume \(h(x+y) > k\) otherwise the expected result is trivial.
@@
 thus \(h(x+y) = k + g(\alpha + \beta) \neq k + g(\alpha) = h(x)\).
-\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1) - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
+\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1)p - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
 Because of the assumption \(h(x) > k\), we necessarily have \(f(p-u) = k+1 = f(p-v)\). 

### 2021-04-15 article/introduction.tex
introduction

\section{Introduction}

We are interested in partioning the set of integers \(\{1, ..., p\}\) in \(n\) subsets such that there is no subset 
containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say the subsets are sum-free. If we 
add the hypothesis \(x \neq y\), we say the subsets are weakly sum-free. The greatest \(p\) for which a 
partition into \(n\) sum-free exists is called the \(n^{\text{th}}\) Schur number and is denoted \(S(n)\). 
\cite{Schur1917} Likewise for weakly sum-free partitions we define \(WS(n)\) the \(n^{\text{th}}\) weak Schur 
number. \cite{Irving1973} Only the first values of these sequences are known.

\par Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
previous generic construction for Schur numbers was given by Abott and Hanson \cite{AbottHanson} in 1972 
with a recursive construction. It gave the best lower bounds for all sufficiently large bounds. No equivalent 
was known for weak Schur numbers and as a result the best known partitions for large weak Schur numbers 
were actually sum-free partitions. As for smaller numbers, the best lower bounds were obtained by conducting 
a computer search. This search for weakly sum-free partitions relied on the recursive assumption that a good 
weakly sum-free partition into \(n+1\) colors starts with a good weakly sum-freepartition into \(n\) colors. In 
2020, Rowley introduced the notion of template for Schur and Ramsey numbers which generalizes Abott and 
Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also gives two 
inequalities for weak Schur numbers that yield significant improvements over previous lower bounds which 
besides are higher than the lower bounds on Schur numbers. \cite{RowleyWS}

\renewcommand{\arraystretch}{1.5}
\setlength{\tabcolsep}{2pt}

\begin{center}
\begin{tabular}{|*{13}{c|}}
    \hline
    \(k\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
    \hline
    \(S(n)\) & & & & & & & & & & & & \\
    old & 1 & 4 & 13 & 44 & 160 \cite{Heule2017} & 536 \cite{Fredricksen} & 1680 \cite{Fredricksen} & 5041 
    \cite{ELIAHOU2012175} & 15124 \cite{ELIAHOU2012175} & 51120 \cite{AbbottHanson} & 172216 
    \cite{AbbottHanson} & 575664 \cite{AbbottHanson} \\
    Rowley & & & & & & & & 5286 & 17694 & 60320 & 201696 & 631840 \\
    new & & & & & & & & & 17803 & 60948 & 203828 & 638548 \\
    \hline
    \(\WS(n)\) & & & & & & & & & & & & \\
    old & 2 & 8 & 23 & 66 & 196 \cite{ELIAHOU2012175} & 582 \cite{EliahouBook} & 1740 
    \cite{Rafilipojaona} & 5201 \cite{Rafilipojaona} & 15596 \cite{Rafilipojaona} & 51520 & 172216 & 575664 \\
    Rowley & & & & & & 642 & 2146 & 6976 & 21848 & 70778 & 241282 & 806786 \\
    new & & & & & & & & & 22536 & 71214 & 243794 & 815314 \\
    \hline
\end{tabular}
\end{center}

\par The main contribution of this article is a generalization of the concept of template to weak Schur numbers. 
This gives new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a 
special case an analogous for weak Schur numbers of Abott and Hanson's construction.

\par We first explain Rowley's template-based construction in the context of Schur numbers and then give 
new templates, thus providing new lowers bounds and inequalities as well as showing that the growth rates 
of both Schur and Ramsey numbers exceed 3.28. Then, we generalize the concept of templates to weak Schur 
numbers and provide new lower bounds for weak Schur numbers. Finally, we analyze the significant difference 
between new lower bounds obtain with templates and the former lower bounds obtained by computer search 
and we provide evidence that the main assumption made in those articles removes the optimal partitions from 
the search.

### 2021-04-15 article/state_of_the_art.tex

@@
     WS(n) & & & & & & & & & & & & \\
-    \text{old} & 2 & 8 & 23 & 66 & 196 \cite{ELIAHOU2012175} & 582 \cite{EliahouBook} & 1740 \cite{Malgache} & 5201 \cite{Malgache} & 
-    15596 \cite{Malgache} & 51520 & 172216 & 575664 \\
+    \text{old} & 2 & 8 & 23 & 66 & 196 \cite{ELIAHOU2012175} & 582 \cite{EliahouBook} & 1740 \cite{Rafilipojaona} & 5201 \cite{Rafilipojaona} & 
+    15596 \cite{Rafilipojaona} & 51520 & 172216 & 575664 \\
     \text{Rowley} & & & & & & 642 & 2146 & 6976 & 21848 & 70778 & 241282 & 806786 \\

### 2021-04-15 article/article.tex
reorganisation sat / search space
Bibliographie par ordre d'apparition
introduction
restructuration + indicatrice plus jolie

@@
 \usepackage{amssymb}
+\usepackage{dsfont}
 
@@
 This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by continuing on
-Rowley's "templates"-based approach for Ramsey and Schur numbers. Finding suitable templates allows us to apply Rowley's construction
-to get explicit partitions improving lower bounds as well as the growth rate of both Schur numbers and Ramsey numbers \(R_n(3)\).
+Rowley's "template"-based approach for Schur and Ramsey numbers. Finding suitable templates allows us to apply Rowley's construction
+to get explicit partitions improving lower bounds as well as the growth rate for both Schur numbers and Ramsey numbers \(R_n(3)\).
 We also developed a new method to improve lower bounds on weak Schur numbers. Furthermore, this paper tries to analyze former
@@
 
-\include{state_of_the_art.tex}
-
-\include{definitions_notations.tex}
+% \include{definitions_notations.tex}
 
@@
 
-\include{sat.tex}
+\include{search_space.tex}
 
@@
 
-\par
-These new results come from an extension of Rowley's template-based approach for Ramsey graphs and Schur numbers which is relatively new.
+\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and Schur numbers which is relatively new.
 Therefore, we would not be surprised if lower bounds are later improved using better templates. Moreover, studying specifically \(S^+(n)\) and
@@
 
-\par
-We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
+\qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
 us during the whole research and writing. Last but not least, we would like to address warm thanks
@@
 \bibliography{biblio}
-\bibliographystyle{plain}
+\bibliographystyle{ieeetr}
 

### 2021-04-15 article/introduction.tex
restructuration + indicatrice plus jolie

@@
 We are interested in partioning the set of integers \(\{1, ..., p\}\) in \(n\) subsets such that there is no subset 
-containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say the subsets are sum-free. If we 
+containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are sum-free. If we 
 add the hypothesis \(x \neq y\), we say the subsets are weakly sum-free. The greatest \(p\) for which a 
-partition into \(n\) sum-free exists is called the \(n^{\text{th}}\) Schur number and is denoted \(S(n)\). 
-\cite{Schur1917} Likewise for weakly sum-free partitions we define \(WS(n)\) the \(n^{\text{th}}\) weak Schur 
-number. \cite{Irving1973} Only the first values of these sequences are known.
+partition into \(n\) sum-free exists is called the \(n^{\text{th}}\) Schur number and is denoted \(S(n)\) 
+\cite{Schur1917}. Likewise for weakly sum-free partitions we define \(WS(n)\) the \(n^{\text{th}}\) weak Schur 
+number \cite{Irving1973}. Only the first values of these sequences are known. This article concerns the lower 
+bounds of these numbers.
 
 \par Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
-previous generic construction for Schur numbers was given by Abott and Hanson \cite{AbottHanson} in 1972 
+previous generic construction for Schur numbers was given by Abbott and Hanson \cite{AbbottHanson} in 1972 
 with a recursive construction. It gave the best lower bounds for all sufficiently large bounds. No equivalent 
 was known for weak Schur numbers and as a result the best known partitions for large weak Schur numbers 
-were actually sum-free partitions. As for smaller numbers, the best lower bounds were obtained by conducting 
-a computer search. This search for weakly sum-free partitions relied on the recursive assumption that a good 
-weakly sum-free partition into \(n+1\) colors starts with a good weakly sum-freepartition into \(n\) colors. In 
-2020, Rowley introduced the notion of template for Schur and Ramsey numbers which generalizes Abott and 
-Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also gives two 
-inequalities for weak Schur numbers that yield significant improvements over previous lower bounds which 
-besides are higher than the lower bounds on Schur numbers. \cite{RowleyWS}
+did not utilize the weakly sum-free hypothesis. As for smaller numbers, the best lower bounds were obtained 
+by conducting a computer search. This search for weakly sum-free partitions relied on the recursive assumption 
+that a good weakly sum-free partition into \(n+1\) colors starts with a good weakly sum-free partition into \(n\) 
+colors. In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers which generalizes 
+Abbott and Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also 
+gives two inequalities for weak Schur numbers that yield significant improvements over previous lower bounds 
+which besides do utilize the weakly sum-free hypothesis \cite{RowleyWS}.
 
 \renewcommand{\arraystretch}{1.5}
-\setlength{\tabcolsep}{2pt}
 
 \begin{center}
+
+\textbf{Table 1 - Comparison of lower bounds for Schur numbers}
+
 \begin{tabular}{|*{13}{c|}}
     \hline
-    \(k\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
+    \(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
     \hline
-    \(S(n)\) & & & & & & & & & & & & \\
-    old & 1 & 4 & 13 & 44 & 160 \cite{Heule2017} & 536 \cite{Fredricksen} & 1680 \cite{Fredricksen} & 5041 
-    \cite{ELIAHOU2012175} & 15124 \cite{ELIAHOU2012175} & 51120 \cite{AbbottHanson} & 172216 
-    \cite{AbbottHanson} & 575664 \cite{AbbottHanson} \\
+    old & 1 & 4 & 13 & 44 & 160 & 536 & 1680 & 5041 & 15124 & 51120 & 172216 & 575664 \\
+      & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{ELIAHOU2012175} & 
+    \cite{ELIAHOU2012175} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
+    \hline
     Rowley & & & & & & & & 5286 & 17694 & 60320 & 201696 & 631840 \\
+    \hline
     new & & & & & & & & & 17803 & 60948 & 203828 & 638548 \\
     \hline
-    \(\WS(n)\) & & & & & & & & & & & & \\
-    old & 2 & 8 & 23 & 66 & 196 \cite{ELIAHOU2012175} & 582 \cite{EliahouBook} & 1740 
-    \cite{Rafilipojaona} & 5201 \cite{Rafilipojaona} & 15596 \cite{Rafilipojaona} & 51520 & 172216 & 575664 \\
+\end{tabular}
+
+\vspace{3ex}
+\textbf{Table 2 - Comparison of lower bounds for weak Schur numbers}
+
+\begin{tabular}{|*{13}{c|}}
+    \hline
+    \(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
+    \hline
+    old & 2 & 8 & 23 & 66 & 196 & 582 & 1740 & 5201 & 15596 & 51520 & 172216 & 575664 \\
+      & & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
+    \cite{Rafilipojaona} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
+    \hline
     Rowley & & & & & & 642 & 2146 & 6976 & 21848 & 70778 & 241282 & 806786 \\
+    \hline
     new & & & & & & & & & 22536 & 71214 & 243794 & 815314 \\
@@
 \end{tabular}
+
 \end{center}
@@
 This gives new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a 
-special case an analogous for weak Schur numbers of Abott and Hanson's construction.
+special case an analogous for weak Schur numbers of Abbott and Hanson's construction.
 
@@
 new templates, thus providing new lowers bounds and inequalities as well as showing that the growth rates 
-of both Schur and Ramsey numbers exceed 3.28. Then, we generalize the concept of templates to weak Schur 
+for both Schur and Ramsey numbers exceed 3.28. Then, we generalize the concept of templates to weak Schur 
 numbers and provide new lower bounds for weak Schur numbers. Finally, we analyze the significant difference 
 between new lower bounds obtain with templates and the former lower bounds obtained by computer search 
-and we provide evidence that the main assumption made in those articles removes the optimal partitions from 
-the search.
+and we provide evidence which indicate that the main assumption made in those articles removes the optimal 
+partitions from the search space.
+
+\begin{notation}
+We denote by \([\![1,p]\!]\) the set of integers \(\{1, 2, ..., p\}\).
+\end{notation}
+
+\begin{notation}
+For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We 
+also denote \(m_i = \min(A_i)\).
+By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do not 
+make this hypothesis since we do not always consider partitions in which every subset plays a symmetric role.
+\end{notation}
+
+\begin{definition}
+We sometimes refer to a partitition as a colouring. The colouring associated to a partition \(A_1, ..., A_n\) of
+\([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition 
+associated to a colouring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
+\end{definition}

### 2021-04-15 article/schur.tex
restructuration + indicatrice plus jolie

@@
 method which generalizes Abbott and Hanson's  construction \cite{AbbottHanson}. Rowley named these partitions "templates", and 
-we will keep this name in the entire article. We find suitable templates and use them to find new lower bounds for Schur numbers.
+we will keep this name in the entire article. We find suitable templates and use them to provide new lower bounds for Schur numbers.
 
@@
 
-\subsection{Inequalities using \(S^+\)}
+\subsection{Construction of Schur partitions using SF-templates}
 
-The main result on \(S^+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(S^+\).
+\qquad The main result on SF-templates follows. It allows us to improve lower bounds on Schur numbers by finding 
+suitable SF-templates.
 
@@
 (see \cite{Schur1917}).
+
+\subsection{Conclusion on SF-templates}

### 2021-04-15 article/search_space.tex
restructuration + indicatrice plus jolie

@@
 
-In this section, we first provide evidence which indicates that the main assumption made by papers which
+\qquad In this section, we first provide evidence which indicate that the main assumption made by papers which
 found the previous best known lower bounds for weak Schur numbers using a computer may not be correct. 
@@
 \subsection{Former assumption appears to be wrong}
-Rowley's new lower bound for \(\WS (6)\) (642) \cite{RowleyWS} was a significant improvement upon
+
+\qquad Rowley's new lower bound for \(\WS (6)\) (642) \cite{RowleyWS} was a significant improvement upon
 the former best known lower bound (582) \cite{EliahouBook}. This previous lower bound has been found 
@@
 would be extremely interesting since it could give indications on a new search space for improving lower bounds with a
-computer. More generally,
-it questions the search space previously used for finding lower bounds for \(\WS (n)\) with a computer. In particular, to
-our knowledge every paper
-that found the lower bound \(\WS (5) \geqslant 196\) used this assumption. Therefore one may wonder
-if this actually a good lower
-bound. In the next subsection, we give properties that a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has
-to verify.
+computer.
+
+\par More generally, this theorem questions the search space previously used for finding lower bounds for \(\WS (n)\) 
+with a computer. In particular, to our knowledge every paper that found the lower bound \(\WS (5) \geqslant 196\) 
+used this assumption. Therefore one may wonder if this is actually a good lower bound. In the next subsection, we give 
+properties that a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has to verify.
 
 \subsection{Weak Schur number five}
-As explained in the previous subsection, the search space used for showing that \(\WS (5) \geqslant 196\) may not contain
+
+\qquad As explained in the previous subsection, the search space used for showing that \(\WS (5) \geqslant 196\) may not contain
 optimal solution. In this subsection,
@@
 \subsection{Conclusion on the search space}
-As explained in the first subsection, the recursive assumption that a good partition for\(\WS (n+1)\) starts with a good partition for 
+
+\qquad As explained in the first subsection, the recursive assumption that a good partition for\(\WS (n+1)\) starts with a good partition for 
 \(\WS (n)\) appears to be wrong. Given that no extensive search for \(\WS(5)\) has been conducted without making this assumption and 

### 2021-04-15 article/weakschur.tex
synthaxe
restructuration + indicatrice plus jolie

@@
 
-In this section, we generalize Rowley's constructions in \cite{RowleyWS}. We then introduce, by analogy with the third
-section, the
-integer \(\WS^+(n)\)
-to build suitable templates.
+\qquad In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
+for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
+we then introduce WSF-templates as well as the sequence \(\WS^+(n)\). We find suitable templates and use them to
+provide new lower bounds for weak Schur numbers.
 
@@
 
-Up to now, there was no equivalent for weak Schur numbers of Abott and Hanson's construction \cite{AbbottHanson}. Here
-we
-give a general lower bound for weak Schur numbers as a function of both regular and weak Schur numbers.
-The following theorem, inspired by Rowley's inequalities for \(\WS (n+1)\) and \(\WS (n+2)\), was found and proved
-by Romain Ageron.
+\qquad Up to now, there was no equivalent for weak Schur numbers of Abbott and Hanson's construction for Schur numbers
+\cite{AbbottHanson}. Here we give a general lower bound for weak Schur numbers as a function of both regular and
+weak Schur numbers. The following theorem, inspired by Rowley's inequalities for \(\WS (n+1)\) and \(\WS (n+2)\),
+was found and proved by Romain Ageron.
 
@@
 \begin{remark}
+This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\), this formula does not give
+new lower bounds.
+\end{remark}
+
+\begin{remark}
 In the above ineqality, a "\(+1\)" can be added to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
@@
 
-We give here an intuitive explanation of the above theorem; a formal proof can be found in the appendix. 
+Given that this theorem will appear as a particular case of a more general theorem after the introduction of
+templates for weak Schur numbers, we only give here an intuitive explanation of the above theorem; a formal
+proof can be found in the appendix.
+
 Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
@@
 is no \(x \in \tilde{\pi}(\mathcal{C})\) such that \(2x \in \tilde{\pi}(\mathcal{C})\) (so that we do not have a sum in \(\mathcal{C}\) when
-taking two numbers in the same column), the colours \(1, ..., n\) are sum-free. \\
+taking two numbers in the same column), the colours \(1, ..., n\) are sum-free.
 
-In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem.
-
-\begin{remark}
-This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\),
-this formula does not give new lower bounds but in the same way as we introduced \(S^+\)\hyperref[SE]{(Definition
-3.1)}, we define \(\WS^+\) and find inequalities between \(\WS^+\),\(\WS\) and \(S\).
-\end{remark}
+In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem.\\
+\par
+As in the previous section, we now introduce WSF-templates and the sequence \(\WS^+\) in order to generalize the above construction.
 
@@
 
-In this subsection, we define the objects and prove the results needed for the general theorem regarding templates for
-weak Schur numbers.
+\qquad In this subsection, we introduce WSF-templates and define the objects and prove the results needed
+for the general theorem regarding templates for weak Schur numbers.
 
@@
 Let \((a,b) \in (\mathbb{N}^*)^2\),\(a>b\), \(n \in \mathbb{N}^*\), we will define \(\pi_{a,b}\) the projection:
-\[ \pi_{a,b}:x \longmapsto (Id+a\mathbf{1}_{ [\![0,b]\!]})(x \mod a))\]
+\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a))\]
 \end{definition}
@@
 \begin{align*}
- \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+y \mod a)\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a)\text{ since } \pi(y)\=y \mod a \\
+ \pi(x+y) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)\\
+& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a)\text{ since } \pi(y)=y \mod a \\
 & =x+ \pi(y)
@@
 \begin{align*}
- \pi(x+y) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+y \mod a)\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a)\text{ since } \pi(y)=y \mod a \\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
-& = x+\pi(y) - a +a\mathbf{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
+ \pi(x+y) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)\\
+& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a)\text{ since } \pi(y)=y \mod a \\
+& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
+& = x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
 & = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
@@
 \begin{align*}
- \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathbf{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})((Id+a\mathbf{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathbf{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
-& = (Id+a\mathbf{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
-& =(Id+a\mathbf{1}_{ [\![0,b]\!]})( x+y \mod a)\\
+ \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
+& = (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
+& = (Id+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
+& =(Id+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
 & =\pi(x+y)
@@
 \textsc{Proof :}Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\),
-\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(\text{x mod a})+\mathbf{1}_{ [\![0,b]\!]}(x \mod a)\)
+\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+\mathds{1}_{ [\![0,b]\!]}(x \mod a)\)
 
@@
 if \(x \mod a \leqslant b\):
-\(a\lambda(x)+\pi(x)-a=a(\left\lfloor\dfrac{x}{a}\right\rfloor-1)+\text{x mod a}+a=x\)
+\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+\text{x mod a}+a=x\)
 
@@
 
-\subsection{Lower bound for Weak schur numbers using Schur and Weak Schur template numbers}
+We now proceed to state and prove the main result of this article.
+
+\subsection{Construction of weak Schur partitions using WSF-templates}
 
@@
 sum-free subsets of \([\![1,p]\!]\) and a partition of \(n\) subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
-\(b\)-WSF of \(n\) colors and lenght \(q\),
+\(b\)-WSF-template of \(n\) colors and lenght \(q\),
  then there exists a partition of \([\![1, b+p \times (q-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
@@
 \([\![b + 1, b + c]\!]\) with \(k\) colors such that:
+
 \begin{itemize}
@@
 \end{itemize}
+
 Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
@@
 
-Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such that:
-\\\\-if  \(x\leqslant b \text{ (we will note }x \in \mathcal{T}): f(x)=g(x)\)
-\\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
-\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
-\\\\
-\(f\) is well defined because \(\pi\) is defined for \(x>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because \(h(\lambda(x))\leqslant k\)
+Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) as follows:
 
-We have parted the integers of \(\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{R}\).
+\begin{itemize}
+\item if  \(x\leqslant b \text{ (we will note }x \in \mathcal{T}): f(x)=g(x)\)
+\item if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
+\item if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
+\end{itemize}
+
+\(f\) is well defined since \(\pi\) is defined for \(x>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because \(h(\lambda(x))\leqslant k\)
+
+We have parted the integers of \([\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{R}\).
 
@@
 \\
-\underline{if (x,y) \(\in (\mathcal{T})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in \mathcal{T}^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
 \\\(x+y<a+b\) since \(b<a\) and \(g(x)=f(x)=f(y)=g(y)\).
@@
 \\\(g(x)=g(\pi(y))=n \text{ since } g(y)=g(\pi(y))\)
-\\Therefore \(g(\pi(x+y))=g(x+\pi(y)) \neq g(x)=n\)(qv previous proposition)
+\\Therefore \(g(\pi(x+y))=g(x+\pi(y)) \neq g(x)=n\) (qv previous proposition)
 \\Hence \(f(x+y)=g(\pi(x+y))\neq n\)
@@
 
-\underline{if \((x,y) \in (\mathcal{C})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in \mathcal{C}^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
 \\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases:
@@
 \begin{align*}
- \\\text{if f(x+y)\(\geqslant\)n, }f(x+y) & =n-1+h(\lambda(x+y))\\
+ \\\text{if \(f(x+y) \geqslant n\), }f(x+y) & =n-1+h(\lambda(x+y))\\
 & =n-1+h(\lambda(x)+\lambda(y)) \\
@@
 \subsection{New lower bounds for Weak Schur numbers}
-Having found suitable templates, which can be found in the appendix, with a SAT solver, we claim that for all \(n \in
+
+\qquad Having found suitable templates, which can be found in the appendix, with a SAT solver, we claim that for all \(n \in
 \mathbb{N}^*\):
@@
 
-In this section, we first gave a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott 
+\qquad In this section, we first gave a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
 and Hanson's construction for sum-free partitions. We then  introduced WSF-templates and generalized this construction. This

### 2021-04-16 article/schur.tex
reorganisation de l'explication

@@
 \section{Schur numbers}
+\label{Schur}
 
-\qquad In this section, we use Rowley's constructions \cite{RowleyRamsey} in the context of Schur numbers. To improve lower bounds
-for Ramsay's numbers, Rowley introduces some sum-free partitions verifying some additional properties which can be extended using a 
-method which generalizes Abbott and Hanson's  construction \cite{AbbottHanson}. Rowley named these partitions "templates", and 
-we will keep this name in the entire article. We find suitable templates and use them to provide new lower bounds for Schur numbers.
+\qquad In this section, we use Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur 
+numbers. To improve lower bounds for Ramsay's numbers, Rowley introduces special sum-free partitions verifying 
+some additional properties which can be extended using a method generalizing Abbott and Hanson's construction 
+\cite{AbbottHanson}. Rowley named these partitions "templates", and we keep this name in the entire article. We 
+then find new templates and use them to provide new lower bounds for Schur numbers.
 
@@
 \begin{definition}
-We call SF-template of \(n\) colors and lenght \(p\) a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets \(A_1,
-A_2, ..., A_n\) which verify :
+A SF-template with length \(p\) and \(n\) colors is defined as a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets 
+\(A_1, A_2, ..., A_n\) verifying:
 \[
@@
 \]
-	We note \(S^+(n)\) the maximal lenght for a SF-template of \(n\) colors.
 \end{definition}
@@
 \begin{remark}
-	Here, \(n\) is the "special" color: it has less constraints than the other colors. However, please note that \(n\) 
+	Here \(n\) is the "special" color: it has less constraints than the other colors. However, please note that \(n\) 
 	is not necessarily the last color by order of appearance.
@@
 \begin{remark}
-	\(SF\)-templates include Abott and Hanson's construction \cite{AbbottHanson} as a special case.
+	\(SF\)-templates include Abbott and Hanson's construction \cite{AbbottHanson} as a special case.
 \end{remark}
@@
 \begin{proposition}
-	Let \(n \in [\![2, +\infty]\!]\). Then
+	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the maximal lenght of a SF-template with \(n\) colors. 
+	\(S^+(n)\) is well defined and verifies:
 	\[
@@
 
-\textsc{Proof :} The lower bound comes from Abott and Hanson's construction. The upper bound comes
-from the fact that a SF-template of length \(p\) with \(n\) colors is also a partition of
-\([\![1, p]\!]\) into \(n\) sum-free subsets.
+\textsc{Proof :} The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
+fact that a SF-template with length \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets.
 
@@
 
-\qquad The main result on SF-templates follows. It allows us to improve lower bounds on Schur numbers by finding 
-suitable SF-templates.
+\qquad Here we state the main result on SF-templates stated by Rowley in the context of Ramsey numbers. It consists 
+in the explicit construction of a sum-free partition using a SF-template and a sum-free partition.
 
 \begin{theorem}
-	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template of \(k+1\) colors and lenght \(p\),
-	and a partition of \(n\) sum-free subsets of \([\![1,q]\!]\) then there exists a partition of \(n+k\) sum-free subsets
-	of \([\![1,pq+m_{k+1}-1]\!]\). \(m_{k+1}\) is the minimum of the special subset in the \(SF\)-template.
+	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with lenght \(p\) and \(k+1\) colors 
+	and a partition of \([\![1,q]\!]\) into \(n\) sum-free subsets then there exists a partition of \([\![1,pq+m_{k+1}
+	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{k+1}\) is the minimum of the special subset in the \(SF\)-template.
 \end{theorem}
@@
 
-\begin{remark}
-The following proposition can help improve the additive constant of a SF-template. Although it does not allow us to improve the SF-templates 
-we have found, the analogous of this proposition for WSF-templates (see next section) allows us to improve one of them.
-\end{remark}
-
-\begin{proposition}
-Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a colouring associated to a SF-template of length \(p\) with \(k+1\) colors. Let 
-\(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a colouring \(g\) of \([\![1, b]\!]\) with \(k+1\) colors such that:
-\begin{itemize}
-	\item \(\forall (x, y) \in [\![1, p]\!]^2,(f(x) = f(y) \text{ and } (x + y) \mod p \leqslant b) 
-	\implies g((x + y) \mod p) \neq f(x)\)
-	\item \(\forall (x, y) \in [\![1, p]\!] \times  [\![1, b]\!], (f(x) = g(y) \text{ and } x + y \leqslant b) 
-	\implies g(x + y) \neq f(x)\)
-\end{itemize}
-Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n))\), we have\\
-\[ S(n+k) \geqslant S^+(k+1)S(n) + b\]
-\end{proposition}
-
-\begin{remark}
-This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
-column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
-intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the colouring of the last 
-row can be weakened.
-\end{remark}
-
-The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. 
-They extend vertically a sum-free partition, and horizontally an other sum-free partition. This way each "block" 
-acts like a security zone for the other one. Here, the horizontal partition is no longer to the side of the 
-vertical one, but it occupies the column of the special color of the \(SF\)-template, i.e the one without the 
-extra condition. We give the following example for \(p = 9, q = 4, n = 2 ~\textrm{and}~ k = 2\). \\
-
-This shows the inequality \(S(2+2) \geqslant S^+(3)S(2) + 4\). The special color is blue and is first used
-to color 5, hence \(4 = m_{3} - 1\). The special color is blue.
+The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. They vertically 
+extend a sum-free partition by repeating it and they use an other sum-free partition to color the other half according 
+to the line number. This way the "blocks" act as safe areas for each other. We give here an example for \(p = 9\), 
+\(q = 4\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott 
+and Hanson's construction and with a SF-template which is not of this type. In both cases, the special color is grey.
 
 \begin{center}
+\textbf{Abbott and Hanson's construction}
+\end{center}
+
 \[
 \begin{array}{|*{9}{c|}}
-	\multicolumn{9}{c}{\overset{S^+(3)}{\overbrace{\rule{6cm}{0pt}}}} \\
 	\hline
-	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9 \\
+	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{cyan} 5 & 
+	\cellcolor{cyan} 6 & \cellcolor{cyan} 7 & \cellcolor{cyan} 8 & \cellcolor{cyan} 9\\
 	\hline
-	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
+	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & 
+	\cellcolor{yellow} 15 & \cellcolor{yellow} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
 	\hline
-	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
+	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & 
+	\cellcolor{yellow} 24 & \cellcolor{yellow} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
 	\hline
-	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{red} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36\\
+	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{cyan} 32 & 
+	\cellcolor{cyan} 33 & \cellcolor{cyan} 34 & \cellcolor{cyan} 35 & \cellcolor{cyan} 36 \\
 	\hline
@@
 \]
+
+\begin{center}
+\begin{tabular}{c c}
+	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
+	\begin{tabular}{|*{9}{c|}}
+		\hline 
+		\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{gray!40} 5 & 
+		\cellcolor{gray!40} 6 & \cellcolor{gray!40} 7 & \cellcolor{gray!40} 8 & \cellcolor{gray!40} 9 \\
+		\hline
+	\end{tabular} &
+	\begin{tabular}{|*{4}{c|}}
+		\hline 
+		\cellcolor{cyan} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{cyan} 4 \\
+		\hline
+	\end{tabular}
+\end{tabular}
 \end{center}
 
+In the general construction with SF-templates, the special color no longer necessarily contains consecutive 
+numbers. However, the special color is still replaced by the colors of the sum-free partition according to the 
+line number and the other colors are still vertically extended.
+
 \begin{center}
+\textbf{SF-template construction}
+\end{center}
+
 \[
-S^+(3) 
 \begin{array}{|*{9}{c|}}
 	\hline
-	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{red} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
+	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{cyan} 5 & 
+	\cellcolor{cyan} 6 & \cellcolor{red} 7 & \cellcolor{cyan} 8 & \cellcolor{cyan} 9\\
 	\hline
-\end{array}  \]
-\[
-S(2) 
-\begin{array}{|*{4}{c|}}
+	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & 
+	\cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
 	\hline
-	\cellcolor{blue} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{blue} 4 \\
+	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & 
+	\cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
 	\hline
-\end{array}
-\]
-\end{center}
-
-To comparison, here is an usual Abbott and Hanson partition : \(S(2+2) \geqslant S(2)(2S(2)+1)+S(2) \). 
-\begin{center}
-\[
-\begin{array}{|*{9}{c|}}
-	\multicolumn{4}{c}{\overset{S(2)}{\overbrace{\rule{2.6cm}{0pt}}}} \\
-	\hline
-	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{blue} 5 & \cellcolor{blue} 6 & \cellcolor{blue} 7 & \cellcolor{blue} 8 & \cellcolor{blue} 9\\
-	\hline
-	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & \cellcolor{yellow} 15 & \cellcolor{yellow} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
-	\hline
-	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & \cellcolor{yellow} 24 & \cellcolor{yellow} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
-	\hline
-	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{blue} 32 & \cellcolor{blue} 33 & \cellcolor{blue} 34 & \cellcolor{blue} 35 & \cellcolor{blue} 36 \\
+	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{cyan} 32 & 
+	\cellcolor{cyan} 33 & \cellcolor{red} 34 & \cellcolor{cyan} 35 & \cellcolor{cyan} 36 \\
 	\hline
@@
 \]
+
+\begin{center}
+\begin{tabular}{c c}
+	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
+	\begin{tabular}{|*{9}{c|}}
+		\hline 
+		\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{gray!40} 5 & 
+		\cellcolor{gray!40} 6 & \cellcolor{red} 7 & \cellcolor{gray!40} 8 & \cellcolor{gray!40} 9 \\
+		\hline
+	\end{tabular} &
+	\begin{tabular}{|*{4}{c|}}
+		\hline 
+		\cellcolor{cyan} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{cyan} 4 \\
+		\hline
+	\end{tabular}
+\end{tabular}
 \end{center}
 
-\textsc{Proof of theorem:} We denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\)
+We know proceed to prove the above mentioned theorem.\\
+
+\textsc{Proof:} We denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\)
 and \(g\) the one associated to the sum-free partition of \([\![1,q]\!]\).
@@
 
+\begin{remark}
+The following proposition can help improve the additive constant of a SF-template. Although it does not allow us to 
+improve the SF-templates we have found, the analogous of this proposition for WSF-templates (see next section) 
+allows us to improve one of them.
+\end{remark}
+
+\begin{proposition}
+Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a colouring associated to a SF-template of length \(p\) with \(k+1\) 
+colors. Let \(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a colouring \(g\) of 
+\([\![1, b]\!]\) with \(k+1\) colors such that:
+
+\begin{itemize}
+	\item \(\forall (x, y) \in [\![1, p]\!]^2,(f(x) = f(y) \text{ and } (x + y) \mod p \leqslant b) 
+	\implies g((x + y) \mod p) \neq f(x)\)
+	\item \(\forall (x, y) \in [\![1, p]\!] \times  [\![1, b]\!], (f(x) = g(y) \text{ and } x + y \leqslant b) 
+	\implies g(x + y) \neq f(x)\)
+\end{itemize}
+
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n))\), we have
+\[ S(n+k) \geqslant S^+(k+1)S(n) + b\]
+\end{proposition}
+
+\begin{remark}
+This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
+column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
+intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the colouring of the last 
+row can be weakened.
+\end{remark}
+
 \begin{definition}
@@
 bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n
-=8\) and \(n = 13\) were obtained thanks to the first one, found by Rowley. The best lower bounds are highlighted.\\
-\\
+=8\) and \(n = 13\) were obtained thanks to the first one, found by Rowley. The best lower bounds are highlighted.
+
 \begin{center}

### 2021-04-16 article/article.tex
amelioration introduction

@@
 \usepackage[table]{xcolor}
+\usepackage{multirow}
 \usepackage[a4paper, total={6in, 8in}]{geometry}
@@
 
-This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by continuing on
-Rowley's "template"-based approach for Schur and Ramsey numbers. Finding suitable templates allows us to apply Rowley's construction
-to get explicit partitions improving lower bounds as well as the growth rate for both Schur numbers and Ramsey numbers \(R_n(3)\).
-We also developed a new method to improve lower bounds on weak Schur numbers. Furthermore, this paper tries to analyze former
-works on the subject based on the principle that good partitions into \(n+1\) subsets start with good partitions
-into \(n\) subsets. We show that exceeding the previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption upon
-imposing certain conditions on the good 5-subsets partition. The new lower bounds include \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\),
+This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
+continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. Finding templates allows us to 
+apply Rowley's construction and to get explicit partitions improving lower bounds as well as the growth rate for 
+both Schur numbers and Ramsey numbers \(R_n(3)\). We also developed a new method to improve lower bounds on 
+weak Schur numbers. Furthermore, this paper tries to analyze former works on the subject based on the principle 
+that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding the 
+previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption upon imposing certain conditions 
+on the good 5-subsets partition. The new lower bounds include \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\),
 \(\WS (9) \geqslant 22536 \) and \(\WS (10) \geqslant 71214 \).
@@
 
-\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and Schur numbers which is relatively new.
-Therefore, we would not be surprised if lower bounds are later improved using better templates. Moreover, studying specifically \(S^+(n)\) and
-\(\WS^+(n)\) might be of interest as they are closely related to Schur and weak Schur numbers.
+\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
+Schur numbers which is relatively new. Therefore, we would not be surprised if lower bounds are later improved 
+using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
+ are closely related to Schur and weak Schur numbers.
 
 \par
-The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak Schur numbers. The assumption behind it
-might have removed the optimal partitions from the search space and thus lowered the highest value that can be reached within it.
-However, algorithms based on randomness such as Monte-Carlo algorithms may prove to be very useful if used in a search space with more
-potential. For instance, such an algorithm could be used to find better templates and improve inequalities and lower bounds for high values
-of \(n\). This could be the subject of a future work.
+The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak 
+Schur numbers. The assumption behind it might have removed the optimal partitions from the search space and thus 
+lowered the highest value that can be reached within it. However, algorithms based on randomness such as 
+Monte-Carlo algorithms may prove to be very useful if used in a search space with more potential. For instance, such 
+an algorithm could be used to find better templates and improve inequalities and lower bounds for high values of \(n\). 
+This could be the subject of a future work.
 

### 2021-04-16 article/introduction.tex
amelioration introduction

@@
 
-We are interested in partioning the set of integers \(\{1, ..., p\}\) in \(n\) subsets such that there is no subset 
-containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are sum-free. If we 
-add the hypothesis \(x \neq y\), we say the subsets are weakly sum-free. The greatest \(p\) for which a 
-partition into \(n\) sum-free exists is called the \(n^{\text{th}}\) Schur number and is denoted \(S(n)\) 
-\cite{Schur1917}. Likewise for weakly sum-free partitions we define \(WS(n)\) the \(n^{\text{th}}\) weak Schur 
-number \cite{Irving1973}. Only the first values of these sequences are known. This article concerns the lower 
-bounds of these numbers.
+\qquad We are interested in partioning the set of integers \(\{1, ..., p\}\) in \(n\) subsets such that there is no 
+subset containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are 
+\textit{sum-free}. If we add the hypothesis \(x \neq y\), we say the subsets are \textit{weakly sum-free}. The 
+greatest \(p\) for which there exists a partition into \(n\) sum-free subsets is called the \(n^{\text{th}}\) Schur 
+number and is denoted \(S(n)\) \cite{Schur1917}. Likewise for weakly sum-free partitions we define \(\WS(n)\) 
+the \(n^{\text{th}}\) weak Schur number \cite{Irving1973}. Only the first values of these sequences are known. 
+This article focuses on the lower bounds for these numbers.
 
-\par Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
+\par
+Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
 previous generic construction for Schur numbers was given by Abbott and Hanson \cite{AbbottHanson} in 1972 
-with a recursive construction. It gave the best lower bounds for all sufficiently large bounds. No equivalent 
+with a recursive construction. It used to give the best lower bounds for all sufficiently large numbers. No equivalent 
 was known for weak Schur numbers and as a result the best known partitions for large weak Schur numbers 
@@
 Abbott and Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also 
-gives two inequalities for weak Schur numbers that yield significant improvements over previous lower bounds 
-which besides do utilize the weakly sum-free hypothesis \cite{RowleyWS}.
+gives two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements over previous 
+lower bounds which besides do utilize the \textit{weakly} sum-free hypothesis.
 
-\renewcommand{\arraystretch}{1.5}
+\renewcommand{\arraystretch}{1.2}
 
@@
     \hline
-    old & 1 & 4 & 13 & 44 & 160 & 536 & 1680 & 5041 & 15124 & 51120 & 172216 & 575664 \\
+    \multirow{2}{*}{old} & 1 & 4 & 13 & 44 & 160 & 536 & 1680 & 5041 & 15124 & 51120 & 172216 & 575664 \\
       & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{ELIAHOU2012175} & 
@@
     \hline
-    Rowley & & & & & & & & 5286 & 17694 & 60320 & 201696 & 631840 \\
+    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyRamsey}\end{tabular} & & & & & & & & 5286 & 17694 & 
+    60320 & 201696 & 631840 \\
     \hline
-    new & & & & & & & & & 17803 & 60948 & 203828 & 638548 \\
+    \hyperref[Schur]{new}  & & & & & & & & & 17803 & 60948 & 203828 & 638548 \\
     \hline
@@
 \vspace{3ex}
+\setlength{\tabcolsep}{4pt}
+
 \textbf{Table 2 - Comparison of lower bounds for weak Schur numbers}
@@
     \hline
-    old & 2 & 8 & 23 & 66 & 196 & 582 & 1740 & 5201 & 15596 & 51520 & 172216 & 575664 \\
+    \multirow{2}{*}{old} & 2 & 8 & 23 & 66 & 196 & 582 & 1740 & 5201 & 15596 & 51520 & 172216 & 575664 \\
       & & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
@@
     \hline
-    Rowley & & & & & & 642 & 2146 & 6976 & 21848 & 70778 & 241282 & 806786 \\
+    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyWS}\end{tabular} & & & & & & 642 & 2146 & 6976 & 21848 
+    & 70778 & 241282 & 806786 \\
     \hline
-    new & & & & & & & & & 22536 & 71214 & 243794 & 815314 \\
+    \hyperref[WeakSchur]{new} & & & & & & & & & 22536 & 71214 & 243794 & 815314 \\
+    \hline
+    \(\displaystyle \frac{\text{new} - \text{old}}{\text{old}}\) & 0\% & 0\% & 0\% & 0\% & 0\% & 10.3\% & 
+    23.3\% & 34.1\% 
+    & 44.5\% & 38.2\% & 41.6\% & 41.6\% \\
     \hline
@@
 
-\par The main contribution of this article is a generalization of the concept of template to weak Schur numbers. 
+\par
+The main contribution of this article is a generalization of the concept of template to weak Schur numbers. 
 This gives new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a 
-special case an analogous for weak Schur numbers of Abbott and Hanson's construction.
+special case an analogous for weak Schur numbers of Abbott and Hanson's construction for Schur numbers.
 
-\par We first explain Rowley's template-based construction in the context of Schur numbers and then give 
+\par
+We first explain Rowley's template-based construction in the context of Schur numbers and then give 
 new templates, thus providing new lowers bounds and inequalities as well as showing that the growth rates 
-for both Schur and Ramsey numbers exceed 3.28. Then, we generalize the concept of templates to weak Schur 
-numbers and provide new lower bounds for weak Schur numbers. Finally, we analyze the significant difference 
-between new lower bounds obtain with templates and the former lower bounds obtained by computer search 
-and we provide evidence which indicate that the main assumption made in those articles removes the optimal 
-partitions from the search space.
+for both Schur and Ramsey numbers \(R_n(3)\) exceed 3.28.
+
+\par
+We then  generalize the concept of templates to weak Schur numbers and provide new lower bounds for weak 
+Schur numbers.
+
+\par
+Finally, we analyze the significant difference between new lower bounds obtain with templates and the former 
+lower bounds obtained by computer search and we provide evidence which indicate that the main assumption 
+made in those articles removes the optimal partitions from the search space.
+
+\par
+We now introduce notations and definitions we use throughout this article.
 
@@
 \begin{definition}
-We sometimes refer to a partitition as a colouring. The colouring associated to a partition \(A_1, ..., A_n\) of
+A partitition is sometimes referred to as a colouring. The colouring associated to a partition \(A_1, ..., A_n\) of
 \([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition 

### 2021-04-16 article/schur.tex
environnement proof -> \begin{proof}[\textsc{Proof.}]

@@
 
-\textsc{Proof :} The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
+\begin{proof}[\textsc{Proof.}]
+The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
 fact that a SF-template with length \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets.
+\end{proof}
 
@@
 
-We know proceed to prove the above mentioned theorem.\\
+We now proceed to prove the above mentioned theorem.\\
 
-\textsc{Proof:} We denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\)
+\begin{proof}[\textsc{Proof.}]
+We denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\)
 and \(g\) the one associated to the sum-free partition of \([\![1,q]\!]\).
@@
 \end{itemize}
+\end{proof}
 
-\begin{remark}
 The following proposition can help improve the additive constant of a SF-template. Although it does not allow us to 
@@
 allows us to improve one of them.
-\end{remark}
 
@@
 
-\textsc{Proof :} The idea is the same as in the previous theorem. The only difference is the \(SF\) property inherited 
-from the second \(SF\)-template.
+\begin{proof}[\textsc{Proof.}]
+The idea is the same as in the previous theorem. The only difference is the SF property inherited 
+from the second SF-template.
+\end{proof}
 

### 2021-04-16 article/weakschur.tex
amelioration introduction
environnement proof -> \begin{proof}[\textsc{Proof.}]

@@
 \section{Weak Schur numbers}
+\label{WeakSchur}
 
@@
 
-\textsc{Proof :}Let  \(x\in [\![1,b]\!]\), let  \(y\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)
+\begin{proof}[\textsc{Proof.}]
+Let  \(x\in [\![1,b]\!]\), let  \(y\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)
 
@@
 \end{align*}
+\end{proof}
 
@@
 
-\textsc{Proof :}Let \((x,y)\in (\mathbb{N}^*)^2\),
+\begin{proof}[\textsc{Proof.}]
+Let \((x,y)\in (\mathbb{N}^*)^2\),
 
@@
 \end{proposition}
-\textsc{Proof :}Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\),
-\\\\ \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+\mathds{1}_{ [\![0,b]\!]}(x \mod a)\)
+\begin{proof}[\textsc{Proof.}]
+Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\),\\
+\(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+\mathds{1}_{ [\![0,b]\!]}(x \mod a)\)
 
@@
 \(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+\text{x mod a}+a=x\)
+\end{proof}
 
@@
 
-\textsc{Proof :} The lower bound comes from the analogous of Abott and Hanson's construction for weak Schur numbers.
+\begin{proof}[\textsc{Proof.}]
+The lower bound comes from the analogous of Abott and Hanson's construction for weak Schur numbers.
 The upper bound comes from the fact that a WSF-template of length \(p\) with \(n\) colors is also a partition of
 \([\![1, p]\!]\) into \(n\) sum-free subsets.
+\end{proof}
 
@@
 
-\textsc{Proof:} Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let \(a=q-b\). \\
+\begin{proof}[\textsc{Proof.}]
+Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let \(a=q-b\). \\
 We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
@@
 \\else, \(f(x+y)=g(\pi(x+y))=g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))=f(x)\)
-
 \end{itemize}
@@
 \end{itemize}
+\end{proof}
 
@@
 
-\textsc{Proof :} The idea is the same as in the previous theorem. The only difference is the \(SF\) property inherited
-from the second \(SF\)-template.
+\begin{proof}[\textsc{Proof.}]
+The idea is the same as in the previous theorem. The only difference is the WSF property inherited
+from the WSF-template.
+\end{proof}
 

### 2021-04-16 article/introduction.tex
reorganisation

@@
 \par
-Finally, we analyze the significant difference between new lower bounds obtain with templates and the former 
+Finally, we analyze the significant difference between new lower bounds obtained with templates and the former 
 lower bounds obtained by computer search and we provide evidence which indicate that the main assumption 
@@
 \begin{definition}
-A partitition is sometimes referred to as a colouring. The colouring associated to a partition \(A_1, ..., A_n\) of
+A partitition is sometimes referred to as a coloring. The coloring associated to a partition \(A_1, ..., A_n\) of
 \([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition 
-associated to a colouring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
+associated to a coloring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
 \end{definition}

### 2021-04-16 article/schur.tex
reorganisation

@@
 \qquad In this section, we use Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur 
-numbers. To improve lower bounds for Ramsay's numbers, Rowley introduces special sum-free partitions verifying 
-some additional properties which can be extended using a method generalizing Abbott and Hanson's construction 
-\cite{AbbottHanson}. Rowley named these partitions "templates", and we keep this name in the entire article. We 
-then find new templates and use them to provide new lower bounds for Schur numbers.
+numbers. In order to improve lower bounds for Schur and Ramsey numbers, Rowley introduces special sum-free 
+partitions verifying some additional properties which can be extended using a method generalizing Abbott and 
+Hanson's construction \cite{AbbottHanson}. Rowley named these partitions "templates", and we keep this name in 
+the entire article. We then find new templates and use them to provide new lower bounds for Schur numbers.
 
@@
 
-\begin{definition}
-A SF-template with \(n\) colors is said to be symmetric if the partition in \(n\) sum-free subsets derived (with the additive constant) from this template is symmetric. 
-A sum-free partition \(A_1, ..., A_n\) of \([\![1, p]\!]\) is said to be symmetric if for all \( x \in [\![1, p]\!]\), \(x\) and \(p + 1 - x\) belong to the same subset 
-(except if \(x = p + 1 - x\)).
-\end{definition}
-
-Using a SAT solver, we exhibited SF-templates, hence providing lower bound on \(S^+\) and inequalities 
-of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
-\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5, in order to reduce the search space we 
-looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
-the \(m_c\)'s out of being too small. Further details about the encoding as a SAT problem can be found in the
-\hyperref[SAT]{SAT section}. \\
-
-Here are the best inequalities on Schur numbers so far (the templates corresponding to the third, fourth and fifth 
-inequalities can be found in the appendix):
-\[ S(n+1) \geqslant 3S(n) + 1 \]
-\[ S(n+2) \geqslant 9S(n) + 4 \]
-\[ S(n+3) \geqslant 33S(n) + 6 \]
-\[ S(n+4) \geqslant 111S(n) + 43 \]
-\[ S(n+5) \geqslant 380S(n) + 148 \]
-\[ S(n+6) \geqslant 1140S(n) + 528 \]
-
-The first inequality comes from the original Schur's paper \cite{Schur1917}. The second one is due to
-Abott \cite{AbbottHanson}
-and the third one to Rowley \cite{RowleyRamsey}. The other ones are new. \\
-
-The first 3 inequalities are optimal. The fourth one is optimal among symmetric SF-templates whose special color is 
-the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
-likely not optimal but should not be too far from the optimal SF-template. 
-Finally, the sixth one is obtained by combining (see below) the SF-template of length 380 and the one of length 3. 
-Although we could not find a better SF-template with 7 colors, the last inequality is definetely very far from the 
-optimal value. One may try to seek better templates by constraining less the search space and by using 
-Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.\\
-
-We also have a similar theorem where only \(S^+\) is involved.
+We also have a similar construction theorem where only \(S^+\) is involved.
 
@@
 
+\begin{definition}
+A SF-template with \(n\) colors is said to be symmetric if the partition in \(n\) sum-free subsets derived (with the additive constant) from this template is symmetric. 
+A sum-free partition \(A_1, ..., A_n\) of \([\![1, p]\!]\) is said to be symmetric if for all \( x \in [\![1, p]\!]\), \(x\) and \(p + 1 - x\) belong to the same subset 
+(except if \(x = p + 1 - x\)).
+\end{definition}
+
+Using a SAT solver, we exhibited SF-templates, hence providing lower bound on \(S^+\) and inequalities 
+of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
+\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5, in order to reduce the search space we 
+looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
+the \(m_c\)'s out of being too small. Further details about the encoding as a SAT problem can be found in \cite{Heule2017}.
+
+\par
+Here are the best inequalities on Schur numbers so far (the templates corresponding to the third, fourth and fifth 
+inequalities can be found in the appendix):
+\[ S(n+1) \geqslant 3S(n) + 1 \]
+\[ S(n+2) \geqslant 9S(n) + 4 \]
+\[ S(n+3) \geqslant 33S(n) + 6 \]
+\[ S(n+4) \geqslant 111S(n) + 43 \]
+\[ S(n+5) \geqslant 380S(n) + 148 \]
+\[ S(n+6) \geqslant 1140S(n) + 528 \]
+
+The first inequality comes from  Schur's original article\cite{Schur1917}. The second one is due to
+Abott \cite{AbbottHanson}
+and the third one to Rowley \cite{RowleyRamsey}. The other ones are new.
+
+\par
+The first 3 inequalities are optimal. The fourth one is optimal among symmetric SF-templates whose special color is 
+the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
+likely not optimal but should not be too far from the optimal. 
+Finally, the sixth one is obtained by combining (see below) the SF-template of length 380 and the one of length 3. 
+Although we could not find a better SF-template with 7 colors, the last inequality is definetely very far from the 
+optimal value. One may try to seek better templates by constraining less the search space and by using 
+Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.
+
+\par
 The previous inequalities give new lower bounds for \(S(n)\) for
@@
 \end{center}
+
 Except for 8, 9 and 13, the best lower bounds are obtained thanks to
@@
 \end{corollary}
-\textsc{Proof :} It is a mere consequence of the inequality \( S(n+5) \geqslant 380S(n) + 148\). As for Ramsey's
-numbers growth rate, a lower bound can be found using Schur's one, thanks to \(S(n) \leqslant R_n(3)-2 \)
-(see \cite{Schur1917}).
+
+\begin{proof}[\textsc{Proof.}]
+It is a mere consequence of the inequality \( S(n+5) \geqslant 380S(n) + 148\). As for Ramsey
+numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}).
+\end{proof}
 

### 2021-04-16 article/weakschur.tex
reorganisation

@@
 \begin{align*}
- \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y)\text{ mod a})\\
+ \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
 & = (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
@@
 \begin{remark}
-In the following theorem, \(\lambda\) is the function which maps an element x to its line number, as mentioned in the intuitive explanation.
+In the following theorem, \(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.
 \end{remark}
@@
 \begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } let ~ b_{max}=max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\},\) \[
-\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}\]
+For every \((n,k) \in (\mathbb{N}^*)^2\), define \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\). 
+Then the following inequality holds.
+\[\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}\]
 \end{corollary}
@@
 In the SF-template construction for Schur numbers, the additive constant comes from the fact that the special color does
-not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_max\) can actually be replaced by \\
+not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by \\
 \[\max \left\{ b + \min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}\]
 \end{remark}
-
-\begin{remark}
-Acutally, like for SF-templates, the additive constant of a WSF-template (in the form given by the above remark) can be improved
-by weakening the hypotheses made on the last row. The principle behind it is the same as in the analogous proposition for SF-templates.
-\end{remark}
-
-\begin{proposition}
-Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a \(b\)-WSF-template of length \(p\) with \(k\) colors. Let
-\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of
-\([\![b + 1, b + c]\!]\) with \(k\) colors such that:
-
-\begin{itemize}
-	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c)
-	\implies g(\pi(x + y)) \neq f(x)\)
-	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c)
-\implies g(\pi(x + y)) \neq f(x)\)
-\end{itemize}
-
-Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
-\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
-\end{proposition}
 
@@
 \begin{remark}
-The WSF-templates can actually be fine-tuned further. However, it gives only minor improvements (most likely only additive
-constant) at the cost of dramatically increasing the size of the search space while. Therefore, it does not seem relevant to
+Acutally, like for SF-templates, the additive constant of a WSF-template can be improved by weakening the hypotheses made on 
+the last row. The principle behind it is the same as in the analogous proposition for SF-templates. 
+\end{remark}
+
+\begin{proposition}
+Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a \(b\)-WSF-template of length \(p\) with \(k\) colors. Let
+\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of
+\([\![b + 1, b + c]\!]\) with \(k\) colors such that:
+
+\begin{itemize}
+	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c)
+	\implies g(\pi(x + y)) \neq f(x)\)
+	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c)
+\implies g(\pi(x + y)) \neq f(x)\)
+\end{itemize}
+
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
+\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
+\end{proposition}
+
+\begin{remark}
+The WSF-templates can actually be fine-tuned further. However, it gives only minor improvements (most likely only an additive
+constant) at the cost of dramatically increasing the size of the search space. Therefore, it does not seem relevant to
 use this sophistications given that we could not even find good WSF-templates with 5 colors using a computer (here good
@@
 
-\par To sum up, one can look for a generalised WSF-template that uses a special colouring for the tail and the first row, a
+\par
+To sum up, one can look for a generalised WSF-template that uses a special colouring for the tail and the first row, a
 colouring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a colouring for all
@@
 with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}.
-This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in the
-\hyperref[SAT]{SAT section}.
+This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in \cite{Heule2017}.
 

### 2021-04-17 article/schur.tex
conclusion schur

@@
 \subsection{Conclusion on SF-templates}
+In this section, we first formalized the Rowley's template-based constructions \cite{RowleyRamsey} by introducing SF-templates.
+In order to formalize the construction, we then defined a new number, \(S^+\), and demonstrated a relation between \(S^+\) and \(S\).
+We found lower bounds for \(S^+\) and that allowed us to obtain new lower bounds for schur numbers.
+One may notice that we only get lower bounds of \(S^+\) and as a result it should be possible to find a better templates by constraining less the search space.
+In the next section, we will introduce \(WS^+\) and deduce a relation that improve lower bounds for weak-schur numbers by analogy with this section.

### 2021-04-18 article/weakschur.tex
Suppression de quelques environnements remarque

@@
 
-\begin{remark}
-This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers.
-\end{remark}
+This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers. This formula includes
+the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\), this formula does not give new lower bounds.
 
 \begin{remark}
-This formula includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\), this formula does not give
-new lower bounds.
-\end{remark}
-
-\begin{remark}
-In the above ineqality, a "\(+1\)" can be added to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
+The above inequality can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
 odd in the theorem). However, it makes the proof less clear and it is never useful in practice.
@@
 
-\begin{remark}
 \(\pi\) is the projection on the first line mentioned in the intuitive explanation.
-\end{remark}
 
@@
 
-\begin{remark}
 In the following theorem, \(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.
-\end{remark}
 
@@
 
-\begin{remark}
 Please note that the special color \(n\) is not necessarily the last color by order of appearance.
-\end{remark}
 
@@
 
-\begin{corollary}
 The general lower bound for weak Schur numbers in function of both regular and weak Schur numbers can be seen as a particular
-case of WSF-template in the same way Abott and Hanson's construction can be seen as a particular case of SF-template.
-\end{corollary}
-
-\begin{remark}
-Acutally, like for SF-templates, the additive constant of a WSF-template can be improved by weakening the hypotheses made on 
+case of WSF-template in the same way Abott and Hanson's construction can be seen as a particular case of SF-template. Acutally,
+like for SF-templates, the additive constant of a WSF-template can be improved by weakening the hypotheses made on 
 the last row. The principle behind it is the same as in the analogous proposition for SF-templates.
-\end{remark}
 
@@
 
-\begin{remark}
 The WSF-templates can actually be fine-tuned further. However, it gives only minor improvements (most likely only an additive
@@
 constant of WSF-templates).
-\end{remark}
 

### 2021-04-18 article/article.tex
environnement proof -> \begin{proof}[\textsc{Proof.}]
introduction + notations / definitions

@@
 \usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{dsfont}
@@
 \usepackage[a4paper, total={6in, 8in}]{geometry}
+
+\renewcommand{\qedsymbol}{\(\square\)}
 
@@
 
-% \include{definitions_notations.tex}
+\include{definitions_notations.tex}
 
@@
 using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
- are closely related to Schur and weak Schur numbers.
+ are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
+randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.
 
@@
 Schur numbers. The assumption behind it might have removed the optimal partitions from the search space and thus 
-lowered the highest value that can be reached within it. However, algorithms based on randomness such as 
-Monte-Carlo algorithms may prove to be very useful if used in a search space with more potential. For instance, such 
-an algorithm could be used to find better templates and improve inequalities and lower bounds for high values of \(n\). 
-This could be the subject of a future work.
+lowered the highest value that can be reached within it. However, the methods used to explore this search space 
+are efficient as the optimum was found. Thereby Monte-Carlo algorithms may prove to be very useful if used in a 
+search space with more potential. Finding a weakly sum-free partition which is better than previous lower bounds 
+and which is not as regular as those obtained with templates would be extremely interesting (even if it does not 
+improve current lower bounds) since it could suggest a new search space which could then be explored with the 
+above mentioned methods.
 

### 2021-04-18 article/introduction.tex
pourcents schur
introduction + notations / definitions

@@
 
-\par
-Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
+\subsection{State of the art}
+
+\qquad Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
 previous generic construction for Schur numbers was given by Abbott and Hanson \cite{AbbottHanson} in 1972 
@@
 was known for weak Schur numbers and as a result the best known partitions for large weak Schur numbers 
-did not utilize the weakly sum-free hypothesis. As for smaller numbers, the best lower bounds were obtained 
-by conducting a computer search. This search for weakly sum-free partitions relied on the recursive assumption 
-that a good weakly sum-free partition into \(n+1\) colors starts with a good weakly sum-free partition into \(n\) 
-colors. In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers which generalizes 
-Abbott and Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also 
-gives two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements over previous 
-lower bounds which besides do utilize the \textit{weakly} sum-free hypothesis.
+did not utilize the weakly sum-free hypothesis.
+
+\par
+As for smaller numbers, the best lower bounds were obtained by conducting a computer search. This search for 
+weakly sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) 
+colors starts with a good weakly sum-free partition into \(n\) colors.
+
+\par
+In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers which generalizes Abbott and 
+Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also gives two 
+inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements over previous lower 
+bounds which besides do utilize the \textit{weakly} sum-free hypothesis.
 
@@
 
+\subsection{Sutructure of this article}
+
 \par
@@
 We now introduce notations and definitions we use throughout this article.
-
-\begin{notation}
-We denote by \([\![1,p]\!]\) the set of integers \(\{1, 2, ..., p\}\).
-\end{notation}
-
-\begin{notation}
-For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We 
-also denote \(m_i = \min(A_i)\).
-By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do not 
-make this hypothesis since we do not always consider partitions in which every subset plays a symmetric role.
-\end{notation}
-
-\begin{definition}
-A partitition is sometimes referred to as a coloring. The coloring associated to a partition \(A_1, ..., A_n\) of
-\([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition 
-associated to a coloring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
-\end{definition}

### 2021-04-18 article/schur.tex
Suppression de quelques environnements remarque

@@
 
-\begin{remark}
 Here \(n\) is the "special" color: it has less constraints than the other colors. However, please note that \(n\) 
-	is not necessarily the last color by order of appearance.
-\end{remark}
-
-\begin{remark}
-	\(SF\)-templates include Abbott and Hanson's construction \cite{AbbottHanson} as a special case.
-\end{remark}
+is not necessarily the last color by order of appearance. \(SF\)-templates include Abbott and Hanson's construction \cite{AbbottHanson}
+as a special case.
 
@@
 
-\begin{remark}
 This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
@@
 row can be weakened.
-\end{remark}
 

### 2021-04-18 article/weakschur.tex
modification saut de ligne

@@
 \begin{align*}
- \\\pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
+ \pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
 & = (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
@@
 \\
-\underline{if \((x,y) \in \mathcal{T}^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in \mathcal{T}^2\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
 \\\(x+y<a+b\) since \(b<a\) and \(g(x)=f(x)=f(y)=g(y)\).
@@
 \\\\
-\underline{if \((x,y) \in \mathcal{T} \times \mathcal{C}\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in \mathcal{T} \times \mathcal{C}\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
 We distinguish two cases:
@@
 
-\underline{if \((x,y) \in \mathcal{T} \times \mathcal{R}\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in \mathcal{T} \times \mathcal{R}\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
 \\Then, \(f(x)=f(y)=n\). We distinguish two cases:
@@
 
-\underline{if \((x,y) \in \mathcal{C}^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in \mathcal{C}^2\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
 \\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases:
@@
 
-\underline{if \((x,y) \in (\mathcal{R})^2\) such that \(f(x)=f(y)\), \(x \neq y\), then \(f(x+y)\neq f(x)\)  :}\\
+\underline{if \((x,y) \in (\mathcal{R})^2\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
 \\Let \(r(x)=\pi(x)-a\) and \(r(y)=\pi(y)-a\),
@@
 \begin{align*}
- \\\lambda(x+y) & =1+\left\lfloor\dfrac{a(\lambda(x)+\lambda(y))+r(x)+r(y)-b-1}{a}\right\rfloor+1\\
+ \lambda(x+y) & =1+\left\lfloor\dfrac{a(\lambda(x)+\lambda(y))+r(x)+r(y)-b-1}{a}\right\rfloor+1\\
 & = \lambda(x)+\lambda(y)+\left\lfloor\dfrac{r(x)+r(y)-b-1}{a}\right\rfloor+1 \\
@@
 \begin{align*}
- \\\text{if \(f(x+y) \geqslant n\), }f(x+y) & =n-1+h(\lambda(x+y))\\
+ \text{if \(f(x+y) \geqslant n\), }f(x+y) & =n-1+h(\lambda(x+y))\\
 & =n-1+h(\lambda(x)+\lambda(y)) \\

### 2021-04-18 article/schur.tex
modif conclusion partie schur

--- 2021-04-16 article/schur.tex
@@
 \begin{corollary}
-The growth rate for Schur numbers (and Ramsey numbers \(R_n(3)\))  satisfies \(\gamma \geqslant \sqrt[5]{380} \approx 3.28 \).
+The growth rate for Schur numbers (and Ramsey numbers \(R_n(3)\))  satisfies \(\gamma \geqslant \sqrt[5]{380} \approx 3.28\).
 \end{corollary}
@@
 \subsection{Conclusion on SF-templates}
+
+\qquad In this section, we first formalized Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur numbers 
+by introducing SF-templates as well as a new sequence, \(S^+\). We provided relations between \(S^+\) and \(S\) then 
+stated Rowley's construction method in the context of Schur numbers. We found new SF-templates allowing us to obtain 
+new lower bounds for schur numbers. One may notice that we mostly gave only lower bounds for \(S^+\). It should be possible to 
+find better SF-templates by making different assumptions or using a different method (Monte-Carlo methods for instance).
+
+\par
+In the next section, we provide similar results for weak Schur numbers. We introduce WSF-templates and a corresponding sequence, 
+\(WS^+\). We then derive similar relations and construction method allowing us to find new lower bounds for weak Schur numbers.

### 2021-04-18 article/definitions_notations.tex
notations

@@
 Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free
-subsets. Given \(p\) and \(n\) two integers, we are interested in partitioning the set of integers from 1 to \(p\) into
-\(n\) (weakly) sum-free subsets.
+subsets. Given \(p\) and \(n\) two integers, we are interested in partitioning the set of integers \(\{1, 2, ..., p\}\), 
+denoted by \([\![1,p]\!]\), into \(n\) (weakly) sum-free subsets.
 
-\begin{notation}
-We denote by \([\![1,p]\!]\) the set of integers \(\{1, 2, ..., p\}\).
-\end{notation}
-
+\par
 Schur proved in \cite{Schur1917} that given a number of subsets \(n\), there exists a value of \(p\)
@@
 
-\begin{notation}
-For a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We also denote
-\(m_i = \min(A_i)\).
-By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do not make this
-hypothesis since we
-do not always consider partitions in which every subset plays a symmetric role.
-\end{notation}
+Given a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We also denote
+\(m_i = \min(A_i)\). By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do 
+not make this hypothesis since we do not always consider partitions in which every subset plays a symmetric role.
 
 \begin{definition}
-We sometimes refer to a partitition as a colouring. The colouring associated to a partition \(A_1, ..., A_n\) of
+We sometimes refer to a partitition as a coloring. The coloring associated to a partition \(A_1, ..., A_n\) of
 \([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition associated to
-a colouring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
+a coloring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
 \end{definition}

### 2021-04-18 article/introduction.tex
tableau moins large
notations

@@
 \renewcommand{\arraystretch}{1.2}
+\setlength{\tabcolsep}{4pt}
 
@@
     \hline
+    \(\displaystyle \frac{\text{new} - \text{old}}{\text{old}}\) & 0\% & 0\% & 0\% & 0\% & 0\% & 0\% & 
+    0\% & 0\%
+     & 17.7\% & 19.2\% & 18.4\% & 11.0\% \\
+    \hline
 \end{tabular}
@@
 \vspace{3ex}
-\setlength{\tabcolsep}{4pt}
 
@@
     \(\displaystyle \frac{\text{new} - \text{old}}{\text{old}}\) & 0\% & 0\% & 0\% & 0\% & 0\% & 10.3\% & 
-    23.3\% & 34.1\% 
-    & 44.5\% & 38.2\% & 41.6\% & 41.6\% \\
+    23.3\% & 34.1\% & 44.5\% & 38.2\% & 41.6\% & 41.6\% \\
     \hline
@@
 
-\subsection{Sutructure of this article}
+\subsection{Structure of this article}
 
@@
 We now introduce notations and definitions we use throughout this article.
+
+\subsection{Definitions and notations}
+
+We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.
+
+\begin{definition}
+A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} when:
+\[ \forall (a,b) \in A^2 \text{, } a+b \notin A\]
+\end{definition}
+
+\begin{definition}
+A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} when:
+\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B\]
+\end{definition}
+
+Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free
+subsets. Given \(p\) and \(n\) two integers, we are interested in partitioning the set of integers \(\{1, 2, ..., p\}\), 
+denoted by \([\![1,p]\!]\), into \(n\) (weakly) sum-free subsets.
+
+\par
+Schur proved in \cite{Schur1917} that given a number of subsets \(n\), there exists a value of \(p\)
+such that there exists no partition of \([\![1,q]\!]\) into \(n\) sum-free subsets for any \(q \geqslant p\). A similar
+property holds for weakly sum-free subsets (reference necessaire). These observations lead to the following definitions.
+
+\begin{definition}
+Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we denote \(S(n)\) (\textit{resp. \(\WS (n)\)}) such that
+\([\![1,S(n)]\!]\) (resp. \([\![1, \WS (n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
+subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(\WS (n)\) the
+\(n\)\textsuperscript{th} weak
+Schur number}.
+\end{definition}
+
+Given a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We also denote
+\(m_i = \min(A_i)\). By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do 
+not make this hypothesis since we do not always consider partitions in which every subset plays a symmetric role.
+
+\begin{definition}
+We sometimes refer to a partitition as a coloring. The coloring associated to a partition \(A_1, ..., A_n\) of
+\([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition associated to
+a coloring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
+\end{definition}

### 2021-05-01 article/weakschur.tex
rien
quelques typo

@@
 Let \((a,b) \in (\mathbb{N}^*)^2\),\(a>b\), \(n \in \mathbb{N}^*\), we will define \(\pi_{a,b}\) the projection:
-\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a))\]
+\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
 \end{definition}
@@
 & = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
-& = x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
+& = x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]}(x+\pi(y) - a) \\
 & = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
@@
 Let \((x,y)\in (\mathbb{N}^*)^2\),
-
 \begin{align*}
  \pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
-& = (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
+& = (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a)\mod a) \\
 & = (Id+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
@@
 
-In the following theorem, \(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.
+In the following theorem, \(\lambda\) is the function which maps an element \(x\) to its line number as mentioned in the intuitive explanation.
 
@@
 if \(x \mod a \leqslant b\):
-\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+\text{x mod a}+a=x\)
+\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+(x \mod a)+a=x\)
 \end{proof}
@@
 \item if  \(x\leqslant b \text{ (we will note }x \in \mathcal{T}): f(x)=g(x)\)
-\item if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
-\item if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
+\item if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n (\text{ we will note } x \in \mathcal{C}): f(x)=g(\pi(x))\)
+\item if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n (\text{ we will note } x \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
 \end{itemize}

### 2021-05-02 article/schur.tex
modfis demos

@@
 \begin{proof}[\textsc{Proof.}]
-We denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\)
-and \(g\) the one associated to the sum-free partition of \([\![1,q]\!]\).
+Denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\) and \(g\) the one associated 
+to the sum-free partition of \([\![1,q]\!]\); where \(f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!]\) and 
+\(g : [\![1,q]\!] \longrightarrow [\![1,n]\!]\).
 
-\[ f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!] \text{ and } \forall (x,y) \in [\![1,p]\!]^2, \left\{
+\par
+The sum-free condition is expressed as
+\[\forall (x,y) \in [\![1,p]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)\]
+\[\forall (x,y) \in [\![1,q]\!]^2 \text{, } g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)\]
+
+The additionnal constraint for the SF-template is
+\[
+\forall (x,y) \in [\![1,p]\!]^2, \left\{
 \begin{array}{ll}
@@
 \end{array}
-\right.
-\Longrightarrow f(x+y-p) \neq f(x)
-\]
-with also the sum-free condition : \[ \forall (x,y) \in [\![1,p]\!]^2 \text{, } f(x) = f(y)
-\Longrightarrow f(x+y) \neq f(x) \]
-Moreover, by definition of \(m_{k+1}\), if \(x < m_{k+1}\), \(f(x) \leqslant k\).
-
-\[g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } g(x) = g(y)
-\Longrightarrow g(x+y) \neq g(x)
+\right. \Longrightarrow f(x+y-p) \neq f(x)
 \]
 
-We now define \(h : [\![1,pq+m_{k+1}-1]\!] \longrightarrow [\![1,n+k]\!] \) as follows :
-\( \forall x \in [\![1,pq + m_{k+1}-1]\!] \), we write \(x = \alpha p - u\) where \(\alpha \in [\![1,q+1]\!] \) and \( u \in
-[\![0,p-1]\!] \).
-This decomposition if of course unique. \\
+For \(x \in [\![1,pq+m_{k+1}-1]\!]\), write \(x = (\alpha - 1) + u\) for some integers \(\alpha \in \mathbb{Z}\) and 
+\(u \in [\![1,p]\!]\). This decomposition is of course unique. \(\alpha\) (resp. \(u\)) can be interpreted as the row 
+(resp. column) number of \(x\). Define a new coloring \(h\) as follows
+\[
+\begin{array}{c c c l}
+	h : & [\![1,pq+m_{k+1}-1]\!] & \longrightarrow & [\![1,n+k]\!] \\
+	& x & \longmapsto & 
+	\left\{ \begin{array}{l l}
+		f(u) & \text{if}~f(u) \leqslant k \\
+		k + g(\alpha) & \text{if}~f(u) = k + 1 \\
+	\end{array} \right.
+\end{array}
+\]
 
-If \(f(p-u) \leqslant k\), we set \(h(x) = f(p-u)\), else (i.e \(f(p-u) = k + 1)\) \(h(x) = k + g(\alpha) \). \\
-If \(\alpha = q+1\), we have a problem plugging it into \(g\). Hopefully, this issue never arises : if 
-\(\alpha = q+1\), we have \(u > p - m_{k+1}\) since \(x \in [\![1,pq + m_{k+1}-1]\!]\), hence \(p-u < m_{k+1}\) and \(f(p-u) \leqslant k\). \\
+\(h\) is well-defined since, by definition of \(m_{k+1}\), \(\forall x \in [\![p q + 1, p q + m_{k + 1} - 1 ]\!], f(u) 
+\leqslant k\) and therefore \(\forall x \in [\![1,pq+m_{k+1}-1]\!], f(u) = k + 1 \implies \alpha \in [\![1, q]\!]\).
 
-Prooving that the partition of \([\![1,pq]\!]\) induced by \(h\) is sum-free will complete the proof.\\
+\par
+We now prove that \(h\) is a sum-free coloring. Let \(x,y \in [\![1,pq + m_{k+1}-1]\!]\) such that \(h(x) = h(y)\) 
+and \(x+y \leqslant pq+m_{k+1}-1\). We claim that \(h(x+y) \neq h(x)\). Write \(x = (\alpha - 1) p + u\) and 
+\(y = (\beta - 1) p + v\) where \(\alpha, \beta \in \mathbb{Z}\) and \(u, v \in [\![1,p]\!]\). Distinguish between 
+two cases according to the value of \(h(x)\). \\
 
-Let \(x,y \in [\![1,pq + m_{k+1}-1]\!]\), with \(h(x) = h(y)\) and \(x+y \leqslant pq+m_{k+1}-1\). We write \(x = \alpha p - u\) and \(y =
-\beta p - v\). We simply need \(h(x+y) \neq h(x)\). \\
+\noindent \underline{\textbf{First case:} \(h(x) \leqslant k\)} \\
+\qquad Assume that \(h(x+y) \leqslant k\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of \(h\) 
+and given that \(h(u) = h(v)\), \(f(u) = f(v)\). Distinguish between two cases according to the value of \(x + y\).
 
-We first examine the case where \(h(x) \leqslant k\). We assume \(h(x+y) \leqslant k\), otherwise we are fine. 
-Thus by definition of \(h\), we have \(h(x) = f(p-u) = f(p-v) = h(y)\).
 \begin{itemize}
-\item If \(u+v < p\), then \(x+y = (\alpha+\beta)p - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
-We have \(f(p-u) = f(p-v) \leqslant k\) and \(p-u + p-v > p\), the extra condition on \(f\) provides \(f(p-u-v) \neq
-f(p-u)\).
-We assumed \(h(x+y) \leqslant k\) hence \(h(x+y) = f(p-u-v)\). Since \(h(x) = f(p-u)\), we have at last \(h(x+y) \neq
-h(x)\).
-\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1)p - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
-We assumed \(h(x+y) \leqslant k \) hence \(h(x+y) = f( p- (u+v-p)) = f(p-u + p-v)\). Since \(f(p-u+p-v) \neq f(p-u)\),
-we get \(h(x+y) \neq h(x)\).
+\item If \(u + v > p\), write \(w = u + v - p \in [\![1, p]\!]\). Then \(x + y = (\alpha + \beta - 1) p + w\). By definition, 
+	\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant k\), the additionnal constraint on \(f\) implies \(f(w) 
+	\neq f(u)\), that is \(h(x + y) \neq h(x)\).
+\item If \(u + v \leqslant p\), write \(w = u + v \in [\![1, p]\!]\). Then \(x+y = (\alpha + \beta- 2) p + w\). By definition, 
+	\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant k\), the sum-free property of \(f\) implies \(f(w) \neq f(u)\), 
+	that is \(h(x + y) \neq h(x)\).
 \end{itemize}
 
-We now assume \(h(x) > k\). Then \(h(x) = k + g(\alpha) = k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). 
-We have the two same cases as before.
+\noindent \underline{\textbf{Second case:} \(h(x) \geqslant k + 1\)} \\
+\qquad \(h(x) = k + g(\alpha) = 
+k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As in the first case, distinguish between two cases according 
+to the value of \(x + y\).
 
 \begin{itemize}
-\item If \(u+v < p\), then \(x+y = (\alpha+\beta)p - (u+v) \) with \(u+v \in [\![0,p-1]\!] \).
-We assume \(h(x+y) > k\) otherwise the expected result is trivial.
-Since \(g(\alpha) = g(\beta)\), the sum-free condition garanties \(g(\alpha) \neq g(\alpha+\beta)\), 
-thus \(h(x+y) = k + g(\alpha + \beta) \neq k + g(\alpha) = h(x)\).
-\item If \(u+v \geqslant p\), then \(x+y = (\alpha+\beta-1)p - (u+v-p) \) with \(u+v-p \in [\![0,p-1]\!] \).
-Because of the assumption \(h(x) > k\), we necessarily have \(f(p-u) = k+1 = f(p-v)\). 
-Then \(f(p-(u+v-p)) = f(p-u + p-v) \leqslant k \) with the sum-free condition on \(f\), 
-hence \(h(x+y) = f(p-(u+v-p)) \) by construction of \(h\). Thus \(h(x+y) \leqslant k < h(x)\).
+\item If \(u + v > p\), write \(w = u + v - p \in [\![1, p]\!]\). Then \(x + y = (\alpha + \beta - 1) p + w\). Assume that 
+	\(h(x+y) \geqslant k + 1\),  otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition, \(h(x + y) = k + g(\alpha + 
+	\beta)\). Given that \(g(\alpha) = g(\beta)\), the sum-free property of \(g\) implies \(g(\alpha + \beta) 
+	\neq g(\alpha)\) that is \(h(x + y) \neq h(x)\).
+\item  If \(u + v \leqslant p\), write \(w = u + v \in [\![1, p]\!]\). Then \(x+y = (\alpha + \beta- 2) p + w\). The sum-free 
+	property of \(f\) implies \(f(w) \neq f(u)\). Therefore \(f(w) \leqslant k\) and thus \(h(x + y) \leqslant k\). In particular,
+	given that \(h(x) \geqslant k + 1\), \(h(x + y) \neq h(x)\).
 \end{itemize}
@@
 inequalities can be found in the appendix):
-\[ S(n+1) \geqslant 3S(n) + 1 \]
-\[ S(n+2) \geqslant 9S(n) + 4 \]
-\[ S(n+3) \geqslant 33S(n) + 6 \]
-\[ S(n+4) \geqslant 111S(n) + 43 \]
-\[ S(n+5) \geqslant 380S(n) + 148 \]
-\[ S(n+6) \geqslant 1140S(n) + 528 \]
+\[
+\begin{array}{r r r r r}
+	S(n + 1) & \geqslant & 3 S(n) & + & 1 \\
+	S(n + 2) & \geqslant & 9 S(n) & + & 4 \\
+	S(n + 3) & \geqslant & 33 S(n) & + & 6 \\
+	S(n + 4) & \geqslant & 111 S(n) & + & 43 \\
+	S(n + 5) & \geqslant & 380 S(n) & + & 148 \\
+	S(n + 6) & \geqslant & 1140 S(n) & + & 528 \\
+\end{array}
+\]
 

### 2021-05-02 article/weakschur.tex
modfis demos

--- 2021-04-18 article/weakschur.tex
@@
 \begin{corollary}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } \WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \frac{\WS (n)}{2}
+\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } \WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \displaystyle \frac{\WS (n)}{2}
 \right \rceil +1 \right) + \WS (n)\)
@@
 
-Like for SF-templates, \(\mathcal{R}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with
+Like SF-templates, \(\mathcal{R}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with
 this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the
@@
 \renewcommand{\arraystretch}{2}
-\begin{center}
 \[
@@
 \]
-\end{center}
+\renewcommand{\arraystretch}{1}
 
@@
 
-In particular, taking \(w = l = \lceil \frac{q}{2} \rceil\) and \(r = \lfloor \frac{q}{2} \rfloor\) works, thus obtaining the above theorem.\\
+In particular, taking \(w = l = \lceil \displaystyle \frac{q}{2} \rceil\) and \(r = \lfloor \displaystyle \frac{q}{2} \rfloor\) works, thus obtaining the above theorem.\\
 \par
@@
 \qquad In this subsection, we introduce WSF-templates and define the objects and prove the results needed
-for the general theorem regarding templates for weak Schur numbers.
+for the general theorem on templates for weak Schur numbers.
 
@@
 
-Let \((a,b) \in (\mathbb{N}^*)^2\),\(a>b\), \(n \in \mathbb{N}^*\), we will define \(\pi_{a,b}\) the projection:
+Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
 \[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a))\]
@@
 
-We will note  the projection \(\pi\) and not \(\pi_{a,b}\) when there is no doubt about the \(a\) and \(b\) we use.
+If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\).
 
@@
 \begin{proposition}
-Let x \(\in [\![1,b]\!]\), let  \(y \in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\), then we have: \(\pi(x+y)=x+\pi(y)\)
+Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\) such that \(x+\pi(y) \leqslant a+b\). Then \(\pi(x+y)=x+\pi(y)\).
 \end{proposition}
@@
 \begin{proof}[\textsc{Proof.}]
-Let  \(x\in [\![1,b]\!]\), let  \(y\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\)
+Let  \(x\in [\![1,b]\!]\), and  \(y\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\).
 
-if \(x+\pi(y)< a:\)we remark that \(\pi(y)>b\) and therefore \(x+\pi(y)>b\):
+\noindent if \(x+\pi(y)< a \):
 
-\begin{align*}
- \pi(x+y) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)\\
-& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a)\text{ since } \pi(y)=y \mod a \\
-& =x+ \pi(y)
-\end{align*}
+\[
+\begin{array}{c c l l}
+	\pi(x+y) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a) & \\
+	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a) & \text{since } \pi(y)=y \mod a \\
+	& = & x+ \pi(y) & 
+\end{array}
+\]
 
-if \(x+\pi(y)\geqslant a\):
-\begin{align*}
- \pi(x+y) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)\\
-& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a)\text{ since } \pi(y)=y \mod a \\
-& = (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
-& = x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) \\
-& = x+\pi(y) - a +a \text{ \quad since } x+\pi(y) - a \in [\![0,b]\!] \\
-& = x+\pi(y)
-\end{align*}
+\noindent if \(x+\pi(y)\geqslant a\):
+\[
+\begin{array}{c c l l}
+	\pi(x+y) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)& \\
+	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a) & \text{since } \pi(y)=y \mod a \\
+	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) & \\
+	& = & x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]}(x+\pi(y) - a) & \\
+	& = & x+\pi(y) - a +a & \text{since } x+\pi(y) - a \in [\![0,b]\!] \\
+	& = & x+\pi(y) &
+\end{array}
+\]
 \end{proof}
@@
 \begin{proposition}
-Let \((x,y)\in (\mathbb{N}^*)^2\), \(\pi(\pi(x)+\pi(y))=\pi(x+y)\)
+Let \((x,y)\in (\mathbb{N}^*)^2\). Then \(\pi(\pi(x)+\pi(y))=\pi(x+y)\).
 \end{proposition}
@@
 \begin{proof}[\textsc{Proof.}]
-Let \((x,y)\in (\mathbb{N}^*)^2\),
+Let \((x,y)\in (\mathbb{N}^*)^2\).
 
-\begin{align*}
- \pi(\pi(x)+\pi(y)) & = (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
-& = (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a)\ mod a) \\
-& = (Id+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
-& =(Id+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
-& =\pi(x+y)
-\end{align*}
+\[
+\begin{array}{c c l}
+	\pi(\pi(x)+\pi(y)) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
+	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a) \mod a) \\
+	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
+	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
+	& = & \pi(x+y)
+\end{array}
+\]
 \end{proof}
@@
 
-Let \((a,b) \in (\mathbb{N}^*)^2\), \(a>b\), let \(n \in\mathbb{N}\) we will define \(\lambda_{a,b}\) the projection:
+Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
 \[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
@@
 
-We will note  the projection \(\lambda\) and not \(\lambda_{a,b}\) when there is no doubt about the \(a\) and \(b\) we use.
+If there is no confusion on the \(a\) and \(b\) to use, \(\lambda_{a, b}\) is denoted by \(\lambda\).
 
-In the following theorem, \(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.
+\(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.
 
 \begin{proposition}
-Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\), \(x=a\lambda(x)+\pi(x)-a\)
+Let \((a,b)\in (\mathbb{N}^*)^2\) such that \(a>b\) and let \(x\in \mathbb{N}^*\). Then \(x=a\lambda(x)+\pi(x)-a\).
 \end{proposition}
+
 \begin{proof}[\textsc{Proof.}]
-Let \((a,b)\in (\mathbb{N}^*)^2\), \(a>b\), let  \(x\in \mathbb{N}^*\),\\
-\(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+\mathds{1}_{ [\![0,b]\!]}(x \mod a)\)
+Let \((a,b)\in (\mathbb{N}^*)^2\) such that \(a>b\) and let \(x\in \mathbb{N}^*\). \\
+\(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+ a \mathds{1}_{ [\![0,b]\!]}(x \mod a)\)
 
-if \(x \mod a>b\): \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)
+\noindent  if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)
 
-if \(x \mod a \leqslant b\):
-\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+\text{x mod a}+a=x\)
+\noindent if \(x \mod a \leqslant b\) then
+\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\)
 \end{proof}
@@
 \\
-\[if \quad x+y>b+2(p-b),\quad x+y-2(p-b)\notin A_n\]
+\[x+y>b+2(p-b) \implies x+y-2(p-b)\notin A_n\]
 \\

### 2021-05-02 article/introduction.tex
modification tableau

--- 2021-04-16 article/introduction.tex
@@
     \hline
-    \multirow{2}{*}{old} & 1 & 4 & 13 & 44 & 160 & 536 & 1680 & 5041 & 15124 & 51120 & 172216 & 575664 \\
+    \multirow{2}{*}{before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1680 & 5041 & 15124 & 51120 & 172216 & 575664 \\
       & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{ELIAHOU2012175} & 
@@
     \hline
-    \hyperref[Schur]{new}  & & & & & & & & & 17803 & 60948 & 203828 & 638548 \\
+    \hyperref[Schur]{our results}  & & & & & & & & & \textbf{17803} & \textbf{60948} & \textbf{203828} & \textbf{638548} \\
     \hline
 \end{tabular}
-
+*these values are not just a lower bound but the exact value for S(n)
 \vspace{3ex}
@@
     \hline
-    \multirow{2}{*}{old} & 2 & 8 & 23 & 66 & 196 & 582 & 1740 & 5201 & 15596 & 51520 & 172216 & 575664 \\
+    \multirow{2}{*}{before Rowley} & 2* & 8* & 23* & 66* & 196 & 582 & 1740 & 5201 & 15596 & 51520 & 172216 & 575664 \\
       & & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
@@
     \hline
-    \hyperref[WeakSchur]{new} & & & & & & & & & 22536 & 71214 & 243794 & 815314 \\
-    \hline
-    \(\displaystyle \frac{\text{new} - \text{old}}{\text{old}}\) & 0\% & 0\% & 0\% & 0\% & 0\% & 10.3\% & 
-    23.3\% & 34.1\% 
-    & 44.5\% & 38.2\% & 41.6\% & 41.6\% \\
+    \hyperref[WeakSchur]{our results} & & & & & & & & & \textbf{22536} & \textbf{71214} & \textbf{243794} & \textbf{815314} \\
     \hline
 \end{tabular}
-
+*these values are not just a lower bound but the exact value for WS(n)
 \end{center}

### 2021-05-02 article/introduction.tex
modification tableau

--- 2021-04-18 article/introduction.tex
@@
     \hline
-    \hyperref[Schur]{new}  & & & & & & & & & 17803 & 60948 & 203828 & 638548 \\
-    \hline
-    \(\displaystyle \frac{\text{new} - \text{old}}{\text{old}}\) & 0\% & 0\% & 0\% & 0\% & 0\% & 0\% & 
-    0\% & 0\%
-     & 17.7\% & 19.2\% & 18.4\% & 11.0\% \\
+    \hyperref[Schur]{our results}  & & & & & & & & & \textbf{17803} & \textbf{60948} & \textbf{203828} & \textbf{638548} \\
     \hline
 \end{tabular}
-
+*these values are not just a lower bound but the exact value for S(n)
 \vspace{3ex}
+\setlength{\tabcolsep}{4pt}
 
@@
     \hline
-    \hyperref[WeakSchur]{new} & & & & & & & & & 22536 & 71214 & 243794 & 815314 \\
-    \hline
-    \(\displaystyle \frac{\text{new} - \text{old}}{\text{old}}\) & 0\% & 0\% & 0\% & 0\% & 0\% & 10.3\% & 
-    23.3\% & 34.1\% & 44.5\% & 38.2\% & 41.6\% & 41.6\% \\
+    \hyperref[WeakSchur]{our results} & & & & & & & & & \textbf{22536} & \textbf{71214} & \textbf{243794} & \textbf{815314} \\
     \hline
 \end{tabular}
-
+*these values are not just a lower bound but the exact value for WS(n)
 \end{center}

### 2021-05-02 article/introduction.tex
state of the art

--- 2021-04-18 article/introduction.tex
@@
 \par
-As for smaller numbers, the best lower bounds were obtained by conducting a computer search. This search for 
-weakly sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) 
-colors starts with a good weakly sum-free partition into \(n\) colors.
+As for smaller numbers, the best lower bounds were obtained by conducting a computer search. Eliahou \cite{ELIAHOU2012175}, 
+Rafilipojaona \cite{Rafilipojaona} and Bouzy \cite{Bouzy2015AnAP} improved lower bounds with Monte-Carlo methods. It 
+has been the main approch in the previous decade. 
+This search for weakly sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) 
+colors starts with a good weakly sum-free partition into \(n\) colors. This assumption was necessary in order for the Monte-Carlo
+approch to yield results. However, we show in the \hyperlink{sat}{last section} how this search space may not countain
+the optimal solution. Thus further work using similar methods might need to put that assumption aside and 
+find a different search space.
 

### 2021-05-02 article/search_space.tex
state of the art

@@
 
-\qquad In this section, we first provide evidence which indicate that the main assumption made by papers which
+\qquad \hypertarget{sat}{In} this section, we first provide evidence which indicate that the main assumption made by papers which
 found the previous best known lower bounds for weak Schur numbers using a computer may not be correct. 

### 2021-05-02 article/weakschur.tex
modifs

@@
 \begin{theorem}
+\label{theorem}
 Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
@@
 templates for weak Schur numbers, we only give here an intuitive explanation of the above theorem; a formal
-proof can be found in the appendix.
+\hyperref[proof_theorem]{proof} can be found in the appendix.
 
@@
 \underline{\textbf{\(\mathcal{C}\) block}} \\
-In this block,  we use colors \(1, ..., n\). We colour an integer \(x\) according to its column number (written \(\tilde{\pi}(x)\), it is linked to the
-projection on the first line, written \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\)). A simple solution is to colour \(x\) with the same colour
+In this block,  we use colors \(1, ..., n\). We colour an integer \(x\) according to its column number, written \(\tilde{\pi}(x)\). It is linked to the
+projection on the first line, written \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\). A simple solution is to colour \(x\) with the same colour
 as \(\tilde{\pi}(x)\) in the weakly sum-free colouring of \([\![1,q]\!]\). As long as \(2b \leqslant a + r\) (not going two far to the right) and there
@@
 
-In particular, taking \(w = l = \lceil \displaystyle \frac{q}{2} \rceil\) and \(r = \lfloor \displaystyle \frac{q}{2} \rfloor\) works, thus obtaining the above theorem.\\
+In particular, taking \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) works, thus obtaining the above theorem.\\
 \par
@@
 Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
-\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a))\]
+\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
 \end{definition}
@@
 
-Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n)\), we have\\
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n))\), we have\\
 \[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
@@
 \[
-\WS(n+1) \geqslant 4S(n) + 1
-\]
-\[
-\WS(n+2) \geqslant 13S(n) + 8
-\]
-\[
-\WS(n+3) \geqslant 42S(n) + 24
-\]
-\[
-\WS(n+4) \geqslant 132S(n) + 26
+\begin{array}{r r r r r}
+	WS(n + 1) & \geqslant & 4 S(n) & + & 2 \\
+	WS(n + 2) & \geqslant & 13 S(n) & + & 8 \\
+	WS(n + 3) & \geqslant & 42 S(n) & + & 24 \\
+	WS(n + 4) & \geqslant & 132 S(n) & + & 26 \\
+\end{array}
 \]
 
-The first two inequalities were found by Rowley, they are detailed in [2]. The third inequality is optimal and was found with a SAT solver.
+The first two inequalities were found by Rowley, they are detailed in \cite{RowleyWS}. The third inequality is optimal and was found with a SAT solver.
 It uses the first sophistication explained in the previous subsection in order to add the last number in the first color.

### 2021-05-04 article/introduction.tex

@@
 
-\renewcommand{\arraystretch}{1.2}
 \setlength{\tabcolsep}{4pt}
@@
     \hline
-    \multirow{2}{*}{before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1680 & 5041 & 15124 & 51120 & 172216 & 575664 \\
+    \multirow{2}{*}{before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
       & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{ELIAHOU2012175} & 
@@
     \hline
-    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyRamsey}\end{tabular} & & & & & & & & 5286 & 17694 & 
-    60320 & 201696 & 631840 \\
+    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyRamsey}\end{tabular} & & & & & & & & 5\,286 & 17\,694 & 
+    60\,320 & 201\,696 & 631\,840 \\
     \hline
-    \hyperref[Schur]{our results}  & & & & & & & & & \textbf{17803} & \textbf{60948} & \textbf{203828} & \textbf{638548} \\
+    \hyperref[Schur]{\textbf{our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{638\,548} \\
     \hline
 \end{tabular}
-*these values are not just a lower bound but the exact value for S(n)
-\vspace{3ex}
-\setlength{\tabcolsep}{4pt}
+
+\vspace{2.5ex}
 
@@
     \hline
-    \multirow{2}{*}{before Rowley} & 2* & 8* & 23* & 66* & 196 & 582 & 1740 & 5201 & 15596 & 51520 & 172216 & 575664 \\
+    \multirow{2}{*}{before Rowley} & 2* & 8* & 23* & 66* & 196 & 582 & 1\,740 & 5\,201 & 15\,596 & 51\,520 & 172\,216 & 575\,664 \\
       & & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
@@
     \hline
-    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyWS}\end{tabular} & & & & & & 642 & 2146 & 6976 & 21848 
-    & 70778 & 241282 & 806786 \\
+    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyWS}\end{tabular} & & & & & & 642 & 2\,146 & 6\,976 & 21\,848 
+    & 70\,778 & 241\,282 & 806\,786 \\
     \hline
-    \hyperref[WeakSchur]{our results} & & & & & & & & & \textbf{22536} & \textbf{71214} & \textbf{243794} & \textbf{815314} \\
+    \hyperref[WeakSchur]{\textbf{our results}} & & & & & & & & & \textbf{22\,536} & \textbf{71\,214} & \textbf{243\,794} & \textbf{815\,314} \\
     \hline
 \end{tabular}
-*these values are not just a lower bound but the exact value for WS(n)
+
+\vspace{1.5ex}
+* denotes an exact value, not just a lower bound
 \end{center}

### 2021-05-04 article/weakschur.tex
Changement de titres

@@
-\section{Weak Schur numbers}
+\section{Templates for weak Schur numbers}
 \label{WeakSchur}
@@
 
-\subsection{Lower bound for Weak Schur numbers using Schur and Weak Schur numbers}
+\subsection{Inequality for weak Schur numbers using Schur and weak Schur numbers}
 
@@
 
-\renewcommand{\arraystretch}{2}
+\renewcommand{\arraystretch}{1.7}
+
 \[
@@
 \]
-\renewcommand{\arraystretch}{1}
+
+\resetarraystretch
 
@@
 
-\(\lambda\) is the function which maps an element x to its line number as mentioned in the intuitive explanation.
+\(\lambda\) is the function which maps an element \(x\) to its line number as mentioned in the intuitive explanation.
 
@@
 
-\subsection{New lower bounds for Weak Schur numbers}
+\subsection{Inequalities and new lower bounds for Weak Schur numbers}
 
@@
 	\hline
-	\(4S(n-1) + 2 \) & 6722 & 21146 & \cellcolor{yellow} 71214 & \cellcolor{yellow} 243794\\
+	\(4S(n-1) + 2 \) & 6\,722 & 21\,146 & \cellcolor{yellow} 71\,214 & \cellcolor{yellow} 243\,794\\
 	\hline
-	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6976 & 21848 & 68726 & 231447\\
+	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6\,976 & 21\,848 & 68\,726 & 231\,447\\
 	\hline
-	\(42S(n-3) + 24 \) & 6744 & \cellcolor{yellow} 22536 & 70584 & 222036 \\
+	\(42S(n-3) + 24 \) & 6\,744 & \cellcolor{yellow} 22\,536 & 70\,584 & 222\,036 \\
 	\hline
-	\(127S(n-4) + 68 \) & 5656 & 20388 & 68140 & 213428\\
+	\(127S(n-4) + 68 \) & 5\,656 & 20\,388 & 68\,140 & 213\,428\\
 	\hline
@@
 	\hline
-	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815314 & 2554194 & 8045162 & \cellcolor{yellow} 27061154\\
+	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815\,314 & 2\,554\,194 & 8\,045\,162 & \cellcolor{yellow} 27\,061\,154\\
 	\hline
-	\(13S(n-2) + 8 \) & 792332 & \cellcolor{yellow}2649772 & 8301132 & 26146778 \\
+	\(13S(n-2) + 8 \) & 792\,332 & \cellcolor{yellow}2\,649\,772 & 8\,301\,132 & 26\,146\,778 \\
 	\hline
-	\(42S(n-3) + 24 \) & 747750 & 2559840 & \cellcolor{yellow} 8560800 &  25886224 \\
+	\(42S(n-3) + 24 \) & 747\,750 & 2\,559\,840 & \cellcolor{yellow} 8\,560\,800 &  25\,886\,224 \\
 	\hline
-	\(127S(n-4) + 68 \) & 671390 & 2261049 & 7740464 & 25886224 \\
+	\(127S(n-4) + 68 \) & 671\,390 & 2\,261\,049 & 7\,740\,464 & 25\,886\,224 \\
 	\hline
@@
 
-With \( S(9) \geqslant 17803 \), we found a new lower bound for \(\WS(10)\) using Rowley's inequality.
+With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using Rowley's inequality.
 Moreover, the third inequality gives new lower bounds for \(\WS(9)\) and \(WS(14)\).

### 2021-05-04 article/introduction.tex
Majuscules

@@
     \hline
-    \multirow{2}{*}{before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
+    \multirow{2}{*}{Before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
       & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{ELIAHOU2012175} & 
@@
     \hline
-    \hyperref[Schur]{\textbf{our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{638\,548} \\
+    \hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{638\,548} \\
     \hline

### 2021-05-04 article/weakschur.tex
Application identité

@@
 Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
-\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
+\[ \pi_{a,b}:x \longmapsto (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
 \end{definition}
@@
 \begin{array}{c c l l}
-	\pi(x+y) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a) & \\
-	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a) & \text{since } \pi(y)=y \mod a \\
+	\pi(x+y) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a) & \\
+	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a) & \text{since } \pi(y)=y \mod a \\
 	& = & x+ \pi(y) &
@@
 \begin{array}{c c l l}
-	\pi(x+y) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)& \\
-	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a) & \text{since } \pi(y)=y \mod a \\
-	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) & \\
+	\pi(x+y) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)& \\
+	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a) & \text{since } \pi(y)=y \mod a \\
+	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) & \\
 	& = & x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]}(x+\pi(y) - a) & \\
@@
 \begin{array}{c c l}
-	\pi(\pi(x)+\pi(y)) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
-	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a) \mod a) \\
-	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
-	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
+	\pi(\pi(x)+\pi(y)) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
+	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a) \mod a) \\
+	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
+	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
 	& = & \pi(x+y)

### 2021-05-04 article/weakschur.tex
def 3.3
jolis tableaux 2/3

--- 2021-05-04 article/weakschur.tex
@@
 \[
-\begin{array}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
-\cline{6-9}
-   \multicolumn{5}{c|}{} & \cellcolor{green} 1 & \cellcolor{green} 2 & \cellcolor{blue} ... &\cellcolor{green} r & r + 1 & ... & b - 1 &  b \\
-\hline
-   \cellcolor{red} a - l & \cellcolor{red} a- l + 1 & \cellcolor{red} ...
-& \cellcolor{red} a - 1 & \cellcolor{red} a & \cellcolor{red} a + 1 & \cellcolor{red} ...
-&\cellcolor{red} a + r - 1 & \cellcolor{red} a + r & a + r + 1 & ...
-& a + b - 1 & a+ b \\
-\hline
-\cellcolor{yellow} 2 a - l &\cellcolor{yellow}...&\cellcolor{yellow}...&\cellcolor{yellow}...&\cellcolor{yellow} 2 a &\cellcolor{yellow} ...
-&\cellcolor{yellow} ...
-&\cellcolor{yellow} ...
-&\cellcolor{yellow} 2 a + r & ...
-& ...
-& ...
-& 2 a + b \\
-\hline
-...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
-\hline
-\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
-\hline
-p a - l & ... & ... & ... &p a & ... & ... & .... & p a + r & ... & ... & ... & p a + b\\
-\hline
-\end{array}
+\begin{NiceArray}{|*{13}{c|}}[corners=NW,standard-cline,hlines]
+\CodeBefore
+	\cellcolor{green}{1-6}
+	\cellcolor{green}{1-7}
+	\cellcolor{cyan}{1-8}
+	\cellcolor{green}{1-9}
+	\cellcolor{cyan}{1-10}
+	\cellcolor{cyan}{1-11}
+	\cellcolor{cyan}{1-12}
+	\cellcolor{green}{1-13}
+	\cellcolor{red}{2-1}
+	\cellcolor{red}{2-2}
+	\cellcolor{red}{2-3}
+	\cellcolor{red}{2-4}
+	\cellcolor{red}{2-5}
+	\cellcolor{red}{2-6}
+	\cellcolor{red}{2-7}
+	\cellcolor{red}{2-8}
+	\cellcolor{red}{2-9}
+	\cellcolor{cyan}{2-10}
+	\cellcolor{cyan}{2-11}
+	\cellcolor{cyan}{2-12}
+	\cellcolor{green}{2-13}
+	\cellcolor{yellow}{3-1}
+	\cellcolor{yellow}{3-2}
+	\cellcolor{yellow}{3-3}
+	\cellcolor{yellow}{3-4}
+	\cellcolor{yellow}{3-5}
+	\cellcolor{yellow}{3-6}
+	\cellcolor{yellow}{3-7}
+	\cellcolor{yellow}{3-8}
+	\cellcolor{yellow}{3-9}
+	\cellcolor{cyan}{3-10}
+	\cellcolor{cyan}{3-11}
+	\cellcolor{cyan}{3-12}
+	\cellcolor{green}{3-13}
+	\cellcolor{yellow}{4-1}
+	\cellcolor{yellow}{4-2}
+	\cellcolor{yellow}{4-3}
+	\cellcolor{yellow}{4-4}
+	\cellcolor{yellow}{4-5}
+	\cellcolor{yellow}{4-6}
+	\cellcolor{yellow}{4-7}
+	\cellcolor{yellow}{4-8}
+	\cellcolor{yellow}{4-9}
+	\cellcolor{cyan}{4-10}
+	\cellcolor{cyan}{4-11}
+	\cellcolor{cyan}{4-12}
+	\cellcolor{green}{4-13}
+	\cellcolor{red}{5-1}
+	\cellcolor{red}{5-2}
+	\cellcolor{red}{5-3}
+	\cellcolor{red}{5-4}
+	\cellcolor{red}{5-5}
+	\cellcolor{red}{5-6}
+	\cellcolor{red}{5-7}
+	\cellcolor{red}{5-8}
+	\cellcolor{red}{5-9}
+	\cellcolor{cyan}{5-10}
+	\cellcolor{cyan}{5-11}
+	\cellcolor{cyan}{5-12}
+	\cellcolor{green}{5-13}
+	\cellcolor{cyan}{6-10}
+	\cellcolor{cyan}{6-11}
+	\cellcolor{cyan}{6-12}
+	\cellcolor{green}{6-13}
+\Body
+	& & & & & 1 & 2 & ... & r & r + 1 & ... & b - 1 & b \\
+	a - l & a - l + 1 & ... & a - 1 & a & a + 1 & ... & a + r - 1 & a + r & a + r + 1 & ... & a + b - 1 & a + b \\
+	2 a - l & ... & ... & ... & 2 a & ... & ... & ... & 2 a + r & ... & ... & ... & 2 a + b \\
+	... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
+	... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
+	p a - l & ... & ... & ... & p a & ... & ... & ... & p a + r & ... & ... & ... & p a + b \\
+\end{NiceArray}
 \]

### 2021-05-04 article/weakschur.tex

@@
 This partition is said to be a b-weakly-sum-free template (b-WSF-template) of \(n\) colors and lenght \(p\) when:
-\\\\
-\underline{\(\forall i \in [\![1, n]\!], \quad A_i\) is weakly-sum-free}
-\\\\
-\underline{\(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
-\\\\
-\underline{For \(A_n\) (the special subset):} \quad \(\forall (x,y) \in A_n^2,\)
-\\
-\[x+y>b+2(p-b) \implies x+y-2(p-b)\notin A_n\]
-\\
-\underline{For the others subsets:}\quad \(\forall i \in [\![0,n-1]\!], \forall(x,y) \in A_i^2,\)
-\\
-\[
+\begin{itemize}
+\item \(\forall i \in [\![1, n]\!], \quad A_i\) is weakly-sum-free
+\item \(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free
+\item For \(A_n\) (the special subset): \[\forall (x,y) \in A_n^2, \,
+x+y>b+2(p-b) \implies x+y-2(p-b)\notin A_n\]
+\item For the others subsets: \\ \[\forall i \in [\![0,n-1]\!], \, \forall(x,y) \in A_i^2, \,
 x+y>p \implies \pi(x+y) \notin A_i
 \]
+\end{itemize}
 \end{definition}

### 2021-05-07 article/appendix.tex
environnement proof -> \begin{proof}[\textsc{Proof.}]
reorganisation
modifs
anglais + erreurs

--- 2021-04-14 article/appendix.tex
@@
 \appendix
+
+\section{SF-templates}
 \renewcommand{\arraystretch}{1}
 
-\section{SF-templates}
+\begin{center}
+SF-template with width 33 and 4 colors \\
 
-\begin{center}
-SF-template partitionning \([\![1, 33]\!]\) into 4 subsets \\
 \begin{tabular}{|*{2}{c|}}
@@
 \begin{center}
-SF-template partitionning \([\![1, 111]\!]\) into 5 subsets
+SF-template with width 111 and 5 colors \\
+
 \begin{tabular}{|*{2}{c|}}
@@
 \begin{center}
-SF-template partitionning \([\![1, 380]\!]\) into 6 subsets
+SF-template with width 380 and 6 colors \\
+
 \begin{tabular}{|*{2}{c|}}
@@
 	\hline
-
 \end{tabular}
@@
 \begin{center}
-WSF-template partitionning \([\![1, 42]\!]\) into 4 subsets
+23-WSF-template with width 42 and 4 colors \\
+
 \begin{tabular}{|*{2}{c|}}
@@
 
-\section{Proof of theorem j'arrive pas a afficher le numero du theoreme avec un lien}
+\resetarraystretch
 
-\textsc{Proof :} Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\), \(N = p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q\),
-\(\alpha = \left \lceil \frac{q}{2} \right \rceil > 0\) and \(\beta = q + \alpha + 1\).
-We denote by \(f\) the colouring associated to the partition of \([\![1,q]\!]\) and \(g\) the
+%\section{Reformulation as a SAT problem}
+%\label{SAT}
+%
+%\qquad In this section, we reframe the question of the existence of (weakly) sum-free partitions as a boolean
+%satisfiability (SAT) problem. We encode the existence of (weakly) sum-free partitions as propositional formulae like in
+%\cite{Heule2017} and then use SAT solvers to determine whether these formulae are satisfiable.
+%
+%\begin{definition}
+%A \textit{literal} is either a variable \(v\) (a positive literal) or the negation \(\bar{v}\) of a variable \(v\) (a
+%negative literal) where \(v\)
+%takes a truth value: \(true\) or \(false\). A \textit{clause} is a disjunction of literals and a \textit{formula} is a
+%conjunction of clauses: it
+%is a propositional formula in \textit{conjonctive normal form} (CNF).
+%\end{definition}
+%
+%\begin{definition}
+%An \textit{assignment} is a function from a set of variables to the truth values \(true\) (1) and \(false\) (0). A
+%literal \(l\) is
+%\textit{satisfied} (\textit{falsified}) by an assignment \(\alpha\) if l is positive and \(\alpha(var (l)) = 1\)
+%(resp. \(\alpha(var (l)) = 0\)) or if it is negative and \(\alpha(var (l)) = 0\) (resp. \(\alpha(var (l)) = 1\)). A
+%clause is \textit{satisfied}
+%by an assignment \(\alpha\) if it contains a literal that is satisfied by \(\alpha\). Finally, a formula is
+%\textit{satisfied} by an assignment
+%\(\alpha\) if all its clauses are satisfied by \(\alpha\). A formula is \textit{satisfiable} if there exists an
+%assignment that satisfies it;
+%otherwise it is \textit{unsatisfiable}.
+%\end{definition}
+%
+%We then encode the existence of a partition of \([\![1,p]\!]\) in \(k\) weakly sum-free subsets as follows: for every
+%integer
+%\(i \in [\![1,p]\!]\), take \(k\) variables \(x^{(i)}_{1}, ..., x^{(i)}_{k}\) and for every \(\forall c \in [\![1,k]\!],
+%x^{(i)}_c = 1 \iff i \in A_c\).
+%The corresponding clauses are:
+%
+%\begin{itemize}
+%\item \textbf{weakly sum-free:} \(\forall c \in [\![1,k]\!], \forall (i, j) \in [\![1,p]\!]^2, (i \neq j ~ \text{and} ~ i + j
+%\leq n) \implies \lnot x^{(i)}_c
+%\lor  \lnot x^{(i)}_c \lor \lnot x^{(i+j)}_c\)
+%\item \textbf{union:} \(\forall i \in [\![1,p]\!], x^{(i)}_1 \lor ... \lor x^{(i)}_k\)
+%\item \textbf{disjoint:} \(\forall i \in [\![1,p]\!],\forall (c_1, c_2) \in [\![1,k]\!]^2, c_1 \neq c_2 \implies \neg
+%x^{(i)}_{c_1} \lor \neg x^{(i)}_{c_2}\)
+%\end{itemize}
+%
+%In the above formula, every color plays a symmetric role. Hence the search space can reduced by \(k!\) by ordering the
+%subsets, that is by
+%enforcing that \(m_1 < ... < m_k\). The corresponding clauses are: \linebreak
+%\textbf{symmetry breaking:} \(x^{(1)}_1 = 1\) and \(\forall c \in [\![2,k-1]\!], \forall i \in [\![1, \WS (c - 1)+1]\!],
+%x^{(1)}_c \lor ... \lor x^{(i)}_c \lor \neg x^{(i+1)}_{c+1}\)
+%
+%\begin{remark}
+%For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary
+%significantly according to the problem.
+%For instance, we used two different SAT solvers in the next two next subsections.
+%\end{remark}
+%
+%\begin{remark}
+%Using a parallel SAT solver usually reduces the computation time, especially when trying to show that a formula is
+%unsatisfiable. However, most of the
+%parallel SAT solver do not have a deterministic behaviour and it can results in a strong variation of running times.
+%\end{remark}
+
+\section{Proof of theorem \ref{theorem}}
+\label{proof_theorem}
+
+\begin{proof}[\textsc{Proof.}]
+Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\), \(N = p(q+\left \lceil \displaystyle \frac{q}{2} \right \rceil + 1)+q\),
+\(\alpha = \left \lceil \displaystyle \frac{q}{2} \right \rceil > 0\) and \(\beta = q + \alpha + 1\).
+We denote by \(f\) the coloring associated to the partition of \([\![1,q]\!]\) and \(g\) the
 one associated to the partition of \([\![1,p]\!]\).
@@
 Finally, we have showed that every classe of equivalence induced by \(h\) is weakly sum-free, which ends the proof.
+\end{proof}

### 2021-05-07 article/schur.tex
Changement de titres
jolis tableaux :'(
anglais + erreurs

@@
-\section{Schur numbers}
+\section{Templates for Schur numbers}
 \label{Schur}
@@
 \begin{definition}
-A SF-template with length \(p\) and \(n\) colors is defined as a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets 
+A SF-template with width \(p\) and \(n\) colors is defined as a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets 
 \(A_1, A_2, ..., A_n\) verifying:
@@
 \begin{proposition}
-	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the maximal lenght of a SF-template with \(n\) colors. 
+	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the maximal width of a SF-template with \(n\) colors. 
 	\(S^+(n)\) is well defined and verifies:
@@
 The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
-fact that a SF-template with length \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets.
+fact that a SF-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets.
 \end{proof}
@@
 \begin{theorem}
-	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with lenght \(p\) and \(k+1\) colors 
+	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors 
 	and a partition of \([\![1,q]\!]\) into \(n\) sum-free subsets then there exists a partition of \([\![1,pq+m_{k+1}
@@
 
-\begin{center}
-\textbf{Abbott and Hanson's construction}
-\end{center}
-
-\[
-\begin{array}{|*{9}{c|}}
-	\hline
-	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{cyan} 5 & 
-	\cellcolor{cyan} 6 & \cellcolor{cyan} 7 & \cellcolor{cyan} 8 & \cellcolor{cyan} 9\\
-	\hline
-	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & 
-	\cellcolor{yellow} 15 & \cellcolor{yellow} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
-	\hline
-	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & 
-	\cellcolor{yellow} 24 & \cellcolor{yellow} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
-	\hline
-	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{cyan} 32 & 
-	\cellcolor{cyan} 33 & \cellcolor{cyan} 34 & \cellcolor{cyan} 35 & \cellcolor{cyan} 36 \\
-	\hline
-	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 \\
-	\cline{1-4}
-\end{array}
-\]
+\renewcommand{\arraystretch}{1.7}
 
 \begin{center}
+\setlength{\tabcolsep}{1.5ex}
+
+\textbf{Abbott and Hanson's construction}
+\vspace{1.7ex}
+
+\begin{NiceTabular}{|*{9}{c|}}[corners=SE,standard-cline,hlines]
+\CodeBefore
+	\cellcolor{red}{1-1}
+	\cellcolor{green}{1-2}
+	\cellcolor{green}{1-3}
+	\cellcolor{red}{1-4}
+	\cellcolor{cyan}{1-5}
+	\cellcolor{cyan}{1-6}
+	\cellcolor{cyan}{1-7}
+	\cellcolor{cyan}{1-8}
+	\cellcolor{cyan}{1-9}
+	\cellcolor{red}{2-1}
+	\cellcolor{green}{2-2}
+	\cellcolor{green}{2-3}
+	\cellcolor{red}{2-4}
+	\cellcolor{yellow}{2-5}
+	\cellcolor{yellow}{2-6}
+	\cellcolor{yellow}{2-7}
+	\cellcolor{yellow}{2-8}
+	\cellcolor{yellow}{2-9}
+	\cellcolor{red}{3-1}
+	\cellcolor{green}{3-2}
+	\cellcolor{green}{3-3}
+	\cellcolor{red}{3-4}
+	\cellcolor{yellow}{3-5}
+	\cellcolor{yellow}{3-6}
+	\cellcolor{yellow}{3-7}
+	\cellcolor{yellow}{3-8}
+	\cellcolor{yellow}{3-9}
+	\cellcolor{red}{4-1}
+	\cellcolor{green}{4-2}
+	\cellcolor{green}{4-3}
+	\cellcolor{red}{4-4}
+	\cellcolor{cyan}{4-5}
+	\cellcolor{cyan}{4-6}
+	\cellcolor{cyan}{4-7}
+	\cellcolor{cyan}{4-8}
+	\cellcolor{cyan}{4-9}
+	\cellcolor{red}{5-1}
+	\cellcolor{green}{5-2}
+	\cellcolor{green}{5-3}
+	\cellcolor{red}{5-4}
+\Body
+	1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
+	10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 \\
+	19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 \\
+	28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 \\
+	37 & 38 & 39 & 40 \\
+\end{NiceTabular}
+
+\vspace{1ex}
+\setlength{\tabcolsep}{2ex}
+
 \begin{tabular}{c c}
 	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
-	\begin{tabular}{|*{9}{c|}}
-		\hline 
-		\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{gray!40} 5 & 
-		\cellcolor{gray!40} 6 & \cellcolor{gray!40} 7 & \cellcolor{gray!40} 8 & \cellcolor{gray!40} 9 \\
-		\hline
-	\end{tabular} &
-	\begin{tabular}{|*{4}{c|}}
-		\hline 
-		\cellcolor{cyan} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{cyan} 4 \\
-		\hline
+	\begin{NiceTabular}{|*{9}{c|}}[standard-cline,hlines]
+	\CodeBefore 
+		\cellcolor{red}{1-1}
+		\cellcolor{green}{1-2}
+		\cellcolor{green}{1-3}
+		\cellcolor{red}{1-4}
+		\cellcolor{gray!40}{1-5}
+		\cellcolor{gray!40}{1-6}
+		\cellcolor{gray!40}{1-7}
+		\cellcolor{gray!40}{1-8}
+		\cellcolor{gray!40}{1-9}
+	\Body
+		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
+	\end{NiceTabular} &
+	\begin{NiceTabular}{|*{4}{c|}}[standard-cline,hlines]
+	\CodeBefore
+		\cellcolor{cyan}{1-1}
+		\cellcolor{yellow}{1-2}
+		\cellcolor{yellow}{1-3}
+		\cellcolor{cyan}{1-4}
+	\Body
+		1 & 2 & 3 & 4 \\
+	\end{NiceTabular}
 \end{tabular}
-\end{tabular}
+
+\setlength{\tabcolsep}{6pt}
 \end{center}
@@
 \begin{center}
+\setlength{\tabcolsep}{1.5ex}
+
 \textbf{SF-template construction}
+\vspace{1.7ex}
+
+\begin{NiceTabular}{|*{9}{c|}}[corners=SE,standard-cline,hlines]
+\CodeBefore
+	\cellcolor{red}{1-1}
+	\cellcolor{green}{1-2}
+	\cellcolor{green}{1-3}
+	\cellcolor{red}{1-4}
+	\cellcolor{cyan}{1-5}
+	\cellcolor{cyan}{1-6}
+	\cellcolor{red}{1-7}
+	\cellcolor{cyan}{1-8}
+	\cellcolor{cyan}{1-9}
+	\cellcolor{red}{2-1}
+	\cellcolor{green}{2-2}
+	\cellcolor{green}{2-3}
+	\cellcolor{red}{2-4}
+	\cellcolor{yellow}{2-5}
+	\cellcolor{yellow}{2-6}
+	\cellcolor{red}{2-7}
+	\cellcolor{yellow}{2-8}
+	\cellcolor{yellow}{2-9}
+	\cellcolor{red}{3-1}
+	\cellcolor{green}{3-2}
+	\cellcolor{green}{3-3}
+	\cellcolor{red}{3-4}
+	\cellcolor{yellow}{3-5}
+	\cellcolor{yellow}{3-6}
+	\cellcolor{red}{3-7}
+	\cellcolor{yellow}{3-8}
+	\cellcolor{yellow}{3-9}
+	\cellcolor{red}{4-1}
+	\cellcolor{green}{4-2}
+	\cellcolor{green}{4-3}
+	\cellcolor{red}{4-4}
+	\cellcolor{cyan}{4-5}
+	\cellcolor{cyan}{4-6}
+	\cellcolor{red}{4-7}
+	\cellcolor{cyan}{4-8}
+	\cellcolor{cyan}{4-9}
+	\cellcolor{red}{5-1}
+	\cellcolor{green}{5-2}
+	\cellcolor{green}{5-3}
+	\cellcolor{red}{5-4}
+\Body
+	1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
+	10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 \\
+	19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 \\
+	28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 \\
+	37 & 38 & 39 & 40 \\
+\end{NiceTabular}
+
+\vspace{1ex}
+\setlength{\tabcolsep}{2ex}
+
+\begin{tabular}{c c}
+	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
+	\begin{NiceTabular}{|*{9}{c|}}[standard-cline,hlines]
+	\CodeBefore 
+		\cellcolor{red}{1-1}
+		\cellcolor{green}{1-2}
+		\cellcolor{green}{1-3}
+		\cellcolor{red}{1-4}
+		\cellcolor{gray!40}{1-5}
+		\cellcolor{gray!40}{1-6}
+		\cellcolor{red}{1-7}
+		\cellcolor{gray!40}{1-8}
+		\cellcolor{gray!40}{1-9}
+	\Body
+		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
+	\end{NiceTabular} &
+	\begin{NiceTabular}{|*{4}{c|}}[standard-cline,hlines]
+	\CodeBefore
+		\cellcolor{cyan}{1-1}
+		\cellcolor{yellow}{1-2}
+		\cellcolor{yellow}{1-3}
+		\cellcolor{cyan}{1-4}
+	\Body
+		1 & 2 & 3 & 4 \\
+	\end{NiceTabular}
+\end{tabular}
+
+\setlength{\tabcolsep}{6pt}
 \end{center}
 
-\[
-\begin{array}{|*{9}{c|}}
-	\hline
-	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{cyan} 5 & 
-	\cellcolor{cyan} 6 & \cellcolor{red} 7 & \cellcolor{cyan} 8 & \cellcolor{cyan} 9\\
-	\hline
-	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & 
-	\cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
-	\hline
-	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & 
-	\cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
-	\hline
-	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{cyan} 32 & 
-	\cellcolor{cyan} 33 & \cellcolor{red} 34 & \cellcolor{cyan} 35 & \cellcolor{cyan} 36 \\
-	\hline
-	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 \\
-	\cline{1-4}
-\end{array}
-\]
-
-\begin{center}
-\begin{tabular}{c c}
-	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
-	\begin{tabular}{|*{9}{c|}}
-		\hline 
-		\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{gray!40} 5 & 
-		\cellcolor{gray!40} 6 & \cellcolor{red} 7 & \cellcolor{gray!40} 8 & \cellcolor{gray!40} 9 \\
-		\hline
-	\end{tabular} &
-	\begin{tabular}{|*{4}{c|}}
-		\hline 
-		\cellcolor{cyan} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{cyan} 4 \\
-		\hline
-	\end{tabular}
-\end{tabular}
-\end{center}
+\resetarraystretch
 
@@
 \begin{proof}[\textsc{Proof.}]
-Denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\) and \(g\) the one associated 
+Denote by \(f\) the coloring associated to the \(SF\)-template with width \(p\) and \(g\) the one associated 
 to the sum-free partition of \([\![1,q]\!]\); where \(f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!]\) and 
@@
 \begin{proposition}
-Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a colouring associated to a SF-template of length \(p\) with \(k+1\) 
-colors. Let \(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a colouring \(g\) of 
+Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a SF-template with width \(p\) and \(k+1\) 
+colors. Let \(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a coloring \(g\) of 
 \([\![1, b]\!]\) with \(k+1\) colors such that:
@@
 
-Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n))\), we have
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(i \longmapsto g(i - p S(n))\), we have
 \[ S(n+k) \geqslant S^+(k+1)S(n) + b\]
@@
 column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
-intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the colouring of the last 
+intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the coloring of the last 
 row can be weakened.
@@
 \begin{theorem}
-	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template of \(k+1\) colors and lenght \(p\),
-	and \(SF\)-template of \(n\) color and lenght \(q\), then there exists \(SF\)-template of \((n+k)\) and lenght \(pq\).
+	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with and \(p\) and \(k+1\) colors,
+	and a \(SF\)-template with width \(q\) and \(n\) colors, then there exists \(SF\)-template with width \(pq\) and \((n+k)\).
 \end{theorem}
@@
 
-\subsection{New lower bounds for Schur numbers}
+\subsection{Inequalities and new lower bounds for Schur numbers}
 
@@
 	S(n + 5) & \geqslant & 380 S(n) & + & 148 \\
-	S(n + 6) & \geqslant & 1140 S(n) & + & 528 \\
+	S(n + 6) & \geqslant & 1\,140 S(n) & + & 528 \\
 \end{array}
@@
 likely not optimal but should not be too far from the optimal. 
-Finally, the sixth one is obtained by combining (see below) the SF-template of length 380 and the one of length 3. 
+Finally, the sixth one is obtained by combining (see below) the SF-template with width 380 and the one with width 3. 
 Although we could not find a better SF-template with 7 colors, the last inequality is definetely very far from the 
@@
 
-\begin{center}
-\begin{tabular}{|*{5}{c|}}
-    \hline
-	\(n\) & 8 & 9 & 10 & 11 \\
-	\hline
-	\(33S(n-3) + 6 \) & \cellcolor{yellow} 5286 & 17694 & 55446 & 174444\\
-	\hline
-	\(111S(n-4) + 43 \) & 4927 & \cellcolor{yellow} 17803 & 59539 & 186523\\
-	\hline
-	\(380S(n-5) + 148 \) & 5088 & 16868 & \cellcolor{yellow} 60948 & \cellcolor{yellow} 203828 \\
-	\hline
-	\(1140S(n-6) + 528 \) & 5088 & 15348 & 50688 & 182928\\
-	\hline
-	\hline
-	\(n\) & 12 & 13 & 14 & 15 \\
-	\hline
-	\(33S(n-3) + 6 \) & 587505 & \cellcolor{yellow} 2011290 & 6726330 & 21072090\\
-	\hline
-	\(111S(n-4) + 43 \) & 586789 & 1976176 & 6765271 & 22624951 \\
-	\hline
-\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\\hline
-	\(1140S(n-6) + 528 \) & 611568 & 1915728 & 6026568 & 20295948 \\
-	\hline
-\end{tabular}
-\end{center}
+\renewcommand{\arraystretch}{0.2}
+
+\[
+\begin{array}{c}
+	\resetarraystretch
+	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
+	\CodeBefore
+		\cellcolor{yellow}{2-2}
+		\cellcolor{yellow}{3-3}
+		\cellcolor{yellow}{4-4}
+		\cellcolor{yellow}{4-5}
+	\Body
+		n & 8 & 9 & 10 & 11 \\
+		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,446 & 174\,444 \\
+		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 186\,523 \\
+		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
+		1\,140 \, S(n-6) + 528 & 5\,088 & 15\,348 & 50\,688 & 182\,928 \\
+	\end{NiceArray}
+	\\ \\
+	\resetarraystretch
+	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
+	\CodeBefore
+		\cellcolor{yellow}{2-3}
+		\cellcolor{yellow}{4-2}
+		\cellcolor{yellow}{4-4}
+		\cellcolor{yellow}{4-5}
+	\Body
+		n & 12 & 13 & 14 & 15 \\
+		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,072\,090 \\
+		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
+		380 \, S(n-5) + 148 & 638\,548 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
+		1\,140 \, S(n-6) + 528 & 611\,568 & 1\,915\,728 & 6\,026\,568 & 20\,295\,948 \\
+	\end{NiceArray}
+\end{array}
+\]
+
+\resetarraystretch
 

### 2021-05-07 article/search_space.tex
Changement de titres
sperateur miliers + jolis tableaux (1/2)
anglais + erreurs

@@
 
-\subsection{Former assumption appears to be wrong}
+\subsection{Limitation of the former assumption}
 
@@
 \par
-For every weakly sum-free colouring \(f\) of \([\![1,65]\!]\) with 4 colors, the sequence \(f(1), f(2), f(3), ...\) always
+For every weakly sum-free coloring \(f\) of \([\![1,65]\!]\) with 4 colors, the sequence \(f(1), f(2), f(3), ...\) always
 starts with the following subsequence 1121222133. Then 11 is always
@@
 
-\subsection{Weak Schur number five}
+\subsection{Investigating weak Schur number five}
 
@@
 
+\resetarraystretch
+\setlength{\tabcolsep}{6pt}
+
 For \(m_4 = 24\), the value \(m_5 \leqslant 53\) was obtained after 7 hours of runtime, and for  \(m_4 = 22\), the

### 2021-05-07 article/weakschur.tex
jolis tableaux :'(
anglais + erreurs

@@
 subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
-and let's try to build a colouring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
+and let's try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
 \(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\).
@@
 
-\underline{\textbf{\(\mathcal{T}\) block}} \\
-We color this block using the weakly sum-free colouring of \([\![1,q]\!]\) with colors \(1, ..., n\).
+\noindent \underline{\textbf{\(\mathcal{T}\) block}}
+\par
+We color this block using the weakly sum-free coloring of \([\![1,q]\!]\) with colors \(1, ..., n\).
 
-\underline{\textbf{\(\mathcal{R}\) block}} \\
-In this block,  we use the colors \(n + 1, ..., n + k\). We colour an integer \(x\) according to its line number (written \(\lambda(x)\)).
-For every \(x \in \mathcal{R}\), we colour \(x\) with \(n + c\) where \(c\) is the colour of \(\lambda(x)\) in the sum-free colouring of  \([\![1,p]\!]\).
+\noindent \underline{\textbf{\(\mathcal{R}\) block}}
+\par
+In this block,  we use the colors \(n + 1, ..., n + k\). We color an integer \(x\) according to its line number (written \(\lambda(x)\)).
+For every \(x \in \mathcal{R}\), we color \(x\) with \(n + c\) where \(c\) is the color of \(\lambda(x)\) in the sum-free coloring of  \([\![1,p]\!]\).
 Let \((x, y) \in \mathcal{R}^2\). The cases are twofold.
@@
 	\item \underline{\(\lambda(x+y) = \lambda(x) + \lambda(y)\)} \\
-	In this case, we use the sum-free property of the colouring of \([\![1,p]\!]\) (in block \(\mathcal{C}\), we only use colours \(1, ..., n\)).
+	In this case, we use the sum-free property of the coloring of \([\![1,p]\!]\) (in block \(\mathcal{C}\), we only use colors \(1, ..., n\)).
 
 	\item \underline{\(\lambda(x+y) \neq \lambda(x) + \lambda(y)\)} \\
-	In this case, we do not have information about the colour of \(\lambda(x+y)\). Thereby, we want to have \(x+y \in \mathcal{C}\).
+	In this case, we do not have information about the color of \(\lambda(x+y)\). Thereby, we want to have \(x+y \in \mathcal{C}\).
 	A simple solution is to limit the horizontal movement, that is if the sum changes line, not to move too far so that it stays in \(\mathcal{C}\).
@@
 	is then expressed as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written as
-	 \(\text{max}(l, r) \leqslant w\).
+	 \(\max(l, r) \leqslant w\).
 \end{itemize}
 
-\underline{\textbf{\(\mathcal{C}\) block}} \\
-In this block,  we use colors \(1, ..., n\). We colour an integer \(x\) according to its column number, written \(\tilde{\pi}(x)\). It is linked to the
-projection on the first line, written \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\). A simple solution is to colour \(x\) with the same colour
-as \(\tilde{\pi}(x)\) in the weakly sum-free colouring of \([\![1,q]\!]\). As long as \(2b \leqslant a + r\) (not going two far to the right) and there
+\noindent \underline{\textbf{\(\mathcal{C}\) block}}
+\par
+In this block,  we use colors \(1, ..., n\). We color an integer \(x\) according to its column number, denoted by \(\tilde{\pi}(x)\). It is linked to the
+projection on the first line, denoted by \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\). A simple solution is to color \(x\) with the same color
+as \(\tilde{\pi}(x)\) in the weakly sum-free coloring of \([\![1,q]\!]\). As long as \(2b \leqslant a + r\) (not going two far to the right) and there
 is no \(x \in \tilde{\pi}(\mathcal{C})\) such that \(2x \in \tilde{\pi}(\mathcal{C})\) (so that we do not have a sum in \(\mathcal{C}\) when
-taking two numbers in the same column), the colours \(1, ..., n\) are sum-free.
+taking two numbers in the same column), the colors \(1, ..., n\) are sum-free.
 
@@
 \begin{definition}
-Let \( (p,n,b) \in (\mathbb{N}^*)^3\), Let \((A_1,...,A_n)\) a partition of  \([\![1, p]\!]\).
-This partition is said to be a b-weakly-sum-free template (b-WSF-template) of \(n\) colors and lenght \(p\) when:
+Let \( (a,n,b) \in (\mathbb{N}^*)^3\), Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
+This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WSF-template) with width \(a\) and \(n\) colors if:
+
 \begin{itemize}
@@
 \item For \(A_n\) (the special subset): \[\forall (x,y) \in A_n^2, \,
-x+y>b+2(p-b) \implies x+y-2(p-b)\notin A_n\]
+x+y>b+2a \implies x+y-2a\notin A_n\]
 \item For the others subsets: \\ \[\forall i \in [\![0,n-1]\!], \, \forall(x,y) \in A_i^2, \,
-x+y>p \implies \pi(x+y) \notin A_i
+x+y>a+b \implies \pi(x+y) \notin A_i
 \]
@@
 \begin{definition}
-Let \( (k,b) \in (\mathbb{N}^*)^2\). If there exist \(p\) such that exists a partition of \([\![1, p]\!]\) into \(k\)
-subsets which is a \(b\)-WSF-template of \(k\) colors and lenght \(p\), we note:
-\\\\\(\WS_b^+=-b+\max \{p\in \mathbb{N}^*\)/ there exists a partition of \([\![1, p]\!]\) into \(k\) subsets which is a
-\(b\)-WSF-template of \(k\) colors and lenght \(p\) \}
-\\\\
-If this \(p\) does not exist, we set \(\WS_b^+= 0\)
+Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WSF-template with width \(a\) 
+and \(n\) colors, define:
+\[
+\WS_b^+(n)=-b+\max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WSF-template with width } a \text{ and } n \text{ colors} \}
+\]
+If no such \(a\) exists, set \(\WS_b^+(n) = 0\).
 \end{definition}
@@
 \begin{definition}
-Let \( n \in \mathbb{N}^*\), we define \(\WS^+(n)=\max_{b\in \mathbb{N}^*} \{\WS_b^+(n)\}\)
+Let \( n \in \mathbb{N}^*\). Define 
+\[
+\WS^+(n)=\max_{b\in \mathbb{N}^*} \WS_b^+(n)
+\]
 \end{definition}
@@
 \begin{proposition}
-	Let \(n \in [\![2, +\infty]\!]\), we have :
+Let \(n \in [\![2, +\infty]\!]\). Then
 \[
@@
 The lower bound comes from the analogous of Abott and Hanson's construction for weak Schur numbers.
-The upper bound comes from the fact that a WSF-template of length \(p\) with \(n\) colors is also a partition of
-\([\![1, p]\!]\) into \(n\) sum-free subsets.
+The upper bound comes from the fact that a WSF-template with width \(a\) and \(n\) colors contains a partition of
+\([\![1, a]\!]\) into \(n\) sum-free subsets.
 \end{proof}
@@
 \begin{theorem}
-Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \(k\)
-sum-free subsets of \([\![1,p]\!]\) and a partition of \(n\) subsets \((A_1,....,A_n)\) of \([\![1, q]\!]\) which is a
-\(b\)-WSF-template of \(n\) colors and lenght \(q\),
- then there exists a partition of \([\![1, b+p \times (q-b)]\!]\) into \((k+n-1)\) weakly sum-free subsets.
+Let \((a,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\) 
+into \(k\) sum-free subsets and a \(b\)-WSF-template \((A_1,...,A_n)\) with width \(a\) and \(n\) colors, 
+then there exists a partition of \([\![1, b+p \times a]\!]\) into \((k+n-1)\) weakly sum-free subsets.
 \end{theorem}
 
-In particular, if we choose \(p = S(k)\) and \(q = \WS^+(n)\) in the last theorem, the next corollary follows.
+In particular, by setting \(p = S(k)\) and \(a = \WS^+(n)\) in the last theorem, the next corollary follows.
 
@@
 not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by \\
-\[\max \left\{ b + \min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}\]
+\[
+\max_{b \in \mathbb{N}^*} \left\{\min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}
+\]
 \end{remark}
@@
 \begin{proof}[\textsc{Proof.}]
-Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let \(a=q-b\). \\
-We denote by \(g\) the colouring associated to the partition of \([\![1,q]\!]\) and \(h\) the
-one associated to the partition of \([\![1,p]\!]\).
-\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a \(b\)-WSF-template.}
-\]
-\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
-\Longrightarrow h(x+y) \neq h(x)
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \( (p,k) \in (\mathbb{N}^*)^2\). Set \(q = a + b\). \\
+We denote by \(g\) the coloring associated to the \(b\)-WSF-template  and \(h\) the one associated 
+to the sum-free partition of \([\![1,p]\!]\).
+
+\[
+\begin{array}{l l}
+	g : [\![1, q]\!] & \longrightarrow [\![1,n]\!] \\
+	h : [\![1,p]\!] & \longrightarrow [\![1,k]\!]
+\end{array}
 \]
@@
 \begin{proposition}
-Let \((b, k, p) \in \mathbb{N}^*)^3\) and let \(f\) be a colouring associated to a \(b\)-WSF-template of length \(p\) with \(k\) colors. Let
-\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a colouring \(g\) of
+Let \((b, k, a) \in \mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WSF-template with width \(p\) and \(k\) colors. Let
+\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a coloring \(g\) of
 \([\![b + 1, b + c]\!]\) with \(k\) colors such that:
@@
 
-Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n))\), we have\\
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(i \longmapsto g(i - p S(n))\), we have\\
 \[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
@@
 \par These modifications work as follows. One may notice that the first row (excluding the "tail") has constraints that other rows
-do not have because of the tail, especially if the special color appears in the tail as well. Thus allowing to have a colouring on the
-first row different from the colouring of the other rows would weaken the constraints. Acutally, one may even go further by
+do not have because of the tail, especially if the special color appears in the tail as well. Thus allowing to have a coloring on the
+first row different from the coloring of the other rows would weaken the constraints. Acutally, one may even go further by
 noticing that on the one hand the first (ordered) color of the sum-free partition used for the extension procedure has more
@@
 \par
-To sum up, one can look for a generalised WSF-template that uses a special colouring for the tail and the first row, a
-colouring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a colouring for all
-the other rows and a special colouring for the last numbers (as previously explained for the improvement of the additive
+To sum up, one can look for a generalised WSF-template that uses a special coloring for the tail and the first row, a
+coloring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a coloring for all
+the other rows and a special coloring for the last numbers (as previously explained for the improvement of the additive
 constant of WSF-templates).
@@
 \begin{theorem}
-	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template of \(k+1\) colors and lenght \(p\),
-	and \(WSF\)-template of \(n\) color and lenght \(q\), then there exists \(WSF\)-template of \((n+k)\) and lenght \(pq\).
+Let \((k,p), (n,a) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors and a 
+\(WSF\)-template with width \(a\) and \(n\) colors, then there exists \(WSF\)-template with width \(pq\) and \((n+k)\)
+ colors.
 \end{theorem}
@@
 \begin{corollary}
-	Let \(n, k \in \mathbb{N}^*\), we have \\
-	\[ \WS^+(n+k) \geqslant S^+(k+1) \WS^+(n) \]
+Let \(n, k \in \mathbb{N}^*\). Then
+\[
+\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n)
+\]
 \end{corollary}
@@
 It uses the first sophistication explained in the previous subsection in order to add the last number in the first color.
-As for the fourth inequality, it was obtained by combining an optimal SF-template of length 33 with a WSF-template of length 4.
+As for the fourth inequality, it was obtained by combining an optimal SF-template with width 33 with a WSF-template with width 4.
 The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
@@
 
-\begin{center}
-\begin{tabular}{|*{5}{c|}}
-    \hline
+\renewcommand{\arraystretch}{0.2}
+
+\[
+\begin{array}{c}
+	\resetarraystretch
+	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
+	\CodeBefore
+		\cellcolor{yellow}{2-4}
+		\cellcolor{yellow}{2-5}
+		\cellcolor{yellow}{3-2}
+		\cellcolor{yellow}{4-3}
+	\Body
 		n & 8 & 9 & 10 & 11 \\
-	\hline
-	\(4S(n-1) + 2 \) & 6\,722 & 21\,146 & \cellcolor{yellow} 71\,214 & \cellcolor{yellow} 243\,794\\
-	\hline
-	\(13S(n-2) + 8 \) & \cellcolor{yellow} 6\,976 & 21\,848 & 68\,726 & 231\,447\\
-	\hline
-	\(42S(n-3) + 24 \) & 6\,744 & \cellcolor{yellow} 22\,536 & 70\,584 & 222\,036 \\
-	\hline
-	\(127S(n-4) + 68 \) & 5\,656 & 20\,388 & 68\,140 & 213\,428\\
-	\hline
-	\hline
+		4 \, S(n-1) + 2 & 6\,722 & 21\,146 & 71\,214 & 243\,794 \\
+		13 \, S(n-2) + 8 & 6\,976 & 21\,848 & 68\,726 & 231\,447 \\
+		42 \, S(n-3) + 24 & 6\,744 & 22\,536 & 70\,584 & 222\,036 \\
+	\end{NiceArray}
+	\\ \\
+	\resetarraystretch
+	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
+	\CodeBefore
+		\cellcolor{yellow}{2-2}
+		\cellcolor{yellow}{2-5}
+		\cellcolor{yellow}{3-3}
+		\cellcolor{yellow}{4-4}
+	\Body
 		n & 12 & 13 & 14 & 15 \\
-	\hline
-	\(4S(n-1) + 2 \) & \cellcolor{yellow} 815\,314 & 2\,554\,194 & 8\,045\,162 & \cellcolor{yellow} 27\,061\,154\\
-	\hline
-	\(13S(n-2) + 8 \) & 792\,332 & \cellcolor{yellow}2\,649\,772 & 8\,301\,132 & 26\,146\,778 \\
-	\hline
-	\(42S(n-3) + 24 \) & 747\,750 & 2\,559\,840 & \cellcolor{yellow} 8\,560\,800 &  25\,886\,224 \\
-	\hline
-	\(127S(n-4) + 68 \) & 671\,390 & 2\,261\,049 & 7\,740\,464 & 25\,886\,224 \\
-	\hline
-\end{tabular}
-\end{center}
+		4 \, S(n-1) + 2 & 815\,314 & 2\,554\,194 & 8\,045\,162 & 27\,061\,154 \\
+		13 \, S(n-2) + 8 & 792\,332 & 2\,649\,772 & 8\,301\,132 & 26\,146\,778 \\
+		42 \, S(n-3) + 24 & 747\,750 & 2\,559\,840 & 8\,560\,800 &  25\,886\,224 \\
+	\end{NiceArray}
+\end{array}
+\]
+
+\resetarraystretch
 

### 2021-05-07 article/article.tex
notations
relecture (pas encore terminée partie weak schur)

@@
 \usepackage[utf8]{inputenc}
+\usepackage{siunitx}
 
@@
 \usepackage{multirow}
+\usepackage{nicematrix}
 \usepackage[a4paper, total={6in, 8in}]{geometry}
@@
 \newcommand{\WS}{\mathit{WS}}
+\newcommand{\docarraystretch}{1.2}
+\newcommand{\resetarraystretch}{\renewcommand{\arraystretch}{\docarraystretch}}
+\resetarraystretch
 
@@
 continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. Finding templates allows us to 
-apply Rowley's construction and to get explicit partitions improving lower bounds as well as the growth rate for 
-both Schur numbers and Ramsey numbers \(R_n(3)\). We also developed a new method to improve lower bounds on 
-weak Schur numbers. Furthermore, this paper tries to analyze former works on the subject based on the principle 
-that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding the 
-previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption upon imposing certain conditions 
-on the good 5-subsets partition. The new lower bounds include \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\),
-\(\WS (9) \geqslant 22536 \) and \(\WS (10) \geqslant 71214 \).
+get explicit partitions improving lower bounds as well as the growth rate for both Schur numbers and Ramsey 
+numbers \(R_n(3)\). We also developed a new method to improve lower bounds for weak Schur numbers. 
+Furthermore, this paper tries to analyze former works on weak Schur numbers based on the principle that good 
+partitions into \(n+1\) weakly sum-free subsets start with a good partition into \(n\) weakly sum-free subsets. 
+We show that exceeding the previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption 
+upon imposing certain conditions on the good 5-subsets partitions. The new lower bounds include 
+\(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS (9) \geqslant 22\,536 \) and 
+\(\WS (10) \geqslant 71\,214 \).
 
@@
 
-\include{definitions_notations.tex}
+% \include{definitions_notations.tex}
 
@@
 \qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
-Schur numbers which is relatively new. Therefore, we would not be surprised if lower bounds are later improved 
+Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
 using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
@@
 \bibliography{biblio}
-\bibliographystyle{ieeetr}
+\bibliographystyle{IEEEtran}
 

### 2021-05-07 article/introduction.tex
relecture (pas encore terminée partie weak schur)

@@
 
-\qquad We are interested in partioning the set of integers \(\{1, ..., p\}\) in \(n\) subsets such that there is no 
+\qquad We are interested in partioning the set of integers \(\{1, ..., p\}\) into \(n\) subsets such that there is no 
 subset containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are 
@@
 \par
-As for smaller numbers, the best lower bounds were obtained by conducting a computer search. Eliahou \cite{ELIAHOU2012175}, 
-Rafilipojaona \cite{Rafilipojaona} and Bouzy \cite{Bouzy2015AnAP} improved lower bounds with Monte-Carlo methods. It 
-has been the main approch in the previous decade. 
-This search for weakly sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) 
-colors starts with a good weakly sum-free partition into \(n\) colors. This assumption was necessary in order for the Monte-Carlo
-approch to yield results. However, we show in the \hyperlink{sat}{last section} how this search space may not countain
-the optimal solution. Thus further work using similar methods might need to put that assumption aside and 
-find a different search space.
+As for smaller weak Schur numbers, the best lower bounds were obtained by conducting a computer search. Eliahou 
+\cite{EliahouBook}, Bouzy \cite{Bouzy2015AnAP} and Rafilipojaona \cite{Rafilipojaona} improved the lower 
+bounds with Monte-Carlo methods. This was the main approach during the past decade. This search for weakly 
+sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) colors 
+starts with a good weakly sum-free partition into \(n\) colors. 
+However, we show in the \hyperref[SearchSpace]{last section} that this search space may not contain the optimal 
+solutions. Thus further works using similar methods might need to put that assumption aside and find a different 
+search space.
 
 \par
-In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers which generalizes Abbott and 
-Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. Rowley also gives two 
-inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements over previous lower 
-bounds which besides do utilize the \textit{weakly} sum-free hypothesis.
+In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers \cite{RowleyRamsey} which 
+generalizes Abbott and Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. 
+Rowley also gives two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
+over previous lower bounds which besides do utilize the \textit{weakly} sum-free hypothesis.
 
@@
     \multirow{2}{*}{Before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
-      & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{ELIAHOU2012175} & 
-    \cite{ELIAHOU2012175} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
+      & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{AbbottHanson} & 
+    \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
     \hline
@@
 
-\par
-The main contribution of this article is a generalization of the concept of template to weak Schur numbers. 
-This gives new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a 
-special case an analogous for weak Schur numbers of Abbott and Hanson's construction for Schur numbers.
+\qquad The main contribution of this article is a generalization of the concept of template to weak Schur numbers. 
+It gives new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special 
+case an analogous for weak Schur numbers of Abbott and Hanson's construction for Schur numbers.
 
 \par
-We first explain Rowley's template-based construction in the context of Schur numbers and then give 
-new templates, thus providing new lowers bounds and inequalities as well as showing that the growth rates 
-for both Schur and Ramsey numbers \(R_n(3)\) exceed 3.28.
+In the \hyperref[Schur]{first section}, we explain Rowley's template-based construction in the context of 
+Schur numbers and then give new templates, thus providing new lowers bounds and inequalities as well as 
+showing that the growth rates for both Schur and Ramsey numbers \(R_n(3)\) exceed 3.28.
 
 \par
-We then  generalize the concept of templates to weak Schur numbers and provide new lower bounds for weak 
-Schur numbers.
+Then, in the \hyperref[WeakSchur]{second section}, we generalize the concept of templates to weak Schur numbers 
+and provide new lower bounds for weak Schur numbers.
 
 \par
-Finally, we analyze the significant difference between new lower bounds obtained with templates and the former 
-lower bounds obtained by computer search and we provide evidence which indicate that the main assumption 
-made in those articles removes the optimal partitions from the search space.
+Finally, in the \hyperref[SearchSpace]{third section}, we analyze the significant difference between new lower 
+bounds obtained with templates and the former lower bounds obtained by computer search and we provide 
+evidence which indicate that the main assumption made in those articles removes the optimal partitions from the 
+search space.
 
@@
 
-We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.
+\qquad We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.
 
 \begin{definition}
-A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} when:
+A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} if
 \[ \forall (a,b) \in A^2 \text{, } a+b \notin A\]
@@
 \begin{definition}
-A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} when:
+A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} if
 \[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B\]
@@
 such that there exists no partition of \([\![1,q]\!]\) into \(n\) sum-free subsets for any \(q \geqslant p\). A similar
-property holds for weakly sum-free subsets (reference necessaire). These observations lead to the following definitions.
+property holds for weakly sum-free subsets \cite{Irving1973}. These observations lead to the following definitions.
 
 \begin{definition}
-Let \(n \in \mathbb{N}^*\). There exists a greatest integer that we denote \(S(n)\) (\textit{resp. \(\WS (n)\)}) such that
+Let \(n \in \mathbb{N}^*\). There exists a greatest integer denoted by \(S(n)\) (\textit{resp. \(\WS (n)\)}) such that
 \([\![1,S(n)]\!]\) (resp. \([\![1, \WS (n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
 subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(\WS (n)\) the
-\(n\)\textsuperscript{th} weak
-Schur number}.
+\(n\)\textsuperscript{th} weak Schur number}.
 \end{definition}
 
-Given a partition of \([\![1, p]\!]\) in \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We also denote
+Given a partition of \([\![1, p]\!]\) into \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We also denote
 \(m_i = \min(A_i)\). By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do 

### 2021-05-07 article/schur.tex
relecture (pas encore terminée partie weak schur)

@@
 \begin{definition}
-A SF-template with width \(p\) and \(n\) colors is defined as a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets 
-\(A_1, A_2, ..., A_n\) verifying:
+Let \((p,n) \in (\mathbb{N}^*)^2\). A SF-template with width \(p\) and \(n\) colors is defined as a partition of 
+\([\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) verifying
 \[
@@
 	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the maximal width of a SF-template with \(n\) colors. 
-	\(S^+(n)\) is well defined and verifies:
+	\(S^+(n)\) is well defined and verifies
 	\[
@@
 \begin{theorem}
-	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors 
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors 
 	and a partition of \([\![1,q]\!]\) into \(n\) sum-free subsets then there exists a partition of \([\![1,pq+m_{k+1}
@@
 to the line number. This way the "blocks" act as safe areas for each other. We give here an example for \(p = 9\), 
-\(q = 4\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott 
-and Hanson's construction and with a SF-template which is not of this type. In both cases, the special color is grey.
+\(q = 4\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott and 
+Hanson's construction and with a SF-template which is not included in Abbott and Hanson's construction. In both cases, 
+the special color is grey.
 
@@
 
-We now proceed to prove the above mentioned theorem.\\
+We now proceed to prove the above mentioned theorem.
 
@@
 
-\noindent \underline{\textbf{First case:} \(h(x) \leqslant k\)} \\
-\qquad Assume that \(h(x+y) \leqslant k\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of \(h\) 
+\noindent \underline{\textbf{First case:} \(h(x) \leqslant k\)}
+\par
+Assume that \(h(x+y) \leqslant k\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of \(h\) 
 and given that \(h(u) = h(v)\), \(f(u) = f(v)\). Distinguish between two cases according to the value of \(x + y\).
@@
 
-\noindent \underline{\textbf{Second case:} \(h(x) \geqslant k + 1\)} \\
-\qquad \(h(x) = k + g(\alpha) = 
+\noindent \underline{\textbf{Second case:} \(h(x) \geqslant k + 1\)}
+\par
+\(h(x) = k + g(\alpha) = 
 k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As in the first case, distinguish between two cases according 
@@
 \begin{itemize}
-\item If \(u + v > p\), write \(w = u + v - p \in [\![1, p]\!]\). Then \(x + y = (\alpha + \beta - 1) p + w\). Assume that 
-	\(h(x+y) \geqslant k + 1\),  otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition, \(h(x + y) = k + g(\alpha + 
-	\beta)\). Given that \(g(\alpha) = g(\beta)\), the sum-free property of \(g\) implies \(g(\alpha + \beta) 
+\item \begin{sloppypar}
+	If \(u + v > p\), write \(w = u + v - p \in [\![1, p]\!]\). Then \(x + y = (\alpha + \beta - 1) p + w\). Assume that 
+	\({h(x+y) \geqslant k + 1}\),  otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition, \({h(x + y) = k + g(\alpha + 
+	\beta)}\). Given that \(g(\alpha) = g(\beta)\), the sum-free property of \(g\) implies \(g(\alpha + \beta) 
 	\neq g(\alpha)\) that is \(h(x + y) \neq h(x)\).
+	\end{sloppypar}
 \item  If \(u + v \leqslant p\), write \(w = u + v \in [\![1, p]\!]\). Then \(x+y = (\alpha + \beta- 2) p + w\). The sum-free 
@@
 \begin{proposition}
-Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a SF-template with width \(p\) and \(k+1\) 
+Let \((p, k) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a SF-template with width \(p\) and \(k+1\) 
 colors. Let \(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a coloring \(g\) of 
-\([\![1, b]\!]\) with \(k+1\) colors such that:
+\([\![1, b]\!]\) with \(k+1\) colors such that
 
@@
 
-This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
-column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
-intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the coloring of the last 
-row can be weakened.
+This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but 
+adding this column to the color would create sums in the color when applying the extension procedure. However, the 
+last row does not intereact with the right-most columns when it comes to creating new sums. As a result, the hypotheses 
+made on the coloring of the last row can be weakened.
 
-We also have a similar construction theorem where only \(S^+\) is involved.
+There is a construction theorem for SF-templates as well.
 
 \begin{theorem}
-	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with and \(p\) and \(k+1\) colors,
-	and a \(SF\)-template with width \(q\) and \(n\) colors, then there exists \(SF\)-template with width \(pq\) and \((n+k)\).
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors,
+and a SF-template with width \(q\) and \(n\) colors, then there exists \(SF\)-template with width \(pq\) and \((n+k)\) 
+colors.
 \end{theorem}
 
-And the associated inequality :
+And the associated inequality
 
 \begin{corollary}
-	Let \(n, k \in \mathbb{N}^*\), we have \\
+Let \(n, k \in \mathbb{N}^*\). Then
 \[ S^+(n+k) \geqslant S^+(k+1)S^+(n) \]
@@
 \begin{proof}[\textsc{Proof.}]
-The idea is the same as in the previous theorem. The only difference is the SF property inherited 
+The idea is the same as in the previous theorem. The only difference is the SF-template property inherited 
 from the second SF-template.
@@
 \begin{definition}
-A SF-template with \(n\) colors is said to be symmetric if the partition in \(n\) sum-free subsets derived (with the additive constant) from this template is symmetric. 
-A sum-free partition \(A_1, ..., A_n\) of \([\![1, p]\!]\) is said to be symmetric if for all \( x \in [\![1, p]\!]\), \(x\) and \(p + 1 - x\) belong to the same subset 
-(except if \(x = p + 1 - x\)).
+A sum-free partition \(A_1, ..., A_n\) of \([\![1, p]\!]\) is said to be symmetric if for all \( x \in [\![1, p]\!]\), 
+\(x\) and \(p + 1 - x\) belong to the same subset (except if \(x = p + 1 - x\)).
+
+A SF-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
+from this template by applying the extension procedure with a sum-free partition of length 1 is symmetric. 
 \end{definition}
 
-Using a SAT solver, we exhibited SF-templates, hence providing lower bound on \(S^+\) and inequalities 
+We exhibited SF-templates using a SAT solver, hence providing lower bound on \(S^+\) and inequalities 
 of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
 \((a, b)\) (for the lexicographic order). When the number of colors excceeded 5, in order to reduce the search space we 
-looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
+only looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
 the \(m_c\)'s out of being too small. Further details about the encoding as a SAT problem can be found in \cite{Heule2017}.
@@
 Here are the best inequalities on Schur numbers so far (the templates corresponding to the third, fourth and fifth 
-inequalities can be found in the appendix):
+inequalities can be found in the appendix).
 \[
@@
 the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
-likely not optimal but should not be too far from the optimal. 
-Finally, the sixth one is obtained by combining (see below) the SF-template with width 380 and the one with width 3. 
-Although we could not find a better SF-template with 7 colors, the last inequality is definetely very far from the 
+likely not optimal but should not be too far from the optimum. 
+Finally, the sixth one is obtained by combining a SF-template with width 380 and one with width 3. 
+Although we could not find a better SF-template with 7 colors, the last inequality is definitely very far from the 
 optimal value. One may try to seek better templates by constraining less the search space and by using 
-Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.
+Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the subject of a future work.
 
@@
 \begin{corollary}
-The growth rate for Schur numbers (and Ramsey numbers \(R_n(3)\))  satisfies \(\gamma \geqslant \sqrt[5]{380} \approx 3.28\).
+\begin{sloppypar}
+The growth rate for Schur numbers (and Ramsey numbers \(R_n(3)\))  satisfies \({\gamma \geqslant \sqrt[5]{380} \approx 3.28}\).
+\end{sloppypar}
 \end{corollary}
@@
 It is a mere consequence of the inequality \( S(n+5) \geqslant 380S(n) + 148\). As for Ramsey
-numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}).
+numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}) hence the result.
 \end{proof}
@@
 In the next section, we provide similar results for weak Schur numbers. We introduce WSF-templates and a corresponding sequence, 
-\(WS^+\). We then derive similar relations and construction method allowing us to find new lower bounds for weak Schur numbers.
+\(\WS^+\). We then derive similar relations and a construction method allowing us to find new lower bounds for weak Schur numbers.

### 2021-05-07 article/weakschur.tex
relecture (pas encore terminée partie weak schur)

@@
 
-First, put the integers of \([\![1, ap + q]\!]\) in the following table (with \(a\) columns and \(p + 1\) lines) and divide it into 3 blocks (the columns are numbered from \(-l\) to \(+q\)):
+First, put the integers of \([\![1, ap + q]\!]\) in the following table (with \(a\) columns and \(p + 1\) lines) 
+and divide it into 3 blocks (the columns are numbered from \(-l\) to \(+q\)).
 
@@
 Let \( (a,n,b) \in (\mathbb{N}^*)^3\), Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
-This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WSF-template) with width \(a\) and \(n\) colors if:
+This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WSF-template) with width \(a\) and \(n\) colors if
 
@@
 \item \(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free
-\item For \(A_n\) (the special subset): \[\forall (x,y) \in A_n^2, \,
-x+y>b+2a \implies x+y-2a\notin A_n\]
-\item For the others subsets: \\ \[\forall i \in [\![0,n-1]\!], \, \forall(x,y) \in A_i^2, \,
-x+y>a+b \implies \pi(x+y) \notin A_i
+\item For \(A_n\) (the special subset)
+	\[
+	\forall (x,y) \in A_n^2, \,x+y>b+2a \implies x+y-2a\notin A_n
+	\]
+\item For the others subsets
+	\[
+	\forall i \in [\![0,n-1]\!], \, \forall(x,y) \in A_i^2, \, x+y>a+b \implies \pi(x+y) \notin A_i
 	\]
@@
 Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WSF-template with width \(a\) 
-and \(n\) colors, define:
+and \(n\) colors, define
 \[
@@
 \begin{theorem}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\) 
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\) 
 into \(k\) sum-free subsets and a \(b\)-WSF-template \((A_1,...,A_n)\) with width \(a\) and \(n\) colors, 
@@
 
-Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) as follows:
+Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) as follows
 
@@
 
-We have to verify that f induces weakly-sum-free templates:\\
+We have to verify that f induces weakly-sum-free templates\\
 \\
@@
 \underline{if \((x,y) \in \mathcal{T} \times \mathcal{C}\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
-We distinguish two cases:
+We distinguish two cases
 
@@
 \underline{if \((x,y) \in \mathcal{T} \times \mathcal{R}\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
-\\Then, \(f(x)=f(y)=n\). We distinguish two cases:
+\\Then, \(f(x)=f(y)=n\). We distinguish two cases
 
@@
 \underline{if \((x,y) \in \mathcal{C}^2\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
-\\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases:
+\\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases
 
@@
 \\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
-\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases:
+\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases
 
@@
 \begin{proposition}
-Let \((b, k, a) \in \mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WSF-template with width \(p\) and \(k\) colors. Let
+Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WSF-template with width \(p\) and \(k\) colors. Let
 \(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a coloring \(g\) of
-\([\![b + 1, b + c]\!]\) with \(k\) colors such that:
+\([\![b + 1, b + c]\!]\) with \(k\) colors such that
 
@@
 
-And the associated inequality :
+And the associated inequality
 
@@
 \qquad Having found suitable templates, which can be found in the appendix, with a SAT solver, we claim that for all \(n \in
-\mathbb{N}^*\):
+\mathbb{N}^*\)
 

### 2021-05-08 article/weakschur.tex
preuve wsf templates

@@
 for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
-we then introduce WSF-templates as well as the sequence \(\WS^+(n)\). We find suitable templates and use them to
+we then introduce WSF-templates as well as an associated sequence \(\WS^+(n)\). We find templates and use them to
 provide new lower bounds for weak Schur numbers.
@@
 
-\qquad Up to now, there was no equivalent for weak Schur numbers of Abbott and Hanson's construction for Schur numbers
-\cite{AbbottHanson}. Here we give a general lower bound for weak Schur numbers as a function of both regular and
-weak Schur numbers. The following theorem, inspired by Rowley's inequalities for \(\WS (n+1)\) and \(\WS (n+2)\),
-was found and proved by Romain Ageron.
+\qquad Up to now, no equivalent for weak Schur numbers of Abbott and Hanson's construction for Schur numbers
+\cite{AbbottHanson} was known. Here we give a general lower bound for weak Schur numbers as a function of both 
+regular and weak Schur numbers. The following theorem, inspired by Rowley's inequalities for \(\WS (n+1)\) and 
+\(\WS (n+2)\), was found and proved by Romain Ageron.
 
@@
 \label{theorem}
-Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
+\begin{sloppypar}
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
 subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free
-subsets then there exists a partition of \([\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]\) into \(n+k\)
+subsets then there exists a partition of \({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\)
 weakly sum-free subsets.
+\end{sloppypar}
 \end{theorem}
 
-In particular, if we choose \(q = \WS (n)\) and \(p = S(k)\) in the last theorem, the next corollary follows.
+In particular, by setting \(q = \WS (n)\) and \(p = S(k)\) in the above theorem, one obtains the following corollary.
 
@@
 
-Let \((p, q) \in \mathbb{N}^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
+Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
 subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
@@
 \renewcommand{\arraystretch}{1.7}
+\setlength{\arraycolsep}{4pt}
 
 \[
-\begin{NiceArray}{|*{13}{c|}}[corners=NW,standard-cline,hlines]
+\begin{NiceArray}{*{13}{c}}[corners=NW,hvlines]
 \CodeBefore
@@
 \resetarraystretch
+\setlength{\arraycolsep}{6pt}
 
@@
 	\item \underline{\(\lambda(x+y) = \lambda(x) + \lambda(y)\)} \\
-	In this case, we use the sum-free property of the coloring of \([\![1,p]\!]\) (in block \(\mathcal{C}\), we only use colors \(1, ..., n\)).
-
+	In this case, we use the sum-free property of the coloring of \([\![1,p]\!]\) (in block \(\mathcal{C}\), we only 
+	use colors \(1, ..., n\)).
 	\item \underline{\(\lambda(x+y) \neq \lambda(x) + \lambda(y)\)} \\
-	In this case, we do not have information about the color of \(\lambda(x+y)\). Thereby, we want to have \(x+y \in \mathcal{C}\).
-	A simple solution is to limit the horizontal movement, that is if the sum changes line, not to move too far so that it stays in \(\mathcal{C}\).
-	There, the maximal displacement to the left (resp. to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left
-	is then expressed as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written as
-	 \(\max(l, r) \leqslant w\).
+	In this case, we do not have information about the color of \(\lambda(x+y)\). Thereby, we want to have 
+	\(x+y \in \mathcal{C}\). A simple solution is to limit the horizontal movement, that is if the sum changes line 
+	(that is its line number is different from \(\lambda(x) + \lambda(y)\)), not to move too far from \((\lambda(x) 
+	+ \lambda(y)) a\) so that the sum stays in \(\mathcal{C}\). There, the maximal displacement to the left (resp. 
+	to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left is then expressed 
+	as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written 
+	as \(\max(l, r) \leqslant w\).
 \end{itemize}
@@
 
-\qquad In this subsection, we introduce WSF-templates and define the objects and prove the results needed
-for the general theorem on templates for weak Schur numbers.
+\qquad In this subsection, we introduce WSF-templates and prove calculative results for the general construction 
+theorem on templates for weak Schur numbers.
 
 \begin{definition}
-
 Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
@@
 
-If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\).
+If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\). Notice that 
+\({\forall x \in \mathbb{Z}, \pi(x) = x \mod a}\) and \({\forall x \in [\![b + 1, a + b]\!], b + 1 \leqslant \pi(x) \leqslant a + b}\).
 
+\begin{sloppypar}
 \(\pi\) is the projection on the first line mentioned in the intuitive explanation. 
+\end{sloppypar}
 
 \begin{proposition}
-Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\) such that \(x+\pi(y) \leqslant a+b\). Then \(\pi(x+y)=x+\pi(y)\).
+\label{prop1}
+\[
+\forall x \in [\![b + 1, a + b]\!], \pi(x) = x
+\]
 \end{proposition}
@@
 \begin{proof}[\textsc{Proof.}]
-Let  \(x\in [\![1,b]\!]\), and  \(y\in \mathbb{N}^*\) such that \(x+\pi(y)\leqslant a+b\).
+\begin{sloppypar}
+Let \(x \in [\![b + 1, a + b]\!]\). If \(x < a\) then \(x \mod a = x \notin [\![1, b]\!]\). Hence \(\pi(x) = x\). 
+Otherwise, \({x \mod a = x - a \in [\![1, b]\!]}\). Hence \({\pi(x) = x - a + a = x}\).
+\end{sloppypar}
+\end{proof}
 
-\noindent if \(x+\pi(y)< a \):
+\begin{proposition}
+\label{prop2}
+Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\). Then 
+\[
+\pi(x+\pi(y)) = \pi(x+y)
+\]
+\end{proposition}
 
+\begin{proof}[\textsc{Proof.}]
+It is a direct consequence of \(pi(x) = x \mod a\). \\
+\end{proof}
+
+\begin{proposition}
+\label{prop3}
+Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\) such that \(x+\pi(y) \leqslant a+b\). Then 
 \[
-\begin{array}{c c l l}
-	\pi(x+y) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a) & \\
-	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a) & \text{since } \pi(y)=y \mod a \\
-	& = & x+ \pi(y) &
-\end{array}
+\pi(x+y)=x+\pi(y)
 \]
+\end{proposition}
 
-\noindent if \(x+\pi(y)\geqslant a\):
+\begin{proof}[\textsc{Proof.}]
+\(\pi(y) \geqslant b + 1\) and thus \(b + 1 \leqslant x + \pi(y) \leqslant a + b\).
 \[
-\begin{array}{c c l l}
-	\pi(x+y) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)& \\
-	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a) & \text{since } \pi(y)=y \mod a \\
-	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) & \\
-	& = & x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]}(x+\pi(y) - a) & \\
-	& = & x+\pi(y) - a +a & \text{since } x+\pi(y) - a \in [\![0,b]\!] \\
-	& = & x+\pi(y) &
+\begin{array}{l l l l}
+	\pi(x + y) & = & \pi(x + \pi(y)) & proposition \ref{prop2} \\
+	 & = & x + \pi(y) & proposition \ref{prop1}
 \end{array}
@@
 \begin{proposition}
-Let \((x,y)\in (\mathbb{N}^*)^2\). Then \(\pi(\pi(x)+\pi(y))=\pi(x+y)\).
+\label{prop4}
+Let \((x,y)\in (\mathbb{N}^*)^2\). Then 
+\[
+\pi(\pi(x)+\pi(y))=\pi(x+y)
+\]
 \end{proposition}
@@
 \begin{proof}[\textsc{Proof.}]
-Let \((x,y)\in (\mathbb{N}^*)^2\).
-
-\[
-\begin{array}{c c l}
-	\pi(\pi(x)+\pi(y)) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
-	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a) \mod a) \\
-	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
-	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
-	& = & \pi(x+y)
-\end{array}
-\]
+It is a direct consequence of \(\pi(x) = x \mod a\). \\
 \end{proof}
@@
 \begin{definition}
-
 Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
@@
 \begin{proposition}
-Let \((a,b)\in (\mathbb{N}^*)^2\) such that \(a>b\) and let \(x\in \mathbb{N}^*\). Then \(x=a\lambda(x)+\pi(x)-a\).
+\label{prop5}
+Let \(x\in \mathbb{N}^*\). Then 
+\[
+x=a\lambda(x)+\pi(x)-a
+\]
 \end{proposition}
@@
 
-\noindent  if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)
+\noindent  if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\) \\
+\vspace{1mm}
+\noindent if \(x \mod a \leqslant b\) then
+\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\) \\
+\end{proof}
 
-\noindent if \(x \mod a \leqslant b\) then
-\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\)
+\begin{proposition}
+\label{prop6}
+Let \(x, y \in \mathbb{Z}\) such that \(\lambda(x + y) = \lambda(y)\). Then 
+\[
+\pi(x + y) = x + \pi(y)
+\]
+\end{proposition}
+
+\begin{proof}[\textsc{Proof.}]
+By applying twice proposition \ref{prop5}, \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\). 
+The result is then obtained by symplying the equality. \\
+\end{proof}
+
+\begin{proposition}
+\label{prop7}
+Let \(x, y \in \mathbb{Z}\) such that \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\). Then 
+\[
+\lambda(x + y) = \lambda(x) + \lambda(y)
+\]
+\end{proposition}
+
+\begin{proof}[\textsc{Proof.}]
+By proposition \ref{prop5}, \(x + y = a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a\). Then
+\[
+\begin{array}{l l l}
+	\lambda(x + y) & = & \left \lfloor \dfrac{x + y - b - 1}{a} \right \rfloor + 1 \vspace{1mm} \\
+	 & = & \left \lfloor \dfrac{a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a - b - 1}{a} \right \rfloor + 1 \vspace{1mm} \\
+	 & = & \lambda(x) + \lambda(y) - 1 \left \lfloor \dfrac{\pi(x) + \pi(y) - b - 1}{a}\right\rfloor \\
+	 & = & \lambda(x)+\lambda(y) -1 +1 ~~~~\text{since } \pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!] \\
+	 & =& \lambda(x)+\lambda(y)
+\end{array}
+\]
 \end{proof}
@@
 \begin{definition}
-Let \( (a,n,b) \in (\mathbb{N}^*)^3\), Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
+Let \( (a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\). Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
 This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WSF-template) with width \(a\) and \(n\) colors if
@@
 \begin{itemize}
-\item \(\forall i \in [\![1, n]\!], \quad A_i\) is weakly-sum-free
-\item \(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free
+\item \(\forall i \in [\![1, n]\!], A_i\) is weakly-sum-free
+\item \(\forall i \in [\![1, n]\!], A_i\backslash [\![1, b]\!]\) is sum-free
 \item For \(A_n\) (the special subset)
@@
 \[
-\WS_b^+(n)=-b+\max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WSF-template with width } a \text{ and } n \text{ colors} \}
+\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WSF-template with width } a \text{ and } n \text{ colors} \}
 \]
@@
 The upper bound comes from the fact that a WSF-template with width \(a\) and \(n\) colors contains a partition of
-\([\![1, a]\!]\) into \(n\) sum-free subsets.
+\([\![1, a]\!]\) into \(n\) sum-free subsets. \\
 \end{proof}
@@
 \begin{theorem}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\) 
-into \(k\) sum-free subsets and a \(b\)-WSF-template \((A_1,...,A_n)\) with width \(a\) and \(n\) colors, 
-then there exists a partition of \([\![1, b+p \times a]\!]\) into \((k+n-1)\) weakly sum-free subsets.
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\) 
+into \(k\) sum-free subsets and a \(b\)-WSF-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors, 
+then there exists a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
 \end{theorem}
 
-In particular, by setting \(p = S(k)\) and \(a = \WS^+(n)\) in the last theorem, the next corollary follows.
+In particular, by setting \(p = S(k)\) and \(a = \WS^+(n + 1)\) in the last theorem, the next corollary follows.
 
 \begin{corollary}
-For every \((n,k) \in (\mathbb{N}^*)^2\), define \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
-Then the following inequality holds.
-\[\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}\]
+Let \(n,k \in \mathbb{N}^*\) and set \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
+Then
+\[
+\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}
+\]
 \end{corollary}
@@
 In the SF-template construction for Schur numbers, the additive constant comes from the fact that the special color does
-not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by \\
+not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by
 \[
@@
 \begin{proof}[\textsc{Proof.}]
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \( (p,k) \in (\mathbb{N}^*)^2\). Set \(q = a + b\). \\
-We denote by \(g\) the coloring associated to the \(b\)-WSF-template  and \(h\) the one associated 
-to the sum-free partition of \([\![1,p]\!]\).
+\begin{sloppypar}
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Denote by \(g\) the coloring 
+associated to the \(b\)-WSF-template  and \(h\) the one associated to the sum-free partition of \([\![1,p]\!]\); where 
+\({g : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({h : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, assume 
+that the sum-free coloring of \([\![1, p]\!]\) is ordered.
+\end{sloppypar}
 
+\par
+NB: In the following 5 predicates, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted for readability.
+\par
+The (weakly) sum-free conditions are expressed as 
 \[
-\begin{array}{l l}
-	g : [\![1, q]\!] & \longrightarrow [\![1,n]\!] \\
-	h : [\![1,p]\!] & \longrightarrow [\![1,k]\!]
+\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
+\begin{array}{l}
+	g(x) = g(y) \\
+	x \neq y
+\end{array}
+\right. \Longrightarrow g(x+y) \neq g(x)
+\]
+\[
+\forall (x,y) \in [\![b+1,a + b]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)
+\]
+\[
+\forall (x,y) \in [\![1,p]\!]^2, h(x) = h(y) \Longrightarrow h(x+y) \neq h(x)
+\]
+
+The additionnal constraints for the WSF-template are
+\[
+\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
+\begin{array}{l}
+	g(x) = g(y) \leqslant n \\
+	x + y > a + b
+\end{array}
+\right. \Longrightarrow g(\pi(x+y)) \neq g(x)
+\]
+\[
+\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
+\begin{array}{l}
+	g(x) = g(y) = n + 1 \\
+	x + y > 2 a + b
+\end{array}
+\right. \Longrightarrow g(x+y - 2 a) \neq g(x)
+\]
+
+Here, we consider \(\pi\) defined in the previous subsection as an application defined on \([\![b + 1, p a + b]\!]\). 
+Split \([\![1, p a + b]\!]\) into 3 subsets.
+
+\begin{itemize}
+	\item \(\mathcal{T} = [\![1, b]\!]\)
+	\item \(\mathcal{C} = \pi^{-1}(g^{-1}([\![1, n]\!]))\)
+	\item \(\mathcal{R} = \pi^{-1}(g^{-1}(\{n + 1\}))\)
+\end{itemize}
+
+Define a new coloring \(f\) as follows
+\[
+\begin{array}{c c c l}
+	h : & [\![1, p a + b]\!] & \longrightarrow & [\![1,n+k]\!] \\
+	& x & \longmapsto & 
+	\left\{ \begin{array}{l l}
+		g(x) & \text{if}~x \in \mathcal{T} \\
+		g(\pi(x)) & \text{if}~x \in \mathcal{C} \\
+		n + h(\lambda(x)) & \text{if}~x \in \mathcal{R}
+	\end{array} \right.
 \end{array}
@@
 
-Define \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) as follows
+\(f\) is well defined since \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) is a partition of  \([\![1, p a + b]\!]\). 
+We now prove that \(f\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) such that \(x \neq y\), 
+\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Distinguish between six cases 
+according to the subsets \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) to which \(x\) and \(y\) belong. It is 
+sufficient to check only six cases out of nine since \(x\) and \(y\) play symmetric roles. \\
 
+\noindent \underline{\textbf{Case 1:} \((x,y) \in \mathcal{T}^2\)}
+\par
+If \(x + y \leqslant b\) then \(f(x+y)=g(x+y)\). Otherwise, \(b < x+y < a+b\) since \(b < a\) and 
+therefore \(\pi(x + y) = x +y\) (proposition \ref{prop1}). Hence in both cases \(f(x+y)=g(x+y)\). Given that 
+\(g\) is a weakly sum-free coloring, \(g(x + y) \neq g(x)\) since \(g(x)=f(x)=f(y)=g(y)\) and \(x \neq y \). That 
+is \(f(x + y) \neq f(x)\). \\
+
+\noindent \underline{\textbf{Case 2:} \((x,y) \in \mathcal{T} \times \mathcal{C}\)}
+\par
+Given that \(f(x) = f(y)\) and by definition of \(f\), \(g(x) = g(\pi(y))\). Besides, \(g(\pi(y)) \leqslant n\) since 
+\(y \in \mathcal{C}\). Distinguish between two cases according to the value of \(x + \pi(y)\).
 \begin{itemize}
-	\item if  \(x\leqslant b \text{ (we will note }x \in \mathcal{T}): f(x)=g(x)\)
-	\item if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n (\text{ we will note } x \in \mathcal{C}): f(x)=g(\pi(x))\)
-	\item if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n (\text{ we will note } x \in \mathcal{R}): f(x)=n-1+h(\lambda(x))\)
+\item \begin{sloppypar}
+	If \(x + \pi(y) \leqslant a + b\) then \(g(x + \pi(y)) = g(\pi(x + y))\) (proposition \ref{prop3}). Given that \(g\) is 
+	a weakly sum-free coloring, \(g(x+\pi(y)) \neq g(x)\) since \(g(x)=g(\pi(y))\) and \(x \neq \pi(y)\) since
+	\({x \leqslant b < \pi(y)}\).
+	\end{sloppypar}
+\item \begin{sloppypar}
+	If \(x+\pi(y)> a+b\) then given that \(g\) is a WSF-template and since \({g(x) = g(\pi(y)) \leqslant n}\), 
+	\({g(\pi(x+\pi(y))) \neq g(x)}\).~Given that \({g(\pi(x+\pi(y))) = g(\pi(x+y))}\) (proposition \ref{prop2}), 
+	\({g(\pi(x+ y)) \neq g(x)}\).
+	\end{sloppypar}
+\end{itemize}
+\par
+Hence in both cases \(g(\pi(x+y)) \neq g(x)\). If  \(g(\pi(x+y)) \leqslant n\) then \(f(x+y) = g(\pi(x+y))\). Therefore 
+\(f(x+y) \neq f(x)\) since \(g(x) = f(x)\). Otherwise, \(g(\pi(x+y)) = n + 1\) and thus \(f(x+y) > n\). In particular, 
+\(f(x + y) \neq f(x)\) since \(f(x) = f(y) \leqslant n\). \\
+
+\noindent \underline{\textbf{Case 3:} \((x,y) \in \mathcal{T} \times \mathcal{R}\)}
+\par
+Necessarily \(f(x) = f(y) = n + 1\). Distinguish between two cases according to the value of \(\lambda(x+y)\).
+\begin{itemize}
+\item If \(\lambda(y)=\lambda(x+y)\) then \(\pi(x + y) = x + \pi(y)\) (proposition \ref{prop6}). By definition of 
+	\(f\), \(g(x) = g(\pi(y))\). Given that \(g\) is a weakly sum-free coloring, \(g(x + \pi(y)) \neq g(x)\) since 
+	\(g(x) = g(\pi(y))\) and \(x \neq \pi(y)\) since \({x \leqslant b < \pi(y)}\). Hence \(f(x + y) \neq f(x)\).
+\item If \(\lambda(y) \neq \lambda(x + y)\) then \(\lambda(x + y) = \lambda(y) + 1\) since \(x \leqslant b < a\). 
+	Besides, \(n + 1 = f(y) = n +  h(\lambda(y))\). Hence \(h(\lambda(y)) = 1\). Moreover \(h(1) = 1\) since \(h\) 
+	is an ordered coloring. Therefore, given that \(h\) is sum-free, \(h(\lambda(y) + 1) \neq 1\). If \(\pi(x + y) \in 
+	A_{n + 1}\) then \(f(x + y) = n + h(\lambda(x + y)) \neq n + 1\). Otherwise, \(f(x + y) \leqslant n\). Hence 
+	in both cases \(f(x + y) \neq f(x)\).
 \end{itemize}
 
-\(f\) is well defined since \(\pi\) is defined for \(x>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because \(h(\lambda(x))\leqslant k\)
+\noindent \underline{\textbf{Case 4:} \((x,y) \in \mathcal{C}^2\)}
+\par
+By definition of \(f\) and since \(f(x)=f(y)\), \(g(\pi(x)) = g(\pi(y))\). Dsistinguish between two cases according 
+to the value of \(\pi(x)+\pi(y)\).
+\begin{itemize}
+\item If \(\pi(x) + \pi(y) \leqslant q\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(g(\pi(x + y) \neq g(\pi(x))\) since 
+	\(g\) is sum-free for \(x>b\)
+\item \begin{sloppypar} 
+	If \(\pi(x)+\pi(y)>q\) then given that \(g\) is a WSF-template, \({g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x))}\) since 
+	\({g(\pi(x)) = g(\pi(y))}\). Besides,  \({g(\pi(\pi(x)+\pi(y))) = g(\pi(x + y))}\) (proposition \ref{prop4}). Hence \({g(\pi(x + y)) 
+	\neq  g(\pi(x))}\).
+	\end{sloppypar}
+\end{itemize}
+\par
+Hence in both cases \(g(\pi(x+y)) \neq g(x)\). If  \(g(\pi(x+y)) \leqslant n\) then \(f(x+y) = g(\pi(x+y))\). Therefore 
+\(f(x+y) \neq f(x)\) since \(g(x) = f(x)\). Otherwise, \(g(\pi(x+y)) = n + 1\) and thus \(f(x+y) > n\). In particular, 
+\(f(x + y) \neq f(x)\) since \(f(x) = f(y) \leqslant n\). \\
 
-We have parted the integers of \([\![1,b+pa]\!]\) in three disjoints subsets \(\mathcal{T},\mathcal{C} \text{ and } \mathcal{R}\).
+\noindent \underline{\textbf{Case 5:} \((x,y) \in \mathcal{C} \times \mathcal{R}\)}
+\par
+By definition of \(f\), \(f(x) \neq f(y)\).\\
 
-We have to verify that f induces weakly-sum-free templates\\
-\\
-\underline{if \((x,y) \in \mathcal{T}^2\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
-\\\(x+y<a+b\) since \(b<a\) and \(g(x)=f(x)=f(y)=g(y)\).
-\\Hence \(f(x+y)=g(x+y)\neq g(x)=f(x)\)
-\\\\
-\underline{if \((x,y) \in \mathcal{T} \times \mathcal{C}\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
-We distinguish two cases
-
+\noindent \underline{\textbf{Case 6:} \((x,y) \in \mathcal{R}^2\)}
+\par
+In particular \(g(\pi(x)) = g(\pi(y))=n\). Distinguish between three cases according to the value of \(\pi(x) + \pi(y)\).
 \begin{itemize}
-\item If \(x+\pi(y)\leqslant a+b\)
-\\\(g(x)=f(x)=f(y)=g(\pi(y)\). Hence \(g(x)\neq g(x+\pi(y))=g(\pi(x+y))\) (qv previous proposition)
-\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
-\\else, \(f(x+y)=g(\pi(x+y))\neq g(x)=f(x)\)
-\item If \(x+\pi(y)> a+b\), \(x+y>a+b\) and by definition of \(g\), \(g(\pi(x+y))\neq g(x)\)
-\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
-\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
+\item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\) 
+	(proposition \ref{prop7}). By definition of \(f\) and since \(f(x) = f(y)\), \(h(\lambda(x)) = h(\lambda(y))\).
+	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x)\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\) 
+	then \(f(x + y) = n + h(\lambda(x + y))\). And \(f(x) = n + h(\lambda(x))\). Therefore, \(f(x + y)  \neq f(x)\). 
+	Otherwise \(f(x+y) \leqslant n < f(x)\). In particular \(f(x + y) \neq f(x)\).
+\item If \(\pi(x)+\pi(y)>2a+b\) then \(g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x)) = n\) since \(g\) is a \(b\)-WSF template and 
+	\(g(\pi(x)) = g(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (proposition \ref{prop4}), \(g(\pi(x+y)) \neq n\).
+\item \begin{sloppypar}
+	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(g_{| [\![b, a + b ]\!]}\) is 
+	sum-free, \({g(\pi(x) + \pi(y)) \neq g(\pi(x)) = n}\). That is \(g(\pi(x + y)) \neq n\) (proposition \ref{prop1}).
+	\end{sloppypar}
 \end{itemize}
-
-\underline{if \((x,y) \in \mathcal{T} \times \mathcal{R}\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
-\\Then, \(f(x)=f(y)=n\). We distinguish two cases
-
-\begin{itemize}
-\item If \(\lambda(y)=\lambda(x+y)\),
-\\\(g(x)=g(\pi(y))=n \text{ since } g(y)=g(\pi(y))\)
-\\Therefore \(g(\pi(x+y))=g(x+\pi(y)) \neq g(x)=n\) (qv previous proposition)
-\\Hence \(f(x+y)=g(\pi(x+y))\neq n\)
-\item If  \(\lambda(y)\neq \lambda(x+y)\), \(\lambda(y)+1= \lambda(x+y)\)\\
-\(n=f(y)=n-1+h(\lambda(y))\). Hence \(h(\lambda(y))=1\).
-\\Moreover \(h(1)=1\), therefore \(h(\lambda(y)+1) \neq 1\)
-\\if \(\pi(x+y) \in A_n\), \(f(x+y)=n-1+h(\lambda(x+y))>n\)
-\end{itemize}
-
-\underline{if \((x,y) \in \mathcal{C}^2\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
-\\Then  \(g(\pi(x))=f(x)=f(y)=g(\pi(y))\). We distinguish two cases
-
-\begin{itemize}
-\item If \(\pi(x)+\pi(y)>q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) (qv previous proposition)
-\\Hence \(g(\pi(x+y))= g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))\)
-\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
-\\else, \(f(x+y)=g(\pi(x+y))\neq g(\pi(x))=f(x)\)
-\item If  \(\pi(x)+\pi(y)\leqslant q\), \(g(\pi(\pi(x)+\pi(y)) \neq g(\pi(x))\) since \(g\) is sum-free for \(x>b\)
-\\if \(g(\pi(x+y))=n, f(x+y)\geqslant n > f(x)\)
-\\else, \(f(x+y)=g(\pi(x+y))=g(\pi(\pi(x)+\pi(y))\neq g(\pi(x))=f(x)\)
-\end{itemize}
-
-\underline{if \((x,y) \in \mathcal{C} \times \mathcal{R} \), \(f(x)\neq f(y)\)}\\
-
-\underline{if \((x,y) \in (\mathcal{R})^2\) such that \(f(x)=f(y)\), \(x \neq y\):}\\
-\\Let \(r(x)=\pi(x)-a\) and \(r(y)=\pi(y)-a\),
-\\We proved that \(x=a\lambda(x)+\pi(x)-a\), therefore \(x=a\lambda(x)+\pi(x)\)
-\\\(x+y=a(\lambda(x)+\lambda(y))+r(x)+r(y)\). We distinguish three cases
-
-\begin{itemize}
-\item If \(r(x)+r(y) \in [\![b-a+1,b]\!]\), \(h(\lambda(x))=f(x)+1-n=f(y)+1-n=h(\lambda(y))\)
-Hence, \(h(\lambda(x)+\lambda(y)) \neq h(\lambda(x))\).
-\begin{align*}
- \lambda(x+y) & =1+\left\lfloor\dfrac{a(\lambda(x)+\lambda(y))+r(x)+r(y)-b-1}{a}\right\rfloor+1\\
-& = \lambda(x)+\lambda(y)+\left\lfloor\dfrac{r(x)+r(y)-b-1}{a}\right\rfloor+1 \\
-& = \lambda(x)+\lambda(y) -1 +1 \text{ since } r(x)+r(y) \in [\![b-a+1,b]\!] \\
-& =\lambda(x)+\lambda(y)
-\end{align*}
-
-\begin{align*}
- \text{if \(f(x+y) \geqslant n\), }f(x+y) & =n-1+h(\lambda(x+y))\\
-& =n-1+h(\lambda(x)+\lambda(y)) \\
-& \neq n-1+h(\lambda(x))\\
-& =f(x)
-\end{align*}
-
-\item If \(r(x)+r(y)>b\), \(\pi(x)+\pi(y)>2a+b\)
-\\Since \(g\) is a \(b\)-WSF template, \(g(\pi(\pi(x)+\pi(y))) \neq n\)
-\\Therefore, \(g(\pi(x+y)) \neq n\) ie \(x+y \in \mathcal{C}\)
-\\Hence \(f(x+y) <n\leqslant f(x)\)
-\item If \(r(x)+r(y) \leqslant b - a\), \(\pi(x)+\pi(y)\leqslant b+a\)
-\\Since \(g\) is sum-free for \(x>b\), since \(g(\pi(x)) = g(\pi(y))=n\), \(g(\pi(x+y)) \neq g(\pi(x))=n\)
-\\Hence, \(f(x+y) <n\leqslant f(x)\)
-\end{itemize}
+\par
+In both of the last two cases, that is \(x+y \in \mathcal{C}\). Therefore \(f(x+y) < n \leqslant f(x)\). In particular, 
+\(f(x + y) \neq f(x)\). \\
 \end{proof}
@@
 \(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a coloring \(g\) of
-\([\![b + 1, b + c]\!]\) with \(k\) colors such that
+\([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),
 
 \begin{itemize}
-	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c)
+\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c)
 	\implies g(\pi(x + y)) \neq f(x)\)
-	\item \(\forall c \in [\![1, k]\!], \forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c)
+\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c)
 	\implies g(\pi(x + y)) \neq f(x)\)
@@
 \begin{theorem}
-Let \((k,p), (n,a) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors and a 
-\(WSF\)-template with width \(a\) and \(n\) colors, then there exists \(WSF\)-template with width \(pq\) and \((n+k)\)
- colors.
+Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\) . If there exists a SF-template with width 
+\(p\) and \(k+1\) colors and a \(b\)-WSF-template with width \(a\) and \(n\) colors, then there exists \(pb\)-WSF-template 
+with width \(pq\) and \((n+k)\) colors.
 \end{theorem}

### 2021-05-09 article/schur.tex

@@
 The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
-fact that a SF-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets.
+fact that a SF-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets. \\
 \end{proof}
@@
 \par
+NB: In the following 3 predicates, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant q\) are omitted for readability.
+\par
 The sum-free condition is expressed as
 \[\forall (x,y) \in [\![1,p]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)\]
-\[\forall (x,y) \in [\![1,q]\!]^2 \text{, } g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)\]
+\[\forall (x,y) \in [\![1,q]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)\]
 
@@
 \forall (x,y) \in [\![1,p]\!]^2, \left\{
-\begin{array}{ll}
+\begin{array}{l}
 	f(x) = f(y) \leqslant k \\
@@
 
-\noindent \underline{\textbf{First case:} \(h(x) \leqslant k\)}
+\noindent \underline{\textbf{Case 1:} \(h(x) \leqslant k\)}
 \par
@@
 
-\noindent \underline{\textbf{Second case:} \(h(x) \geqslant k + 1\)}
+\noindent \underline{\textbf{Case 2:} \(h(x) \geqslant k + 1\)}
 \par
@@
 \begin{theorem}
-Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors,
-and a SF-template with width \(q\) and \(n\) colors, then there exists \(SF\)-template with width \(pq\) and \((n+k)\) 
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a SF-template with width \(p\) and \(k+1\) colors,
+and a SF-template with width \(q\) and \(n\) colors, then there exists SF-template with width \(pq\) and \((n+k)\) 
 colors.
@@
 The idea is the same as in the previous theorem. The only difference is the SF-template property inherited 
-from the second SF-template.
+from the second SF-template. \\
 \end{proof}
@@
 It is a mere consequence of the inequality \( S(n+5) \geqslant 380S(n) + 148\). As for Ramsey
-numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}) hence the result.
+numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}) hence the result. \\
 \end{proof}

### 2021-05-09 article/search_space.tex

@@
 \section{Analysis of the former search space}
+\label{SearchSpace}
 
@@
 in computation time by giving additional information to the SAT solver without losing in generality. In this 
-section, we assume that the subsets are ordered.
+section, \textit{we assume that the subsets are ordered}.
 
@@
 values of \(n\). Therefore, one may wonder whether the limiting factor are the assumptions or the 
-methods used to search for partitions. It appears that the search space induced by these assumptions does 
-not contain the optimal partitions.
+methods used to search for partitions.Here we provide evidence indicating that the search space induced by 
+these assumptions does not contain the optimal partitions.
 
 \begin{computational theorem}
-There is no weakly sum-free partition of \([\![1,583]\!]\) in 6 parts such that:
+There is no weakly sum-free partition of \([\![1,583]\!]\) into 6 subsets such that
 \begin{itemize}
@@
 in a weakly sum-free
-partition of \([\![1,185]\!]\) which starts with a weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets. Adding
+partition of \([\![1,185]\!]\) which starts with a weakly sum-free partition of \([\![1,65]\!]\) into 4 subsets. Adding
 these constraints to the
-formula corresponding to the above theorem gives additional information to the SAT solver without losing in generality.
+formula corresponding to the above theorem gives additional information to the SAT solver without loss of generality.
 
@@
 papers which found it.
-Therefore, finding a partition of \([\![1,n]\!]\) in 6 weakly sum-free subsets for some \(n \geqslant 590\) which does
+Therefore, finding a partition of \([\![1,n]\!]\) into 6 weakly sum-free subsets for some \(n \geqslant 590\) which does
 not have a template-like structure
 would be extremely interesting since it could give indications on a new search space for improving lower bounds with a
-computer.
+computer search.
 
@@
 with a computer. In particular, to our knowledge every paper that found the lower bound \(\WS (5) \geqslant 196\) 
-used this assumption. Therefore one may wonder if this is actually a good lower bound. In the next subsection, we give 
-properties that a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets has to verify.
+used this assumption. Therefore one may wonder whether this is actually a good lower bound. In the next subsection, we give 
+properties that a hypothetical partition of \([\![1,197]\!]\) into 5 weakly sum-free subsets has to verify.
 
@@
 optimal solution. In this subsection,
-we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the
+we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) into 5 weakly sum-free subsets using the
 same type of methods as in the
@@
 there exists a partition of
-\([\![1,p]\!]\) in n weakly sum-free subsets which verifies P.
+\([\![1,p]\!]\) into n weakly sum-free subsets which verifies P.
 \end{notation}
@@
 \par
-\cite{ELIAHOU2012175} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of
+\cite{ELIAHOU2012175} verified with a SAT solver that there are no partition into 5 weakly sum-free subsets of
 \([\![1,197]\!]\) with
@@
 this subsection, we used the parallel version of glucose).
-The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free
+The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) into 4 weakly sum-free
 subsets starts with a partition of
-\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among
-the 3 partitions of \([\![1,23]\!]\) in
+\([\![1,23]\!]\) into 3 weakly sum-free subsets (this can be checked in a dozen of minutes with a SAT solver). Among
+the 3 partitions of \([\![1,23]\!]\) into
 3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two
@@
 \begin{computational theorem}
-If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leqslant 59\).
+If there exists a partition of \([\![1,197]\!]\) into 5 weakly sum-free subsets then \(m_5 \leqslant 59\).
 \end{computational theorem}
@@
 For \(m_4 = 24\), the value \(m_5 \leqslant 53\) was obtained after 7 hours of runtime, and for  \(m_4 = 22\), the
-value \(m_5 \leqslant 59\) was obtained after 11 hours of runtime. All the other values took between 1 minutes and 2 hours.
-To obtain these results, we once again provided additionnal information to the SAT solver. We added two different types information.
-The first one is the same as previously: we compute the subsets in which the first numbers can appear. The second type of
-information is the maximum length of a sequence using only a certain subset of the colors. For instance,
-if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3.
+value \(m_5 \leqslant 59\) was obtained after 11 hours of runtime. As for the other values, they were obtained after 
+between 1 minute and 2 hours of runtime. To obtain these results, we once again provided additionnal information to 
+the SAT solver. We added two different types information. The first one is the same as previously: we compute the 
+subsets in which the first numbers can appear. The second type of information is the maximum length of a sequence 
+using only a certain subset of the colors. For instance, if \(m_4 \geqslant 22\), then there cannot be more than 17 
+consecutive numbers with color 1, 2 or 3.
 
@@
 
-\qquad As explained in the first subsection, the recursive assumption that a good partition for\(\WS (n+1)\) starts with a good partition for 
+\qquad As explained in the first subsection, the recursive assumption that a good partition for \(\WS (n+1)\) starts with a good partition for 
 \(\WS (n)\) appears to be wrong. Given that no extensive search for \(\WS(5)\) has been conducted without making this assumption and 
@@
 investigating this special case further. In a spirit of orientating this search, we then give necessary conditions on an hypothetical partition 
-of \([\![1,197]\!]\) in 5 weakly sum-free subsets. Finding partitions that exceeds the lower bounds found with a computer (even if they 
+of \([\![1,197]\!]\) into 5 weakly sum-free subsets. Finding partitions that exceeds the lower bounds found with a computer (even if they 
 do not exceed those obtained with templates) which are not as regular as those obtained with templates would be extremely interesing 

### 2021-05-09 article/weakschur.tex
corrections

@@
 \[
-\begin{NiceArray}{*{13}{c}}[corners=NW,hvlines]
+\begin{NiceArray}{*{13}{c}}[corners=NW,hvlines,xdots/line-style={solid}]
 \CodeBefore
@@
 \begin{proof}[\textsc{Proof.}]
-It is a direct consequence of \(pi(x) = x \mod a\). \\
+It is a direct consequence of \(\pi(x) = x \mod a\). \\
 \end{proof}
@@
 We now prove that \(f\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) such that \(x \neq y\), 
-\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Distinguish between six cases 
+\(f(x) = f(y)\) and \(x+y \leqslant p a+ b\). We claim that \(f(x+y) \neq f(x)\). Distinguish between six cases 
 according to the subsets \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) to which \(x\) and \(y\) belong. It is 
@@
 \par
-In particular \(g(\pi(x)) = g(\pi(y))=n\). Distinguish between three cases according to the value of \(\pi(x) + \pi(y)\).
+In particular \(g(\pi(x)) = g(\pi(y))=n + 1\). Distinguish between three cases according to the value of \(\pi(x) + \pi(y)\).
 \begin{itemize}
@@
 	Otherwise \(f(x+y) \leqslant n < f(x)\). In particular \(f(x + y) \neq f(x)\).
-\item If \(\pi(x)+\pi(y)>2a+b\) then \(g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x)) = n\) since \(g\) is a \(b\)-WSF template and 
-	\(g(\pi(x)) = g(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (proposition \ref{prop4}), \(g(\pi(x+y)) \neq n\).
+\item If \(\pi(x)+\pi(y)>2a+b\) then \(g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x)) = n + 1\) since \(g\) is a \(b\)-WSF template and 
+	\(g(\pi(x)) = g(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (proposition \ref{prop4}), \(g(\pi(x+y)) \neq n + 1\).
 \item \begin{sloppypar}
 	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(g_{| [\![b, a + b ]\!]}\) is 
-	sum-free, \({g(\pi(x) + \pi(y)) \neq g(\pi(x)) = n}\). That is \(g(\pi(x + y)) \neq n\) (proposition \ref{prop1}).
+	sum-free, \({g(\pi(x) + \pi(y)) \neq g(\pi(x)) = n + 1}\). That is \({g(\pi(x + y)) \neq n + 1}\) (proposition \ref{prop1}).
 	\end{sloppypar}
@@
 \par
-In both of the last two cases, that is \(x+y \in \mathcal{C}\). Therefore \(f(x+y) < n \leqslant f(x)\). In particular, 
-\(f(x + y) \neq f(x)\). \\
+In both of the last two cases, \({g(\pi(x + y)) \neq n + 1}\) that is \(x+y \in \mathcal{C}\). Therefore \(f(x+y) < n \leqslant f(x)\). 
+In particular, \(f(x + y) \neq f(x)\). \\
 \end{proof}

### 2021-05-09 article/weakschur.tex
Modif weakschur
typographie weak schur

@@
 	If \(x+\pi(y)> a+b\) then given that \(g\) is a WSF-template and since \({g(x) = g(\pi(y)) \leqslant n}\), 
-	\({g(\pi(x+\pi(y))) \neq g(x)}\).~Given that \({g(\pi(x+\pi(y))) = g(\pi(x+y))}\) (proposition \ref{prop2}), 
+	\({g(\pi(x+\pi(y))) \neq g(x)}\).~Furthermore \({g(\pi(x+\pi(y))) = g(\pi(x+y))}\) (proposition \ref{prop2}), such that 
 	\({g(\pi(x+ y)) \neq g(x)}\).
@@
 \par
-By definition of \(f\) and since \(f(x)=f(y)\), \(g(\pi(x)) = g(\pi(y))\). Dsistinguish between two cases according 
+By definition of \(f\) and since \(f(x)=f(y)\), \(g(\pi(x)) = g(\pi(y))\). Distinguish between two cases according 
 to the value of \(\pi(x)+\pi(y)\).
 \begin{itemize}
-\item If \(\pi(x) + \pi(y) \leqslant q\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(g(\pi(x + y) \neq g(\pi(x))\) since 
+\item If \(\pi(x) + \pi(y) \leqslant a+b\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(g(\pi(x + y)) \neq g(\pi(x))\) since 
 	\(g\) is sum-free for \(x>b\)
 \item \begin{sloppypar} 
-	If \(\pi(x)+\pi(y)>q\) then given that \(g\) is a WSF-template, \({g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x))}\) since 
+	If \(\pi(x)+\pi(y)>a+b\) then given that \(g\) is a WSF-template, \({g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x))}\) since 
 	\({g(\pi(x)) = g(\pi(y))}\). Besides,  \({g(\pi(\pi(x)+\pi(y))) = g(\pi(x + y))}\) (proposition \ref{prop4}). Hence \({g(\pi(x + y)) 
@@
 	(proposition \ref{prop7}). By definition of \(f\) and since \(f(x) = f(y)\), \(h(\lambda(x)) = h(\lambda(y))\).
-	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x)\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\) 
+	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x))\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\) 
 	then \(f(x + y) = n + h(\lambda(x + y))\). And \(f(x) = n + h(\lambda(x))\). Therefore, \(f(x + y)  \neq f(x)\). 

### 2021-05-09 article/schur.tex
schur p to q n to k

@@
 \begin{theorem}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors 
-	and a partition of \([\![1,q]\!]\) into \(n\) sum-free subsets then there exists a partition of \([\![1,pq+m_{k+1}
-	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{k+1}\) is the minimum of the special subset in the \(SF\)-template.
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(q\) and \(n+1\) colors 
+	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there exists a partition of \([\![1,pq+m_{n+1}
+	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) is the minimum of the special subset in the \(SF\)-template.
 \end{theorem}
 
-Setting \(p = S^+(k+1)\) and \(q = S(n)\) yields the following corollary.
+Setting \(q = S^+(n+1)\) and \(p = S(k)\) yields the following corollary.
 
@@
 	Let \(n, k \in \mathbb{N}^*\). Then
-	\[ S(n+k) \geqslant S^+(k+1)S(n) + m_{k+1} - 1 \]
+	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1 \]
 \end{corollary}
@@
 \begin{proof}[\textsc{Proof.}]
-Denote by \(f\) the coloring associated to the \(SF\)-template with width \(p\) and \(g\) the one associated 
-to the sum-free partition of \([\![1,q]\!]\); where \(f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!]\) and 
-\(g : [\![1,q]\!] \longrightarrow [\![1,n]\!]\).
+	Denote by \(f\) the coloring associated to the \(SF\)-template with width \(q\) and \(g\) the one associated 
+	to the sum-free partition of \([\![1,p]\!]\); where \(f : [\![1,q]\!] \longrightarrow [\![1,n+1]\!]\) and 
+	\(g : [\![1,p]\!] \longrightarrow [\![1,k]\!]\).
 
 	\par
-NB: In the following 3 predicates, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant q\) are omitted for readability.
+	NB: In the following 3 predicates, the conditions \(x + y \leqslant q\)  and \(x + y \leqslant p\) are omitted for readability.
 	\par
 	The sum-free condition is expressed as
-\[\forall (x,y) \in [\![1,p]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)\]
-\[\forall (x,y) \in [\![1,q]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)\]
+	\[\forall (x,y) \in [\![1,q]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)\]
+	\[\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)\]
 
@@
 	\[
-\forall (x,y) \in [\![1,p]\!]^2, \left\{
+	\forall (x,y) \in [\![1,q]\!]^2, \left\{
 	\begin{array}{l}
-	f(x) = f(y) \leqslant k \\
-	x + y > p
+		f(x) = f(y) \leqslant n \\
+		x + y > q
 	\end{array}
-\right. \Longrightarrow f(x+y-p) \neq f(x)
+	\right. \Longrightarrow f(x+y-q) \neq f(x)
 	\]
 
-For \(x \in [\![1,pq+m_{k+1}-1]\!]\), write \(x = (\alpha - 1) + u\) for some integers \(\alpha \in \mathbb{Z}\) and 
-\(u \in [\![1,p]\!]\). This decomposition is of course unique. \(\alpha\) (resp. \(u\)) can be interpreted as the row 
+	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), write \(x = (\alpha - 1) + u\) for some integers \(\alpha \in \mathbb{Z}\) and 
+	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\) (resp. \(u\)) can be interpreted as the row 
 	(resp. column) number of \(x\). Define a new coloring \(h\) as follows
@@
 	\begin{array}{c c c l}
-	h : & [\![1,pq+m_{k+1}-1]\!] & \longrightarrow & [\![1,n+k]\!] \\
+		h : & [\![1,pq+m_{n+1}-1]\!] & \longrightarrow & [\![1,n+k]\!] \\
 		& x & \longmapsto & 
 		\left\{ \begin{array}{l l}
-		f(u) & \text{if}~f(u) \leqslant k \\
-		k + g(\alpha) & \text{if}~f(u) = k + 1 \\
+			f(u) & \text{if}~f(u) \leqslant n \\
+			k + g(\alpha) & \text{if}~f(u) = n + 1 \\
 		\end{array} \right.
@@
 
-\(h\) is well-defined since, by definition of \(m_{k+1}\), \(\forall x \in [\![p q + 1, p q + m_{k + 1} - 1 ]\!], f(u) 
-\leqslant k\) and therefore \(\forall x \in [\![1,pq+m_{k+1}-1]\!], f(u) = k + 1 \implies \alpha \in [\![1, q]\!]\).
+	\(h\) is well-defined since, by definition of \(m_{n+1}\), \(\forall x \in [\![p q + 1, p q + m_{n + 1} - 1 ]\!], f(u) 
+	\leqslant k\) and therefore \(\forall x \in [\![1,pq+m_{n+1}-1]\!], f(u) = n + 1 \implies \alpha \in [\![1, p]\!]\).
 
 	\par
-We now prove that \(h\) is a sum-free coloring. Let \(x,y \in [\![1,pq + m_{k+1}-1]\!]\) such that \(h(x) = h(y)\) 
-and \(x+y \leqslant pq+m_{k+1}-1\). We claim that \(h(x+y) \neq h(x)\). Write \(x = (\alpha - 1) p + u\) and 
-\(y = (\beta - 1) p + v\) where \(\alpha, \beta \in \mathbb{Z}\) and \(u, v \in [\![1,p]\!]\). Distinguish between 
+	We now prove that \(h\) is a sum-free coloring. Let \(x,y \in [\![1,pq + m_{n+1}-1]\!]\) such that \(h(x) = h(y)\) 
+	and \(x+y \leqslant pq+m_{n+1}-1\). We claim that \(h(x+y) \neq h(x)\). Write \(x = (\alpha - 1) q + u\) and 
+	\(y = (\beta - 1) q + v\) where \(\alpha, \beta \in \mathbb{Z}\) and \(u, v \in [\![1,q]\!]\). Distinguish between 
 	two cases according to the value of \(h(x)\). \\
@@
 	\begin{itemize}
-\item If \(u + v > p\), write \(w = u + v - p \in [\![1, p]\!]\). Then \(x + y = (\alpha + \beta - 1) p + w\). By definition, 
-	\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant k\), the additionnal constraint on \(f\) implies \(f(w) 
+	\item If \(u + v > q\), write \(w = u + v - q \in [\![1, q]\!]\). Then \(x + y = (\alpha + \beta - 1) q + w\). By definition, 
+		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the additionnal constraint on \(f\) implies \(f(w) 
 		\neq f(u)\), that is \(h(x + y) \neq h(x)\).
-\item If \(u + v \leqslant p\), write \(w = u + v \in [\![1, p]\!]\). Then \(x+y = (\alpha + \beta- 2) p + w\). By definition, 
-	\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant k\), the sum-free property of \(f\) implies \(f(w) \neq f(u)\), 
+	\item If \(u + v \leqslant p\), write \(w = u + v \in [\![1, q]\!]\). Then \(x+y = (\alpha + \beta- 2) q + w\). By definition, 
+		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the sum-free property of \(f\) implies \(f(w) \neq f(u)\), 
 		that is \(h(x + y) \neq h(x)\).
@@
 
-\noindent \underline{\textbf{Case 2:} \(h(x) \geqslant k + 1\)}
+	\noindent \underline{\textbf{Case 2:} \(h(x) \geqslant n + 1\)}
 	\par
-\(h(x) = k + g(\alpha) = 
+	\(h(x) = n + g(\alpha) = 
 	k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As in the first case, distinguish between two cases according 
@@
 	\item \begin{sloppypar}
-	If \(u + v > p\), write \(w = u + v - p \in [\![1, p]\!]\). Then \(x + y = (\alpha + \beta - 1) p + w\). Assume that 
-	\({h(x+y) \geqslant k + 1}\),  otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition, \({h(x + y) = k + g(\alpha + 
+		If \(u + v > q\), write \(w = u + v - q \in [\![1, q]\!]\). Then \(x + y = (\alpha + \beta - 1) q + w\). Assume that 
+		\({h(x+y) \geqslant n + 1}\),  otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition, \({h(x + y) = n + g(\alpha + 
 		\beta)}\). Given that \(g(\alpha) = g(\beta)\), the sum-free property of \(g\) implies \(g(\alpha + \beta) 
@@
 		\end{sloppypar}
-\item  If \(u + v \leqslant p\), write \(w = u + v \in [\![1, p]\!]\). Then \(x+y = (\alpha + \beta- 2) p + w\). The sum-free 
-	property of \(f\) implies \(f(w) \neq f(u)\). Therefore \(f(w) \leqslant k\) and thus \(h(x + y) \leqslant k\). In particular,
-	given that \(h(x) \geqslant k + 1\), \(h(x + y) \neq h(x)\).
+	\item  If \(u + v \leqslant q\), write \(w = u + v \in [\![1, q]\!]\). Then \(x+y = (\alpha + \beta- 2) q + w\). The sum-free 
+		property of \(f\) implies \(f(w) \neq f(u)\). Therefore \(f(w) \leqslant k\) and thus \(h(x + y) \leqslant n\). In particular,
+		given that \(h(x) \geqslant n + 1\), \(h(x + y) \neq h(x)\).
 	\end{itemize}
@@
 \begin{proposition}
-Let \((p, k) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a SF-template with width \(p\) and \(k+1\) 
-colors. Let \(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a coloring \(g\) of 
-\([\![1, b]\!]\) with \(k+1\) colors such that
+	Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a SF-template with width \(q\) and \(n+1\) 
+	colors. Let \(b \in \mathbb{N}\) (\(b = m_{n+1} - 1\) works) and assume there there exists a coloring \(g\) of 
+	\([\![1, b]\!]\) with \(n+1\) colors such that
 
 	\begin{itemize}
-	\item \(\forall (x, y) \in [\![1, p]\!]^2,(f(x) = f(y) \text{ and } (x + y) \mod p \leqslant b) 
-	\implies g((x + y) \mod p) \neq f(x)\)
-	\item \(\forall (x, y) \in [\![1, p]\!] \times  [\![1, b]\!], (f(x) = g(y) \text{ and } x + y \leqslant b) 
+		\item \(\forall (x, y) \in [\![1, q]\!]^2,(f(x) = f(y) \text{ and } (x + y) \mod q \leqslant b) 
+		\implies g((x + y) \mod q) \neq f(x)\)
+		\item \(\forall (x, y) \in [\![1, q]\!] \times  [\![1, b]\!], (f(x) = g(y) \text{ and } x + y \leqslant b) 
 		\implies g(x + y) \neq f(x)\)
@@
 
-Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(i \longmapsto g(i - p S(n))\), we have
-\[ S(n+k) \geqslant S^+(k+1)S(n) + b\]
+	Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have
+	\[ S(n+k) \geqslant S^+(n+1)S(k) + b\]
 \end{proposition}
@@
 \begin{theorem}
-Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a SF-template with width \(p\) and \(k+1\) colors,
-and a SF-template with width \(q\) and \(n\) colors, then there exists SF-template with width \(pq\) and \((n+k)\) 
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a SF-template with width \(q\) and \(n+1\) colors,
+	and a SF-template with width \(p\) and \(k\) colors, then there exists SF-template with width \(pq\) and \((n+k)\) 
 	colors.
@@
 	Let \(n, k \in \mathbb{N}^*\). Then
-\[ S^+(n+k) \geqslant S^+(k+1)S^+(n) \]
+	\[ S^+(n+k) \geqslant S^+(n+1)S^+(k) \]
 \end{corollary}

### 2021-05-09 article/weakschur.tex

@@
 \begin{sloppypar}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Denote by \(g\) the coloring 
-associated to the \(b\)-WSF-template  and \(h\) the one associated to the sum-free partition of \([\![1,p]\!]\); where 
-\({g : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({h : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, assume 
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Denote by \(f\) the coloring 
+associated to the \(b\)-WSF-template  and \(g\) the one associated to the sum-free partition of \([\![1,p]\!]\); where 
+\({f : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({g : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, assume 
 that the sum-free coloring of \([\![1, p]\!]\) is ordered.
@@
 \begin{array}{l}
-	g(x) = g(y) \\
+	f(x) = f(y) \\
 	x \neq y
 \end{array}
-\right. \Longrightarrow g(x+y) \neq g(x)
+\right. \Longrightarrow f(x+y) \neq f(x)
 \]
 \[
-\forall (x,y) \in [\![b+1,a + b]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)
+\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
 \]
 \[
-\forall (x,y) \in [\![1,p]\!]^2, h(x) = h(y) \Longrightarrow h(x+y) \neq h(x)
+\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)
 \]
@@
 \begin{array}{l}
-	g(x) = g(y) \leqslant n \\
+	f(x) = f(y) \leqslant n \\
 	x + y > a + b
 \end{array}
-\right. \Longrightarrow g(\pi(x+y)) \neq g(x)
+\right. \Longrightarrow f(\pi(x+y)) \neq f(x)
 \]
@@
 \begin{array}{l}
-	g(x) = g(y) = n + 1 \\
+	f(x) = f(y) = n + 1 \\
 	x + y > 2 a + b
 \end{array}
-\right. \Longrightarrow g(x+y - 2 a) \neq g(x)
+\right. \Longrightarrow f(x+y - 2 a) \neq f(x)
 \]
@@
 	\item \(\mathcal{T} = [\![1, b]\!]\)
-	\item \(\mathcal{C} = \pi^{-1}(g^{-1}([\![1, n]\!]))\)
-	\item \(\mathcal{R} = \pi^{-1}(g^{-1}(\{n + 1\}))\)
+	\item \(\mathcal{C} = \pi^{-1}(f^{-1}([\![1, n]\!]))\)
+	\item \(\mathcal{R} = \pi^{-1}(f^{-1}(\{n + 1\}))\)
 \end{itemize}
 
-Define a new coloring \(f\) as follows
+Define a new coloring \(h\) as follows
 \[
@@
 	\left\{ \begin{array}{l l}
-		g(x) & \text{if}~x \in \mathcal{T} \\
-		g(\pi(x)) & \text{if}~x \in \mathcal{C} \\
-		n + h(\lambda(x)) & \text{if}~x \in \mathcal{R}
+		f(x) & \text{if}~x \in \mathcal{T} \\
+		f(\pi(x)) & \text{if}~x \in \mathcal{C} \\
+		n + g(\lambda(x)) & \text{if}~x \in \mathcal{R}
 	\end{array} \right.
@@
 
-\(f\) is well defined since \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) is a partition of  \([\![1, p a + b]\!]\). 
-We now prove that \(f\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) such that \(x \neq y\), 
-\(f(x) = f(y)\) and \(x+y \leqslant p a+ b\). We claim that \(f(x+y) \neq f(x)\). Distinguish between six cases 
+\(h\) is well defined since \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) is a partition of  \([\![1, p a + b]\!]\). 
+We now prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) such that \(x \neq y\), 
+\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Distinguish between six cases 
 according to the subsets \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) to which \(x\) and \(y\) belong. It is 
@@
 \par
-If \(x + y \leqslant b\) then \(f(x+y)=g(x+y)\). Otherwise, \(b < x+y < a+b\) since \(b < a\) and 
-therefore \(\pi(x + y) = x +y\) (proposition \ref{prop1}). Hence in both cases \(f(x+y)=g(x+y)\). Given that 
-\(g\) is a weakly sum-free coloring, \(g(x + y) \neq g(x)\) since \(g(x)=f(x)=f(y)=g(y)\) and \(x \neq y \). That 
-is \(f(x + y) \neq f(x)\). \\
+If \(x + y \leqslant b\) then \(h(x+y)=f(x+y)\). Otherwise, \(b < x+y < a+b\) since \(b < a\) and 
+therefore \(\pi(x + y) = x +y\) (proposition \ref{prop1}). Hence in both cases \(h(x+y)=f(x+y)\). Given that 
+\(f\) is a weakly sum-free coloring, \(f(x + y) \neq f(x)\) since \(f(x)=h(x)=h(y)=f(y)\) and \(x \neq y \). That 
+is \(h(x + y) \neq h(x)\). \\
 
@@
 \par
-Given that \(f(x) = f(y)\) and by definition of \(f\), \(g(x) = g(\pi(y))\). Besides, \(g(\pi(y)) \leqslant n\) since 
+Given that \(h(x) = h(y)\) and by definition of \(h\), \(f(x) = f(\pi(y))\). Besides, \(f(\pi(y)) \leqslant n\) since 
 \(y \in \mathcal{C}\). Distinguish between two cases according to the value of \(x + \pi(y)\).
@@
 \item \begin{sloppypar}
-	If \(x + \pi(y) \leqslant a + b\) then \(g(x + \pi(y)) = g(\pi(x + y))\) (proposition \ref{prop3}). Given that \(g\) is 
-	a weakly sum-free coloring, \(g(x+\pi(y)) \neq g(x)\) since \(g(x)=g(\pi(y))\) and \(x \neq \pi(y)\) since
+	If \(x + \pi(y) \leqslant a + b\) then \(f(x + \pi(y)) = f(\pi(x + y))\) (proposition \ref{prop3}). Given that \(f\) is 
+	a weakly sum-free coloring, \(f(x+\pi(y)) \neq f(x)\) since \(f(x)=f(\pi(y))\) and \(x \neq \pi(y)\) since
 	\({x \leqslant b < \pi(y)}\).
@@
 \item \begin{sloppypar}
-	If \(x+\pi(y)> a+b\) then given that \(g\) is a WSF-template and since \({g(x) = g(\pi(y)) \leqslant n}\), 
-	\({g(\pi(x+\pi(y))) \neq g(x)}\).~Furthermore \({g(\pi(x+\pi(y))) = g(\pi(x+y))}\) (proposition \ref{prop2}), such that 
-	\({g(\pi(x+ y)) \neq g(x)}\).
+	If \(x+\pi(y)> a+b\) then given that \(f\) is a WSF-template and since \({f(x) = f(\pi(y)) \leqslant n}\), 
+	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (proposition \ref{prop2}), such that 
+	\({f(\pi(x+ y)) \neq f(x)}\).
 	\end{sloppypar}
@@
 \par
-Hence in both cases \(g(\pi(x+y)) \neq g(x)\). If  \(g(\pi(x+y)) \leqslant n\) then \(f(x+y) = g(\pi(x+y))\). Therefore 
-\(f(x+y) \neq f(x)\) since \(g(x) = f(x)\). Otherwise, \(g(\pi(x+y)) = n + 1\) and thus \(f(x+y) > n\). In particular, 
-\(f(x + y) \neq f(x)\) since \(f(x) = f(y) \leqslant n\). \\
+Hence in both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore 
+\(h(x+y) \neq h(x)\) since \(f(x) = h(x)\). Otherwise, \(f(\pi(x+y)) = n + 1\) and thus \(h(x+y) > n\). In particular, 
+\(h(x + y) \neq h(x)\) since \(h(x) = h(y) \leqslant n\). \\
 
@@
 \par
-Necessarily \(f(x) = f(y) = n + 1\). Distinguish between two cases according to the value of \(\lambda(x+y)\).
+Necessarily \(h(x) = h(y) = n + 1\). Distinguish between two cases according to the value of \(\lambda(x+y)\).
 \begin{itemize}
 \item If \(\lambda(y)=\lambda(x+y)\) then \(\pi(x + y) = x + \pi(y)\) (proposition \ref{prop6}). By definition of 
-	\(f\), \(g(x) = g(\pi(y))\). Given that \(g\) is a weakly sum-free coloring, \(g(x + \pi(y)) \neq g(x)\) since 
-	\(g(x) = g(\pi(y))\) and \(x \neq \pi(y)\) since \({x \leqslant b < \pi(y)}\). Hence \(f(x + y) \neq f(x)\).
+	\(h\), \(f(x) = f(\pi(y))\). Given that \(f\) is a weakly sum-free coloring, \(f(x + \pi(y)) \neq f(x)\) since 
+	\(f(x) = f(\pi(y))\) and \(x \neq \pi(y)\) since \({x \leqslant b < \pi(y)}\). Hence \(h(x + y) \neq h(x)\).
 \item If \(\lambda(y) \neq \lambda(x + y)\) then \(\lambda(x + y) = \lambda(y) + 1\) since \(x \leqslant b < a\). 
-	Besides, \(n + 1 = f(y) = n +  h(\lambda(y))\). Hence \(h(\lambda(y)) = 1\). Moreover \(h(1) = 1\) since \(h\) 
-	is an ordered coloring. Therefore, given that \(h\) is sum-free, \(h(\lambda(y) + 1) \neq 1\). If \(\pi(x + y) \in 
-	A_{n + 1}\) then \(f(x + y) = n + h(\lambda(x + y)) \neq n + 1\). Otherwise, \(f(x + y) \leqslant n\). Hence 
-	in both cases \(f(x + y) \neq f(x)\).
+	Besides, \(n + 1 = h(y) = n +  g(\lambda(y))\). Hence \(g(\lambda(y)) = 1\). Moreover \(g(1) = 1\) since \(g\) 
+	is an ordered coloring. Therefore, given that \(g\) is sum-free, \(g(\lambda(y) + 1) \neq 1\). If \(\pi(x + y) \in 
+	A_{n + 1}\) then \(h(x + y) = n + g(\lambda(x + y)) \neq n + 1\). Otherwise, \(h(x + y) \leqslant n\). Hence 
+	in both cases \(h(x + y) \neq h(x)\).
 \end{itemize}
@@
 \par
-By definition of \(f\) and since \(f(x)=f(y)\), \(g(\pi(x)) = g(\pi(y))\). Distinguish between two cases according 
+By definition of \(h\) and since \(h(x)=h(y)\), \(f(\pi(x)) = f(\pi(y))\). Distinguish between two cases according 
 to the value of \(\pi(x)+\pi(y)\).
 \begin{itemize}
-\item If \(\pi(x) + \pi(y) \leqslant a+b\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(g(\pi(x + y)) \neq g(\pi(x))\) since 
-	\(g\) is sum-free for \(x>b\)
+\item If \(\pi(x) + \pi(y) \leqslant a+b\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(f(\pi(x + y)) \neq f(\pi(x))\) since 
+	\(f\) is sum-free for \(x>b\)
 \item \begin{sloppypar} 
-	If \(\pi(x)+\pi(y)>a+b\) then given that \(g\) is a WSF-template, \({g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x))}\) since 
-	\({g(\pi(x)) = g(\pi(y))}\). Besides,  \({g(\pi(\pi(x)+\pi(y))) = g(\pi(x + y))}\) (proposition \ref{prop4}). Hence \({g(\pi(x + y)) 
-	\neq  g(\pi(x))}\).
+	If \(\pi(x)+\pi(y)>a+b\) then given that \(f\) is a WSF-template, \({f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x))}\) since 
+	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (proposition \ref{prop4}). Hence \({f(\pi(x + y)) 
+	\neq  f(\pi(x))}\).
 	\end{sloppypar}
@@
 \par
-By definition of \(f\), \(f(x) \neq f(y)\).\\
+By definition of \(h\), \(h(x) \neq h(y)\).\\
 
@@
 \par
-In particular \(g(\pi(x)) = g(\pi(y))=n + 1\). Distinguish between three cases according to the value of \(\pi(x) + \pi(y)\).
+In particular \(f(\pi(x)) = f(\pi(y))=n + 1\). Distinguish between three cases according to the value of \(\pi(x) + \pi(y)\).
 \begin{itemize}
 \item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\) 
-	(proposition \ref{prop7}). By definition of \(f\) and since \(f(x) = f(y)\), \(h(\lambda(x)) = h(\lambda(y))\).
+	(proposition \ref{prop7}). By definition of \(h\) and since \(h(x) = h(y)\), \(g(\lambda(x)) = g(\lambda(y))\).
 	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x))\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\) 
-	then \(f(x + y) = n + h(\lambda(x + y))\). And \(f(x) = n + h(\lambda(x))\). Therefore, \(f(x + y)  \neq f(x)\). 
-	Otherwise \(f(x+y) \leqslant n < f(x)\). In particular \(f(x + y) \neq f(x)\).
-\item If \(\pi(x)+\pi(y)>2a+b\) then \(g(\pi(\pi(x)+\pi(y))) \neq g(\pi(x)) = n + 1\) since \(g\) is a \(b\)-WSF template and 
-	\(g(\pi(x)) = g(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (proposition \ref{prop4}), \(g(\pi(x+y)) \neq n + 1\).
+	then \(h(x + y) = n + g(\lambda(x + y))\). And \(h(x) = n + g(\lambda(x))\). Therefore, \(h(x + y)  \neq h(x)\). 
+	Otherwise \(h(x+y) \leqslant n < h(x)\). In particular \(h(x + y) \neq h(x)\).
+\item If \(\pi(x)+\pi(y)>2a+b\) then \(f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x)) = n + 1\) since \(f\) is a \(b\)-WSF template and 
+	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (proposition \ref{prop4}), \(f(\pi(x+y)) \neq n + 1\).
 \item \begin{sloppypar}
-	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(g_{| [\![b, a + b ]\!]}\) is 
-	sum-free, \({g(\pi(x) + \pi(y)) \neq g(\pi(x)) = n + 1}\). That is \({g(\pi(x + y)) \neq n + 1}\) (proposition \ref{prop1}).
+	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(f_{| [\![b, a + b ]\!]}\) is 
+	sum-free, \({f(\pi(x) + \pi(y)) \neq f(\pi(x)) = n + 1}\). That is \({f(\pi(x + y)) \neq n + 1}\) (proposition \ref{prop1}).
 	\end{sloppypar}
@@
 \par
-In both of the last two cases, \({g(\pi(x + y)) \neq n + 1}\) that is \(x+y \in \mathcal{C}\). Therefore \(f(x+y) < n \leqslant f(x)\). 
-In particular, \(f(x + y) \neq f(x)\). \\
+In both of the last two cases, \({f(\pi(x + y)) \neq n + 1}\) that is \(x+y \in \mathcal{C}\). Therefore \(h(x+y) < n \leqslant h(x)\). 
+In particular, \(h(x + y) \neq h(x)\). \\
 \end{proof}

### 2021-05-09 article/introduction.tex

@@
     \hline
-    \multirow{2}{*}{before Rowley} & 2* & 8* & 23* & 66* & 196 & 582 & 1\,740 & 5\,201 & 15\,596 & 51\,520 & 172\,216 & 575\,664 \\
+    \multirow{2}{*}{Before Rowley} & 2* & 8* & 23* & 66* & 196 & 582 & 1\,740 & 5\,201 & 15\,596 & 51\,520 & 172\,216 & 575\,664 \\
       & & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
@@
     \hline
-    \hyperref[WeakSchur]{\textbf{our results}} & & & & & & & & & \textbf{22\,536} & \textbf{71\,214} & \textbf{243\,794} & \textbf{815\,314} \\
+    \hyperref[WeakSchur]{\textbf{Our results}} & & & & & & & & & \textbf{22\,536} & \textbf{71\,214} & \textbf{243\,794} & \textbf{815\,314} \\
     \hline

### 2021-05-09 article/schur.tex
article push

@@
 			f(u) & \text{if}~f(u) \leqslant n \\
-			k + g(\alpha) & \text{if}~f(u) = n + 1 \\
+			n + g(\alpha) & \text{if}~f(u) = n + 1 \\
 		\end{array} \right.
@@
 	\(h\) is well-defined since, by definition of \(m_{n+1}\), \(\forall x \in [\![p q + 1, p q + m_{n + 1} - 1 ]\!], f(u) 
-	\leqslant k\) and therefore \(\forall x \in [\![1,pq+m_{n+1}-1]\!], f(u) = n + 1 \implies \alpha \in [\![1, p]\!]\).
+	\leqslant n\) and therefore \(\forall x \in [\![1,pq+m_{n+1}-1]\!], f(u) = n + 1 \implies \alpha \in [\![1, p]\!]\).
 
@@
 
-	\noindent \underline{\textbf{Case 1:} \(h(x) \leqslant k\)}
+	\noindent \underline{\textbf{Case 1:} \(h(x) \leqslant n\)}
 	\par
-	Assume that \(h(x+y) \leqslant k\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of \(h\) 
+	Assume that \(h(x+y) \leqslant n\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of \(h\) 
 	and given that \(h(u) = h(v)\), \(f(u) = f(v)\). Distinguish between two cases according to the value of \(x + y\).
@@
 \begin{itemize}
-		\item \(\forall (x, y) \in [\![1, q]\!]^2,(f(x) = f(y) \text{ and } (x + y) \mod q \leqslant b) 
-		\implies g((x + y) \mod q) \neq f(x)\)
-		\item \(\forall (x, y) \in [\![1, q]\!] \times  [\![1, b]\!], (f(x) = g(y) \text{ and } x + y \leqslant b) 
-		\implies g(x + y) \neq f(x)\)
+\item \(\forall (x, y) \in [\![1, q]\!]^2, \left\{
+	\begin{array}{l}
+		f(x) = f(y) \\
+		(x + y) \mod q \leqslant b
+	\end{array}
+	\right. \implies g((x + y) \mod q) \neq f(x)\)
+\item \(\forall (x, y) \in [\![1, q]\!] \times  [\![1, b]\!],  \left\{
+	\begin{array}{l}
+		f(x) = g(y) \\
+		x + y \leqslant b
+	\end{array}
+	\right. \implies g(x + y) \neq f(x)\)
 \end{itemize}
@@
 \par
-Here are the best inequalities on Schur numbers so far (the templates corresponding to the third, fourth and fifth 
-inequalities can be found in the appendix).
+Here are the best inequalities on Schur numbers so far (the \hyperref[SF-templates]{templates} corresponding to 
+the third, fourth and fifth inequalities can be found in the appendix).
 \[

### 2021-05-09 article/weakschur.tex
accolades
article push

@@
 \renewcommand{\arraystretch}{1.7}
-\setlength{\arraycolsep}{4pt}
+\setlength{\arraycolsep}{3pt}
 
 \[
-\begin{NiceArray}{*{13}{c}}[corners=NW,hvlines,xdots/line-style={solid}]
+\begin{NiceArray}{*{13}{c}}[corners={NW,SW},hvlines,first-row,last-row,first-col]
 \CodeBefore
@@
 \Body
-	& & & & & 1 & 2 & ... & r & r + 1 & ... & b - 1 & b \\
-	a - l & a - l + 1 & ... & a - 1 & a & a + 1 & ... & a + r - 1 & a + r & a + r + 1 & ... & a + b - 1 & a + b \\
-	2 a - l & ... & ... & ... & 2 a & ... & ... & ... & 2 a + r & ... & ... & ... & 2 a + b \\
-	... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
-	... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
-	p a - l & ... & ... & ... & p a & ... & ... & ... & p a + r & ... & ... & ... & p a + b \\
+	& & & & & & \Block{1-8}{\overbrace{\hphantom{---------------------------}}^{\mathcal{T}}} \\
+	& & & & & & 1 & 2 & ... & r & r + 1 & ... & b - 1 & b \\
+	\Block{5-1}{\mathcal{R} \left\{ \vphantom{\begin{array}{l} . \\ . \\ . \\ . \\ . \\ . \\ . \\ . \\ . \end{array}} \right.} 
+	& a - l & a - l + 1 & ... & a - 1 & a & a + 1 & ... & a + r - 1 & a + r & a + r + 1 & ... & a + b - 1 & a + b \\
+	& 2 a - l & ... & ... & ... & 2 a & ... & ... & ... & 2 a + r & ... & ... & ... & 2 a + b \\
+	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
+	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
+	& p a - l & ... & ... & ... & p a & ... & ... & ... & p a + r & ... & ... & ... & p a + b \\
+	& & & & & & & & & & \Block{1-4}{\underbrace{\hphantom{--------------}}_{\mathcal{C}}} \\
 \end{NiceArray}
@@
 \begin{itemize}
-\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!], (f(x) = f(y) \text{ and } \pi(x + y) \leqslant b + c)
-	\implies g(\pi(x + y)) \neq f(x)\)
-\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!],  (f(x) = g(y) \text{ and } \pi(x + y) \leqslant b + c)
-	\implies g(\pi(x + y)) \neq f(x)\)
+\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!],  \left\{
+	\begin{array}{l}
+		f(x) = f(y) \\
+		\pi(x + y) \leqslant b + c
+	\end{array}
+	\right. \implies g(\pi(x + y)) \neq f(x)\)
+\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!], \left\{
+	\begin{array}{l}
+		f(x) = g(y) \\
+		\pi(x + y) \leqslant b + c
+	\end{array}
+	\right. \implies g(\pi(x + y)) \neq f(x)\)
 \end{itemize}
 
-Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(i \longmapsto g(i - p S(n))\), we have\\
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have\\
 \[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
@@
 The idea is the same as in the previous theorem. The only difference is the WSF property inherited
-from the WSF-template.
+from the WSF-template. \\
 \end{proof}
@@
 
-\qquad Having found suitable templates, which can be found in the appendix, with a SAT solver, we claim that for all \(n \in
-\mathbb{N}^*\)
+\qquad We exhibited WSF-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities 
+of the type \(WS(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
+\((a, b)\) (for the lexicographic order).
 
@@
 
-The first two inequalities were found by Rowley, they are detailed in \cite{RowleyWS}. The third inequality is optimal and was found with a SAT solver.
-It uses the first sophistication explained in the previous subsection in order to add the last number in the first color.
+The first two inequalities were found by Rowley, they are detailed in \cite{RowleyWS}. The third inequality is optimal 
+and was found with a SAT solver. It uses the first sophistication explained in the previous subsection in order to add 
+the last number in the first color. The \hyperref[WSF-templates]{corresponding template} can be found in the appendix.
 As for the fourth inequality, it was obtained by combining an optimal SF-template with width 33 with a WSF-template with width 4.
@@
 It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of
-5 colors which start with a good \(\WS(4)\) partition. However, this approach most likely prevents us from finding the best WSF-templates
+5 colors which start with a good \(\WS(4)\) partition and we assumed that the special color was the last by order of 
+appearance. However, this approach most likely prevents us from finding the best WSF-templates
 as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates

### 2021-06-01 rapport/schur.tex
Correction coquille

--- 2021-05-09 article/schur.tex
@@
 extend a sum-free partition by repeating it and they use an other sum-free partition to color the other half according 
-to the line number. This way the "blocks" act as safe areas for each other. We give here an example for \(p = 9\), 
-\(q = 4\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott and 
+to the line number. This way the "blocks" act as safe areas for each other. We give here an example for \(p = 4\), 
+\(q = 9\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott and 
 Hanson's construction and with a SF-template which is not included in Abbott and Hanson's construction. In both cases, 

### 2021-06-04 article/article.tex
Correction numérotation
corrections
accolades
elsarticle
adieu sat
ptites modifs

@@
-\documentclass{article}
+\documentclass[3p]{elsarticle}
 \title{New lower bounds for Schur and weak Schur numbers}
@@
 \usepackage{dsfont}
+\usepackage{MyMnSymbol}
 
@@
 \usepackage{nicematrix}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
 
@@
 \newtheorem{notation}[definition]{Notation}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{computational theorem}{Computational Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{remark}{Remark}[section]
-\newtheorem{proposition}{Proposition}[section]
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{computational theorem}[definition]{Computational Theorem}
+\newtheorem{corollary}[definition]{Corollary}
+\newtheorem{remark}[definition]{Remark}
+\newtheorem{proposition}[definition]{Proposition}
 
@@
 
-\maketitle
-
 \begin{abstract}
@@
 get explicit partitions improving lower bounds as well as the growth rate for both Schur numbers and Ramsey 
-numbers \(R_n(3)\). We also developed a new method to improve lower bounds for weak Schur numbers. 
-Furthermore, this paper tries to analyze former works on weak Schur numbers based on the principle that good 
-partitions into \(n+1\) weakly sum-free subsets start with a good partition into \(n\) weakly sum-free subsets. 
+numbers \(R_n(3)\). We also developed a method to improve lower bounds for weak Schur numbers. 
+Furthermore, we try to analyze former works on weak Schur numbers based on the principle that \textit{good} 
+partitions into \(n+1\) weakly sum-free subsets start with a \textit{good} partition into \(n\) weakly sum-free subsets. 
 We show that exceeding the previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption 
-upon imposing certain conditions on the good 5-subsets partitions. The new lower bounds include 
-\(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS (9) \geqslant 22\,536 \) and 
+upon imposing certain conditions on the \textit{good} 5-subsets partitions. The new lower bounds include 
+\(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS (9) \geqslant 22\,536\) and 
 \(\WS (10) \geqslant 71\,214 \).
@@
 
-\include{introduction.tex}
+\maketitle
 
-% \include{definitions_notations.tex}
+\input{introduction.tex}
 
-\include{schur.tex}
+\input{schur.tex}
 
-\include{weakschur.tex}
-
-\include{search_space.tex}
+\input{weakschur.tex}
 

### 2021-06-04 rapport/introduction.tex
ptites modifs

--- 2021-05-09 article/introduction.tex
@@
 the \(n^{\text{th}}\) weak Schur number \cite{Irving1973}. Only the first values of these sequences are known. 
-This article focuses on the lower bounds for these numbers.
+Our study focuses on the lower bounds for these numbers.
 
@@
 was known for weak Schur numbers and as a result the best known partitions for large weak Schur numbers 
-did not utilize the weakly sum-free hypothesis.
+did not use the weakly sum-free hypothesis.
 
@@
 \par
-In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers \cite{RowleyRamsey} which 
-generalizes Abbott and Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. 
-Rowley also gives two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
+In 2020, Rowley introduced the notion of templates for Schur and Ramsey numbers \cite{RowleyRamsey} which 
+generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalties) for Schur numbers. 
+He also provides two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
 over previous lower bounds which besides do utilize the \textit{weakly} sum-free hypothesis.
@@
 \vspace{1.5ex}
-* denotes an exact value, not just a lower bound
+* denotes the exact value
 \end{center}
@@
 
-\qquad The main contribution of this article is a generalization of the concept of template to weak Schur numbers. 
-It gives new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special 
+\qquad Our main contribution is a generalization of the concept of template to weak Schur numbers. 
+Our templates provide new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special 
 case an analogous for weak Schur numbers of Abbott and Hanson's construction for Schur numbers.
@@
 \par
-In the \hyperref[Schur]{first section}, we explain Rowley's template-based construction in the context of 
+In the \hyperref[Schur]{section 2}, we explain Rowley's template-based construction in the context of 
 Schur numbers and then give new templates, thus providing new lowers bounds and inequalities as well as 
@@
 \par
-Then, in the \hyperref[WeakSchur]{second section}, we generalize the concept of templates to weak Schur numbers 
+Then, in the \hyperref[WeakSchur]{section 3}, we generalize the concept of templates to weak Schur numbers 
 and provide new lower bounds for weak Schur numbers.
@@
 \par
-Finally, in the \hyperref[SearchSpace]{third section}, we analyze the significant difference between new lower 
+Finally, in the \hyperref[SearchSpace]{section 4}, we analyze the significant difference between new lower 
 bounds obtained with templates and the former lower bounds obtained by computer search and we provide 
-evidence which indicate that the main assumption made in those articles removes the optimal partitions from the 
+evidence which indicates that the main assumption made in those articles removes the optimal partitions from the 
 search space.

### 2021-06-04 rapport/schur.tex
ptites modifs

@@
 	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there exists a partition of \([\![1,pq+m_{n+1}
-	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) is the minimum of the special subset in the \(SF\)-template.
+	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element in the special subset in the \(SF\)-template.
 \end{theorem}
@@
 	\par
-	NB: In the following 3 predicates, the conditions \(x + y \leqslant q\)  and \(x + y \leqslant p\) are omitted for readability.
+	NB: In the following three predicates, the conditions \(x + y \leqslant q\)  and \(x + y \leqslant p\) are omitted for readability.
 	\par
-	The sum-free condition is expressed as
-	\[\forall (x,y) \in [\![1,q]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)\]
-	\[\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)\]
+	The sum-free condition is expressed as:
+	\[\forall (x,y) \in [\![1,q]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)\],
+	\[\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)\].
 
-	The additionnal constraint for the SF-template is
+	The additionnal constraint for the SF-template is:
 	\[
@@
 	\right. \Longrightarrow f(x+y-q) \neq f(x)
-	\]
+	\].
 
-	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), write \(x = (\alpha - 1) + u\) for some integers \(\alpha \in \mathbb{Z}\) and 
+	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), write \(x = (\alpha - 1) + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
 	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\) (resp. \(u\)) can be interpreted as the row 
-	(resp. column) number of \(x\). Define a new coloring \(h\) as follows
+	(resp. column) number of \(x\). A new coloring \(h\) is defined as follows:
 	\[
 	\begin{array}{c c c l}
-		h : & [\![1,pq+m_{n+1}-1]\!] & \longrightarrow & [\![1,n+k]\!] \\
+		h : & [\![1,pq+m_{n+1}-1]\!] & \longrightarrow & [\![1,n+k]\!], \\
 		& x & \longmapsto & 
 		\left\{ \begin{array}{l l}
-			f(u) & \text{if}~f(u) \leqslant n \\
-			n + g(\alpha) & \text{if}~f(u) = n + 1 \\
+			f(u), & \text{if}~f(u) \leqslant n, \\
+			n + g(\alpha), & \text{if}~f(u) = n + 1. \\
 		\end{array} \right.
@@
 
-	\(h\) is well-defined since, by definition of \(m_{n+1}\), \(\forall x \in [\![p q + 1, p q + m_{n + 1} - 1 ]\!], f(u) 
+	Function \(h\) is well-defined since, by definition of \(m_{n+1}\), \(\forall x \in [\![p q + 1, p q + m_{n + 1} - 1 ]\!], f(u) 
 	\leqslant n\) and therefore \(\forall x \in [\![1,pq+m_{n+1}-1]\!], f(u) = n + 1 \implies \alpha \in [\![1, p]\!]\).
@@
 	We now prove that \(h\) is a sum-free coloring. Let \(x,y \in [\![1,pq + m_{n+1}-1]\!]\) such that \(h(x) = h(y)\) 
-	and \(x+y \leqslant pq+m_{n+1}-1\). We claim that \(h(x+y) \neq h(x)\). Write \(x = (\alpha - 1) q + u\) and 
-	\(y = (\beta - 1) q + v\) where \(\alpha, \beta \in \mathbb{Z}\) and \(u, v \in [\![1,q]\!]\). Distinguish between 
-	two cases according to the value of \(h(x)\). \\
+	and \(x+y \leqslant pq+m_{n+1}-1\). We claim that \(h(x+y) \neq h(x)\). We write \(x = (\alpha - 1) q + u\) and 
+	\(y = (\beta - 1) q + v\) where \(\alpha, \beta \in \mathbb{Z}\) and \(u, v \in [\![1,q]\!]\). Two cases are to be
+	distinguished according to the value of \(h(x)\). \\
 
@@
 	\par
-	Assume that \(h(x+y) \leqslant n\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of \(h\) 
-	and given that \(h(u) = h(v)\), \(f(u) = f(v)\). Distinguish between two cases according to the value of \(x + y\).
+	Let us assume that \(h(x+y) \leqslant n\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of function 
+	\(h\) and given that \(h(u) = h(v)\), we conclude \(f(u) = f(v)\). Two cases are to b distinguished according to the value of \(x + y\).
 
 	\begin{itemize}
-	\item If \(u + v > q\), write \(w = u + v - q \in [\![1, q]\!]\). Then \(x + y = (\alpha + \beta - 1) q + w\). By definition, 
+	\item If \(u + v > q\), we write \(w = u + v - q \in [\![1, q]\!]\). Consequentely \(x + y = (\alpha + \beta - 1) q + w\). By definition, 
 		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the additionnal constraint on \(f\) implies \(f(w) 
 		\neq f(u)\), that is \(h(x + y) \neq h(x)\).
-	\item If \(u + v \leqslant p\), write \(w = u + v \in [\![1, q]\!]\). Then \(x+y = (\alpha + \beta- 2) q + w\). By definition, 
+	\item If \(u + v \leqslant p\), we write \(w = u + v \in [\![1, q]\!]\). Consequentely \(x+y = (\alpha + \beta- 2) q + w\). By definition, 
 		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the sum-free property of \(f\) implies \(f(w) \neq f(u)\), 
@@
 	\par
-	\(h(x) = n + g(\alpha) = 
+	Now we have \(h(x) = n + g(\alpha) = 
 	k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As in the first case, distinguish between two cases according 
@@
 
-The following proposition can help improve the additive constant of a SF-template. Although it does not allow us to 
+The following proposition may improve the additive constant of a SF-template. Although it does not allow us to 
 improve the SF-templates we have found, the analogous of this proposition for WSF-templates (see next section) 
@@
 Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a SF-template with width \(q\) and \(n+1\) 
-colors. Let \(b \in \mathbb{N}\) (\(b = m_{n+1} - 1\) works) and assume there there exists a coloring \(g\) of 
-\([\![1, b]\!]\) with \(n+1\) colors such that
+colors. Let \(b \in \mathbb{N}\) and assume there is a coloring \(g\) of 
+\([\![1, b]\!]\) with \(n+1\) colors such that:
 
@@
 	\end{array}
-	\right. \implies g((x + y) \mod q) \neq f(x)\)
+	\right. \implies g((x + y) \mod q) \neq f(x)\),
 \item \(\forall (x, y) \in [\![1, q]\!] \times  [\![1, b]\!],  \left\{
@@
 	\end{array}
-	\right. \implies g(x + y) \neq f(x)\)
+	\right. \implies g(x + y) \neq f(x)\).
 \end{itemize}
@@
 Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have
-\[ S(n+k) \geqslant S^+(n+1)S(k) + b\]
+\[ S(n+k) \geqslant S^+(n+1)S(k) + b\].
 \end{proposition}
@@
 \begin{theorem}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a SF-template with width \(q\) and \(n+1\) colors,
-	and a SF-template with width \(p\) and \(k\) colors, then there exists SF-template with width \(pq\) and \((n+k)\) 
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is a SF-template with width \(q\) and \(n+1\) colors,
+	and a SF-template with width \(p\) and \(k\) colors, then there also is a SF-template with width \(pq\) and \((n+k)\) 
 	colors.
@@
 
-	And the associated inequality
+	The inequality associated with this theorme is given by:
 
@@
 	Let \(n, k \in \mathbb{N}^*\). Then
-	\[ S^+(n+k) \geqslant S^+(n+1)S^+(k) \]
+	\[ S^+(n+k) \geqslant S^+(n+1)S^+(k) \].
 \end{corollary}
@@
 
-We exhibited SF-templates using a SAT solver, hence providing lower bound on \(S^+\) and inequalities 
-of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
-\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5, in order to reduce the search space we 
+We produced SF-templates using a SAT solver, hence providing lower bound on \(S^+\) and inequalities 
+of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing the largest value of 
+\((a, b)\) (in the lexicographic order). When the number of colors excceeded five, in order to reduce the search space we 
 only looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
@@
 Abott \cite{AbbottHanson}
-and the third one to Rowley \cite{RowleyRamsey}. The other ones are new.
+and the third one to Rowley \cite{RowleyRamsey}. The three last inequalies are our result.
 
 \par
-The first 3 inequalities are optimal. The fourth one is optimal among symmetric SF-templates whose special color is 
+The first three inequalities are optimal. The fourth one is optimal among symmetric SF-templates whose special color is 
 the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
@@
 Finally, the sixth one is obtained by combining a SF-template with width 380 and one with width 3. 
-Although we could not find a better SF-template with 7 colors, the last inequality is definitely very far from the 
+Although we could not find a better SF-template with seven colors, the last inequality is definitely very far from the 
 optimal value. One may try to seek better templates by constraining less the search space and by using 

### 2021-06-04 rapport/weakschur.tex
ptites modifs

--- 2021-05-09 article/weakschur.tex
@@
 \par
-NB: In the following 5 predicates, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted for readability.
+NB: To keep the notation short, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted in the following five predicates.
 \par
-The (weakly) sum-free conditions are expressed as 
+The (weakly) sum-free conditions are expressed as:
 \[
@@
 \[
-\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
+\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),
 \]
 \[
-\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)
+\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).
 \]
 
-The additionnal constraints for the WSF-template are
+The additionnal constraints for the WSF-template are:
 \[
@@
 \end{array}
-\right. \Longrightarrow f(\pi(x+y)) \neq f(x)
+\right. \Longrightarrow f(\pi(x+y)) \neq f(x),
 \]
@@
 \end{array}
-\right. \Longrightarrow f(x+y - 2 a) \neq f(x)
+\right. \Longrightarrow f(x+y - 2 a) \neq f(x).
 \]
 
-Here, we consider \(\pi\) defined in the previous subsection as an application defined on \([\![b + 1, p a + b]\!]\). 
-Split \([\![1, p a + b]\!]\) into 3 subsets.
+Here, we consider \(\pi\) defined in subsection 3.2 \textbf{LABEL NECESSAIRE} as an application defined on \([\![b + 1, p a + b]\!]\). 
+Split \([\![1, p a + b]\!]\) into three subsets.
 
@@
 
-Define a new coloring \(h\) as follows
+A new coloring \(h\) is defined as follows:
 \[
@@
 
-\(h\) is well defined since \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) is a partition of  \([\![1, p a + b]\!]\). 
-We now prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) such that \(x \neq y\), 
-\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Distinguish between six cases 
+Function \(h\) is well defined since \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) is a partition of  \([\![1, p a + b]\!]\). 
+We now prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) be such that \(x \neq y\), 
+\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). We distinguish between six cases 
 according to the subsets \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) to which \(x\) and \(y\) belong. It is 

### 2021-06-05 rapport/weakschur.tex
Première série de corrections - partie WS

@@
 \begin{theorem}
-\label{theorem}
+\label{Theorem3.1}
 \begin{sloppypar}
@@
 
-In particular, by setting \(q = \WS (n)\) and \(p = S(k)\) in the above theorem, one obtains the following corollary.
+In particular, by setting \(q = \WS (n)\) and \(p = S(k)\) in \hyperref[Theorem3.1]{Theorem 3.1}, one obtains the following corollary.
 
 \begin{corollary}
+\label{Corollary3.2}
 \( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } \WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \displaystyle \frac{\WS (n)}{2}
@@
 \begin{remark}
-The above inequality can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
+The inequality from \hyperref[Corollary3.2]{Corollary 3.2} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
 odd in the theorem). However, it makes the proof less clear and it is never useful in practice.
@@
 
-Given that this theorem will appear as a particular case of a more general theorem after the introduction of
-templates for weak Schur numbers, we only give here an intuitive explanation of the above theorem; a formal
+Given that \hyperref[Theorem3.1]{Theorem 3.1} will appear as a particular case of a more general theorem after the introduction of
+templates for weak Schur numbers, we only give here an intuitive explanation of the demonstration; a formal
 \hyperref[proof_theorem]{proof} can be found in the appendix.
@@
 subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
-and let's try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
+and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
 \(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\).
 
-First, put the integers of \([\![1, ap + q]\!]\) in the following table (with \(a\) columns and \(p + 1\) lines) 
+First, we put the integers of \([\![1, ap + q]\!]\) in the following table (with \(a\) columns and \(p + 1\) lines) 
 and divide it into 3 blocks (the columns are numbered from \(-l\) to \(+q\)).
@@
 \subsection{Definition of \(\WS^+\)}
+\label{DefinitionWS+}
 
@@
 \begin{definition}
-Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
-\[ \pi_{a,b}:x \longmapsto (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
+Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). We define :
+\[ \pi_{a,b}:x \longmapsto (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x \mod a).\]
 \end{definition}
 
-If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\). Notice that 
-\({\forall x \in \mathbb{Z}, \pi(x) = x \mod a}\) and \({\forall x \in [\![b + 1, a + b]\!], b + 1 \leqslant \pi(x) \leqslant a + b}\).
+If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\). Notice that for all
+\(x \in \mathbb{Z}, \pi(x) = x \mod a\) and for all \(x \in [\![b + 1, a + b]\!], b + 1 \leqslant \pi(x) \leqslant a + b\).
 
 \begin{sloppypar}
-\(\pi\) is the projection on the first line mentioned in the intuitive explanation. 
+\(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
+calculative properties on \(\pi\) reflecting the behaviour of an element's column number in Table 3.1 and that we will use later
+when we introduce WSF-templates.
 \end{sloppypar}
@@
 \begin{array}{l l l l}
-	\pi(x + y) & = & \pi(x + \pi(y)) & proposition \ref{prop2} \\
-	 & = & x + \pi(y) & proposition \ref{prop1}
+	\pi(x + y) & = & \pi(x + \pi(y)) & \text{by \hyperref[prop2]{Proposition 3.6}} \\
+	 & = & x + \pi(y) & \text{by \hyperref[prop1]{Proposition 3.5}}
 \end{array}
@@
 
+After defining the function related to the column number of each element in Table 3.1,
+we introduce the function related to its line number.
+
 \begin{definition}
@@
 
-\(\lambda\) is the function which maps an element \(x\) to its line number as mentioned in the intuitive explanation.
+Function \(\lambda\) maps an element \(x\) to its line number as mentioned in the intuitive explanation.
+As we just did with \(\pi\), we proove three more results on both \(\pi\) and \(\lambda\) that will appear useful in
+\hyperref[ConstructionWSF]{Subsection 3.3}.
 
@@
 \begin{proof}[\textsc{Proof.}]
-By applying twice proposition \ref{prop5}, \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\). 
-The result is then obtained by symplying the equality. \\
+By applying \hyperref[prop5]{Proposition 3.10} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\). 
+The result is then obtained by simplying the equality. \\
 \end{proof}
@@
 \begin{proof}[\textsc{Proof.}]
-By proposition \ref{prop5}, \(x + y = a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a\). Then
+By \hyperref[prop5]{Proposition 3.10}, \(x + y = a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a\). Then
 \[
@@
 Let \( (a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\). Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
-This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WSF-template) with width \(a\) and \(n\) colors if
+This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WSF-template) with width \(a\) and \(n\) colors when :
 
 \begin{itemize}
-\item \(\forall i \in [\![1, n]\!], A_i\) is weakly-sum-free
-\item \(\forall i \in [\![1, n]\!], A_i\backslash [\![1, b]\!]\) is sum-free
-\item For \(A_n\) (the special subset)
+\item \(\forall i \in [\![1, n]\!], A_i\) is weakly-sum-free,
+\item \(\forall i \in [\![1, n]\!], A_i\backslash [\![1, b]\!]\) is sum-free,
+\item For \(A_n\) (the special subset) :
 	\[
-	\forall (x,y) \in A_n^2, \,x+y>b+2a \implies x+y-2a\notin A_n
+	\forall (x,y) \in A_n^2, \,x+y>b+2a \implies x+y-2a\notin A_n,
 	\]
@@
 	\[
-	\forall i \in [\![0,n-1]\!], \, \forall(x,y) \in A_i^2, \, x+y>a+b \implies \pi(x+y) \notin A_i
+	\forall i \in [\![0,n-1]\!], \, \forall(x,y) \in A_i^2, \, x+y>a+b \implies \pi(x+y) \notin A_i.
 	\]
@@
 Please note that the special color \(n\) is not necessarily the last color by order of appearance.
+We now introduce the number \(\WS^+(n)\) that plays the same role as \(\S^+(n)\) for SF-templates.
+However, WSF-templates being more sophisticated than SF-templates, the definition of \(\WS^+(n)\)
+is slighty more complicted.
 
@@
 Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WSF-template with width \(a\) 
-and \(n\) colors, define
+and \(n\) colors, we define :
 \[
-\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WSF-template with width } a \text{ and } n \text{ colors} \}
+\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WSF-template with width } a \text{ and } n \text{ colors} \}.
 \]
-If no such \(a\) exists, set \(\WS_b^+(n) = 0\).
+If no such \(a\) exists, we set \(\WS_b^+(n) = 0\).
 \end{definition}
@@
 \begin{definition}
-Let \( n \in \mathbb{N}^*\). Define 
+Let \( n \in \mathbb{N}^*\). We define :
 \[
-\WS^+(n)=\max_{b\in \mathbb{N}^*} \WS_b^+(n)
+\WS^+(n)=\max_{b\in \mathbb{N}^*} \WS_b^+(n).
 \]
 \end{definition}
-
+The following proposition briefly shows how \(\WS^+(n)\) compares to weak Schur numers.
 \begin{proposition}
-Let \(n \in [\![2, +\infty]\!]\). Then
+Let \(n \in [\![2, +\infty]\!]\). Then :
 \[
-\frac{3}{2} \WS (n-1)+1 \leqslant \WS^+(n) \leqslant \WS (n)
+\frac{3}{2} \WS (n-1)+1 \leqslant \WS^+(n) \leqslant \WS (n).
 \]
@@
 \subsection{Construction of weak Schur partitions using WSF-templates}
+\label{ConstructionWSF}
 
 \begin{theorem}
+\label{Theorem3.18}
 Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\) 
@@
 
-In particular, by setting \(p = S(k)\) and \(a = \WS^+(n + 1)\) in the last theorem, the next corollary follows.
+In particular, by setting \(p = S(k)\) and \(a = \WS^+(n + 1)\) in \hyperref[Theorem3.18]{Theorem 3.18}, the next corollary follows.
 
@@
 Let \(n,k \in \mathbb{N}^*\) and set \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
-Then
+Then :
 \[
-\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}
+\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}.
 \]
@@
 \[
-\max_{b \in \mathbb{N}^*} \left\{\min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}
+\max_{b \in \mathbb{N}^*} \left\{\min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}.
 \]
@@
 The (weakly) sum-free conditions are expressed as:
-\[
+\begin{equation}
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \right. \Longrightarrow f(x+y) \neq f(x)
-\]
-\[
+\end{equation}
+\begin{equation}
 \forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),
-\]
-\[
+\end{equation}
+\begin{equation}
 \forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).
-\]
+\end{equation}
 
 The additionnal constraints for the WSF-template are:
-\[
+\begin{equation}
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \right. \Longrightarrow f(\pi(x+y)) \neq f(x),
-\]
-\[
+\end{equation}
+\begin{equation}
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \right. \Longrightarrow f(x+y - 2 a) \neq f(x).
-\]
+\end{equation}
 
-Here, we consider \(\pi\) defined in subsection 3.2 \textbf{LABEL NECESSAIRE} as an application defined on \([\![b + 1, p a + b]\!]\). 
+Here, we consider \(\pi\) defined in \hyperref[DefinitionWS+]{subsection 3.2} as an application defined on \([\![b + 1, p a + b]\!]\). 
 Split \([\![1, p a + b]\!]\) into three subsets.
@@
 We now prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) be such that \(x \neq y\), 
-\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). We distinguish between six cases 
+\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Nine cases are to be distinguished 
 according to the subsets \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) to which \(x\) and \(y\) belong. It is 
@@
 Given that \(h(x) = h(y)\) and by definition of \(h\), \(f(x) = f(\pi(y))\). Besides, \(f(\pi(y)) \leqslant n\) since 
-\(y \in \mathcal{C}\). Distinguish between two cases according to the value of \(x + \pi(y)\).
+\(y \in \mathcal{C}\). Two cases are to be distinguished according to the value of \(x + \pi(y)\).
 \begin{itemize}
 \item \begin{sloppypar}
-	If \(x + \pi(y) \leqslant a + b\) then \(f(x + \pi(y)) = f(\pi(x + y))\) (proposition \ref{prop3}). Given that \(f\) is 
+	If \(x + \pi(y) \leqslant a + b\) then \(f(x + \pi(y)) = f(\pi(x + y))\) (\hyperref[prop3]{Proposition 3.7}). Given that \(f\) is 
 	a weakly sum-free coloring, \(f(x+\pi(y)) \neq f(x)\) since \(f(x)=f(\pi(y))\) and \(x \neq \pi(y)\) since
@@
 	If \(x+\pi(y)> a+b\) then given that \(f\) is a WSF-template and since \({f(x) = f(\pi(y)) \leqslant n}\), 
-	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (proposition \ref{prop2}), such that 
+	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (\hyperref[prop2]{Proposition 3.6}), such that 
 	\({f(\pi(x+ y)) \neq f(x)}\).
@@
 \par
-Necessarily \(h(x) = h(y) = n + 1\). Distinguish between two cases according to the value of \(\lambda(x+y)\).
+Necessarily \(h(x) = h(y) = n + 1\). Two cases are to be distinguished according to the value of \(\lambda(x+y)\).
 \begin{itemize}
-\item If \(\lambda(y)=\lambda(x+y)\) then \(\pi(x + y) = x + \pi(y)\) (proposition \ref{prop6}). By definition of 
+\item If \(\lambda(y)=\lambda(x+y)\) then \(\pi(x + y) = x + \pi(y)\) (\hyperref[prop6]{Proposition 3.11}). By definition of 
 	\(h\), \(f(x) = f(\pi(y))\). Given that \(f\) is a weakly sum-free coloring, \(f(x + \pi(y)) \neq f(x)\) since 
@@
 \par
-By definition of \(h\) and since \(h(x)=h(y)\), \(f(\pi(x)) = f(\pi(y))\). Distinguish between two cases according 
+By definition of \(h\) and since \(h(x)=h(y)\), \(f(\pi(x)) = f(\pi(y))\). Two cases are to be distinguished according 
 to the value of \(\pi(x)+\pi(y)\).
@@
 	If \(\pi(x)+\pi(y)>a+b\) then given that \(f\) is a WSF-template, \({f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x))}\) since 
-	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (proposition \ref{prop4}). Hence \({f(\pi(x + y)) 
+	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (\hyperref[prop4]{Proposition 3.8}). Hence \({f(\pi(x + y)) 
 	\neq  f(\pi(x))}\).
@@
 \par
-In particular \(f(\pi(x)) = f(\pi(y))=n + 1\). Distinguish between three cases according to the value of \(\pi(x) + \pi(y)\).
+In particular \(f(\pi(x)) = f(\pi(y))=n + 1\). Three cases are to be distinguished according to the value of \(\pi(x) + \pi(y)\).
 \begin{itemize}
 \item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\) 
-	(proposition \ref{prop7}). By definition of \(h\) and since \(h(x) = h(y)\), \(g(\lambda(x)) = g(\lambda(y))\).
+	(\hyperref[prop7]{Proposition 3.12}). By definition of \(h\) and since \(h(x) = h(y)\), \(g(\lambda(x)) = g(\lambda(y))\).
 	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x))\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\) 
@@
 \item If \(\pi(x)+\pi(y)>2a+b\) then \(f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x)) = n + 1\) since \(f\) is a \(b\)-WSF template and 
-	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (proposition \ref{prop4}), \(f(\pi(x+y)) \neq n + 1\).
+	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (\hyperref[prop4]{Proposition 3.8}), \(f(\pi(x+y)) \neq n + 1\).
 \item \begin{sloppypar}
 	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(f_{| [\![b, a + b ]\!]}\) is 
-	sum-free, \({f(\pi(x) + \pi(y)) \neq f(\pi(x)) = n + 1}\). That is \({f(\pi(x + y)) \neq n + 1}\) (proposition \ref{prop1}).
+	sum-free, \({f(\pi(x) + \pi(y)) \neq f(\pi(x)) = n + 1}\). That is \({f(\pi(x + y)) \neq n + 1}\) (\hyperref[prop1]{Proposition 3.5}).
 	\end{sloppypar}
@@
 constant) at the cost of dramatically increasing the size of the search space. Therefore, it does not seem relevant to
-use this sophistications given that we could not even find good WSF-templates with 5 colors using a computer (here good
+use this sophistications given that we could not even find good WSF-templates with five colors using a computer (here good
 means better than those obtain by combining smaller templates).
@@
 \begin{theorem}
+\label{Theorem3.22}
 Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\) . If there exists a SF-template with width 
@@
 
-And the associated inequality
+\hyperref[Theorem3.22]{Theorem 3.22} yields the following corollary.
 
@@
 of the type \(WS(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
-\((a, b)\) (for the lexicographic order).
+\((a, b)\) (in the lexicographic order).
 

### 2021-06-06 article/introduction.tex
CC des changements dans rapport vers article + modifs intro

@@
 the \(n^{\text{th}}\) weak Schur number \cite{Irving1973}. Only the first values of these sequences are known. 
-This article focuses on the lower bounds for these numbers.
+In this study, we improve the lower bounds on these numbers.
 
@@
 bounds with Monte-Carlo methods. This was the main approach during the past decade. This search for weakly 
-sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) colors 
-starts with a good weakly sum-free partition into \(n\) colors. 
-However, we show in the \hyperref[SearchSpace]{last section} that this search space may not contain the optimal 
-solutions. Thus further works using similar methods might need to put that assumption aside and find a different 
-search space.
+sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) subsets 
+starts with a good weakly sum-free partition into \(n\) subsets.
 
 \par
-In 2020, Rowley introduced the notion of template for Schur and Ramsey numbers \cite{RowleyRamsey} which 
-generalizes Abbott and Hanson's construction and gives new lower bounds (and inequalties) for Schur numbers. 
-Rowley also gives two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
-over previous lower bounds which besides do utilize the \textit{weakly} sum-free hypothesis.
+In 2020, Rowley introduced the notion of templates for Schur and Ramsey numbers \cite{RowleyRamsey} which 
+generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalties) for Schur numbers. 
+He also provides two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
+over previous lower bounds, and besides do utilize the \textit{weakly} sum-free hypothesis.
 
@@
 
-\begin{center}
-
-\textbf{Table 1 - Comparison of lower bounds for Schur numbers}
-
+\begin{table}
+  \centering
 \begin{tabular}{|*{13}{c|}}
@@
 \end{tabular}
-
+\caption{Comparison of lower bounds for Schur numbers}
+\label{table:1}
+\end{table}
 \vspace{2.5ex}
 
-\textbf{Table 2 - Comparison of lower bounds for weak Schur numbers}
-
+\begin{table}
+  \centering
 \begin{tabular}{|*{13}{c|}}
@@
 \vspace{1.5ex}
-* denotes an exact value, not just a lower bound
-\end{center}
+* denotes the exact value
+\caption{Comparison of lower bounds for weak Schur numbers}
+\label{table:2}
+\end{table}
 
@@
 
-\qquad The main contribution of this article is a generalization of the concept of template to weak Schur numbers. 
-It gives new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special 
-case an analogous for weak Schur numbers of Abbott and Hanson's construction for Schur numbers.
+\qquad Our main contribution is a generalization of the concept of template to weak Schur numbers. 
+Our templates provide new lower bounds (and inequalities) for weak Schur numbers. This construction also includes, 
+as a special case, a construction similar to Abbott and Hanson's \cite{AbbottHanson}, but this time with 
+\textit{weak} Schur numbers.
 
 \par
-In the \hyperref[Schur]{first section}, we explain Rowley's template-based construction in the context of 
-Schur numbers and then give new templates, thus providing new lowers bounds and inequalities as well as 
+In the \hyperref[Schur]{section 2}, we explain Rowley's template-based construction in the context of 
+Schur numbers. Then, we give new templates, thus providing new lowers bounds and inequalities as well as 
 showing that the growth rates for both Schur and Ramsey numbers \(R_n(3)\) exceed 3.28.
@@
 \par
-Then, in the \hyperref[WeakSchur]{second section}, we generalize the concept of templates to weak Schur numbers 
+Then, in the \hyperref[WeakSchur]{section 3}, we generalize the concept of templates to weak Schur numbers 
 and provide new lower bounds for weak Schur numbers.
-
-\par
-Finally, in the \hyperref[SearchSpace]{third section}, we analyze the significant difference between new lower 
-bounds obtained with templates and the former lower bounds obtained by computer search and we provide 
-evidence which indicate that the main assumption made in those articles removes the optimal partitions from the 
-search space.
 

### 2021-06-06 article/weakschur.tex
Deuxième série de corrections - partie WS (dans le bon dossier)

@@
 
+\begin{figure}[H]
+\caption{Construction of the weakly sum-free coloring}
+\label{SchemaWS}
 \[
@@
 \]
+\end{figure}
 
@@
 \begin{definition}
-Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
-\[ \pi_{a,b}:x \longmapsto (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
+Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). We define :
+\[ \pi_{a,b}:x \longmapsto (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x \mod a).\]
 \end{definition}
 
-If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\). Notice that 
-\({\forall x \in \mathbb{Z}, \pi(x) = x \mod a}\) and \({\forall x \in [\![b + 1, a + b]\!], b + 1 \leqslant \pi(x) \leqslant a + b}\).
+If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\). Notice that for all
+\(x \in \mathbb{Z}, \pi(x) = x \mod a\) and for all \(x \in [\![b + 1, a + b]\!], b + 1 \leqslant \pi(x) \leqslant a + b\).
 
 \begin{sloppypar}
-\(\pi\) is the projection on the first line mentioned in the intuitive explanation. 
+\(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
+calculative properties on \(\pi\) reflecting the behaviour of an element's column number in \hyperref[SchemaWS]{Figure \ref{SchemaWS}} and
+that we will use later when we introduce WSF-templates.
 \end{sloppypar}
@@
 
+After defining the function related to the column number of each element in \hyperref[SchemaWS]{Figure \ref{SchemaWS}},
+we introduce the function related to its line number.
+
 \begin{definition}
@@
 \par
-NB: In the following 5 predicates, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted for readability.
+NB: To keep the notation short, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted in the following five predicates.
 \par
-The (weakly) sum-free conditions are expressed as 
-\[
+The (weakly) sum-free conditions are expressed as:
+\begin{equation}
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \right. \Longrightarrow f(x+y) \neq f(x)
-\]
-\[
-\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)
-\]
-\[
-\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)
-\]
+\end{equation}
+\begin{equation}
+\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),
+\end{equation}
+\begin{equation}
+\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).
+\end{equation}
 
-The additionnal constraints for the WSF-template are
-\[
+The additionnal constraints for the WSF-template are:
+\begin{equation}
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \end{array}
-\right. \Longrightarrow f(\pi(x+y)) \neq f(x)
-\]
-\[
+\right. \Longrightarrow f(\pi(x+y)) \neq f(x),
+\end{equation}
+\begin{equation}
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \end{array}
-\right. \Longrightarrow f(x+y - 2 a) \neq f(x)
-\]
+\right. \Longrightarrow f(x+y - 2 a) \neq f(x).
+\end{equation}
 
-Here, we consider \(\pi\) defined in the previous subsection as an application defined on \([\![b + 1, p a + b]\!]\). 
-Split \([\![1, p a + b]\!]\) into 3 subsets.
+Here, we consider \(\pi\) defined in \hyperref[DefinitionWS+]{subsection 3.2} as an application defined on \([\![b + 1, p a + b]\!]\). 
+Split \([\![1, p a + b]\!]\) into three subsets.
 
@@
 
-\(h\) is well defined since \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) is a partition of  \([\![1, p a + b]\!]\). 
-We now prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) such that \(x \neq y\), 
-\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Distinguish between six cases 
+Function \(h\) is well defined since \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) is a partition of  \([\![1, p a + b]\!]\). 
+We now prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) be such that \(x \neq y\), 
+\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Nine cases are to be distinguished 
 according to the subsets \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) to which \(x\) and \(y\) belong. It is 
@@
 
-\subsection{Inequalities and new lower bounds for Weak Schur numbers}
+\subsection{New lower bounds for Weak Schur numbers}
 
@@
 of the type \(WS(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
-\((a, b)\) (for the lexicographic order).
+\((a, b)\) (in the lexicographic order). As we will see, this way of computing lower bounds is not necessarily the best
+we can do. In the following, we give the strongest inequalities we have so far and further insight about how they were produced.
 
-\[
-\begin{array}{r r r r r}
-	WS(n + 1) & \geqslant & 4 S(n) & + & 2 \\
-	WS(n + 2) & \geqslant & 13 S(n) & + & 8 \\
-	WS(n + 3) & \geqslant & 42 S(n) & + & 24 \\
-	WS(n + 4) & \geqslant & 132 S(n) & + & 26 \\
-\end{array}
-\]
+\begin{align}
+	WS(n + 1) &\geqslant  4 S(n)  +  2 \label{WS(n+1)} \\
+	WS(n + 2) &\geqslant  13 S(n)  +  8 \label{WS(n+2)} \\
+	WS(n + 3) &\geqslant  42 S(n)  +  24 \label{WS(n+3)} \\
+	WS(n + 4) &\geqslant  132 S(n)  +  26 \label{WS(n+4)}
+\end{align}
 
-The first two inequalities were found by Rowley, they are detailed in \cite{RowleyWS}. The third inequality is optimal 
-and was found with a SAT solver. It uses the first sophistication explained in the previous subsection in order to add 
+\hyperref[WS(n+1)]{(\ref{WS(n+1)})} and \hyperref[WS(n+2)]{(\ref{WS(n+2)})} were already found by Rowley, they are detailed in \cite{RowleyWS}. \hyperref[WS(n+3)]{(\ref{WS(n+3)})} is optimal 
+and was found with a SAT solver. It uses the first sophistication explained in the \hyperref[ConstructionWSF]{Subsection 3.3} in order to add 
 the last number in the first color. The \hyperref[WSF-templates]{corresponding template} can be found in the appendix.
-As for the fourth inequality, it was obtained by combining an optimal SF-template with width 33 with a WSF-template with width 4.
+As for \hyperref[WS(n+4)]{(\ref{WS(n+4)})}, it was obtained by combining an optimal SF-template with width 33 with a WSF-template with width 4.
 The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
 It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of
-5 colors which start with a good \(\WS(4)\) partition and we assumed that the special color was the last by order of 
+five colors which start with a good \(\WS(4)\) partition and we assumed that the special color was the last by order of 
 appearance. However, this approach most likely prevents us from finding the best WSF-templates
@@
 
-Like in 3.3, we compute the lower bounds given by the previous inequalities for \( n \in [\![8,15]\!] \). The best lower bound
+Like in Subsection 2.3 \textbf{LABEL NECESSAIRE}, we compute the lower bounds given by \hyperref[WS(n+1)]{(\ref{WS(n+1)})}, 
+\hyperref[WS(n+2)]{(\ref{WS(n+2)})} and \hyperref[WS(n+3)]{(\ref{WS(n+3)})} for \( n \in [\![8,15]\!] \). The best lower bound
 for each integer is highlighted.
@@
 
+\begin{table}[H]
+\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
+\label{LowerBoundsWS}
 \[
@@
 \]
+\end{table}
 
@@
 
-With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using Rowley's inequality.
-Moreover, the third inequality gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
+With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using \hyperref[WS(n+1)]{(\ref{WS(n+1)})}.
+Moreover, \hyperref[WS(n+3]{(\ref{WS(n+3)})} gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
 
@@
 and Hanson's construction for sum-free partitions. We then  introduced WSF-templates and generalized this construction. This
-allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant difference
+allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant gap
 between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
-obtained with WSF-templates (including Rowley's two inequalities). In the next section, we try to analyze this phenomenon.
+obtained with WSF-templates (including \hyperref[WS(n+1)]{(\ref{WS(n+1)})} and \hyperref[WS(n+2]{(\ref{WS(n+2)})}).

### 2021-06-06 article/schur.tex
première modifs schur

@@
 \begin{definition}
-Let \((p,n) \in (\mathbb{N}^*)^2\). A SF-template with width \(p\) and \(n\) colors is defined as a partition of 
+Let \((p,n) \in (\mathbb{N}^*)^2\). A S-template with width \(p\) and \(n\) colors is defined as a partition of 
 \([\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) verifying
@@
 
-Here \(n\) is the "special" color: it has less constraints than the other colors. However, please note that \(n\) 
-is not necessarily the last color by order of appearance. \(SF\)-templates include Abbott and Hanson's construction \cite{AbbottHanson}
-as a special case.
+Here \(n\) is the "special" color: the numbers colored in the special color has less constraints than the other colors. However, please note that \(n\) 
+is not necessarily the last color by order of appearance.
 
 \begin{proposition}
-	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the maximal width of a SF-template with \(n\) colors. 
+	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer such that \( [\![1, S^+(n)]\!]\) is a S-template with \(n\) colors. 
 	\(S^+(n)\) is well defined and verifies
@@
 The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
-fact that a SF-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets. \\
+fact that a S-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets. \\
 \end{proof}
@@
 
-\subsection{Construction of Schur partitions using SF-templates}
+\subsection{Construction of Schur partitions using S-templates}
 
-\qquad Here we state the main result on SF-templates stated by Rowley in the context of Ramsey numbers. It consists 
-in the explicit construction of a sum-free partition using a SF-template and a sum-free partition.
+\qquad We start by reminding the explicite construction of a sum-free partition with the use of a S-template and another sum free partition.
+We apply this contruction stated by Rowley in the context of Ramsey numbers to the Schur numbers.
 
 \begin{theorem}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(q\) and \(n+1\) colors 
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
 	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there exists a partition of \([\![1,pq+m_{n+1}
-	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element in the special subset in the \(SF\)-template.
+	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
 \end{theorem}
@@
 \(q = 9\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott and 
-Hanson's construction and with a SF-template which is not included in Abbott and Hanson's construction. In both cases, 
+Hanson's construction and with a S-template which is not included in Abbott and Hanson's construction. In both cases, 
 the special color is grey.
@@
 \begin{tabular}{c c}
-	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
+	\textbf{Corresponding S-template} & \textbf{Corresponding sum-free partition} \\
 	\begin{NiceTabular}{|*{9}{c|}}[standard-cline,hlines]
@@
 
-In the general construction with SF-templates, the special color no longer necessarily contains consecutive 
+In the general construction with S-templates, the special color no longer necessarily contains consecutive 
 numbers. However, the special color is still replaced by the colors of the sum-free partition according to the 
@@
 
-\textbf{SF-template construction}
+\textbf{S-template construction}
 \vspace{1.7ex}
@@
 \begin{proof}[\textsc{Proof.}]
-	Denote by \(f\) the coloring associated to the \(SF\)-template with width \(q\) and \(g\) the one associated 
+	Denote by \(f\) the coloring associated to the \(S\)-template with width \(q\) and \(g\) the one associated 
 	to the sum-free partition of \([\![1,p]\!]\); where \(f : [\![1,q]\!] \longrightarrow [\![1,n+1]\!]\) and 
@@
 
-	The additionnal constraint for the SF-template is:
+	The additionnal constraint for the S-template is:
 	\[
@@
 
-	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), write \(x = (\alpha - 1) + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
-	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\) (resp. \(u\)) can be interpreted as the row 
-	(resp. column) number of \(x\). A new coloring \(h\) is defined as follows:
+	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
+	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\)  can be interpreted as the row number of \(x\) and \(u\) as the collumn number of \(x\). A new coloring is define as follows:
 	\[
@@
 
-The following proposition may improve the additive constant of a SF-template. Although it does not allow us to 
-improve the SF-templates we have found, the analogous of this proposition for WSF-templates (see next section) 
-allows us to improve one of them.
+The following proposition may improve the additive constant of a S-template.
 
 \begin{proposition}
-Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a SF-template with width \(q\) and \(n+1\) 
+Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a S-template with width \(q\) and \(n+1\) 
 colors. Let \(b \in \mathbb{N}\) and assume there is a coloring \(g\) of 
@@
 
-There is a construction theorem for SF-templates as well.
+There is a construction theorem for S-templates as well.
 
 \begin{theorem}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is a SF-template with width \(q\) and \(n+1\) colors,
-	and a SF-template with width \(p\) and \(k\) colors, then there also is a SF-template with width \(pq\) and \((n+k)\) 
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is a S-template with width \(q\) and \(n+1\) colors,
+	and a S-template with width \(p\) and \(k\) colors, then there also is a S-template with width \(pq\) and \((n+k)\) 
 	colors.
@@
 
-	The inequality associated with this theorme is given by:
+	The inequality associated with this theorem is given by:
 
@@
 \begin{proof}[\textsc{Proof.}]
-The idea is the same as in the previous theorem. The only difference is the SF-template property inherited 
-from the second SF-template. \\
+The idea is the same as in the previous theorem. The only difference is the S-template property inherited 
+from the second S-template. \\
 \end{proof}
@@
 
-A SF-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
+A S-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
 from this template by applying the extension procedure with a sum-free partition of length 1 is symmetric. 
@@
 
-We produced SF-templates using a SAT solver, hence providing lower bound on \(S^+\) and inequalities 
+We produced S-templates using a SAT solver, hence providing lower bound on \(S^+\) and inequalities 
 of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing the largest value of 
 \((a, b)\) (in the lexicographic order). When the number of colors excceeded five, in order to reduce the search space we 
-only looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
+only looked for symmetric S-templates, we assumed that the special color was the last color to appear and we constrained 
 the \(m_c\)'s out of being too small. Further details about the encoding as a SAT problem can be found in \cite{Heule2017}.
@@
 \par
-Here are the best inequalities on Schur numbers so far (the \hyperref[SF-templates]{templates} corresponding to 
+Here are the best inequalities on Schur numbers so far (the \hyperref[S-templates]{templates} corresponding to 
 the third, fourth and fifth inequalities can be found in the appendix).
@@
 \par
-The first three inequalities are optimal. The fourth one is optimal among symmetric SF-templates whose special color is 
+The first three inequalities are optimal. The fourth one is optimal among symmetric S-templates whose special color is 
 the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
 likely not optimal but should not be too far from the optimum. 
-Finally, the sixth one is obtained by combining a SF-template with width 380 and one with width 3. 
-Although we could not find a better SF-template with seven colors, the last inequality is definitely very far from the 
+Finally, the sixth one is obtained by combining a S-template with width 380 and one with width 3. 
+Although we could not find a better S-template with seven colors, the last inequality is definitely very far from the 
 optimal value. One may try to seek better templates by constraining less the search space and by using 
@@
 
-\subsection{Conclusion on SF-templates}
+\subsection{Conclusion on S-templates}
 
 \qquad In this section, we first formalized Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur numbers 
-by introducing SF-templates as well as a new sequence, \(S^+\). We provided relations between \(S^+\) and \(S\) then 
-stated Rowley's construction method in the context of Schur numbers. We found new SF-templates allowing us to obtain 
+by introducing S-templates as well as a new sequence, \(S^+\). We provided relations between \(S^+\) and \(S\) then 
+stated Rowley's construction method in the context of Schur numbers. We found new S-templates allowing us to obtain 
 new lower bounds for schur numbers. One may notice that we mostly gave only lower bounds for \(S^+\). It should be possible to 
-find better SF-templates by making different assumptions or using a different method (Monte-Carlo methods for instance).
+find better S-templates by making different assumptions or using a different method (Monte-Carlo methods for instance).
 
 \par
-In the next section, we provide similar results for weak Schur numbers. We introduce WSF-templates and a corresponding sequence, 
+In the next section, we provide similar results for weak Schur numbers. We introduce WS-templates and a corresponding sequence, 
 \(\WS^+\). We then derive similar relations and a construction method allowing us to find new lower bounds for weak Schur numbers.

### 2021-06-06 article/schur.tex
corrections partie schur

@@
 \subsection{Definition of \(S^+\)}
+
+We define \(S^+\) to reduce the constraints of Abbott and Hanson's construction to improve this construction.
 
@@
 \begin{theorem}
+\label{Theorem2.4}
 	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
@@
 \begin{corollary}
+\label{Corollary2.5}
 	Let \(n, k \in \mathbb{N}^*\). Then
@@
 
-We now proceed to prove the above mentioned theorem.
+We now proceed to prove \hyperref[Theorem2.4]{Theorem 2.4}
 
@@
 
-The following proposition may improve the additive constant of a S-template.
+The following proposition may improve the additive constant of \hyperref[Corollary2.5]{Corollary 2.5}
 
@@
 \end{proposition}
-
-This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but 
-adding this column to the color would create sums in the color when applying the extension procedure. However, the 
-last row does not intereact with the right-most columns when it comes to creating new sums. As a result, the hypotheses 
-made on the coloring of the last row can be weakened.
+This proposition corresponds to the fact that the hypotheses made on the coloring of the last row can be weakened and as a result, we can change the coloring on the last row to extend the previous partitions.
+\newline
 
@@
 \begin{proof}[\textsc{Proof.}]
-The idea is the same as in the previous theorem. The only difference is the S-template property inherited 
+The idea is the same as in the \hyperref[Theorem2.4]{Theorem 2.4}. The only difference is the S-template property inherited 
 from the second S-template. \\
@@
 
-\subsection{Inequalities and new lower bounds for Schur numbers}
+\subsection{New lower bounds for Schur numbers}
+In the following, we give the strongest inequalities we have so far and further insight about how they were produced.
 
@@
 the third, fourth and fifth inequalities can be found in the appendix).
-\[
-\begin{array}{r r r r r}
-	S(n + 1) & \geqslant & 3 S(n) & + & 1 \\
-	S(n + 2) & \geqslant & 9 S(n) & + & 4 \\
-	S(n + 3) & \geqslant & 33 S(n) & + & 6 \\
-	S(n + 4) & \geqslant & 111 S(n) & + & 43 \\
-	S(n + 5) & \geqslant & 380 S(n) & + & 148 \\
-	S(n + 6) & \geqslant & 1\,140 S(n) & + & 528 \\
-\end{array}
-\]
 
-The first inequality comes from  Schur's original article\cite{Schur1917}. The second one is due to
+\begin{align}
+	S(n + 1) \geqslant  3 S(n)  + 1 \label{S(n+1)}\\
+	S(n + 2) \geqslant  9 S(n)  + 4 \label{S(n+2)}\\
+	S(n + 3) \geqslant  33 S(n) + 6 \label{S(n+3)}\\
+	S(n + 4) \geqslant  111 S(n) + 43 \label{S(n+4)}\\
+	S(n + 5) \geqslant  380 S(n) + 148 \label{S(n+5)}\\
+	S(n + 6) \geqslant 1\,140 S(n) + 528 \label{S(n+6)}
+\end{align}
+
+\hyperref[S(n+1)]{(\ref{S(n+1)})} comes from  Schur's original article\cite{Schur1917}. \hyperref[S(n+2)]{(\ref{S(n+2)})} is due to
 Abott \cite{AbbottHanson}
-and the third one to Rowley \cite{RowleyRamsey}. The three last inequalies are our result.
+and \hyperref[S(n+3)]{(\ref{S(n+3)})} to Rowley \cite{RowleyRamsey}. \hyperref[S(n+4)]{(\ref{S(n+4)})}, \hyperref[S(n+5)]{(\ref{S(n+5)})} and \hyperref[S(n+6)]{(\ref{S(n+6)})} are our result.
 
 \par
-The first three inequalities are optimal. The fourth one is optimal among symmetric S-templates whose special color is 
-the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
+\hyperref[S(n+1)]{(\ref{S(n+1)})}, \hyperref[S(n+2)]{(\ref{S(n+2)})} and \hyperref[S(n+3)]{(\ref{S(n+3)})} are optimal.
+\hyperref[S(n+4)]{(\ref{S(n+4)})} is optimal among symmetric S-templates whose special color is
+the last in the order of apparition (and with a multiplicative factor less than or equal to 118). \hyperref[S(n+5)]{(\ref{S(n+5)})} is most 
 likely not optimal but should not be too far from the optimum. 
-Finally, the sixth one is obtained by combining a S-template with width 380 and one with width 3. 
-Although we could not find a better S-template with seven colors, the last inequality is definitely very far from the 
+Finally, \hyperref[S(n+6)]{(\ref{S(n+6)})} is obtained by combining a S-template with width 380 and one with width three. 
+Although we could not find a better S-template with seven colors, \hyperref[S(n+6)]{(\ref{S(n+6)})} is definitely very far from the 
 optimal value. One may try to seek better templates by constraining less the search space and by using 
@@
 		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
-		1\,140 \, S(n-6) + 528 & 5\,088 & 15\,348 & 50\,688 & 182\,928 \\
 	\end{NiceArray}
@@
 		380 \, S(n-5) + 148 & 638\,548 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
-		1\,140 \, S(n-6) + 528 & 611\,568 & 1\,915\,728 & 6\,026\,568 & 20\,295\,948 \\
 	\end{NiceArray}
@@
 \]
-
+\end{table}
 \resetarraystretch

### 2021-06-07 article/schur.tex
Phrase intro

@@
 
-We define \(S^+\) to reduce the constraints of Abbott and Hanson's construction to improve this construction.
+We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
+of Figure 1 not as a combination of two blocs anymore but as a whole, single construction. We thereby define a S-template as
+a new object filling the role of the first line but with less, yet sufficiant, constraints that will allow the expansion of the
+table.
 

### 2021-06-07 article/article.tex
Deuxième série de corrections - partie WS (dans le bon dossier)
environnements figure

@@
 \usepackage{siunitx}
+\usepackage{float}
 
@@
 
-\par
-The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak 
-Schur numbers. The assumption behind it might have removed the optimal partitions from the search space and thus 
-lowered the highest value that can be reached within it. However, the methods used to explore this search space 
-are efficient as the optimum was found. Thereby Monte-Carlo algorithms may prove to be very useful if used in a 
-search space with more potential. Finding a weakly sum-free partition which is better than previous lower bounds 
-and which is not as regular as those obtained with templates would be extremely interesting (even if it does not 
-improve current lower bounds) since it could suggest a new search space which could then be explored with the 
-above mentioned methods.
-
 \section{Acknowledgments}

### 2021-06-07 article/schur.tex
environnements figure

@@
 \renewcommand{\arraystretch}{1.7}
-
+\begin{figure}[H]
 \begin{center}
@@
 \setlength{\tabcolsep}{6pt}
+\caption{Visualisation of an Abbott and Hanson construction}
 \end{center}
-
+\label{figure:1}
+\end{figure}
 In the general construction with S-templates, the special color no longer necessarily contains consecutive 
@@
 
+\begin{figure}[H]
 \begin{center}
+\textbf{S-template construction}
 \setlength{\tabcolsep}{1.5ex}
 
-\textbf{S-template construction}
 \vspace{1.7ex}
@@
 \setlength{\tabcolsep}{6pt}
+\caption{Visualisation of a template-based construction}
+\label{figure:2}
+
 \end{center}
+\end{figure}
 
@@
 \begin{table}[H]
-\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
+
 \label{LowerBoundsWS}
@@
 \]
+\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
 \end{table}

### 2021-06-12 article/article.tex
modifs

@@
 This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
-continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. Finding templates allows us to 
-get explicit partitions improving lower bounds as well as the growth rate for both Schur numbers and Ramsey 
-numbers \(R_n(3)\). We also developed a method to improve lower bounds for weak Schur numbers. 
-Furthermore, we try to analyze former works on weak Schur numbers based on the principle that \textit{good} 
-partitions into \(n+1\) weakly sum-free subsets start with a \textit{good} partition into \(n\) weakly sum-free subsets. 
-We show that exceeding the previous lower bound \(\WS (6) \geqslant 582\) is impossible with such an assumption 
-upon imposing certain conditions on the \textit{good} 5-subsets partitions. The new lower bounds include 
-\(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS (9) \geqslant 22\,536\) and 
+continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. We also generalized the concept 
+of "template" to weak Schur numbers. Finding new templates allows us to get explicit partitions improving lower bounds 
+as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). The new lower 
+bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS (9) \geqslant 22\,536\) and 
 \(\WS (10) \geqslant 71\,214 \).

### 2021-06-12 article/introduction.tex
modifs

@@
 
-\qquad Before Rowley's "template"-based approach for Schur and Ramsey numbers \cite{RowleyRamsey}, the 
-previous generic construction for Schur numbers was given by Abbott and Hanson \cite{AbbottHanson} in 1972 
-with a recursive construction. It used to give the best lower bounds for all sufficiently large numbers. No equivalent 
-was known for weak Schur numbers and as a result the best known partitions for large weak Schur numbers 
-did not use the weakly sum-free hypothesis.
+\qquad Up to recently, the most efficient generic construction for Schur numbers was given by Abbott and Hanson 
+\cite{AbbottHanson} in 1972 with a recursive construction. It gave the best lower bounds for all sufficiently large 
+numbers. No equivalent was known for weak Schur numbers and as a result the best known partitions for large 
+weak Schur numbers did not use the weakly sum-free hypothesis.
 
@@
 \cite{EliahouBook}, Bouzy \cite{Bouzy2015AnAP} and Rafilipojaona \cite{Rafilipojaona} improved the lower 
-bounds with Monte-Carlo methods. This was the main approach during the past decade. This search for weakly 
-sum-free partitions relied on the recursive assumption that a good weakly sum-free partition into \(n+1\) subsets 
-starts with a good weakly sum-free partition into \(n\) subsets.
+bounds with Monte-Carlo methods. This was the main approach during the past decade.
 
@@
 He also provides two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
-over previous lower bounds, and besides do utilize the \textit{weakly} sum-free hypothesis.
+over previous lower bounds. Besides, these two inequalities do use the \textit{weakly} sum-free hypothesis.
 
@@
 
-\begin{table}
+\begin{table}[H]
   \centering
@@
 \end{tabular}
-
-\vspace{1.5ex}
-* denotes the exact value
 \caption{Comparison of lower bounds for weak Schur numbers}
@@
 
+\begin{center}
+* denotes the exact value
+\end{center}
+
 \subsection{Structure of this article}
 
-\qquad Our main contribution is a generalization of the concept of template to weak Schur numbers. 
-Our templates provide new lower bounds (and inequalities) for weak Schur numbers. This construction also includes, 
-as a special case, a construction similar to Abbott and Hanson's \cite{AbbottHanson}, but this time with 
-\textit{weak} Schur numbers.
+\qquad Our main contribution is a generalization of the concept of template to weak Schur numbers. Our templates 
+provide new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special case 
+a construction similar to Abbott and Hanson's \cite{AbbottHanson}, but this time for \textit{weak} Schur numbers.
 
 \par
-In the \hyperref[Schur]{section 2}, we explain Rowley's template-based construction in the context of 
+In \hyperref[Schur]{section 2}, we explain Rowley's template-based construction in the context of 
 Schur numbers. Then, we give new templates, thus providing new lowers bounds and inequalities as well as 
@@
 \par
-Then, in the \hyperref[WeakSchur]{section 3}, we generalize the concept of templates to weak Schur numbers 
+In \hyperref[WeakSchur]{section 3}, we generalize the concept of templates to weak Schur numbers 
 and provide new lower bounds for weak Schur numbers.
@@
 \begin{definition}
-Let \(n \in \mathbb{N}^*\). There exists a greatest integer denoted by \(S(n)\) (\textit{resp. \(\WS (n)\)}) such that
-\([\![1,S(n)]\!]\) (resp. \([\![1, \WS (n)]\!]\)) can be partitioned into \(n\) sum-free subsets (resp. weakly sum-free
-subsets). \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number} and \textit{\(\WS (n)\) the
-\(n\)\textsuperscript{th} weak Schur number}.
+Let \(n \in \mathbb{N}^*\). There exists a largest integer denoted by \(S(n)\) such that \([\![1, S(n)]\!]\) can be
+ partitioned into \(n\) sum-free subsets. \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number}.
+\end{definition}
+
+\begin{definition}
+Let \(n \in \mathbb{N}^*\). There exists a largest integer denoted by \(\WS (n)\) such that \([\![1, \WS (n)]\!]\)) 
+can be partitioned into \(n\) weakly sum-free subsets. \(\WS(n)\) is called the \(n\)\textsuperscript{th} weak Schur 
+number.
 \end{definition}

### 2021-06-12 article/schur.tex
modifs

@@
 \begin{align}
-	S(n + 1) \geqslant  3 S(n)  + 1 \label{S(n+1)}\\
-	S(n + 2) \geqslant  9 S(n)  + 4 \label{S(n+2)}\\
-	S(n + 3) \geqslant  33 S(n) + 6 \label{S(n+3)}\\
-	S(n + 4) \geqslant  111 S(n) + 43 \label{S(n+4)}\\
-	S(n + 5) \geqslant  380 S(n) + 148 \label{S(n+5)}\\
-	S(n + 6) \geqslant 1\,140 S(n) + 528 \label{S(n+6)}
+	S(n + 1) \geqslant &~3\,S(n)  + 1 \label{S(n+1)}\\
+	S(n + 2) \geqslant &~9\,S(n)  + 4 \label{S(n+2)}\\
+	S(n + 3) \geqslant &~33\,S(n) + 6 \label{S(n+3)}\\
+	S(n + 4) \geqslant &~111\,S(n) + 43 \label{S(n+4)}\\
+	S(n + 5) \geqslant &~380\,S(n) + 148 \label{S(n+5)}\\
+	S(n + 6) \geqslant &~1\,140\,S(n) + 528 \label{S(n+6)}
 \end{align}
 
-\hyperref[S(n+1)]{(\ref{S(n+1)})} comes from  Schur's original article\cite{Schur1917}. \hyperref[S(n+2)]{(\ref{S(n+2)})} is due to
-Abott \cite{AbbottHanson}
-and \hyperref[S(n+3)]{(\ref{S(n+3)})} to Rowley \cite{RowleyRamsey}. \hyperref[S(n+4)]{(\ref{S(n+4)})}, \hyperref[S(n+5)]{(\ref{S(n+5)})} and \hyperref[S(n+6)]{(\ref{S(n+6)})} are our result.
+Inequality (\ref{S(n+1)}) comes from  Schur's original article\cite{Schur1917}. Inequality (\ref{S(n+2)}) is due to
+Abott and Hanson \cite{AbbottHanson} and inequality (\ref{S(n+3)}) to Rowley \cite{RowleyRamsey}. Inequalities 
+(\ref{S(n+4)}), (\ref{S(n+5)}) and (\ref{S(n+6)}) are our results.
 
 \par
-\hyperref[S(n+1)]{(\ref{S(n+1)})}, \hyperref[S(n+2)]{(\ref{S(n+2)})} and \hyperref[S(n+3)]{(\ref{S(n+3)})} are optimal.
-\hyperref[S(n+4)]{(\ref{S(n+4)})} is optimal among symmetric S-templates whose special color is
-the last in the order of apparition (and with a multiplicative factor less than or equal to 118). \hyperref[S(n+5)]{(\ref{S(n+5)})} is most 
-likely not optimal but should not be too far from the optimum. 
-Finally, \hyperref[S(n+6)]{(\ref{S(n+6)})} is obtained by combining a S-template with width 380 and one with width three. 
-Although we could not find a better S-template with seven colors, \hyperref[S(n+6)]{(\ref{S(n+6)})} is definitely very far from the 
-optimal value. One may try to seek better templates by constraining less the search space and by using 
-Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the subject of a future work.
+Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}) and (\ref{S(n+3)}) are optimal. Inequality (\ref{S(n+4)}) is optimal 
+among symmetric S-templates whose special color is the last in the order of apparition (and with a multiplicative 
+factor less than or equal to 118). Inequality (\ref{S(n+5)}) is most likely not optimal but should not be too far 
+from the optimum. Finally, inequality (\ref{S(n+6)}) is obtained by combining a S-template with width 380 and 
+one with width three. Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) 
+is definitely very far from the optimal value. One may try to seek better templates by constraining less the search 
+space and by using Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the subject of a future work.
 

### 2021-06-12 article/weakschur.tex
environnements figure
modifs

@@
 \begin{figure}[H]
-\caption{Construction of the weakly sum-free coloring}
+
 \label{SchemaWS}
@@
 \]
+\caption{Construction of the weakly sum-free coloring}
 \end{figure}
@@
 \(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
-calculative properties on \(\pi\) reflecting the behaviour of an element's column number in \hyperref[SchemaWS]{Figure \ref{SchemaWS}} and
+calculative properties on \(\pi\) reflecting the behaviour of an element's column number in Figure \ref{SchemaWS} and
 that we will use later when we introduce WSF-templates.
@@
 
-After defining the function related to the column number of each element in \hyperref[SchemaWS]{Figure \ref{SchemaWS}},
+After defining the function related to the column number of each element in Figure \ref{SchemaWS},
 we introduce the function related to its line number.
@@
 Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WSF-template with width \(p\) and \(k\) colors. Let
-\(c \in \mathbb{N}\) (\(c = \min (A_{k+1} \backslash [\![1, b ]\!]) - 1\) works) and assume there there exists a coloring \(g\) of
-\([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),
+\(c \in \mathbb{N}\) and assume there there exists a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),
 
@@
 Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\) . If there exists a SF-template with width 
-\(p\) and \(k+1\) colors and a \(b\)-WSF-template with width \(a\) and \(n\) colors, then there exists \(pb\)-WSF-template 
+\(p\) and \(k+1\) colors and a \(b\)-WSF-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WSF-template 
 with width \(pq\) and \((n+k)\) colors.
@@
 \begin{align}
-	WS(n + 1) &\geqslant  4 S(n)  +  2 \label{WS(n+1)} \\
-	WS(n + 2) &\geqslant  13 S(n)  +  8 \label{WS(n+2)} \\
-	WS(n + 3) &\geqslant  42 S(n)  +  24 \label{WS(n+3)} \\
-	WS(n + 4) &\geqslant  132 S(n)  +  26 \label{WS(n+4)}
+	WS(n + 1) &\geqslant  4\,S(n)  +  2 \label{WS(n+1)} \\
+	WS(n + 2) &\geqslant  13\,S(n)  +  8 \label{WS(n+2)} \\
+	WS(n + 3) &\geqslant  42\,S(n)  +  24 \label{WS(n+3)} \\
+	WS(n + 4) &\geqslant  132\,S(n)  +  26 \label{WS(n+4)}
 \end{align}
 
-\hyperref[WS(n+1)]{(\ref{WS(n+1)})} and \hyperref[WS(n+2)]{(\ref{WS(n+2)})} were already found by Rowley, they are detailed in \cite{RowleyWS}. \hyperref[WS(n+3)]{(\ref{WS(n+3)})} is optimal 
+(\ref{WS(n+1)}) and (\ref{WS(n+2)}) were already found by Rowley, they are detailed in \cite{RowleyWS}. (\ref{WS(n+3)}) is optimal 
 and was found with a SAT solver. It uses the first sophistication explained in the \hyperref[ConstructionWSF]{Subsection 3.3} in order to add 
 the last number in the first color. The \hyperref[WSF-templates]{corresponding template} can be found in the appendix.
-As for \hyperref[WS(n+4)]{(\ref{WS(n+4)})}, it was obtained by combining an optimal SF-template with width 33 with a WSF-template with width 4.
+As for (\ref{WS(n+4)}), it was obtained by combining an optimal SF-template with width 33 with a WSF-template with width 4.
 The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
@@
 
-Like in Subsection 2.3 \textbf{LABEL NECESSAIRE}, we compute the lower bounds given by \hyperref[WS(n+1)]{(\ref{WS(n+1)})}, 
-\hyperref[WS(n+2)]{(\ref{WS(n+2)})} and \hyperref[WS(n+3)]{(\ref{WS(n+3)})} for \( n \in [\![8,15]\!] \). The best lower bound
+Like in Subsection 2.3 \textbf{LABEL NECESSAIRE}, we compute the lower bounds given by (\ref{WS(n+1)}), 
+(\ref{WS(n+2)}) and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound
 for each integer is highlighted.
@@
 
-With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using \hyperref[WS(n+1)]{(\ref{WS(n+1)})}.
-Moreover, \hyperref[WS(n+3]{(\ref{WS(n+3)})} gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
+With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using (\ref{WS(n+1)}).
+Moreover, (\ref{WS(n+3)}) gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
 
@@
 between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
-obtained with WSF-templates (including \hyperref[WS(n+1)]{(\ref{WS(n+1)})} and \hyperref[WS(n+2]{(\ref{WS(n+2)})}).
+obtained with WSF-templates (including (\ref{WS(n+1)}) and (\ref{WS(n+2)}).

### 2021-06-12 article/appendix.tex
relecture (pas encore terminée partie weak schur)
preuve wsf templates
modifs

--- 2021-04-14 article/appendix.tex
@@
 \appendix
+
+\section{S-templates}
+\label{S-templates}
+
 \renewcommand{\arraystretch}{1}
+\vspace{-1.5ex}
 
-\section{SF-templates}
-
-\begin{center}
-SF-template partitionning \([\![1, 33]\!]\) into 4 subsets \\
-\begin{tabular}{|*{2}{c|}}
+\begin{table}[H]
+\[
+\begin{array}{|*{2}{c|}}
 	\hline
@@
 	\hline
-\end{tabular}
-\end{center}
+\end{array}
+\]
+\vspace{-3ex}
+\caption{S-template with width 33 and 4 colors}
+\vspace{-2ex}
+\end{table}
 
-\begin{center}
-SF-template partitionning \([\![1, 111]\!]\) into 5 subsets
-\begin{tabular}{|*{2}{c|}}
+\begin{table}[H]
+\[
+\begin{array}{|*{2}{c|}}
 	\hline
@@
 	\hline
-\end{tabular}
-\end{center}
+\end{array}
+\]
+\vspace{-3ex}
+\caption{S-template with width 111 and 5 colors}
+\vspace{-2ex}
+\end{table}
 
-\begin{center}
-SF-template partitionning \([\![1, 380]\!]\) into 6 subsets
-\begin{tabular}{|*{2}{c|}}
+\begin{table}[H]
+\[
+\begin{array}{|*{2}{c|}}
 	\hline
@@
 	\hline
+\end{array}
+\]
+\vspace{-3ex}
+\caption{S-template with width 380 and 6 colors}
+\vspace{-2ex}
+\end{table}
 
-\end{tabular}
-\end{center}
+\section{WS-templates}
+\label{WS-templates}
 
-\section{WSF-templates}
+\vspace{-1.5ex}
 
-\begin{center}
-WSF-template partitionning \([\![1, 42]\!]\) into 4 subsets
-\begin{tabular}{|*{2}{c|}}
+\begin{table}[H]
+\[
+\begin{array}{|*{2}{c|}}
 	\hline
-	1 & 1, 2, 4, 8, 11, 22, 25, \(\mathbf{(N+1)}\)\\
+	1 & 1, 2, 4, 8, 11, 22, 25, \mathbf{(N+1)}\\
 	\hline
@@
 	\hline
-\end{tabular}
-\end{center}
+\end{array}
+\]
+\vspace{-3ex}
+\caption{23-WS-template with width 42 and 4 colors}
+\vspace{-1ex}
+\end{table}
 
-This template provides the inequality \(\WS (n+3) \geqslant 42S(n) + 24\)
+This template provides the inequality \(\WS (n+3) \geqslant 42 \, S(n) + 24\)
 by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.
 
-\section{Proof of theorem j'arrive pas a afficher le numero du theoreme avec un lien}
-
-\textsc{Proof :} Let \((p,q), (n,k) \in (\mathbb{N}^*)^2\), \(N = p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q\),
-\(\alpha = \left \lceil \frac{q}{2} \right \rceil > 0\) and \(\beta = q + \alpha + 1\).
-We denote by \(f\) the colouring associated to the partition of \([\![1,q]\!]\) and \(g\) the
-one associated to the partition of \([\![1,p]\!]\).
-\[ f : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2, \left\{
-\begin{array}{ll}
-	x \neq y \\
-	f(x) = f(y)
-\end{array}
-\right.
-\Longrightarrow f(x+y) \neq f(x)
-\]
-\[g : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } f(x) = f(y)
-\Longrightarrow f(x+y) \neq f(x)
-\]
-Let us start by parting the integers of \([\![1,N]\!]\) in two subsets \(\mathcal{A}\) and \(\mathcal{B}\) where
-\(\mathcal{A} = [\![1,\alpha]\!] \cup \{a\beta + u \mid (a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\}\) and
-\(\mathcal{B} = \{a\beta + u \mid (a,u) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\}\).\\
-\\
-First, \underline{\(\mathcal{A} \cap \mathcal{B} = \varnothing\)} : \\
-By contradiction, suppose there exists \(x \in \mathcal{A} \cap \mathcal{B} \neq \varnothing \). Then there are \((a,u)
-\in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\) and \((b,v) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\) such that \(x
-= a\beta + u = b\beta +v\). By definition of \(\alpha\) and \(\beta\) we have \(u \in [\![\alpha + 1,q]\!] \subset
-[\![0,\beta - 1]\!]\).
-From there, we distinguish two cases :
-\begin{itemize}
-\item If \(v \in [\![0,\alpha]\!]\) then \(v \in [\![0,\beta - 1]\!]\) and \(v \neq u\) because \(v < \alpha + 1
-\leqslant u\)
-\item If \(v \in [\![-\alpha,-1]\!]\), we note \(\tilde{v} = \beta + v\) and thus have \(x = (b-1)\beta + \tilde{v}\)
-with \(\tilde{v} \in [\![\beta - \alpha,\beta - 1]\!] \subset [\![0,\beta - 1]\!]\) and \(\tilde{v} \neq u\) because
-\(u< q+1 = \beta - \alpha \leqslant \tilde{v}\).
-\end{itemize}
-In either cases, we run into a contradiction because of the remainder's uniqueness in the euclidean division of \(x\)
-by\(\beta\).\\
-\\
-Then, we have \underline{\(\mathcal{A} \cup \mathcal{B} = [\![1,N]\!]\)}:
-\begin{itemize}
-	\item On the one hand : \(1 = \text{min}(\mathcal{A}) \leqslant \text{max}(\mathcal{A}) = p\beta + q = N\) and
-\(1 \leqslant \beta - \alpha = \text{min}(\mathcal{B}) \leqslant \text{max}(\mathcal{B}) = p\beta + \alpha \leqslant
-N\),
-	which gives \(\mathcal{A} \cup \mathcal{B} \subset [\![1,N]\!]\).
-\item On the other hand, let \(x \in [\![1,N]\!]\). If \(x \leqslant \alpha\), we directly have \(x \in \mathcal{A}\),
-let us then suppose that \(x > \alpha\) and write \(x = a\beta + u\)
-the euclidean division of \(x\) by \(\beta\). We have \(x \leqslant N\), thus \(a \leqslant p\). We distinguish three
-cases : \\
-- If \(u \in [\![0,\alpha]\!]\) then we necessarily have \(a \geqslant 1\) because \(x > \alpha\), and so \(x \in
-\mathcal{B}\).\\
-	- If \(u \in [\![\alpha + 1,q]\!]\), then \(x \in \mathcal{A}\). \\
-- If \(u \in [\![q + 1,\beta - 1]\!]\) then \(x = (a+1)\beta - (\beta - u)\) with \(-\alpha \leqslant \beta - u
-\leqslant 0\).
-	Furthermore, \(a \leqslant p - 1\), else we would have \(x > N\), and so \(x \in \mathcal{B}\) \\
-In any case, \(x \in \mathcal{A} \cup \mathcal{B}\) and we can thus conclude that \([\![1,N]\!] \subset \mathcal{A}
-\cup\mathcal{B}\).
-\end{itemize}
-This first partition of \([\![1,N]\!]\) will help us to define our final partition by the projection of its equivalence
-relation.
-We thereby define \(h : [\![1,N]\!] \longrightarrow [\![1,n+k]\!]\) as such :\\
-- If \(x \in \mathcal{A}\) then \(h(x) = f(x \text{ mod } \beta)\) (well defined because \(x \text{ mod } \beta \in
-[\![1,N]\!]\))\\
-- If \(x \in \mathcal{B}\) then \(x = a\beta + u\) with a unique \((a,u) \in [\![1,p]\!] \times
-[\![-\alpha,\alpha]\!]\)and we define \(h(x) = n + g(a)\)\\
-The fact that \((\mathcal{A}, \mathcal{B})\) is a partition of \([\![1,N]\!]\) ensures that this definition of \(h\) is
-valid. We then have to verify that \(h\) induces weakly sum-free subsets.\\
-\\
-\underline{The classes of equivalence \(h(x)\) for \(x \in \mathcal{A}\) are weakly sum-free :}
-\\
-\\
-Let \((x,y) \in \mathcal{A}^2\) such that \(h(x) = h(y)\), \(x \neq y\) and \(x + y \leqslant N\)
-\begin{itemize}
-	\item If \((x,y) \in [\![1,\alpha]\!]^2\) :\\
-	We have \(x + y \leqslant 2\alpha \leqslant q\) and \(x + y = 0\beta + x + y\), therefore \(x + y \in \mathcal{A}\).
-Then, by definition : \(h(x) = f(x)\), \(h(y) = f(y)\) and \(h(x+y) = f(x+y)\), which gives us, thanks to the property
-verified by \(f\), that \(h(x+y) \neq h(x)\).
-	\item If \((x,y) \in [\![1,\alpha]\!] \times ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] )\) :\\
-We write \(y = a\beta + u\) with \((a,u) \in [\![0,p]\!] \times [\![\alpha + 1,q]\!]\). Then \(x+y = a\beta + x + u =
-(a+1)\beta + x + u - \beta\),
-and if \(x + u > q\) it follows that \(a \leqslant p-1\) since \(x+y \leqslant N\), and \(-\alpha \leqslant x + u -
-\beta \leqslant -1\).
-Therefore \(x+y \in \mathcal{B}\) and \(h(x+y) \neq h(x) = f(x)\) by definition of h. On the contrary, if \(x - u
-\leqslant n\),
-then \(x+y \in \mathcal{A}\) and \(h(x+y) = f(x+u)\) because \(x+u\) is actually the remainder of the euclidean
-divisionof \(x+y\) by \(\beta\).
-Moreover, \(h(x) = f(x)\), \(x < u\) and, with our initial hypothesis, \(h(x) = h(y) = f(u)\). The property verified by
-\(f\) gives us \(f(x+u) \neq f(x)\) which can be rewritten as \(h(x+y) \neq h(x)\).
-	\item If \((x,y) \in ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] ) \times [\![1,\alpha]\!]\) : \\
-	This case is handled exactly like the previous one by swaping the roles of \(x\) and \(y\).
-	\item If \((x,y) \in ( \mathcal{A} \text{ \textbackslash} ~ [\![1,\alpha]\!] )^2\) : \\
-We write \(x = a\beta + u\) and \(y = b\beta + v\) with \((a,u)\) and \((b,v)\) in \([\![0,p]\!] \times [\![\alpha +
-1,q]\!]\). Then \(x+y = (a+b)\beta + u+v = (a+b+1)\beta + u + v - \beta\)
-with \(a+b \leqslant p-1\) (else we would have \(x+y > N\) because \(u+v > q\)) and \(-\alpha \leqslant u + v - \beta
-\leqslant \alpha\), therefore \(x+y \in \mathcal{B}\) and by definition \(h(x+y) \neq h(x)\).
-\end{itemize}
-In any case, \(h(x+y) \neq h(x)\) and the classes of equivalence \(h(x)\) for \(x \in \mathcal{A}\) are weakly
-sum-free.\\
-\\
-\underline{The classes of equivalence \(h(x)\) for \(x \in \mathcal{B}\) are weakly sum-free :}
-\\
-\\
-Let \((x,y) \in \mathcal{B}^2\) such that \(h(x) = h(y)\), \(x \neq y\) and \(x + y \leqslant N\).\\
-We write \(x = a\beta + u\) and \(y = b\beta + v\) with \((a,u)\) and \((b,v)\) in \([\![1,p]\!] \times
-[\![-\alpha,\alpha]\!]\).
-We have \(h(x) = q + g(a)\) and \(h(y) = q + g(b)\), therefore \(g(a) = g(b)\). We also have \(x+y = (a+b)\beta + u
-+v\).\\
-If \(u + v \in [\![-\alpha,\alpha]\!]\), then \(x+y \in \mathcal{B}\) and \(h(x+y) = g(a+b)\), hence we can deduce that
-\(h(x+y) \neq h(x)\) because of the property verified by \(g\). On the contrary, if \(u+v \notin
-[\![-\alpha,\alpha]\!]\), then necessarily \(x+y \in \mathcal{A}\). Suppose \(x+y \in \mathcal{B}\), then \(x+y =
-c\beta+ w\) with \((c,w) \in [\![1,p]\!] \times [\![-\alpha,\alpha]\!]\). Thus, \(c\beta + w = (a+b)\beta + u + v\) and
-\((a+b-c)\beta = w-u-v\). Furthermore \(a+b-c \neq 0\), else we would have \(u+v = w \in [\![-\alpha,\alpha]\!]\). This
-finally leads to the following inequality :
-\[\beta \leqslant |a+b-c|\beta = |w-u-v| \leqslant |w| + |u| + |v| \leqslant 3\alpha \leqslant q + \alpha < \beta
-\]
-which is absurd. We can therefore conclude that \(x+y \in \mathcal{A}\) and by definition of \(h\), \(h(x+y) \neq
-h(x)\), proving that the classes of equivalence \(h(x)\) for \(x \in \mathcal{B}\) are weakly sum-free.\\
-\\
-Finally, we have showed that every classe of equivalence induced by \(h\) is weakly sum-free, which ends the proof.
+\resetarraystretch

### 2021-06-12 article/schur.tex
modifs

@@
 \qquad In this section, we use Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur 
-numbers. In order to improve lower bounds for Schur and Ramsey numbers, Rowley introduces special sum-free 
+numbers. In order to improve lower bounds for Schur and Ramsey numbers, he introduces special sum-free 
 partitions verifying some additional properties which can be extended using a method generalizing Abbott and 
-Hanson's construction \cite{AbbottHanson}. Rowley named these partitions "templates", and we keep this name in 
+Hanson's construction \cite{AbbottHanson}. He named these partitions "templates", and we keep this name in 
 the entire article. We then find new templates and use them to provide new lower bounds for Schur numbers.
@@
 Let \((p,n) \in (\mathbb{N}^*)^2\). A S-template with width \(p\) and \(n\) colors is defined as a partition of 
-\([\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) verifying
+\([\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) verifying for all subsets but \(A_n\)
 \[
@@
 
-Here \(n\) is the "special" color: the numbers colored in the special color has less constraints than the other colors. However, please note that \(n\) 
-is not necessarily the last color by order of appearance.
+Here \(n\) can be seen as a "special" color in the sense that we do not impose this above additionnal constraint on this color. 
+However, please note that \(n\) is not necessarily the last color by order of appearance.
 
@@
 	The sum-free condition is expressed as:
-	\[\forall (x,y) \in [\![1,q]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x)\],
-	\[\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x)\].
+	\[\forall (x,y) \in [\![1,q]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),\]
+	\[\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).\]
 
@@
 	\end{array}
-	\right. \Longrightarrow f(x+y-q) \neq f(x)
-	\].
+	\right. \Longrightarrow f(x+y-q) \neq f(x).
+	\]
 
@@
 
-The following proposition may improve the additive constant of \hyperref[Corollary2.5]{Corollary 2.5}
+The following proposition may improve the additive constant of \hyperref[Corollary2.5]{Corollary 2.5}.
 
 \begin{proposition}
+\label{Proposition2.6}
 Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a S-template with width \(q\) and \(n+1\) 
@@
 \subsection{New lower bounds for Schur numbers}
-In the following, we give the strongest inequalities we have so far and further insight about how they were produced.
+\label{Subsection2.3}
+We now give the inequalities correspondng to the current  best S-templates (to our knowledge).
 
@@
 only looked for symmetric S-templates, we assumed that the special color was the last color to appear and we constrained 
-the \(m_c\)'s out of being too small. Further details about the encoding as a SAT problem can be found in \cite{Heule2017}.
+the \(m_c\)'s out of being too small. Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.
 
 \par
-Here are the best inequalities on Schur numbers so far (the \hyperref[S-templates]{templates} corresponding to 
-the third, fourth and fifth inequalities can be found in the appendix).
+Here are the inequalities given by the current best S-templates (to our knowledge). The \hyperref[S-templates]{templates} 
+corresponding to the third, fourth and fifth inequalities can be found in the appendix.
 
@@
 \par
-Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}) and (\ref{S(n+3)}) are optimal. Inequality (\ref{S(n+4)}) is optimal 
-among symmetric S-templates whose special color is the last in the order of apparition (and with a multiplicative 
-factor less than or equal to 118). Inequality (\ref{S(n+5)}) is most likely not optimal but should not be too far 
-from the optimum. Finally, inequality (\ref{S(n+6)}) is obtained by combining a S-template with width 380 and 
-one with width three. Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) 
-is definitely very far from the optimal value. One may try to seek better templates by constraining less the search 
-space and by using Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the subject of a future work.
+Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}) and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
+Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
+last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
+likely be further improved but the improvement proabably will not be substantial. Finally, inequality (\ref{S(n+6)}) is obtained 
+by combining a S-template with width 380 and one with width three. Although we could not find a better S-template with seven 
+colors, inequality (\ref{S(n+6)}) can definitely be improved by a wide margin. One may try to seek better templates by 
+constraining less the search space and by using Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the subject 
+of a future work.
 
@@
 
-Except for 8, 9 and 13, the best lower bounds are obtained thanks to
-the third inequality \( S(n+5) \geqslant 380S(n) + 148\). The table
+Except for\(S(8)\), \(S(9)\) and \(S(13)\), the best lower bounds are obtained thanks to
+the third inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table
 doesn't go any further, but the same inequality allows to improve the

### 2021-06-12 article/weakschur.tex
modifs

@@
 for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
-we then introduce WSF-templates as well as an associated sequence \(\WS^+(n)\). We find templates and use them to
+we then introduce WS-templates as well as an associated sequence \(\WS^+(n)\). We find templates and use them to
 provide new lower bounds for weak Schur numbers.
@@
 templates for weak Schur numbers, we only give here an intuitive explanation of the demonstration; a formal
-\hyperref[proof_theorem]{proof} can be found in the appendix.
+\hyperref[PreuveThm]{proof} using templates for weak Schur numbers is provided.
 
@@
 
-Like SF-templates, \(\mathcal{R}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with
+Like S-templates, \(\mathcal{R}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with
 this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the
@@
 \par
-As in the previous section, we now introduce WSF-templates and the sequence \(\WS^+\) in order to generalize the above construction.
+As in the previous section, we now introduce WS-templates and the sequence \(\WS^+\) in order to generalize the above construction.
 
@@
 
-\qquad In this subsection, we introduce WSF-templates and prove calculative results for the general construction 
+\qquad In this subsection, we introduce WS-templates and prove calculative results for the general construction
 theorem on templates for weak Schur numbers.
@@
 calculative properties on \(\pi\) reflecting the behaviour of an element's column number in Figure \ref{SchemaWS} and
-that we will use later when we introduce WSF-templates.
+that we will use later when we introduce WS-templates.
 \end{sloppypar}
@@
 As we just did with \(\pi\), we proove three more results on both \(\pi\) and \(\lambda\) that will appear useful in
-\hyperref[ConstructionWSF]{Subsection 3.3}.
+\hyperref[ConstructionWS]{Subsection 3.3}.
 
@@
 
-\noindent  if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\) \\
-\vspace{1mm}
-\noindent if \(x \mod a \leqslant b\) then
-\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\) \\
+\begin{itemize}
+\item if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)
+\item if \(x \mod a \leqslant b\) then \(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\)
+\end{itemize}
 \end{proof}
@@
 Let \( (a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\). Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
-This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WSF-template) with width \(a\) and \(n\) colors when :
+This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WS-template) with width \(a\) and \(n\) colors when :
 
@@
 Please note that the special color \(n\) is not necessarily the last color by order of appearance.
-We now introduce the number \(\WS^+(n)\) that plays the same role as \(\S^+(n)\) for SF-templates.
-However, WSF-templates being more sophisticated than SF-templates, the definition of \(\WS^+(n)\)
+We now introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.
+However, WS-templates being more sophisticated than S-templates, the definition of \(\WS^+(n)\)
 is slighty more complicted.
@@
 \begin{definition}
-Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WSF-template with width \(a\) 
+Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WS-template with width \(a\)
 and \(n\) colors, we define :
 \[
-\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WSF-template with width } a \text{ and } n \text{ colors} \}.
+\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WS-template with width } a \text{ and } n \text{ colors} \}.
 \]
@@
 The lower bound comes from the analogous of Abott and Hanson's construction for weak Schur numbers.
-The upper bound comes from the fact that a WSF-template with width \(a\) and \(n\) colors contains a partition of
+The upper bound comes from the fact that a WS-template with width \(a\) and \(n\) colors contains a partition of
 \([\![1, a]\!]\) into \(n\) sum-free subsets. \\
@@
 
-\subsection{Construction of weak Schur partitions using WSF-templates}
-\label{ConstructionWSF}
+\subsection{Construction of weak Schur partitions using WS-templates}
+\label{ConstructionWS}
 
@@
 Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\)
-into \(k\) sum-free subsets and a \(b\)-WSF-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors, 
+into \(k\) sum-free subsets and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
 then there exists a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
@@
 \begin{remark}
-In the SF-template construction for Schur numbers, the additive constant comes from the fact that the special color does
+In the S-template construction for Schur numbers, the additive constant comes from the fact that the special color does
 not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by
@@
 Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Denote by \(f\) the coloring
-associated to the \(b\)-WSF-template  and \(g\) the one associated to the sum-free partition of \([\![1,p]\!]\); where 
+associated to the \(b\)-WS-template  and \(g\) the one associated to the sum-free partition of \([\![1,p]\!]\); where
 \({f : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({g : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, assume
@@
 \end{array}
-\right. \Longrightarrow f(x+y) \neq f(x)
+\right. \Longrightarrow f(x+y) \neq f(x),
 \end{equation}
@@
 
-The additionnal constraints for the WSF-template are:
+The additionnal constraints for the WS-template are:
 \begin{equation}
@@
 
-Here, we consider \(\pi\) defined in \hyperref[DefinitionWS+]{subsection 3.2} as an application defined on \([\![b + 1, p a + b]\!]\). 
-Split \([\![1, p a + b]\!]\) into three subsets.
+Split \([\![1, p a + b]\!]\) into three subsets. \\
+NB: To keep the notation short, the restriction to \([\![b + 1, p a + b]\!]\) of \(\pi\) defined in \hyperref[DefinitionWS+]{Subsection 3.2}
+is denoted by \(pi\) in the hereunder equations.
 
@@
 If \(x + y \leqslant b\) then \(h(x+y)=f(x+y)\). Otherwise, \(b < x+y < a+b\) since \(b < a\) and
-therefore \(\pi(x + y) = x +y\) (proposition \ref{prop1}). Hence in both cases \(h(x+y)=f(x+y)\). Given that 
+therefore \(\pi(x + y) = x +y\) (\hyperref[prop1]{Proposition 3.5}). Hence in both cases \(h(x+y)=f(x+y)\). Given that
 \(f\) is a weakly sum-free coloring, \(f(x + y) \neq f(x)\) since \(f(x)=h(x)=h(y)=f(y)\) and \(x \neq y \). That
@@
 \item \begin{sloppypar}
-	If \(x+\pi(y)> a+b\) then given that \(f\) is a WSF-template and since \({f(x) = f(\pi(y)) \leqslant n}\), 
+	If \(x+\pi(y)> a+b\) then given that \(f\) is a WS-template and since \({f(x) = f(\pi(y)) \leqslant n}\),
 	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (\hyperref[prop2]{Proposition 3.6}), such that
@@
 \item \begin{sloppypar}
-	If \(\pi(x)+\pi(y)>a+b\) then given that \(f\) is a WSF-template, \({f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x))}\) since 
+	If \(\pi(x)+\pi(y)>a+b\) then given that \(f\) is a WS-template, \({f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x))}\) since
 	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (\hyperref[prop4]{Proposition 3.8}). Hence \({f(\pi(x + y))
@@
 	Otherwise \(h(x+y) \leqslant n < h(x)\). In particular \(h(x + y) \neq h(x)\).
-\item If \(\pi(x)+\pi(y)>2a+b\) then \(f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x)) = n + 1\) since \(f\) is a \(b\)-WSF template and 
+\item If \(\pi(x)+\pi(y)>2a+b\) then \(f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x)) = n + 1\) since \(f\) is a \(b\)-WS template and
 	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (\hyperref[prop4]{Proposition 3.8}), \(f(\pi(x+y)) \neq n + 1\).
@@
 
-The general lower bound for weak Schur numbers in function of both regular and weak Schur numbers can be seen as a particular
-case of WSF-template in the same way Abott and Hanson's construction can be seen as a particular case of SF-template. Acutally,
-like for SF-templates, the additive constant of a WSF-template can be improved by weakening the hypotheses made on
-the last row. The principle behind it is the same as in the analogous proposition for SF-templates.
+There is a construction theorem for S-templates as well.
+
+\begin{theorem}
+\label{Theorem3.21}
+Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there exists a S-template with width
+\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WS-template
+with width \(pq\) and \((n+k)\) colors.
+\end{theorem}
+
+\hyperref[Theorem3.21]{Theorem 3.21} yields the following corollary.
+
+\begin{corollary}
+Let \(n, k \in \mathbb{N}^*\). Then
+\[
+\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n)
+\]
+\end{corollary}
+
+\begin{proof}[\textsc{Proof.}]
+The idea is the same as in the previous theorem. The only difference is the WS property inherited
+from the WS-template. \\
+\end{proof}
+
+\hyperref[Theorem3.1]{Theorem 3.1} can be seen as a particular case of WS-template in the same way Abott and Hanson's 
+construction can be seen as a particular case of S-template.
+
+\begin{proof}[\textsc{Proof of \hyperref[Theorem3.1]{Theorem 3.1}.}]
+\label{PreuveThm}
+\textbf{REFORMULER LA PREUVE EN TERMES DE WS-TEMPLATES.} \\
+\end{proof}
+
+As in \hyperref[Corollary2.5]{Corollary 2.5}, the additive constant \hyperref[Theorem3.18]{Theorem 3.18} can be improved 
+by weakening the hypotheses made on the last row. The principle behind it is the same as in \hyperref[Proposition2.6]{Proposition2.6}.
 
 \begin{proposition}
-Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WSF-template with width \(p\) and \(k\) colors. Let
+Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WS-template with width \(p\) and \(k\) colors. Let
 \(c \in \mathbb{N}\) and assume there there exists a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),
@@
 
-The WSF-templates can actually be fine-tuned further. However, it gives only minor improvements (most likely only an additive
+The WS-templates can actually be fine-tuned further. However, it only gives minor improvements (most likely only an additive
 constant) at the cost of dramatically increasing the size of the search space. Therefore, it does not seem relevant to
-use this sophistications given that we could not even find good WSF-templates with five colors using a computer (here good
+use this sophistications given that we could not even find good WS-templates with five colors using a computer (here good
 means better than those obtain by combining smaller templates).
@@
 \par
-To sum up, one can look for a generalised WSF-template that uses a special coloring for the tail and the first row, a
+To sum up, one can look for a generalised WS-template that uses a special coloring for the tail and the first row, a
 coloring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a coloring for all
 the other rows and a special coloring for the last numbers (as previously explained for the improvement of the additive
-constant of WSF-templates).
+constant of WS-templates).
 
@@
 
-\begin{theorem}
-\label{Theorem3.22}
-Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\) . If there exists a SF-template with width 
-\(p\) and \(k+1\) colors and a \(b\)-WSF-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WSF-template 
-with width \(pq\) and \((n+k)\) colors.
-\end{theorem}
-
-\hyperref[Theorem3.22]{Theorem 3.22} yields the following corollary.
-
-\begin{corollary}
-Let \(n, k \in \mathbb{N}^*\). Then
-\[
-\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n)
-\]
-\end{corollary}
-
-\begin{proof}[\textsc{Proof.}]
-The idea is the same as in the previous theorem. The only difference is the WSF property inherited
-from the WSF-template. \\
-\end{proof}
-
 \subsection{New lower bounds for Weak Schur numbers}
 
-\qquad We exhibited WSF-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities 
-of the type \(WS(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
-\((a, b)\) (in the lexicographic order). As we will see, this way of computing lower bounds is not necessarily the best
-we can do. In the following, we give the strongest inequalities we have so far and further insight about how they were produced.
+\qquad We produced WS-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities
+of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) (in the 
+lexicographic order). Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.
+
+\par
+Here are the inequalities given by the current best WS-templates (to our knowledge). The \hyperref[WS-templates]{templates} 
+corresponding to the third inequality can be found in the appendix.
 
@@
 
-(\ref{WS(n+1)}) and (\ref{WS(n+2)}) were already found by Rowley, they are detailed in \cite{RowleyWS}. (\ref{WS(n+3)}) is optimal 
-and was found with a SAT solver. It uses the first sophistication explained in the \hyperref[ConstructionWSF]{Subsection 3.3} in order to add 
-the last number in the first color. The \hyperref[WSF-templates]{corresponding template} can be found in the appendix.
-As for (\ref{WS(n+4)}), it was obtained by combining an optimal SF-template with width 33 with a WSF-template with width 4.
-The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
-It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of
-five colors which start with a good \(\WS(4)\) partition and we assumed that the special color was the last by order of 
-appearance. However, this approach most likely prevents us from finding the best WSF-templates
-as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates
-with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}.
-This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in \cite{Heule2017}.
+Inequalities (\ref{WS(n+1)}) and (\ref{WS(n+2)}) were found by Rowley, they are detailed in \cite{RowleyWS}. 
+Inequality (\ref{WS(n+3)}) is cannot be further improved and was found with a SAT solver. It uses the first 
+sophistication explained in the \hyperref[ConstructionWS]{Subsection 3.3} in order to add
+the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining a S-template with 
+width 33 with a WS-template with width 4. The best template we could find with a computer search gives the 
+inequality \(\WS(n+4) \geqslant 127 S(n) + 68\). It was also found with the SAT solver. In order to reduce the search space, 
+we only looked for WS-templates of five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
+special color was the last by order of appearance. We highly suspect that bettert WS-templates with \(n \geqslant 5\) 
+colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
+using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.
 
-Like in Subsection 2.3 \textbf{LABEL NECESSAIRE}, we compute the lower bounds given by (\ref{WS(n+1)}), 
-(\ref{WS(n+2)}) and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound
-for each integer is highlighted.
+Like in \hyperref[Subsection2.3]{Subsection 2.3}, we compute the lower bounds given by inequalities (\ref{WS(n+1)}),
+(\ref{WS(n+2)}) and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound for each value of \(n\) is highlighted.
 
@@
 With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using (\ref{WS(n+1)}).
-Moreover, (\ref{WS(n+3)}) gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
+Moreover, inequality (\ref{WS(n+3)}) gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
 
-\subsection{Conclusion on WSF-templates}
+\subsection{Conclusion on WS-templates}
 
 \qquad In this section, we first gave a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
-and Hanson's construction for sum-free partitions. We then  introduced WSF-templates and generalized this construction. This
+and Hanson's construction for sum-free partitions. We then  introduced WS-templates and generalized this construction. This
 allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant gap
 between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
-obtained with WSF-templates (including (\ref{WS(n+1)}) and (\ref{WS(n+2)}).
+obtained with WS-templates.

### 2021-06-12 article/schur.tex
qq typos + biblio

@@
 We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
-of Figure 1 not as a combination of two blocs anymore but as a whole, single construction. We thereby define a S-template as
+of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. We thereby define a S-template as
 a new object filling the role of the first line but with less, yet sufficiant, constraints that will allow the expansion of the
@@
 
-\qquad We start by reminding the explicite construction of a sum-free partition with the use of a S-template and another sum free partition.
+\qquad We start by reminding the explicit construction of a sum-free partition with the use of a S-template and another sum free partition.
 We apply this contruction stated by Rowley in the context of Ramsey numbers to the Schur numbers.
@@
 \label{Subsection2.3}
-We now give the inequalities correspondng to the current  best S-templates (to our knowledge).
+We now give the inequalities corresponding to the current  best S-templates (to our knowledge).
 
@@
 of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing the largest value of 
-\((a, b)\) (in the lexicographic order). When the number of colors excceeded five, in order to reduce the search space we 
+\((a, b)\) (in the lexicographic order). When the number of colors exceeded five, in order to reduce the search space we 
 only looked for symmetric S-templates, we assumed that the special color was the last color to appear and we constrained 
@@
 last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
-likely be further improved but the improvement proabably will not be substantial. Finally, inequality (\ref{S(n+6)}) is obtained 
+likely be further improved but the improvement probably will not be substantial. Finally, inequality (\ref{S(n+6)}) is obtained 
 by combining a S-template with width 380 and one with width three. Although we could not find a better S-template with seven 

### 2021-06-13 article/introduction.tex
modifs
valeurs exactes en couleur

@@
 number and is denoted \(S(n)\) \cite{Schur1917}. Likewise for weakly sum-free partitions we define \(\WS(n)\) 
-the \(n^{\text{th}}\) weak Schur number \cite{Irving1973}. Only the first values of these sequences are known. 
-In this study, we improve the lower bounds on these numbers.
+the \(n^{\text{th}}\) weak Schur number \cite{Irving1973}. Values of \(S(n)\) and \(\WS(n)\) are known for small \(n\) only.
 
@@
 
-\setlength{\tabcolsep}{4pt}
+\par The hereunder tables recap the lower bounds respectively for Schur and weak Schur numbers. Gray cells 
+indicate the exact values.
 
@@
   \centering
-\begin{tabular}{|*{13}{c|}}
+\begin{NiceTabular}{*{13}{c}}[vlines]
+\CodeBefore
+	\cellcolor{gray!40}{2-2}
+	\cellcolor{gray!40}{2-3}
+	\cellcolor{gray!40}{2-4}
+	\cellcolor{gray!40}{2-5}
+	\cellcolor{gray!40}{2-6}
+	\cellcolor{gray!40}{3-2}
+	\cellcolor{gray!40}{3-3}
+	\cellcolor{gray!40}{3-4}
+	\cellcolor{gray!40}{3-5}
+	\cellcolor{gray!40}{3-6}
+\Body
 	\hline
@@
 	\hline
-    \multirow{2}{*}{Before Rowley} & 1* & 4* & 13* & 44* & 160* & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
-      & & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{AbbottHanson} & 
-    \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
+	\Block{2-1}{Before Rowley} & 1 & 4 & 13 & 44 & 160 & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
+	& & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{AbbottHanson} & \cite{AbbottHanson} & 
+		\cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
 	\hline
-    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyRamsey}\end{tabular} & & & & & & & & 5\,286 & 17\,694 & 
-    60\,320 & 201\,696 & 631\,840 \\
+	Rowley & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & 
+		\Block{2-1}{5\,286} & \Block{2-1}{17\,694} & \Block{2-1}{60\,320} & \Block{2-1}{201\,696} & \Block{2-1}{631\,840} \\
+	\cite{RowleyRamsey} & & & & & & & & & & & & \\
 	\hline
@@
 	\hline
-\end{tabular}
+\end{NiceTabular}
 \caption{Comparison of lower bounds for Schur numbers}
@@
 \end{table}
-\vspace{2.5ex}
 
@@
   \centering
-\begin{tabular}{|*{13}{c|}}
+\begin{NiceTabular}{*{13}{c}}[vlines]
+\CodeBefore
+	\cellcolor{gray!40}{2-2}
+	\cellcolor{gray!40}{2-3}
+	\cellcolor{gray!40}{2-4}
+	\cellcolor{gray!40}{2-5}
+	\cellcolor{gray!40}{3-2}
+	\cellcolor{gray!40}{3-3}
+	\cellcolor{gray!40}{3-4}
+	\cellcolor{gray!40}{3-5}
+\Body
 	\hline
@@
 	\hline
-    \multirow{2}{*}{Before Rowley} & 2* & 8* & 23* & 66* & 196 & 582 & 1\,740 & 5\,201 & 15\,596 & 51\,520 & 172\,216 & 575\,664 \\
-      & & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
-    \cite{Rafilipojaona} & \cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
+	\Block{2-1}{Before Rowley} & 2 & 8 & 23 & 66 & 196 & 582 & 1\,740 & 5\,201 & 15\,596 & 51\,520 & 172\,216 & 575\,664 \\
+	& & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
+		\cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
 	\hline
-    \begin{tabular}{@{}c@{}}Rowley \\ \cite{RowleyWS}\end{tabular} & & & & & & 642 & 2\,146 & 6\,976 & 21\,848 
-    & 70\,778 & 241\,282 & 806\,786 \\
+	Rowley & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{642} & \Block{2-1}{2\,146} & 
+		\Block{2-1}{6\,976} & \Block{2-1}{21\,848} & \Block{2-1}{70\,778} & \Block{2-1}{241\,282} & \Block{2-1}{806\,786} \\
+	\cite{RowleyWS} & & & & & & & & & & & & \\
 	\hline
-    \hyperref[WeakSchur]{\textbf{Our results}} & & & & & & & & & \textbf{22\,536} & \textbf{71\,214} & \textbf{243\,794} & \textbf{815\,314} \\
+	\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{22\,536} & \textbf{71\,214} & \textbf{243\,794} & \textbf{815\,314} \\
 	\hline
-\end{tabular}
+\end{NiceTabular}
 \caption{Comparison of lower bounds for weak Schur numbers}
@@
 \end{table}
-
-\begin{center}
-* denotes the exact value
-\end{center}
 
@@
 \qquad We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers. 
+We denote \(\mathbb{N} = \{0, 1, 2, ...\}\) and \(\mathbb{N}^* =\mathbb{N} \backslash \{0\}\).
 

### 2021-06-13 article/weakschur.tex
valeurs exactes en couleur

@@
 
-\qquad In this section, we first gave a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
-and Hanson's construction for sum-free partitions. We then  introduced WS-templates and generalized this construction. This
+\qquad We started by giving a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
+and Hanson's construction for sum-free partitions. We then generalized this construction by introducing WS-templates. This
 allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant gap

### 2021-06-15 article/introduction.tex
majuscules + corrections

@@
 \par
-In \hyperref[Schur]{section 2}, we explain Rowley's template-based construction in the context of 
+In \hyperref[Schur]{Section 2}, we explain Rowley's template-based construction in the context of 
 Schur numbers. Then, we give new templates, thus providing new lowers bounds and inequalities as well as 
@@
 \par
-In \hyperref[WeakSchur]{section 3}, we generalize the concept of templates to weak Schur numbers 
+In \hyperref[WeakSchur]{Section 3}, we generalize the concept of templates to weak Schur numbers 
 and provide new lower bounds for weak Schur numbers.

### 2021-06-15 article/weakschur.tex
majuscules + corrections

@@
 \begin{figure}[H]
-
-\label{SchemaWS}
 \[
@@
 \]
+\label{SchemaWS}
 \caption{Construction of the weakly sum-free coloring}
@@
 
-If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\). Notice that for all
-\(x \in \mathbb{Z}, \pi(x) = x \mod a\) and for all \(x \in [\![b + 1, a + b]\!], b + 1 \leqslant \pi(x) \leqslant a + b\).
+\begin{sloppypar}
+If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\). Notice that for all \(x \in \mathbb{Z}\), 
+\({\pi(x) = x \mod a}\) and for all \(x \in [\![b + 1, a + b]\!], b + 1 \leqslant \pi(x) \leqslant a + b\).
+\end{sloppypar}
 
@@
 \(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
-calculative properties on \(\pi\) reflecting the behaviour of an element's column number in Figure \ref{SchemaWS} and
+calculative properties on \(\pi\) reflecting the behaviour of an element's column number in \hyperref[SchemaWS]{Figure 3} and
 that we will use later when we introduce WS-templates.
@@
 
-After defining the function related to the column number of each element in Figure \ref{SchemaWS},
+After defining the function related to the column number of each element in \hyperref[SchemaWS]{Figure 3},
 we introduce the function related to its line number.

### 2021-06-20 article/weakschur.tex
reformulation en terme de templates de la demo WS > 3/2 WS

@@
 The inequality from \hyperref[Corollary3.2]{Corollary 3.2} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
-odd in the theorem). However, it makes the proof less clear and it is never useful in practice.
+odd in the theorem). However, it lengthens the proof and it is never useful in practice.
 \end{remark}
@@
 	\[
-	\forall i \in [\![0,n-1]\!], \, \forall(x,y) \in A_i^2, \, x+y>a+b \implies \pi(x+y) \notin A_i.
+	\forall i \in [\![1,n-1]\!], \, \forall(x,y) \in A_i^2, \, x+y>a+b \implies \pi(x+y) \notin A_i.
 	\]
@@
 
-There is a construction theorem for S-templates as well.
+There is a construction theorem for WS-templates as well.
 
@@
 \label{PreuveThm}
-\textbf{REFORMULER LA PREUVE EN TERMES DE WS-TEMPLATES.} \\
+Let \((q, n) \in (\mathbb{N}^*)^2\) such that there exists a partition of \([\![1, q]\!]\) into n weakly sum-free subsets. 
+Let \(f: [\![1, q]\!] \rightarrow [\!]1, n]\!]\) a weakly sum-free colouring.
+Let \(b=q\) and \(a = q + \left \lceil \dfrac{q}{2} \right \rceil + 1\). A new colouring \(g\) is defined as follows:
+
+\[
+\begin{array}{c c c l}
+	g : & [\![1, a + b]\!] & \longrightarrow & [\![1, n + 1]\!] \\
+	& x & \longmapsto &
+		\left\{ \begin{array}{l l}
+			f(x) & \text{if}~x \in [\![1, b]\!]  \\
+			n + 1 & \text{if}~x \in [\![b + 1, 2 b + 1]\!] \\
+			f(x - a) & \text{if}~x \in  [\![2 b + 2, a + b]\!]
+		\end{array} \right.
+\end{array}
+\]
+
+We claim that \(g\) is a \(b\)-WSF-template with width \(a\) and \(n + 1\) colours.
+
+\begin{itemize}
+\item Function \(g_{|[\![b + 1, a + b]\!]}\) is a sum-free colouring. Indeed, let \((x, y) \in 
+	[\![b + 1, a + b]\!]^2\) such that \(g(x) = g(y)\). If \(g(x) = n + 1\) then \(z = x + y > 2 b + 1\) 
+	and therefore, either \(z > a + b\) or \(f(z) \neq n + 1\). Otherwise, \(x + y > a + b\).
+\item Function \(g\) is a weakly sum-free colouring. Indeed, let \((x, y) \in [\![1, a + b]\!]^2\) such that 
+	\(z = x + y \leqslant a + b\) and \(g(x) = g(y)\). Given that \(x\) and \(y\) have symmetric roles, 
+	we can assume that \(x \leqslant y\). If \(x > b\) then \(g(z) \neq g(x)\) as seen above. If \(y \leqslant b\) then 
+	\(f(x) = g(x) = g(y) = f(y) \leqslant n\) and either \(z \leqslant a + b\) and \(f(z) \neq f(x)\) since \(f\) is a weakly 
+	sun-free colouring or \(a + b + 1 \leqslant z \leqslant 2 b\) and \(g(z) = n + 1\); therefore \(g(z) \neq g(x)\). If 
+	\(x \leqslant b\) and \(y > b\) then \(g(x) = f(x)\), \(g(y) = f(y - a)\) and \(g(z) = f(z - a)\).We have \(x \neq y - a\) 
+	(otherwise, we would have \(a + b \geqslant z = 2 y  - a \geqslant 4 b + 4 - a > a + b\)) and thus \(f(x + y - a) \neq f(x)\),
+	that is \(g(z) \neq g(x)\).
+\item Colour \(n + 1\) verifies the additionnal constraints for the special colour. Indeed, \(b + 2 a \geqslant 4 b + 2\). 
+	Hence, \(\forall (x, y) \in g^{-1}(\{n + 1\}), x + y \leqslant b + 2 a\).
+\item Colours \(1, ..., n\) verify the additionnal constraints for the regular colours. Indeed, let 
+	\((x, y) \in g^{-1}([\![1, n]\!])\) such that \(x + y > a + b\). Given that \(x\) and \(y\) have symmetric roles, 
+	we can assume that \(x \leqslant y\). Necessarily \(y \geqslant 2 b + 2\). If \(x \leqslant b\) then 
+	\(z = x + y \in [\![a + b + 1, a + 2 b]\!]\) and therefore \(\pi(z) \in [\![b + 1, 2 b]\!]\). Otherwise, 
+	\(z = x + y \in [\![4 b + 4, 2 a + 2 b]\!]\) and therefore \(\pi(z) \in [\![b + 1, 2 b]\!]\). Hence, in both cases, 
+	\(g(\pi(z)) \neq g(x)\).
+\end{itemize}
+
+The result is then obtained by applying \hyperref[Theorem3.18]{Theorem 3.18}. \\
 \end{proof}

### 2021-06-25 article/weakschur.tex
Nouveau style biblio
2 typos (on se sent utile)

@@
 	\(f(x) = g(x) = g(y) = f(y) \leqslant n\) and either \(z \leqslant a + b\) and \(f(z) \neq f(x)\) since \(f\) is a weakly 
-	sun-free colouring or \(a + b + 1 \leqslant z \leqslant 2 b\) and \(g(z) = n + 1\); therefore \(g(z) \neq g(x)\). If 
+	sum-free colouring or \(a + b + 1 \leqslant z \leqslant 2 b\) and \(g(z) = n + 1\); therefore \(g(z) \neq g(x)\). If 
 	\(x \leqslant b\) and \(y > b\) then \(g(x) = f(x)\), \(g(y) = f(y - a)\) and \(g(z) = f(z - a)\).We have \(x \neq y - a\) 
@@
 As in \hyperref[Corollary2.5]{Corollary 2.5}, the additive constant \hyperref[Theorem3.18]{Theorem 3.18} can be improved 
-by weakening the hypotheses made on the last row. The principle behind it is the same as in \hyperref[Proposition2.6]{Proposition2.6}.
+by weakening the hypotheses made on the last row. The principle behind it is the same as in \hyperref[Proposition2.6]{Proposition 2.6}.
 
@@
 Inequalities (\ref{WS(n+1)}) and (\ref{WS(n+2)}) were found by Rowley, they are detailed in \cite{RowleyWS}. 
-Inequality (\ref{WS(n+3)}) is cannot be further improved and was found with a SAT solver. It uses the first 
+Inequality (\ref{WS(n+3)}) cannot be further improved and was found with a SAT solver. It uses the first 
 sophistication explained in the \hyperref[ConstructionWS]{Subsection 3.3} in order to add

### 2021-06-27 schur_5_extension/apply.sh
code ws 6

@@ -1,0 +1,8 @@
+#!/bin/sh
+CNF=$1
+CUBES=$2
+LINE=$3
+
+EXTRA=`head -n $LINE $CUBES | tail -n 1 | awk '{print NF-2}'`
+cat $CNF | awk '/ 0/ {print $0} /cnf/ {print "p cnf " $3 " " $4 + '$EXTRA'}'
+head -n $LINE $CUBES | tail -n 1 | sed 's|a ||' | sed 's|[-]*[0-9]* |&0X|g' | tr "X" "\n" | awk '{if (NF == 2) print $0}'

### 2021-06-27 schur_5_extension/compute_backdoors.py

@@ -1,0 +1,88 @@
+import subprocess
+import tqdm
+
+
+N_BACKDOORS = 1616
+SAT_SOLVER = ["./solvers/lingeling/lingeling", '-n']
+
+
+def generate_dimacs():
+    for i in tqdm.trange(1, N_BACKDOORS + 1):
+        cmd = ["./apply.sh", "Schur_160_5_SBP.cnf", "backdoors.cubes", str(i)]
+        result = subprocess.run(cmd, stdout=subprocess.PIPE)
+        dimacs = result.stdout.decode('utf-8')
+        filename = f"dimacs_files/Schur-5-{i}.cnf"
+        with open(filename, mode='w') as file:
+            file.write(dimacs)
+
+
+def get_fixed_dimacs(i):
+    filename = f'dimacs_files/Schur-5-{i}.cnf'
+    with open(filename) as dimacs:
+        n_clauses = int(dimacs.readline().split()[-1]) + 1
+        header = f"p cnf 800 {n_clauses}\n"
+        clauses = dimacs.readlines()
+    fixed_dimacs = header + ''.join(clauses)
+    return fixed_dimacs
+
+
+def is_solution(answer):
+    for line in answer.splitlines():
+        if line[0] != 's':
+            continue
+        return line[2] == 'S'
+    raise RuntimeError
+
+
+def compute_backdoor(fixed_dimacs):
+    backdoor = []
+    for a in range(160):
+        possibilities = []
+        for c in range(1, 6):
+            dimacs = fixed_dimacs + f"{5 * a + c} 0\n"
+            dimacs = dimacs.encode('utf-8')
+            result = subprocess.run(SAT_SOLVER, stdout=subprocess.PIPE,
+                                    input=dimacs)
+            if is_solution(result.stdout.decode('utf-8')):
+                possibilities.append(c)
+        backdoor.append(possibilities)
+    return backdoor
+
+
+def sort_colours(backdoor):
+    colours = [[] for _ in range(5)]
+    for a, possibilities in enumerate(backdoor):
+        for c in possibilities:
+            colours[c - 1].append(a)
+    colours.sort(key=min)
+    backdoor = [[] for _ in range(160)]
+    for c, colour in enumerate(colours):
+        for a in colour:
+            backdoor[a].append(c + 1)
+    backdoor = [' '.join(map(str, possibilities)) for possibilities in backdoor]
+    return backdoor
+
+
[…]

### 2021-06-27 schur_5_extension/decode_ws6.py

@@ -1,0 +1,73 @@
+import sys
+
+
+def build_mapping(n, lim):
+    mapping = {1: 1, 2: 2}
+    count = 2
+    for a in range(3, min(4 * lim + 3, n + 1)):
+        if a % 4 != 1:
+            count += 1
+        mapping[a] = count
+    for a in range(4 * lim + 3, n + 1):
+        count += 1
+        mapping[a] = count
+    return mapping, count
+
+
+def is_sum_free(s_raw):
+    s_list = list(s_raw)
+    s_set = set(s_raw)
+
+    for i, a in enumerate(s_list):
+        for j in range(i + 1, len(s_list)):
+            b = s_list[j]
+            if a + b in s_set:
+                print(a, b, a + b)
+                return False
+    return True
+
+
+def decode_answer(n, mapping, count):
+    is_var_line = lambda line: line[0] == 'v'
+    trim_line = lambda line: line[2:].rstrip('\n 0')
+
+    solution = filter(is_var_line, sys.stdin.readlines())
+    solution = map(trim_line, solution)
+    solution = " ".join(solution).split()
+    solution = map(int, solution)
+
+    assigned = set()
+    solu = {}
+    for x in solution:
+        if x <= 0:
+            continue
+        x -= 1
+        i, colour = divmod(x, 6)
+        number = i + 1
+        if number not in assigned:
+            assigned.add(number)
+            solu[number] = colour
+        else:
+            raise RuntimeError
+    assert assigned == set(range(1, count + 1))
+
+    partition = [[] for _ in range(6)]
+    for i in range(1, n + 1):
+        j = mapping[i]
+        partition[solu[j]].append(i)
+
+    assert all(map(is_sum_free, partition))
+    return partition
+
+
+def main():
+    n = int(sys.argv[1])
+    lim = int(sys.argv[2])
+    mapping, count = build_mapping(n, lim)
+    partition = decode_answer(n, mapping, count)
+    for col in partition:
+        print(*col)
+
+
+if __name__ == '__main__':
+    main()

### 2021-06-27 schur_5_extension/weak_schur_6.py

@@ -1,0 +1,108 @@
+import subprocess
+import sys
+import tqdm
+
+
+def build_mapping(n, lim):
+    mapping = {1: 1, 2: 2}
+    count = 2
+    for a in range(3, min(4 * lim + 3, n + 1)):
+        if a % 4 != 1:
+            count += 1
+        mapping[a] = count
+    for a in range(4 * lim + 3, n + 1):
+        count += 1
+        mapping[a] = count
+    return mapping, count
+
+
+def weakly_sum_free(n, mapping):
+    cnf = []
+    for c in range(6):
+        for i in range(1, n + 1):
+            for j in range(i + 1, n + 1):
+                tot = i + j
+                if tot > n:
+                    break
+                x = 6 * mapping[i]
+                y = 6 * mapping[j]
+                z = 6 * mapping[tot]
+                no_sum = f"-{x  - c} -{y - c} -{z - c}"
+                cnf.append(no_sum)
+    return cnf
+
+
+def use_all(count):
+    cnf = []
+    for i in range(count):
+        use_i = " ".join(map(str, range(6 * i + 1, 6 * (i + 1) + 1)))
+        cnf.append(use_i)
+    return cnf
+
+
+def disjoint(count):
+    cnf = []
+    for i in range(1, count + 1):
+        for c1 in range(6):
+            for c2 in range(c1 + 1, 6):
+                cnf.append(f"-{6 * i - c1} -{6 * i - c2}")
+    return cnf
+
+
+def apply_backdoor(mapping, lim, backdoor_num):
+    filename = f"backdoors/backdoor-{backdoor_num}"
+    cnf = ["1", "7"]
+    with open(filename) as file:
+        for a, possibilities in enumerate(file.readlines()[:lim]):
+            base_lit = mapping[4 * (a + 1)]
+            to_litterals = lambda c: str(6 * (base_lit - 1) + int(c) + 1)
+            clause = ' '.join(map(to_litterals, possibilities.split()))
+            cnf.append(clause)
+    return cnf
+
+
+def weak_schur_cnf(n, mapping, count, lim, backdoor):
+    cnf = weakly_sum_free(n, mapping)
+    cnf.extend(use_all(count))
+    cnf.extend(disjoint(count))
+    cnf.extend(apply_backdoor(mapping, lim, backdoor))
+    return cnf
+
+
[…]

### 2021-07-05 article/article.tex
Nouveau style biblio
ws 6

@@
 as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). The new lower 
-bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS (9) \geqslant 22\,536\) and 
+bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\) and 
 \(\WS (10) \geqslant 71\,214 \).
@@
 \qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
-us during the whole research and writing. Last but not least, we would like to address warm thanks
+us during the whole research and writing. We also would like to address warm thanks
 to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
+Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
+new lower bound for \(\WS(6)\).
 
 \bibliography{biblio}
-\bibliographystyle{IEEEtran}
+\bibliographystyle{elsarticle-num.bst}
 

### 2021-07-05 article/weakschur.tex
ws 6

@@
 we then introduce WS-templates as well as an associated sequence \(\WS^+(n)\). We find templates and use them to
-provide new lower bounds for weak Schur numbers.
+provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for the new lower bound 
+\(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds given in this 
+paper.
 
@@
 \begin{corollary}
+\label{Corollary3.19}
 Let \(n,k \in \mathbb{N}^*\) and set \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
@@
 
+\subsection{\(\WS(6) \geqslant 646\)}
+\qquad When applying the inequality \(\WS(n+1) \geqslant 4 \, S(n) + 2\), one may realize that it is possible to build a weakly 
+sum-free partition of length \(4 \, S(n) + 3\) for small values of \(n\) (\(n \leqslant 4\)) by using the contruction of 
+\hyperref[Corollary3.19]{Corollary 3.19} for the integers 1, 2, \(4i\) and \(4i+1\) for \(i \in [\![1, S(n)]\!]\) but not 
+constraining the other integers. We did the same for the Schur partitions corresponding to Schur number five. More precisely, 
+we imposed these constraints only for \(i \leqslant 50\) in order to have more degrees of freedom. The number 50 was chosen 
+arbitrarly so that all of the Schur number five partitions could tested in a few hours.
+
+However, trying out all of the 2\,447\,113\,088 Schur number five partitions (\cite{Heule2017}) one by one would not result in a 
+reasonable computation time: it is necessary to test the construction on several partitions at once. We encoded the problem as a 
+satisfiability problem and used the 1616 backdoors that were used in \cite{Heule2017} in order to encode a group of partitions in 
+a compact and efficient way. Among all of the 1616 backdoors, only the 911\textsuperscript{th} backdoor gave a weakly sum-free 
+partition of length 643. This backdoor gave a weakly sum-free partition of length 646 and cannot give a weakly sum-free 
+partition of length 647. A weakly sum-free partition of length 646 can be found in the \hyperref[WS(6)]{appendix}.
+
 \subsection{Conclusion on WS-templates}

### 2021-08-13 article/schur.tex
nouvelles valeurs

@@
 	S(n + 5) \geqslant &~380\,S(n) + 148 \label{S(n+5)}\\
-	S(n + 6) \geqslant &~1\,140\,S(n) + 528 \label{S(n+6)}
+	S(n + 6) \geqslant &~1\,160\,S(n) + 536 \label{S(n+6)}
 \end{align}
@@
 last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
-likely be further improved but the improvement probably will not be substantial. Finally, inequality (\ref{S(n+6)}) is obtained 
-by combining a S-template with width 380 and one with width three. Although we could not find a better S-template with seven 
-colors, inequality (\ref{S(n+6)}) can definitely be improved by a wide margin. One may try to seek better templates by 
-constraining less the search space and by using Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the subject 
-of a future work.
+likely be further improved but the improvement probably will not be substantial. Finally, a S-template corresponding to inequality 
+(\ref{S(n+6)}) was found by extending into a S-template the Schur 6 partition used in \cite{rowley2021improved} (owing to the 
+size of this template, its limited interest and since it can easily be derived from above mentioned partition, it is not given in 
+the appendix). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
+improved by a wide margin. One may try to seek better templates by constraining less the search space and by using Monte-Carlo 
+methods, as in \cite{Bouzy2015AnAP}. This could be the subject of a future work.
 
@@
 
-Except for\(S(8)\), \(S(9)\) and \(S(13)\), the best lower bounds are obtained thanks to
+Except for \(S(8)\), \(S(9)\) and \(S(13)\), the best lower bounds are obtained thanks to
 the third inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table

### 2021-08-14 article/schur.tex
modifs

@@
 
-\subsection{Definition of \(S^+\)}
+\subsection{Definition of \( [\![ 1, S^+ ]\!] \)}
 
@@
 Here \(n\) can be seen as a "special" color in the sense that we do not impose this above additionnal constraint on this color. 
-However, please note that \(n\) is not necessarily the last color by order of appearance.
+However, note that \(n\) is not necessarily the last color by order of appearance, any color can play this role.
 
@@
 	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
-	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\)  can be interpreted as the row number of \(x\) and \(u\) as the collumn number of \(x\). A new coloring is define as follows:
+	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\)  can be interpreted as the row number of \(x\) and 
+	\(u\) as the collumn number of \(x\). A new coloring is define as follows:
 	\[
@@
 \( n \geqslant 9 \). We compute the lower
-bounds for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the best values for \( n
-=8\) and \(n = 13\) were obtained thanks to the first one, found by Rowley. The best lower bounds are highlighted.
+bounds for \( n \in [\![8,15]\!] \) using the four different inequalities. The best lower bounds are highlighted.
 

### 2021-08-14 article/weakschur.tex
modifs

@@
 
-\subsection{Definition of \(\WS^+\)}
+\subsection{Definition of \([\![ 1, \WS^+ ]\!]\)}
 \label{DefinitionWS+}
@@
 
-Please note that the special color \(n\) is not necessarily the last color by order of appearance.
+Note that the special color \(n\) is not necessarily the last color by order of appearance, any color can play this role.
 We now introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.
@@
 Inequality (\ref{WS(n+3)}) cannot be further improved and was found with a SAT solver. It uses the first 
-sophistication explained in the \hyperref[ConstructionWS]{Subsection 3.3} in order to add
+sophistication explained in \hyperref[ConstructionWS]{Subsection 3.3} in order to add
 the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining a S-template with 
@@
 we imposed these constraints only for \(i \leqslant 50\) in order to have more degrees of freedom. The number 50 was chosen 
-arbitrarly so that all of the Schur number five partitions could tested in a few hours.
+arbitrarly so that all of the Schur number 5-partitions could be tested in a few hours.
 
-However, trying out all of the 2\,447\,113\,088 Schur number five partitions (\cite{Heule2017}) one by one would not result in a 
+However, trying out all of the 2\,447\,113\,088 Schur number 5-partitions (\cite{Heule2017}) one by one would not result in a 
 reasonable computation time: it is necessary to test the construction on several partitions at once. We encoded the problem as a 

### 2021-09-20 article/schur.tex
valeurs bis
3 + "its limited"

@@
 (\ref{S(n+6)}) was found by extending into a S-template the Schur 6 partition used in \cite{rowley2021improved} (owing to the 
-size of this template, its limited interest and since it can easily be derived from above mentioned partition, it is not given in 
+size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 
 the appendix). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
@@
 		n & 8 & 9 & 10 & 11 \\
-		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,446 & 174\,444 \\
-		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 186\,523 \\
+		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,974 & 174\,444 \\
+		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 188\,299 \\
 		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
@@
 		n & 12 & 13 & 14 & 15 \\
-		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,072\,090 \\
+		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,272\,730 \\
 		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
-		380 \, S(n-5) + 148 & 638\,548 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
+		380 \, S(n-5) + 148 & 644\,628 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
 	\end{NiceArray}

### 2021-09-20 article/introduction.tex
ws 6
nouvelles valeurs
une seule ligne State of the art

@@
 	\hline
-	\Block{2-1}{Before Rowley} & 1 & 4 & 13 & 44 & 160 & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
-	& & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{AbbottHanson} & \cite{AbbottHanson} & 
-		\cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
+	\Block{2-1}{State of the art} & 1 & 4 & 13 & 44 & 160 & 536 & 1\,696 & 5\,286 & 17\,694 & 60\,320 & 201\,696 & 637\,856 \\
+	& & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{rowley2021improved} & \cite{RowleyRamsey} & \cite{RowleyRamsey} & 
+		\cite{RowleyRamsey} & \cite{RowleyRamsey} & \cite{RowleyRamsey} \\
 	\hline
-	Rowley & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & 
-		\Block{2-1}{5\,286} & \Block{2-1}{17\,694} & \Block{2-1}{60\,320} & \Block{2-1}{201\,696} & \Block{2-1}{631\,840} \\
-	\cite{RowleyRamsey} & & & & & & & & & & & & \\
-	\hline
-	\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{638\,548} \\
+	\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{644\,628} \\
 	\hline
@@
 	\hline
-	\Block{2-1}{Before Rowley} & 2 & 8 & 23 & 66 & 196 & 582 & 1\,740 & 5\,201 & 15\,596 & 51\,520 & 172\,216 & 575\,664 \\
-	& & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
-		\cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
+	\Block{2-1}{State of the art} & 2 & 8 & 23 & 66 & 196 & 642 & 2\,146 & 6\,976 & 22\,056 & 70\,778 & 241\,282 & 806\,786 \\
+	& & & & & \cite{ELIAHOU2012175} &\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & 
+		\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} \\
 	\hline
-	Rowley & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{642} & \Block{2-1}{2\,146} & 
-		\Block{2-1}{6\,976} & \Block{2-1}{21\,848} & \Block{2-1}{70\,778} & \Block{2-1}{241\,282} & \Block{2-1}{806\,786} \\
-	\cite{RowleyWS} & & & & & & & & & & & & \\
-	\hline
-	\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{22\,536} & \textbf{71\,214} & \textbf{243\,794} & \textbf{815\,314} \\
+	\hyperref[Schur]{\textbf{Our results}}  & & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
 	\hline

### 2021-09-20 article/weakschur.tex
valeurs bis
contexte + titre 3.5

@@
 we only looked for WS-templates of five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
-special color was the last by order of appearance. We highly suspect that bettert WS-templates with \(n \geqslant 5\) 
+special color was the last by order of appearance. We highly suspect that better WS-templates with \(n \geqslant 5\) 
 colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
@@
 	\CodeBefore
-		\cellcolor{yellow}{2-4}
 		\cellcolor{yellow}{2-5}
@@
 		\cellcolor{yellow}{4-3}
+		\cellcolor{yellow}{4-4}
 	\Body
 		n & 8 & 9 & 10 & 11 \\
-		4 \, S(n-1) + 2 & 6\,722 & 21\,146 & 71\,214 & 243\,794 \\
-		13 \, S(n-2) + 8 & 6\,976 & 21\,848 & 68\,726 & 231\,447 \\
-		42 \, S(n-3) + 24 & 6\,744 & 22\,536 & 70\,584 & 222\,036 \\
+		4 \, S(n-1) + 2 & 6\,786 & 21\,146 & 71\,214 & 243\,794 \\
+		13 \, S(n-2) + 8 & 6\,976 & 22\,056 & 68\,726 & 231\,447 \\
+		42 \, S(n-3) + 24 & 6\,744 & 22\,536 & 71\,256 & 222\,036 \\
 	\end{NiceArray}
@@
 		\cellcolor{yellow}{2-2}
-		\cellcolor{yellow}{2-5}
 		\cellcolor{yellow}{3-3}
 		\cellcolor{yellow}{4-4}
+		\cellcolor{yellow}{4-5}
 	\Body
 		n & 12 & 13 & 14 & 15 \\
-		4 \, S(n-1) + 2 & 815\,314 & 2\,554\,194 & 8\,045\,162 & 27\,061\,154 \\
-		13 \, S(n-2) + 8 & 792\,332 & 2\,649\,772 & 8\,301\,132 & 26\,146\,778 \\
-		42 \, S(n-3) + 24 & 747\,750 & 2\,559\,840 & 8\,560\,800 &  25\,886\,224 \\
+		4 \, S(n-1) + 2 & 815\,314 & 2\,578\,514 & 8\,045\,162 & 27\,061\,154 \\
+		13 \, S(n-2) + 8 & 792\,332 & 2\,649\,772 & 8\,380\,172 & 26\,146\,778 \\
+		42 \, S(n-3) + 24 & 747\,750 & 2\,559\,840 & 8\,560\,800 &  27\,074\,400 \\
 	\end{NiceArray}
@@
 With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using (\ref{WS(n+1)}).
-Moreover, inequality (\ref{WS(n+3)}) gives new lower bounds for \(\WS(9)\) and \(WS(14)\).
+Moreover, inequality (\ref{WS(n+3)}) gives new lower bounds for \(\WS(9)\), \(\WS(10)\), \(\WS(14)\) and \(\WS(15)\).
 
-\subsection{\(\WS(6) \geqslant 646\)}
-\qquad When applying the inequality \(\WS(n+1) \geqslant 4 \, S(n) + 2\), one may realize that it is possible to build a weakly 
+\subsection{Another approach: \(\WS(6) \geqslant 646\)}
+\qquad The weak Schur partitions obtained with WS-templates have an extremely regular structure. Therefore, one may 
+expect to find larger partitions by allowing more freedom in the structure of the partition while still preserving a structure 
+somewhat close to a template-based partition thus reducing the search space to a manageable size.
+
+When applying the inequality \(\WS(n+1) \geqslant 4 \, S(n) + 2\), one may realize that it is possible to build a weakly 
 sum-free partition of length \(4 \, S(n) + 3\) for small values of \(n\) (\(n \leqslant 4\)) by using the contruction of 

### 2021-09-21 article/schur.tex
modifs + numerotation cassee :'(

@@
 We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
-of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. We thereby define a S-template as
-a new object filling the role of the first line but with less, yet sufficiant, constraints that will allow the expansion of the
-table.
+of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. A S-template 
+is then defined as a new object filling the role of the first line but with less, yet sufficiant, constraints which allow a linear 
+expansion of the partition.
 
@@
 \end{proof}
-
-\begin{remark}
-	\(S^+\) and \(S\) have the same asymptotic growth rate.
-\end{remark}
 

### 2021-09-21 article/weakschur.tex
modifs + numerotation cassee :'(

@@
 for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
-we then introduce WS-templates as well as an associated sequence \(\WS^+(n)\). We find templates and use them to
-provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for the new lower bound 
-\(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds given in this 
-paper.
+we then introduce WS-templates, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
+We find templates and use them to provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for 
+the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
+given in this paper.
 
@@
 
-\begin{remark}
-\(\WS^+\) and \(\WS\) have the same asymptotic growth rate.
-\end{remark}
-
 We now proceed to state and prove the main result of this article.
@@
 \label{ConstructionWS}
+
+Theorem provides a way to extend a S-template into a larger Schur partitions using other Schur partitions. Likewise, a WS-template can 
+be extended into larger weak Schur partitions in using Schur partitions. This is the object of the following theorem.
 

### 2021-09-22 article/abstract-JTO.tex
Add files via upload
Une proposition de l'abstract.

--- 2021-07-05 article/article.tex
@@
-\documentclass[3p]{elsarticle}
-\title{New lower bounds for Schur and weak Schur numbers}
-\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}
+\documentclass[12pt]{article}
 
@@
 \usepackage{amsthm}
-\usepackage{dsfont}
-\usepackage{MyMnSymbol}
-
-\usepackage[english]{babel}
-\usepackage[hyphens]{url}
-\usepackage{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage{siunitx}
-\usepackage{float}
-
-\usepackage[table]{xcolor}
-\usepackage{multirow}
-\usepackage{nicematrix}
-
-\renewcommand{\qedsymbol}{\(\square\)}
-
-\newtheorem{definition}{Definition}[section]
-\newtheorem{notation}[definition]{Notation}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{computational theorem}[definition]{Computational Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-\newtheorem{remark}[definition]{Remark}
-\newtheorem{proposition}[definition]{Proposition}
 
 \newcommand{\WS}{\mathit{WS}}
-\newcommand{\docarraystretch}{1.2}
-\newcommand{\resetarraystretch}{\renewcommand{\arraystretch}{\docarraystretch}}
-\resetarraystretch
 
@@
 
-\begin{abstract}
+\textbf{INITIAL VERSION}
+
+\smallskip
 
@@
 bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\) and 
-\(\WS (10) \geqslant 71\,214 \).
+\(\WS (10) \geqslant 71\,256 \).
 
-\end{abstract}
+\bigskip
 
-\maketitle
+\textbf{REVISED VERSION}
 
-\input{introduction.tex}
+\smallskip
 
-\input{schur.tex}
+We provide one with new lower bounds for both Schur and weak Schur numbers exploiting a template-based approach for Schur and Ramsey numbers.
+These bounds for Schur are \(S(9) \geqslant 17\,803\) and \(S(10) \geqslant 60\,948\), while for weak Schur they are \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\), and
+\(\WS (10) \geqslant 71\,256 \).
 
-\input{weakschur.tex}
-
-\section{Conclusions and future work}
-
-\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
-Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
-using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
- are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
-randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.
-
-\section{Acknowledgments}
-
-\qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
-us during the whole research and writing. We also would like to address warm thanks
-to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
-Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
-new lower bound for \(\WS(6)\).
-
-\bibliography{biblio}
-\bibliographystyle{elsarticle-num.bst}
-
-\include{appendix.tex}
+The enriched templates developed also allow us to explicit the growth rate for Schur,  weak Schur, and Ramsey numbers \(R_n(3)\).
 

### 2021-09-22 article/introduction.tex
fix refs + precisions

@@
 \par
-In \hyperref[Schur]{Section 2}, we explain Rowley's template-based construction in the context of 
+In Section \ref{Schur}, we explain Rowley's template-based construction in the context of 
 Schur numbers. Then, we give new templates, thus providing new lowers bounds and inequalities as well as 
@@
 \par
-In \hyperref[WeakSchur]{Section 3}, we generalize the concept of templates to weak Schur numbers 
-and provide new lower bounds for weak Schur numbers.
+In Section \ref{WeakSchur}, we generalize the concept of templates to weak Schur numbers 
+and provide new lower bounds for weak Schur numbers. We then use a different approach and give a new 
+lower bound for \(\WS(6)\).
 

### 2021-09-22 article/schur.tex
fix refs + precisions

@@
 \begin{theorem}
-\label{Theorem2.4}
+\label{thm:Stemp}
 	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
@@
 \begin{corollary}
-\label{Corollary2.5}
+\label{cor:ineqS}
 	Let \(n, k \in \mathbb{N}^*\). Then
@@
 
-We now proceed to prove \hyperref[Theorem2.4]{Theorem 2.4}
+We now proceed to prove Theorem \ref{thm:Stemp}.
 
@@
 
-The following proposition may improve the additive constant of \hyperref[Corollary2.5]{Corollary 2.5}.
+The following proposition may improve the additive constant of Corollary \ref{cor:ineqS}.
 
 \begin{proposition}
-\label{Proposition2.6}
+\label{prop:rafStemp}
 Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a S-template with width \(q\) and \(n+1\) 
@@
 \begin{proof}[\textsc{Proof.}]
-The idea is the same as in the \hyperref[Theorem2.4]{Theorem 2.4}. The only difference is the S-template property inherited 
+The idea is the same as in the Theorem \ref{thm:Stemp}. The only difference is the S-template property inherited 
 from the second S-template. \\
@@
 \subsection{New lower bounds for Schur numbers}
-\label{Subsection2.3}
-We now give the inequalities corresponding to the current  best S-templates (to our knowledge).
+\label{subsec:lowS}
+We now give the inequalities corresponding to the current  best S-templates.
 
@@
 \par
-Here are the inequalities given by the current best S-templates (to our knowledge). The \hyperref[S-templates]{templates} 
+Here are the inequalities given by the current best S-templates. The \hyperref[S-templates]{templates} 
 corresponding to the third, fourth and fifth inequalities can be found in the appendix.
@@
 \begin{proof}[\textsc{Proof.}]
-It is a mere consequence of the inequality \( S(n+5) \geqslant 380S(n) + 148\). As for Ramsey
+It is a mere consequence of the inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). As for Ramsey
 numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}) hence the result. \\

### 2021-09-22 article/weakschur.tex
fix refs + precisions

@@
 \qquad In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
-for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
+for weak Schur numbers of Abbott and Hanson's construction for Schur numbers \cite{AbbottHanson}. By analogy with the previous section,
 we then introduce WS-templates, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
@@
 \cite{AbbottHanson} was known. Here we give a general lower bound for weak Schur numbers as a function of both
-regular and weak Schur numbers. The following theorem, inspired by Rowley's inequalities for \(\WS (n+1)\) and
-\(\WS (n+2)\), was found and proved by Romain Ageron.
+regular and weak Schur numbers.
 
 \begin{theorem}
-\label{Theorem3.1}
+\label{thm:WS-ab}
 \begin{sloppypar}
@@
 
-In particular, by setting \(q = \WS (n)\) and \(p = S(k)\) in \hyperref[Theorem3.1]{Theorem 3.1}, one obtains the following corollary.
+In particular, by setting \(q = \WS (n)\) and \(p = S(k)\) in Theorem \ref{thm:WS-ab}, one obtains the following corollary.
 
 \begin{corollary}
-\label{Corollary3.2}
+\label{cor:ineqWS-S}
 \( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } \WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \displaystyle \frac{\WS (n)}{2}
@@
 \begin{remark}
-The inequality from \hyperref[Corollary3.2]{Corollary 3.2} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
-odd in the theorem). However, it lengthens the proof and it is never useful in practice.
+The inequality from Corollary \ref{cor:ineqWS-S} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
+odd in Theorem \ref{thm:WS-ab}). However, it lengthens the proof and it is never useful in practice.
 \end{remark}
 
-Given that \hyperref[Theorem3.1]{Theorem 3.1} will appear as a particular case of a more general theorem after the introduction of
+Given that Theorem \ref{thm:WS-ab} will appear as a particular case of a more general theorem after the introduction of
 templates for weak Schur numbers, we only give here an intuitive explanation of the demonstration; a formal
-\hyperref[PreuveThm]{proof} using templates for weak Schur numbers is provided.
+\hyperref[PreuveThm]{proof} using templates for weak Schur numbers is provided in Subsection \ref{ConstructionWS}.
 
@@
 \begin{array}{l l l l}
-	\pi(x + y) & = & \pi(x + \pi(y)) & \text{by \hyperref[prop2]{Proposition 3.6}} \\
-	 & = & x + \pi(y) & \text{by \hyperref[prop1]{Proposition 3.5}}
+	\pi(x + y) & = & \pi(x + \pi(y)) & \text{by Proposition \ref{prop2}} \\
+	 & = & x + \pi(y) & \text{by Proposition \ref{prop1}}
 \end{array}
@@
 Function \(\lambda\) maps an element \(x\) to its line number as mentioned in the intuitive explanation.
-As we just did with \(\pi\), we proove three more results on both \(\pi\) and \(\lambda\) that will appear useful in
-\hyperref[ConstructionWS]{Subsection 3.3}.
+As we just did with \(\pi\), we prove three more calculative results on both \(\pi\) and \(\lambda\) that are used in
+Subsection \ref{ConstructionWS}.
 
@@
 \begin{proof}[\textsc{Proof.}]
-By applying \hyperref[prop5]{Proposition 3.10} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
+By applying Proposition \ref{prop5} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
 The result is then obtained by simplying the equality. \\
@@
 \begin{proof}[\textsc{Proof.}]
-By \hyperref[prop5]{Proposition 3.10}, \(x + y = a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a\). Then
+By Proposition \ref{prop5}, \(x + y = a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a\). Then
 \[
@@
 \begin{proof}[\textsc{Proof.}]
-The lower bound comes from the analogous of Abott and Hanson's construction for weak Schur numbers.
-The upper bound comes from the fact that a WS-template with width \(a\) and \(n\) colors contains a partition of
-\([\![1, a]\!]\) into \(n\) sum-free subsets. \\
+The lower bound comes from Corollary \ref{cor:ineqWS-S}.
+The upper bound comes from the fact that a WS-template with width \(a\) and \(n\) colors is in particular a partition of
+\([\![1, a]\!]\) into \(n\) weakly sum-free subsets. \\
 \end{proof}
@@
 
-Theorem provides a way to extend a S-template into a larger Schur partitions using other Schur partitions. Likewise, a WS-template can 
-be extended into larger weak Schur partitions in using Schur partitions. This is the object of the following theorem.
+Theorem \ref{thm:Stemp} provides a way to extend a S-template into a larger Schur partitions using other Schur partitions. Likewise, a WS-template can 
+be extended into larger weak Schur partitions by using Schur partitions. This is the object of the following theorem.
 
 \begin{theorem}
-\label{Theorem3.18}
+\label{thm:WStemp}
 Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\)
@@
 
-In particular, by setting \(p = S(k)\) and \(a = \WS^+(n + 1)\) in \hyperref[Theorem3.18]{Theorem 3.18}, the next corollary follows.
+In particular, by setting \(p = S(k)\) and \(a = \WS^+(n + 1)\) in Theorem \ref{thm:WStemp}, the next corollary follows.
 
 \begin{corollary}
-\label{Corollary3.19}
+\label{cor:ineqWS+}
 Let \(n,k \in \mathbb{N}^*\) and set \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
@@
 Split \([\![1, p a + b]\!]\) into three subsets. \\
-NB: To keep the notation short, the restriction to \([\![b + 1, p a + b]\!]\) of \(\pi\) defined in \hyperref[DefinitionWS+]{Subsection 3.2}
-is denoted by \(pi\) in the hereunder equations.
+NB: To keep the notation short, the restriction to \([\![b + 1, p a + b]\!]\) of \(\pi\) defined in Subsection \ref{DefinitionWS+}
+is denoted by \(\pi\) in the hereunder equations.
 
@@
 If \(x + y \leqslant b\) then \(h(x+y)=f(x+y)\). Otherwise, \(b < x+y < a+b\) since \(b < a\) and
-therefore \(\pi(x + y) = x +y\) (\hyperref[prop1]{Proposition 3.5}). Hence in both cases \(h(x+y)=f(x+y)\). Given that
+therefore \(\pi(x + y) = x +y\) (Proposition \ref{prop1}). Hence in both cases \(h(x+y)=f(x+y)\). Given that
 \(f\) is a weakly sum-free coloring, \(f(x + y) \neq f(x)\) since \(f(x)=h(x)=h(y)=f(y)\) and \(x \neq y \). That
@@
 \item \begin{sloppypar}
-	If \(x + \pi(y) \leqslant a + b\) then \(f(x + \pi(y)) = f(\pi(x + y))\) (\hyperref[prop3]{Proposition 3.7}). Given that \(f\) is
+	If \(x + \pi(y) \leqslant a + b\) then \(f(x + \pi(y)) = f(\pi(x + y))\) (Proposition \ref{prop3}). Given that \(f\) is
 	a weakly sum-free coloring, \(f(x+\pi(y)) \neq f(x)\) since \(f(x)=f(\pi(y))\) and \(x \neq \pi(y)\) since
@@
 	If \(x+\pi(y)> a+b\) then given that \(f\) is a WS-template and since \({f(x) = f(\pi(y)) \leqslant n}\),
-	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (\hyperref[prop2]{Proposition 3.6}), such that
+	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (Proposition \ref{prop2}), such that
 	\({f(\pi(x+ y)) \neq f(x)}\).
@@
 \begin{itemize}
-\item If \(\lambda(y)=\lambda(x+y)\) then \(\pi(x + y) = x + \pi(y)\) (\hyperref[prop6]{Proposition 3.11}). By definition of
+\item If \(\lambda(y)=\lambda(x+y)\) then \(\pi(x + y) = x + \pi(y)\) (Proposition \ref{prop6}). By definition of
 	\(h\), \(f(x) = f(\pi(y))\). Given that \(f\) is a weakly sum-free coloring, \(f(x + \pi(y)) \neq f(x)\) since
@@
 	If \(\pi(x)+\pi(y)>a+b\) then given that \(f\) is a WS-template, \({f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x))}\) since
-	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (\hyperref[prop4]{Proposition 3.8}). Hence \({f(\pi(x + y))
+	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (Proposition \ref{prop4}). Hence \({f(\pi(x + y))
 	\neq  f(\pi(x))}\).
@@
 \item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\)
-	(\hyperref[prop7]{Proposition 3.12}). By definition of \(h\) and since \(h(x) = h(y)\), \(g(\lambda(x)) = g(\lambda(y))\).
+	(Proposition \ref{prop7}). By definition of \(h\) and since \(h(x) = h(y)\), \(g(\lambda(x)) = g(\lambda(y))\).
 	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x))\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\)
@@
 \item If \(\pi(x)+\pi(y)>2a+b\) then \(f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x)) = n + 1\) since \(f\) is a \(b\)-WS template and
-	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (\hyperref[prop4]{Proposition 3.8}), \(f(\pi(x+y)) \neq n + 1\).
+	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (Proposition \ref{prop4}), \(f(\pi(x+y)) \neq n + 1\).
 \item \begin{sloppypar}
 	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(f_{| [\![b, a + b ]\!]}\) is
-	sum-free, \({f(\pi(x) + \pi(y)) \neq f(\pi(x)) = n + 1}\). That is \({f(\pi(x + y)) \neq n + 1}\) (\hyperref[prop1]{Proposition 3.5}).
+	sum-free, \({f(\pi(x) + \pi(y)) \neq f(\pi(x)) = n + 1}\). That is \({f(\pi(x + y)) \neq n + 1}\) (Proposition \ref{prop1}).
 	\end{sloppypar}
@@
 \begin{theorem}
-\label{Theorem3.21}
+\label{thm:compWStemp}
 Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there exists a S-template with width
@@
 
-\hyperref[Theorem3.21]{Theorem 3.21} yields the following corollary.
+Theorem \ref{thm:compWStemp} yields the following corollary.
 
@@
 The idea is the same as in the previous theorem. The only difference is the WS property inherited
-from the WS-template. \\
+from both the S-template and the WS-template. \\
 \end{proof}
 
-\hyperref[Theorem3.1]{Theorem 3.1} can be seen as a particular case of WS-template in the same way Abott and Hanson's 
-construction can be seen as a particular case of S-template.
+Theorem \ref{thm:WS-ab} can be seen as a particular case of WS-template in the same way Abott and Hanson's 
+construction \cite{AbbottHanson} can be seen as a particular case of S-template.
 
-\begin{proof}[\textsc{Proof of \hyperref[Theorem3.1]{Theorem 3.1}.}]
+\begin{proof}[\textsc{Proof of Theorem \ref{thm:WS-ab}.}]
 \label{PreuveThm}
@@
 
-The result is then obtained by applying \hyperref[Theorem3.18]{Theorem 3.18}. \\
+The result is then obtained by applying Theorem \ref{thm:WStemp}. \\
 \end{proof}
 
-As in \hyperref[Corollary2.5]{Corollary 2.5}, the additive constant \hyperref[Theorem3.18]{Theorem 3.18} can be improved 
-by weakening the hypotheses made on the last row. The principle behind it is the same as in \hyperref[Proposition2.6]{Proposition 2.6}.
+As in Corollary \ref{cor:ineqS}, the additive constant Theorem \ref{thm:WStemp} can be improved 
+by weakening the hypotheses made on the last row. The principle behind it is the same as in Proposition \ref{prop:rafStemp}.
 
@@
 
-We also have a similar theorem where only \(\WS^+\) is involved.
-
 \subsection{New lower bounds for Weak Schur numbers}
@@
 \par
-Here are the inequalities given by the current best WS-templates (to our knowledge). The \hyperref[WS-templates]{templates} 
+Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{templates} 
 corresponding to the third inequality can be found in the appendix.
@@
 Inequality (\ref{WS(n+3)}) cannot be further improved and was found with a SAT solver. It uses the first 
-sophistication explained in \hyperref[ConstructionWS]{Subsection 3.3} in order to add
+sophistication explained in Subsection \ref{ConstructionWS} in order to add
 the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining a S-template with 
@@
 
-Like in \hyperref[Subsection2.3]{Subsection 2.3}, we compute the lower bounds given by inequalities (\ref{WS(n+1)}),
+Like in  Subsection \ref{subsec:lowS}, we compute the lower bounds given by inequalities (\ref{WS(n+1)}),
 (\ref{WS(n+2)}) and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound for each value of \(n\) is highlighted.
@@
 sum-free partition of length \(4 \, S(n) + 3\) for small values of \(n\) (\(n \leqslant 4\)) by using the contruction of 
-\hyperref[Corollary3.19]{Corollary 3.19} for the integers 1, 2, \(4i\) and \(4i+1\) for \(i \in [\![1, S(n)]\!]\) but not 
+Corollary \ref{cor:ineqWS+} for the integers 1, 2, \(4i\) and \(4i+1\) for \(i \in [\![1, S(n)]\!]\) but not 
 constraining the other integers. We did the same for the Schur partitions corresponding to Schur number five. More precisely, 
@@
 between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
-obtained with WS-templates.
+obtained with WS-templates. We reckon better WS-templates with \(n \geqslant 5\) colors can be found by making different assumptions 
+and using a different method (Monte-Carlo methods for instance).

### 2021-09-23 article/article.tex
nouvelles valeurs
Nouvelle conclusion

@@
 bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\) and 
-\(\WS (10) \geqslant 71\,214 \).
+\(\WS (10) \geqslant 71\,256 \).
 
@@
 
-\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
+\qquad [OLD VERSION] These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
 Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
@@
 randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.
+
+\qquad [NEW VERSION] The new results we provide come from an extension of a template-based approach for Ramsey graphs
+and Schur numbers. Our theoretical work allowed to improve the lower bounds on Schur and Weak Schur numbers and have
+a better understanding of this relatively new approach. Furthermore we introduced the new quantities \(S^+(n)\) and
+\(\WS^+(n)\), which may have an interest as they are closely related to the problem at hand. As the use of templates
+is quite recent, we expect the bounds to be improved by carrying on our work further. For example, one may try to use
+algorithms based on randomness such as Monte-Carlo algorithms to find better templates.
 

### 2021-09-23 article/article.tex
Modifs

--- 2021-07-05 article/article.tex
@@
 This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
-continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. We also generalized the concept 
+exploiting a "template"-based approach for Schur and Ramsey numbers. This article also generalizes the concept 
 of "template" to weak Schur numbers. Finding new templates allows us to get explicit partitions improving lower bounds 

### 2021-09-23 article/weakschur.tex
Modifs
Phrase intro Subsection 3.3

@@
 By applying Proposition \ref{prop5} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
-The result is then obtained by simplying the equality. \\
+The result is then obtained by simplifying the equality. \\
 \end{proof}
@@
 
-We now proceed to state and prove the main result of this article.
+Having established these properties, we now have everything we need to state and prove our main result. We proceed to do so
+in the next subsection.
 
@@
 	WS(n + 1) &\geqslant  4\,S(n)  +  2 \label{WS(n+1)} \\
-	WS(n + 2) &\geqslant  13\,S(n)  +  8 \label{WS(n+2)} \\
+	WS(n + 2) &\geqslant  13\,S(n)  +  8 \label{WS(n+2)} 
+\end{align}
+
+Inequalities (\ref{WS(n+1)}) and (\ref{WS(n+2)}) were found by Rowley, they are detailed in \cite{RowleyWS}.
+
+\begin{align}
 	WS(n + 3) &\geqslant  42\,S(n)  +  24 \label{WS(n+3)} \\
@@
 
-Inequalities (\ref{WS(n+1)}) and (\ref{WS(n+2)}) were found by Rowley, they are detailed in \cite{RowleyWS}. 
 Inequality (\ref{WS(n+3)}) cannot be further improved and was found with a SAT solver. It uses the first 

### 2021-09-23 article/article.tex
removed qquad

@@
 
-\qquad [OLD VERSION] These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
+[OLD VERSION] These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
 Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
@@
 
-\qquad [NEW VERSION] The new results we provide come from an extension of a template-based approach for Ramsey graphs
+[NEW VERSION] The new results we provide come from an extension of a template-based approach for Ramsey graphs
 and Schur numbers. Our theoretical work allowed to improve the lower bounds on Schur and Weak Schur numbers and have
@@
 
-\qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
+We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
 us during the whole research and writing. We also would like to address warm thanks

### 2021-09-23 article/weakschur.tex
removed qquad

@@
 
-\qquad In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
+In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
 for weak Schur numbers of Abbott and Hanson's construction for Schur numbers \cite{AbbottHanson}. By analogy with the previous section,
@@
 
-\qquad Up to now, no equivalent for weak Schur numbers of Abbott and Hanson's construction for Schur numbers
+Up to now, no equivalent for weak Schur numbers of Abbott and Hanson's construction for Schur numbers
 \cite{AbbottHanson} was known. Here we give a general lower bound for weak Schur numbers as a function of both
@@
 
-\qquad In this subsection, we introduce WS-templates and prove calculative results for the general construction
+In this subsection, we introduce WS-templates and prove calculative results for the general construction
 theorem on templates for weak Schur numbers.
@@
 By applying Proposition \ref{prop5} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
-The result is then obtained by simplifying the equality. \\
+The result is then obtained by simplying the equality. \\
 \end{proof}
@@
 
-Having established these properties, we now have everything we need to state and prove our main result. We proceed to do so
-in the next subsection.
+We now proceed to state and prove the main result of this article.
 

### 2021-09-23 article/article.tex
reformulation acknowledgments

--- 2021-09-23 article/article.tex
@@
 
-\qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
-us during the whole research and writing. We also would like to address warm thanks
-to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
-Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
-new lower bound for \(\WS(6)\).
+\qquad We would first like to thank our school CentraleSupélec and its Research Pole 005 led by Joanna Tomasik allowing us to
+make this project in our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
+and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors
+used in the computation of the new lower bound for \(\WS(6)\).
 

### 2021-09-23 article/article.tex

--- 2021-09-23 article/article.tex
@@
 
-We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
-us during the whole research and writing. We also would like to address warm thanks
-to Fred Rowley who kindly answered our many questions and with who it was a pleasure to exchange. 
-Last but not least, we would like to thank Marijn Heule for providing the backdoors used in the computation of the 
-new lower bound for \(\WS(6)\).
+\qquad We would first like to thank our school CentraleSupélec and its Research Pole 005 led by Joanna Tomasik allowing us to
+make this project in our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
+and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors
+used in the computation of the new lower bound for \(\WS(6)\).
 

### 2021-09-23 article/weakschur.tex

@@
 
-\qquad We produced WS-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities
+We produced WS-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities
 of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) (in the 
@@
 \subsection{Another approach: \(\WS(6) \geqslant 646\)}
-\qquad The weak Schur partitions obtained with WS-templates have an extremely regular structure. Therefore, one may 
+
+The weak Schur partitions obtained with WS-templates have an extremely regular structure. Therefore, one may 
 expect to find larger partitions by allowing more freedom in the structure of the partition while still preserving a structure 
@@
 
-\qquad We started by giving a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
+We started by giving a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
 and Hanson's construction for sum-free partitions. We then generalized this construction by introducing WS-templates. This

### 2021-09-23 article/article.tex
affiliations + keywords

--- 2021-09-23 article/article.tex
@@
 \documentclass[3p]{elsarticle}
-\title{New lower bounds for Schur and weak Schur numbers}
-\author{Romain Ageron, Paul Casteras, Thibaut Pellerin, Yann Portella}
 
@@
 
+\title{New lower bounds for Schur and weak Schur numbers}
+
+\author[1]{Romain Ageron\fnref{fn1}}
+\ead{romain.ageron@student-cs.fr}
+
+\author[1]{Paul Casteras\fnref{fn1}}
+\ead{paul.casteras@student-cs.fr}
+
+\author[1]{Thibaut Pellerin\fnref{fn1}}
+\ead{thibaut.pellerin@student-cs.fr}
+
+\author[1]{Yann Portella\fnref{fn1}}
+\ead{yann.portella@student-cs.fr}
+
+\author[2]{Arpad Rimmel\fnref{fn2}}
+\ead{arpad.rimmel@centralesupelec.fr}
+
+\author[2]{Joanna Tomasik\corref{cor1}\fnref{fn2}}
+\ead{joanna.tomasik@centralesupelec.fr}
+
+\cortext[cor1]{Corresponding author}
+\fntext[fn1]{These authors contributed equally.}
+\fntext[fn2]{These authors supervised the work of the main authors.}
+
+\address[1]{\textit{CentraleSup\'elec}, Universit\'e Paris-Saclay}
+\address[2]{LRI, \textit{CentraleSup\'elec}, Universit\'e Paris-Saclay, F-91405, Orsay, France}
+
 \begin{document}
@@
 This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
-exploiting a "template"-based approach for Schur and Ramsey numbers. This article also generalizes the concept 
+continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. We also generalized the concept 
 of "template" to weak Schur numbers. Finding new templates allows us to get explicit partitions improving lower bounds 
@@
 \end{abstract}
+
+\begin{keyword}
+Schur number \sep weak Schur number \sep Ramsey theory \sep Sumfree partition
+\MSC[2020]{05D10 \sep 05A17 \sep 11B75 \sep 11B81}
+\end{keyword}
 
@@
 
-[OLD VERSION] These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
+\qquad These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
 Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
@@
 
-[NEW VERSION] The new results we provide come from an extension of a template-based approach for Ramsey graphs
-and Schur numbers. Our theoretical work allowed to improve the lower bounds on Schur and Weak Schur numbers and have
-a better understanding of this relatively new approach. Furthermore we introduced the new quantities \(S^+(n)\) and
-\(\WS^+(n)\), which may have an interest as they are closely related to the problem at hand. As the use of templates
-is quite recent, we expect the bounds to be improved by carrying on our work further. For example, one may try to use
-algorithms based on randomness such as Monte-Carlo algorithms to find better templates.
-
 \section{Acknowledgments}
 
-We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
+\qquad We would first like to thank our professors, Joanna Tomasik and Arpad Rimmel, who guided and advised
 us during the whole research and writing. We also would like to address warm thanks

### 2021-09-23 article/schur.tex
Modifs

@@
 
-\qquad In this section, we use Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur 
+In this section, we use Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur 
 numbers. In order to improve lower bounds for Schur and Ramsey numbers, he introduces special sum-free 
@@
 
-\qquad We start by reminding the explicit construction of a sum-free partition with the use of a S-template and another sum free partition.
+We start by reminding the explicit construction of a sum-free partition with the use of a S-template and another sum free partition.
 We apply this contruction stated by Rowley in the context of Ramsey numbers to the Schur numbers.
@@
 \label{subsec:lowS}
+
 We now give the inequalities corresponding to the current  best S-templates.
@@
 	S(n + 3) \geqslant &~33\,S(n) + 6 \label{S(n+3)}\\
+\end{align}
+
+Inequality (\ref{S(n+1)}) comes from  Schur's original article\cite{Schur1917}. Inequality (\ref{S(n+2)}) is due to
+Abott and Hanson \cite{AbbottHanson} and inequality (\ref{S(n+3)}) to Rowley \cite{RowleyRamsey}. 
+The three following inequalities are our result.
+
+\begin{align}
 	S(n + 4) \geqslant &~111\,S(n) + 43 \label{S(n+4)}\\
@@
 \end{align}
-
-Inequality (\ref{S(n+1)}) comes from  Schur's original article\cite{Schur1917}. Inequality (\ref{S(n+2)}) is due to
-Abott and Hanson \cite{AbbottHanson} and inequality (\ref{S(n+3)}) to Rowley \cite{RowleyRamsey}. Inequalities 
-(\ref{S(n+4)}), (\ref{S(n+5)}) and (\ref{S(n+6)}) are our results.
 
@@
 
-\qquad In this section, we first formalized Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur numbers 
+In this section, we first formalized Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur numbers 
 by introducing S-templates as well as a new sequence, \(S^+\). We provided relations between \(S^+\) and \(S\) then 

### 2021-09-23 article/article.tex
abstract + future works + .!!!!

@@
 
-This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
-exploiting a "template"-based approach for Schur and Ramsey numbers. This article also generalizes the concept 
-of "template" to weak Schur numbers. Finding new templates allows us to get explicit partitions improving lower bounds 
-as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). The new lower 
-bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\) and 
-\(\WS (10) \geqslant 71\,256 \).
+This article provides new lower bounds for both Schur and weak Schur numbers by exploiting a "template"-based approach. 
+The concept of "template" is also generalized to weak Schur numbers. Finding new templates leads to explicit partitions 
+improving lower bounds as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). 
+The new lower bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), 
+\(\WS (9) \geqslant 22\,536\) and \(\WS (10) \geqslant 71\,256 \).
 
@@
 \begin{keyword}
-Schur number \sep weak Schur number \sep Ramsey theory \sep Sumfree partition
+Schur number \sep Weak Schur number \sep Ramsey theory \sep Sumfree partition
 \MSC[2020]{05D10 \sep 05A17 \sep 11B75 \sep 11B81}
@@
 
-\section{Conclusions and future work}
+\section{Conclusion and future work}
 
-[OLD VERSION] These new results come from an extension of Rowley's template-based approach for Ramsey graphs and 
-Schur numbers which is relatively new. Therefore, we will not be surprised if lower bounds are later improved 
-using better templates. Moreover, studying specifically \(S^+(n)\) and \(\WS^+(n)\) might be of interest as they
- are closely related to Schur and weak Schur numbers. In order to find new templates, algorithms based on 
-randomness such as Monte-Carlo algorithms may prove to be very useful. This could be the subject of a future work.
-
-[NEW VERSION] The new results we provide come from an extension of a template-based approach for Ramsey graphs
+The new results we provide come from an extension of a template-based approach for Ramsey graphs
 and Schur numbers. Our theoretical work allowed to improve the lower bounds on Schur and Weak Schur numbers and have
 a better understanding of this relatively new approach. Furthermore we introduced the new quantities \(S^+(n)\) and
-\(\WS^+(n)\), which may have an interest as they are closely related to the problem at hand. As the use of templates
-is quite recent, we expect the bounds to be improved by carrying on our work further. For example, one may try to use
+\(\WS^+(n)\), which may have an interest as they are closely related to the problem at hand.
+
+Given that the introduction of templates is quite recent, we expect the bounds to be improved as this special type of partition 
+becomes better understood and larger templates are found. For example, one may try to use
 algorithms based on randomness such as Monte-Carlo algorithms to find better templates.
+
+The best lower bound \(\WS(6) \geqslant 583\) achieved with a computer search using Monte-Carlo methods 
+\cite{EliahouBook} is significantly lower than those obtained with a template-like structure (\(\WS(6) \geqslant 642\) \cite{RowleyWS}, 
+\(\WS(6) \geqslant 646\) in the present article). We have evidence that 583 is the maximal value in the search space considered by 
+\cite{EliahouBook,Bouzy2015AnAP,Rafilipojaona}. Therefore, it questions the assumption that large partitions for \(\WS(n+1)\) 
+start with large partitions for \(\WS(n)\). It also indicates that \(\WS(5)\) might need further investigation since the current lower 
+bound \(\WS(5) \geqslant 196\) \cite{ELIAHOU2012175} it was obtained by considering the same type of search space.
 
@@
 
-\qquad We would first like to thank our school CentraleSupélec and its Research Pole 005 led by Joanna Tomasik allowing us to
-make this project in our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
+\qquad We would first like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
+on this project during our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
 and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors

### 2021-09-24 article/article.tex
conclusion

@@
 
-The new results we provide come from an extension of a template-based approach for Ramsey graphs
-and Schur numbers. Our theoretical work allowed to improve the lower bounds on Schur and Weak Schur numbers and have
-a better understanding of this relatively new approach. Furthermore we introduced the new quantities \(S^+(n)\) and
-\(\WS^+(n)\), which may have an interest as they are closely related to the problem at hand.
+We exhibit new templates for Schur and Ramsey numbers. We also generalize the concept of template to weak Schur numbers. 
+These templates provide new general inequalities of the form \(S(n+k) \geqslant a S(n) + b\) and \(\WS(n+k) \geqslant a S(n) + b\) 
+as well as new lower bounds for both Schur and weak Schur numbers. We also give a new lower bound \(\WS(6) \geqslant 646\) with 
+a method that can yield slight improvements for fixed values of \(n\) over lower bounds obtained with the inequality 
+\(\WS(n+1) \geqslant 4 S(n) + 2\).
 
 Given that the introduction of templates is quite recent, we expect the bounds to be improved as this special type of partition 
-becomes better understood and larger templates are found. For example, one may try to use
-algorithms based on randomness such as Monte-Carlo algorithms to find better templates.
+becomes better understood and larger templates are found. One may try to find better templates by using heuristics or 
+approximation algorithms, such as Monte-Carlo algorithms for instance.
 
@@
 start with large partitions for \(\WS(n)\). It also indicates that \(\WS(5)\) might need further investigation since the current lower 
-bound \(\WS(5) \geqslant 196\) \cite{ELIAHOU2012175} it was obtained by considering the same type of search space.
+bound \(\WS(5) \geqslant 196\) \cite{ELIAHOU2012175} was obtained by considering the same type of search space.
 
@@
 
-\qquad We would first like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
+\qquad First we would like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
 on this project during our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions

### 2021-09-24 article/article.tex
corrections x42

@@
 The concept of "template" is also generalized to weak Schur numbers. Finding new templates leads to explicit partitions 
-improving lower bounds as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). 
+improving lower bounds as well as the growth rate for Schur numbers, weak Schur numbers and multicolor Ramsey numbers \(R_n(3)\). 
 The new lower bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), 
@@
 
-\qquad First we would like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
+First we would like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
 on this project during our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions

### 2021-09-24 article/introduction.tex
abstract + future works + .!!!!
corrections x42

@@
 
-\qquad We are interested in partioning the set of integers \(\{1, ..., p\}\) into \(n\) subsets such that there is no 
+We are interested in partioning the set of integers \(\{1, ..., p\}\) into \(n\) subsets such that there is no 
 subset containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are 
@@
 
-\qquad Up to recently, the most efficient generic construction for Schur numbers was given by Abbott and Hanson 
+Up to recently, the most efficient generic construction for Schur numbers was given by Abbott and Hanson 
 \cite{AbbottHanson} in 1972 with a recursive construction. It gave the best lower bounds for all sufficiently large 
@@
 generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalties) for Schur numbers. 
-He also provides two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
+He also provided two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
 over previous lower bounds. Besides, these two inequalities do use the \textit{weakly} sum-free hypothesis.
@@
 	\hline
-	\hyperref[Schur]{\textbf{Our results}}  & & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
+	\hyperref[WeakSchur]{\textbf{Our results}}  & & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
 	\hline
@@
 
-\qquad Our main contribution is a generalization of the concept of template to weak Schur numbers. Our templates 
+Our main contribution is a generalization of the concept of template to weak Schur numbers. Our templates 
 provide new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special case 
@@
 \par
-In Section \ref{WeakSchur}, we generalize the concept of templates to weak Schur numbers 
+In Section \ref{WeakSchur}, we generalize the concept of template to weak Schur numbers 
 and provide new lower bounds for weak Schur numbers. We then use a different approach and give a new 
@@
 
-\qquad We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers. 
+We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers. 
 We denote \(\mathbb{N} = \{0, 1, 2, ...\}\) and \(\mathbb{N}^* =\mathbb{N} \backslash \{0\}\).
@@
 A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} if
-\[ \forall (a,b) \in A^2 \text{, } a+b \notin A\]
+\[ \forall (a,b) \in A^2 \text{, } a+b \notin A.\]
 \end{definition}
@@
 A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} if
-\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B\]
+\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B.\]
 \end{definition}
@@
 \begin{definition}
-Let \(n \in \mathbb{N}^*\). There exists a largest integer denoted by \(\WS (n)\) such that \([\![1, \WS (n)]\!]\)) 
+Let \(n \in \mathbb{N}^*\). There exists a largest integer denoted by \(\WS (n)\) such that \([\![1, \WS (n)]\!]\) 
 can be partitioned into \(n\) weakly sum-free subsets. \(\WS(n)\) is called the \(n\)\textsuperscript{th} weak Schur 

### 2021-09-24 article/schur.tex
abstract + future works + .!!!!
corrections x42

@@
 of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. A S-template 
-is then defined as a new object filling the role of the first line but with less, yet sufficiant, constraints which allow a linear 
-expansion of the partition.
+is then defined as a new object filling the role of the first line but with less, yet sufficient, constraints which allow for an 
+expansion of the partition using a sum-free partition.
 
@@
 \forall i \in [\![1, n-1]\!], \forall (x,y) \in A_i^2, x+y > p
-\Longrightarrow x+y-p \notin A_i
+\Longrightarrow x+y-p \notin A_i.
 \]
@@
 \begin{proposition}
-	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer such that \( [\![1, S^+(n)]\!]\) is a S-template with \(n\) colors. 
+	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer \(w\) such that there exists a S-template with 
+	width \(w\) and \(n\) colors. 
 	\(S^+(n)\) is well defined and verifies
 	\[
-	2S(n-1)+1 \leqslant S^+(n) \leqslant S(n)
+	2S(n-1)+1 \leqslant S^+(n) \leqslant S(n).
 	\]
@@
 \begin{proof}[\textsc{Proof.}]
-The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
-fact that a S-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets. \\
+The upper bound comes from the fact that a S-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) 
+into \(n\) sum-free subsets. The lower bound comes from Abbott and Hanson's construction \cite{AbbottHanson}. \\
 \end{proof}
@@
 We start by reminding the explicit construction of a sum-free partition with the use of a S-template and another sum free partition. 
-We apply this contruction stated by Rowley in the context of Ramsey numbers to the Schur numbers.
+We rephrase in terms of Schur numbers this contruction stated by Rowley in the context of Ramsey numbers \cite{RowleyRamsey}.
 
@@
 	Let \(n, k \in \mathbb{N}^*\). Then
-	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1 \]
+	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1.\]
 \end{corollary}
@@
 \textbf{Abbott and Hanson's construction}
+\label{figure:1}
 \vspace{1.7ex}
@@
 \end{center}
-\label{figure:1}
 \end{figure}
@@
 
-	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
+	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) q + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
 	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\)  can be interpreted as the row number of \(x\) and 
@@
 Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have
-\[ S(n+k) \geqslant S^+(n+1)S(k) + b\].
+\[ S(n+k) \geqslant S^+(n+1)S(k) + b.\]
 \end{proposition}
@@
 	Let \(n, k \in \mathbb{N}^*\). Then
-	\[ S^+(n+k) \geqslant S^+(n+1)S^+(k) \].
+	\[ S^+(n+k) \geqslant S^+(n+1)S^+(k).\]
 \end{corollary}
@@
 \par
-Here are the inequalities given by the current best S-templates. The \hyperref[S-templates]{templates} 
-corresponding to the third, fourth and fifth inequalities can be found in the appendix.
+The following six inequalities are given by the current best S-templates with \(n \leqslant 7\) colors.
 
@@
 	S(n + 2) \geqslant &~9\,S(n)  + 4 \label{S(n+2)}\\
-	S(n + 3) \geqslant &~33\,S(n) + 6 \label{S(n+3)}\\
+	S(n + 3) \geqslant &~33\,S(n) + 6 \label{S(n+3)}
 \end{align}
@@
 \end{align}
+
+\par The \hyperref[S-templates]{templates} corresponding to inequalities (\ref{S(n+3)}), (\ref{S(n+4)}) and 
+(\ref{S(n+5)}) can be found in the appendix.
 
@@
 Except for \(S(8)\), \(S(9)\) and \(S(13)\), the best lower bounds are obtained thanks to
-the third inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table
+the fifth inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table
 doesn't go any further, but the same inequality allows to improve the

### 2021-09-24 article/weakschur.tex
abstract + future works + .!!!!
corrections x42

@@
 for weak Schur numbers of Abbott and Hanson's construction for Schur numbers \cite{AbbottHanson}. By analogy with the previous section,
-we then introduce WS-templates, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
+we then introduce \textit{WS-templates}, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
 We find templates and use them to provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for 
@@
 \[
-\forall x \in [\![b + 1, a + b]\!], \pi(x) = x
+\forall x \in [\![b + 1, a + b]\!], \pi(x) = x.
 \]
@@
 \[
-\pi(x+\pi(y)) = \pi(x+y)
+\pi(x+\pi(y)) = \pi(x+y).
 \]
@@
 \[
-\pi(x+y)=x+\pi(y)
+\pi(x+y)=x+\pi(y).
 \]
@@
 \[
-\pi(\pi(x)+\pi(y))=\pi(x+y)
+\pi(\pi(x)+\pi(y))=\pi(x+y).
 \]
@@
 Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
-\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor\]
+\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor.\]
 \end{definition}
@@
 \[
-x=a\lambda(x)+\pi(x)-a
+x=a\lambda(x)+\pi(x)-a.
 \]
@@
 Let \((a,b)\in (\mathbb{N}^*)^2\) such that \(a>b\) and let \(x\in \mathbb{N}^*\). \\
-\(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+ a \mathds{1}_{ [\![0,b]\!]}(x \mod a)\)
+We have \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+ a \mathds{1}_{ [\![0,b]\!]}(x \mod a)\).
 
 \begin{itemize}
-\item if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)
-\item if \(x \mod a \leqslant b\) then \(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\)
+\item If \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\).
+\item If \(x \mod a \leqslant b\) then \(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\).
 \end{itemize}
@@
 \[
-\pi(x + y) = x + \pi(y)
+\pi(x + y) = x + \pi(y).
 \]
@@
 \[
-\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n)
+\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n).
 \]
@@
 	\end{array}
-	\right. \implies g(\pi(x + y)) \neq f(x)\)
+	\right. \implies g(\pi(x + y)) \neq f(x)\),
 \item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!], \left\{
@@
 	\end{array}
-	\right. \implies g(\pi(x + y)) \neq f(x)\)
+	\right. \implies g(\pi(x + y)) \neq f(x)\).
 \end{itemize}
@@
 Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have\\
-\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c\]
+\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c.\]
 \end{proposition}
@@
 \par
-Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{templates} 
+Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{template} 
 corresponding to the third inequality can be found in the appendix.

### 2021-09-28 article/schur.tex
Corrections

@@
 to the line number. This way the "blocks" act as safe areas for each other. We give here an example for \(p = 4\), 
-\(q = 9\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) (2 S(2) + 1) + S(2)\), both with Abbott and 
+\(q = 9\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) \left(2 S(2) + 1\right) + S(2)\), both with Abbott and 
 Hanson's construction and with a S-template which is not included in Abbott and Hanson's construction. In both cases, 
@@
 
-	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) q + u\) for certain integers \(\alpha \in \mathbb{Z}\) and 
+	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) q + u\) for certain integers \(\alpha \in \mathbb{N}^*\) and 
 	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\)  can be interpreted as the row number of \(x\) and 
@@
 	Let us assume that \(h(x+y) \leqslant n\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of function 
-	\(h\) and given that \(h(u) = h(v)\), we conclude \(f(u) = f(v)\). Two cases are to b distinguished according to the value of \(x + y\).
+	\(h\) and given that \(h(u) = h(v)\), we conclude \(f(u) = f(v)\). Two cases are to be distinguished according to the value of \(x + y\).
 
@@
 		\neq f(u)\), that is \(h(x + y) \neq h(x)\).
-	\item If \(u + v \leqslant p\), we write \(w = u + v \in [\![1, q]\!]\). Consequentely \(x+y = (\alpha + \beta- 2) q + w\). By definition, 
+	\item If \(u + v \leqslant q\), we write \(w = u + v \in [\![1, q]\!]\). Consequentely \(x+y = (\alpha + \beta- 2) q + w\). By definition, 
 		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the sum-free property of \(f\) implies \(f(w) \neq f(u)\), 
@@
 	Now we have \(h(x) = n + g(\alpha) = 
-	k + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As in the first case, distinguish between two cases according 
+	n + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As in the first case, distinguish between two cases according 
 	to the value of \(x + y\).
@@
 	\item  If \(u + v \leqslant q\), write \(w = u + v \in [\![1, q]\!]\). Then \(x+y = (\alpha + \beta- 2) q + w\). The sum-free 
-		property of \(f\) implies \(f(w) \neq f(u)\). Therefore \(f(w) \leqslant k\) and thus \(h(x + y) \leqslant n\). In particular,
+		property of \(f\) implies \(f(w) \neq f(u)\). Therefore \(f(w) \leqslant n\) and thus \(h(x + y) \leqslant n\). In particular,
 		given that \(h(x) \geqslant n + 1\), \(h(x + y) \neq h(x)\).
@@
 \label{prop:rafStemp}
-Let \((q, n) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a S-template with width \(q\) and \(n+1\) 
+Let \((q, n) \in \left(\mathbb{N}^* \right)^2\) and let \(f\) be a coloring associated to a S-template with width \(q\) and \(n+1\) 
 colors. Let \(b \in \mathbb{N}\) and assume there is a coloring \(g\) of 
@@
 the appendix). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
-improved by a wide margin. One may try to seek better templates by constraining less the search space and by using Monte-Carlo 
-methods, as in \cite{Bouzy2015AnAP}. This could be the subject of a future work.
+improved by a wide margin.
 

### 2021-09-30 article/schur.tex
modifs (nom nul mais pas d'inspi ¯\_(ツ)_/¯)

@@
 
-Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have
-\[ S(n+k) \geqslant S^+(n+1)S(k) + b.\]
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - q S(n))\), we have
+\[ S(n+k) \geqslant q S(k) + b.\]
 \end{proposition}
-This proposition corresponds to the fact that the hypotheses made on the coloring of the last row can be weakened and as a result, we can change the coloring on the last row to extend the previous partitions.
+This proposition corresponds to the fact that the hypotheses made on the coloring of the last row can be weakened because 
+the constraints in the definition of a S-template prevent a number from both being the sum of two of numbers of its own color 
+as well as creating a sum in its own color, the later of which is not always relevant on the last row given that it is not completely filled.
+As a result, we can change the coloring on \([\![ q S(k) + 1,  q S(k) + b]\!]\) (the last row) to extend the previous partitions.
 \newline

### 2021-09-30 article/weakschur.tex
modifs (nom nul mais pas d'inspi ¯\_(ツ)_/¯)

@@
 \[
-\lambda(x + y) = \lambda(x) + \lambda(y)
+\lambda(x + y) = \lambda(x) + \lambda(y).
 \]
@@
 	 & = & \lambda(x)+\lambda(y) -1 +1 ~~~~\text{since } \pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!] \\
-	 & =& \lambda(x)+\lambda(y)
+	 & =& \lambda(x)+\lambda(y).
 \end{array}
@@
 inequality \(\WS(n+4) \geqslant 127 S(n) + 68\). It was also found with the SAT solver. In order to reduce the search space, 
-we only looked for WS-templates of five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
+we only looked for WS-templates with five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
 special color was the last by order of appearance. We highly suspect that better WS-templates with \(n \geqslant 5\) 
 colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
-using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.
+with a different method,for instance with Monte-Carlo methods as in \cite{Bouzy2015AnAP}. This could be the suject of a 
+future work.
 
@@
 
-With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using (\ref{WS(n+1)}).
-Moreover, inequality (\ref{WS(n+3)}) gives new lower bounds for \(\WS(9)\), \(\WS(10)\), \(\WS(14)\) and \(\WS(15)\).
-
 \subsection{Another approach: \(\WS(6) \geqslant 646\)}
@@
 The weak Schur partitions obtained with WS-templates have an extremely regular structure. Therefore, one may 
-expect to find larger partitions by allowing more freedom in the structure of the partition while still preserving a structure 
+expect to find larger partitions by allowing more freedom in the structure of the partitions while still preserving a structure 
 somewhat close to a template-based partition thus reducing the search space to a manageable size.
@@
 
-However, trying out all of the 2\,447\,113\,088 Schur number 5-partitions (\cite{Heule2017}) one by one would not result in a 
+However, trying out all of the 2\,447\,113\,088 Schur number 5-partitions \cite{Heule2017} one by one would not result in a 
 reasonable computation time: it is necessary to test the construction on several partitions at once. We encoded the problem as a 
@@
 between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
-obtained with WS-templates. We reckon better WS-templates with \(n \geqslant 5\) colors can be found by making different assumptions 
+obtained with WS-templates; thus questionning the methods used and the assumptions made when obtaining these former lower 
+bounds. We reckon better WS-templates with \(n \geqslant 5\) colors can be found by making different assumptions 
 and using a different method (Monte-Carlo methods for instance).

### 2021-09-30 article/weakschur.tex
Encore des corrections

--- 2021-09-24 article/weakschur.tex
@@
 and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
-\(l = a - b - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = b - r\).
+\(l = a - q - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = q - r\).
 
@@
 	& & & & & & \Block{1-8}{\overbrace{\hphantom{---------------------------}}^{\mathcal{T}}} \\
-	& & & & & & 1 & 2 & ... & r & r + 1 & ... & b - 1 & b \\
+	& & & & & & 1 & 2 & ... & r & r + 1 & ... & q - 1 & q \\
 	\Block{5-1}{\mathcal{R} \left\{ \vphantom{\begin{array}{l} . \\ . \\ . \\ . \\ . \\ . \\ . \\ . \\ . \end{array}} \right.}
-	& a - l & a - l + 1 & ... & a - 1 & a & a + 1 & ... & a + r - 1 & a + r & a + r + 1 & ... & a + b - 1 & a + b \\
-	& 2 a - l & ... & ... & ... & 2 a & ... & ... & ... & 2 a + r & ... & ... & ... & 2 a + b \\
+	& a - l & a - l + 1 & ... & a - 1 & a & a + 1 & ... & a + r - 1 & a + r & a + r + 1 & ... & a + q - 1 & a + q \\
+	& 2 a - l & ... & ... & ... & 2 a & ... & ... & ... & 2 a + r & ... & ... & ... & 2 a + q \\
 	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
 	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
-	& p a - l & ... & ... & ... & p a & ... & ... & ... & p a + r & ... & ... & ... & p a + b \\
+	& p a - l & ... & ... & ... & p a & ... & ... & ... & p a + r & ... & ... & ... & p a + q \\
 	& & & & & & & & & & \Block{1-4}{\underbrace{\hphantom{--------------}}_{\mathcal{C}}} \\
@@
 	In this case, we do not have information about the color of \(\lambda(x+y)\). Thereby, we want to have
-	\(x+y \in \mathcal{C}\). A simple solution is to limit the horizontal movement, that is if the sum changes line
-	(that is its line number is different from \(\lambda(x) + \lambda(y)\)), not to move too far from \((\lambda(x)
-	+ \lambda(y)) a\) so that the sum stays in \(\mathcal{C}\). There, the maximal displacement to the left (resp.
+	\(x+y \in \mathcal{C}\). A simple solution is to limit the horizontal movement made by summing the two integers.
+	That is, when the sum's line number is different from \(\lambda(x) + \lambda(y)\), not to move too far from \((\lambda(x)
+	+ \lambda(y)) a\) so that \(x+y\) stays in \(\mathcal{C}\). There, the maximal displacement to the left (resp.
 	to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left is then expressed
@@
 	 & = & \left \lfloor \dfrac{a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a - b - 1}{a} \right \rfloor + 1 \vspace{1mm} \\
-	 & = & \lambda(x) + \lambda(y) - 1 \left \lfloor \dfrac{\pi(x) + \pi(y) - b - 1}{a}\right\rfloor \\
+	 & = & \lambda(x) + \lambda(y) - 1 + \left \lfloor \dfrac{\pi(x) + \pi(y) - b - 1}{a}\right\rfloor \\
 	 & = & \lambda(x)+\lambda(y) -1 +1 ~~~~\text{since } \pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!] \\
@@
 However, WS-templates being more sophisticated than S-templates, the definition of \(\WS^+(n)\)
-is slighty more complicted.
+is slighty more complicated.
 
@@
 \end{definition}
-The following proposition briefly shows how \(\WS^+(n)\) compares to weak Schur numers.
+The following proposition briefly shows how \(\WS^+(n)\) compares to weak Schur numbers.
 \begin{proposition}
@@
 special color was the last by order of appearance. We highly suspect that better WS-templates with \(n \geqslant 5\) 
-colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
-using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.
+colors can be found but one would have not to use the above assumptions.
 

### 2021-09-30 article/weakschur.tex
fear of the dark

@@
 the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
-given in this paper.
+given in this article.
 
@@
 projection on the first line, denoted by \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\). A simple solution is to color \(x\) with the same color
-as \(\tilde{\pi}(x)\) in the weakly sum-free coloring of \([\![1,q]\!]\). As long as \(2b \leqslant a + r\) (not going two far to the right) and there
+as \(\tilde{\pi}(x)\) in the weakly sum-free coloring of \([\![1,q]\!]\). As long as \(2q \leqslant a + r\) (not going two far to the right) and there
 is no \(x \in \tilde{\pi}(\mathcal{C})\) such that \(2x \in \tilde{\pi}(\mathcal{C})\) (so that we do not have a sum in \(\mathcal{C}\) when
@@
 \par
-By definition of \(h\), \(h(x) \neq h(y)\).\\
+By definition of function \(h\), \(h(x) \neq h(y)\).\\
 
@@
 do not have because of the tail, especially if the special color appears in the tail as well. Thus allowing to have a coloring on the
-first row different from the coloring of the other rows would weaken the constraints. Acutally, one may even go further by
+first row different from the coloring of the other rows would weaken the constraints. Actually, one may even go further by
 noticing that on the one hand the first (ordered) color of the sum-free partition used for the extension procedure has more
@@
 special color was the last by order of appearance. We highly suspect that better WS-templates with \(n \geqslant 5\) 
-colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
-with a different method,for instance with Monte-Carlo methods as in \cite{Bouzy2015AnAP}. This could be the suject of a 
-future work.
+colors can be found but one would have not to use the above assumptions.
 

### 2021-10-06 article/article.tex
affiliations modifiees

@@
 
-\address[1]{\textit{CentraleSup\'elec}, Universit\'e Paris-Saclay}
-\address[2]{LRI, \textit{CentraleSup\'elec}, Universit\'e Paris-Saclay, F-91405, Orsay, France}
+\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190 Gif-sur-Yvette, France}
+\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}
 
@@
 
-First we would like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
-on this project during our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
+This study results from a long-term project performed within the framework of the Project Cluster "Training for Research" of CentraleSupélec. 
+We would like to address warm thanks to Fred Rowley who kindly answered our many questions
 and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors

### 2021-10-07 article/article.tex
modifs sans WS

--- 2021-09-24 article/article.tex
@@
 
-We exhibit new templates for Schur and Ramsey numbers. We also generalize the concept of template to weak Schur numbers. 
+We have produced new templates for Schur and Ramsey numbers. We also have generalized the concept of template to weak Schur numbers. 
 These templates provide new general inequalities of the form \(S(n+k) \geqslant a S(n) + b\) and \(\WS(n+k) \geqslant a S(n) + b\) 
-as well as new lower bounds for both Schur and weak Schur numbers. We also give a new lower bound \(\WS(6) \geqslant 646\) with 
+as well as new lower bounds for both Schur and weak Schur numbers. We have given a new lower bound \(\WS(6) \geqslant 646\) with 
 a method that can yield slight improvements for fixed values of \(n\) over lower bounds obtained with the inequality 
@@
 Given that the introduction of templates is quite recent, we expect the bounds to be improved as this special type of partition 
-becomes better understood and larger templates are found. One may try to find better templates by using heuristics or 
+becomes better understood and larger templates are found. One may try to produce better templates by using heuristics or 
 approximation algorithms, such as Monte-Carlo algorithms for instance.
@@
 The best lower bound \(\WS(6) \geqslant 583\) achieved with a computer search using Monte-Carlo methods 
-\cite{EliahouBook} is significantly lower than those obtained with a template-like structure (\(\WS(6) \geqslant 642\) \cite{RowleyWS}, 
-\(\WS(6) \geqslant 646\) in the present article). We have evidence that 583 is the maximal value in the search space considered by 
+\cite{EliahouBook} is significantly lower than those obtained with a template-like structure: \(\WS(6) \geqslant 642\) \cite{RowleyWS}, 
+\(\WS(6) \geqslant 646\). We have evidence that 583 is the maximal value in the search space considered by 
 \cite{EliahouBook,Bouzy2015AnAP,Rafilipojaona}. Therefore, it questions the assumption that large partitions for \(\WS(n+1)\) 

### 2021-10-07 article/introduction.tex
modifs sans WS

@@
 subset containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are 
-\textit{sum-free}. If we add the hypothesis \(x \neq y\), we say the subsets are \textit{weakly sum-free}. The 
-greatest \(p\) for which there exists a partition into \(n\) sum-free subsets is called the \(n^{\text{th}}\) Schur 
+\textit{sum-free}. If we lessen the above constraint by only considering integers \(x,y\) such that \(x \neq y\), we say the subsets are \textit{weakly sum-free}. The 
+greatest \(p\) for which there is a partition into \(n\) sum-free subsets is called the \(n^{\text{th}}\) Schur 
 number and is denoted \(S(n)\) \cite{Schur1917}. Likewise for weakly sum-free partitions we define \(\WS(n)\) 
@@
 \cite{AbbottHanson} in 1972 with a recursive construction. It gave the best lower bounds for all sufficiently large 
-numbers. No equivalent was known for weak Schur numbers and as a result the best known partitions for large 
-weak Schur numbers did not use the weakly sum-free hypothesis.
+numbers. No equivalent was known for weak Schur numbers and, as a result, the best known partitions for large 
+weak Schur numbers did not use the \textit{weakly} sum-free property.
 
 \par
-As for smaller weak Schur numbers, the best lower bounds were obtained by conducting a computer search. Eliahou 
+As for smaller weak Schur numbers, the best lower bounds were obtained by computations. Eliahou 
 \cite{EliahouBook}, Bouzy \cite{Bouzy2015AnAP} and Rafilipojaona \cite{Rafilipojaona} improved the lower 
@@
 generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalties) for Schur numbers. 
-He also provided two inequalities for weak Schur numbers \cite{RowleyWS} that yield significant improvements 
-over previous lower bounds. Besides, these two inequalities do use the \textit{weakly} sum-free hypothesis.
+He also provided two inequalities for weak Schur numbers \cite{RowleyWS}. Besides, these two inequalities do use the \textit{weakly} sum-free property.
 
-\par The hereunder tables recap the lower bounds respectively for Schur and weak Schur numbers. Gray cells 
+\par The hereunder tables recap the lower bounds for Schur and weak Schur numbers, respectively. Gray cells 
 indicate the exact values.
@@
 Our main contribution is a generalization of the concept of template to weak Schur numbers. Our templates 
-provide new lower bounds (and inequalities) for weak Schur numbers. This construction also includes as a special case 
-a construction similar to Abbott and Hanson's \cite{AbbottHanson}, but this time for \textit{weak} Schur numbers.
+provide new lower bounds (and inequalities) for weak Schur numbers. As a special case, our construction also includes  
+a construction similar to Abbott and Hanson's \cite{AbbottHanson}, but for \textit{weak} Schur numbers this time.
 
 \par
-In Section \ref{Schur}, we explain Rowley's template-based construction in the context of 
+In Section \ref{Schur}, we explain Rowley's template-based construction for 
 Schur numbers. Then, we give new templates, thus providing new lowers bounds and inequalities as well as 
@@
 In Section \ref{WeakSchur}, we generalize the concept of template to weak Schur numbers 
-and provide new lower bounds for weak Schur numbers. We then use a different approach and give a new 
+and provide new lower bounds for weak Schur numbers. Then, we use a different approach and give a new 
 lower bound for \(\WS(6)\).
@@
 \par
-We now introduce notations and definitions we use throughout this article.
+Now, we introduce notations and definitions used throughout this article.
 
@@
 We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers. 
-We denote \(\mathbb{N} = \{0, 1, 2, ...\}\) and \(\mathbb{N}^* =\mathbb{N} \backslash \{0\}\).
+The set of positive natural numbers is denoted by \(\mathbb{N}^* =\mathbb{N} \backslash \{0\}\).
 
@@
 \par
-Schur proved in \cite{Schur1917} that given a number of subsets \(n\), there exists a value of \(p\)
-such that there exists no partition of \([\![1,q]\!]\) into \(n\) sum-free subsets for any \(q \geqslant p\). A similar
-property holds for weakly sum-free subsets \cite{Irving1973}. These observations lead to the following definitions.
+Schur proved \cite{Schur1917} that given a number of subsets \(n\), there is a value of \(p\)
+such that \([\![1,q]\!]\) cannot be partionned into \(n\) sum-free subsets for \(q \geqslant p\). A similar
+property holds for weakly sum-free subsets \cite{Irving1973}. These observations lead to the following definitions
+written for \(n \in \mathbb{N}^*\):
 
 \begin{definition}
-Let \(n \in \mathbb{N}^*\). There exists a largest integer denoted by \(S(n)\) such that \([\![1, S(n)]\!]\) can be
+There is a largest integer denoted by \(S(n)\) such that \([\![1, S(n)]\!]\) can be
  partitioned into \(n\) sum-free subsets. \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number}.
@@
 \begin{definition}
-Let \(n \in \mathbb{N}^*\). There exists a largest integer denoted by \(\WS (n)\) such that \([\![1, \WS (n)]\!]\) 
+There is a largest integer denoted by \(\WS (n)\) such that \([\![1, \WS (n)]\!]\) 
 can be partitioned into \(n\) weakly sum-free subsets. \(\WS(n)\) is called the \(n\)\textsuperscript{th} weak Schur 
@@
 
-Given a partition of \([\![1, p]\!]\) into \(n\) subsets, we generally denote these subsets \(A_1, ..., A_n\). We also denote
+Subsets of an \(n\)-partition are denoted \(A_1, ..., A_n\). The smallest element of \(A_i\) is denoted  
 \(m_i = \min(A_i)\). By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). However, if not specified we do 
-not make this hypothesis since we do not always consider partitions in which every subset plays a symmetric role.
+not make this assumption since we do not always consider partitions in which every subset plays a symmetric role.
+
+A partition may be seen as a number coloring.
 
 \begin{definition}
-We sometimes refer to a partitition as a coloring. The coloring associated to a partition \(A_1, ..., A_n\) of 
+The coloring associated to a partition \(A_1, ..., A_n\) of 
 \([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition associated to

### 2021-10-07 article/schur.tex
rajout d'une lettre
modifs sans WS

@@
 
-In this section, we use Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur 
-numbers. In order to improve lower bounds for Schur and Ramsey numbers, he introduces special sum-free 
+We use Rowley's template-based constructions \cite{RowleyRamsey} for Schur 
+numbers. To improve lower bounds for Schur and Ramsey numbers, he has introduced special sum-free 
 partitions verifying some additional properties which can be extended using a method generalizing Abbott and 
-Hanson's construction \cite{AbbottHanson}. He named these partitions "templates", and we keep this name in 
-the entire article. We then find new templates and use them to provide new lower bounds for Schur numbers.
+Hanson's construction \cite{AbbottHanson}. He called these partitions "templates", and we keep this nomination. 
+Then, we propose new templates and use them to produce new lower bounds for Schur numbers.
 
@@
 We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
-of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. A S-template 
-is then defined as a new object filling the role of the first line but with less, yet sufficient, constraints which allow for an 
-expansion of the partition using a sum-free partition.
+of \hyperref[figure:1]{Figure 1} not as a combination of two blocs, like in \cite{AbbottHanson} but as a whole, single construction. 
+An S-template is then defined as a new object playing the role of the first line but with less, yet sufficient, 
+constraints which allow for an expansion of the partition using a sum-free partition.
 
 \begin{definition}
-Let \((p,n) \in (\mathbb{N}^*)^2\). A S-template with width \(p\) and \(n\) colors is defined as a partition of 
+Let \((p,n) \in (\mathbb{N}^*)^2\). An S-template with \(n\) colors is defined as a partition of 
 \([\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) verifying for all subsets but \(A_n\)
-\[
-\forall i \in [\![1, n-1]\!], \forall (x,y) \in A_i^2, x+y > p
+\begin{equation}
+\label{eq:constemp}
+\forall (x,y) \in A_i^2, x+y > p
 \Longrightarrow x+y-p \notin A_i.
-\]
+\end{equation}
+The integer \(p\) is called the \textit{width} of the template.
 \end{definition}
 
-Here \(n\) can be seen as a "special" color in the sense that we do not impose this above additionnal constraint on this color. 
+Here \(n\) can be seen as a "special" color in the sense that it is no constrained by \ref{eq:constemp}.
 However, note that \(n\) is not necessarily the last color by order of appearance, any color can play this role.
@@
 \begin{proof}[\textsc{Proof.}]
-The upper bound comes from the fact that a S-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) 
+The upper bound comes from the fact that an S-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) 
 into \(n\) sum-free subsets. The lower bound comes from Abbott and Hanson's construction \cite{AbbottHanson}. \\
@@
 
-We start by reminding the explicit construction of a sum-free partition with the use of a S-template and another sum free partition. 
+We start by reminding the explicit construction of a sum-free partition with the use of an S-template and another sum free partition. 
 We rephrase in terms of Schur numbers this contruction stated by Rowley in the context of Ramsey numbers \cite{RowleyRamsey}.
@@
 \label{thm:Stemp}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
-	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there exists a partition of \([\![1,pq+m_{n+1}
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is an S-template with width \(q\) and \(n+1\) colors 
+	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there is a partition of \([\![1,pq+m_{n+1}
 	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
@@
 
-Setting \(q = S^+(n+1)\) and \(p = S(k)\) yields the following corollary.
-
-\begin{corollary}
-\label{cor:ineqS}
-	Let \(n, k \in \mathbb{N}^*\). Then
-	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1.\]
-\end{corollary}
-
-The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. They vertically 
-extend a sum-free partition by repeating it and they use an other sum-free partition to color the other half according 
-to the line number. This way the "blocks" act as safe areas for each other. We give here an example for \(p = 4\), 
+The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. They 
+extended a sum-free partition vertically by repeating it. Next, they used another sum-free partition to color the other half according 
+to the line number, as in \hyperref[figure:1]{Figure 1}. We give an example for \(p = 4\), 
 \(q = 9\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) \left(2 S(2) + 1\right) + S(2)\), both with Abbott and 
-Hanson's construction and with a S-template which is not included in Abbott and Hanson's construction. In both cases, 
+Hanson's construction and with an S-template which is not included in Abbott and Hanson's construction. In both cases, 
 the special color is grey.
@@
 \end{figure}
-In the general construction with S-templates, the special color no longer necessarily contains consecutive 
-numbers. However, the special color is still replaced by the colors of the sum-free partition according to the 
+In the general construction with S-templates, the special color may not paint consecutive 
+numbers any longer. However, the special color is still replaced by the colors of the sum-free partition according to the 
 line number and the other colors are still vertically extended.
@@
 
-We now proceed to prove Theorem \ref{thm:Stemp}.
+Now, we prove Theorem \ref{thm:Stemp}.
 
 \begin{proof}[\textsc{Proof.}]
-	Denote by \(f\) the coloring associated to the \(S\)-template with width \(q\) and \(g\) the one associated 
-	to the sum-free partition of \([\![1,p]\!]\); where \(f : [\![1,q]\!] \longrightarrow [\![1,n+1]\!]\) and 
+	Let \(f\) and \(g\) be colorings associated to the S-template with width \(q\) and the sum-free partition of 
+	\([\![1,p]\!]\), respectively: \(f : [\![1,q]\!] \longrightarrow [\![1,n+1]\!]\) and 
 	\(g : [\![1,p]\!] \longrightarrow [\![1,k]\!]\).
@@
 	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) q + u\) for certain integers \(\alpha \in \mathbb{N}^*\) and 
-	\(u \in [\![1,q]\!]\). This decomposition is of course unique. \(\alpha\)  can be interpreted as the row number of \(x\) and 
-	\(u\) as the collumn number of \(x\). A new coloring is define as follows:
+	\(u \in [\![1,q]\!]\). Obviously, this decomposition unique. Coefficients \(\alpha\) and \(u\) may be interpreted as the row index of \(x\) and 
+	as line and column coordinates of \(x\) in the template. A new coloring is defined as:
 	\[
@@
 	\par
-	We now prove that \(h\) is a sum-free coloring. Let \(x,y \in [\![1,pq + m_{n+1}-1]\!]\) such that \(h(x) = h(y)\) 
+	Now, we prove that \(h\) is a sum-free coloring. Let \(x,y \in [\![1,pq + m_{n+1}-1]\!]\) such that \(h(x) = h(y)\) 
 	and \(x+y \leqslant pq+m_{n+1}-1\). We claim that \(h(x+y) \neq h(x)\). We write \(x = (\alpha - 1) q + u\) and 
@@
 	Now we have \(h(x) = n + g(\alpha) = 
-	n + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As in the first case, distinguish between two cases according 
+	n + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As above, we distinguish between two cases according 
 	to the value of \(x + y\).
@@
 \end{proof}
+
+Setting \(q = S^+(n+1)\) and \(p = S(k)\) in theorem \ref{thm:Stemp} yields the following corollary.
+
+\begin{corollary}
+\label{cor:ineqS}
+	Let \(n, k \in \mathbb{N}^*\). Then
+	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1.\]
+\end{corollary}
 
@@
 This proposition corresponds to the fact that the hypotheses made on the coloring of the last row can be weakened because 
-the constraints in the definition of a S-template prevent a number from both being the sum of two of numbers of its own color 
-as well as creating a sum in its own color, the later of which is not always relevant on the last row given that it is not completely filled.
+the constraints in the definition of a S-template prevent a number from: 
+\begin{itemize}
+\item being the sum of two of numbers of its own color. 
+\item creating a sum in its own color. 
+\end{itemize}
+The later is not always relevant on the last row given that it is not completely filled.
 As a result, we can change the coloring on \([\![ q S(k) + 1,  q S(k) + b]\!]\) (the last row) to extend the previous partitions.
@@
 A S-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
-from this template by applying the extension procedure with a sum-free partition of length 1 is symmetric. 
+from this template by applying the extension procedure of theorem \ref{thm:Stemp} with a sum-free partition of length 1 is symmetric. 
 \end{definition}
 
-We produced S-templates using a SAT solver, hence providing lower bound on \(S^+\) and inequalities 
-of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing the largest value of 
-\((a, b)\) (in the lexicographic order). When the number of colors exceeded five, in order to reduce the search space we 
+We produced S-templates using a SAT solver \cite{Lingeling2017}, hence providing lower bound on \(S^+\) and inequalities 
+of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing us with the largest value of 
+\((a, b)\) (in the lexicographic order). In order to reduce the search space when the number of colors exceeded 
+five we 
 only looked for symmetric S-templates, we assumed that the special color was the last color to appear and we constrained 
@@
 The following six inequalities are given by the current best S-templates with \(n \leqslant 7\) colors.
-
 \begin{align}
@@
 \par The \hyperref[S-templates]{templates} corresponding to inequalities (\ref{S(n+3)}), (\ref{S(n+4)}) and 
-(\ref{S(n+5)}) can be found in the appendix.
+(\ref{S(n+5)}) are listed in Appendix \ref{S-templates}.
 
@@
 size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 
-the appendix). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
+Appendix \ref{S-templates}). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
 improved by a wide margin.
@@
 the fifth inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table
-doesn't go any further, but the same inequality allows to improve the
-lower bounds for every \( n \geqslant 15 \).
+does not go any further, but the same inequality allows one to improve the
+lower bounds for \( n \geqslant 15 \).
 
@@
 
-In this section, we first formalized Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur numbers 
-by introducing S-templates as well as a new sequence, \(S^+\). We provided relations between \(S^+\) and \(S\) then 
-stated Rowley's construction method in the context of Schur numbers. We found new S-templates allowing us to obtain 
+First, we formalized Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur numbers 
+by introducing S-templates as well as a new sequence, \(S^+\). We found new S-templates allowing us to obtain 
 new lower bounds for schur numbers. One may notice that we mostly gave only lower bounds for \(S^+\). It should be possible to 
-find better S-templates by making different assumptions or using a different method (Monte-Carlo methods for instance).
+find better S-templates by making different assumptions or using a different method (Monte-Carlo methods, for instance).
 
@@
 In the next section, we provide similar results for weak Schur numbers. We introduce WS-templates and a corresponding sequence, 
-\(\WS^+\). We then derive similar relations and a construction method allowing us to find new lower bounds for weak Schur numbers.
+\(\WS^+\). Then, we derive similar relations and a construction method allowing us to find new lower bounds for weak Schur numbers.

### 2021-10-13 article/schur.tex
modifs ws + les there is / are arrivent

@@
 \(q = 9\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) \left(2 S(2) + 1\right) + S(2)\), both with Abbott and 
-Hanson's construction and with an S-template which is not included in Abbott and Hanson's construction. In both cases, 
-the special color is grey.
+Hanson's construction (\hyperref[figure:1]{Figure 1}) and with an S-template which is not included in Abbott and Hanson's construction 
+(\hyperref[figure:2]{Figure 2}). In both cases, the special color is grey.
 
@@
 \textbf{S-template construction}
+\label{figure:2}
 \setlength{\tabcolsep}{1.5ex}
@@
 \caption{Visualisation of a template-based construction}
-\label{figure:2}
 
@@
 
-	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) q + u\) for certain integers \(\alpha \in \mathbb{N}^*\) and 
-	\(u \in [\![1,q]\!]\). Obviously, this decomposition unique. Coefficients \(\alpha\) and \(u\) may be interpreted as the row index of \(x\) and 
-	as line and column coordinates of \(x\) in the template. A new coloring is defined as:
+	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) q + u\) for certain integers \(\alpha \in \mathbb{N}^*\) 
+	and \(u \in [\![1,q]\!]\). Obviously, this decomposition unique. Coefficients \(\alpha\) and \(u\) may be interpreted as line 
+	and column coordinates of \(x\) in the template. We define a coloring \(h\) of \([\![1,pq+m_{n+1}-1]\!]\) using \( [\![1,n+k]\!]\) colors:
 	\[
@@
 
+\begin{proof}[\textsc{Proof.}]
+The idea is the same as in the Theorem \ref{thm:Stemp}. The only difference is the S-template property inherited 
+from the second S-template. \\
+\end{proof}
+
 The inequality associated with this theorem is given by:
@@
 \end{corollary}
-
-\begin{proof}[\textsc{Proof.}]
-The idea is the same as in the Theorem \ref{thm:Stemp}. The only difference is the S-template property inherited 
-from the second S-template. \\
-\end{proof}
 
@@
 
-We produced S-templates using a SAT solver \cite{Lingeling2017}, hence providing lower bound on \(S^+\) and inequalities 
-of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing us with the largest value of 
-\((a, b)\) (in the lexicographic order). In order to reduce the search space when the number of colors exceeded 
-five we 
-only looked for symmetric S-templates, we assumed that the special color was the last color to appear and we constrained 
-the \(m_c\)'s out of being too small. Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.
+We produced S-templates using the lingeling SAT solver \cite{Lingeling2017}, hence providing lower bound on 
+\(S^+\) and inequalities of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing us with 
+the largest value of \((a, b)\) (in the lexicographic order). In order to reduce the search space when the number 
+of colors exceeded five we only looked for symmetric S-templates, we assumed that the special color was the last 
+color to appear and we constrained the \(m_c\)'s out of being too small. Details concerning the encoding as a SAT 
+problem can be found in \cite{Heule2017}.
 
@@
 \par The \hyperref[S-templates]{templates} corresponding to inequalities (\ref{S(n+3)}), (\ref{S(n+4)}) and 
-(\ref{S(n+5)}) are listed in Appendix \ref{S-templates}.
+(\ref{S(n+5)}) are listed in \ref{S-templates}.
 
@@
 size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 
-Appendix \ref{S-templates}). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
+\ref{S-templates}). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
 improved by a wide margin.

### 2021-10-13 article/weakschur.tex
modifs ws + les there is / are arrivent

@@
 
-In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
-for weak Schur numbers of Abbott and Hanson's construction for Schur numbers \cite{AbbottHanson}. By analogy with the previous section,
-we then introduce \textit{WS-templates}, standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). 
-We find templates and use them to provide new lower bounds for weak Schur numbers. Finally, we give a short explanation for 
-the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
-given in this article.
+We generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS}. We give an analogous for weak Schur numbers of Abbott 
+and Hanson's construction for Schur numbers \cite{AbbottHanson}. Then, as in the previous section, we introduce \textit{WS-templates}, 
+standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). We find templates and use them to provide 
+new lower bounds for weak Schur numbers. Finally, we give a short explanation for the new lower bound \(\WS(6) \geqslant 646\) which 
+was not directly obtained with a template, contrary to the other lower bounds given in this article.
 
@@
 \begin{sloppypar}
-Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
-subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free
-subsets then there exists a partition of \({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\)
-weakly sum-free subsets.
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) and
+a sum-frree \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \({[\![1,p(q+\left \lceil \frac{q}{2} \right 
+\rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
 \end{sloppypar}
@@
 
-In particular, by setting \(q = \WS (n)\) and \(p = S(k)\) in Theorem \ref{thm:WS-ab}, one obtains the following corollary.
-
-\begin{corollary}
-\label{cor:ineqWS-S}
-\( \forall (n,k) \in (\mathbb{N}^*)^2 \text{, } \WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \displaystyle \frac{\WS (n)}{2}
-\right \rceil +1 \right) + \WS (n)\)
-\end{corollary}
-
-This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers. This formula includes
-the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\), this formula does not give new lower bounds.
-
-\begin{remark}
-The inequality from Corollary \ref{cor:ineqWS-S} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
-odd in Theorem \ref{thm:WS-ab}). However, it lengthens the proof and it is never useful in practice.
-\end{remark}
-
 Given that Theorem \ref{thm:WS-ab} will appear as a particular case of a more general theorem after the introduction of
-templates for weak Schur numbers, we only give here an intuitive explanation of the demonstration; a formal
-\hyperref[PreuveThm]{proof} using templates for weak Schur numbers is provided in Subsection \ref{ConstructionWS}.
+templates for weak Schur numbers, we only outline the demonstration; a \hyperref[PreuveThm]{proof} using templates 
+for weak Schur numbers is in Subsection \ref{ConstructionWS}.
 
@@
 \begin{itemize}
-	\item \(\mathcal{T}\) (the "tail"): the integers from 1 to \(q\). NB: this is line number 0.
-	\item \(\mathcal{R}\) (the "rows"): the integers in columns \(-l\) to \(+r\) (excluding  \(\mathcal{T}\)).
-	\item \(\mathcal{C}\) (the "columns"): the integers in the last \(w\) columns (excluding  \(\mathcal{T}\)).
+	\item \(\mathcal{T}\) (the "tail"): In the row indexed by 0: numbers from \([\![1,q]\!]\).
+	\item \(\mathcal{R}\) (the "rows"): the integers in columns \(-l\) to \(+r\).
+	\item \(\mathcal{C}\) (the "columns"): the integers in the last \(w\) columns.
 \end{itemize}
 
-Like S-templates, \(\mathcal{R}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with
-this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the
+Note that with this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to the
 sum of the columns modulo \(a\).
@@
 \par
-In this block,  we use the colors \(n + 1, ..., n + k\). We color an integer \(x\) according to its line number (written \(\lambda(x)\)).
-For every \(x \in \mathcal{R}\), we color \(x\) with \(n + c\) where \(c\) is the color of \(\lambda(x)\) in the sum-free coloring of  \([\![1,p]\!]\).
+We use the colors \(n + 1, ..., n + k\) in this block. We color an integer \(x\) according to its line number \(\lambda(x)\).
+For any \(x \in \mathcal{R}\), we color \(x\) with \(n + c\) where \(c\) is the color of \(\lambda(x)\) in the sum-free coloring of  \([\![1,p]\!]\).
 Let \((x, y) \in \mathcal{R}^2\). The cases are twofold.
@@
 	\item \underline{\(\lambda(x+y) = \lambda(x) + \lambda(y)\)} \\
-	In this case, we use the sum-free property of the coloring of \([\![1,p]\!]\) (in block \(\mathcal{C}\), we only
-	use colors \(1, ..., n\)).
+	If \(x + y\in \mathcal{R}\), we use the sum-free property of the coloring of \([\![1,p]\!]\). Otherwise, \(x + y\in \mathcal{C}\) which 
+	is fine because we only use colors \(1, ..., n\) in block \(\mathcal{C}\).
 	\item \underline{\(\lambda(x+y) \neq \lambda(x) + \lambda(y)\)} \\
 	In this case, we do not have information about the color of \(\lambda(x+y)\). Thereby, we want to have
-	\(x+y \in \mathcal{C}\). A simple solution is to limit the horizontal movement made by summing the two integers.
-	That is, when the sum's line number is different from \(\lambda(x) + \lambda(y)\), not to move too far from \((\lambda(x)
-	+ \lambda(y)) a\) so that \(x+y\) stays in \(\mathcal{C}\). There, the maximal displacement to the left (resp.
-	to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left is then expressed
-	as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written
+	\(x+y \in \mathcal{C}\). A simple solution is to limit the horizontal displacement made by summing the two integers.
+	That is, when the sum's row number is different from \(\lambda(x) + \lambda(y)\), to upper bound 
+	\(|x + y - (\lambda(x) + \lambda(y)) a|\) so that \(x+y\) stays in \(\mathcal{C}\). There, the maximal displacement 
+	to the left (resp. to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left is then 
+	expressed as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written
 	as \(\max(l, r) \leqslant w\).
@@
 \par
-In this block,  we use colors \(1, ..., n\). We color an integer \(x\) according to its column number, denoted by \(\tilde{\pi}(x)\). It is linked to the
-projection on the first line, denoted by \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\). A simple solution is to color \(x\) with the same color
-as \(\tilde{\pi}(x)\) in the weakly sum-free coloring of \([\![1,q]\!]\). As long as \(2q \leqslant a + r\) (not going two far to the right) and there
-is no \(x \in \tilde{\pi}(\mathcal{C})\) such that \(2x \in \tilde{\pi}(\mathcal{C})\) (so that we do not have a sum in \(\mathcal{C}\) when
-taking two numbers in the same column), the colors \(1, ..., n\) are sum-free.
+In this block, we use colors \(1, ..., n\). We color an integer \(x\) according to its projection on the first row \(\pi(x)\) offeset by \(a\), 
+that is its column number. A simple solution is to color \(x\) with the same color as \(\pi(x) - a\) in the weakly sum-free coloring of 
+\([\![1,q]\!]\). As long as \(2q \leqslant a + r\) (not going two far to the right) and there is no \(x \in \pi(\mathcal{C}) - a\) such that 
+\(2x \in \pi(\mathcal{C}) - a\) (so that we do not have a sum in \(\mathcal{C}\) when taking two numbers in the same column), 
+the colors \(1, ..., n\) are sum-free.
 
-In particular, taking \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) works, thus obtaining the above theorem.\\
+Setting \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) satsfies these 
+constraints: this is the construction corresponding to Theorem \ref{thm:WS-ab}. \\
+
+By setting \(q = \WS (n)\) and \(p = S(k)\) in Theorem \ref{thm:WS-ab}, one obtains the following corollary.
+
+\begin{corollary}
+\label{cor:ineqWS-S}
+\(\WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \displaystyle \frac{\WS (n)}{2} \right \rceil +1 \right) + \WS (n)\)
+for all \((n,k) \in (\mathbb{N}^*)^2\).
+\end{corollary}
+
+This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers 
+\cite{AbbottHanson}. This formula also includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\), 
+the formula from corollary \ref{cor:ineqWS-S} does not give new lower bounds.
+
+\begin{remark}
+The inequality from Corollary \ref{cor:ineqWS-S} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
+odd in Theorem \ref{thm:WS-ab}). However, it lengthens the proof and it is never useful in practice.
+\end{remark}
 \par
-As in the previous section, we now introduce WS-templates and the sequence \(\WS^+\) in order to generalize the above construction.
+Now, we introduce WS-templates and the sequence \(\WS^+\) in order to generalize the above construction.
 
@@
 Note that the special color \(n\) is not necessarily the last color by order of appearance, any color can play this role.
-We now introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.
-However, WS-templates being more sophisticated than S-templates, the definition of \(\WS^+(n)\)
-is slighty more complicated.
+Now, we introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.
 
@@
 
-Having established these properties, we now have everything we need to state and prove our main result. We proceed to do so
-in the next subsection.
+Having established these properties, we prove our main result.
 
@@
 
-Theorem \ref{thm:Stemp} provides a way to extend a S-template into a larger Schur partitions using other Schur partitions. Likewise, a WS-template can 
-be extended into larger weak Schur partitions by using Schur partitions. This is the object of the following theorem.
+Theorem \ref{thm:Stemp} describes a manner to extend a S-template into a larger Schur partitions using other Schur 
+partitions. Likewise, a WS-template can be extended into larger weak Schur partitions by using Schur partitions. This 
+is the object of the following theorem.
 
@@
 \label{thm:WStemp}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\)
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there are a partition of \([\![1,p]\!]\)
 into \(k\) sum-free subsets and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
-then there exists a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
+then there is a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
 \end{theorem}
-
-In particular, by setting \(p = S(k)\) and \(a = \WS^+(n + 1)\) in Theorem \ref{thm:WStemp}, the next corollary follows.
-
-\begin{corollary}
-\label{cor:ineqWS+}
-Let \(n,k \in \mathbb{N}^*\) and set \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
-Then :
-\[
-\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}.
-\]
-\end{corollary}
-
-\begin{remark}
-In the S-template construction for Schur numbers, the additive constant comes from the fact that the special color does
-not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by
-\[
-\max_{b \in \mathbb{N}^*} \left\{\min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}.
-\]
-\end{remark}
 
@@
 \begin{sloppypar}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Denote by \(f\) the coloring
-associated to the \(b\)-WS-template  and \(g\) the one associated to the sum-free partition of \([\![1,p]\!]\); where
-\({f : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({g : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, assume
-that the sum-free coloring of \([\![1, p]\!]\) is ordered.
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Let \(f\) and \(g\) be colorings associated 
+to the \(b\)-WS-template and to the sum-free partition of \([\![1,p]\!]\), respectively: 
+\({f : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({g : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, 
+we assume that the sum-free coloring of \([\![1, p]\!]\) is ordered.
 \end{sloppypar}
@@
 
-Split \([\![1, p a + b]\!]\) into three subsets. \\
+We split \([\![1, p a + b]\!]\) into three subsets. \\
 NB: To keep the notation short, the restriction to \([\![b + 1, p a + b]\!]\) of \(\pi\) defined in Subsection \ref{DefinitionWS+}
@@
 
-A new coloring \(h\) is defined as follows:
+We define a coloring \(h\) of \([\![1, p a + b]\!]\) using \( [\![1,n+k]\!]\) colors:
 \[
@@
 
-Function \(h\) is well defined since \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) is a partition of  \([\![1, p a + b]\!]\).
-We now prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) be such that \(x \neq y\),
-\(h(x) = h(y)\) and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Nine cases are to be distinguished
-according to the subsets \((\mathcal{T}, \mathcal{C}, \mathcal{R})\) to which \(x\) and \(y\) belong. It is
+Function \(h\) is well defined since sets \(\mathcal{T}, \mathcal{C}, \mathcal{R}\) partition \([\![1, p a + b]\!]\).
+Now, we prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) be such that \(x \neq y\),
+\(h(x) = h(y)\), and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Nine cases are to be distinguished
+according to which of the sets \(\mathcal{T}, \mathcal{C}, \mathcal{R}\) \(x\) and \(y\) belong to. It is
 sufficient to check only six cases out of nine since \(x\) and \(y\) play symmetric roles. \\
@@
 \par
-Hence in both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore
+In both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore
 \(h(x+y) \neq h(x)\) since \(f(x) = h(x)\). Otherwise, \(f(\pi(x+y)) = n + 1\) and thus \(h(x+y) > n\). In particular,
@@
 	is an ordered coloring. Therefore, given that \(g\) is sum-free, \(g(\lambda(y) + 1) \neq 1\). If \(\pi(x + y) \in
-	A_{n + 1}\) then \(h(x + y) = n + g(\lambda(x + y)) \neq n + 1\). Otherwise, \(h(x + y) \leqslant n\). Hence
-	in both cases \(h(x + y) \neq h(x)\).
+	A_{n + 1}\) then \(h(x + y) = n + g(\lambda(x + y)) \neq n + 1\). Otherwise, \(h(x + y) \leqslant n\).
 \end{itemize}
+\par
+In both cases \(h(x + y) \neq h(x)\).
 
@@
 
-There is a construction theorem for WS-templates as well.
-
-\begin{theorem}
-\label{thm:compWStemp}
-Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there exists a S-template with width
-\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WS-template
-with width \(pq\) and \((n+k)\) colors.
-\end{theorem}
-
-Theorem \ref{thm:compWStemp} yields the following corollary.
-
-\begin{corollary}
-Let \(n, k \in \mathbb{N}^*\). Then
-\[
-\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n).
-\]
-\end{corollary}
-
-\begin{proof}[\textsc{Proof.}]
-The idea is the same as in the previous theorem. The only difference is the WS property inherited
-from both the S-template and the WS-template. \\
-\end{proof}
-
-Theorem \ref{thm:WS-ab} can be seen as a particular case of WS-template in the same way Abott and Hanson's 
-construction \cite{AbbottHanson} can be seen as a particular case of S-template.
+Theorem \ref{thm:WS-ab} can be seen as a particular case of Theorem \ref{thm:WStemp} in the same way Abott and Hanson's 
+construction \cite{AbbottHanson} can be seen as a particular case of theorem \ref{thm:Stemp}.
 
@@
 
+By setting \(p = S(k)\) and \(a = \WS^+(n + 1)\) in Theorem \ref{thm:WStemp}, one obtains:
+
+\begin{corollary}
+\label{cor:ineqWS+}
+Let \(n,k \in \mathbb{N}^*\) and set \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
+Then :
+\[
+\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}.
+\]
+\end{corollary}
+
+\begin{remark}
+In the S-template construction for Schur numbers, the additive constant comes from the fact that the special color does
+not necessarily appear at the very begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by
+\[
+\max_{b \in \mathbb{N}^*} \left\{\min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}.
+\]
+\end{remark}
+
 As in Corollary \ref{cor:ineqS}, the additive constant Theorem \ref{thm:WStemp} can be improved 
@@
 \begin{proposition}
+\label{prop:tunelastrow}
 Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WS-template with width \(p\) and \(k\) colors. Let
@@
 
-The WS-templates can actually be fine-tuned further. However, it only gives minor improvements (most likely only an additive
-constant) at the cost of dramatically increasing the size of the search space. Therefore, it does not seem relevant to
-use this sophistications given that we could not even find good WS-templates with five colors using a computer (here good
-means better than those obtain by combining smaller templates).
-
-\par These modifications work as follows. One may notice that the first row (excluding the "tail") has constraints that other rows
-do not have because of the tail, especially if the special color appears in the tail as well. Thus allowing to have a coloring on the
-first row different from the coloring of the other rows would weaken the constraints. Actually, one may even go further by
-noticing that on the one hand the first (ordered) color of the sum-free partition used for the extension procedure has more
-more constraints than the other colors of the sum-free partition since the first row is of this color and is more constrained than
-the other rows, but that on the other hand it has more degrees of freedom than the other colors of the sum-free partition since in
-the sum-free partition there cannot be two consecutive numbers of this color. As a result, it removes  some constraints imposed
- by the first row on the other rows.
+The WS-templates can actually be fine-tuned further. However, it only gives minor improvements (most likely only an 
+additive constant) while increasing the size of the search space.
 
 \par
-To sum up, one can look for a generalised WS-template that uses a special coloring for the tail and the first row, a
-coloring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a coloring for all
-the other rows and a special coloring for the last numbers (as previously explained for the improvement of the additive
-constant of WS-templates).
+These modifications rely on one main observation: the first row (excluding the "tail") has constraints that other rows do not 
+have because of the tail, especially if the special color appears in the tail as well. Therefore, having a coloring dedicated to 
+the first row and another coloring dedicated to the repeating pattern would weaken the constraints on the repeating pattern.
+
+\par
+These additionnal constraints on the first row imply additionnal constraints on the rows of the its color (compared to other 
+colors). However, one may notice that there are never two consecutive rows of this color. Moreover these additionnal constraints 
+mostly concern two consecutive rows. Having a special coloring for rows of this color as well as another color dedicated to the 
+first row avoids enforcing these constraints specific to one color on the other colors and thus on the main repeating pattern.
+
+\par
+Finally, given that the color of the first row is different from the special color of the main repeating pattern, coloring \(g\) in
+Proposition \ref{prop:tunelastrow} can exploit this difference. \\
+
+There is a construction theorem for WS-templates as well.
+
+\begin{theorem}
+\label{thm:compWStemp}
+Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there exists a S-template with width
+\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WS-template
+with width \(pq\) and \((n+k)\) colors.
+\end{theorem}
+
+\begin{proof}[\textsc{Proof.}]
+The idea is the same as in theorem \ref{thm:WStemp}. The properties specific to WS-templates are inherited 
+from both the S-template and the WS-template. \\
+\end{proof}
+
+Theorem \ref{thm:compWStemp} yields the following corollary.
+
+\begin{corollary}
+Let \(n, k \in \mathbb{N}^*\). Then
+\[
+\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n).
+\]
+\end{corollary}
 
@@
 
-We produced WS-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities
-of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) (in the 
-lexicographic order). Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.
+We produced WS-templates using the lingeling SAT solver \cite{Lingeling2017}, hence providing lower bound on \(WS^+\) 
+and inequalities of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) 
+(in the lexicographic order). Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.
 
@@
 Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{template} 
-corresponding to the third inequality can be found in the appendix.
+corresponding to the third inequality can be found in the \ref{WS-templates}.
 
@@
 partition of length 643. This backdoor gave a weakly sum-free partition of length 646 and cannot give a weakly sum-free 
-partition of length 647. A weakly sum-free partition of length 646 can be found in the \hyperref[WS(6)]{appendix}.
+partition of length 647. A weakly sum-free partition of length 646 can be found in the \ref{WS(6)}.
 

### 2021-10-13 article/weakschur.tex
plus de exist + pdf 13/10

@@
 
-Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
+Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
 subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
@@
 \begin{definition}
-Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WS-template with width \(a\)
+Let \( (n,b) \in (\mathbb{N}^*)^2\). If there is \(a\) such that there is a \(b\)-WS-template with width \(a\)
 and \(n\) colors, we define :
 \[
-\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WS-template with width } a \text{ and } n \text{ colors} \}.
+\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there is a } b \text{-WS-template with width } a \text{ and } n \text{ colors} \}.
 \]
-If no such \(a\) exists, we set \(\WS_b^+(n) = 0\).
+If there is no such \(a\), we set \(\WS_b^+(n) = 0\).
 \end{definition}
@@
 \label{PreuveThm}
-Let \((q, n) \in (\mathbb{N}^*)^2\) such that there exists a partition of \([\![1, q]\!]\) into n weakly sum-free subsets. 
+Let \((q, n) \in (\mathbb{N}^*)^2\) such that there is a partition of \([\![1, q]\!]\) into n weakly sum-free subsets. 
 Let \(f: [\![1, q]\!] \rightarrow [\!]1, n]\!]\) a weakly sum-free colouring.
@@
 Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WS-template with width \(p\) and \(k\) colors. Let
-\(c \in \mathbb{N}\) and assume there there exists a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),
+\(c \in \mathbb{N}\) and assume there is a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),
 
@@
 \label{thm:compWStemp}
-Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there exists a S-template with width
-\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WS-template
+Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there are a S-template with width
+\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there is a \(pb\)-WS-template
 with width \(pq\) and \((n+k)\) colors.

### 2021-10-13 article/schur.tex
plus de exist + pdf 13/10
Modif type n-partions

--- 2021-09-30 article/schur.tex
@@
 	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
-	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there exists a partition of \([\![1,pq+m_{n+1}
+	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there exists a partition of \([\![1,pq+m_{n+1}
 	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
@@
 
-A S-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
+A S-template with \(n\) colors is said to be symmetric if the sum-free \(n\)-partition derived 
 from this template by applying the extension procedure with a sum-free partition of length 1 is symmetric. 

### 2021-10-13 article/weakschur.tex
Modif type n-partions

--- 2021-09-30 article/weakschur.tex
@@
 the new lower bound \(\WS(6) \geqslant 646\) which was not directly obtained with a template contrary to the other lower bounds 
-given in this article.
+given in this paper.
 
@@
 \begin{sloppypar}
-Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
-subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free
-subsets then there exists a partition of \({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\)
-weakly sum-free subsets.
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a weakly sum-free \(n\)-partition of \([\![1,q]\!]\)
+and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there exists a partition of
+\({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
 \end{sloppypar}
@@
 
-Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
-subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
+Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there exists a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) 
+and a sum-free \(k\)-partition of \([\![1,p]\!]\). Let \(a \in \mathbb{N}\) with \(a > q\)
 and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
@@
 projection on the first line, denoted by \(\pi\), by the relation \(\tilde{\pi}(x) = \pi(x) - a\). A simple solution is to color \(x\) with the same color
-as \(\tilde{\pi}(x)\) in the weakly sum-free coloring of \([\![1,q]\!]\). As long as \(2q \leqslant a + r\) (not going two far to the right) and there
+as \(\tilde{\pi}(x)\) in the weakly sum-free coloring of \([\![1,q]\!]\). As long as \(2b \leqslant a + r\) (not going two far to the right) and there
 is no \(x \in \tilde{\pi}(\mathcal{C})\) such that \(2x \in \tilde{\pi}(\mathcal{C})\) (so that we do not have a sum in \(\mathcal{C}\) when
@@
 \label{thm:WStemp}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\)
-into \(k\) sum-free subsets and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a sum-free \(k\)-partition of
+\([\![1,p]\!]\) and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
 then there exists a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
@@
 \par
-By definition of function \(h\), \(h(x) \neq h(y)\).\\
+By definition of \(h\), \(h(x) \neq h(y)\).\\
 
@@
 do not have because of the tail, especially if the special color appears in the tail as well. Thus allowing to have a coloring on the
-first row different from the coloring of the other rows would weaken the constraints. Actually, one may even go further by
+first row different from the coloring of the other rows would weaken the constraints. Acutally, one may even go further by
 noticing that on the one hand the first (ordered) color of the sum-free partition used for the extension procedure has more
@@
 special color was the last by order of appearance. We highly suspect that better WS-templates with \(n \geqslant 5\) 
-colors can be found but one would have not to use the above assumptions.
+colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
+with a different method,for instance with Monte-Carlo methods as in \cite{Bouzy2015AnAP}. This could be the suject of a 
+future work.
 

### 2021-10-13 article/schur.tex

--- 2021-10-13 article/schur.tex
@@
 \begin{proposition}
-	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer \(w\) such that there exists a S-template with 
+	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer \(w\) such that there is a S-template with 
 	width \(w\) and \(n\) colors. 
@@
 \label{thm:Stemp}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is an S-template with width \(q\) and \(n+1\) colors 
-	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there is a partition of \([\![1,pq+m_{n+1}
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
+	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there exists a partition of \([\![1,pq+m_{n+1}
 	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
@@
 
-A S-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
-from this template by applying the extension procedure of theorem \ref{thm:Stemp} with a sum-free partition of length 1 is symmetric. 
+A S-template with \(n\) colors is said to be symmetric if the sum-free \(n\)-partition derived 
+from this template by applying the extension procedure with a sum-free partition of length 1 is symmetric. 
 \end{definition}

### 2021-10-13 article/weakschur.tex

--- 2021-10-13 article/weakschur.tex
@@
 \begin{sloppypar}
-Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) and
-a sum-frree \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \({[\![1,p(q+\left \lceil \frac{q}{2} \right 
-\rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a weakly sum-free \(n\)-partition of \([\![1,q]\!]\)
+and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there exists a partition of
+\({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
 \end{sloppypar}
@@
 
-Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
-subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
+Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there exists a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) 
+and a sum-free \(k\)-partition of \([\![1,p]\!]\). Let \(a \in \mathbb{N}\) with \(a > q\)
 and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
@@
 \label{thm:WStemp}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there are a partition of \([\![1,p]\!]\)
-into \(k\) sum-free subsets and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
-then there is a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a sum-free \(k\)-partition of
+\([\![1,p]\!]\) and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
+then there exists a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
 \end{theorem}

### 2021-10-13 article/schur.tex
Le cancre de Git corrige ses bêtises

@@
 \label{thm:Stemp}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a \(S\)-template with width \(q\) and \(n+1\) colors 
-	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there exists a partition of \([\![1,pq+m_{n+1}
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is a \(S\)-template with width \(q\) and \(n+1\) colors 
+	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \([\![1,pq+m_{n+1}
 	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.

### 2021-10-13 article/weakschur.tex
Le cancre de Git corrige ses bêtises

@@
 \begin{sloppypar}
-Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there exists a weakly sum-free \(n\)-partition of \([\![1,q]\!]\)
-and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there exists a partition of
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\)
+and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of
 \({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
@@
 
-Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there exists a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) 
+Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) 
 and a sum-free \(k\)-partition of \([\![1,p]\!]\). Let \(a \in \mathbb{N}\) with \(a > q\)
@@
 \label{thm:WStemp}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a sum-free \(k\)-partition of
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there are a sum-free \(k\)-partition of
 \([\![1,p]\!]\) and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
-then there exists a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
+then there is a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
 \end{theorem}

### 2021-10-14 article/schur.tex
modifs :O

@@
 \begin{proposition}
-	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer \(w\) such that there is a S-template with 
+	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer \(w\) such that there is an S-template with 
 	width \(w\) and \(n\) colors. 
@@
 \label{thm:Stemp}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is a \(S\)-template with width \(q\) and \(n+1\) colors 
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a \(S\)-template with width \(q\) and \(n+1\) colors 
 	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \([\![1,pq+m_{n+1}
@@
 \label{prop:rafStemp}
-Let \((q, n) \in \left(\mathbb{N}^* \right)^2\) and let \(f\) be a coloring associated to a S-template with width \(q\) and \(n+1\) 
+Let \((q, n) \in \left(\mathbb{N}^* \right)^2\) and let \(f\) be a coloring associated to an S-template with width \(q\) and \(n+1\) 
 colors. Let \(b \in \mathbb{N}\) and assume there is a coloring \(g\) of 
@@
 This proposition corresponds to the fact that the hypotheses made on the coloring of the last row can be weakened because 
-the constraints in the definition of a S-template prevent a number from: 
+the constraints in the definition of an S-template prevent a number from: 
 \begin{itemize}
@@
 \begin{theorem}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is a S-template with width \(q\) and \(n+1\) colors,
-	and a S-template with width \(p\) and \(k\) colors, then there also is a S-template with width \(pq\) and \((n+k)\) 
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are an S-template with width \(q\) and \(n+1\) colors,
+	and an S-template with width \(p\) and \(k\) colors, then there also is an S-template with width \(pq\) and \((n+k)\) 
 	colors.
@@
 
-A S-template with \(n\) colors is said to be symmetric if the sum-free \(n\)-partition derived 
-from this template by applying the extension procedure with a sum-free partition of length 1 is symmetric. 
+An S-template with \(n\) colors is said to be symmetric if the sum-free \(n\)-partition derived 
+from this template by applying the extension procedure of Theorem \ref{thm:Stemp} with a sum-free 
+partition with length one is symmetric. 
 \end{definition}
@@
 last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
-likely be further improved but the improvement probably will not be substantial. Finally, a S-template corresponding to inequality 
-(\ref{S(n+6)}) was found by extending into a S-template the Schur 6 partition used in \cite{rowley2021improved} (owing to the 
+likely be further improved but the improvement probably will not be substantial. Finally, an S-template corresponding to inequality 
+(\ref{S(n+6)}) was found by extending into an S-template the Schur 6 partition used in \cite{rowley2021improved} (owing to the 
 size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 

### 2021-10-14 article/weakschur.tex
modifs :O

@@
 
-First, we put the integers of \([\![1, ap + q]\!]\) in the following table (with \(a\) columns and \(p + 1\) lines)
-and divide it into 3 blocks (the columns are numbered from \(-l\) to \(+q\)).
+First, we construct the following table with \(a\) columns and \(p+1\) rows containing the integers from \([\![1, ap + q]\!]\). 
+The columns are numbered from \(-l\) to \(+q\). This table is made of three different blocks.
 
@@
 \end{itemize}
-
-Note that with this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to the
-sum of the columns modulo \(a\).
 
@@
 \([\![1,q]\!]\). As long as \(2q \leqslant a + r\) (not going two far to the right) and there is no \(x \in \pi(\mathcal{C}) - a\) such that 
-\(2x \in \pi(\mathcal{C}) - a\) (so that we do not have a sum in \(\mathcal{C}\) when taking two numbers in the same column), 
-the colors \(1, ..., n\) are sum-free.
+\(2x \in \pi(\mathcal{C}) - a\), we do not have a sum in \(\mathcal{C}\) when taking two numbers in the same colum. Finally, the 
+weakly sum-free property of the coloring of \([\![1,q]\!]\) guarantees that if \(x \in [\![1,r]\!]\) and \(y \in \mathcal{C}\) are colored 
+the same, then \(x + y\) is colored differently.
 
 Setting \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) satsfies these 
-constraints: this is the construction corresponding to Theorem \ref{thm:WS-ab}. \\
+constraints: it corresponds to Theorem \ref{thm:WS-ab}. \\
 
@@
 \end{definition}
-The following proposition briefly shows how \(\WS^+(n)\) compares to weak Schur numbers.
+The following proposition shows how \(\WS^+(n)\) compares to weak Schur numbers.
 \begin{proposition}
@@
 
-Theorem \ref{thm:Stemp} describes a manner to extend a S-template into a larger Schur partitions using other Schur 
+Theorem \ref{thm:Stemp} describes a manner to extend an S-template into a larger Schur partitions using other Schur 
 partitions. Likewise, a WS-template can be extended into larger weak Schur partitions by using Schur partitions. This 
@@
 NB: To keep the notation short, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted in the following five predicates.
-\par
-The (weakly) sum-free conditions are expressed as:
-\begin{equation}
+
+The sum-free conditions are expressed as:
+\[
+\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),
+\]
+\[
+\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).
+\]
+
+The weakly sum-free condition is expressed as:
+\[
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \right. \Longrightarrow f(x+y) \neq f(x),
-\end{equation}
-\begin{equation}
-\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),
-\end{equation}
-\begin{equation}
-\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).
-\end{equation}
+\]
 
-The additionnal constraints for the WS-template are:
-\begin{equation}
+The additionnal constraints for the WS-template are expressed as:
+\[
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \right. \Longrightarrow f(\pi(x+y)) \neq f(x),
-\end{equation}
-\begin{equation}
+\]
+\[
 \forall (x,y) \in [\![1,a + b]\!]^2, \left\{
@@
 \right. \Longrightarrow f(x+y - 2 a) \neq f(x).
-\end{equation}
+\]
 
@@
 Let \((q, n) \in (\mathbb{N}^*)^2\) such that there is a partition of \([\![1, q]\!]\) into n weakly sum-free subsets. 
-Let \(f: [\![1, q]\!] \rightarrow [\!]1, n]\!]\) a weakly sum-free colouring.
+Let \(f: [\![1, q]\!] \rightarrow [\!]1, n]\!]\) be a weakly sum-free colouring.
 Let \(b=q\) and \(a = q + \left \lceil \dfrac{q}{2} \right \rceil + 1\). A new colouring \(g\) is defined as follows:
@@
 \label{thm:compWStemp}
-Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there are a S-template with width
+Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there are an S-template with width
 \(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there is a \(pb\)-WS-template
@@
 sophistication explained in Subsection \ref{ConstructionWS} in order to add
-the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining a S-template with 
+the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining an S-template with 
 width 33 with a WS-template with width 4. The best template we could find with a computer search gives the 

### 2021-10-28 article/article.tex
modifs :O
oups

@@
 The concept of "template" is also generalized to weak Schur numbers. Finding new templates leads to explicit partitions 
-improving lower bounds as well as the growth rate for Schur numbers, weak Schur numbers and multicolor Ramsey numbers \(R_n(3)\). 
+improving lower bounds as well as the growth rate for Schur numbers, weak Schur numbers, and multicolor Ramsey numbers \(R_n(3)\). 
 The new lower bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), 

### 2021-10-28 article/schur.tex
oups

--- 2021-10-13 article/schur.tex
@@
 
-Here \(n\) can be seen as a "special" color in the sense that it is no constrained by \ref{eq:constemp}.
+Here \(n\) can be seen as a "special" color in the sense that it is not constrained by Assertion (\ref{eq:constemp}).
 However, note that \(n\) is not necessarily the last color by order of appearance, any color can play this role.
@@
 \begin{proof}[\textsc{Proof.}]
-The upper bound comes from the fact that an S-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) 
-into \(n\) sum-free subsets. The lower bound comes from Abbott and Hanson's construction \cite{AbbottHanson}. \\
+The upper bound comes from the fact that an S-template with width \(p\) and \(n\) colors is also a sum-free \(n\)-partition 
+of \([\![1, p]\!]\). The lower bound comes from Abbott and Hanson's construction \cite{AbbottHanson}. \\
 \end{proof}
@@
 
-We start by reminding the explicit construction of a sum-free partition with the use of an S-template and another sum free partition. 
+We start by reminding the explicit construction of a sum-free partition with the use of an S-template and a sum-free partition. 
 We rephrase in terms of Schur numbers this contruction stated by Rowley in the context of Ramsey numbers \cite{RowleyRamsey}.
@@
 \label{thm:Stemp}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is a \(S\)-template with width \(q\) and \(n+1\) colors 
-	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \([\![1,pq+m_{n+1}
-	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is an S-template with width \(q\) and \(n+1\) colors 
+	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there is a partition of \([\![1,pq+m_{n+1}
+	-1]\!]\) into \(n+k\) sum-free subsets. Number \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
 \end{theorem}
 
-The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. They 
+The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. First, they
+put the integers from \([\![1,S(k)(2S(n)+1)+S(n)]\!]\) in a table with width \(2S(n)+1\) and height \(S(k)+1\) and they 
+numbered both the rows and the columns, starting from one upwards. Then, they 
 extended a sum-free partition vertically by repeating it. Next, they used another sum-free partition to color the other half according 
@@
 
-Setting \(q = S^+(n+1)\) and \(p = S(k)\) in theorem \ref{thm:Stemp} yields the following corollary.
+Setting \(q = S^+(n+1)\) and \(p = S(k)\) in Theorem \ref{thm:Stemp} yields the following corollary.
 
@@
 
-A S-template with \(n\) colors is said to be symmetric if the sum-free \(n\)-partition derived 
-from this template by applying the extension procedure with a sum-free partition of length 1 is symmetric. 
+A S-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
+from this template by applying the extension procedure of theorem \ref{thm:Stemp} with a sum-free partition of length 1 is symmetric. 
 \end{definition}
 
-We produced S-templates using the lingeling SAT solver \cite{Lingeling2017}, hence providing lower bound on 
+We produced S-templates using the lingeling SAT solver \cite{Lingeling2017}, hence providing lower bounds on 
 \(S^+\) and inequalities of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing us with 
@@
 
-Inequality (\ref{S(n+1)}) comes from  Schur's original article\cite{Schur1917}. Inequality (\ref{S(n+2)}) is due to
+Inequality (\ref{S(n+1)}) comes from  Schur's original article \cite{Schur1917}. Inequality (\ref{S(n+2)}) is due to
 Abott and Hanson \cite{AbbottHanson} and inequality (\ref{S(n+3)}) to Rowley \cite{RowleyRamsey}. 
-The three following inequalities are our result.
+The three following inequalities are our result:
 
@@
 
-\par The \hyperref[S-templates]{templates} corresponding to inequalities (\ref{S(n+3)}), (\ref{S(n+4)}) and 
+\par The \hyperref[S-templates]{templates} corresponding to inequalities (\ref{S(n+3)}), (\ref{S(n+4)}), and 
 (\ref{S(n+5)}) are listed in \ref{S-templates}.
@@
 \par
-Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}) and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
+Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}), and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
 Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
@@
 likely be further improved but the improvement probably will not be substantial. Finally, a S-template corresponding to inequality 
-(\ref{S(n+6)}) was found by extending into a S-template the Schur 6 partition used in \cite{rowley2021improved} (owing to the 
+(\ref{S(n+6)}) was found by extending into a S-template the Schur 6-partition used in \cite{rowley2021improved} (owing to the 
 size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 
@@
 
-Except for \(S(8)\), \(S(9)\) and \(S(13)\), the best lower bounds are obtained thanks to
+Except for \(S(8)\), \(S(9)\), and \(S(13)\), the best lower bounds are obtained thanks to
 the fifth inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table

### 2021-10-28 article/weakschur.tex
oups

--- 2021-10-13 article/weakschur.tex
@@
 \begin{sloppypar}
-Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\)
-and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of
-\({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) and
+a sum-frree \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \({[\![1,p(q+\left \lceil \frac{q}{2} \right 
+\rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
 \end{sloppypar}
@@
 
-Given that Theorem \ref{thm:WS-ab} will appear as a particular case of a more general theorem after the introduction of
-templates for weak Schur numbers, we only outline the demonstration; a \hyperref[PreuveThm]{proof} using templates 
+As Theorem \ref{thm:WS-ab} is actually a particular case of a more general theorem (Theorem \ref{thm:WStemp}) which will
+be formulated after the introduction of templates for weak Schur number,
+we only outline the demonstration. Its complete \hyperref[PreuveThm]{proof} using templates 
 for weak Schur numbers is in Subsection \ref{ConstructionWS}.
 
-Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) 
-and a sum-free \(k\)-partition of \([\![1,p]\!]\). Let \(a \in \mathbb{N}\) with \(a > q\)
+Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
+subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
 and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
@@
 \begin{itemize}
-	\item \(\mathcal{T}\) (the "tail"): In the row indexed by 0: numbers from \([\![1,q]\!]\).
-	\item \(\mathcal{R}\) (the "rows"): the integers in columns \(-l\) to \(+r\).
+	\item \(\mathcal{T}\) (the "tail"): in the row indexed by 0: numbers from \([\![1,q]\!]\).
+	\item \(\mathcal{R}\) (the "rows"): the integers in columns from \(-l\) to \(+r\).
 	\item \(\mathcal{C}\) (the "columns"): the integers in the last \(w\) columns.
@@
 This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers 
-\cite{AbbottHanson}. This formula also includes the results of Rowley \cite{RowleyWS} as a special case. For \(n>2\), 
-the formula from corollary \ref{cor:ineqWS-S} does not give new lower bounds.
+\cite{AbbottHanson}. This formula also includes the results from \cite{RowleyWS} as a special case. For \(n>2\), 
+the formula from Corollary \ref{cor:ineqWS-S} does not give new lower bounds.
 
@@
 \begin{definition}
-Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). We define :
+Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). We define:
 \[ \pi_{a,b}:x \longmapsto (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x \mod a).\]
@@
 \begin{sloppypar}
-\(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
+Function \(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
 calculative properties on \(\pi\) reflecting the behaviour of an element's column number in \hyperref[SchemaWS]{Figure 3} and
@@
 Function \(\lambda\) maps an element \(x\) to its line number as mentioned in the intuitive explanation.
-As we just did with \(\pi\), we prove three more calculative results on both \(\pi\) and \(\lambda\) that are used in
+As we have just done with \(\pi\), we prove three more calculative results on both \(\pi\) and \(\lambda\) that are used in
 Subsection \ref{ConstructionWS}.
@@
 Let \( (a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\). Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
-This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WS-template) with width \(a\) and \(n\) colors when :
+This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WS-template) with width \(a\) and \(n\) colors when:
 
@@
 \item \(\forall i \in [\![1, n]\!], A_i\backslash [\![1, b]\!]\) is sum-free,
-\item For \(A_n\) (the special subset) :
+\item For \(A_n\) (the special subset):
 	\[
@@
 Let \( (n,b) \in (\mathbb{N}^*)^2\). If there is \(a\) such that there is a \(b\)-WS-template with width \(a\)
-and \(n\) colors, we define :
+and \(n\) colors, we define:
 \[
@@
 \begin{definition}
-Let \( n \in \mathbb{N}^*\). We define :
+Let \( n \in \mathbb{N}^*\). We define:
 \[
@@
 \begin{proposition}
-Let \(n \in [\![2, +\infty]\!]\). Then :
+Let \(n \in [\![2, +\infty]\!]\). Then:
 \[
@@
 \label{thm:WStemp}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there are a sum-free \(k\)-partition of
-\([\![1,p]\!]\) and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there are a partition of \([\![1,p]\!]\)
+into \(k\) sum-free subsets and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
 then there is a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
@@
 NB: To keep the notation short, the restriction to \([\![b + 1, p a + b]\!]\) of \(\pi\) defined in Subsection \ref{DefinitionWS+}
-is denoted by \(\pi\) in the hereunder equations.
+is denoted by \(\pi\) in the hereunder equations:
 
 \begin{itemize}
-	\item \(\mathcal{T} = [\![1, b]\!]\)
-	\item \(\mathcal{C} = \pi^{-1}(f^{-1}([\![1, n]\!]))\)
-	\item \(\mathcal{R} = \pi^{-1}(f^{-1}(\{n + 1\}))\)
+	\item \(\mathcal{T} = [\![1, b]\!]\),
+	\item \(\mathcal{C} = \pi^{-1}(f^{-1}([\![1, n]\!]))\),
+	\item \(\mathcal{R} = \pi^{-1}(f^{-1}(\{n + 1\}))\).
 \end{itemize}
@@
 \begin{array}{c c c l}
-	h : & [\![1, p a + b]\!] & \longrightarrow & [\![1,n+k]\!] \\
+	h : & [\![1, p a + b]\!] & \longrightarrow & [\![1,n+k]\!],\\
 	& x & \longmapsto &
 	\left\{ \begin{array}{l l}
-		f(x) & \text{if}~x \in \mathcal{T} \\
-		f(\pi(x)) & \text{if}~x \in \mathcal{C} \\
-		n + g(\lambda(x)) & \text{if}~x \in \mathcal{R}
+		f(x), & \text{if}~x \in \mathcal{T}, \\
+		f(\pi(x)), & \text{if}~x \in \mathcal{C}, \\
+		n + g(\lambda(x)), & \text{if}~x \in \mathcal{R}.
 	\end{array} \right.
@@
 
-Theorem \ref{thm:WS-ab} can be seen as a particular case of Theorem \ref{thm:WStemp} in the same way Abott and Hanson's 
-construction \cite{AbbottHanson} can be seen as a particular case of theorem \ref{thm:Stemp}.
+We go back to Theorem \ref{thm:WS-ab} which can be seen as a particular case of Theorem \ref{thm:WStemp} in the same way Abott and Hanson's 
+construction \cite{AbbottHanson} can be seen as a particular case of Theorem \ref{thm:Stemp}. Its deferred proof is given below.
 
@@
 \begin{array}{c c c l}
-	g : & [\![1, a + b]\!] & \longrightarrow & [\![1, n + 1]\!] \\
+	g : & [\![1, a + b]\!] & \longrightarrow & [\![1, n + 1]\!], \\
 	& x & \longmapsto &
 		\left\{ \begin{array}{l l}
-			f(x) & \text{if}~x \in [\![1, b]\!]  \\
-			n + 1 & \text{if}~x \in [\![b + 1, 2 b + 1]\!] \\
-			f(x - a) & \text{if}~x \in  [\![2 b + 2, a + b]\!]
+			f(x), & \text{if}~x \in [\![1, b]\!],  \\
+			n + 1, & \text{if}~x \in [\![b + 1, 2 b + 1]\!], \\
+			f(x - a), & \text{if}~x \in  [\![2 b + 2, a + b]\!].
 		\end{array} \right.
@@
 Let \(n,k \in \mathbb{N}^*\) and set \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
-Then :
+Then:
 \[
@@
 These modifications rely on one main observation: the first row (excluding the "tail") has constraints that other rows do not 
-have because of the tail, especially if the special color appears in the tail as well. Therefore, having a coloring dedicated to 
+have because of the tail, especially if the special color appears in the tail as well. Indeed, the line number of the
+sum of two numbers in the tail is never greater than one. Therefore, having a coloring dedicated to 
 the first row and another coloring dedicated to the repeating pattern would weaken the constraints on the repeating pattern.
@@
 
-We produced WS-templates using the lingeling SAT solver \cite{Lingeling2017}, hence providing lower bound on \(WS^+\) 
+We produced WS-templates using the lingeling SAT solver \cite{Lingeling2017}, hence providing lower bounds on \(WS^+\) 
 and inequalities of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) 
@@
 
-Inequality (\ref{WS(n+3)}) cannot be further improved and was found with a SAT solver. It uses the first 
+Inequality (\ref{WS(n+3)}), found with a SAT solver \cite{Lingeling2017}, cannot be improved (with this 
+definition of WS-template). It uses the first 
 sophistication explained in Subsection \ref{ConstructionWS} in order to add
@@
 we only looked for WS-templates with five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
-special color was the last by order of appearance. We highly suspect that better WS-templates with \(n \geqslant 5\) 
+special color was the last by order of appearance. We expect that better WS-templates with \(n \geqslant 5\) 
 colors can be found but one would have not to use the above assumptions.
 
-Like in  Subsection \ref{subsec:lowS}, we compute the lower bounds given by inequalities (\ref{WS(n+1)}),
-(\ref{WS(n+2)}) and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound for each value of \(n\) is highlighted.
+Like in  Subsection \ref{subsec:lowS}, we compute the lower bounds given by Inequalities (\ref{WS(n+1)}),
+(\ref{WS(n+2)}), and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound for each value of \(n\) is highlighted.
 

### 2021-10-28 article/weakschur.tex

@@
 \begin{sloppypar}
-Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) and
-a sum-frree \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \({[\![1,p(q+\left \lceil \frac{q}{2} \right 
-\rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\)
+and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of
+\({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
 \end{sloppypar}
@@
 
-Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
-subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
+Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) 
+and a sum-free \(k\)-partition of \([\![1,p]\!]\). Let \(a \in \mathbb{N}\) with \(a > q\)
 and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
@@
 \label{thm:WStemp}
-Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there are a partition of \([\![1,p]\!]\)
-into \(k\) sum-free subsets and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there are a sum-free \(k\)-partition of
+\([\![1,p]\!]\) and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
 then there is a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.

### 2021-10-28 article/article.tex
verifs

@@
 
-\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190 Gif-sur-Yvette, France}
+\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190, Gif-sur-Yvette, France}
 \address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}
@@
 \begin{keyword}
-Schur number \sep Weak Schur number \sep Ramsey theory \sep Sumfree partition
+Schur number \sep Weak Schur number \sep Ramsey theory \sep Sum-free partition
 \MSC[2020]{05D10 \sep 05A17 \sep 11B75 \sep 11B81}

### 2022-02-24 article/soumission_SIAM/schur.tex
dossier siam

--- 2021-10-28 article/schur.tex
@@
 \label{thm:Stemp}
-	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there is an S-template with width \(q\) and \(n+1\) colors 
-	and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets then there is a partition of \([\![1,pq+m_{n+1}
-	-1]\!]\) into \(n+k\) sum-free subsets. Number \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are an \(S\)-template with width \(q\) and \(n+1\) colors 
+	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \([\![1,pq+m_{n+1}
+	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
 \end{theorem}
@@
 
-A S-template with \(n\) colors is said to be symmetric if the partition into \(n\) sum-free subsets derived 
-from this template by applying the extension procedure of theorem \ref{thm:Stemp} with a sum-free partition of length 1 is symmetric. 
+An S-template with \(n\) colors is said to be symmetric if the sum-free \(n\)-partition derived 
+from this template by applying the extension procedure of Theorem \ref{thm:Stemp} with a sum-free 
+partition with length one is symmetric. 
 \end{definition}
@@
 last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
-likely be further improved but the improvement probably will not be substantial. Finally, a S-template corresponding to inequality 
+likely be further improved but the improvement probably will not be substantial. Finally, an S-template corresponding to inequality 
 (\ref{S(n+6)}) was found by extending into a S-template the Schur 6-partition used in \cite{rowley2021improved} (owing to the 

### 2022-02-24 article/soumission_SIAM/weakschur.tex

--- 2021-10-28 article/weakschur.tex
@@
 Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{template} 
-corresponding to the third inequality can be found in the \ref{WS-templates}.
+corresponding to the third inequality can be found in \ref{WS-templates}.
 
@@
 partition of length 643. This backdoor gave a weakly sum-free partition of length 646 and cannot give a weakly sum-free 
-partition of length 647. A weakly sum-free partition of length 646 can be found in the \ref{WS(6)}.
+partition of length 647. A weakly sum-free partition of length 646 can be found in \ref{WS(6)}.
 

### 2022-02-24 article/soumission_SIAM/article.tex
dossier siam
sauv-siam

--- 2021-10-28 article/article.tex
@@
-\documentclass[3p]{elsarticle}
+\documentclass[review,onefignum,onetabnum]{siamart190516}
 
-\usepackage{amsmath}
+%\usepackage{amsmath}
 \usepackage{amssymb}
-\usepackage{amsthm}
+%\usepackage{amsthm}
 \usepackage{dsfont}
@@
 
-\usepackage[english]{babel}
-\usepackage[hyphens]{url}
-\usepackage{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage{siunitx}
+%\usepackage[english]{babel}
+%\usepackage[hyphens]{url}
+%\usepackage[hidelinks]{hyperref}
+%\usepackage[utf8]{inputenc}
+%\usepackage{siunitx}
 \usepackage{float}
 
-\usepackage[table]{xcolor}
+%\usepackage[table]{xcolor}
 \usepackage{multirow}
@@
 
-\newtheorem{definition}{Definition}[section]
-\newtheorem{notation}[definition]{Notation}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{computational theorem}[definition]{Computational Theorem}
-\newtheorem{corollary}[definition]{Corollary}
-\newtheorem{remark}[definition]{Remark}
-\newtheorem{proposition}[definition]{Proposition}
+\newsiamremark{remark}{Remark}
 
@@
 
-\author[1]{Romain Ageron\fnref{fn1}}
-\ead{romain.ageron@student-cs.fr}
+%\author[1]{Romain Ageron\fnref{fn1}}
+%\ead{romain.ageron@student-cs.fr}
 
-\author[1]{Paul Casteras\fnref{fn1}}
-\ead{paul.casteras@student-cs.fr}
+%\author[1]{Paul Casteras\fnref{fn1}}
+%\ead{paul.casteras@student-cs.fr}
 
-\author[1]{Thibaut Pellerin\fnref{fn1}}
-\ead{thibaut.pellerin@student-cs.fr}
+%\author[1]{Thibaut Pellerin\fnref{fn1}}
+%\ead{thibaut.pellerin@student-cs.fr}
 
-\author[1]{Yann Portella\fnref{fn1}}
-\ead{yann.portella@student-cs.fr}
+%\author[1]{Yann Portella\fnref{fn1}}
+%\ead{yann.portella@student-cs.fr}
 
-\author[2]{Arpad Rimmel\fnref{fn2}}
-\ead{arpad.rimmel@centralesupelec.fr}
+%\author[2]{Arpad Rimmel\fnref{fn2}}
+%\ead{arpad.rimmel@centralesupelec.fr}
 
-\author[2]{Joanna Tomasik\corref{cor1}\fnref{fn2}}
-\ead{joanna.tomasik@centralesupelec.fr}
+%\author[2]{Joanna Tomasik\corref{cor1}\fnref{fn2}}
+%\ead{joanna.tomasik@centralesupelec.fr}
 
-\cortext[cor1]{Corresponding author}
-\fntext[fn1]{These authors contributed equally.}
-\fntext[fn2]{These authors supervised the work of the main authors.}
+%\cortext[cor1]{Corresponding author}
+%\fntext[fn1]{These authors contributed equally.}
+%\fntext[fn2]{These authors supervised the work of the main authors.}
 
-\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190 Gif-sur-Yvette, France}
-\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}
+%\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190, Gif-sur-Yvette, France}
+%\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}
 
@@
 
-\begin{keyword}
-Schur number \sep Weak Schur number \sep Ramsey theory \sep Sumfree partition
-\MSC[2020]{05D10 \sep 05A17 \sep 11B75 \sep 11B81}
-\end{keyword}
+%\begin{keyword}
+%Schur number \sep Weak Schur number \sep Ramsey theory \sep Sum-free %partition
+%\MSC[2020]{05D10 \sep 11P81 \sep 05A17 \sep 11B75}
+%\end{keyword}
 
@@
 \bibliography{biblio}
-\bibliographystyle{elsarticle-num.bst}
+\bibliographystyle{siamplain}
 
 \include{appendix.tex}
-
 \end{document}

### 2022-02-24 article/soumission_SIAM/article.tex
entete + tableaux

@@
-\documentclass[review,onefignum,onetabnum]{siamart190516}
+\documentclass[final,onefignum,onetabnum]{siamart190516}
 
-%\usepackage{amsmath}
 \usepackage{amssymb}
-%\usepackage{amsthm}
 \usepackage{dsfont}
@@
 
-%\usepackage[english]{babel}
-%\usepackage[hyphens]{url}
-%\usepackage[hidelinks]{hyperref}
-%\usepackage[utf8]{inputenc}
-%\usepackage{siunitx}
 \usepackage{float}
 
-%\usepackage[table]{xcolor}
-\usepackage{multirow}
 \usepackage{nicematrix}
-
-\renewcommand{\qedsymbol}{\(\square\)}
 
@@
 \newcommand{\WS}{\mathit{WS}}
-\newcommand{\docarraystretch}{1.2}
-\newcommand{\resetarraystretch}{\renewcommand{\arraystretch}{\docarraystretch}}
-\resetarraystretch
 
-\title{New lower bounds for Schur and weak Schur numbers}
+\title{New lower bounds for Schur and weak Schur numbers \thanks{Submitted to the editors 02/24/2022.}}
 
-%\author[1]{Romain Ageron\fnref{fn1}}
-%\ead{romain.ageron@student-cs.fr}
+\author{Romain Ageron\thanks{CentraleSup\'elec, Universit\'e{} Paris-Saclay, Gif-sur-Yvette, France
+	(\email{romain.ageron@student-cs.fr}, \email{paul.casteras@student-cs.fr},
+	\email{thibaut.pellerin@student-cs.fr}, \email{yann.portella@student-cs.fr}).}
+\and Paul Casteras\footnotemark[2]
+\and Thibaut Pellerin\footnotemark[2]
+\and Yann Portella\footnotemark[2]
+\and Arpad Rimmel\footnotemark[2]\ \thanks{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, Orsay, France
+	(\email{arpad.rimmel@centralesupelec.fr}).}
+\and Joanna Tomasik\footnotemark[2]\ \footnotemark[3]\ \thanks{Corresponding author
+	(\email{joanna.tomasik@centralesupelec.fr}).}}
 
-%\author[1]{Paul Casteras\fnref{fn1}}
-%\ead{paul.casteras@student-cs.fr}
-
-%\author[1]{Thibaut Pellerin\fnref{fn1}}
-%\ead{thibaut.pellerin@student-cs.fr}
-
-%\author[1]{Yann Portella\fnref{fn1}}
-%\ead{yann.portella@student-cs.fr}
-
-%\author[2]{Arpad Rimmel\fnref{fn2}}
-%\ead{arpad.rimmel@centralesupelec.fr}
-
-%\author[2]{Joanna Tomasik\corref{cor1}\fnref{fn2}}
-%\ead{joanna.tomasik@centralesupelec.fr}
-
-%\cortext[cor1]{Corresponding author}
-%\fntext[fn1]{These authors contributed equally.}
-%\fntext[fn2]{These authors supervised the work of the main authors.}
-
-%\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190, Gif-sur-Yvette, France}
-%\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}
+\headers{New lower bounds for Schur and weak Schur numbers}{R. Ageron, P. Casteras,
+T. Pellerin, Y. Portella, A. Rimmel, J. Tomasik}
 
 \begin{document}
+\maketitle
 
 \begin{abstract}
-
 This article provides new lower bounds for both Schur and weak Schur numbers by exploiting a "template"-based approach. 
@@
 \(\WS (9) \geqslant 22\,536\) and \(\WS (10) \geqslant 71\,256 \).
-
 \end{abstract}
 
-%\begin{keyword}
-%Schur number \sep Weak Schur number \sep Ramsey theory \sep Sum-free %partition
-%\MSC[2020]{05D10 \sep 11P81 \sep 05A17 \sep 11B75}
-%\end{keyword}
+\begin{keywords}
+	Schur number, Weak Schur number, Ramsey theory, Sum-free partition
+\end{keywords}
 
-\maketitle
+\begin{AMS}
+	05D10, 11P81, 05A17, 11B75
+\end{AMS}
 
@@
 \include{appendix.tex}
+
 \end{document}

### 2022-02-24 article/soumission_SIAM/article.tex
merge Q_Q
proof

@@
 
-\input{introduction.tex}
+\section{Introduction}
 
-\input{schur.tex}
+We are interested in partioning the set of integers \(\{1, ..., p\}\) into \(n\) subsets such that there is no
+subset containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are
+\textit{sum-free}. If we lessen the above constraint by only considering integers \(x,y\) such that \(x \neq y\), we say the subsets are \textit{weakly sum-free}. The
+greatest \(p\) for which there is a partition into \(n\) sum-free subsets is called the \(n^{\text{th}}\) Schur
+number and is denoted \(S(n)\) \cite{Schur1917}. Likewise for weakly sum-free partitions we define \(\WS(n)\)
+the \(n^{\text{th}}\) weak Schur number \cite{Irving1973}. Values of \(S(n)\) and \(\WS(n)\) are known for small \(n\) only.
 
-\input{weakschur.tex}
+\subsection{State of the art}
+
+Up to recently, the most efficient generic construction for Schur numbers was given by Abbott and Hanson
+\cite{AbbottHanson} in 1972 with a recursive construction. It gave the best lower bounds for all sufficiently large
+numbers. No equivalent was known for weak Schur numbers and, as a result, the best known partitions for large
+weak Schur numbers did not use the \textit{weakly} sum-free property.
+
+\par
+As for smaller weak Schur numbers, the best lower bounds were obtained by computations. Eliahou
+\cite{EliahouBook}, Bouzy \cite{Bouzy2015AnAP} and Rafilipojaona \cite{Rafilipojaona} improved the lower
+bounds with Monte-Carlo methods. This was the main approach during the past decade.
+
+\par
+In 2020, Rowley introduced the notion of templates for Schur and Ramsey numbers \cite{RowleyRamsey} which
+generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalties) for Schur numbers.
+He also provided two inequalities for weak Schur numbers \cite{RowleyWS}. Besides, these two inequalities do use the \textit{weakly} sum-free property.
+
+\par The hereunder tables recap the lower bounds for Schur and weak Schur numbers, respectively. Gray cells
+indicate the exact values.
+
+\begin{table}[H]
+  \centering
+\begin{small}
+\setlength{\tabcolsep}{3pt}
+\renewcommand{\arraystretch}{1.2}
+\begin{NiceTabular}{*{13}{c}}[vlines]
+\CodeBefore
+	\cellcolor{gray!40}{2-2}
+	\cellcolor{gray!40}{2-3}
+	\cellcolor{gray!40}{2-4}
+	\cellcolor{gray!40}{2-5}
+	\cellcolor{gray!40}{2-6}
+	\cellcolor{gray!40}{3-2}
+	\cellcolor{gray!40}{3-3}
+	\cellcolor{gray!40}{3-4}
+	\cellcolor{gray!40}{3-5}
+	\cellcolor{gray!40}{3-6}
+\Body
+	\hline
+	\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
+	\hline
+	\Block{2-1}{State of the art} & 1 & 4 & 13 & 44 & 160 & 536 & 1\,696 & 5\,286 & 17\,694 & 60\,320 & 201\,696 & 637\,856 \\
+	& & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{rowley2021improved} & \cite{RowleyRamsey} & \cite{RowleyRamsey} &
+		\cite{RowleyRamsey} & \cite{RowleyRamsey} & \cite{RowleyRamsey} \\
+	\hline
+	\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{644\,628} \\
+	\hline
+\end{NiceTabular}
+\end{small}
+\caption{Comparison of lower bounds for Schur numbers}
+\label{table:1}
+\end{table}
+
+\begin{table}[H]
+  \centering
+\begin{small}
+\setlength{\tabcolsep}{3pt}
+\renewcommand{\arraystretch}{1.2}
+\begin{NiceTabular}{*{13}{c}}[vlines]
+\CodeBefore
+	\cellcolor{gray!40}{2-2}
+	\cellcolor{gray!40}{2-3}
+	\cellcolor{gray!40}{2-4}
+	\cellcolor{gray!40}{2-5}
+	\cellcolor{gray!40}{3-2}
+	\cellcolor{gray!40}{3-3}
+	\cellcolor{gray!40}{3-4}
+	\cellcolor{gray!40}{3-5}
+\Body
+	\hline
+	\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
+	\hline
+	\Block{2-1}{State of the art} & 2 & 8 & 23 & 66 & 196 & 642 & 2\,146 & 6\,976 & 22\,056 & 70\,778 & 241\,282 & 806\,786 \\
+	& & & & & \cite{ELIAHOU2012175} &\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} &
+		\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} \\
+	\hline
+	\hyperref[WeakSchur]{\textbf{Our results}}& & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
+	\hline
+\end{NiceTabular}
+\end{small}
+\caption{Comparison of lower bounds for weak Schur numbers}
+\label{table:2}
+\end{table}
+
+\subsection{Organization of this article}
+
+Our main contribution is a generalization of the concept of template to weak Schur numbers. Our templates
+provide new lower bounds (and inequalities) for weak Schur numbers. As a special case, our construction also includes
+a construction similar to Abbott and Hanson's \cite{AbbottHanson}, but for \textit{weak} Schur numbers this time.
+
+\par
+In Section \ref{Schur}, we explain Rowley's template-based construction for
+Schur numbers. Then, we give new templates, thus providing new lowers bounds and inequalities as well as
+showing that the growth rates for both Schur and Ramsey numbers \(R_n(3)\) exceed 3.28.
+
+\par
+In Section \ref{WeakSchur}, we generalize the concept of template to weak Schur numbers
+and provide new lower bounds for weak Schur numbers. Then, we use a different approach and give a new
+lower bound for \(\WS(6)\).
+
+\par
+Now, we introduce notations and definitions used throughout this article.
+
+\subsection{Definitions and notations}
+
+We start by defining sum-free and weakly sum-free subsets to introduce regular and weak Schur numbers.
+The set of positive natural numbers is denoted by \(\mathbb{N}^* =\mathbb{N} \backslash \{0\}\).
+
+\begin{definition}
+A subset \(A\) of \(\mathbb{N}\) is said to be \textit{sum-free} if
+\[ \forall (a,b) \in A^2 \text{, } a+b \notin A.\]
+\end{definition}
+
+\begin{definition}
+A subset \(B\) of \(\mathbb{N}\) is said to be \textit{weakly sum-free} if
+\[ \forall (a,b) \in B^2 \text{, } a \neq b \Longrightarrow a+b \notin B.\]
+\end{definition}
+
+Let us notice that a sum-free subset is also weakly sum-free, hence justifying the name of \textit{weakly} sum-free
+subsets. Given \(p\) and \(n\) two integers, we are interested in partitioning the set of integers \(\{1, 2, ..., p\}\),
+denoted by \([\![1,p]\!]\), into \(n\) (weakly) sum-free subsets.
+
+\par
+Schur proved \cite{Schur1917} that given a number of subsets \(n\), there is a value of \(p\)
+such that \([\![1,q]\!]\) cannot be partionned into \(n\) sum-free subsets for \(q \geqslant p\). A similar
+property holds for weakly sum-free subsets \cite{Irving1973}. These observations lead to the following definitions
+written for \(n \in \mathbb{N}^*\):
+
+\begin{definition}
+There is a largest integer denoted by \(S(n)\) such that \([\![1, S(n)]\!]\) can be
+ partitioned into \(n\) sum-free subsets. \(S(n)\) is called the \textit{\(n\)\textsuperscript{th} Schur number}.
+\end{definition}
+
+\begin{definition}
+There is a largest integer denoted by \(\WS (n)\) such that \([\![1, \WS (n)]\!]\)
+can be partitioned into \(n\) weakly sum-free subsets. \(\WS(n)\) is called the \(n\)\textsuperscript{th} weak Schur
+number.
+\end{definition}
+
+Subsets of an \(n\)-partition are denoted \(A_1, ..., A_n\). The smallest element of \(A_i\) is denoted
+\(m_i = \min(A_i)\). By ordering the subsets, we mean assuming that \(m_1 < ... < m_n\). We will make clear in the text
+when we use a subset ordering.
+
+A partition may be seen as a number coloring.
+
+\begin{definition}
+The coloring associated to a partition \(A_1, ..., A_n\) of
+\([\![1, p]\!]\) is the function \(f\) such that \(\forall x \in [\![1, p]\!], x \in A_{f(x)}\). Likewise, the partition associated to
+a coloring \(f\) of \([\![1, p]\!]\) with \(n\) colors is \(\forall c \in [\![1, n]\!], A_c = f^{-1}(c)\).
+\end{definition}
+
+\section{Templates for Schur numbers}
+\label{Schur}
+
+We use Rowley's template-based constructions \cite{RowleyRamsey} for Schur 
+numbers. To improve lower bounds for Schur and Ramsey numbers, he has introduced special sum-free 
+partitions verifying some additional properties which can be extended using a method generalizing Abbott and 
+Hanson's construction \cite{AbbottHanson}. He called these partitions "templates", and we keep this nomination. 
+Then, we propose new templates and use them to produce new lower bounds for Schur numbers.
+
+\subsection{Definition of \( [\![ 1, S^+ ]\!] \)}
+
+We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
+of \hyperref[figure:1]{Figure 1} not as a combination of two blocs, like in \cite{AbbottHanson} but as a whole, single construction. 
+An S-template is then defined as a new object playing the role of the first line but with less, yet sufficient, 
+constraints which allow for an expansion of the partition using a sum-free partition.
+
+\begin{definition}
+Let \((p,n) \in (\mathbb{N}^*)^2\). An S-template with \(n\) colors is defined as a partition of 
+\([\![1,p]\!]\) into \(n\) sum-free subsets \(A_1, A_2, ..., A_n\) verifying for all subsets but \(A_n\)
+\begin{equation}
+\label{eq:constemp}
+\forall (x,y) \in A_i^2, x+y > p
+\Longrightarrow x+y-p \notin A_i.
+\end{equation}
+The integer \(p\) is called the \textit{width} of the template.
+\end{definition}
+
+Here \(n\) can be seen as a "special" color in the sense that it is not constrained by Assertion (\ref{eq:constemp}).
+However, note that \(n\) is not necessarily the last color by order of appearance, any color can play this role.
+
+\begin{proposition}
+	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the greatest integer \(w\) such that there is an S-template with 
+	width \(w\) and \(n\) colors. 
+	\(S^+(n)\) is well defined and verifies
+	\[
+	2S(n-1)+1 \leqslant S^+(n) \leqslant S(n).
+	\]
+\end{proposition}
+
+\begin{proof}
+The upper bound comes from the fact that an S-template with width \(p\) and \(n\) colors is also a sum-free \(n\)-partition 
+of \([\![1, p]\!]\). The lower bound comes from Abbott and Hanson's construction \cite{AbbottHanson}. \\
+\end{proof}
+
+\subsection{Construction of Schur partitions using S-templates}
+
+We start by reminding the explicit construction of a sum-free partition with the use of an S-template and a sum-free partition. 
+We rephrase in terms of Schur numbers this contruction stated by Rowley in the context of Ramsey numbers \cite{RowleyRamsey}.
+
+\begin{theorem}
+\label{thm:Stemp}
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are an \(S\)-template with width \(q\) and \(n+1\) colors 
+	and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of \([\![1,pq+m_{n+1}
+	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{n+1}\) denotes the minimum element colored with the special color in the \(S\)-template.
+\end{theorem}
+
+The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. First, they
+put the integers from \([\![1,S(k)(2S(n)+1)+S(n)]\!]\) in a table with width \(2S(n)+1\) and height \(S(k)+1\) and they 
+numbered both the rows and the columns, starting from one upwards. Then, they 
+extended a sum-free partition vertically by repeating it. Next, they used another sum-free partition to color the other half according 
+to the line number, as in \hyperref[figure:1]{Figure 1}. We give an example for \(p = 4\), 
+\(q = 9\), \(n = 2\) and \(k = 2\) showing that \(S(2 + 2) \geqslant S(2) \left(2 S(2) + 1\right) + S(2)\), both with Abbott and 
+Hanson's construction (\hyperref[figure:1]{Figure 1}) and with an S-template which is not included in Abbott and Hanson's construction 
+(\hyperref[figure:2]{Figure 2}). In both cases, the special color is grey.
+
+\begin{figure}[H]
+\begin{center}
+
+\textbf{Abbott and Hanson's construction}
+\label{figure:1}
+\vspace{1.7ex}
+
+\renewcommand{\arraystretch}{1.5}
+\setlength{\tabcolsep}{1.2ex}
+\begin{NiceTabular}{|*{9}{c|}}[corners=SE,standard-cline,hlines]
+\CodeBefore
+	\cellcolor{red}{1-1}
+	\cellcolor{green}{1-2}
+	\cellcolor{green}{1-3}
+	\cellcolor{red}{1-4}
+	\cellcolor{cyan}{1-5}
+	\cellcolor{cyan}{1-6}
+	\cellcolor{cyan}{1-7}
+	\cellcolor{cyan}{1-8}
+	\cellcolor{cyan}{1-9}
+	\cellcolor{red}{2-1}
+	\cellcolor{green}{2-2}
+	\cellcolor{green}{2-3}
+	\cellcolor{red}{2-4}
+	\cellcolor{yellow}{2-5}
+	\cellcolor{yellow}{2-6}
+	\cellcolor{yellow}{2-7}
+	\cellcolor{yellow}{2-8}
+	\cellcolor{yellow}{2-9}
+	\cellcolor{red}{3-1}
+	\cellcolor{green}{3-2}
+	\cellcolor{green}{3-3}
+	\cellcolor{red}{3-4}
+	\cellcolor{yellow}{3-5}
+	\cellcolor{yellow}{3-6}
+	\cellcolor{yellow}{3-7}
+	\cellcolor{yellow}{3-8}
+	\cellcolor{yellow}{3-9}
+	\cellcolor{red}{4-1}
+	\cellcolor{green}{4-2}
+	\cellcolor{green}{4-3}
+	\cellcolor{red}{4-4}
+	\cellcolor{cyan}{4-5}
+	\cellcolor{cyan}{4-6}
+	\cellcolor{cyan}{4-7}
+	\cellcolor{cyan}{4-8}
+	\cellcolor{cyan}{4-9}
+	\cellcolor{red}{5-1}
+	\cellcolor{green}{5-2}
+	\cellcolor{green}{5-3}
+	\cellcolor{red}{5-4}
+\Body
+	1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
+	10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 \\
+	19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 \\
+	28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 \\
+	37 & 38 & 39 & 40 \\
+\end{NiceTabular}
+
+\vspace{1ex}
+\setlength{\tabcolsep}{2ex}
+
+\begin{tabular}{c c}
+	\textbf{Corresponding S-template} & \textbf{Corresponding sum-free partition} \\
+	\setlength{\tabcolsep}{1.5ex}
+	\begin{NiceTabular}{|*{9}{c|}}[standard-cline,hlines]
+	\CodeBefore 
+		\cellcolor{red}{1-1}
+		\cellcolor{green}{1-2}
+		\cellcolor{green}{1-3}
+		\cellcolor{red}{1-4}
+		\cellcolor{gray!40}{1-5}
+		\cellcolor{gray!40}{1-6}
+		\cellcolor{gray!40}{1-7}
+		\cellcolor{gray!40}{1-8}
+		\cellcolor{gray!40}{1-9}
+	\Body
+		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
+	\end{NiceTabular} &
+	\setlength{\tabcolsep}{1.5ex}
+	\begin{NiceTabular}{|*{4}{c|}}[standard-cline,hlines]
+	\CodeBefore
+		\cellcolor{cyan}{1-1}
+		\cellcolor{yellow}{1-2}
+		\cellcolor{yellow}{1-3}
+		\cellcolor{cyan}{1-4}
+	\Body
+		1 & 2 & 3 & 4 \\
+	\end{NiceTabular}
+\end{tabular}
+
+\setlength{\tabcolsep}{6pt}
+\caption{Visualisation of an Abbott and Hanson construction}
+\end{center}
+\end{figure}
+In the general construction with S-templates, the special color may not paint consecutive 
+numbers any longer. However, the special color is still replaced by the colors of the sum-free partition according to the 
+line number and the other colors are still vertically extended.
+
+\begin{figure}[H]
+\begin{center}
+\textbf{S-template construction}
+\label{figure:2}
+\setlength{\tabcolsep}{1.2ex}
+\renewcommand{\arraystretch}{1.5}
+
+\vspace{1.7ex}
+\begin{NiceTabular}{|*{9}{c|}}[corners=SE,standard-cline,hlines]
+\CodeBefore
+	\cellcolor{red}{1-1}
+	\cellcolor{green}{1-2}
+	\cellcolor{green}{1-3}
+	\cellcolor{red}{1-4}
+	\cellcolor{cyan}{1-5}
+	\cellcolor{cyan}{1-6}
+	\cellcolor{red}{1-7}
+	\cellcolor{cyan}{1-8}
+	\cellcolor{cyan}{1-9}
+	\cellcolor{red}{2-1}
+	\cellcolor{green}{2-2}
+	\cellcolor{green}{2-3}
+	\cellcolor{red}{2-4}
+	\cellcolor{yellow}{2-5}
+	\cellcolor{yellow}{2-6}
+	\cellcolor{red}{2-7}
+	\cellcolor{yellow}{2-8}
+	\cellcolor{yellow}{2-9}
+	\cellcolor{red}{3-1}
+	\cellcolor{green}{3-2}
+	\cellcolor{green}{3-3}
+	\cellcolor{red}{3-4}
+	\cellcolor{yellow}{3-5}
+	\cellcolor{yellow}{3-6}
+	\cellcolor{red}{3-7}
+	\cellcolor{yellow}{3-8}
+	\cellcolor{yellow}{3-9}
+	\cellcolor{red}{4-1}
+	\cellcolor{green}{4-2}
+	\cellcolor{green}{4-3}
+	\cellcolor{red}{4-4}
+	\cellcolor{cyan}{4-5}
+	\cellcolor{cyan}{4-6}
+	\cellcolor{red}{4-7}
+	\cellcolor{cyan}{4-8}
+	\cellcolor{cyan}{4-9}
+	\cellcolor{red}{5-1}
+	\cellcolor{green}{5-2}
+	\cellcolor{green}{5-3}
+	\cellcolor{red}{5-4}
+\Body
+	1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
+	10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 \\
+	19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 \\
+	28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 \\
+	37 & 38 & 39 & 40 \\
+\end{NiceTabular}
+
+\vspace{1ex}
+\setlength{\tabcolsep}{1.5ex}
+
+\begin{tabular}{c c}
+	\textbf{Corresponding S-template} & \textbf{Corresponding sum-free partition} \\
+	\setlength{\tabcolsep}{1.5ex}
+	\begin{NiceTabular}{|*{9}{c|}}[standard-cline,hlines]
+	\CodeBefore 
+		\cellcolor{red}{1-1}
+		\cellcolor{green}{1-2}
+		\cellcolor{green}{1-3}
+		\cellcolor{red}{1-4}
+		\cellcolor{gray!40}{1-5}
+		\cellcolor{gray!40}{1-6}
+		\cellcolor{red}{1-7}
+		\cellcolor{gray!40}{1-8}
+		\cellcolor{gray!40}{1-9}
+	\Body
+		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
+	\end{NiceTabular} &
+	\setlength{\tabcolsep}{1.5ex}
+	\begin{NiceTabular}{|*{4}{c|}}[standard-cline,hlines]
+	\CodeBefore
+		\cellcolor{cyan}{1-1}
+		\cellcolor{yellow}{1-2}
+		\cellcolor{yellow}{1-3}
+		\cellcolor{cyan}{1-4}
+	\Body
+		1 & 2 & 3 & 4 \\
+	\end{NiceTabular}
+\end{tabular}
+
+\setlength{\tabcolsep}{6pt}
+\caption{Visualisation of a template-based construction}
+
+\end{center}
+\end{figure}
+
+Now, we prove Theorem \ref{thm:Stemp}.
+
+\begin{proof}
+	Let \(f\) and \(g\) be colorings associated to the S-template with width \(q\) and the sum-free partition of 
+	\([\![1,p]\!]\), respectively: \(f : [\![1,q]\!] \longrightarrow [\![1,n+1]\!]\) and 
+	\(g : [\![1,p]\!] \longrightarrow [\![1,k]\!]\).
+
+	\par
+	NB: In the following three predicates, the conditions \(x + y \leqslant q\)  and \(x + y \leqslant p\) are omitted for readability.
+	\par
+	The sum-free condition is expressed as:
+	\[\forall (x,y) \in [\![1,q]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),\]
+	\[\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).\]
+
+	The additionnal constraint for the S-template is:
+	\[
+	\forall (x,y) \in [\![1,q]\!]^2, \left\{
+	\begin{array}{l}
+		f(x) = f(y) \leqslant n \\
+		x + y > q
+	\end{array}
+	\right. \Longrightarrow f(x+y-q) \neq f(x).
+	\]
+
+	For \(x \in [\![1,pq+m_{n+1}-1]\!]\), we write \(x = (\alpha - 1) q + u\) for certain integers \(\alpha \in \mathbb{N}^*\) 
+	and \(u \in [\![1,q]\!]\). Obviously, this decomposition unique. Coefficients \(\alpha\) and \(u\) may be interpreted as line 
+	and column coordinates of \(x\) in the template. We define a coloring \(h\) of \([\![1,pq+m_{n+1}-1]\!]\) using \( [\![1,n+k]\!]\) colors:
+	\[
+	\begin{array}{c c c l}
+		h : & [\![1,pq+m_{n+1}-1]\!] & \longrightarrow & [\![1,n+k]\!], \\
+		& x & \longmapsto & 
+		\left\{ \begin{array}{l l}
+			f(u), & \text{if}~f(u) \leqslant n, \\
+			n + g(\alpha), & \text{if}~f(u) = n + 1. \\
+		\end{array} \right.
+	\end{array}
+	\]
+
+	Function \(h\) is well-defined since, by definition of \(m_{n+1}\), \(\forall x \in [\![p q + 1, p q + m_{n + 1} - 1 ]\!], f(u) 
+	\leqslant n\) and therefore \(\forall x \in [\![1,pq+m_{n+1}-1]\!], f(u) = n + 1 \implies \alpha \in [\![1, p]\!]\).
+
+	\par
+	Now, we prove that \(h\) is a sum-free coloring. Let \(x,y \in [\![1,pq + m_{n+1}-1]\!]\) such that \(h(x) = h(y)\) 
+	and \(x+y \leqslant pq+m_{n+1}-1\). We claim that \(h(x+y) \neq h(x)\). We write \(x = (\alpha - 1) q + u\) and 
+	\(y = (\beta - 1) q + v\) where \(\alpha, \beta \in \mathbb{Z}\) and \(u, v \in [\![1,q]\!]\). Two cases are to be
+	distinguished according to the value of \(h(x)\). \\
+
+	\noindent \underline{\textbf{Case 1:} \(h(x) \leqslant n\)}
+	\par
+	Let us assume that \(h(x+y) \leqslant n\), otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition of function 
+	\(h\) and given that \(h(u) = h(v)\), we conclude \(f(u) = f(v)\). Two cases are to be distinguished according to the value of \(x + y\).
+
+	\begin{itemize}
+	\item If \(u + v > q\), we write \(w = u + v - q \in [\![1, q]\!]\). Consequentely \(x + y = (\alpha + \beta - 1) q + w\). By definition, 
+		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the additionnal constraint on \(f\) implies \(f(w) 
+		\neq f(u)\), that is \(h(x + y) \neq h(x)\).
+	\item If \(u + v \leqslant q\), we write \(w = u + v \in [\![1, q]\!]\). Consequentely \(x+y = (\alpha + \beta- 2) q + w\). By definition, 
+		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the sum-free property of \(f\) implies \(f(w) \neq f(u)\), 
+		that is \(h(x + y) \neq h(x)\).
+	\end{itemize}
+
+	\noindent \underline{\textbf{Case 2:} \(h(x) \geqslant n + 1\)}
+	\par
+	Now we have \(h(x) = n + g(\alpha) = 
+	n + g(\beta) = h(y)\), hence \(g(\alpha) = g(\beta)\). As above, we distinguish between two cases according 
+	to the value of \(x + y\).
+
+	\begin{itemize}
+	\item \begin{sloppypar}
+		If \(u + v > q\), write \(w = u + v - q \in [\![1, q]\!]\). Then \(x + y = (\alpha + \beta - 1) q + w\). Assume that 
+		\({h(x+y) \geqslant n + 1}\),  otherwise \(h(x + y) \neq h(x)\) obviously holds. By definition, \({h(x + y) = n + g(\alpha + 
+		\beta)}\). Given that \(g(\alpha) = g(\beta)\), the sum-free property of \(g\) implies \(g(\alpha + \beta) 
+		\neq g(\alpha)\) that is \(h(x + y) \neq h(x)\).
+		\end{sloppypar}
+	\item  If \(u + v \leqslant q\), write \(w = u + v \in [\![1, q]\!]\). Then \(x+y = (\alpha + \beta- 2) q + w\). The sum-free 
+		property of \(f\) implies \(f(w) \neq f(u)\). Therefore \(f(w) \leqslant n\) and thus \(h(x + y) \leqslant n\). In particular,
+		given that \(h(x) \geqslant n + 1\), \(h(x + y) \neq h(x)\).
+	\end{itemize}
+\end{proof}
+
+Setting \(q = S^+(n+1)\) and \(p = S(k)\) in Theorem \ref{thm:Stemp} yields the following corollary.
+
+\begin{corollary}
+\label{cor:ineqS}
+	Let \(n, k \in \mathbb{N}^*\). Then
+	\[ S(n+k) \geqslant S^+(n+1)S(k) + m_{n+1} - 1.\]
+\end{corollary}
+
+The following proposition may improve the additive constant of Corollary \ref{cor:ineqS}.
+
+\begin{proposition}
+\label{prop:rafStemp}
+Let \((q, n) \in \left(\mathbb{N}^* \right)^2\) and let \(f\) be a coloring associated to an S-template with width \(q\) and \(n+1\) 
+colors. Let \(b \in \mathbb{N}\) and assume there is a coloring \(g\) of 
+\([\![1, b]\!]\) with \(n+1\) colors such that:
+
+\begin{itemize}
+\item \(\forall (x, y) \in [\![1, q]\!]^2, \left\{
+	\begin{array}{l}
+		f(x) = f(y) \\
+		(x + y) \mod q \leqslant b
+	\end{array}
+	\right. \implies g((x + y) \mod q) \neq f(x)\),
+\item \(\forall (x, y) \in [\![1, q]\!] \times  [\![1, b]\!],  \left\{
+	\begin{array}{l}
+		f(x) = g(y) \\
+		x + y \leqslant b
+	\end{array}
+	\right. \implies g(x + y) \neq f(x)\).
+\end{itemize}
+
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - q S(n))\), we have
+\[ S(n+k) \geqslant q S(k) + b.\]
+\end{proposition}
+This proposition corresponds to the fact that the hypotheses made on the coloring of the last row can be weakened because 
+the constraints in the definition of an S-template prevent a number from: 
+\begin{itemize}
+\item being the sum of two of numbers of its own color. 
+\item creating a sum in its own color. 
+\end{itemize}
+The later is not always relevant on the last row given that it is not completely filled.
+As a result, we can change the coloring on \([\![ q S(k) + 1,  q S(k) + b]\!]\) (the last row) to extend the previous partitions.
+\newline
+
+There is a construction theorem for S-templates as well.
+
+\begin{theorem}
+	Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are an S-template with width \(q\) and \(n+1\) colors,
+	and an S-template with width \(p\) and \(k\) colors, then there also is an S-template with width \(pq\) and \((n+k)\) 
+	colors.
+\end{theorem}
+
+\begin{proof}
+The idea is the same as in the Theorem \ref{thm:Stemp}. The only difference is the S-template property inherited 
+from the second S-template. \\
+\end{proof}
+
+The inequality associated with this theorem is given by:
+
+\begin{corollary}
+	Let \(n, k \in \mathbb{N}^*\). Then
+	\[ S^+(n+k) \geqslant S^+(n+1)S^+(k).\]
+\end{corollary}
+
+\subsection{New lower bounds for Schur numbers}
+\label{subsec:lowS}
+
+We now give the inequalities corresponding to the current  best S-templates.
+
+\begin{definition}
+A sum-free partition \(A_1, ..., A_n\) of \([\![1, p]\!]\) is said to be symmetric if for all \( x \in [\![1, p]\!]\), 
+\(x\) and \(p + 1 - x\) belong to the same subset (except if \(x = p + 1 - x\)).
+
+An S-template with \(n\) colors is said to be symmetric if the sum-free \(n\)-partition derived 
+from this template by applying the extension procedure of Theorem \ref{thm:Stemp} with a sum-free 
+partition with length one is symmetric. 
+\end{definition}
+
+We produced S-templates using the lingeling SAT solver \cite{Lingeling2017}, hence providing lower bounds on 
+\(S^+\) and inequalities of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing us with 
+the largest value of \((a, b)\) (in the lexicographic order). In order to reduce the search space when the number 
+of colors exceeded five we only looked for symmetric S-templates, we assumed that the special color was the last 
+color to appear and we constrained the \(m_c\)'s out of being too small. Details concerning the encoding as a SAT 
+problem can be found in \cite{Heule2017}.
+
+\par
+The following six inequalities are given by the current best S-templates with \(n \leqslant 7\) colors.
+\begin{align}
+	S(n + 1) \geqslant &~3\,S(n)  + 1 \label{S(n+1)}\\
+	S(n + 2) \geqslant &~9\,S(n)  + 4 \label{S(n+2)}\\
+	S(n + 3) \geqslant &~33\,S(n) + 6 \label{S(n+3)}
+\end{align}
+
+Inequality (\ref{S(n+1)}) comes from  Schur's original article \cite{Schur1917}. Inequality (\ref{S(n+2)}) is due to
+Abott and Hanson \cite{AbbottHanson} and inequality (\ref{S(n+3)}) to Rowley \cite{RowleyRamsey}. 
+The three following inequalities are our result:
+
+\begin{align}
+	S(n + 4) \geqslant &~111\,S(n) + 43 \label{S(n+4)}\\
+	S(n + 5) \geqslant &~380\,S(n) + 148 \label{S(n+5)}\\
+	S(n + 6) \geqslant &~1\,160\,S(n) + 536 \label{S(n+6)}
+\end{align}
+
+\par The \hyperref[S-templates]{templates} corresponding to inequalities (\ref{S(n+3)}), (\ref{S(n+4)}), and 
+(\ref{S(n+5)}) are listed in \ref{S-templates}.
+
+\par
+Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}), and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
+Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
+last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
+likely be further improved but the improvement probably will not be substantial. Finally, an S-template corresponding to inequality 
+(\ref{S(n+6)}) was found by extending into a S-template the Schur 6-partition used in \cite{rowley2021improved} (owing to the 
+size of this template, its interest is limited and since it can easily be derived from above mentioned partition, it is not given in 
+\ref{S-templates}). Although we could not find a better S-template with seven colors, inequality (\ref{S(n+6)}) can definitely be 
+improved by a wide margin.
+
+\par
+The previous inequalities give new lower bounds for \(S(n)\) for
+\( n \geqslant 9 \). We compute the lower
+bounds for \( n \in [\![8,15]\!] \) using the four different inequalities. The best lower bounds are highlighted.
+
+\begin{table}[H]
+
+\label{LowerBoundsS}
+\[
+\begin{array}{c}
+	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
+	\CodeBefore
+		\cellcolor{yellow}{2-2}
+		\cellcolor{yellow}{3-3}
+		\cellcolor{yellow}{4-4}
+		\cellcolor{yellow}{4-5}
+	\Body
+		n & 8 & 9 & 10 & 11 \\
+		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,974 & 174\,444 \\
+		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 188\,299 \\
+		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
+	\end{NiceArray}
+	\\ \\
+	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
+	\CodeBefore
+		\cellcolor{yellow}{2-3}
+		\cellcolor{yellow}{4-2}
+		\cellcolor{yellow}{4-4}
+		\cellcolor{yellow}{4-5}
+	\Body
+		n & 12 & 13 & 14 & 15 \\
+		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,272\,730 \\
+		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
+		380 \, S(n-5) + 148 & 644\,628 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
+	\end{NiceArray}
+\end{array}
+\]
+\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
+\end{table}
+
+Except for \(S(8)\), \(S(9)\), and \(S(13)\), the best lower bounds are obtained thanks to
+the fifth inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). The table
+does not go any further, but the same inequality allows one to improve the
+lower bounds for \( n \geqslant 15 \).
+
+\begin{corollary}
+\begin{sloppypar}
+The growth rate for Schur numbers (and Ramsey numbers \(R_n(3)\))  satisfies \({\gamma \geqslant \sqrt[5]{380} \approx 3.28}\).
+\end{sloppypar}
+\end{corollary}
+
+\begin{proof}
+It is a mere consequence of the inequality \( S(n+5) \geqslant 380 \, S(n) + 148\). As for Ramsey
+numbers, the following inequality holds \(S(n) \leqslant R_n(3) - 2\) (see \cite{AbbottHanson}) hence the result. \\
+\end{proof}
+
+\subsection{Conclusion on S-templates}
+
+First, we formalized Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur numbers 
+by introducing S-templates as well as a new sequence, \(S^+\). We found new S-templates allowing us to obtain 
+new lower bounds for schur numbers. One may notice that we mostly gave only lower bounds for \(S^+\). It should be possible to 
+find better S-templates by making different assumptions or using a different method (Monte-Carlo methods, for instance).
+
+\par
+In the next section, we provide similar results for weak Schur numbers. We introduce WS-templates and a corresponding sequence, 
+\(\WS^+\). Then, we derive similar relations and a construction method allowing us to find new lower bounds for weak Schur numbers.
+
+\section{Templates for weak Schur numbers}
+\label{WeakSchur}
+
+We generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS}. We give an analogous for weak Schur numbers of Abbott 
+and Hanson's construction for Schur numbers \cite{AbbottHanson}. Then, as in the previous section, we introduce \textit{WS-templates}, 
+standing for \textit{"weak Schur templates"}, as well as an associated sequence \(\WS^+(n)\). We find templates and use them to provide 
+new lower bounds for weak Schur numbers. Finally, we give a short explanation for the new lower bound \(\WS(6) \geqslant 646\) which 
+was not directly obtained with a template, contrary to the other lower bounds given in this article.
+
+\subsection{Inequality for weak Schur numbers using Schur and weak Schur numbers}
+
+Up to now, no equivalent for weak Schur numbers of Abbott and Hanson's construction for Schur numbers
+\cite{AbbottHanson} was known. Here we give a general lower bound for weak Schur numbers as a function of both
+regular and weak Schur numbers.
+
+\begin{theorem}
+\label{thm:WS-ab}
+\begin{sloppypar}
+Let \((p,k), (q,n) \in (\mathbb{N}^*)^2\). If there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\)
+and a sum-free \(k\)-partition of \([\![1,p]\!]\) then there is a partition of
+\({[\![1,p(q+\left \lceil \frac{q}{2} \right \rceil + 1)+q]\!]}\) into \(n+k\) weakly sum-free subsets.
+\end{sloppypar}
+\end{theorem}
+
+As Theorem \ref{thm:WS-ab} is actually a particular case of a more general theorem (Theorem \ref{thm:WStemp}) which will
+be formulated after the introduction of templates for weak Schur number,
+we only outline the demonstration. Its complete \hyperref[PreuveThm]{proof} using templates 
+for weak Schur numbers is in Subsection \ref{ConstructionWS}.
+
+Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a weakly sum-free \(n\)-partition of \([\![1,q]\!]\) 
+and a sum-free \(k\)-partition of \([\![1,p]\!]\). Let \(a \in \mathbb{N}\) with \(a > q\)
+and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
+\(l = a - q - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = q - r\).
+
+First, we construct the following table with \(a\) columns and \(p+1\) rows containing the integers from \([\![1, ap + q]\!]\). 
+The columns are numbered from \(-l\) to \(+q\). This table is made of three different blocks.
+
+\begin{itemize}
+	\item \(\mathcal{T}\) (the "tail"): in the row indexed by 0: numbers from \([\![1,q]\!]\).
+	\item \(\mathcal{R}\) (the "rows"): the integers in columns from \(-l\) to \(+r\).
+	\item \(\mathcal{C}\) (the "columns"): the integers in the last \(w\) columns.
+\end{itemize}
+
+\setlength{\arraycolsep}{2pt}
+
+\begin{figure}[H]
+\renewcommand{\arraystretch}{1.5}
+\begin{small}
+\[
+\begin{NiceArray}{*{13}{c}}[corners={NW,SW},hvlines,first-row,last-row,first-col]
+\CodeBefore
+	\cellcolor{green}{1-6}
+	\cellcolor{green}{1-7}
+	\cellcolor{cyan}{1-8}
+	\cellcolor{green}{1-9}
+	\cellcolor{cyan}{1-10}
+	\cellcolor{cyan}{1-11}
+	\cellcolor{cyan}{1-12}
+	\cellcolor{green}{1-13}
+	\cellcolor{red}{2-1}
+	\cellcolor{red}{2-2}
+	\cellcolor{red}{2-3}
+	\cellcolor{red}{2-4}
+	\cellcolor{red}{2-5}
+	\cellcolor{red}{2-6}
+	\cellcolor{red}{2-7}
+	\cellcolor{red}{2-8}
+	\cellcolor{red}{2-9}
+	\cellcolor{cyan}{2-10}
+	\cellcolor{cyan}{2-11}
+	\cellcolor{cyan}{2-12}
+	\cellcolor{green}{2-13}
+	\cellcolor{yellow}{3-1}
+	\cellcolor{yellow}{3-2}
+	\cellcolor{yellow}{3-3}
+	\cellcolor{yellow}{3-4}
+	\cellcolor{yellow}{3-5}
+	\cellcolor{yellow}{3-6}
+	\cellcolor{yellow}{3-7}
+	\cellcolor{yellow}{3-8}
+	\cellcolor{yellow}{3-9}
+	\cellcolor{cyan}{3-10}
+	\cellcolor{cyan}{3-11}
+	\cellcolor{cyan}{3-12}
+	\cellcolor{green}{3-13}
+	\cellcolor{yellow}{4-1}
+	\cellcolor{yellow}{4-2}
+	\cellcolor{yellow}{4-3}
+	\cellcolor{yellow}{4-4}
+	\cellcolor{yellow}{4-5}
+	\cellcolor{yellow}{4-6}
+	\cellcolor{yellow}{4-7}
+	\cellcolor{yellow}{4-8}
+	\cellcolor{yellow}{4-9}
+	\cellcolor{cyan}{4-10}
+	\cellcolor{cyan}{4-11}
+	\cellcolor{cyan}{4-12}
+	\cellcolor{green}{4-13}
+	\cellcolor{red}{5-1}
+	\cellcolor{red}{5-2}
+	\cellcolor{red}{5-3}
+	\cellcolor{red}{5-4}
+	\cellcolor{red}{5-5}
+	\cellcolor{red}{5-6}
+	\cellcolor{red}{5-7}
+	\cellcolor{red}{5-8}
+	\cellcolor{red}{5-9}
+	\cellcolor{cyan}{5-10}
+	\cellcolor{cyan}{5-11}
+	\cellcolor{cyan}{5-12}
+	\cellcolor{green}{5-13}
+	\cellcolor{cyan}{6-10}
+	\cellcolor{cyan}{6-11}
+	\cellcolor{cyan}{6-12}
+	\cellcolor{green}{6-13}
+\Body
+	& & & & & & \Block{1-8}{\overbrace{\hphantom{---------------------------}}^{\mathcal{T}}} \\
+	& & & & & & 1 & 2 & ... & r & r + 1 & ... & q - 1 & q \\
+	\Block{5-1}{\mathcal{R} \left\{ \vphantom{\begin{array}{l} . \\ . \\ . \\ . \\ . \\ . \\ . \\  . \end{array}} \right.}
+	& a - l & a - l + 1 & ... & a - 1 & a & a + 1 & ... & a + r - 1 & a + r & a + r + 1 & ... & a + q - 1 & a + q \\
+	& 2 a - l & ... & ... & ... & 2 a & ... & ... & ... & 2 a + r & ... & ... & ... & 2 a + q \\
+	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
+	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
+	& p a - l & ... & ... & ... & p a & ... & ... & ... & p a + r & ... & ... & ... & p a + q \\
+	& & & & & & & & & & \Block{1-4}{\underbrace{\hphantom{--------------}}_{\mathcal{C}}} \\
+\end{NiceArray}
+\]
+\end{small}
+\label{SchemaWS}
+\caption{Construction of the weakly sum-free coloring}
+\end{figure}
+
+\setlength{\arraycolsep}{6pt}
+
+\noindent \underline{\textbf{\(\mathcal{T}\) block}}
+\par
+We color this block using the weakly sum-free coloring of \([\![1,q]\!]\) with colors \(1, ..., n\).
+
+\noindent \underline{\textbf{\(\mathcal{R}\) block}}
+\par
+We use the colors \(n + 1, ..., n + k\) in this block. We color an integer \(x\) according to its line number \(\lambda(x)\).
+For any \(x \in \mathcal{R}\), we color \(x\) with \(n + c\) where \(c\) is the color of \(\lambda(x)\) in the sum-free coloring of  \([\![1,p]\!]\).
+Let \((x, y) \in \mathcal{R}^2\). The cases are twofold.
+
+\begin{itemize}
+	\item \underline{\(\lambda(x+y) = \lambda(x) + \lambda(y)\)} \\
+	If \(x + y\in \mathcal{R}\), we use the sum-free property of the coloring of \([\![1,p]\!]\). Otherwise, \(x + y\in \mathcal{C}\) which 
+	is fine because we only use colors \(1, ..., n\) in block \(\mathcal{C}\).
+	\item \underline{\(\lambda(x+y) \neq \lambda(x) + \lambda(y)\)} \\
+	In this case, we do not have information about the color of \(\lambda(x+y)\). Thereby, we want to have
+	\(x+y \in \mathcal{C}\). A simple solution is to limit the horizontal displacement made by summing the two integers.
+	That is, when the sum's row number is different from \(\lambda(x) + \lambda(y)\), to upper bound 
+	\(|x + y - (\lambda(x) + \lambda(y)) a|\) so that \(x+y\) stays in \(\mathcal{C}\). There, the maximal displacement 
+	to the left (resp. to the right) is \(2l\) (resp. \(2r\)). Not crossing entirely \(\mathcal{C}\) by going to the left is then 
+	expressed as \(-2l > -a + r\). Likewise, not going to far to the right is expressed as \(2r < a - l\). It can then be written
+	as \(\max(l, r) \leqslant w\).
+\end{itemize}
+
+\noindent \underline{\textbf{\(\mathcal{C}\) block}}
+\par
+In this block, we use colors \(1, ..., n\). We color an integer \(x\) according to its projection on the first row \(\pi(x)\) offeset by \(a\), 
+that is its column number. A simple solution is to color \(x\) with the same color as \(\pi(x) - a\) in the weakly sum-free coloring of 
+\([\![1,q]\!]\). As long as \(2q \leqslant a + r\) (not going two far to the right) and there is no \(x \in \pi(\mathcal{C}) - a\) such that 
+\(2x \in \pi(\mathcal{C}) - a\), we do not have a sum in \(\mathcal{C}\) when taking two numbers in the same colum. Finally, the 
+weakly sum-free property of the coloring of \([\![1,q]\!]\) guarantees that if \(x \in [\![1,r]\!]\) and \(y \in \mathcal{C}\) are colored 
+the same, then \(x + y\) is colored differently.
+
+Setting \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) satsfies these 
+constraints: it corresponds to Theorem \ref{thm:WS-ab}. \\
+
+By setting \(q = \WS (n)\) and \(p = S(k)\) in Theorem \ref{thm:WS-ab}, one obtains the following corollary.
+
+\begin{corollary}
+\label{cor:ineqWS-S}
+\(\WS (n+k) \geqslant S(k) \left (\WS (n) + \left \lceil \displaystyle \frac{\WS (n)}{2} \right \rceil +1 \right) + \WS (n)\)
+for all \((n,k) \in (\mathbb{N}^*)^2\).
+\end{corollary}
+
+This can be seen as an equivalent for weak Schur numbers of Abott and Hanson's construction for Schur numbers 
+\cite{AbbottHanson}. This formula also includes the results from \cite{RowleyWS} as a special case. For \(n>2\), 
+the formula from Corollary \ref{cor:ineqWS-S} does not give new lower bounds.
+
+\begin{remark}
+The inequality from Corollary \ref{cor:ineqWS-S} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
+odd in Theorem \ref{thm:WS-ab}). However, it lengthens the proof and it is never useful in practice.
+\end{remark}
+\par
+Now, we introduce WS-templates and the sequence \(\WS^+\) in order to generalize the above construction.
+
+\subsection{Definition of \([\![ 1, \WS^+ ]\!]\)}
+\label{DefinitionWS+}
+
+In this subsection, we introduce WS-templates and prove calculative results for the general construction
+theorem on templates for weak Schur numbers.
+
+\begin{definition}
+Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). We define:
+\[ \pi_{a,b}:x \longmapsto (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x \mod a).\]
+\end{definition}
+
+\begin{sloppypar}
+If there is no confusion on the \(a\) and \(b\) to use, \(\pi_{a, b}\) is denoted by \(\pi\). Notice that for all \(x \in \mathbb{Z}\), 
+\({\pi(x) = x \mod a}\) and for all \(x \in [\![b + 1, a + b]\!], b + 1 \leqslant \pi(x) \leqslant a + b\).
+\end{sloppypar}
+
+\begin{sloppypar}
+Function \(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
+calculative properties on \(\pi\) reflecting the behaviour of an element's column number in \hyperref[SchemaWS]{Figure 3} and
+that we will use later when we introduce WS-templates.
+\end{sloppypar}
+
+\begin{proposition}
+\label{prop1}
+\[
+\forall x \in [\![b + 1, a + b]\!], \pi(x) = x.
+\]
+\end{proposition}
+
+\begin{proof}
+\begin{sloppypar}
+Let \(x \in [\![b + 1, a + b]\!]\). If \(x < a\) then \(x \mod a = x \notin [\![1, b]\!]\). Hence \(\pi(x) = x\).
+Otherwise, \({x \mod a = x - a \in [\![1, b]\!]}\). Hence \({\pi(x) = x - a + a = x}\).
+\end{sloppypar}
+\end{proof}
+
+\begin{proposition}
+\label{prop2}
+Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\). Then
+\[
+\pi(x+\pi(y)) = \pi(x+y).
+\]
+\end{proposition}
+
+\begin{proof}
+It is a direct consequence of \(\pi(x) = x \mod a\). \\
+\end{proof}
+
+\begin{proposition}
+\label{prop3}
+Let x \(\in [\![1,b]\!]\) and \(y \in \mathbb{N}^*\) such that \(x+\pi(y) \leqslant a+b\). Then
+\[
+\pi(x+y)=x+\pi(y).
+\]
+\end{proposition}
+
+\begin{proof}
+\(\pi(y) \geqslant b + 1\) and thus \(b + 1 \leqslant x + \pi(y) \leqslant a + b\).
+\[
+\begin{array}{l l l l}
+	\pi(x + y) & = & \pi(x + \pi(y)) & \text{by Proposition \ref{prop2}} \\
+	 & = & x + \pi(y) & \text{by Proposition \ref{prop1}}
+\end{array}
+\]
+\end{proof}
+
+\begin{proposition}
+\label{prop4}
+Let \((x,y)\in (\mathbb{N}^*)^2\). Then
+\[
+\pi(\pi(x)+\pi(y))=\pi(x+y).
+\]
+\end{proposition}
+
+\begin{proof}
+It is a direct consequence of \(\pi(x) = x \mod a\). \\
+\end{proof}
+
+After defining the function related to the column number of each element in \hyperref[SchemaWS]{Figure 3},
+we introduce the function related to its line number.
+
+\begin{definition}
+Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
+\[ \lambda_{a,b}:x \longmapsto 1+ \left\lfloor\dfrac{x-b-1}{a}\right\rfloor.\]
+\end{definition}
+
+If there is no confusion on the \(a\) and \(b\) to use, \(\lambda_{a, b}\) is denoted by \(\lambda\).
+
+Function \(\lambda\) maps an element \(x\) to its line number as mentioned in the intuitive explanation.
+As we have just done with \(\pi\), we prove three more calculative results on both \(\pi\) and \(\lambda\) that are used in
+Subsection \ref{ConstructionWS}.
+
+\begin{proposition}
+\label{prop5}
+Let \(x\in \mathbb{N}^*\). Then
+\[
+x=a\lambda(x)+\pi(x)-a.
+\]
+\end{proposition}
+
+\begin{proof}
+Let \((a,b)\in (\mathbb{N}^*)^2\) such that \(a>b\) and let \(x\in \mathbb{N}^*\). \\
+We have \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x-b-1}{a}\right\rfloor+(x \mod a)+ a \mathds{1}_{ [\![0,b]\!]}(x \mod a)\).
+
+\begin{itemize}
+\item If \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\).
+\item If \(x \mod a \leqslant b\) then \(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\).
+\end{itemize}
+\end{proof}
+
+\begin{proposition}
+\label{prop6}
+Let \(x, y \in \mathbb{Z}\) such that \(\lambda(x + y) = \lambda(y)\). Then
+\[
+\pi(x + y) = x + \pi(y).
+\]
+\end{proposition}
+
+\begin{proof}
+By applying Proposition \ref{prop5} twice, we get \(a \lambda(x + y) + \pi(x + y) - a = x + y = x + a \lambda(y) + \pi(y) - a\).
+The result is then obtained by simplifying the equality. \\
+\end{proof}
+
+\begin{proposition}
+\label{prop7}
+Let \(x, y \in \mathbb{Z}\) such that \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\). Then
+\[
+\lambda(x + y) = \lambda(x) + \lambda(y).
+\]
+\end{proposition}
+
+\begin{proof}
+By Proposition \ref{prop5}, \(x + y = a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a\). Then
+\[
+\begin{array}{l l l}
+	\lambda(x + y) & = & \left \lfloor \dfrac{x + y - b - 1}{a} \right \rfloor + 1 \vspace{1mm} \\
+	 & = & \left \lfloor \dfrac{a (\lambda(x) + \lambda(y)) + \pi(x) + \pi(y) - 2 a - b - 1}{a} \right \rfloor + 1 \vspace{1mm} \\
+	 & = & \lambda(x) + \lambda(y) - 1 + \left \lfloor \dfrac{\pi(x) + \pi(y) - b - 1}{a}\right\rfloor \\
+	 & = & \lambda(x)+\lambda(y) -1 +1 ~~~~\text{since } \pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!] \\
+	 & =& \lambda(x)+\lambda(y).
+\end{array}
+\]
+\end{proof}
+
+\begin{definition}
+Let \( (a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\). Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
+This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WS-template) with width \(a\) and \(n\) colors when:
+
+\begin{itemize}
+\item \(\forall i \in [\![1, n]\!], A_i\) is weakly-sum-free,
+\item \(\forall i \in [\![1, n]\!], A_i\backslash [\![1, b]\!]\) is sum-free,
+\item For \(A_n\) (the special subset):
+	\[
+	\forall (x,y) \in A_n^2, \,x+y>b+2a \implies x+y-2a\notin A_n,
+	\]
+\item For the others subsets
+	\[
+	\forall i \in [\![1,n-1]\!], \, \forall(x,y) \in A_i^2, \, x+y>a+b \implies \pi(x+y) \notin A_i.
+	\]
+\end{itemize}
+\end{definition}
+
+Note that the special color \(n\) is not necessarily the last color by order of appearance, any color can play this role.
+Now, we introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.
+
+\begin{definition}
+Let \( (n,b) \in (\mathbb{N}^*)^2\). If there is \(a\) such that there is a \(b\)-WS-template with width \(a\)
+and \(n\) colors, we define:
+\[
+\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there is a } b \text{-WS-template with width } a \text{ and } n \text{ colors} \}.
+\]
+If there is no such \(a\), we set \(\WS_b^+(n) = 0\).
+\end{definition}
+
+\begin{definition}
+Let \( n \in \mathbb{N}^*\). We define:
+\[
+\WS^+(n)=\max_{b\in \mathbb{N}^*} \WS_b^+(n).
+\]
+\end{definition}
+The following proposition shows how \(\WS^+(n)\) compares to weak Schur numbers.
+\begin{proposition}
+Let \(n \in [\![2, +\infty]\!]\). Then:
+\[
+\frac{3}{2} \WS (n-1)+1 \leqslant \WS^+(n) \leqslant \WS (n).
+\]
+\end{proposition}
+
+\begin{proof}
+The lower bound comes from Corollary \ref{cor:ineqWS-S}.
+The upper bound comes from the fact that a WS-template with width \(a\) and \(n\) colors is in particular a partition of
+\([\![1, a]\!]\) into \(n\) weakly sum-free subsets. \\
+\end{proof}
+
+Having established these properties, we prove our main result.
+
+\subsection{Construction of weak Schur partitions using WS-templates}
+\label{ConstructionWS}
+
+Theorem \ref{thm:Stemp} describes a manner to extend an S-template into a larger Schur partitions using other Schur 
+partitions. Likewise, a WS-template can be extended into larger weak Schur partitions by using Schur partitions. This 
+is the object of the following theorem.
+
+\begin{theorem}
+\label{thm:WStemp}
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there are a sum-free \(k\)-partition of
+\([\![1,p]\!]\) and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
+then there is a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
+\end{theorem}
+
+\begin{proof}
+\begin{sloppypar}
+Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Let \(f\) and \(g\) be colorings associated 
+to the \(b\)-WS-template and to the sum-free partition of \([\![1,p]\!]\), respectively: 
+\({f : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({g : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, 
+we assume that the sum-free coloring of \([\![1, p]\!]\) is ordered.
+\end{sloppypar}
+
+\par
+NB: To keep the notation short, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted in the following five predicates.
+
+The sum-free conditions are expressed as:
+\[
+\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),
+\]
+\[
+\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).
+\]
+
+The weakly sum-free condition is expressed as:
+\[
+\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
+\begin{array}{l}
+	f(x) = f(y) \\
+	x \neq y
+\end{array}
+\right. \Longrightarrow f(x+y) \neq f(x),
+\]
+
+The additionnal constraints for the WS-template are expressed as:
+\[
+\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
+\begin{array}{l}
+	f(x) = f(y) \leqslant n \\
+	x + y > a + b
+\end{array}
+\right. \Longrightarrow f(\pi(x+y)) \neq f(x),
+\]
+\[
+\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
+\begin{array}{l}
+	f(x) = f(y) = n + 1 \\
+	x + y > 2 a + b
+\end{array}
+\right. \Longrightarrow f(x+y - 2 a) \neq f(x).
+\]
+
+We split \([\![1, p a + b]\!]\) into three subsets. \\
+NB: To keep the notation short, the restriction to \([\![b + 1, p a + b]\!]\) of \(\pi\) defined in Subsection \ref{DefinitionWS+}
+is denoted by \(\pi\) in the hereunder equations:
+
+\begin{itemize}
+	\item \(\mathcal{T} = [\![1, b]\!]\),
+	\item \(\mathcal{C} = \pi^{-1}(f^{-1}([\![1, n]\!]))\),
+	\item \(\mathcal{R} = \pi^{-1}(f^{-1}(\{n + 1\}))\).
+\end{itemize}
+
+We define a coloring \(h\) of \([\![1, p a + b]\!]\) using \( [\![1,n+k]\!]\) colors:
+\[
+\begin{array}{c c c l}
+	h : & [\![1, p a + b]\!] & \longrightarrow & [\![1,n+k]\!],\\
+	& x & \longmapsto &
+	\left\{ \begin{array}{l l}
+		f(x), & \text{if}~x \in \mathcal{T}, \\
+		f(\pi(x)), & \text{if}~x \in \mathcal{C}, \\
+		n + g(\lambda(x)), & \text{if}~x \in \mathcal{R}.
+	\end{array} \right.
+\end{array}
+\]
+
+Function \(h\) is well defined since sets \(\mathcal{T}, \mathcal{C}, \mathcal{R}\) partition \([\![1, p a + b]\!]\).
+Now, we prove that \(h\) is a weakly sum-free coloring. Let \(x,y \in [\![1, p a + b]\!]\) be such that \(x \neq y\),
+\(h(x) = h(y)\), and \(x+y \leqslant p a+ b\). We claim that \(h(x+y) \neq h(x)\). Nine cases are to be distinguished
+according to which of the sets \(\mathcal{T}, \mathcal{C}, \mathcal{R}\) \(x\) and \(y\) belong to. It is
+sufficient to check only six cases out of nine since \(x\) and \(y\) play symmetric roles. \\
+
+\noindent \underline{\textbf{Case 1:} \((x,y) \in \mathcal{T}^2\)}
+\par
+If \(x + y \leqslant b\) then \(h(x+y)=f(x+y)\). Otherwise, \(b < x+y < a+b\) since \(b < a\) and
+therefore \(\pi(x + y) = x +y\) (Proposition \ref{prop1}). Hence in both cases \(h(x+y)=f(x+y)\). Given that
+\(f\) is a weakly sum-free coloring, \(f(x + y) \neq f(x)\) since \(f(x)=h(x)=h(y)=f(y)\) and \(x \neq y \). That
+is \(h(x + y) \neq h(x)\). \\
+
+\noindent \underline{\textbf{Case 2:} \((x,y) \in \mathcal{T} \times \mathcal{C}\)}
+\par
+Given that \(h(x) = h(y)\) and by definition of \(h\), \(f(x) = f(\pi(y))\). Besides, \(f(\pi(y)) \leqslant n\) since
+\(y \in \mathcal{C}\). Two cases are to be distinguished according to the value of \(x + \pi(y)\).
+\begin{itemize}
+\item \begin{sloppypar}
+	If \(x + \pi(y) \leqslant a + b\) then \(f(x + \pi(y)) = f(\pi(x + y))\) (Proposition \ref{prop3}). Given that \(f\) is
+	a weakly sum-free coloring, \(f(x+\pi(y)) \neq f(x)\) since \(f(x)=f(\pi(y))\) and \(x \neq \pi(y)\) since
+	\({x \leqslant b < \pi(y)}\).
+	\end{sloppypar}
+\item \begin{sloppypar}
+	If \(x+\pi(y)> a+b\) then given that \(f\) is a WS-template and since \({f(x) = f(\pi(y)) \leqslant n}\),
+	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (Proposition \ref{prop2}), such that
+	\({f(\pi(x+ y)) \neq f(x)}\).
+	\end{sloppypar}
+\end{itemize}
+\par
+In both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore
+\(h(x+y) \neq h(x)\) since \(f(x) = h(x)\). Otherwise, \(f(\pi(x+y)) = n + 1\) and thus \(h(x+y) > n\). In particular,
+\(h(x + y) \neq h(x)\) since \(h(x) = h(y) \leqslant n\). \\
+
+\noindent \underline{\textbf{Case 3:} \((x,y) \in \mathcal{T} \times \mathcal{R}\)}
+\par
+Necessarily \(h(x) = h(y) = n + 1\). Two cases are to be distinguished according to the value of \(\lambda(x+y)\).
+\begin{itemize}
+\item If \(\lambda(y)=\lambda(x+y)\) then \(\pi(x + y) = x + \pi(y)\) (Proposition \ref{prop6}). By definition of
+	\(h\), \(f(x) = f(\pi(y))\). Given that \(f\) is a weakly sum-free coloring, \(f(x + \pi(y)) \neq f(x)\) since
+	\(f(x) = f(\pi(y))\) and \(x \neq \pi(y)\) since \({x \leqslant b < \pi(y)}\). Hence \(h(x + y) \neq h(x)\).
+\item If \(\lambda(y) \neq \lambda(x + y)\) then \(\lambda(x + y) = \lambda(y) + 1\) since \(x \leqslant b < a\).
+	Besides, \(n + 1 = h(y) = n +  g(\lambda(y))\). Hence \(g(\lambda(y)) = 1\). Moreover \(g(1) = 1\) since \(g\)
+	is an ordered coloring. Therefore, given that \(g\) is sum-free, \(g(\lambda(y) + 1) \neq 1\). If \(\pi(x + y) \in
+	A_{n + 1}\) then \(h(x + y) = n + g(\lambda(x + y)) \neq n + 1\). Otherwise, \(h(x + y) \leqslant n\).
+\end{itemize}
+\par
+In both cases \(h(x + y) \neq h(x)\).
+
+\noindent \underline{\textbf{Case 4:} \((x,y) \in \mathcal{C}^2\)}
+\par
+By definition of \(h\) and since \(h(x)=h(y)\), \(f(\pi(x)) = f(\pi(y))\). Two cases are to be distinguished according
+to the value of \(\pi(x)+\pi(y)\).
+\begin{itemize}
+\item If \(\pi(x) + \pi(y) \leqslant a+b\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(f(\pi(x + y)) \neq f(\pi(x))\) since
+	\(f\) is sum-free for \(x>b\)
+\item \begin{sloppypar}
+	If \(\pi(x)+\pi(y)>a+b\) then given that \(f\) is a WS-template, \({f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x))}\) since
+	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (Proposition \ref{prop4}). Hence \({f(\pi(x + y))
+	\neq  f(\pi(x))}\).
+	\end{sloppypar}
+\end{itemize}
+\par
+In both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore
+\(h(x+y) \neq h(x)\) since \(f(x) = h(x)\). Otherwise, \(f(\pi(x+y)) = n + 1\) and thus \(h(x+y) > n\). In particular,
+\(h(x + y) \neq h(x)\) since \(h(x) = h(y) \leqslant n\). \\
+
+\noindent \underline{\textbf{Case 5:} \((x,y) \in \mathcal{C} \times \mathcal{R}\)}
+\par
+By definition of function \(h\), \(h(x) \neq h(y)\).\\
+
+\noindent \underline{\textbf{Case 6:} \((x,y) \in \mathcal{R}^2\)}
+\par
+In particular \(f(\pi(x)) = f(\pi(y))=n + 1\). Three cases are to be distinguished according to the value of \(\pi(x) + \pi(y)\).
+\begin{itemize}
+\item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\)
+	(Proposition \ref{prop7}). By definition of \(h\) and since \(h(x) = h(y)\), \(g(\lambda(x)) = g(\lambda(y))\).
+	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x))\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\)
+	then \(h(x + y) = n + g(\lambda(x + y))\). And \(h(x) = n + g(\lambda(x))\). Therefore, \(h(x + y)  \neq h(x)\).
+	Otherwise \(h(x+y) \leqslant n < h(x)\). In particular \(h(x + y) \neq h(x)\).
+\item If \(\pi(x)+\pi(y)>2a+b\) then \(f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x)) = n + 1\) since \(f\) is a \(b\)-WS template and
+	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (Proposition \ref{prop4}), \(f(\pi(x+y)) \neq n + 1\).
+\item \begin{sloppypar}
+	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(f_{| [\![b, a + b ]\!]}\) is
+	sum-free, \({f(\pi(x) + \pi(y)) \neq f(\pi(x)) = n + 1}\). That is \({f(\pi(x + y)) \neq n + 1}\) (Proposition \ref{prop1}).
+	\end{sloppypar}
+\end{itemize}
+\par
+In both of the last two cases, \({f(\pi(x + y)) \neq n + 1}\) that is \(x+y \in \mathcal{C}\). Therefore \(h(x+y) < n \leqslant h(x)\).
+In particular, \(h(x + y) \neq h(x)\). \\
+\end{proof}
+
+We go back to Theorem \ref{thm:WS-ab} which can be seen as a particular case of Theorem \ref{thm:WStemp} in the same way Abott and Hanson's 
+construction \cite{AbbottHanson} can be seen as a particular case of Theorem \ref{thm:Stemp}. Its deferred proof is given below.
+
+\begin{proof}[\textsc{Proof of Theorem \ref{thm:WS-ab}.}]
+\label{PreuveThm}
+Let \((q, n) \in (\mathbb{N}^*)^2\) such that there is a partition of \([\![1, q]\!]\) into n weakly sum-free subsets. 
+Let \(f: [\![1, q]\!] \rightarrow [\!]1, n]\!]\) be a weakly sum-free colouring.
+Let \(b=q\) and \(a = q + \left \lceil \dfrac{q}{2} \right \rceil + 1\). A new colouring \(g\) is defined as follows:
+
+\[
+\begin{array}{c c c l}
+	g : & [\![1, a + b]\!] & \longrightarrow & [\![1, n + 1]\!], \\
+	& x & \longmapsto &
+		\left\{ \begin{array}{l l}
+			f(x), & \text{if}~x \in [\![1, b]\!],  \\
+			n + 1, & \text{if}~x \in [\![b + 1, 2 b + 1]\!], \\
+			f(x - a), & \text{if}~x \in  [\![2 b + 2, a + b]\!].
+		\end{array} \right.
+\end{array}
+\]
+
+We claim that \(g\) is a \(b\)-WSF-template with width \(a\) and \(n + 1\) colours.
+
+\begin{itemize}
+\item Function \(g_{|[\![b + 1, a + b]\!]}\) is a sum-free colouring. Indeed, let \((x, y) \in 
+	[\![b + 1, a + b]\!]^2\) such that \(g(x) = g(y)\). If \(g(x) = n + 1\) then \(z = x + y > 2 b + 1\) 
+	and therefore, either \(z > a + b\) or \(f(z) \neq n + 1\). Otherwise, \(x + y > a + b\).
+\item Function \(g\) is a weakly sum-free colouring. Indeed, let \((x, y) \in [\![1, a + b]\!]^2\) such that 
+	\(z = x + y \leqslant a + b\) and \(g(x) = g(y)\). Given that \(x\) and \(y\) have symmetric roles, 
+	we can assume that \(x \leqslant y\). If \(x > b\) then \(g(z) \neq g(x)\) as seen above. If \(y \leqslant b\) then 
+	\(f(x) = g(x) = g(y) = f(y) \leqslant n\) and either \(z \leqslant a + b\) and \(f(z) \neq f(x)\) since \(f\) is a weakly 
+	sum-free colouring or \(a + b + 1 \leqslant z \leqslant 2 b\) and \(g(z) = n + 1\); therefore \(g(z) \neq g(x)\). If 
+	\(x \leqslant b\) and \(y > b\) then \(g(x) = f(x)\), \(g(y) = f(y - a)\) and \(g(z) = f(z - a)\).We have \(x \neq y - a\) 
+	(otherwise, we would have \(a + b \geqslant z = 2 y  - a \geqslant 4 b + 4 - a > a + b\)) and thus \(f(x + y - a) \neq f(x)\),
+	that is \(g(z) \neq g(x)\).
+\item Colour \(n + 1\) verifies the additionnal constraints for the special colour. Indeed, \(b + 2 a \geqslant 4 b + 2\). 
+	Hence, \(\forall (x, y) \in g^{-1}(\{n + 1\}), x + y \leqslant b + 2 a\).
+\item Colours \(1, ..., n\) verify the additionnal constraints for the regular colours. Indeed, let 
+	\((x, y) \in g^{-1}([\![1, n]\!])\) such that \(x + y > a + b\). Given that \(x\) and \(y\) have symmetric roles, 
+	we can assume that \(x \leqslant y\). Necessarily \(y \geqslant 2 b + 2\). If \(x \leqslant b\) then 
+	\(z = x + y \in [\![a + b + 1, a + 2 b]\!]\) and therefore \(\pi(z) \in [\![b + 1, 2 b]\!]\). Otherwise, 
+	\(z = x + y \in [\![4 b + 4, 2 a + 2 b]\!]\) and therefore \(\pi(z) \in [\![b + 1, 2 b]\!]\). Hence, in both cases, 
+	\(g(\pi(z)) \neq g(x)\).
+\end{itemize}
+
+The result is then obtained by applying Theorem \ref{thm:WStemp}. \\
+\end{proof}
+
+By setting \(p = S(k)\) and \(a = \WS^+(n + 1)\) in Theorem \ref{thm:WStemp}, one obtains:
+
+\begin{corollary}
+\label{cor:ineqWS+}
+Let \(n,k \in \mathbb{N}^*\) and set \( b_{max} = \max \{b\in \mathbb{N}^*/ \WS_b^+(n+1) = \WS^+(n+1)\}\).
+Then:
+\[
+\WS(n+k) \geqslant S(k) \WS^+(n+1)+b_{max}.
+\]
+\end{corollary}
+
+\begin{remark}
+In the S-template construction for Schur numbers, the additive constant comes from the fact that the special color does
+not necessarily appear at the very begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by
+\[
+\max_{b \in \mathbb{N}^*} \left\{\min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}.
+\]
+\end{remark}
+
+As in Corollary \ref{cor:ineqS}, the additive constant Theorem \ref{thm:WStemp} can be improved 
+by weakening the hypotheses made on the last row. The principle behind it is the same as in Proposition \ref{prop:rafStemp}.
+
+\begin{proposition}
+\label{prop:tunelastrow}
+Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WS-template with width \(p\) and \(k\) colors. Let
+\(c \in \mathbb{N}\) and assume there is a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),
+
+\begin{itemize}
+\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, a + b]\!],  \left\{
+	\begin{array}{l}
+		f(x) = f(y) \\
+		\pi(x + y) \leqslant b + c
+	\end{array}
+	\right. \implies g(\pi(x + y)) \neq f(x)\),
+\item \(\forall (x, y) \in  [\![1, a + b]\!] \times  [\![b + 1, b + c]\!], \left\{
+	\begin{array}{l}
+		f(x) = g(y) \\
+		\pi(x + y) \leqslant b + c
+	\end{array}
+	\right. \implies g(\pi(x + y)) \neq f(x)\).
+\end{itemize}
+
+Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(x \longmapsto g(x - p S(n))\), we have\\
+\[ \WS(n+k) \geqslant \WS^+(k+1) S(n) + b + c.\]
+\end{proposition}
+
+The WS-templates can actually be fine-tuned further. However, it only gives minor improvements (most likely only an 
+additive constant) while increasing the size of the search space.
+
+\par
+These modifications rely on one main observation: the first row (excluding the "tail") has constraints that other rows do not 
+have because of the tail, especially if the special color appears in the tail as well. Indeed, the line number of the
+sum of two numbers in the tail is never greater than one. Therefore, having a coloring dedicated to 
+the first row and another coloring dedicated to the repeating pattern would weaken the constraints on the repeating pattern.
+
+\par
+These additionnal constraints on the first row imply additionnal constraints on the rows of the its color (compared to other 
+colors). However, one may notice that there are never two consecutive rows of this color. Moreover these additionnal constraints 
+mostly concern two consecutive rows. Having a special coloring for rows of this color as well as another color dedicated to the 
+first row avoids enforcing these constraints specific to one color on the other colors and thus on the main repeating pattern.
+
+\par
+Finally, given that the color of the first row is different from the special color of the main repeating pattern, coloring \(g\) in
+Proposition \ref{prop:tunelastrow} can exploit this difference. \\
+
+There is a construction theorem for WS-templates as well.
+
+\begin{theorem}
+\label{thm:compWStemp}
+Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there are an S-template with width
+\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there is a \(pb\)-WS-template
+with width \(pq\) and \((n+k)\) colors.
+\end{theorem}
+
+\begin{proof}
+The idea is the same as in theorem \ref{thm:WStemp}. The properties specific to WS-templates are inherited 
+from both the S-template and the WS-template. \\
+\end{proof}
+
+Theorem \ref{thm:compWStemp} yields the following corollary.
+
+\begin{corollary}
+Let \(n, k \in \mathbb{N}^*\). Then
+\[
+\WS^+(n+k) \geqslant S^+(k+1) \WS^+(n).
+\]
+\end{corollary}
+
+\subsection{New lower bounds for Weak Schur numbers}
+
+We produced WS-templates using the lingeling SAT solver \cite{Lingeling2017}, hence providing lower bounds on \(WS^+\) 
+and inequalities of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) 
+(in the lexicographic order). Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.
+
+\par
+Here are the inequalities given by the current best WS-templates. The \hyperref[WS-templates]{template} 
+corresponding to the third inequality can be found in \ref{WS-templates}.
+
+\begin{align}
+	WS(n + 1) &\geqslant  4\,S(n)  +  2 \label{WS(n+1)} \\
+	WS(n + 2) &\geqslant  13\,S(n)  +  8 \label{WS(n+2)} 
+\end{align}
+
+Inequalities (\ref{WS(n+1)}) and (\ref{WS(n+2)}) were found by Rowley, they are detailed in \cite{RowleyWS}.
+
+\begin{align}
+	WS(n + 3) &\geqslant  42\,S(n)  +  24 \label{WS(n+3)} \\
+	WS(n + 4) &\geqslant  132\,S(n)  +  26 \label{WS(n+4)}
+\end{align}
+
+Inequality (\ref{WS(n+3)}), found with a SAT solver \cite{Lingeling2017}, cannot be improved (with this 
+definition of WS-template). It uses the first 
+sophistication explained in Subsection \ref{ConstructionWS} in order to add
+the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining an S-template with 
+width 33 with a WS-template with width 4. The best template we could find with a computer search gives the 
+inequality \(\WS(n+4) \geqslant 127 S(n) + 68\). It was also found with the SAT solver. In order to reduce the search space, 
+we only looked for WS-templates with five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
+special color was the last by order of appearance. We expect that better WS-templates with \(n \geqslant 5\) 
+colors can be found but one would have not to use the above assumptions.
+
+Like in  Subsection \ref{subsec:lowS}, we compute the lower bounds given by Inequalities (\ref{WS(n+1)}),
+(\ref{WS(n+2)}), and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound for each value of \(n\) is highlighted.
+
+\begin{table}[H]
+
+\label{LowerBoundsWS}
+\[
+\begin{array}{c}
+	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
+	\CodeBefore
+		\cellcolor{yellow}{2-5}
+		\cellcolor{yellow}{3-2}
+		\cellcolor{yellow}{4-3}
+		\cellcolor{yellow}{4-4}
+	\Body
+		n & 8 & 9 & 10 & 11 \\
+		4 \, S(n-1) + 2 & 6\,786 & 21\,146 & 71\,214 & 243\,794 \\
+		13 \, S(n-2) + 8 & 6\,976 & 22\,056 & 68\,726 & 231\,447 \\
+		42 \, S(n-3) + 24 & 6\,744 & 22\,536 & 71\,256 & 222\,036 \\
+	\end{NiceArray}
+	\\ \\
+	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
+	\CodeBefore
+		\cellcolor{yellow}{2-2}
+		\cellcolor{yellow}{3-3}
+		\cellcolor{yellow}{4-4}
+		\cellcolor{yellow}{4-5}
+	\Body
+		n & 12 & 13 & 14 & 15 \\
+		4 \, S(n-1) + 2 & 815\,314 & 2\,578\,514 & 8\,045\,162 & 27\,061\,154 \\
+		13 \, S(n-2) + 8 & 792\,332 & 2\,649\,772 & 8\,380\,172 & 26\,146\,778 \\
+		42 \, S(n-3) + 24 & 747\,750 & 2\,559\,840 & 8\,560\,800 &  27\,074\,400 \\
+	\end{NiceArray}
+\end{array}
+\]
+\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
+\end{table}
+
+\subsection{Another approach: \(\WS(6) \geqslant 646\)}
+
+The weak Schur partitions obtained with WS-templates have an extremely regular structure. Therefore, one may 
+expect to find larger partitions by allowing more freedom in the structure of the partitions while still preserving a structure 
+somewhat close to a template-based partition thus reducing the search space to a manageable size.
+
+When applying the inequality \(\WS(n+1) \geqslant 4 \, S(n) + 2\), one may realize that it is possible to build a weakly 
+sum-free partition of length \(4 \, S(n) + 3\) for small values of \(n\) (\(n \leqslant 4\)) by using the contruction of 
+Corollary \ref{cor:ineqWS+} for the integers 1, 2, \(4i\) and \(4i+1\) for \(i \in [\![1, S(n)]\!]\) but not 
+constraining the other integers. We did the same for the Schur partitions corresponding to Schur number five. More precisely, 
+we imposed these constraints only for \(i \leqslant 50\) in order to have more degrees of freedom. The number 50 was chosen 
+arbitrarly so that all of the Schur number 5-partitions could be tested in a few hours.
+
+However, trying out all of the 2\,447\,113\,088 Schur number 5-partitions \cite{Heule2017} one by one would not result in a 
+reasonable computation time: it is necessary to test the construction on several partitions at once. We encoded the problem as a 
+satisfiability problem and used the 1616 backdoors that were used in \cite{Heule2017} in order to encode a group of partitions in 
+a compact and efficient way. Among all of the 1616 backdoors, only the 911\textsuperscript{th} backdoor gave a weakly sum-free 
+partition of length 643. This backdoor gave a weakly sum-free partition of length 646 and cannot give a weakly sum-free 
+partition of length 647. A weakly sum-free partition of length 646 can be found in \ref{WS(6)}.
+
+\subsection{Conclusion on WS-templates}
+
+We started by giving a new construction which can be seen as an equivalent for weakly sum-free partitions of Abott
+and Hanson's construction for sum-free partitions. We then generalized this construction by introducing WS-templates. This
+allows us to find new lower bounds and new inequalities for weak Schur numbers. One may notice the significant gap
+between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
+obtained with WS-templates; thus questionning the methods used and the assumptions made when obtaining these former lower 
+bounds. We reckon better WS-templates with \(n \geqslant 5\) colors can be found by making different assumptions 
+and using a different method (Monte-Carlo methods for instance).
 
@@
 
-\include{appendix.tex}
+\appendix
+
+\section{S-templates}
+\label{S-templates}
+
+\vspace{-1.5ex}
+
+\begin{table}[H]
+\renewcommand{\arraystretch}{1.1}
+\begin{small}
+\[
+\begin{array}{|*{2}{c|}}
+	\hline
+	1 & 1, 6, 9, 13, 16, 20, 24, 27, 31 \\
+	\hline
+	2 & 2, 5, 14, 15, 25, 26 \\
+	\hline
+	3 & 3, 4, 10, 11, 12, 28, 29, 30 \\
+	\hline
+	4 & 7, 8, 17, 18, 19, 21, 22, 23, 32, 33 \\
+	\hline
+\end{array}
+\]
+\end{small}
+\vspace{-3ex}
+\caption{S-template with width 33 and 4 colors}
+\vspace{-2ex}
+\end{table}
+
+\begin{table}[H]
+\renewcommand{\arraystretch}{1.1}
+\begin{small}
+\[
+\begin{array}{|*{2}{c|}}
+	\hline
+	1 & 1, 5, 8, 12, 14 ,21, 23, 30, 32, 36, 39, 43, 45, 52, 103, 106, 110 \\
+	\hline
+	2 & 2, 6, 7, 10, 15, 18, 26, 29, 34, 37, 38, 42, 46, 51, 54, 101, 104, 109 \\
+	\hline
+	3 & 3, 4, 9, 11, 17, 19, 25, 27, 33, 35, 40, 41, 47, 48, 55, 100, 107, 108 \\
+	\hline
+	4 & 13, 16, 20, 22, 24, 28, 31, 58, 61, 67, 88, 94, 97 \\
+	\hline
+	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70\\
+	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85\\
+	& 86, 87, 89, 90, 91, 92, 93, 95, 96, 98, 99, 102, 105, 111 \\
+	\hline
+\end{array}
+\]
+\end{small}
+\vspace{-3ex}
+\caption{S-template with width 111 and 5 colors}
+\vspace{-2ex}
+\end{table}
+
+\begin{table}[H]
+\renewcommand{\arraystretch}{1.1}
+\begin{small}
+\[
+\begin{array}{|*{2}{c|}}
+	\hline
+	1 & 1, 5, 8, 11, 15, 17, 29, 33, 36, 39, 43, 57, 61, 88, 92 \\
+	& 106, 110, 113, 116, 120, 132, 134, 138, 141, 144, 148, 150, 154, 157, 160 \\
+	& 164, 178, 182, 185, 188, 341, 344, 347, 351, 365, 369, 372, 375, 379\\
+	\hline
+	2 & 2, 9, 13, 16, 20, 23, 24, 27, 28, 31, 34, 35, 38, 42, 45\\
+	& 49, 53, 60, 67, 71, 78, 82, 89, 96, 100, 104, 107, 111, 114, 115\\
+	& 118, 121, 122, 125, 126, 129, 133, 136, 140, 147, 158, 162, 165, 169, 172\\
+	& 176, 183, 187, 194, 201, 328, 335, 342, 346, 353, 357, 360, 364, 367, 371\\
+	\hline
+	3 & 3, 4, 12, 14, 19, 25, 30, 32, 40, 41, 47, 48, 58, 91, 101\\
+	& 102, 108, 109, 117, 119, 124, 130, 135, 137, 145, 146, 152, 153, 161, 163\\
+	& 168, 179, 181, 190, 339, 348, 350, 361, 366, 368, 376, 377\\
+	\hline
+	4 & 6, 7, 10, 18, 21, 22, 26, 37, 46, 50, 51, 54, 65, 70, 79, 84, 95, 98\\
+	& 99, 103, 112, 123, 127, 128, 131, 139, 142, 143, 151, 155, 156, 159\\
+	& 167, 170, 171, 175, 186, 343, 354, 358, 359, 362, 370, 373, 374, 378\\
+	\hline
+	5 & 44, 52, 55, 56, 59, 62, 63, 64, 66, 68, 69, 72, 73, 74, 75, 76, 77, 80, 81, 83,\\
+	&  85, 86, 87, 90, 93, 94, 97, 105, 189, 196, 197, 200, 203, 206, 207, \\
+	& 209, 214, 219, 231, 298, 310, 315, 320, 322, 323,  326, 329, 332, 333, 340\\
+	\hline
+	6 & 149, 166, 173, 174, 177, 180, 184, 191, 192, 193, 195, 198, 199, 202, 204\\
+	& 205, 208, 210, 211, 212, 213, 215, 216, 217, 218, 220, 221, 222, 223, 224\\
+	& 225, 226, 227, 228, 229, 230, 232, 233, 234, 235, 236, 237, 238, 239, 240\\
+	& 241, 242, 243, 244, 245, 246, 247, 248, 249, 250, 251, 252, 253, 254, 255\\
+	& 256, 257, 258, 259, 260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270\\
+	& 271, 272, 273, 274, 275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285\\
+	& 286, 287, 288, 289, 290, 291, 292, 293, 294, 295, 296, 297, 299, 300, 301, 302,\\
+	& 303, 304, 305, 306, 307, 308, 309, 311, 312, 313, 314, 316, 317, 318, 319, 321,\\
+	& 324, 325, 327, 330, 331, 334, 336, 337, 338, 345, 349, 352, 355, 356, 363, 380\\
+	\hline
+\end{array}
+\]
+\end{small}
+\vspace{-3ex}
+\caption{S-template with width 380 and 6 colors}
+\vspace{-2ex}
+\end{table}
+
+\section{WS-templates}
+\label{WS-templates}
+
+\vspace{-1.5ex}
+
+\begin{table}[H]
+\renewcommand{\arraystretch}{1.05}
+\begin{small}
+\[
+\begin{array}{|*{2}{c|}}
+	\hline
+	1 & 1, 2, 4, 8, 11, 22, 25, \mathbf{(N+1)}\\
+	\hline
+	2 & 3, 5, 6, 7, 19, 21, 23, 36\\
+	\hline
+	3 & 9, 10, 12, 13, 14, 15, 16, 17, 18, 20\\
+	\hline
+	4 & 24, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 37, 38, 39, 40, 41, 42\\
+	\hline
+\end{array}
+\]
+\end{small}
+\vspace{-3ex}
+\caption{23-WS-template with width 42 and 4 colors}
+\vspace{-1ex}
+\end{table}
+
+This template provides the inequality \(\WS (n+3) \geqslant 42 \, S(n) + 24\)
+by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.
+
+\section{\(\WS(6) \geqslant 646\)}
+\label{WS(6)}
+
+\begin{table}[H]
+\renewcommand{\arraystretch}{1.02}
+\begin{small}
+	\[
+	\begin{array}{|*{2}{c|}}
+		\hline
+		1 & 1, 2, 6, 10, 14, 18, 26, 30, 34, 42, 46, 50, 54, 62, 70, 79, 82, 90, 95, 99, 111, \\
+		& 115, 119, 123, 131, 135, 139, 143, 151, 155, 159, 163, 171, 175, 179, 183, 187, \\
+		& 195, 199, 203, 207, 211, 215, 220, 224, 228, 232, 236, 239, 244, 252, 256, 260, 264, \\
+		& 267, 272, 275, 280, 284, 292, 296, 300, 304, 308, 312, 316, 320, 328, 340, 344, 348, \\
+		& 353, 360, 364, 368, 372, 381, 385, 388, 393, 397, 404, 408, 413, 417, 425, 428, 433, \\
+		& 441, 445, 449, 453, 457, 461, 465, 469, 473, 485, 489, 493, 497, 502, 505, 509, 513, \\
+		& 517, 521, 525, 529, 533, 537, 541, 546, 549, 553, 558, 562, 566, 569, 574, 578, 586, \\
+		& 590, 593, 598, 602, 606, 610, 614, 618, 622, 626, 630, 634, 638, 642, 646 \\
+		\hline
+		2 & 3, 4, 5, 15, 16, 17, 27, 28, 29, 39, 40, 41, 47, 48, 49, 112, 113, 114, 120, 121, \\
+		& 122, 132, 133, 134, 156, 157, 158, 176, 177, 178, 200, 201, 202, 221, 222, 258, 259, \\
+		& 281, 282, 283, 301, 302, 303, 345, 346, 347, 365, 366, 367, 389, 426, 427, 446, 447, \\
+		& 448, 470, 471, 472, 490, 491, 492, 514, 515, 516, 526, 527, 528, 534, 535, 536, 599, \\
+		& 600, 601, 607, 608, 609, 619, 620, 621, 631, 632, 633, 643, 644, 645 \\
+		\hline
+		3 & 7, 8, 9, 19, 20, 21, 22, 23, 24, 25, 35, 36, 37, 38, 87, 88, 89, 136, 137, 138, 150, 152, 153, 154,\\
+		& 180, 181, 182, 196, 197, 198, 208, 209, 210, 212, 213, 214, 261, 262, 263, 265, 266, 276, 277,\\
+		& 278, 279, 309, 321, 322, 323, 324, 325, 326, 327, 338, 339, 369, 370, 371, 382, 384, 386, 387,\\
+		& 434, 435, 436, 437, 438, 439, 440, 450, 451, 452, 466, 467, 468, 482, 494, 495, 496, 499, 500, \\
+		& 510, 511, 512, 559, 560, 561, 611, 612, 613, 623, 624, 625, 627, 628, 629, 639, 640, 641\\
+		\hline
+		4 & 11, 12, 13, 31, 32, 33, 51, 100, 101, 102, 103, 104, 105, 106, 107, 108, 109, 110, 124, \\
+		& 125, 126, 127, 128, 129, 130, 144, 145, 146, 147, 148, 149, 164, 165, 166, 167, 168, 169, \\
+		& 170, 172, 173, 174, 188, 189, 190, 191, 192, 193, 194, 454, 455, 456, 458, 459, 460, 474, \\
+		& 475, 476, 477, 478, 479, 480, 481, 483, 484, 498, 501, 503, 504, 518, 519, 520, 522, 523, \\
+		& 524, 538, 539, 540, 542, 543, 544, 545, 547, 548, 597, 615, 616, 617, 635, 636, 637 \\
+		\hline
+		5 & 43, 44, 45, 52, 53, 55, 56, 57, 58, 59, 60, 61, 63, 64, 65, 66, 67, 68, 69, 71, 72, 73, \\
+		& 74, 75, 76, 77, 78, 80, 81, 83, 84, 85, 86, 91, 92, 93, 94, 216, 217, 218, 219, 223, 225, \\
+		& 226, 227, 231, 233, 234, 235, 237, 238, 240, 241, 242, 243, 245, 246, 247, 251, 253, 254, \\
+		& 255, 257, 383, 390, 391, 392, 394, 395, 396, 400, 401, 402, 403, 405, 406, 407, 409, 410, \\
+		& 411, 412, 414, 415, 416, 421, 422, 423, 424, 429, 430, 431, 432, 554, 555, 556, 557, 563, \\ 
+		& 564, 565, 567, 568, 570, 571, 572, 573, 575, 576, 577, 579, 580, 581, 582, 583, 584, 585, \\
+		& 587, 588, 589, 591, 592, 594, 595, 596, 603, 604, 605 \\
+		\hline
+		6 & 96, 97, 98, 116, 117, 118, 140, 141, 142, 160, 161, 162, 184, 185, 186, 204, 205, 206, \\
+		& 229, 230, 248, 249, 250, 268, 269, 270, 271, 273, 274, 285, 286, 287, 288, 289, 290, 291, \\
+		& 293, 294, 295, 297, 298, 299, 305, 306, 307, 310, 311, 313, 314, 315, 317, 318, 319, 329, \\
+		& 330, 331, 332, 333, 334, 335, 336, 337, 341, 342, 343, 349, 350, 351, 352, 354, 355, 356, \\
+		& 357, 358, 359, 361, 362, 363, 373, 374, 375, 376, 377, 378, 379, 380, 398, 399, 418, 419, \\
+		& 420, 442, 443, 444, 462, 463, 464, 486, 487, 488, 506, 507, 508, 530, 531, 532, 550, 551, 552 \\
+		\hline
+	\end{array}
+	\]
+\end{small}
+\vspace{-3ex}
+\caption{Weakly sum-free partition of \([\![ 1, 646 ]\!] \) into 6 subsets.}
+\vspace{-2ex}
+\end{table}
 

### 2022-02-24 article/soumission_SIAM/article.tex
caption

@@
 
-\begin{table}[H]
-  \centering
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{Comparison of lower bounds for Schur numbers}\label{table:1}
+\begin{center}
 	\begin{small}
@@
 	\end{small}
-\caption{Comparison of lower bounds for Schur numbers}
-\label{table:1}
+\end{center}
+}
 \end{table}
 
-\begin{table}[H]
-  \centering
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{Comparison of lower bounds for weak Schur numbers}\label{table:2}
+\begin{center}
 	\begin{small}
@@
 	\end{small}
-\caption{Comparison of lower bounds for weak Schur numbers}
-\label{table:2}
+\end{center}
+}
 \end{table}
@@
 
-\begin{figure}[H]
+\begin{figure}[tbhp]
+{\footnotesize
+	\caption{Visualisation of an Abbott and Hanson construction}\label{figure:1}}
 \begin{center}
@@
 \textbf{Abbott and Hanson's construction}
-\label{figure:1}
 \vspace{1.7ex}
@@
 \setlength{\tabcolsep}{6pt}
-\caption{Visualisation of an Abbott and Hanson construction}
 \end{center}
@@
 
-\begin{figure}[H]
+\begin{figure}[tbhp]
+{\footnotesize
+	\caption{Visualisation of a template-based construction}\label{figure:2}}
 \begin{center}
 \textbf{S-template construction}
-\label{figure:2}
 \setlength{\tabcolsep}{1.2ex}
@@
 \setlength{\tabcolsep}{6pt}
-\caption{Visualisation of a template-based construction}
-
 \end{center}
@@
 
-\begin{table}[H]
-
-\label{LowerBoundsS}
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{New lower bounds for \(S(n)\) with \( n \in [\![8,15]\!] \)}\label{LowerBoundsS}}
+\begin{center}
 \[
@@
 \]
-\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
+\end{center}
 \end{table}
@@
 
-\begin{figure}[H]
+\begin{figure}[tbhp]
+{\footnotesize
+	\caption{Construction of the weakly sum-free coloring}\label{SchemaWS}}
+\begin{center}
 \renewcommand{\arraystretch}{1.5}
@@
 \end{small}
-\label{SchemaWS}
-\caption{Construction of the weakly sum-free coloring}
+\end{center}
 \end{figure}
@@
 
-\begin{table}[H]
-
-\label{LowerBoundsWS}
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{New lower bounds for  \(\WS(n)\) with \( n \in [\![8,15]\!] \)}\label{LowerBoundsWS}}
+\begin{center}
 \[
@@
 
-\vspace{-1.5ex}
-
-\begin{table}[H]
-\renewcommand{\arraystretch}{1.1}
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{S-template with width 33 and 4 colors}}
+\begin{center}
 \begin{small}
@@
 \end{small}
-\vspace{-3ex}
-\caption{S-template with width 33 and 4 colors}
-\vspace{-2ex}
+\end{center}
 \end{table}
 
-\begin{table}[H]
-\renewcommand{\arraystretch}{1.1}
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{S-template with width 111 and 5 colors}}
+\begin{center}
 \begin{small}
@@
 	\hline
-	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70\\
-	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85\\
+	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70,\\
+	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85,\\
 	& 86, 87, 89, 90, 91, 92, 93, 95, 96, 98, 99, 102, 105, 111 \\
@@
 \end{small}
-\vspace{-3ex}
-\caption{S-template with width 111 and 5 colors}
-\vspace{-2ex}
+\end{center}
 \end{table}
 
-\begin{table}[H]
-\renewcommand{\arraystretch}{1.1}
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{S-template with width 380 and 6 colors}}
+\begin{center}
 \begin{small}
@@
 	\hline
-	1 & 1, 5, 8, 11, 15, 17, 29, 33, 36, 39, 43, 57, 61, 88, 92 \\
-	& 106, 110, 113, 116, 120, 132, 134, 138, 141, 144, 148, 150, 154, 157, 160 \\
+	1 & 1, 5, 8, 11, 15, 17, 29, 33, 36, 39, 43, 57, 61, 88, 92, \\
+	& 106, 110, 113, 116, 120, 132, 134, 138, 141, 144, 148, 150, 154, 157, 160, \\
 	& 164, 178, 182, 185, 188, 341, 344, 347, 351, 365, 369, 372, 375, 379\\
 	\hline
-	2 & 2, 9, 13, 16, 20, 23, 24, 27, 28, 31, 34, 35, 38, 42, 45\\
-	& 49, 53, 60, 67, 71, 78, 82, 89, 96, 100, 104, 107, 111, 114, 115\\
-	& 118, 121, 122, 125, 126, 129, 133, 136, 140, 147, 158, 162, 165, 169, 172\\
+	2 & 2, 9, 13, 16, 20, 23, 24, 27, 28, 31, 34, 35, 38, 42, 45,\\
+	& 49, 53, 60, 67, 71, 78, 82, 89, 96, 100, 104, 107, 111, 114, 115,\\
+	& 118, 121, 122, 125, 126, 129, 133, 136, 140, 147, 158, 162, 165, 169, 172,\\
 	& 176, 183, 187, 194, 201, 328, 335, 342, 346, 353, 357, 360, 364, 367, 371\\
 	\hline
-	3 & 3, 4, 12, 14, 19, 25, 30, 32, 40, 41, 47, 48, 58, 91, 101\\
-	& 102, 108, 109, 117, 119, 124, 130, 135, 137, 145, 146, 152, 153, 161, 163\\
+	3 & 3, 4, 12, 14, 19, 25, 30, 32, 40, 41, 47, 48, 58, 91, 101,\\
+	& 102, 108, 109, 117, 119, 124, 130, 135, 137, 145, 146, 152, 153, 161, 163,\\
 	& 168, 179, 181, 190, 339, 348, 350, 361, 366, 368, 376, 377\\
 	\hline
-	4 & 6, 7, 10, 18, 21, 22, 26, 37, 46, 50, 51, 54, 65, 70, 79, 84, 95, 98\\
-	& 99, 103, 112, 123, 127, 128, 131, 139, 142, 143, 151, 155, 156, 159\\
+	4 & 6, 7, 10, 18, 21, 22, 26, 37, 46, 50, 51, 54, 65, 70, 79, 84, 95, 98,\\
+	& 99, 103, 112, 123, 127, 128, 131, 139, 142, 143, 151, 155, 156, 159,\\
 	& 167, 170, 171, 175, 186, 343, 354, 358, 359, 362, 370, 373, 374, 378\\
@@
 	\hline
-	6 & 149, 166, 173, 174, 177, 180, 184, 191, 192, 193, 195, 198, 199, 202, 204\\
-	& 205, 208, 210, 211, 212, 213, 215, 216, 217, 218, 220, 221, 222, 223, 224\\
-	& 225, 226, 227, 228, 229, 230, 232, 233, 234, 235, 236, 237, 238, 239, 240\\
-	& 241, 242, 243, 244, 245, 246, 247, 248, 249, 250, 251, 252, 253, 254, 255\\
-	& 256, 257, 258, 259, 260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270\\
-	& 271, 272, 273, 274, 275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285\\
+	6 & 149, 166, 173, 174, 177, 180, 184, 191, 192, 193, 195, 198, 199, 202, 204,\\
+	& 205, 208, 210, 211, 212, 213, 215, 216, 217, 218, 220, 221, 222, 223, 224,\\
+	& 225, 226, 227, 228, 229, 230, 232, 233, 234, 235, 236, 237, 238, 239, 240,\\
+	& 241, 242, 243, 244, 245, 246, 247, 248, 249, 250, 251, 252, 253, 254, 255,\\
+	& 256, 257, 258, 259, 260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270,\\
+	& 271, 272, 273, 274, 275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285,\\
 	& 286, 287, 288, 289, 290, 291, 292, 293, 294, 295, 296, 297, 299, 300, 301, 302,\\
@@
 \end{small}
-\vspace{-3ex}
-\caption{S-template with width 380 and 6 colors}
-\vspace{-2ex}
+\end{center}
 \end{table}
@@
 
-\vspace{-1.5ex}
-
-\begin{table}[H]
-\renewcommand{\arraystretch}{1.05}
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{23-WS-template with width 42 and 4 colors}}
+\begin{center}
 \begin{small}
@@
 \end{small}
-\vspace{-3ex}
-\caption{23-WS-template with width 42 and 4 colors}
-\vspace{-1ex}
+\end{center}
 \end{table}
@@
 
-\begin{table}[H]
-\renewcommand{\arraystretch}{1.02}
+\begin{table}[tbhp]
+{\footnotesize
+	\caption{Weakly sum-free partition of \([\![ 1, 646 ]\!] \) into 6 subsets}}
+\begin{center}
 \begin{small}
@@
 \end{small}
-\vspace{-3ex}
-\caption{Weakly sum-free partition of \([\![ 1, 646 ]\!] \) into 6 subsets.}
-\vspace{-2ex}
+\end{center}
 \end{table}

### 2022-02-24 article/soumission_SIAM/article.tex
remarque rowley

@@
-\documentclass[final,onefignum,onetabnum]{siamart190516}
+\documentclass[review,onefignum,onetabnum]{siamart190516}
 
@@
 Here \(n\) can be seen as a "special" color in the sense that it is not constrained by Assertion (\ref{eq:constemp}).
-However, note that \(n\) is not necessarily the last color by order of appearance, any color can play this role.
+Number \(p\) is necessarily colored with color \(n\). However, note that \(n\) is not necessarily the last color by order of appearance.
 
@@
 
-Note that the special color \(n\) is not necessarily the last color by order of appearance, any color can play this role.
+Number \(a\) is necessarily colored with color \(n\). Note that the special color \(n\) is not necessarily the last color by order of appearance.
 Now, we introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.

### 2022-02-26 article/soumission_SIAM/article.tex
typos

@@
 
-We are interested in partioning the set of integers \(\{1, ..., p\}\) into \(n\) subsets such that there is no
+We are interested in partitioning the set of integers \(\{1, ..., p\}\) into \(n\) subsets such that there is no
 subset containing three integers \(x\), \(y\) and \(z\) verifying \(x + y = z\). We say these subsets are
@@
 In 2020, Rowley introduced the notion of templates for Schur and Ramsey numbers \cite{RowleyRamsey} which
-generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalties) for Schur numbers.
+generalizes Abbott and Hanson's construction and produces new lower bounds (and inequalities) for Schur numbers.
 He also provided two inequalities for weak Schur numbers \cite{RowleyWS}. Besides, these two inequalities do use the \textit{weakly} sum-free property.
@@
 Schur proved \cite{Schur1917} that given a number of subsets \(n\), there is a value of \(p\)
-such that \([\![1,q]\!]\) cannot be partionned into \(n\) sum-free subsets for \(q \geqslant p\). A similar
+such that \([\![1,q]\!]\) cannot be partioned into \(n\) sum-free subsets for \(q \geqslant p\). A similar
 property holds for weakly sum-free subsets \cite{Irving1973}. These observations lead to the following definitions
@@
 We start by reminding the explicit construction of a sum-free partition with the use of an S-template and a sum-free partition. 
-We rephrase in terms of Schur numbers this contruction stated by Rowley in the context of Ramsey numbers \cite{RowleyRamsey}.
+We rephrase in terms of Schur numbers this construction stated by Rowley in the context of Ramsey numbers \cite{RowleyRamsey}.
 
@@
 
-The idea lying beneath this theorem is similar to Abbott and Hanson's contruction \cite{AbbottHanson}. First, they
+The idea lying beneath this theorem is similar to Abbott and Hanson's construction \cite{AbbottHanson}. First, they
 put the integers from \([\![1,S(k)(2S(n)+1)+S(n)]\!]\) in a table with width \(2S(n)+1\) and height \(S(k)+1\) and they 
@@
 
-\textbf{Abbott and Hanson's construction}
+{\footnotesize\textbf{Abbott and Hanson's construction}}
 \vspace{1.7ex}
@@
 \begin{tabular}{c c}
-	\textbf{Corresponding S-template} & \textbf{Corresponding sum-free partition} \\
+	{\footnotesize\textbf{Corresponding S-template}} & {\footnotesize\textbf{Corresponding sum-free partition}} \\
 	\setlength{\tabcolsep}{1.5ex}
@@
 \begin{center}
-\textbf{S-template construction}
+{\footnotesize\textbf{S-template construction}}
 \setlength{\tabcolsep}{1.2ex}
@@
 
-	The additionnal constraint for the S-template is:
+	The  additional constraint for the S-template is:
 	\[
@@
 	\begin{itemize}
-	\item If \(u + v > q\), we write \(w = u + v - q \in [\![1, q]\!]\). Consequentely \(x + y = (\alpha + \beta - 1) q + w\). By definition, 
-		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the additionnal constraint on \(f\) implies \(f(w) 
+	\item If \(u + v > q\), we write \(w = u + v - q \in [\![1, q]\!]\). Consequently \(x + y = (\alpha + \beta - 1) q + w\). By definition, 
+		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the  additional constraint on \(f\) implies \(f(w) 
 		\neq f(u)\), that is \(h(x + y) \neq h(x)\).
-	\item If \(u + v \leqslant q\), we write \(w = u + v \in [\![1, q]\!]\). Consequentely \(x+y = (\alpha + \beta- 2) q + w\). By definition, 
+	\item If \(u + v \leqslant q\), we write \(w = u + v \in [\![1, q]\!]\). Consequently \(x+y = (\alpha + \beta- 2) q + w\). By definition, 
 		\(h(x + y) = f(w)\). Given that \(f(u) = f(v) \leqslant n\), the sum-free property of \(f\) implies \(f(w) \neq f(u)\), 
@@
 
-Setting \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) satsfies these 
+Setting \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) satisfies these 
 constraints: it corresponds to Theorem \ref{thm:WS-ab}. \\
@@
 
-The additionnal constraints for the WS-template are expressed as:
+The  additional constraints for the WS-template are expressed as:
 \[
@@
 	that is \(g(z) \neq g(x)\).
-\item Colour \(n + 1\) verifies the additionnal constraints for the special colour. Indeed, \(b + 2 a \geqslant 4 b + 2\). 
+\item Colour \(n + 1\) verifies the  additional constraints for the special colour. Indeed, \(b + 2 a \geqslant 4 b + 2\). 
 	Hence, \(\forall (x, y) \in g^{-1}(\{n + 1\}), x + y \leqslant b + 2 a\).
-\item Colours \(1, ..., n\) verify the additionnal constraints for the regular colours. Indeed, let 
+\item Colours \(1, ..., n\) verify the  additional constraints for the regular colours. Indeed, let 
 	\((x, y) \in g^{-1}([\![1, n]\!])\) such that \(x + y > a + b\). Given that \(x\) and \(y\) have symmetric roles, 
@@
 \par
-These additionnal constraints on the first row imply additionnal constraints on the rows of the its color (compared to other 
-colors). However, one may notice that there are never two consecutive rows of this color. Moreover these additionnal constraints 
+These  additional constraints on the first row imply  additional constraints on the rows of the its color (compared to other 
+colors). However, one may notice that there are never two consecutive rows of this color. Moreover these  additional constraints 
 mostly concern two consecutive rows. Having a special coloring for rows of this color as well as another color dedicated to the 
@@
 When applying the inequality \(\WS(n+1) \geqslant 4 \, S(n) + 2\), one may realize that it is possible to build a weakly 
-sum-free partition of length \(4 \, S(n) + 3\) for small values of \(n\) (\(n \leqslant 4\)) by using the contruction of 
+sum-free partition of length \(4 \, S(n) + 3\) for small values of \(n\) (\(n \leqslant 4\)) by using the construction of 
 Corollary \ref{cor:ineqWS+} for the integers 1, 2, \(4i\) and \(4i+1\) for \(i \in [\![1, S(n)]\!]\) but not 
@@
 between the former lower bounds for weak Schur numbers obtained by conducting a computer search and the new lower bounds
-obtained with WS-templates; thus questionning the methods used and the assumptions made when obtaining these former lower 
+obtained with WS-templates; thus questioning the methods used and the assumptions made when obtaining these former lower 
 bounds. We reckon better WS-templates with \(n \geqslant 5\) colors can be found by making different assumptions 
@@
 
-\section{Acknowledgments}
+\section{Acknowledgements}
 

### 2022-06-05 ramsey/fast_template/src/main.rs
dpll suite

@@ -1,8 +1,17 @@
 use fast_template::cliques::no_clique;
+use std::time::Instant;
 
 fn main() {
-    let n = 10;
-    let k = 3;
-    let clauses = no_clique(n, k);
-    println!("{:?}", clauses);
+    let n = 30;
+    let k = 5;
+
+    let now = Instant::now();
+    let mut clauses = no_clique(n, k);
+    let elapsed = now.elapsed();
+    println!("{:?} -- {:?}", elapsed, clauses.len());
+
+    let now = Instant::now();
+    clauses.remove_non_minimal();
+    let elapsed = now.elapsed();
+    println!("{:?} -- {:?}", elapsed, clauses.len());
 }

### 2022-06-05 ramsey/fast_template/src/sat.rs

@@ -18,15 +18,18 @@ pub struct ColorCNF {
 
 #[derive(Clone, Debug, Eq, PartialEq)]
 pub struct CNF {
-    clauses: Vec<ColorCNF>,
+    assigned: Vec<Vec<usize>>,
+    cnfs: Vec<ColorCNF>,
+    possibilities: Vec<Vec<usize>>,
 }
 
 impl Clause {
+    pub const MAX_SIZE: usize = 3 * u128::BITS as usize;
     pub const EMPTY: Self = Self(0, 0, 0);
 
     #[inline]
     pub fn add_literal(&mut self, x: usize) {
-        let (bit_set, x) = self.corresponding_mut(x - 1);
+        let (bit_set, x) = self.corresponding_mut(x);
         *bit_set |= 1 << x;
     }
 
@@ -189,13 +192,18 @@ impl ColorCNF {
             .collect()
     }
 
+    pub fn len(&self) -> usize {
+        self.cnf.len()
+    }
+
     pub fn new() -> Self {
         Self {
             cnf: AHashSet::new(),
         }
     }
 
-    pub fn pure_literals(&self, assigned: Clause) -> Vec<usize> {
+    pub fn pure_literals(&self, assigned: &[usize]) -> Vec<usize> {
+        let assigned = Clause::from(assigned);
         self.cnf
             .iter()
             .fold(assigned, |acc, clause| acc.union(clause))
@@ -236,22 +244,16 @@ impl ColorCNF {
             .collect()
     }
 
-    pub fn unit_propagation(&mut self) -> Vec<usize> {
+    pub fn unit_propagation(&self) -> Vec<usize> {
         let mut single_literals = Vec::new();
         for clause in &self.cnf {
             match clause.size() {
                 0 => panic!("unsatisfiable formula"),
-                1 => single_literals.push(clause.clone()),
+                1 => single_literals.push(clause.min_literal().unwrap()),
                 _ => (),
             }
         }
         single_literals
-            .iter()
-            .map(|clause| {
-                self.cnf.remove(clause);
-                clause.min_literal().unwrap()
-            })
-            .collect()
     }
 
     fn clauses_with_id(&mut self) -> (Vec<Clause>, AHashMap<usize, AHashSet<usize>>) {
@@ -259,8 +261,7 @@ impl ColorCNF {
         mem::swap(&mut self.cnf, &mut temp);
         let mut clauses: Vec<Clause> = temp.into_iter().collect();
[…]

### 2022-06-06 ramsey/amelioration_templates_tamsey_schur.tex
explications ramsey (partie 1)

\documentclass{article}
\title{Une amélioration des templates pour les nombres de Ramsey mutlticolores et les nombres de Schur}
\author{Romain Ageron}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{mathtools}

\usepackage{enumerate}

\usepackage[french]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{float}

\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{nicematrix}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}[definition]{Théorème}
\newtheorem{corollary}[definition]{Corollaire}
\newtheorem{proposition}[definition]{Proposition}

\DeclareMathOperator{\cons}{Cons}
\DeclareMathOperator{\findef}{Default}

\newcommand{\defeq}{\vcentcolon=}

\begin{document}

\maketitle

\begin{abstract}
Récement, l'introduction de constructions basées sur des objets particuliers appelés "template" a permis d'améliorer plusieurs bornes inférieures pour les nombres Ramsey multicolores, les nombres de Schur et les nombres de Schur faible. Ce document de travail présente des améliorations apportées au concept de template, notamment une généralisation : les b-templates. Cela conduit à une amélioration des inégalités et bornes inférieures connues certains nombre de Ramsey multicolores et certains nombres de Schur.
\end{abstract}

\section{Organisation de ce document de travail}
La section \ref{sec:def} présente des notations, des définitions, ainsi que des propriétés utiles. La section \ref{sec:temp} présente mon approche et mes résultats sur les templates. elle commence par une explication des différences avec l'approche de Rowley. Elle fait aussi office de revue de l'état de l'art en précisant les résultats de Rowley en fin de section. La section \ref{sec:b-temp} introduit les b-templates, une généralisation des templates qui est utilisée dans la plupart des améliorations présentées. La section \ref{sec:results} compare les nouvelles inégalités et bornes inférieures à celles connues auparavant.

\section{Définitions et propriétés}
\label{sec:def}

Pour \(n \in \mathbb{N}\), on note \(K_n\) le graphe complet d'ordre \(n\).

\begin{definition}[Coloriage de Ramsey]
Soit \(n \in \mathbb{N}\), la taille du graphe, et soit \(r \in \mathbb{N}\), le nombre de couleurs. Soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). On appelle coloriage de Ramsey tout coloriage des arêtes de \(K_n\) avec \(r\) couleurs tel que pour toute couleur \(c \in [\![1, r]\!]\), le coloriage ne contient pas de sous-graphe complet \(K_{k_c}\) monochromatique en la couleur \(c\). \(R(k_1, ..., k_r ; n)\) désigne l'un (quelconque) de ces coloriages. Si tous les \(k_c\) sont égaux à un \(k\), on utilise également la notation \(R_r(k; n)\).
\end{definition}

\begin{theorem}[Théorème de Ramsey fini \cite{Ramsey}]
\label{thm:ram}
Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). Alors il existe un entier \(n \in \mathbb{N}\) tel qu'il n'existe pas de \(R(k_1, ..., k_r ; n)\).
\end{theorem}

Le théorème \ref{thm:ram} justifie la définition suivante.

\begin{definition}[Nombre de Ramsey]
Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). On définit le nombre de Ramsey \(R(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel qu'il n'existe pas de \(R(k_1, ..., k_r ; n)\). Si tous les \(k_c\) sont égaux à un \(k\), ce nombre est également noté \(R_r(k)\).
\end{definition}

On remarque que, contrairement aux nombres de Schur, les nombres de Ramsey désigne le plus petit entier tel qu'il n'existe pas de coloriage, et non pas la taille maximale d'un coloriage.

\begin{definition}[Coloriage de Ramsey linéaire]
Soit \(n \in \mathbb{N}\), et soit \(r \in \mathbb{N}\). Soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). On indexe les sommets de \(K_n\) avec les entiers de \([\![0, n - 1]\!]\). On appelle coloriage de Ramsey linéaire tout \(R(k_1, ..., k_r ; n)\) pour lequel la couleur de l'arête \((u, v)\) dépend uniquement de \(|u - v|\). Un \(L(k_1, ..., k_r ; n)\) désigne l'un (quelconque) de ces coloriages. Si tous les \(k_c\) sont égaux à un \(k\), on utilise également la notation \(L_r(k; n)\).
\end{definition}

Le théorème \ref{thm:ram} justifie la définition suivante.

\begin{definition}[Nombre de Ramsey linéaire]
Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). On définit le nombre de Ramsey linéaire \(L(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel qu'il n'existe pas de \(L(k_1, ..., k_r ; n)\). Si tous les \(k_c\) sont égaux à un \(k\), ce nombre est également noté \(L_r(k)\).
\end{definition}

\begin{proposition}
\(\forall r \in \mathbb{N}, (k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r, L(k_1, ..., k_r) \leqslant R(k_1, ..., k_r)\)
\end{proposition}

On remarque qu'un \(L(k_1, ..., k_r ; n)\) induit un coloriage de \([\![1, n - 1]\!]\). Réciproquement, tout coloriage de \([\![1, n - 1]\!]\) correspond à un coloriage linéraire de \(K_n\). Le théorème suivant porte sur le lien entre un coloriage sur \([\![1, n]\!]\) et les nombres de cliques du coloriage linéaire de \(K_{n+1}\) associé.

\begin{theorem}[Lien avec les coloriages sans-sommes \cite{AbbottHanson}]
\label{thm:lien-partitions}
Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\). Soit \(n \in \mathbb{N}\) et soit \(\gamma\) un coloriage de \([\![1, n]\!]\) avec \(r\) couleurs. Alors les deux conditions suivantes sont équivalentes :
\begin{itemize}
\item dans le coloriage linéaire de \(K_{n+1}\) associé à \(\gamma\), la couleur \(c\) contient un sous-graphe complet de taille \(k_c\)
\item il existe un sous-ensemble \(S\) de \([\![1, n]\!]\) monochromatique de couleur \(c\) et de cardinal \(k_c - 1\) vérifiant : pour tous \(x, y \in S\) distincts, \(\gamma(|x - y|) = c\) 
\end{itemize}
\end{theorem}

Dans la suite, on utilise également \(L(k_1, ..., k_r ; n)\) pour désigner un coloriage de \([\![1, n - 1]\!]\)  associé à un \(L(k_1, ..., k_r ; n)\).

Le théorème \ref{thm:lien-partitions} donne le corollaire suivant.

\begin{corollary}[Lien avec les nombres de Schur]
On a \(S(n) = L_n(3) - 2 \leqslant R_n(3) - 2\). 
\end{corollary}

\section{Templates}
\label{sec:temp}

Dans cette section, j'utilise des notations et définitions différentes de celle de Rowley \cite{RowleyRamsey}. Notamment, les templates et constructions sont introduits différement et sont manipulés en termes de partitions et non de graphes. De plus la couleur spéciale est désignée de manière abstraite par un "t" au lieu d'un "3" qui pourrait être confondu avec l'un des \(k_c\). Par ailleurs, je définis un template directement comme une partition pour laquelle la construction fonctionne. Enfin, J'utilise une formulation différente de la condition sur les templates.

\begin{definition}[Permutation partielle]
Pour \(S\) un ensemble quelconque et \(a \in \mathbb{N}\) un entier naturel, on appelle permutation partielle à \(a\) éléments de \(S\) tout a-uplet d'éléments de \(S\) deux à deux distincts. L'ensemble des permutations partielles à \(a\) éléments de \(S\) est noté \(\mathfrak{S}_a(S)\), c'est-à-dire : \(\mathfrak{S}_a(S) = \left\{ (x_i)_{1 \leqslant i \leqslant a} ~|~ \forall (i, j) \in [\![1, a]\!]^2, i \neq j \implies x_i \neq x_j \right\}\). En particulier, \(\mathfrak{S}_2(S)\) désigne l'ensemble des couples d'éléments distincts. Si \(S = [\![1, n]\!]\) pour un \(n \in \mathbb{N}\), \(\mathfrak{S}_a(S)\) est plus simplement noté \(\mathfrak{S}_a^n\).
\end{definition}

Dans cette section, pour un entier \(n\) (en pratique sous-entendu), on note \(\pi\) l'application qui a un entier \(x \in \mathbb{Z}\) associe son unique représentant modulo \(n\) dans \([\![1, n]\!]\).

\begin{definition}[Reformulation des templates]
Soit \(n \in \mathbb{N}\). Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\). Un template de taille \(n\) à \(r + 1\) couleurs, noté \(T(k_1, ..., k_r, t; n)\), est défini comme une partition de \([\![1, n]\!]\) en \(r+1\) sous-ensembles \(A_1, ..., A_{r+1}\) vérifiant : 
\begin{itemize}
\item \(n \in A_{r+1}\)
\item pour la couleur spéciale \(r + 1\) : \(\forall (x,y) \in A_{r+1}^2, x + y \notin A_{r+1}\),
\item pour les autres couleurs \(c \in [\![1, r]\!]\) : \(\forall x \in \mathfrak{S}_{k_c - 1}(A_c), \exists (i, j) \in \mathfrak{S}_2^{k_c - 1}, \pi(x_i - x_j) \notin A_c\).
\end{itemize}
\end{definition}

La couleur \(r + 1\)  n'est pas nécessairement la dernière par ordre d'apparition, la désignation de \(r+1\) comme couleur spéciale signalée par \(t\) est une convention qui allège les notations en évitant de devoir écrire \(T(k_1, ..., k_{i - 1}, t,  k_{i + 1}, ..., k_r; n)\).

Dans le cas où tous les \(k_c\) sont égaux à 3, on retouve la définition des S-templates.

\begin{definition}[valeur par défaut]
TODO
\end{definition}

\begin{definition}[Méthode de construction]
Soit \((n, p) \in {\mathbb{N}^*}^2\) les tailles des coloriages. Soit \((r, s) \in {\mathbb{N}^*}^2\). On se donne un coloriage de \([\![1, n]\!]\) à \(r + 1\) couleurs (appelée \(\mathcal{H}\), pour horizontal), et un coloriage de \([\![1, p]\!]\) à \(s\) couleurs (appelée \(\mathcal{V}\), pour vertical).

Pour un \(b \in \mathbb{N}\), on se donne aussi un coloriage dit final \(\mathcal{F}\) de \([\![1, b]\!]\) à \(r + 1\) couleurs. Il est parfois utile de définir \(\mathcal{F}\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut : \(b = \min \mathcal{H}^{-1}(\{r + 1\}) - 1\) et \(\mathcal{F} = \findef(\mathcal{H}) \defeq \mathcal{H}_{|\,[\![1, b]\!]}\).

On construit alors un coloriage \(\gamma\) de \([\![1, n \times p + b]\!]\) à \(r + s\) couleurs comme suit. De manière informelle, on répéte \(p\) fois le motif formé l'enchaînement des couleurs dans \(\mathcal{H}\) en remplaçant pour la \(i\)-ème itération la couleur spéciale par \(r + \mathcal{V}(i)\) puis on ajoute à la fin le motif formé l'enchaînement des couleurs dans \(\mathcal{F}\). Formellement :
\[\begin{array}{c c c c}
	\gamma: & [\![1, n \times p + b]\!]  & \longrightarrow &  [\![1, r + s]\!] \\
 	& x & \longmapsto & 
		\left\{\begin{array}{l l}
			\mathcal{H}(\pi(x)) & ~\text{si}~ x \leqslant n \times p ~\text{et}~ \mathcal{H}(\pi(x)) \neq r + 1 \\
			r + \mathcal{V}\left(\left\lceil \dfrac{x}{n} \right\rceil\right) & ~\text{si}~ x \leqslant n \times p ~\text{et}~ \mathcal{H}(\pi(x)) = r + 1 \\
			\mathcal{F}(x - n \times p) & ~\text{si}~ x > n \times p
		\end{array}\right.
\end{array}\]
\end{definition}

\begin{figure}[H]\begin{center}
\renewcommand{\arraystretch}{1.8}
\begin{NiceTabular}{|*{9}{c|}}[corners=SE,standard-cline,hlines]
\CodeBefore
	\cellcolor{red}{1-1}
	\cellcolor{green}{1-2}
	\cellcolor{green}{1-3}
	\cellcolor{red}{1-4}
	\cellcolor{cyan}{1-5}
	\cellcolor{cyan}{1-6}
	\cellcolor{red}{1-7}
	\cellcolor{cyan}{1-8}
	\cellcolor{cyan}{1-9}
	\cellcolor{red}{2-1}
	\cellcolor{green}{2-2}
	\cellcolor{green}{2-3}
	\cellcolor{red}{2-4}
	\cellcolor{yellow}{2-5}
	\cellcolor{yellow}{2-6}
	\cellcolor{red}{2-7}
	\cellcolor{yellow}{2-8}
	\cellcolor{yellow}{2-9}
	\cellcolor{red}{3-1}
	\cellcolor{green}{3-2}
	\cellcolor{green}{3-3}
	\cellcolor{red}{3-4}
	\cellcolor{yellow}{3-5}
	\cellcolor{yellow}{3-6}
	\cellcolor{red}{3-7}
	\cellcolor{yellow}{3-8}
	\cellcolor{yellow}{3-9}
	\cellcolor{red}{4-1}
	\cellcolor{green}{4-2}
	\cellcolor{green}{4-3}
	\cellcolor{red}{4-4}
	\cellcolor{cyan}{4-5}
	\cellcolor{cyan}{4-6}
	\cellcolor{red}{4-7}
	\cellcolor{cyan}{4-8}
	\cellcolor{cyan}{4-9}
	\cellcolor{red}{5-1}
	\cellcolor{green}{5-2}
	\cellcolor{green}{5-3}
	\cellcolor{red}{5-4}
\Body
	1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
	10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 \\
	19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 \\
	28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 \\
	37 & 38 & 39 & 40 \\
\end{NiceTabular}
\caption{Construction d'un \(L_4(3;40)\) avec \(\mathcal{H} = T(3,3,t;9)\), \(\mathcal{V} = L_2(3;4)\) et \(\mathcal{F} = \findef(\mathcal{H})\)}
\end{center}\end{figure}

\begin{definition}[compatibilité avec un template]
TODO
\end{definition}

\begin{proposition}[compatibilité de la valeur par défaut]
TODO
\end{proposition}

\begin{theorem}[Construction en utilisant les templates]
Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\). Soit \(n \in \mathbb{N}^*\). Soit \(\mathcal{H}\) un coloriage de \([\![1,n]\!]\) à \(r + 1\) couleurs. Les deux conditions suivantes sont équivalentes.

\begin{enumerate}[(i)]
\item \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\)
\item \(\forall s \in \mathbb{N}^*, \forall l \in {[\![3, +\infty[\![}^s, \forall \mathcal{V} \in \mathcal{L}(l_1, ..., l_s ; p), \cons(\mathcal{H}, \mathcal{V}, \varnothing) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; n \times p)\)
\end{enumerate}

On suppose maintenant que \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\). Soient \(s \in \mathbb{N}^*, l \in [\![3, +\infty[\![^s\) et \(\mathcal{V} \in \mathcal{L}(l_1, ..., l_s ; p)\). Soit \(b \in \mathbb{N}\) et soit \(\mathcal{F}\) un coloriage de \([\![1, b]\!]\) à \(r + 1\) couleurs compatible avec \(\mathcal{H}\). Alors \(\cons(\mathcal{H}, \mathcal{V}, \mathcal{F}) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; n \times p + b)\).
\end{theorem}

Rowley évoque seulement \((i) \implies (ii)\) mais pas \((ii) \implies (i)\) qui montre l'optimalité des conditions dans la définition des templates.

La construction de Rowley comprend uniquement le coloriage finale par défaut, l'introduction du coloriage final variable et la notion de compatibilité sont nouvelles. Cela correspond à une extension aux templates pour les nombres de Ramsey du raffinement sur la dernière ligne pour les S-templates.
\section{b-Templates}
\label{sec:b-temp}

\section{Nouvelles inégalités et bornes inférieures}
\label{sec:results}

\bibliographystyle{IEEEtran}
\bibliography{biblio}

\end{document}

### 2022-06-06 poster_congres/poster.tex

\documentclass[roundedcorners=true, titleposition=left]{beamerthemeruhuisstijlposter}

\usepackage{grffile}
\usepackage[french]{babel}
\usepackage[utf8]{inputenc}

\usepackage{amsmath,amsthm, amssymb, latexsym}
\usepackage{nicematrix}
\boldmath

\usepackage{array,booktabs,tabularx}
\listfiles

\newcommand{\WS}{\mathit{WS}}

\institute[CLS]{CentraleSupélec, Pôle Projet \og{}Formation à la recherche \fg{}}
\title{Les nombres de Schur et de Schur faibles}
\date{\today}
\author{\underline{Romain Ageron}, \underline{Paul Castéras}, \underline{Thibaut Pellerin}, Yann Portella,\\ Arpad Rimmel, Joanna Tomasik (encadrants)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\setbeamertemplate{caption}{\raggedright\insertcaption\par}

\begin{frame}
\begin{columns}
\begin{column}{0.49\textwidth}
\begin{beamercolorbox}[center, wd=\textwidth]{postercolumn}
\begin{minipage}[T]{0.95\textwidth}
\parbox[t][\columnheight]{\textwidth}{%
    \begin{block}{Un peu d'histoire}
    	\begin{itemize}
    	    \item 1917 : Introduction par Schur des partitions sans somme lors d'une étude du \textbf{grand théorème de Fermat}
    	    \item 1930 : Introduction de la \textbf{théorie de Ramsey}
    	    \item 1972 : \textbf{Inégalités récursives} obtenues par Abbott et Hanson 
    	    \item 1990-2020 : Approche \textbf{numérique} (MCTS, SAT, ...)
    	    \item 2020 : Introduction des \textbf{templates} par Rowley, nouvelles inégalités
    	    \item Notre contribution : \textbf{généralisation} des templates, \textbf{nouvelles bornes inférieures}
    	\end{itemize}
    \end{block}
  \begin{block}{Définitions et propriétés}
	\textbf{Issai Schur} a posé le problème suivant :

	\begin{itemize}
		\item Pour \(n \geqslant 1\) un entier ( = taille du problème)
		\item \(k \geqslant 1\) un autre entier ( = nombre de \textbf{couleurs})

	\vspace{1ex}
	\textbf{Peut-on colorier les entiers de \(1\) à \(n\) de sorte que si deux 
	nombres ont la même couleur, leur somme n'est pas de cette couleur ?}

    \vspace{1ex}
    Si oui, un tel coloriage est dit \textbf{sans somme}.
			\vspace{1ex}

		\item On note \(S(k)\) le plus grand entier \(n\) vérifiant cette propriété.
\vspace{2ex}

Les nombres de Schur faibles sont une variante des nombres de Schur. On se demande : Peut-on colorier les entiers de \(1\) à \(n\) de sorte que si deux 
	nombres \textbf{distincts} ont la même couleur, leur somme n'est pas de cette couleur ?

    \vspace{1ex}
	\item On note \(\WS(k)\) le plus grand entier \(n\) vérifiant cette propriété.

	\vspace{2ex}
	Le comportement asymptotique de ces suites est mal connu.
	\vspace{1ex}	
	\item \(c \, \sqrt[5]{380}^k \leqslant S(k) \leqslant \WS(k)\)
	\item Lien avec les nombres de Ramsey \(S(k) \leqslant R_k(3) - 2 \leqslant \left\lfloor k! \left(e - \frac{1}{6}\right) \right\rfloor - 1\)
    \end{itemize}
  \end{block}

 	\vspace{-0.5ex}
    \begin{block}{Exemples}
    \centering
    On a \(S(3) = 13\) et \(WS(2) = 8\)
    \setlength{\arraycolsep}{0.8ex}
    \renewcommand{\arraystretch}{1.5}
    \begin{figure}

    \caption{\large Partition sans-somme à 3 couleurs}
    \vspace{1ex}
   	\(\begin{NiceArray}{|*{13}{c|}}[standard-cline,hlines]
		\CodeBefore
			\cellcolor{red}{1-1}
			\cellcolor{cyan}{1-2}
			\cellcolor{cyan}{1-3}
			\cellcolor{red}{1-4}
			\cellcolor{green}{1-5}
			\cellcolor{green}{1-6}
			\cellcolor{cyan}{1-7}
			\cellcolor{green}{1-8}
			\cellcolor{green}{1-9}
			\cellcolor{red}{1-10}
			\cellcolor{cyan}{1-11}
			\cellcolor{cyan}{1-12}
			\cellcolor{red}{1-13}
		\Body
			\,\,1\,\,\, & \,\,2\,\,\, & \,\,3\,\,\, & \,\,4\,\,\, & \,\,5\,\,\, & \,\,6\,\,\, & \,\,7\,\,\, & \,\,8\,\,\, & \,\,9\,\,\, & 10 & 11 & 12 & 13\\
	\end{NiceArray}\)

	\end{figure}
	\bigskip

	\setlength{\arraycolsep}{1.5ex}
    \renewcommand{\arraystretch}{1.5}
    \begin{figure}
    \caption{\large Partition \textit{faiblement} sans-somme à 2 couleurs}
    \vspace{1ex}
	\(\begin{NiceArray}{|*{8}{c|}}[standard-cline,hlines]
		\CodeBefore
			\cellcolor{red}{1-1}
			\cellcolor{red}{1-2}
			\cellcolor{cyan}{1-3}
			\cellcolor{red}{1-4}
			\cellcolor{cyan}{1-5}
			\cellcolor{cyan}{1-6}
			\cellcolor{cyan}{1-7}
			\cellcolor{red}{1-8}
		\Body
			1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
	\end{NiceArray}\)

	\end{figure}

    \end{block}

    \vfill

}
\end{minipage}
\end{beamercolorbox}
\end{column}

\begin{column}{0.49\textwidth}
\begin{beamercolorbox}[center, wd=\textwidth]{postercolumn}
\begin{minipage}[T]{0.95\textwidth}
\parbox[t][\columnheight]{\textwidth}{%
  \begin{block}{Templates}
    \vspace{-1ex}
    \setlength{\arraycolsep}{0.8ex}\renewcommand{\arraystretch}{1.5}
    \begin{figure}
    \caption{\large Partition sans somme construite à l'aide d'un template}
    \vspace{1ex}
    \(\begin{NiceArray}{*{10}{c}}[corners={NW},hvlines]
    \CodeBefore
    	\cellcolor{red}{1-9}
    	\cellcolor{green}{1-10}
    	\cellcolor{cyan}{2-1}
    	\cellcolor{cyan}{2-2}
	\cellcolor{red}{2-3}
	\cellcolor{green}{2-4}
	\cellcolor{green}{2-5}
	\cellcolor{red}{2-6}
    	\cellcolor{cyan}{2-7}
    	\cellcolor{cyan}{2-8}
    	\cellcolor{cyan}{2-9}
	\cellcolor{red}{2-10}
	\cellcolor{yellow}{3-1}
    	\cellcolor{yellow}{3-2}
	\cellcolor{red}{3-3}
	\cellcolor{green}{3-4}
	\cellcolor{green}{3-5}
	\cellcolor{red}{3-6}
    	\cellcolor{yellow}{3-7}
    	\cellcolor{yellow}{3-8}
    	\cellcolor{yellow}{3-9}
	\cellcolor{red}{3-10}
	\cellcolor{yellow}{4-1}
    	\cellcolor{yellow}{4-2}
	\cellcolor{red}{4-3}
	\cellcolor{green}{4-4}
	\cellcolor{green}{4-5}
	\cellcolor{red}{4-6}
    	\cellcolor{yellow}{4-7}
    	\cellcolor{yellow}{4-8}
    	\cellcolor{yellow}{4-9}
	\cellcolor{red}{4-10}
	\cellcolor{cyan}{5-1}
    	\cellcolor{cyan}{5-2}
	\cellcolor{red}{5-3}
	\cellcolor{green}{5-4}
	\cellcolor{green}{5-5}
	\cellcolor{red}{5-6}
    	\cellcolor{cyan}{5-7}
    	\cellcolor{cyan}{5-8}
    	\cellcolor{cyan}{5-9}
	\cellcolor{red}{5-10}
    \Body
    	   &    &    &    &    &    &    &    &  1 &  2 \\
    	 3 &  4 &  5 &  6 &  7 &  8 &  9 & 10 & 11 & 12 \\
    	13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 \\
    	23 & 24 & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 \\
    	33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 & 42 \\
    \end{NiceArray}\)
    \end{figure}
\end{block}

    \begin{block}{Forme des inégalités obtenues}
    	\begin{itemize}

   \item Forme des inégalités pour les nombres de Schur :
   \[S(k+l) \geqslant aS(k) + b.\]

   Une approche précédente avait obtenu $a=2S(l)+1$ et $b=S(l)$.
   \vspace{1ex}
   \item Forme des inégalités pour les nombres de Schur faibles :
   \[ \WS(k+l) \geqslant cS(k) + d.\]

   Nous avons obtenu : $c \geqslant \WS (l) + \left \lceil \WS(l)/2 \right \rceil +1$.

  \end{itemize}
  \end{block}

  \medskip
  \begin{block}{Reformulation en formule booléenne (CNF)}
  \begin{itemize}
      \item \(x_i^{(c)} = 1\) si le nombre \(i\) est dans la couleur \(c\), \(0\) sinon.
      \item \(\mathit{Col}_i = \bigvee\limits_{c} x_i^{(c)} \) : \(i\) est dans au moins une couleur.
      \item \(\mathit{Disj}_i = \bigwedge\limits_{c_1 \neq c_2} \neg x_i^{(c_1)} \vee \neg x_i^{(c_2)}\) : \(i\) a au plus une couleur.
      \item \(\mathit{Som}_c = \bigwedge\limits_{i + j \leqslant n} \neg x_i^{(c)} \vee \neg x_j^{(c)} \vee \neg x_{i+j}^{(c)}\) : \(c\) est sans somme.
  \end{itemize}
  \end{block}
  \medskip
  \vspace{-1ex}
\begin{block}{Résultats}
\vspace{-1ex}
\begin{center}
    \begin{table}
		\caption{\large Bornes inférieures pour les nombres de Schur}

		 \begin{normalsize}

		\begin{tabular}{|*{11}{c|}}
		    \hline
		    \(k\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
		    \hline
		    Etat de l'art & 1* & 4* & 13* & 44* & 160* & 536 & 1\,696 &5\,286 & 17\,694 & 60\,320 \\
		    \hline
		    \textbf{Nos résultats} & & & & & & & & \textbf{5\,362} & \textbf{17\,803} & \textbf{60\,948} \\
		    \hline
		\end{tabular}

		\end{normalsize}
	\end{table}

	\vspace{1ex}

    \begin{table}
		\caption{\large Bornes inférieures pour les nombres de Schur faibles}
        \begin{normalsize}
    		\begin{tabular}{|*{11}{c|}}
    		    \hline
    		    \(k\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
    		    \hline
    		    Etat de l'art & 2* & 8* & 23* & 66* & 196 & 642 & 2\,146 & 6\,976 & 22\,056 & 70\,778 \\
    		    \hline
    		    \textbf{Nos résultats} & & & & & &\textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} \\
    		    \hline
    		\end{tabular}
    	\end{normalsize}
    \end{table}
    \vspace{1ex}
	* désigne une valeur exacte
\end{center}
Nous avons aussi obtenu de nouvelles bornes inférieures pour tout \(k \geqslant 11\).
\end{block}
\medskip

}
\end{minipage}
\end{beamercolorbox}
\end{column}
\end{columns}
\end{frame}

\end{document}

### 2022-06-07 ramsey/amelioration_templates_tamsey_schur.tex
partie templates

@@
 \begin{abstract}
-Récement, l'introduction de constructions basées sur des objets particuliers appelés "template" a permis d'améliorer plusieurs bornes inférieures pour les nombres Ramsey multicolores, les nombres de Schur et les nombres de Schur faible.
+Récement, l'introduction de constructions basées sur des objets particuliers appelés "templates" a permis d'améliorer plusieurs bornes inférieures pour les nombres Ramsey multicolores, les nombres de Schur et les nombres de Schur faibles.
 Ce document de travail présente des améliorations apportées au concept de template, notamment une généralisation : les b-templates.
@@
 On appelle coloriage de Ramsey tout coloriage des arêtes de \(K_n\) avec \(r\) couleurs tel que pour toute couleur \(c \in [\![1, r]\!]\), le coloriage ne contient pas de sous-graphe complet \(K_{k_c}\) monochromatique en la couleur \(c\).
-\(R(k_1, ..., k_r ; n)\) désigne l'un (quelconque) de ces coloriages.
-Si tous les \(k_c\) sont égaux à un \(k\), on utilise également la notation \(R_r(k; n)\).
+\(R(k_1, ..., k_r ; n)\) désigne l'un (quelconque) de ces coloriages et l'ensemble de ces coloriages est noté \(\mathcal{R}(k_1, ..., k_r ; n)\).
+Si tous les \(k_c\) sont égaux à un \(k\), on utilise également les notations \(R_r(k; n)\) et \(\mathcal{R}_r(k; n)\).
 \end{definition}
@@
 \label{thm:ram}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). Alors il existe un entier \(n \in \mathbb{N}\) tel qu'il n'existe pas de \(R(k_1, ..., k_r ; n)\).
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). Alors il existe un entier \(n \in \mathbb{N}\) tel que \(\mathcal{R}(k_1, ..., k_r ; n) = \varnothing\).
 \end{theorem}
@@
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
-On définit le nombre de Ramsey \(R(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel qu'il n'existe pas de \(R(k_1, ..., k_r ; n)\).
+On définit le nombre de Ramsey \(R(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel que \(\mathcal{R}(k_1, ..., k_r ; n) = \varnothing\).
 Si tous les \(k_c\) sont égaux à un \(k\), ce nombre est également noté \(R_r(k)\).
@@
 On appelle coloriage de Ramsey linéaire tout \(R(k_1, ..., k_r ; n)\) pour lequel la couleur de l'arête \((u, v)\) dépend uniquement de \(|u - v|\).
-Un \(L(k_1, ..., k_r ; n)\) désigne l'un (quelconque) de ces coloriages.
-Si tous les \(k_c\) sont égaux à un \(k\), on utilise également la notation \(L_r(k; n)\).
+Un \(L(k_1, ..., k_r ; n)\) désigne l'un (quelconque) de ces coloriages et l'ensemble de ces coloriages est noté \(\mathcal{L}(k_1, ..., k_r ; n)\).
+Si tous les \(k_c\) sont égaux à un \(k\), on utilise également les notations \(L_r(k; n)\) et \(\mathcal{L}_r(k; n)\).
 \end{definition}
@@
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
-On définit le nombre de Ramsey linéaire \(L(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel qu'il n'existe pas de \(L(k_1, ..., k_r ; n)\).
+On définit le nombre de Ramsey linéaire \(L(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r ; n) = \varnothing\).
 Si tous les \(k_c\) sont égaux à un \(k\), ce nombre est également noté \(L_r(k)\).
@@
 Alors les deux conditions suivantes sont équivalentes :
-\begin{itemize}
+\begin{enumerate}[(i)]
 \item dans le coloriage linéaire de \(K_{n+1}\) associé à \(\gamma\), la couleur \(c\) contient un sous-graphe complet de taille \(k_c\)
 \item il existe un sous-ensemble \(S\) de \([\![1, n]\!]\) monochromatique de couleur \(c\) et de cardinal \(k_c - 1\) vérifiant : pour tous \(x, y \in S\) distincts, \(\gamma(|x - y|) = c\) 
-\end{itemize}
+\end{enumerate}
 \end{theorem}
@@
 L'ensemble des permutations partielles à \(a\) éléments de \(S\) est noté \(\mathfrak{S}_a(S)\), c'est-à-dire : \(\mathfrak{S}_a(S) = \left\{ (x_i)_{1 \leqslant i \leqslant a} ~|~ \forall (i, j) \in [\![1, a]\!]^2, i \neq j \implies x_i \neq x_j \right\}\).
-En particulier, \(\mathfrak{S}_2(S)\) désigne l'ensemble des couples d'éléments distincts.
-Si \(S = [\![1, n]\!]\) pour un \(n \in \mathbb{N}\), \(\mathfrak{S}_a(S)\) est plus simplement noté \(\mathfrak{S}_a^n\).
 \end{definition}
@@
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\).
-Un template de taille \(n\) à \(r + 1\) couleurs, noté \(T(k_1, ..., k_r, t; n)\), est défini comme une partition de \([\![1, n]\!]\) en \(r+1\) sous-ensembles \(A_1, ..., A_{r+1}\) vérifiant :
-\begin{itemize}
+Un template de taille \(n\) à \(r + 1\) couleur, est défini comme une partition de \([\![1, n]\!]\) en \(r+1\) sous-ensembles \(A_1, ..., A_{r+1}\) vérifiant :
+\begin{enumerate}[(i)]
 \item \(n \in A_{r+1}\)
 \item pour la couleur spéciale \(r + 1\) : \(\forall (x,y) \in A_{r+1}^2, x + y \notin A_{r+1}\),
-\item pour les autres couleurs \(c \in [\![1, r]\!]\) : \(\forall x \in \mathfrak{S}_{k_c - 1}(A_c), \exists (i, j) \in \mathfrak{S}_2^{k_c - 1}, \pi(x_i - x_j) \notin A_c\).
-\end{itemize}
+\item pour \(c \in [\![1, r]\!]\) : \(\forall x \in \mathfrak{S}_{k_c - 1}(A_c), \exists (i, j) \in {[\![1, k_c - 1]\!]}^2, i < j ~\text{et}~ \pi(x_j - x_i) \notin A_c\).
+\end{enumerate}
+ \(T(k_1, ..., k_r, t; n)\) désigne l'un (quelconque) de ces templates et l'ensemble de ces templates est noté \(\mathcal{T}(k_1, ..., k_r, t; n)\).
 \end{definition}
@@
 
-\begin{definition}[valeur par défaut]
-TODO
+\begin{definition}[coloriage par défaut]
+Soit \(n \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
+Soit \(\mathcal{H}\) un coloriage de \([\![1, n]\!]\) à \(r +1\) couleurs.
+On pose \(d = \min \mathcal{H}^{-1}(\{r + 1\}) - 1\).
+On définit alors un coloriage \(\findef(\mathcal{H})\), dit par défaut, associé au coloriage \(\mathcal{H}\) : \(\findef(\mathcal{H}) \defeq \mathcal{H}_{|\,[\![1, d]\!]}\).
 \end{definition}
+
+La méthode de construction suivante permet, à partir d'un template et d'un coloriage de Ramsey linéaire, de construire un nouveau coloriage de Ramsey linéaire (théorème \ref{thm:temp}).
 
@@
 
-Pour un \(b \in \mathbb{N}\), on se donne aussi un coloriage dit final \(\mathcal{F}\) de \([\![1, b]\!]\) à \(r + 1\) couleurs.
-Il est parfois utile de définir \(\mathcal{F}\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut : \(b = \min \mathcal{H}^{-1}(\{r + 1\}) - 1\) et \(\mathcal{F} = \findef(\mathcal{H}) \defeq \mathcal{H}_{|\,[\![1, b]\!]}\).
+Pour un \(d \in \mathbb{N}\), on se donne aussi un coloriage dit final \(\mathcal{F}\) de \([\![1, d]\!]\) à \(r + 1\) couleurs.
+Il est parfois utile de définir \(\mathcal{F}\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut \(\mathcal{F} = \findef(\mathcal{H})\).
 
-On construit alors un coloriage \(\gamma\) de \([\![1, n \times p + b]\!]\) à \(r + s\) couleurs comme suit.
+On construit alors un coloriage \(\gamma\) de \([\![1, n \times p + d]\!]\) à \(r + s\) couleurs comme suit.
 De manière informelle, on répéte \(p\) fois le motif formé l'enchaînement des couleurs dans \(\mathcal{H}\) en remplaçant pour la \(i\)-ème itération la couleur spéciale par \(r + \mathcal{V}(i)\) puis on ajoute à la fin le motif formé l'enchaînement des couleurs dans \(\mathcal{F}\).
@@
 \[\begin{array}{c c c c}
-	\gamma: & [\![1, n \times p + b]\!]  & \longrightarrow &  [\![1, r + s]\!] \\
+	\gamma: & [\![1, n \times p + d]\!]  & \longrightarrow &  [\![1, r + s]\!] \\
  	& x & \longmapsto & 
@@
 
+Pour un ensemble \(B \subset \mathbb{N}\) et \(k \in \mathbb{N}\), on note \(\mathcal{P}_k(B)\) l'ensemble des parties à \(k\) élélments de \(B\).
+Pour \(x \in \mathcal{P}_k(B)\), on note \(x = \{x_1, ..., x_k\}\).
+
+La définition suivante caractérise le fait que dans la construction le coloriage \(\mathcal{F}\) est moins contraint que le coloriage \(\mathcal{H}\) puisque les nombres coloriés par \(\mathcal{F}\) intéragissent seulement avec des nombres plus petits qu'eux, ce qui n'est pas le cas pour les nombres coloriés par \(\mathcal{H}\).
+
 \begin{definition}[compatibilité avec un template]
-TODO
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\).
+Soit \(n \in \mathbb{N}\).
+Soit \(T \in \mathcal{T}(k_1, ..., k_r, t; n)\) un template et soit \(A_1, ..., A_{r+1}\) la partition associée.
+Soit \(d \in [\![1, n]\!]\) et soit \(\mathcal{F}\) un coloriage de \([\![1, d]\!]\) et soit \(B_1, ..., B_{r+1}\) la partition associée.
+Le coloriage \(\mathcal{F}\) est dit compatible avec le template \(T\) si il vérifie :
+\begin{enumerate}[(i)]
+\item \(\forall (x,y) \in A_{r+1}^2, \pi(x + y) \leqslant d \implies \pi(x + y)  \notin B_{r+1}\)
+\item \(\forall (x,y) \in A_{r+1} \times B_{r+1}, x + y \leqslant d \implies x + y  \notin B_{r+1}\)
+\item \(\forall c \in [\![1, r]\!], \forall k \in [\![1, k_c-1]\!], \forall (x_i)_{1 \leqslant i \leqslant k} \in\mathcal{P}_k(B_c), \forall (y_i)_{1 \leqslant i \leqslant k_c - k - 1} \in \mathfrak{S}_{k_c - k - 1}(A_c), \\
+	\left\{ \text{ou} 
+	\begin{array}{l}
+		\exists (i, j) \in {[\![1, k]\!]}^2, |x_i - x_j| \notin A_c, \\
+		\exists (i, j) \in [\![1, k]\!] \times [\![1, k_c - k - 1]\!], x_i \geqslant y_j  ~\text{et}~ x_i - y_j \notin A_c ~\text{et}~  x_i - y_j  \notin B_c, \\
+		\exists (i, j) \in [\![1, k]\!] \times [\![1, k_c - k - 1]\!], x_i \leqslant y_j  ~\text{et}~ \pi(x_i - y_j) \notin A_c, \\
+		\exists (i, j) \in {[\![1, k_c - k - 1]\!]}^2, i < j ~\text{et}~ \pi(y_j - y_i) \notin A_c.
+	\end{array}
+	\right.\)
+\end{enumerate}
 \end{definition}
@@
 \begin{proposition}[compatibilité de la valeur par défaut]
-TODO
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\).
+Soit \(n \in \mathbb{N}\).
+Soit \(T \in \mathcal{T}(k_1, ..., k_r, t; n)\) un template.
+Alors \(T\) et \(\findef(T)\) sont compatibles.
 \end{proposition}
 
-\begin{theorem}[Construction en utilisant les templates]
+\begin{theorem}[Construction et templates]
+\label{thm:temp}
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\).
@@
 Soit \(\mathcal{H}\) un coloriage de \([\![1,n]\!]\) à \(r + 1\) couleurs.
+Soit \(d \in \mathbb{N}\) et soit \(\mathcal{F}\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
 Les deux conditions suivantes sont équivalentes.
@@
 \begin{enumerate}[(i)]
-\item \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\)
-\item \(\forall s \in \mathbb{N}^*, \forall l \in {[\![3, +\infty[\![}^s, \forall \mathcal{V} \in \mathcal{L}(l_1, ..., l_s ; p), \cons(\mathcal{H}, \mathcal{V}, \varnothing) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; n \times p)\)
+\item \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\) et \(\mathcal{F}\) est compatible  avec \(\mathcal{H}\).
+\item \(\forall s \in \mathbb{N}^*, \forall l \in {[\![3, +\infty[\![}^s, \forall \mathcal{V} \in \mathcal{L}(l_1, ..., l_s ; p), \cons(\mathcal{H}, \mathcal{V}, \mathcal{F}) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; n \times p + d)\)
 \end{enumerate}
-
-On suppose maintenant que \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\).
-Soient \(s \in \mathbb{N}^*, l \in [\![3, +\infty[\![^s\) et \(\mathcal{V} \in \mathcal{L}(l_1, ..., l_s ; p)\).
-Soit \(b \in \mathbb{N}\) et soit \(\mathcal{F}\) un coloriage de \([\![1, b]\!]\) à \(r + 1\) couleurs compatible avec \(\mathcal{H}\).
-Alors \(\cons(\mathcal{H}, \mathcal{V}, \mathcal{F}) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; n \times p + b)\).
 \end{theorem}
 
-Rowley évoque seulement \((i) \implies (ii)\) mais pas \((ii) \implies (i)\) qui montre l'optimalité des conditions dans la définition des templates.
-
+Rowley évoque seulement \((i) \implies (ii)\) mais pas \((ii) \implies (i)\) qui montre l'optimalité des conditions dans la définition des templates ainsi que celle de la définition de compatibilité.
 La construction de Rowley comprend uniquement le coloriage finale par défaut, l'introduction du coloriage final variable et la notion de compatibilité sont nouvelles.

### 2022-06-08 ramsey/amelioration_templates_ramsey_schur.tex
partie template complete

--- 2022-06-07 ramsey/amelioration_templates_tamsey_schur.tex
@@
 Ce document de travail présente des améliorations apportées au concept de template, notamment une généralisation : les b-templates.
-Cela conduit à une amélioration des inégalités et bornes inférieures connues certains nombre de Ramsey multicolores et certains nombres de Schur.
+Cela conduit à une amélioration des inégalités et bornes inférieures connues pour certains nombre de Ramsey multicolores et certains nombres de Schur.
 \end{abstract}
@@
 La section \ref{sec:temp} présente mon approche et mes résultats sur les templates.
-elle commence par une explication des différences avec l'approche de Rowley.
+Elle commence par une explication des différences avec l'approche de Rowley.
 Elle fait aussi office de revue de l'état de l'art en précisant les résultats de Rowley en fin de section.
@@
 
-On remarque que, contrairement aux nombres de Schur, les nombres de Ramsey désigne le plus petit entier tel qu'il n'existe pas de coloriage, et non pas la taille maximale d'un coloriage.
+Contrairement aux nombres de Schur, les nombres de Ramsey désignent le plus petit entier tel qu'il n'existe pas de coloriage, et non pas la taille maximale d'un coloriage.
 
@@
 
-On remarque qu'un \(L(k_1, ..., k_r ; n)\) induit un coloriage de \([\![1, n - 1]\!]\).
+Un \(L(k_1, ..., k_r ; n)\) induit un coloriage de \([\![1, n - 1]\!]\).
 Réciproquement, tout coloriage de \([\![1, n - 1]\!]\) correspond à un coloriage linéraire de \(K_n\).
@@
 \label{thm:lien-partitions}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\).
-Soit \(n \in \mathbb{N}\) et soit \(\gamma\) un coloriage de \([\![1, n]\!]\) avec \(r\) couleurs.
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
+Soit \(n \in \mathbb{N}^*\) et soit \(\gamma\) un coloriage de \([\![1, n]\!]\) avec \(r\) couleurs.
 Alors les deux conditions suivantes sont équivalentes :
@@
 \begin{corollary}[Lien avec les nombres de Schur]
-On a \(S(n) = L_n(3) - 2 \leqslant R_n(3) - 2\). 
+\[\forall n \in \mathbb{N}^*, S(n) = L_n(3) - 2 \leqslant R_n(3) - 2\] 
 \end{corollary}
@@
 Par ailleurs, je définis un template directement comme une partition pour laquelle la construction fonctionne.
-Enfin, J'utilise une formulation différente de la condition sur les templates.
+Enfin, j'utilise une formulation différente de la condition sur les templates.
 
@@
 Pour \(S\) un ensemble quelconque et \(a \in \mathbb{N}\) un entier naturel, on appelle permutation partielle à \(a\) éléments de \(S\) tout a-uplet d'éléments de \(S\) deux à deux distincts.
-L'ensemble des permutations partielles à \(a\) éléments de \(S\) est noté \(\mathfrak{S}_a(S)\), c'est-à-dire : \(\mathfrak{S}_a(S) = \left\{ (x_i)_{1 \leqslant i \leqslant a} ~|~ \forall (i, j) \in [\![1, a]\!]^2, i \neq j \implies x_i \neq x_j \right\}\).
+L'ensemble des permutations partielles à \(a\) éléments de \(S\) est noté \(\mathfrak{S}_a(S)\), c'est-à-dire : \(\mathfrak{S}_a(S) = \left\{ (x_i)_{1 \leqslant i \leqslant a} ~:~ \forall (i, j) \in [\![1, a]\!]^2, i \neq j \implies x_i \neq x_j \right\}\).
 \end{definition}
@@
 Soit \(n \in \mathbb{N}\).
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\).
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
 Un template de taille \(n\) à \(r + 1\) couleur, est défini comme une partition de \([\![1, n]\!]\) en \(r+1\) sous-ensembles \(A_1, ..., A_{r+1}\) vérifiant :
@@
 Il est parfois utile de définir \(\mathcal{F}\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut \(\mathcal{F} = \findef(\mathcal{H})\).
+Dans le cas où \(\mathcal{F}\) n'est pas utilisé, on note \(\mathcal{F} = \varnothing\) l'application vide.
 
@@
 
-La définition suivante caractérise le fait que dans la construction le coloriage \(\mathcal{F}\) est moins contraint que le coloriage \(\mathcal{H}\) puisque les nombres coloriés par \(\mathcal{F}\) intéragissent seulement avec des nombres plus petits qu'eux, ce qui n'est pas le cas pour les nombres coloriés par \(\mathcal{H}\).
+Lorsque l'on cherche à construire un \(L(k_1, ..., k_r ; n)\) à l'aide de la construction, le coloriage \(\mathcal{F}\) est moins contraint que le coloriage \(\mathcal{H}\) puisque les nombres coloriés par \(\mathcal{F}\) intéragissent seulement avec des nombres plus petits qu'eux, ce qui n'est pas le cas pour les nombres coloriés par \(\mathcal{H}\).
+C'est ce que caractérise la définition suivante.
 
 \begin{definition}[compatibilité avec un template]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\).
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\).
 Soit \(n \in \mathbb{N}\).
 Soit \(T \in \mathcal{T}(k_1, ..., k_r, t; n)\) un template et soit \(A_1, ..., A_{r+1}\) la partition associée.
-Soit \(d \in [\![1, n]\!]\) et soit \(\mathcal{F}\) un coloriage de \([\![1, d]\!]\) et soit \(B_1, ..., B_{r+1}\) la partition associée.
+Soit \(d \in [\![1, n]\!]\).
+Soit \(\mathcal{F}\) un coloriage de \([\![1, d]\!]\) et soit \(B_1, ..., B_{r+1}\) la partition associée.
 Le coloriage \(\mathcal{F}\) est dit compatible avec le template \(T\) si il vérifie :
@@
 \begin{proposition}[compatibilité de la valeur par défaut]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\).
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\).
 Soit \(n \in \mathbb{N}\).
@@
 
-\begin{theorem}[Construction et templates]
+\begin{theorem}[Construction de coloriages linéaires]
 \label{thm:temp}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in \mathbb{N}^r\) avec \(\forall c \in [\![1,r]\!], k_c \geqslant 3\).
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
 Soit \(n \in \mathbb{N}^*\).
@@
 Cela correspond à une extension aux templates pour les nombres de Ramsey du raffinement sur la dernière ligne pour les S-templates.
+
+Le théorème \ref{thm:temp} montre l'inégalité suivante.
+
+\begin{corollary}
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
+On pose \(a =\max \{p \in \mathbb{N}^* ~:~ \mathcal{T}(l_1, ..., l_s, t; p) \neq \varnothing\}\).
+On note \(d \in \mathbb{N}\) la taille maximale d'un coloriage \(\mathcal{F}\) tel qu'il existe\(T \in \mathcal{T}(l_1, ..., l_s, t; a)\) tel que \(\mathcal{F}\) est compatible avec \(T\).
+Alors \(L(k_1, ..., k_r, l_1, ..., l_s) - 2 \geqslant a (L(k_1, ..., k_r) - 2) + d\).
+\end{corollary}
+
+Le théorème \ref{thm:temp} consistue une généralisation de l'inégalité \(S(n + p) \geqslant S(n)  (2 \, S(p) + 1) + S(p)\) montrée dans \cite{AbbottHanson} et étendue aux nombres de Ramsey linéaires dans \cite{rowleyramseyabott}.
+Cette construction fournit des exemples de templates.
+
+\begin{proposition}
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r; n) \neq \varnothing\).
+Alors \(\mathcal{T}(k_1, ..., k_r, t; 2 \, n - 1) \neq \varnothing\).
+\end{proposition}
+
+La construction s'applique aussi aux templates (non évoqué par Rowley).
+
+\begin{proposition}[Construction de templates]
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
+Soit \((n, p) \in {\mathbb{N}^*}^2\).
+Soit \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\) et soit \(\mathcal{V} \in \mathcal{T}(l_1, ..., l_s, t; p)\).
+Alors on a \(\cons(\mathcal{H}, \mathcal{V}, \varnothing) \in \mathcal{T}(k_1, ..., k_r, l_1, ..., l_s, t; n \times p)\).
+\end{proposition}
+
+\begin{proposition}[Compatibilité et construction de templates]
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
+Soit \((n, p) \in {\mathbb{N}^*}^2\).
+Soit \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\) et soit \(\mathcal{V} \in \mathcal{T}(l_1, ..., l_s, t; p)\).
+Soit \(\mathcal{F}_\mathcal{H}\) un coloriage compatible avec \(\mathcal{H}\) et  soit \(\mathcal{F}_\mathcal{V}\) un coloriage compatible avec \(\mathcal{V}\).
+Alors  \(\cons(\mathcal{H}, \mathcal{F}_\mathcal{V}, \mathcal{F}_\mathcal{H})\) est compatible avec \(\cons(\mathcal{H}, \mathcal{V}, \varnothing)\).
+\end{proposition}
+
 \section{b-Templates}
 \label{sec:b-temp}
+Dans cette section, on introduit les \(b\)-templates. Les templates présentés dans la section \ref{sec:b-temp} vont apparaître comme un cas particulier des \(b\)-templates.
 
@@
 \label{sec:results}
+
+\subsection{Nombres de Schur}
+
+L'existence d'un 2-S-template de largeur 10 à 3 couleurs non exprimable en tant que S-template fournit une nouvelle inégalité. L'ancienne inégalité était \(S(n + 2) \geqslant 9 \, S(n) + 4\).
+
+\begin{proposition}
+	\[\forall n \in \mathbb{N}^*, S(n + 2) \geqslant 10 \, S(n) + 2\]
+\end{proposition}
+
+Cette inégalité fournit les nouvelles bornes inférieures suivantes : \(S(8) \geqslant 5\,362\) et \(S(13) \geqslant 2\,038\,282\) (contre respectivement \(5\,286\) dans \cite{RowleyRamsey} et \(2\,011\,290\) dans \cite{schurboyz}).
+Plus généralement, cette inégalité améliore les bornes inférieures des \(S(5 k + 3), \forall k \in \mathbb{N}^*\).
+
+\subsection{Nombres de Ramsey}
+
+On obtient des ingégalités de la forme \(L(k_1, ..., k_r, k_{r+1}, ..., k_{r+s}) - 2 \geqslant a \, (L(k_1, ..., k_r) - 2) + d\).
+Les "\(k_i\) ajoutés" désignent \( k_{r+1}, ..., k_{r+s}\).
+Dans le tableau ci-dessous, \(b\)-template désigne un \(b\)-template non exprimable en tant que template.
+Les anciennes valeurs viennent de \cite{rowleyramseysat}.
+\begin{table}[H]\begin{center}
+\begin{tabular}{| c | c | c | c | c |}
+	\hline
+	\(k_i\) ajoutés & ancien (a, d) & nouveau (a, d) & type de template & coloriage final \\
+	\hline
+	3, 3 & 9, 4 & 10, 2 & \(b\)-template & défaut \\
+	\hline
+	3, 4 & 18, 7 & 19, 2 & \(b\)-template & défaut \\
+	\hline
+	3, 5 & 30, 12 & 31, 3 & \(b\)-template & spécifique \\
+	\hline
+	4, 5 & 51, 21 & 55, 23 & template & défaut \\
+	\hline
+\end{tabular}
+\end{center}\end{table}
+
+En ce qui concerne les bornes inférieures, on a  \(R_8(3) \geqslant 5\,364\) et \(R_{13}(3)\geqslant 2\,038\,284\) (contre respectivement \(5\,288\) dans \cite{RowleyRamsey} et \(2\,011\,292\) dans \cite{schurboyz}), et plus généralement une amélioration pour les \(R_{5 k + 3}(3), \forall k \in \mathbb{N}^*\).
+On a aussi \(R(3 , 4 , 5 , 5) \geqslant 764\) (contre 729 dans \cite{rowleyramseysat}).
+Il existe de nombreuses inégalités récursives et constructions pour les nombres de Ramsey.
+Afin de savoir quelles bornes précisément ont été améliorées, il faudrait recenser chacunes des bornes inférieures et des méthodes existantes puis calculer toutes les bornes et voir si cetaines sont améliorées.
+Il est probable que les inégalités de cette section permettent d'améliorer les bornes inférieures pour d'autres nombres de Ramsey mais je n'ai pas effectué cette vérification.
 

### 2022-06-11 ramsey/explications/amelioration_templates_ramsey_schur.tex
avancement partie b-templates

--- 2022-06-08 ramsey/amelioration_templates_ramsey_schur.tex
@@
 \usepackage{mathtools}
+\usepackage{MyMnSymbol}
 
@@
 \DeclareMathOperator{\cons}{Cons}
-\DeclareMathOperator{\findef}{Default}
+\DeclareMathOperator{\coldef}{Default}
+\DeclareMathOperator{\tree}{Tree}
+\DeclareMathOperator{\treeset}{TreeSet}
 
 \newcommand{\defeq}{\vcentcolon=}
+\newcommand{\TS}{\mathit{TS}}
 
@@
 \item \(n \in A_{r+1}\)
-\item pour la couleur spéciale \(r + 1\) : \(\forall (x,y) \in A_{r+1}^2, x + y \notin A_{r+1}\),
-\item pour \(c \in [\![1, r]\!]\) : \(\forall x \in \mathfrak{S}_{k_c - 1}(A_c), \exists (i, j) \in {[\![1, k_c - 1]\!]}^2, i < j ~\text{et}~ \pi(x_j - x_i) \notin A_c\).
+\item \(\forall (x,y) \in A_{r+1}^2, x + y \notin A_{r+1}\),
+\item \(\forall c \in [\![1, r]\!] \forall x \in \mathfrak{S}_{k_c - 1}(A_c), \exists (i, j) \in {[\![1, k_c - 1]\!]}^2, i < j ~\text{et}~ \pi(x_j - x_i) \notin A_c\).
 \end{enumerate}
  \(T(k_1, ..., k_r, t; n)\) désigne l'un (quelconque) de ces templates et l'ensemble de ces templates est noté \(\mathcal{T}(k_1, ..., k_r, t; n)\).
+La couleur \(r + 1\) joue un rôle particulier et elle est appelée "couleur template".
 \end{definition}
 
-La couleur \(r + 1\)  n'est pas nécessairement la dernière par ordre d'apparition, la désignation de \(r+1\) comme couleur spéciale signalée par \(t\) est une convention qui allège les notations en évitant de devoir écrire \(T(k_1, ..., k_{i - 1}, t,  k_{i + 1}, ..., k_r; n)\).
+La couleur \(r + 1\)  n'est pas nécessairement la dernière par ordre d'apparition, la désignation de \(r+1\) comme couleur template signalée par \(t\) est une convention qui allège les notations en évitant de devoir écrire \(\mathcal{T}(k_1, ..., k_{i - 1}, t,  k_{i + 1}, ..., k_r; n)\) par exemple.
 
@@
 
-\begin{definition}[coloriage par défaut]
+\begin{definition}[Coloriage par défaut]
 Soit \(n \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
-Soit \(\mathcal{H}\) un coloriage de \([\![1, n]\!]\) à \(r +1\) couleurs.
-On pose \(d = \min \mathcal{H}^{-1}(\{r + 1\}) - 1\).
-On définit alors un coloriage \(\findef(\mathcal{H})\), dit par défaut, associé au coloriage \(\mathcal{H}\) : \(\findef(\mathcal{H}) \defeq \mathcal{H}_{|\,[\![1, d]\!]}\).
+Soit \(H\) un coloriage de \([\![1, n]\!]\) à \(r +1\) couleurs.
+On pose \(d = \min H^{-1}(\{r + 1\}) - 1\).
+On définit alors un coloriage \(\coldef(H)\), dit par défaut, associé au coloriage \(H\) : \(\coldef(H) \defeq H_{|\,[\![1, d]\!]}\).
 \end{definition}
@@
 Soit \((r, s) \in {\mathbb{N}^*}^2\).
-On se donne un coloriage de \([\![1, n]\!]\) à \(r + 1\) couleurs (appelée \(\mathcal{H}\), pour horizontal), et un coloriage de \([\![1, p]\!]\) à \(s\) couleurs (appelée \(\mathcal{V}\), pour vertical).
+On se donne un coloriage de \([\![1, n]\!]\) à \(r + 1\) couleurs (appelée \(H\), pour horizontal), et un coloriage de \([\![1, p]\!]\) à \(s\) couleurs (appelée \(V\), pour vertical).
 
-Pour un \(d \in \mathbb{N}\), on se donne aussi un coloriage dit final \(\mathcal{F}\) de \([\![1, d]\!]\) à \(r + 1\) couleurs.
-Il est parfois utile de définir \(\mathcal{F}\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut \(\mathcal{F} = \findef(\mathcal{H})\).
-Dans le cas où \(\mathcal{F}\) n'est pas utilisé, on note \(\mathcal{F} = \varnothing\) l'application vide.
+Pour un \(d \in \mathbb{N}\), on se donne aussi un coloriage dit final \(F\) de \([\![1, d]\!]\) à \(r + 1\) couleurs.
+Il est parfois utile de définir \(F\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut \(F = \coldef(H)\).
+Dans le cas où \(F\) n'est pas utilisé, on note \(F = \varnothing\) l'application vide.
 
 On construit alors un coloriage \(\gamma\) de \([\![1, n \times p + d]\!]\) à \(r + s\) couleurs comme suit.
-De manière informelle, on répéte \(p\) fois le motif formé l'enchaînement des couleurs dans \(\mathcal{H}\) en remplaçant pour la \(i\)-ème itération la couleur spéciale par \(r + \mathcal{V}(i)\) puis on ajoute à la fin le motif formé l'enchaînement des couleurs dans \(\mathcal{F}\).
+De manière informelle, on répéte \(p\) fois le motif formé l'enchaînement des couleurs dans \(H\) en remplaçant pour la \(i\)-ème itération la couleur spéciale par \(r + V(i)\) puis on ajoute à la fin le motif formé l'enchaînement des couleurs dans \(F\).
 Formellement :
@@
 		\left\{\begin{array}{l l}
-			\mathcal{H}(\pi(x)) & ~\text{si}~ x \leqslant n \times p ~\text{et}~ \mathcal{H}(\pi(x)) \neq r + 1 \\
-			r + \mathcal{V}\left(\left\lceil \dfrac{x}{n} \right\rceil\right) & ~\text{si}~ x \leqslant n \times p ~\text{et}~ \mathcal{H}(\pi(x)) = r + 1 \\
-			\mathcal{F}(x - n \times p) & ~\text{si}~ x > n \times p
+			H(\pi(x)) & ~\text{si}~ x \leqslant n \times p ~\text{et}~ H(\pi(x)) \neq r + 1 \\
+			r + V \left(\left\lceil \dfrac{x}{n} \right\rceil\right) & ~\text{si}~ x \leqslant n \times p ~\text{et}~ H(\pi(x)) = r + 1 \\
+			F(x - n \times p) & ~\text{si}~ x > n \times p
 		\end{array}\right.
@@
 \begin{figure}[H]\begin{center}
+\caption{Construction d'un \(L_4(3;40)\) avec \(H = T(3,3,t;9)\), \(V = L_2(3;4)\) et \(F = \coldef(H)\)}
+\vspace{1ex}
 \renewcommand{\arraystretch}{1.8}
@@
 \end{NiceTabular}
-\caption{Construction d'un \(L_4(3;40)\) avec \(\mathcal{H} = T(3,3,t;9)\), \(\mathcal{V} = L_2(3;4)\) et \(\mathcal{F} = \findef(\mathcal{H})\)}
 \end{center}\end{figure}
@@
 
-Lorsque l'on cherche à construire un \(L(k_1, ..., k_r ; n)\) à l'aide de la construction, le coloriage \(\mathcal{F}\) est moins contraint que le coloriage \(\mathcal{H}\) puisque les nombres coloriés par \(\mathcal{F}\) intéragissent seulement avec des nombres plus petits qu'eux, ce qui n'est pas le cas pour les nombres coloriés par \(\mathcal{H}\).
+Lorsque l'on cherche à construire un \(L(k_1, ..., k_r ; n)\) à l'aide de la construction, le coloriage \(F\) est moins contraint que le coloriage \(H\) puisque les nombres coloriés par \(F\) intéragissent seulement avec des nombres plus petits qu'eux, ce qui n'est pas le cas pour les nombres coloriés par \(H\).
 C'est ce que caractérise la définition suivante.
 
-\begin{definition}[compatibilité avec un template]
+\begin{definition}[Compatibilité avec un template]
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\).
@@
 Soit \(d \in [\![1, n]\!]\).
-Soit \(\mathcal{F}\) un coloriage de \([\![1, d]\!]\) et soit \(B_1, ..., B_{r+1}\) la partition associée.
-Le coloriage \(\mathcal{F}\) est dit compatible avec le template \(T\) si il vérifie :
+Soit \(F\) un coloriage de \([\![1, d]\!]\) et soit \(B_1, ..., B_{r+1}\) la partition associée.
+Le coloriage \(F\) est dit compatible avec le template \(T\) si il vérifie :
 \begin{enumerate}[(i)]
@@
 
-\begin{proposition}[compatibilité de la valeur par défaut]
+\begin{proposition}[Compatibilité de la valeur par défaut]
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\).
@@
 Soit \(T \in \mathcal{T}(k_1, ..., k_r, t; n)\) un template.
-Alors \(T\) et \(\findef(T)\) sont compatibles.
+Alors \(T\) et \(\coldef(T)\) sont compatibles.
 \end{proposition}
@@
 Soit \(n \in \mathbb{N}^*\).
-Soit \(\mathcal{H}\) un coloriage de \([\![1,n]\!]\) à \(r + 1\) couleurs.
-Soit \(d \in \mathbb{N}\) et soit \(\mathcal{F}\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
+Soit \(H\) un coloriage de \([\![1,n]\!]\) à \(r + 1\) couleurs.
+Soit \(d \in \mathbb{N}\) et soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
 Les deux conditions suivantes sont équivalentes.
@@
 \begin{enumerate}[(i)]
-\item \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\) et \(\mathcal{F}\) est compatible  avec \(\mathcal{H}\).
-\item \(\forall s \in \mathbb{N}^*, \forall l \in {[\![3, +\infty[\![}^s, \forall \mathcal{V} \in \mathcal{L}(l_1, ..., l_s ; p), \cons(\mathcal{H}, \mathcal{V}, \mathcal{F}) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; n \times p + d)\)
+\item \(H \in \mathcal{T}(k_1, ..., k_r, t; n)\) et \(F\) est compatible  avec \(H\).
+\item \(\forall s \in \mathbb{N}^*, \forall l \in {[\![3, +\infty[\![}^s, \forall V \in \mathcal{L}(l_1, ..., l_s ; p), \cons(H, V, F) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; n \times p + d)\)
 \end{enumerate}
@@
 
-\begin{corollary}
+\begin{corollary}[Inégalités pour les nombres de Ramsey linéaires]
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
@@
 On pose \(a =\max \{p \in \mathbb{N}^* ~:~ \mathcal{T}(l_1, ..., l_s, t; p) \neq \varnothing\}\).
-On note \(d \in \mathbb{N}\) la taille maximale d'un coloriage \(\mathcal{F}\) tel qu'il existe\(T \in \mathcal{T}(l_1, ..., l_s, t; a)\) tel que \(\mathcal{F}\) est compatible avec \(T\).
+On note \(d \in \mathbb{N}\) la taille maximale d'un coloriage \(F\) tel qu'il existe \(T \in \mathcal{T}(l_1, ..., l_s, t; a)\) tel que \(F\) est compatible avec \(T\).
 Alors \(L(k_1, ..., k_r, l_1, ..., l_s) - 2 \geqslant a (L(k_1, ..., k_r) - 2) + d\).
@@
 Soit \((n, p) \in {\mathbb{N}^*}^2\).
-Soit \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\) et soit \(\mathcal{V} \in \mathcal{T}(l_1, ..., l_s, t; p)\).
-Alors on a \(\cons(\mathcal{H}, \mathcal{V}, \varnothing) \in \mathcal{T}(k_1, ..., k_r, l_1, ..., l_s, t; n \times p)\).
+Soit \(H \in \mathcal{T}(k_1, ..., k_r, t; n)\) et soit \(V \in \mathcal{T}(l_1, ..., l_s, t; p)\).
+Alors on a \(\cons(H, V, \varnothing) \in \mathcal{T}(k_1, ..., k_r, l_1, ..., l_s, t; n \times p)\).
 \end{proposition}
@@
 Soit \((n, p) \in {\mathbb{N}^*}^2\).
-Soit \(\mathcal{H} \in \mathcal{T}(k_1, ..., k_r, t; n)\) et soit \(\mathcal{V} \in \mathcal{T}(l_1, ..., l_s, t; p)\).
-Soit \(\mathcal{F}_\mathcal{H}\) un coloriage compatible avec \(\mathcal{H}\) et  soit \(\mathcal{F}_\mathcal{V}\) un coloriage compatible avec \(\mathcal{V}\).
-Alors  \(\cons(\mathcal{H}, \mathcal{F}_\mathcal{V}, \mathcal{F}_\mathcal{H})\) est compatible avec \(\cons(\mathcal{H}, \mathcal{V}, \varnothing)\).
+Soit \(H \in \mathcal{T}(k_1, ..., k_r, t; n)\) et soit \(V \in \mathcal{T}(l_1, ..., l_s, t; p)\).
+Soit \(F_H\) un coloriage compatible avec \(H\) et  soit \(F_V\) un coloriage compatible avec \(V\).
+Alors  \(\cons(H, F_V, F_H)\) est compatible avec \(\cons(H, V, \varnothing)\).
 \end{proposition}
 
-\section{b-Templates}
+\section{\(b\)-Templates}
 \label{sec:b-temp}
-Dans cette section, on introduit les \(b\)-templates. Les templates présentés dans la section \ref{sec:b-temp} vont apparaître comme un cas particulier des \(b\)-templates.
+Dans cette section, on introduit les \(b\)-templates.
+Les templates présentés dans la section \ref{sec:b-temp} vont apparaître comme un cas particulier des \(b\)-templates puisqu'ils correspondent au cas \(b = 0\).
+
+\subsection{Définitions}
+On commence par décrire \(\TS_{b,k}\), un ensemble particulier de \(k\)-tuples qui sera utilisé dans la définition des \(b\)-templates.
+
+\begin{definition}[Arbre associé à un tuple]
+Soit \(a \in \mathbb{N}^*\), soit \(b \in \mathbb{N}\). A chaque tuple d'entiers, on associe un arbre de manière récurssive :
+\[ \left\{
+\begin{array}{l}
+	\forall x \in \mathbb{R}, \tree(x) = x, \\
+	\forall k \in [\![2, +\infty[\![, \forall x \in \mathbb{R}^k,
+		\left\{
+		\begin{array}{l l}
+			\tree(x) = (x_1, \tree(x_2, ..., x_k)) &  ~\text{si}~ x_2 - x_1 > b, \\
+			\tree(x) = (x_1, \tree(x_2, ..., x_k), \tree(x_2 + a, ..., x_k)) &  ~\text{si}~ 0 \leqslant x_2 - x_1 \leqslant b, \\
+			\tree(x) = \tree\left(x_1, x_2 + a \left\lceil \dfrac{x_1 - x_2}{a}\right\rceil, x_3, ..., x_k\right) & ~\text{si}~ x_2 < x_1.
+		\end{array}
+		\right.
+\end{array}
+\right. \]
+Pour un arbre \(\tree(x)\), on note \(\treeset(x)\) l'ensemble des tuples d'entiers que l'on peut construire en collectant les labels au cours d'une descente de cet arbre.
+\end{definition}
+
+\begin{definition}[Ensembles \(S_{b,k}(A)\) et \(\TS_{b,k}(A)\)]
+Soit \(A \subset \mathbb{N}^*\), soit \(b \in \mathbb{N}\) et soit \(k \in [\![2, +\infty[\![\).
+On note \(S_{b,k}(A)\) l'ensemble de \(k\)-tuples  à valeurs distinctes dans \(A\) et dont les éléments de \([\![1, b]\!]\) sont situés au début et apparaissent dans l'ordre croissant :\\
+\(S_{b,k}(A) = \left\{ x \in \mathfrak{S}_k(A) ~:~ \forall i \in  [\![2, k]\!], x_i \leqslant b \implies x_i \geqslant x_{i -1} \right\}\).
+On définit alors un ensemble \(\TS_{b,k}(A)\) de \(k\)-tuples : \(\TS_{b,k}(A) = \displaystyle\bigcup\limits_{x \in S_{b,k}(A)} \treeset(x)\).
+\end{definition}
+
+On définit aussi un opérateur de projection de \(\mathbb{Z}\) vers \([\![1, a + b]\!]\).
+
+\begin{definition}[Projection \(\pi_{a, b}\)]
+Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
+On définit une projection, noté \(\pi_{a, b}\) ou plus simplement \(\pi\) si il n'y a pas d'ambiguïté, sur \([\![1, a + b]\!]\) de la manière suivante.
+\[ \begin{array}{c c c l}
+	\pi_{a, b} : & \mathbb{Z} & \longrightarrow & [\![1, a + b]\!] \\
+	 & x & \longmapsto & 
+		\left\{
+		\begin{array}{l l}
+			x & ~\text{si}~ 1 \leqslant x \leqslant b \\
+			(x \mod a) + \mathds{1}_{[\![0, b]\!]}(x \mod a) & ~\text{si}~ x > b
+		\end{array}
+		\right.
+\end{array} \]
+\end{definition}
+
+On peut maintenant définir les \(b\)-templates.
+
+\begin{definition}[\(b\)-Templates]
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
+Un \(b\)-template de largeur \(a\) à \(r + 1\) couleurs, est défini comme une partition de \([\![1, a + b]\!]\) en \(r+1\) sous-ensembles \(A_1, ..., A_{r+1}\) vérifiant :
+\begin{enumerate}[(i)]
+\item \(a \in A_{r+1}\),
+\item \(\forall (x, y) \in A_{r + 1}^2, x + y \notin [\![a + b + 1, 2 a + b]\!] \implies \pi(x + y) \notin A_{r + 1}\),
+\item \(\forall c \in [\![1, c]\!], \forall x \in \TS_{b, k_c - 1}(A_c), \exists (i, j) \in {[\![1, k_c - 1]\!]}^2, i < j ~\text{et}~ \pi(x_j - x_i) \notin A_c\).
+\end{enumerate}
+ \(T_b(k_1, ..., k_r, t; a)\) désigne l'un (quelconque) de ces \(b\)-templates et l'ensemble de ces \(b\)-templates est noté \(\mathcal{T}_b(k_1, ..., k_r, t; a)\).
+La couleur \(r + 1\) joue un rôle particulier et elle est appelée "couleur template".
+\end{definition}
+
+La couleur \(r + 1\)  n'est pas nécessairement la dernière par ordre d'apparition, la désignation de \(r+1\) comme couleur template signalée par \(t\) est une convention qui allège les notations en évitant de devoir écrire \(\mathcal{T}_b(k_1, ..., k_{i - 1}, t,  k_{i + 1}, ..., k_r; n)\) par exemple.
+
+Dans le cas où tous les \(k_c\) sont égaux à 3, ces \(b\)-templates constituent des \(b\)-S-templates applicables pour les nombres de Schur similaires au \(b\)-WS-templates pour les nombres de Schur faibles définis dans \cite{schurboyz}.
+
+\begin{proposition}[Lien avec les templates]
+Soit \(r \in \mathbb{N}\), soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\) et soit \(a \in \mathbb{N}^*\). Alors :
+\[ \mathcal{T}(k_1, ..., k_r, t; a) = \mathcal{T}_0(k_1, ..., k_r, t; a). \]
+\end{proposition}
+
+\begin{definition}[Coloriage par défaut]
+Soit \(n \in \mathbb{N}^*\), soit \(b \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
+Soit \(H\) un coloriage de \([\![1, n]\!]\) à \(r +1\) couleurs.
+On pose \(d = \min \left(H^{-1}(\{r + 1\}) \backslash [\![1, b]\!] \right) - b  - 1\).
+On définit alors un coloriage \(\coldef_b(H)\), dit par défaut, associé au coloriage \(H\) :
+\[\begin{array}{c c c c}
+	\coldef_b(H) : & [\![1, d]\!] & \longrightarrow & [\![1, r + 1]\!] \\
+	 & x & \longmapsto & H(x + b)
+\end{array}\]
+\end{definition}
+
+\begin{definition}[Méthode de construction]
+Soit \((a, p) \in {\mathbb{N}^*}^2\) et soit \(b \in \mathbb{N}\).
+Soit \((r, s) \in {\mathbb{N}^*}^2\).
+On se donne un coloriage de \([\![1, a + b]\!]\) à \(r + 1\) couleurs (appelée \(H\), pour horizontal), et un coloriage de \([\![1, p]\!]\) à \(s\) couleurs (appelée \(V\), pour vertical).
+
+Pour un \(d \in \mathbb{N}\), on se donne aussi un coloriage dit final \(F\) de \([\![1, d]\!]\) à \(r + 1\) couleurs.
+Il est parfois utile de définir \(F\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut \(F = \coldef_b(H)\).
+Dans le cas où \(F\) n'est pas utilisé, on note \(F = \varnothing\) l'application vide.
+
+On construit alors un coloriage \(\gamma\) de \([\![1, a \times p + b + d]\!]\) à \(r + s\) couleurs comme suit.
+De manière informelle, on commence par utiliser le coloriage initial \(I \defeq H_{| \, [\![1, b]\!]}\), puis on répéte \(p\) fois le pattern \(P \defeq H_{| \, [\![b + 1, a + b]\!]}\) en remplaçant pour la \(i\)-ème itération la couleur spéciale par \(r + \mathcal{V}(i)\), et finalement on ajoute le motif formé l'enchaînement des couleurs dans \(\mathcal{F}\).
+Formellement :
+\[\begin{array}{c c c l}
+	\gamma: & [\![1, a \times p + b + d]\!]  & \longrightarrow &  [\![1, r + s]\!] \\
+ 	& x & \longmapsto & 
+		\left\{\begin{array}{l l}
+			H(x) & ~\text{si}~ x \leqslant b \\
+			H(\pi(x)) & ~\text{si}~  b + 1 \leqslant x \leqslant a \times p + b ~\text{et}~ H(\pi(x)) \neq r + 1 \\
+			r + V \left(\left\lceil \dfrac{x - b}{a} \right\rceil\right) & ~\text{si}~ b + 1 \leqslant x \leqslant a \times p + b ~\text{et}~ H(\pi(x)) = r + 1 \\
+			F(x - a \times p - b) & ~\text{si}~ x \geqslant a \times p + b + 1
+		\end{array}\right.
+\end{array}\]
+\end{definition}
+
+\begin{figure}[H]
+\caption{Exemple de construction avec \(b = 5\)}
+\renewcommand{\arraystretch}{1.7}
+\begin{center}
+
+\begin{tabular}{c}
+	\begin{NiceTabular}{c}[hvlines]
+		\CodeBefore
+			\cellcolor{cyan}{1-1}
+		\Body
+			couleur template
+	\end{NiceTabular} \\
+	coloriage \(H\) \\
+	\(
+		\begin{NiceArray}{*{17}{c}}[hvlines,last-row]
+		\CodeBefore
+			\cellcolor{red}{1-1}
+			\cellcolor{red}{1-2}
+			\cellcolor{cyan}{1-3}
+			\cellcolor{red}{1-4}
+			\cellcolor{green}{1-5}
+			\cellcolor{green}{1-6}
+			\cellcolor{red}{1-7}
+			\cellcolor{green}{1-8}
+			\cellcolor{cyan}{1-9}
+			\cellcolor{cyan}{1-10}
+			\cellcolor{cyan}{1-11}
+			\cellcolor{cyan}{1-12}
+			\cellcolor{cyan}{1-13}
+			\cellcolor{red}{1-14}
+			\cellcolor{green}{1-15}
+			\cellcolor{cyan}{1-16}
+			\cellcolor{red}{1-17}
+		\Body
+			\,\,1\,\, & \,\,2\,\, & \,\,3\,\, & \,\,4\,\, & \,\,5\,\, & \,\,6\,\, & \,\,7\,\, & \,\,8\,\, & \,\,9\,\, & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 \\
+			\Block{1-5}{\underbrace{\hphantom{................................}}_{\textstyle I}} & & & & & \Block{1-12}{\underbrace{\hphantom{..................................................................................}}_{\textstyle P}}
+		\end{NiceArray}\) \\
+	\begin{tabular}{c c}
+		coloriage \(V\) & coloriage \(F\) \\
+		\(
+			\begin{NiceArray}{c}[hvlines]
+			\CodeBefore
+				\cellcolor{cyan}{1-1}
+				\cellcolor{yellow}{2-1}
+				\cellcolor{yellow}{3-1}
+				\cellcolor{cyan}{4-1}
+			\Body
+				\,\,1\,\, \\
+				\,\,2\,\, \\
+				\,\,3\,\, \\
+				\,\,4\,\, \\
+			\end{NiceArray}\) &
+			\( \begin{NiceArray}{*{4}{c}}[hvlines]
+			\CodeBefore
+				\cellcolor{red}{1-1}
+				\cellcolor{cyan}{1-2}
+				\cellcolor{green}{1-3}
+				\cellcolor{green}{1-4}
+			\Body
+				\,\,1\,\, & \,\,2\,\, & \,\,3\,\, & \,\,4\,\,
+			\end{NiceArray}\) \\	
+	\end{tabular} \\
+	\(\cons_5(H, V, F)\) \\
+	\(
+		\begin{NiceArray}{*{12}{c}}[corners={NW,SE},hvlines]
+		\CodeBefore
+		    	\cellcolor{red}{1-8}
+			\cellcolor{red}{1-9}
+			\cellcolor{cyan}{1-10}
+			\cellcolor{red}{1-11}
+			\cellcolor{green}{1-12}
+			\cellcolor{green}{2-1}
+			\cellcolor{red}{2-2}
+			\cellcolor{green}{2-3}
+			\cellcolor{cyan}{2-4}
+			\cellcolor{cyan}{2-5}
+			\cellcolor{cyan}{2-6}
+			\cellcolor{cyan}{2-7}
+			\cellcolor{cyan}{2-8}
+			\cellcolor{red}{2-9}
+			\cellcolor{green}{2-10}
+			\cellcolor{cyan}{2-11}
+			\cellcolor{red}{2-12}
+			\cellcolor{green}{3-1}
+			\cellcolor{red}{3-2}
+			\cellcolor{green}{3-3}
+			\cellcolor{yellow}{3-4}
+			\cellcolor{yellow}{3-5}
+			\cellcolor{yellow}{3-6}
+			\cellcolor{yellow}{3-7}
+			\cellcolor{yellow}{3-8}
+			\cellcolor{red}{3-9}
+			\cellcolor{green}{3-10}
+			\cellcolor{yellow}{3-11}
+			\cellcolor{red}{3-12}
+			\cellcolor{green}{4-1}
+			\cellcolor{red}{4-2}
+			\cellcolor{green}{4-3}
+			\cellcolor{yellow}{4-4}
+			\cellcolor{yellow}{4-5}
+			\cellcolor{yellow}{4-6}
+			\cellcolor{yellow}{4-7}
+			\cellcolor{yellow}{4-8}
+			\cellcolor{red}{4-9}
+			\cellcolor{green}{4-10}
+			\cellcolor{yellow}{4-11}
+			\cellcolor{red}{4-12}
+			\cellcolor{green}{5-1}
+			\cellcolor{red}{5-2}
+			\cellcolor{green}{5-3}
+			\cellcolor{cyan}{5-4}
+			\cellcolor{cyan}{5-5}
+			\cellcolor{cyan}{5-6}
+			\cellcolor{cyan}{5-7}
+			\cellcolor{cyan}{5-8}
+			\cellcolor{red}{5-9}
+			\cellcolor{green}{5-10}
+			\cellcolor{cyan}{5-11}
+			\cellcolor{red}{5-12}
+			\cellcolor{red}{6-1}
+			\cellcolor{cyan}{6-2}
+			\cellcolor{green}{6-3}
+			\cellcolor{green}{6-4}
+		 \Body
+		    	   & & & & & & & 1 &  2 & 3 &  4 &  5 \\
+		    	 6 &  7 &  8 &  9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 \\
+		    	18 & 19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 & 28 & 29 \\
+		    	30 & 31 & 32 & 33 & 34 & 35 & 36 & 37 & 38 & 39 & 40 & 41 \\
+			42 & 43 & 44 & 45 & 46 & 47 & 48 & 49 & 50 & 51 & 51 & 53 \\
+			54 & 55 & 56 & 57 \\
+		\end{NiceArray}\)
+\end{tabular}
+\end{center}
+\end{figure}
+
+\begin{definition}[Compatibilité avec un \(b\)-template]
+TODO
+\end{definition}
+
+\subsection{Propriétés}
+
+\begin{proposition}[Compatibilité de la valeur par défaut]
+TODO
+\end{proposition}
+
+\begin{theorem}[Construction de coloriages linéaires]
+TODO
+\end{theorem}
+
+\begin{corollary}[Inégalités pour les nombres de Ramsey linéaires]
+TODO
+\end{corollary}
+
+\begin{proposition}[Construction de \(b\)-templates]
+TODO
+\end{proposition}
+
+\begin{proposition}[Compatibilité et construction de \(b\)-templates]
+TODO
+\end{proposition}
 

### 2022-06-11 ramsey/src/construction.py
cohérence noms

@@ -77,7 +77,7 @@ def save_partition(cliques, coloring):
     partition = [[] for _ in cliques]
     for x, c in enumerate(coloring, 1):
         partition[c - 1].append(x)
-    filename = f"../results/partitions/U({','.join(cliques)};{len(coloring)}).txt"
+    filename = f"../results/partitions/L({','.join(cliques)};{len(coloring)}).txt"
     with open(filename, 'w') as file:
         for col in partition:
             content = " ".join(map(str, col)) + '\n'

### 2022-06-14 ramsey/explications/amelioration_templates_ramsey_schur.tex
props b-templates

@@
 Soit \(d \in [\![1, n]\!]\).
-Soit \(F\) un coloriage de \([\![1, d]\!]\) et soit \(B_1, ..., B_{r+1}\) la partition associée.
+Soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r +1\) couleurs et soit \(B_1, ..., B_{r+1}\) la partition associée.
 Le coloriage \(F\) est dit compatible avec le template \(T\) si il vérifie :
@@
 \begin{definition}[Compatibilité avec un \(b\)-template]
-TODO
+Soit \(a \in \mathbb{N}^*\), soit \(b \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
+Soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, + \infty [\![}^r\).
+Soit \(T \in \mathcal{T}_b(k_1, ..., k_r; a)\) un \(b\)-template et soit \(A_1, ..., A_{r+1}\) la partition associée.
+Soit \(d \in [\![1, a]\!]\).
+Soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r +1\) couleurs et soit \(B_1, ..., B_{r + 1}\) la partition associée.
+Le coloriage \(F\)  est dit compatible avec le coloriage \(T\) si il vérifie :
+\begin{enumerate}[(i)]
+\item \(\forall (x,y) \in A_{r+1}^2, (x + y > b ~\text{et}~ \pi(x + y) \leqslant d) \implies \pi(x + y)  \notin B_{r+1}\)
+\item \(\forall (x,y) \in A_{r+1} \times B_{r+1}, x + y \leqslant d \implies x + y  \notin B_{r+1}\)
+\item \(\forall c \in [\![1, r]\!], \forall k \in [\![1, k_c-1]\!], \\
+	\left\{ \text{ou} 
+	\begin{array}{l}
+		\exists (i, j) \in {[\![1, k]\!]}^2, |x_i - x_j| \notin A_c, \\
+		TODO \\
+		\exists (i, j) \in {[\![1, k_c - k - 1]\!]}^2, i < j ~\text{et}~ \pi(y_j - y_i) \notin A_c.
+	\end{array}
+	\right.\)
+\end{enumerate}
 \end{definition}
@@
 \begin{proposition}[Compatibilité de la valeur par défaut]
-TODO
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\).
+Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
+Soit \(T \in \mathcal{T}_b(k_1, ..., k_r, t; a)\) un \(b\)-template.
+Alors \(T\) et \(\coldef_b(T)\) sont compatibles.
 \end{proposition}
@@
 \begin{theorem}[Construction de coloriages linéaires]
+\label{thm:b-temp}
 TODO
@@
 \begin{corollary}[Inégalités pour les nombres de Ramsey linéaires]
-TODO
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
+Soient \(a \in \mathbb{N}^*\) et \(b \in \mathbb{N}\) tels que \(\mathcal{T}_b(l_1, ..., l_s, t; a) \neq \varnothing\), et on fixe \(T\) un tel \(b\)-template.
+Soit \(d \in [\![1, a]\!]\) tel qu'il existe un coloriage de \([\![1, d]\!]\) à \(s + 1\) couleurs compatible avec \(T\).
+Alors \(L(k_1, ..., k_r, l_1, ..., l_s) - 2 \geqslant a (L(k_1, ..., k_r) - 2) + b + d\).
 \end{corollary}
@@
 \begin{proposition}[Construction de \(b\)-templates]
-TODO
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
+Soit \((a_H, a_V) \in {\mathbb{N}^*}^2\) et soit \((b_H, b_V) \in \mathbb{N}^2\).
+Soit \(H \in \mathcal{T}_{b_H}(k_1, ..., k_r, t; a_H)\) et soit \(V \in \mathcal{T}_{b_V}(l_1, ..., l_s, t; a_V)\).
+Alors on a \(\cons_{b_H}(H, V, \varnothing) \in \mathcal{T}_{b_H + a_H b_V}(k_1, ..., k_r, l_1, ..., l_s, t; a_H \times a_V)\).
 \end{proposition}
@@
 \begin{proposition}[Compatibilité et construction de \(b\)-templates]
-TODO
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
+Soit \((a_H, a_V) \in {\mathbb{N}^*}^2\) et soit \((b_H, b_V) \in \mathbb{N}^2\).
+Soit \(H \in \mathcal{T}_{b_H}(k_1, ..., k_r, t; a_H)\) et soit \(V \in \mathcal{T}_{b_V}(l_1, ..., l_s, t; a_V)\).
+Soit \(F_H\) un coloriage compatible avec \(H\) et  soit \(F_V\) un coloriage compatible avec \(V\).
+Alors \(\cons_{b_H}(H, F_V, F_H)\) est compatible avec \(\cons_{b_H}(H, V, \varnothing)\).
 \end{proposition}
+
+Les deux propositions précédentes ainsi que leur réciproques forment un équivalent du théoèreme \ref{thm:b-temp} pour les \(b\)-templates.
 

### 2022-06-15 ramsey/explications/amelioration_templates_ramsey_schur.tex
structure + -1 pour alléger

@@
 \newtheorem{corollary}[definition]{Corollaire}
+\newtheorem{lemma}[definition]{Lemme}
 \newtheorem{proposition}[definition]{Proposition}
+\newtheorem{example}{Exemple}[section]
 
@@
 On appelle coloriage de Ramsey linéaire tout \(R(k_1, ..., k_r ; n)\) pour lequel la couleur de l'arête \((u, v)\) dépend uniquement de \(|u - v|\).
-Un \(L(k_1, ..., k_r ; n)\) désigne l'un (quelconque) de ces coloriages et l'ensemble de ces coloriages est noté \(\mathcal{L}(k_1, ..., k_r ; n)\).
-Si tous les \(k_c\) sont égaux à un \(k\), on utilise également les notations \(L_r(k; n)\) et \(\mathcal{L}_r(k; n)\).
+Un \(L(k_1, ..., k_r ; n - 1)\) désigne l'un (quelconque) de ces coloriages et l'ensemble de ces coloriages est noté \(\mathcal{L}(k_1, ..., k_r ; n - 1)\).
+Si tous les \(k_c\) sont égaux à un \(k\), on utilise également les notations \(L_r(k; n - 1)\) et \(\mathcal{L}_r(k; n - 1)\).
 \end{definition}
@@
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
-On définit le nombre de Ramsey linéaire \(L(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r ; n) = \varnothing\).
+On définit le nombre de Ramsey linéaire \(L(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r ; n - 1) = \varnothing\).
 Si tous les \(k_c\) sont égaux à un \(k\), ce nombre est également noté \(L_r(k)\).
@@
 Soit \(H\) un coloriage de \([\![1,n]\!]\) à \(r + 1\) couleurs.
-Soit \(d \in \mathbb{N}\) et soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
+Soit \(d \in [\![0, n - 1]\!]\) et soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
 Les deux conditions suivantes sont équivalentes.
@@
 Soit \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r; n) \neq \varnothing\).
-Alors \(\mathcal{T}(k_1, ..., k_r, t; 2 \, n - 1) \neq \varnothing\).
+Alors \(\mathcal{T}(k_1, ..., k_r, t; 2 \, n + 1) \neq \varnothing\).
 \end{proposition}
@@
 \end{proposition}
+
+Les deux propositions précédentes ainsi que leur réciproques forment un équivalent du théoèreme \ref{thm:temp} pour les templates.
 
@@
 
+\begin{example}
+TODO - type Abott pour ramsey (cf  Rowley 2017)
+\end{example}
+
 \begin{proposition}[Lien avec les templates]
@@
 \[ \mathcal{T}(k_1, ..., k_r, t; a) = \mathcal{T}_0(k_1, ..., k_r, t; a). \]
+\end{proposition}
+
+\begin{proposition}
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
+Alors  \(T_b(k_1, ..., k_r, t; a) \subset L(k_1, ..., k_r, 3; a + b)\).
 \end{proposition}
@@
 
+\begin{proposition}[Condition suffisante pour les templates]
+TODO
+\end{proposition}
+
 \begin{proposition}[Compatibilité de la valeur par défaut]
@@
 \label{thm:b-temp}
-TODO
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
+Soit \(H\) un coloriage de \([\![1, a + b]\!]\) à \(r + 1\) couleurs.
+Soit \(d \in [\![0, a - 1]\!]\) et soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
+Les deux conditions suivantes sont équivalentes.
+
+\begin{enumerate}[(i)]
+\item \(H \in \mathcal{T}_b(k_1, ..., k_r, t; a)\) et \(F\) est compatible  avec \(H\).
+\item \(\forall s \in \mathbb{N}^*, \forall l \in {[\![3, +\infty[\![}^s, \forall V \in \mathcal{L}(l_1, ..., l_s ; p), \cons_b(H, V, F) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; a \times p + b + d)\)
+\end{enumerate}
 \end{theorem}
@@
 
-\begin{proposition}[Construction de \(b\)-templates]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
-Soit \((a_H, a_V) \in {\mathbb{N}^*}^2\) et soit \((b_H, b_V) \in \mathbb{N}^2\).
-Soit \(H \in \mathcal{T}_{b_H}(k_1, ..., k_r, t; a_H)\) et soit \(V \in \mathcal{T}_{b_V}(l_1, ..., l_s, t; a_V)\).
-Alors on a \(\cons_{b_H}(H, V, \varnothing) \in \mathcal{T}_{b_H + a_H b_V}(k_1, ..., k_r, l_1, ..., l_s, t; a_H \times a_V)\).
-\end{proposition}
+\begin{lemma}[associativité de la construction]
+TODO
+\end{lemma}
 
-\begin{proposition}[Compatibilité et construction de \(b\)-templates]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
-Soit \((a_H, a_V) \in {\mathbb{N}^*}^2\) et soit \((b_H, b_V) \in \mathbb{N}^2\).
-Soit \(H \in \mathcal{T}_{b_H}(k_1, ..., k_r, t; a_H)\) et soit \(V \in \mathcal{T}_{b_V}(l_1, ..., l_s, t; a_V)\).
-Soit \(F_H\) un coloriage compatible avec \(H\) et  soit \(F_V\) un coloriage compatible avec \(V\).
-Alors \(\cons_{b_H}(H, F_V, F_H)\) est compatible avec \(\cons_{b_H}(H, V, \varnothing)\).
-\end{proposition}
-
-Les deux propositions précédentes ainsi que leur réciproques forment un équivalent du théoèreme \ref{thm:b-temp} pour les \(b\)-templates.
+\begin{theorem}[Construction de \(b\)-templates]
+TODO
+\end{theorem}
 

### 2022-06-22 ramsey/explications/amelioration_templates_ramsey_schur.tex
reciproques

@@
 
-\begin{example}
-TODO - type Abott pour ramsey (cf  Rowley 2017)
-\end{example}
+La construction présentée dans \cite{rowleyramseyabott} utilise des coloriages linéaires afin de construire des \(0\)-templates.
+La proposition suivante présente cette construction sous l'angle des \(b\)-templates.
+\begin{proposition}
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r; n) \neq \varnothing\) et on se donne \(\gamma\) un tel coloriage.
+On définit un nouveau coloriage T de la manière suivante.
+\[\begin{array}{c c c l}
+	T : & [\![1, 2 n + 1]\!] & \longrightarrow & [\![1, r + 1]\!] \\
+	 & x & \longmapsto & \left\{
+		\begin{array}{l l}
+			\gamma(x) & ~\text{si}~ x \leqslant n \\
+			r + 1 & ~\text{si}~ x > n \\
+		\end{array}
+		\right.
+\end{array}\]
+Alors \(T \in \mathcal{T}_0(k_1, ..., k_r, t; 2 \, n + 1)\).
+\end{proposition}
 
@@
 
+On a une cractérisation similaire à celle donnée dans \cite{RowleyRamsey} pour les sf-templates.
 \begin{proposition}[Condition suffisante pour les templates]
-TODO
+Soit \(a \in \mathbb{N}^*\), soit \(b \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
+Soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, + \infty [\![}^r\).
+Soit \(T\) un coloriage de \([\![1,  a + b]\!]\) à \(r + 1\) couleurs.
+Soit \(d \in [\![1, a - 1 ]\!]\) et soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
+Soit \(n \in [\![3, + \infty [\![\) tel que \(n \geqslant \max_{1 \leqslant c \leqslant r} k_c - 1\).
+Soit \(s \in \mathbb{N}^*\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, + \infty [\![}^s\).
+Soit enfin \(\gamma \in \mathcal{L}(l_1, ..., l_s; n)\) tel qu'il existe une couleur \(c \in [\![1, s]\!]\) et un sous-ensemble \(S\) de \([\![1, n]\!]\) monochromatique de couleur \(c\) et de cardinal \(k_c - 2\) vérifiant pour tous \(x, y \in S\) distincts, \(\gamma(|x - y|) = c\).
+Supposons que \(\cons_b(T, \gamma, F) \in \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s; a n + b + d)\).
+Alors \(T \in \mathcal{T}_b(k_1, ..., k_r, t; a)\) et \(F\) est compatible avec \(T\).
 \end{proposition}
@@
 TODO
+\[
+\cons_{b_{H_1}}(H_1, , )
+\]
 \end{lemma}

### 2022-06-23 article_ramsey/template_improvement.tex
intro

--- 2022-06-22 ramsey/explications/amelioration_templates_ramsey_schur.tex
@@
 \documentclass{article}
-\title{Une amélioration des templates pour les nombres de Ramsey mutlticolores et les nombres de Schur}
+\title{Improving the templates for multicolor Ramsey numbers and Schur numbers}
 \author{Romain Ageron}
@@
 
-\usepackage[french]{babel}
 \usepackage[hyphens]{url}
@@
 \newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}[definition]{Théorème}
-\newtheorem{corollary}[definition]{Corollaire}
-\newtheorem{lemma}[definition]{Lemme}
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{corollary}[definition]{Corollary}
+\newtheorem{lemma}[definition]{Lemma}
 \newtheorem{proposition}[definition]{Proposition}
-\newtheorem{example}{Exemple}[section]
 
@@
 \begin{abstract}
-Récement, l'introduction de constructions basées sur des objets particuliers appelés "templates" a permis d'améliorer plusieurs bornes inférieures pour les nombres Ramsey multicolores, les nombres de Schur et les nombres de Schur faibles.
-Ce document de travail présente des améliorations apportées au concept de template, notamment une généralisation : les b-templates.
-Cela conduit à une amélioration des inégalités et bornes inférieures connues pour certains nombre de Ramsey multicolores et certains nombres de Schur.
+Lower bounds for several multicolor Ramsey numbers as well as Schur numbers have recently been improved using a 
+construction based on a particular type of colorings nammed "sf-templates". This article describes a generalization of 
+the sf-templates: the \(b\)-templates.
 \end{abstract}
 
-\section{Organisation de ce document de travail}
-La section \ref{sec:def} présente des notations, des définitions, ainsi que des propriétés utiles.
-La section \ref{sec:temp} présente mon approche et mes résultats sur les templates.
-Elle commence par une explication des différences avec l'approche de Rowley.
-Elle fait aussi office de revue de l'état de l'art en précisant les résultats de Rowley en fin de section.
-La section \ref{sec:b-temp} introduit les b-templates, une généralisation des templates qui est utilisée dans la plupart des améliorations présentées.
-La section \ref{sec:results} compare les nouvelles inégalités et bornes inférieures à celles connues auparavant.
+\section{Introduction}
+This article addresses the edge-coloring of complete graphs in an arbitrary number of colors while limiting the clique 
+number in each color. In \cite{RowleyRamsey}, a construction using as a repeating pattern a particular type of 
+colorings nammed sf-templates is described and used to improve lower bounds on several Ramsey numbers as well as Schur 
+numbers.
 
-\section{Définitions et propriétés}
+Ramsey numbers and Schur numbers are defined in Section \ref{sec:def}. Section \ref{sec:temp} defines the 
+\(b\)-templates and describes the corrresponding construction. Section \ref{sec:results} states and proves the main 
+results on \(b\)-templates and the construction. Section \ref{sec:bounds} records the new inequalities and some new 
+lower bounds.
+
+\section{Definitions}
 \label{sec:def}
@@
 
-\section{Templates}
+\section{\(b\)-Templates}
 \label{sec:temp}
-
-Dans cette section, j'utilise des notations et définitions différentes de celle de Rowley \cite{RowleyRamsey}.
-Notamment, les templates et constructions sont introduits différement et sont manipulés en termes de partitions et non de graphes.
-De plus la couleur spéciale est désignée de manière abstraite par un "t" au lieu d'un "3" qui pourrait être confondu avec l'un des \(k_c\).
-Par ailleurs, je définis un template directement comme une partition pour laquelle la construction fonctionne.
-Enfin, j'utilise une formulation différente de la condition sur les templates.
-
-\begin{definition}[Permutation partielle]
-Pour \(S\) un ensemble quelconque et \(a \in \mathbb{N}\) un entier naturel, on appelle permutation partielle à \(a\) éléments de \(S\) tout a-uplet d'éléments de \(S\) deux à deux distincts.
-L'ensemble des permutations partielles à \(a\) éléments de \(S\) est noté \(\mathfrak{S}_a(S)\), c'est-à-dire : \(\mathfrak{S}_a(S) = \left\{ (x_i)_{1 \leqslant i \leqslant a} ~:~ \forall (i, j) \in [\![1, a]\!]^2, i \neq j \implies x_i \neq x_j \right\}\).
-\end{definition}
-
-Dans cette section, pour un entier \(n\) (en pratique sous-entendu), on note \(\pi\) l'application qui a un entier \(x \in \mathbb{Z}\) associe son unique représentant modulo \(n\) dans \([\![1, n]\!]\).
-
-\begin{definition}[Reformulation des templates]
-Soit \(n \in \mathbb{N}\).
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Un template de taille \(n\) à \(r + 1\) couleur, est défini comme une partition de \([\![1, n]\!]\) en \(r+1\) sous-ensembles \(A_1, ..., A_{r+1}\) vérifiant :
-\begin{enumerate}[(i)]
-\item \(n \in A_{r+1}\)
-\item \(\forall (x,y) \in A_{r+1}^2, x + y \notin A_{r+1}\),
-\item \(\forall c \in [\![1, r]\!] \forall x \in \mathfrak{S}_{k_c - 1}(A_c), \exists (i, j) \in {[\![1, k_c - 1]\!]}^2, i < j ~\text{et}~ \pi(x_j - x_i) \notin A_c\).
-\end{enumerate}
- \(T(k_1, ..., k_r, t; n)\) désigne l'un (quelconque) de ces templates et l'ensemble de ces templates est noté \(\mathcal{T}(k_1, ..., k_r, t; n)\).
-La couleur \(r + 1\) joue un rôle particulier et elle est appelée "couleur template".
-\end{definition}
-
-La couleur \(r + 1\)  n'est pas nécessairement la dernière par ordre d'apparition, la désignation de \(r+1\) comme couleur template signalée par \(t\) est une convention qui allège les notations en évitant de devoir écrire \(\mathcal{T}(k_1, ..., k_{i - 1}, t,  k_{i + 1}, ..., k_r; n)\) par exemple.
-
-Dans le cas où tous les \(k_c\) sont égaux à 3, on retouve la définition des S-templates.
-
-\begin{definition}[Coloriage par défaut]
-Soit \(n \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
-Soit \(H\) un coloriage de \([\![1, n]\!]\) à \(r +1\) couleurs.
-On pose \(d = \min H^{-1}(\{r + 1\}) - 1\).
-On définit alors un coloriage \(\coldef(H)\), dit par défaut, associé au coloriage \(H\) : \(\coldef(H) \defeq H_{|\,[\![1, d]\!]}\).
-\end{definition}
-
-La méthode de construction suivante permet, à partir d'un template et d'un coloriage de Ramsey linéaire, de construire un nouveau coloriage de Ramsey linéaire (théorème \ref{thm:temp}).
-
-\begin{definition}[Méthode de construction]
-Soit \((n, p) \in {\mathbb{N}^*}^2\) les tailles des coloriages.
-Soit \((r, s) \in {\mathbb{N}^*}^2\).
-On se donne un coloriage de \([\![1, n]\!]\) à \(r + 1\) couleurs (appelée \(H\), pour horizontal), et un coloriage de \([\![1, p]\!]\) à \(s\) couleurs (appelée \(V\), pour vertical).
-
-Pour un \(d \in \mathbb{N}\), on se donne aussi un coloriage dit final \(F\) de \([\![1, d]\!]\) à \(r + 1\) couleurs.
-Il est parfois utile de définir \(F\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut \(F = \coldef(H)\).
-Dans le cas où \(F\) n'est pas utilisé, on note \(F = \varnothing\) l'application vide.
-
-On construit alors un coloriage \(\gamma\) de \([\![1, n \times p + d]\!]\) à \(r + s\) couleurs comme suit.
-De manière informelle, on répéte \(p\) fois le motif formé l'enchaînement des couleurs dans \(H\) en remplaçant pour la \(i\)-ème itération la couleur spéciale par \(r + V(i)\) puis on ajoute à la fin le motif formé l'enchaînement des couleurs dans \(F\).
-Formellement :
-\[\begin{array}{c c c c}
-	\gamma: & [\![1, n \times p + d]\!]  & \longrightarrow &  [\![1, r + s]\!] \\
- 	& x & \longmapsto & 
-		\left\{\begin{array}{l l}
-			H(\pi(x)) & ~\text{si}~ x \leqslant n \times p ~\text{et}~ H(\pi(x)) \neq r + 1 \\
-			r + V \left(\left\lceil \dfrac{x}{n} \right\rceil\right) & ~\text{si}~ x \leqslant n \times p ~\text{et}~ H(\pi(x)) = r + 1 \\
-			F(x - n \times p) & ~\text{si}~ x > n \times p
-		\end{array}\right.
-\end{array}\]
-\end{definition}
-
-\begin{figure}[H]\begin{center}
-\caption{Construction d'un \(L_4(3;40)\) avec \(H = T(3,3,t;9)\), \(V = L_2(3;4)\) et \(F = \coldef(H)\)}
-\vspace{1ex}
-\renewcommand{\arraystretch}{1.8}
-\begin{NiceTabular}{|*{9}{c|}}[corners=SE,standard-cline,hlines]
-\CodeBefore
-	\cellcolor{red}{1-1}
-	\cellcolor{green}{1-2}
-	\cellcolor{green}{1-3}
-	\cellcolor{red}{1-4}
-	\cellcolor{cyan}{1-5}
-	\cellcolor{cyan}{1-6}
-	\cellcolor{red}{1-7}
-	\cellcolor{cyan}{1-8}
-	\cellcolor{cyan}{1-9}
-	\cellcolor{red}{2-1}
-	\cellcolor{green}{2-2}
-	\cellcolor{green}{2-3}
-	\cellcolor{red}{2-4}
-	\cellcolor{yellow}{2-5}
-	\cellcolor{yellow}{2-6}
-	\cellcolor{red}{2-7}
-	\cellcolor{yellow}{2-8}
-	\cellcolor{yellow}{2-9}
-	\cellcolor{red}{3-1}
-	\cellcolor{green}{3-2}
-	\cellcolor{green}{3-3}
-	\cellcolor{red}{3-4}
-	\cellcolor{yellow}{3-5}
-	\cellcolor{yellow}{3-6}
-	\cellcolor{red}{3-7}
-	\cellcolor{yellow}{3-8}
-	\cellcolor{yellow}{3-9}
-	\cellcolor{red}{4-1}
-	\cellcolor{green}{4-2}
-	\cellcolor{green}{4-3}
-	\cellcolor{red}{4-4}
-	\cellcolor{cyan}{4-5}
-	\cellcolor{cyan}{4-6}
-	\cellcolor{red}{4-7}
-	\cellcolor{cyan}{4-8}
-	\cellcolor{cyan}{4-9}
-	\cellcolor{red}{5-1}
-	\cellcolor{green}{5-2}
-	\cellcolor{green}{5-3}
-	\cellcolor{red}{5-4}
-\Body
-	1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
-	10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 \\
-	19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 \\
-	28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 \\
-	37 & 38 & 39 & 40 \\
-\end{NiceTabular}
-\end{center}\end{figure}
-
-Pour un ensemble \(B \subset \mathbb{N}\) et \(k \in \mathbb{N}\), on note \(\mathcal{P}_k(B)\) l'ensemble des parties à \(k\) élélments de \(B\).
-Pour \(x \in \mathcal{P}_k(B)\), on note \(x = \{x_1, ..., x_k\}\).
-
-Lorsque l'on cherche à construire un \(L(k_1, ..., k_r ; n)\) à l'aide de la construction, le coloriage \(F\) est moins contraint que le coloriage \(H\) puisque les nombres coloriés par \(F\) intéragissent seulement avec des nombres plus petits qu'eux, ce qui n'est pas le cas pour les nombres coloriés par \(H\).
-C'est ce que caractérise la définition suivante.
-
-\begin{definition}[Compatibilité avec un template]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\).
-Soit \(n \in \mathbb{N}\).
-Soit \(T \in \mathcal{T}(k_1, ..., k_r, t; n)\) un template et soit \(A_1, ..., A_{r+1}\) la partition associée.
-Soit \(d \in [\![1, n]\!]\).
-Soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r +1\) couleurs et soit \(B_1, ..., B_{r+1}\) la partition associée.
-Le coloriage \(F\) est dit compatible avec le template \(T\) si il vérifie :
-\begin{enumerate}[(i)]
-\item \(\forall (x,y) \in A_{r+1}^2, \pi(x + y) \leqslant d \implies \pi(x + y)  \notin B_{r+1}\)
-\item \(\forall (x,y) \in A_{r+1} \times B_{r+1}, x + y \leqslant d \implies x + y  \notin B_{r+1}\)
-\item \(\forall c \in [\![1, r]\!], \forall k \in [\![1, k_c-1]\!], \forall (x_i)_{1 \leqslant i \leqslant k} \in\mathcal{P}_k(B_c), \forall (y_i)_{1 \leqslant i \leqslant k_c - k - 1} \in \mathfrak{S}_{k_c - k - 1}(A_c), \\
-	\left\{ \text{ou} 
-	\begin{array}{l}
-		\exists (i, j) \in {[\![1, k]\!]}^2, |x_i - x_j| \notin A_c, \\
-		\exists (i, j) \in [\![1, k]\!] \times [\![1, k_c - k - 1]\!], x_i \geqslant y_j  ~\text{et}~ x_i - y_j \notin A_c ~\text{et}~  x_i - y_j  \notin B_c, \\
-		\exists (i, j) \in [\![1, k]\!] \times [\![1, k_c - k - 1]\!], x_i \leqslant y_j  ~\text{et}~ \pi(x_i - y_j) \notin A_c, \\
-		\exists (i, j) \in {[\![1, k_c - k - 1]\!]}^2, i < j ~\text{et}~ \pi(y_j - y_i) \notin A_c.
-	\end{array}
-	\right.\)
-\end{enumerate}
-\end{definition}
-
-\begin{proposition}[Compatibilité de la valeur par défaut]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\).
-Soit \(n \in \mathbb{N}\).
-Soit \(T \in \mathcal{T}(k_1, ..., k_r, t; n)\) un template.
-Alors \(T\) et \(\coldef(T)\) sont compatibles.
-\end{proposition}
-
-\begin{theorem}[Construction de coloriages linéaires]
-\label{thm:temp}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(n \in \mathbb{N}^*\).
-Soit \(H\) un coloriage de \([\![1,n]\!]\) à \(r + 1\) couleurs.
-Soit \(d \in [\![0, n - 1]\!]\) et soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
-Les deux conditions suivantes sont équivalentes.
-
-\begin{enumerate}[(i)]
-\item \(H \in \mathcal{T}(k_1, ..., k_r, t; n)\) et \(F\) est compatible  avec \(H\).
-\item \(\forall s \in \mathbb{N}^*, \forall l \in {[\![3, +\infty[\![}^s, \forall V \in \mathcal{L}(l_1, ..., l_s ; p), \cons(H, V, F) \in  \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s ; n \times p + d)\)
-\end{enumerate}
-\end{theorem}
-
-Rowley évoque seulement \((i) \implies (ii)\) mais pas \((ii) \implies (i)\) qui montre l'optimalité des conditions dans la définition des templates ainsi que celle de la définition de compatibilité.
-La construction de Rowley comprend uniquement le coloriage finale par défaut, l'introduction du coloriage final variable et la notion de compatibilité sont nouvelles.
-Cela correspond à une extension aux templates pour les nombres de Ramsey du raffinement sur la dernière ligne pour les S-templates.
-
-Le théorème \ref{thm:temp} montre l'inégalité suivante.
-
-\begin{corollary}[Inégalités pour les nombres de Ramsey linéaires]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
-On pose \(a =\max \{p \in \mathbb{N}^* ~:~ \mathcal{T}(l_1, ..., l_s, t; p) \neq \varnothing\}\).
-On note \(d \in \mathbb{N}\) la taille maximale d'un coloriage \(F\) tel qu'il existe \(T \in \mathcal{T}(l_1, ..., l_s, t; a)\) tel que \(F\) est compatible avec \(T\).
-Alors \(L(k_1, ..., k_r, l_1, ..., l_s) - 2 \geqslant a (L(k_1, ..., k_r) - 2) + d\).
-\end{corollary}
-
-Le théorème \ref{thm:temp} consistue une généralisation de l'inégalité \(S(n + p) \geqslant S(n)  (2 \, S(p) + 1) + S(p)\) montrée dans \cite{AbbottHanson} et étendue aux nombres de Ramsey linéaires dans \cite{rowleyramseyabott}.
-Cette construction fournit des exemples de templates.
-
-\begin{proposition}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r; n) \neq \varnothing\).
-Alors \(\mathcal{T}(k_1, ..., k_r, t; 2 \, n + 1) \neq \varnothing\).
-\end{proposition}
-
-La construction s'applique aussi aux templates (non évoqué par Rowley).
-
-\begin{proposition}[Construction de templates]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
-Soit \((n, p) \in {\mathbb{N}^*}^2\).
-Soit \(H \in \mathcal{T}(k_1, ..., k_r, t; n)\) et soit \(V \in \mathcal{T}(l_1, ..., l_s, t; p)\).
-Alors on a \(\cons(H, V, \varnothing) \in \mathcal{T}(k_1, ..., k_r, l_1, ..., l_s, t; n \times p)\).
-\end{proposition}
-
-\begin{proposition}[Compatibilité et construction de templates]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(s \in \mathbb{N}\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, +\infty[\![}^s\).
-Soit \((n, p) \in {\mathbb{N}^*}^2\).
-Soit \(H \in \mathcal{T}(k_1, ..., k_r, t; n)\) et soit \(V \in \mathcal{T}(l_1, ..., l_s, t; p)\).
-Soit \(F_H\) un coloriage compatible avec \(H\) et  soit \(F_V\) un coloriage compatible avec \(V\).
-Alors  \(\cons(H, F_V, F_H)\) est compatible avec \(\cons(H, V, \varnothing)\).
-\end{proposition}
-
-Les deux propositions précédentes ainsi que leur réciproques forment un équivalent du théoèreme \ref{thm:temp} pour les templates.
-
-\section{\(b\)-Templates}
-\label{sec:b-temp}
 Dans cette section, on introduit les \(b\)-templates.
@@
 
-\subsection{Définitions}
 On commence par décrire \(\TS_{b,k}\), un ensemble particulier de \(k\)-tuples qui sera utilisé dans la définition des \(b\)-templates.
@@
 
-\subsection{Propriétés}
+\section{Properties of the \(b\)-templates}
+\label{sec:results}
 
@@
 \section{Nouvelles inégalités et bornes inférieures}
-\label{sec:results}
+\label{sec:bounds}
 

### 2022-06-23 article_schur/article.tex
intro

--- 2022-02-26 article/soumission_SIAM/article.tex
@@
-\documentclass[review,onefignum,onetabnum]{siamart190516}
-
+\documentclass{article}
+
+\usepackage{amsmath}
 \usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{dsfont}
@@
 
+\usepackage[english]{babel}
+\usepackage[hyphens]{url}
+\usepackage{hyperref}
+\hypersetup{hidelinks}
+\usepackage[utf8]{inputenc}
+\usepackage{siunitx}
 \usepackage{float}
 
+\usepackage[table]{xcolor}
+\usepackage{multirow}
 \usepackage{nicematrix}
 
-\newsiamremark{remark}{Remark}
+\addtolength{\textheight}{108pt} \addtolength{\topmargin}{-60pt}
+\oddsidemargin=-6pt \addtolength{\textwidth}{120pt}
+\righthyphenmin=2
+
+\renewcommand{\qedsymbol}{\(\square\)}
+
+\newtheorem{definition}{Definition}[section]
+\newtheorem{notation}[definition]{Notation}
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{computational theorem}[definition]{Computational Theorem}
+\newtheorem{corollary}[definition]{Corollary}
+\newtheorem{remark}[definition]{Remark}
+\newtheorem{proposition}[definition]{Proposition}
 
@@
 
-\title{New lower bounds for Schur and weak Schur numbers \thanks{Submitted to the editors 02/24/2022.}}
-
-\author{Romain Ageron\thanks{CentraleSup\'elec, Universit\'e{} Paris-Saclay, Gif-sur-Yvette, France
-	(\email{romain.ageron@student-cs.fr}, \email{paul.casteras@student-cs.fr},
-	\email{thibaut.pellerin@student-cs.fr}, \email{yann.portella@student-cs.fr}).}
-\and Paul Casteras\footnotemark[2]
-\and Thibaut Pellerin\footnotemark[2]
-\and Yann Portella\footnotemark[2]
-\and Arpad Rimmel\footnotemark[2]\ \thanks{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, Orsay, France
-	(\email{arpad.rimmel@centralesupelec.fr}).}
-\and Joanna Tomasik\footnotemark[2]\ \footnotemark[3]\ \thanks{Corresponding author
-	(\email{joanna.tomasik@centralesupelec.fr}).}}
-
-\headers{New lower bounds for Schur and weak Schur numbers}{R. Ageron, P. Casteras,
-T. Pellerin, Y. Portella, A. Rimmel, J. Tomasik}
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  \addtocounter{footnote}{-1}%
+  \endgroup
+}
+
+\title{New lower bounds for Schur and weak Schur numbers}
+
+\author{
+Romain Ageron\textsuperscript{a,1}\and
+Paul Casteras\textsuperscript{a,1}\and
+Thibaut Pellerin\textsuperscript{a,1}\and
+Yann Portella\textsuperscript{a,1}\and
+Arpad Rimmel\textsuperscript{b,2}\and
+Joanna Tomasik\textsuperscript{b,2,}*
+}
+
+\date{
+	\textsuperscript{a}CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190, Gif-sur-Yvette, France\\
+	\textsuperscript{b}LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France\\[2ex]
+	\today
+}
 
 \begin{document}
+
 \maketitle
+
+\blfootnote{\textsuperscript{1}These authors contributed equally.}
+\blfootnote{\textsuperscript{2}These authors supervised the work of the main authors.}
+\blfootnote{*Corresponding author (\tt{joanna.tomasik@centralesupelec.fr})}
+\vspace{-5ex}
 
@@
 
-\begin{keywords}
-	Schur number, Weak Schur number, Ramsey theory, Sum-free partition
-\end{keywords}
-
-\begin{AMS}
-	05D10, 11P81, 05A17, 11B75
-\end{AMS}
+Keywords: Schur number, Weak Schur number, Ramsey theory, Sum-free partition
+
+MSC 2020: 05D10, 05A17, 11B75, 11P81
 
@@
 
-\begin{table}[tbhp]
+\begin{table}[H]
 {\footnotesize
@@
 
-\begin{figure}[tbhp]
+\begin{figure}[H]
 {\footnotesize
@@
 
+\bibliographystyle{IEEEtran}
 \bibliography{biblio}
-\bibliographystyle{siamplain}
 
@@
 	\hline
-	1 & 1, 2, 4, 8, 11, 22, 25, \mathbf{(N+1)}\\
-	\hline
-	2 & 3, 5, 6, 7, 19, 21, 23, 36\\
-	\hline
-	3 & 9, 10, 12, 13, 14, 15, 16, 17, 18, 20\\
-	\hline
-	4 & 24, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 37, 38, 39, 40, 41, 42\\
+	1 & 1, 2, 4, 8, 11, 22, 25, 48, 53, \mathbf{(N+1)}\\
+	\hline
+	2 & 3, 5, 6, 7, 19, 21, 23, 36, 50, 51, 52, 63, 64, 65\\
+	\hline
+	3 & 9, 10, 12, 13, 14, 15, 16, 17, 18, 20, 54, 55, 56, 57, 58, 59, 60, 61, 62\\
+	\hline
+	4 & 24, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 49\\
 	\hline
@@
 This template provides the inequality \(\WS (n+3) \geqslant 42 \, S(n) + 24\)
-by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset.
+by placing one last number, here represented by \(\mathbf{(N+1)}\), in the first subset (see Proposition \ref{prop:tunelastrow}).
 

### 2022-06-25 article_ramsey/template_improvement.tex
definitions

@@
 Lower bounds for several multicolor Ramsey numbers as well as Schur numbers have recently been improved using a 
-construction based on a particular type of colorings nammed "sf-templates". This article describes a generalization of 
-the sf-templates: the \(b\)-templates.
+pattern based construction with a particular type of coloring nammed "sf-template". This article describes a 
+generalization of the sf-templates: the \(b\)-templates.
 \end{abstract}
@@
 This article addresses the edge-coloring of complete graphs in an arbitrary number of colors while limiting the clique 
-number in each color. In \cite{RowleyRamsey}, a construction using as a repeating pattern a particular type of 
-colorings nammed sf-templates is described and used to improve lower bounds on several Ramsey numbers as well as Schur 
-numbers.
+number in each color, as well as sum-free colorings of positive integers. A pattern based construction which uses a 
+particular type of coloring nammed sf-template was described in \cite{RowleyRamsey}. This construction was used to 
+improve lower bounds on several Ramsey numbers as well as Schur numbers. Lower bounds were then improved by describing 
+larger templates in \cite{schurboyz} for Schur numbers and in \cite{rowleyramseysat} for multicolor Ramsey numbers.
 
@@
 \(b\)-templates and describes the corrresponding construction. Section \ref{sec:results} states and proves the main 
-results on \(b\)-templates and the construction. Section \ref{sec:bounds} records the new inequalities and some new 
+results on \(b\)-templates and on the construction. Section \ref{sec:bounds} records the new inequalities and some new 
 lower bounds.
@@
 
-Pour \(n \in \mathbb{N}\), on note \(K_n\) le graphe complet d'ordre \(n\).
-
-\begin{definition}[Coloriage de Ramsey]
-Soit \(n \in \mathbb{N}\), la taille du graphe, et soit \(r \in \mathbb{N}\), le nombre de couleurs.
-Soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
-On appelle coloriage de Ramsey tout coloriage des arêtes de \(K_n\) avec \(r\) couleurs tel que pour toute couleur \(c \in [\![1, r]\!]\), le coloriage ne contient pas de sous-graphe complet \(K_{k_c}\) monochromatique en la couleur \(c\).
-\(R(k_1, ..., k_r ; n)\) désigne l'un (quelconque) de ces coloriages et l'ensemble de ces coloriages est noté \(\mathcal{R}(k_1, ..., k_r ; n)\).
-Si tous les \(k_c\) sont égaux à un \(k\), on utilise également les notations \(R_r(k; n)\) et \(\mathcal{R}_r(k; n)\).
+\begin{definition}[Coloring and partition]
+Let \(S\) and \(T\) be two sets. A coloring of \(S\) with colors in \(T\) is an application 
+\(\gamma: S \rightarrow T\). The partition associated to the coloring \(\gamma\) is the partition 
+\((\gamma^{-1}(t))_{t \in T ~\text{and}~ \gamma^{-1}(\{t\}) \neq \varnothing}\). Conversely, the coloring associated to 
+a partition \((A_i)_{i \in I}\) for some \(I \subset T\) is the application \(\gamma: S \rightarrow T\) such that 
+\(\forall s \in S, \forall t \in T, \gamma(s) = t \iff s \in A_t\).
 \end{definition}
 
-\begin{theorem}[Théorème de Ramsey fini \cite{Ramsey}]
+The set of positive natural numbers is denoted by \(\mathbb{N}^* = \mathbb{N} \backslash \{0\}\). Given two integers 
+\(a, b \in \mathbb{Z}\), the set of integers \(\{a, a + 1, ..., b - 1, b\}\) is denoted by \([\![a, b]\!]\). For 
+\(n \in \mathbb{N}\),  the complete graph of order \(n\) is denoted by \(K_n\).
+
+\begin{definition}[Ramsey coloring]
+Let  \(n \in \mathbb{N}\), the order of the graph, and let \(r \in \mathbb{N}\), the number of colors. Let 
+\((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). A Ramsey coloring is an edge coloring of \(K_n\) with 
+\(r\) colors such that for any color \(c \in [\![1, r]\!]\), the coloring does not contain any monochramatic complete 
+sub-graph of order \(k_c\) with color \(c\). The set of these colorings is denoted by 
+\(\mathcal{R}(k_1, ..., k_r ; n)\).
+\end{definition}
+
+\begin{theorem}[Ramsey's theorem \cite{Ramsey}]
 \label{thm:ram}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). Alors il existe un entier \(n \in \mathbb{N}\) tel que \(\mathcal{R}(k_1, ..., k_r ; n) = \varnothing\).
+Let \(r \in \mathbb{N}\) and let \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). Then there is 
+\(n \in \mathbb{N}\) such that \(\mathcal{R}(k_1, ..., k_r ; n) = \varnothing\).
 \end{theorem}
 
-Le théorème \ref{thm:ram} justifie la définition suivante.
+Theorem \ref{thm:ram} leads to the following definition.
 
-\begin{definition}[Nombre de Ramsey]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
-On définit le nombre de Ramsey \(R(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel que \(\mathcal{R}(k_1, ..., k_r ; n) = \varnothing\).
-Si tous les \(k_c\) sont égaux à un \(k\), ce nombre est également noté \(R_r(k)\).
+\begin{definition}[Multicolor Ramsey number]
+Let \(r \in \mathbb{N}\) and let \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). The multicolor Ramsey  
+number \(R(k_1, ..., k_r)\) is defined as the smallest integer \(n \in \mathbb{N}\) such 
+\(\mathcal{R}(k_1, ..., k_r ; n) = \varnothing\). If all the \(k_c\)'s are equal to some \(k\), this Ramsey number is 
+also denoted by \(R_r(k)\).
 \end{definition}
 
-Contrairement aux nombres de Schur, les nombres de Ramsey désignent le plus petit entier tel qu'il n'existe pas de coloriage, et non pas la taille maximale d'un coloriage.
+The construction described in \cite{RowleyRamsey} as well as the one described in this article use a subset of Ramsey 
+colorings, the linear Ramsey colorings.
 
-\begin{definition}[Coloriage de Ramsey linéaire]
-Soit \(n \in \mathbb{N}\), et soit \(r \in \mathbb{N}\).
-Soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
-On indexe les sommets de \(K_n\) avec les entiers de \([\![0, n - 1]\!]\).
-On appelle coloriage de Ramsey linéaire tout \(R(k_1, ..., k_r ; n)\) pour lequel la couleur de l'arête \((u, v)\) dépend uniquement de \(|u - v|\).
-Un \(L(k_1, ..., k_r ; n - 1)\) désigne l'un (quelconque) de ces coloriages et l'ensemble de ces coloriages est noté \(\mathcal{L}(k_1, ..., k_r ; n - 1)\).
-Si tous les \(k_c\) sont égaux à un \(k\), on utilise également les notations \(L_r(k; n - 1)\) et \(\mathcal{L}_r(k; n - 1)\).
+\begin{definition}[Linear Ramsey coloring]
+Let \(n \in \mathbb{N}\), and let \(r \in \mathbb{N}\). Let \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). 
+We assume that the vertices of \(K_{n + 1}\) are the integers from \([\![0, n]\!]\). A linear Ramsey coloring is any 
+Ramsey coloring such that the color of the edge \((u, v)\) only depends on the value of \(|u - v|\). The set of these 
+colorings is denoted by \(\mathcal{L}(k_1, ..., k_r ; n)\). The integer coloring associated to a linear Ramsey coloring 
+is the coloring of \([\![1, n]\!]\) such that every \(x \in [\![1, n]\!]\) is colored with the color of the edges \((u, v)\) 
+such that \(|u - v| = x\).
 \end{definition}
 
-Le théorème \ref{thm:ram} justifie la définition suivante.
+Unlike Ramsey colorings, the set \(\mathcal{L}(k_1, ..., k_r ; n)\) corresponds to graph colorings of order \(n + 1\). 
+This definition is chosen in this article because linear Ramsey colorings are studied using their associated integer 
+coloring. Also, in this article the linear Ramsey numbers are defined as the largest size of a coloring (contrary to 
+Ramsey numbers) because it is more convenient in inequalities.
 
-\begin{definition}[Nombre de Ramsey linéaire]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
-On définit le nombre de Ramsey linéaire \(L(k_1, ..., k_r)\) comme le plus petit entier \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r ; n - 1) = \varnothing\).
-Si tous les \(k_c\) sont égaux à un \(k\), ce nombre est également noté \(L_r(k)\).
+\begin{definition}[Linear Ramsey number]
+Let \(r \in \mathbb{N}\) and let \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). The linear Ramsey number 
+\(L(k_1, ..., k_r)\) is defined as the largest integer \(n \in \mathbb{N}\) such that 
+\(\mathcal{L}(k_1, ..., k_r ; n) \neq \varnothing\). If all the \(k_c\)'s are equal to some \(k\), this linear Ramsey 
+number is also denoted by \(L_r(k)\).
 \end{definition}
 
-\begin{proposition}
-\(\forall r \in \mathbb{N}, (k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r, L(k_1, ..., k_r) \leqslant R(k_1, ..., k_r)\)
-\end{proposition}
+Linear Ramsey numbers can be used to construct lower bounds for Ramsey numbers because a linear Ramsey coloring is 
+also a Ramsey coloring. Therefore for all \(r \in \mathbb{N}\) and for all 
+\((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\), \(R(k_1, ..., k_r) \geqslant L(k_1, ..., k_r) + 2\).
 
-Un \(L(k_1, ..., k_r ; n)\) induit un coloriage de \([\![1, n - 1]\!]\).
-Réciproquement, tout coloriage de \([\![1, n - 1]\!]\) correspond à un coloriage linéraire de \(K_n\).
-Le théorème suivant porte sur le lien entre un coloriage sur \([\![1, n]\!]\) et les nombres de cliques du coloriage linéaire de \(K_{n+1}\) associé.
+Let \(n \in \mathbb{N}\). Any linear coloring of \(K_{n + 1}\) induces a coloring of \([\![1, n]\!]\). Conversely, any 
+coloring of \([\![1, n]\!]\) corresponds to a linear coloring of \(K_{n + 1}\). Theorem \ref{thm:linkintegers} gives a 
+link between some sum-free properties of the coloring of \([\![1, n]\!]\) and the clique numbers of the associated 
+coloring of \(K_{n+1}\).
 
-\begin{theorem}[Lien avec les coloriages sans-sommes \cite{AbbottHanson}]
-\label{thm:lien-partitions}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\).
-Soit \(n \in \mathbb{N}^*\) et soit \(\gamma\) un coloriage de \([\![1, n]\!]\) avec \(r\) couleurs.
-Alors les deux conditions suivantes sont équivalentes :
+\begin{theorem}[Link to sum-free colorings \cite{AbbottHanson}]
+\label{thm:linkintegers}
+Let \(r \in \mathbb{N}\) and let \((k_c)_{1 \leqslant c \leqslant r} \in {\mathbb{N}^*}^r\). Let \(n \in \mathbb{N}^*\) 
+and let \(\gamma\) be a coloring of \([\![1, n]\!]\) with \(r\) colors. Then the two following conditions are equivalent.
 \begin{enumerate}[(i)]
-\item dans le coloriage linéaire de \(K_{n+1}\) associé à \(\gamma\), la couleur \(c\) contient un sous-graphe complet de taille \(k_c\)
-\item il existe un sous-ensemble \(S\) de \([\![1, n]\!]\) monochromatique de couleur \(c\) et de cardinal \(k_c - 1\) vérifiant : pour tous \(x, y \in S\) distincts, \(\gamma(|x - y|) = c\) 
+\item There is a monochromatic subgraph of order \(k_c\) with color \(c\) in the linear coloring of \(K_{n+1}\) 
+	associated  to \(\gamma\).
+\item There is a monochromatic subset \(S\) of \([\![1, n]\!]\) with color \(c\) and cardinality \(k_c - 1\) such that 
+	for all distinct \(x, y \in S\), \(\gamma(|x - y|) = c\).
 \end{enumerate}
@@
 
-Dans la suite, on utilise également \(L(k_1, ..., k_r ; n)\) pour désigner un coloriage de \([\![1, n - 1]\!]\)  associé à un \(L(k_1, ..., k_r ; n)\).
+\begin{definition}[Schur number]
+A subset \(A\) of \(\mathbb{N}\) is said to be sum-free if \(\forall (a, b) \in A^2, a + b \notin A\). Let 
+\(n \in \mathbb{N}\). Schur proved in \cite{Schur1917} that there is a largest integer denoted by \(S(n)\) such that 
+\([\![1, S(n)]\!]\) can be partioned into \(n\) sum-free subsets. \(S(n)\) is called the \(n\)\textsuperscript{th} 
+Schur number.
+\end{definition}
 
-Le théorème \ref{thm:lien-partitions} donne le corollaire suivant.
-
-\begin{corollary}[Lien avec les nombres de Schur]
-\[\forall n \in \mathbb{N}^*, S(n) = L_n(3) - 2 \leqslant R_n(3) - 2\] 
-\end{corollary}
+Theorem \ref{thm:linkintegers} shows a link between Schur numbers and Ramsey numbers:
+\[\forall n \in \mathbb{N}^*, S(n) = L_n(3) \leqslant R_n(3) - 2\].
 

### 2022-06-26 article_ramsey/template_improvement.tex
definitions

@@
 \section{Introduction}
+
 This article addresses the edge-coloring of complete graphs in an arbitrary number of colors while limiting the clique 
@@
 Theorem \ref{thm:linkintegers} shows a link between Schur numbers and Ramsey numbers:
-\[\forall n \in \mathbb{N}^*, S(n) = L_n(3) \leqslant R_n(3) - 2\].
+\[\forall n \in \mathbb{N}^*, S(n) = L_n(3) \leqslant R_n(3) - 2.\]
 
@@
 \label{sec:temp}
-Dans cette section, on introduit les \(b\)-templates.
-Les templates présentés dans la section \ref{sec:b-temp} vont apparaître comme un cas particulier des \(b\)-templates puisqu'ils correspondent au cas \(b = 0\).
 
-On commence par décrire \(\TS_{b,k}\), un ensemble particulier de \(k\)-tuples qui sera utilisé dans la définition des \(b\)-templates.
+\begin{definition}[Construction method]
+Let \((a, p) \in {\mathbb{N}^*}^2\) and let \(b \in \mathbb{N}\). Let \((r, s) \in {\mathbb{N}^*}^2\). Let \(H\) 
+(standing for "horizontal") be a coloring of \([\![1, a + b]\!]\) with \(r + 1\) colors, and let \(V\)  (standing for 
+"vertical") be a coloring of \([\![1, p]\!]\) with \(s\) colors. Let \(d \in \mathbb{N}\) and let \(F\) (standing for 
+"final") be a coloring of \([\![1, d]\!]\) with \(r + 1\) colors. The empty coloring (i.e. \(d = 0\)) is denoted by 
+\(F = \varnothing\). The construction produces a coloring \(\cons_b(H, V, F)\) of \([\![1, a p + b + d]\!]\) with 
+\(r + s\) colors.
 
-\begin{definition}[Arbre associé à un tuple]
-Soit \(a \in \mathbb{N}^*\), soit \(b \in \mathbb{N}\). A chaque tuple d'entiers, on associe un arbre de manière récurssive :
-\[ \left\{
-\begin{array}{l}
-	\forall x \in \mathbb{R}, \tree(x) = x, \\
-	\forall k \in [\![2, +\infty[\![, \forall x \in \mathbb{R}^k,
-		\left\{
-		\begin{array}{l l}
-			\tree(x) = (x_1, \tree(x_2, ..., x_k)) &  ~\text{si}~ x_2 - x_1 > b, \\
-			\tree(x) = (x_1, \tree(x_2, ..., x_k), \tree(x_2 + a, ..., x_k)) &  ~\text{si}~ 0 \leqslant x_2 - x_1 \leqslant b, \\
-			\tree(x) = \tree\left(x_1, x_2 + a \left\lceil \dfrac{x_1 - x_2}{a}\right\rceil, x_3, ..., x_k\right) & ~\text{si}~ x_2 < x_1.
-		\end{array}
-		\right.
-\end{array}
-\right. \]
-Pour un arbre \(\tree(x)\), on note \(\treeset(x)\) l'ensemble des tuples d'entiers que l'on peut construire en collectant les labels au cours d'une descente de cet arbre.
-\end{definition}
-
-\begin{definition}[Ensembles \(S_{b,k}(A)\) et \(\TS_{b,k}(A)\)]
-Soit \(A \subset \mathbb{N}^*\), soit \(b \in \mathbb{N}\) et soit \(k \in [\![2, +\infty[\![\).
-On note \(S_{b,k}(A)\) l'ensemble de \(k\)-tuples  à valeurs distinctes dans \(A\) et dont les éléments de \([\![1, b]\!]\) sont situés au début et apparaissent dans l'ordre croissant :\\
-\(S_{b,k}(A) = \left\{ x \in \mathfrak{S}_k(A) ~:~ \forall i \in  [\![2, k]\!], x_i \leqslant b \implies x_i \geqslant x_{i -1} \right\}\).
-On définit alors un ensemble \(\TS_{b,k}(A)\) de \(k\)-tuples : \(\TS_{b,k}(A) = \displaystyle\bigcup\limits_{x \in S_{b,k}(A)} \treeset(x)\).
-\end{definition}
-
-On définit aussi un opérateur de projection de \(\mathbb{Z}\) vers \([\![1, a + b]\!]\).
-
-\begin{definition}[Projection \(\pi_{a, b}\)]
-Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
-On définit une projection, noté \(\pi_{a, b}\) ou plus simplement \(\pi\) si il n'y a pas d'ambiguïté, sur \([\![1, a + b]\!]\) de la manière suivante.
-\[ \begin{array}{c c c l}
-	\pi_{a, b} : & \mathbb{Z} & \longrightarrow & [\![1, a + b]\!] \\
-	 & x & \longmapsto & 
-		\left\{
-		\begin{array}{l l}
-			x & ~\text{si}~ 1 \leqslant x \leqslant b \\
-			(x \mod a) + \mathds{1}_{[\![0, b]\!]}(x \mod a) & ~\text{si}~ x > b
-		\end{array}
-		\right.
-\end{array} \]
-\end{definition}
-
-On peut maintenant définir les \(b\)-templates.
-
-\begin{definition}[\(b\)-Templates]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
-Un \(b\)-template de largeur \(a\) à \(r + 1\) couleurs, est défini comme une partition de \([\![1, a + b]\!]\) en \(r+1\) sous-ensembles \(A_1, ..., A_{r+1}\) vérifiant :
-\begin{enumerate}[(i)]
-\item \(a \in A_{r+1}\),
-\item \(\forall (x, y) \in A_{r + 1}^2, x + y \notin [\![a + b + 1, 2 a + b]\!] \implies \pi(x + y) \notin A_{r + 1}\),
-\item \(\forall c \in [\![1, c]\!], \forall x \in \TS_{b, k_c - 1}(A_c), \exists (i, j) \in {[\![1, k_c - 1]\!]}^2, i < j ~\text{et}~ \pi(x_j - x_i) \notin A_c\).
-\end{enumerate}
- \(T_b(k_1, ..., k_r, t; a)\) désigne l'un (quelconque) de ces \(b\)-templates et l'ensemble de ces \(b\)-templates est noté \(\mathcal{T}_b(k_1, ..., k_r, t; a)\).
-La couleur \(r + 1\) joue un rôle particulier et elle est appelée "couleur template".
-\end{definition}
-
-La couleur \(r + 1\)  n'est pas nécessairement la dernière par ordre d'apparition, la désignation de \(r+1\) comme couleur template signalée par \(t\) est une convention qui allège les notations en évitant de devoir écrire \(\mathcal{T}_b(k_1, ..., k_{i - 1}, t,  k_{i + 1}, ..., k_r; n)\) par exemple.
-
-Dans le cas où tous les \(k_c\) sont égaux à 3, ces \(b\)-templates constituent des \(b\)-S-templates applicables pour les nombres de Schur similaires au \(b\)-WS-templates pour les nombres de Schur faibles définis dans \cite{schurboyz}.
-
-La construction présentée dans \cite{rowleyramseyabott} utilise des coloriages linéaires afin de construire des \(0\)-templates.
-La proposition suivante présente cette construction sous l'angle des \(b\)-templates.
-\begin{proposition}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r; n) \neq \varnothing\) et on se donne \(\gamma\) un tel coloriage.
-On définit un nouveau coloriage T de la manière suivante.
-\[\begin{array}{c c c l}
-	T : & [\![1, 2 n + 1]\!] & \longrightarrow & [\![1, r + 1]\!] \\
-	 & x & \longmapsto & \left\{
-		\begin{array}{l l}
-			\gamma(x) & ~\text{si}~ x \leqslant n \\
-			r + 1 & ~\text{si}~ x > n \\
-		\end{array}
-		\right.
-\end{array}\]
-Alors \(T \in \mathcal{T}_0(k_1, ..., k_r, t; 2 \, n + 1)\).
-\end{proposition}
-
-\begin{proposition}[Lien avec les templates]
-Soit \(r \in \mathbb{N}\), soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\) et soit \(a \in \mathbb{N}^*\). Alors :
-\[ \mathcal{T}(k_1, ..., k_r, t; a) = \mathcal{T}_0(k_1, ..., k_r, t; a). \]
-\end{proposition}
-
-\begin{proposition}
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
-Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
-Alors  \(T_b(k_1, ..., k_r, t; a) \subset L(k_1, ..., k_r, 3; a + b)\).
-\end{proposition}
-
-\begin{definition}[Coloriage par défaut]
-Soit \(n \in \mathbb{N}^*\), soit \(b \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
-Soit \(H\) un coloriage de \([\![1, n]\!]\) à \(r +1\) couleurs.
-On pose \(d = \min \left(H^{-1}(\{r + 1\}) \backslash [\![1, b]\!] \right) - b  - 1\).
-On définit alors un coloriage \(\coldef_b(H)\), dit par défaut, associé au coloriage \(H\) :
-\[\begin{array}{c c c c}
-	\coldef_b(H) : & [\![1, d]\!] & \longrightarrow & [\![1, r + 1]\!] \\
-	 & x & \longmapsto & H(x + b)
-\end{array}\]
-\end{definition}
-
-\begin{definition}[Méthode de construction]
-Soit \((a, p) \in {\mathbb{N}^*}^2\) et soit \(b \in \mathbb{N}\).
-Soit \((r, s) \in {\mathbb{N}^*}^2\).
-On se donne un coloriage de \([\![1, a + b]\!]\) à \(r + 1\) couleurs (appelée \(H\), pour horizontal), et un coloriage de \([\![1, p]\!]\) à \(s\) couleurs (appelée \(V\), pour vertical).
-
-Pour un \(d \in \mathbb{N}\), on se donne aussi un coloriage dit final \(F\) de \([\![1, d]\!]\) à \(r + 1\) couleurs.
-Il est parfois utile de définir \(F\) au cas par cas, mais on peut aussi lui attribuer une valeur par défaut \(F = \coldef_b(H)\).
-Dans le cas où \(F\) n'est pas utilisé, on note \(F = \varnothing\) l'application vide.
-
-On construit alors un coloriage \(\gamma\) de \([\![1, a \times p + b + d]\!]\) à \(r + s\) couleurs comme suit.
-De manière informelle, on commence par utiliser le coloriage initial \(I \defeq H_{| \, [\![1, b]\!]}\), puis on répéte \(p\) fois le pattern \(P \defeq H_{| \, [\![b + 1, a + b]\!]}\) en remplaçant pour la \(i\)-ème itération la couleur spéciale par \(r + \mathcal{V}(i)\), et finalement on ajoute le motif formé l'enchaînement des couleurs dans \(\mathcal{F}\).
-Formellement :
-\[\begin{array}{c c c l}
-	\gamma: & [\![1, a \times p + b + d]\!]  & \longrightarrow &  [\![1, r + s]\!] \\
- 	& x & \longmapsto & 
+Informally, one starts by using the initial coloring \(I \defeq H_{| \, [\![1, b]\!]}\), then repeats \(p\) times the 
+pattern \(P \defeq H_{| \, [\![b + 1, a + b]\!]}\) while replacing at the \(i\)\textsuperscript{th} iteration the color 
+\(r + 1\) by \(r + \mathcal{V}(i)\), and eventually appends the coloring \(\mathcal{F}\). Formally:
+\[\begin{array}{ccl}
+	[\![1, a p + b + d]\!]  & \longrightarrow &  [\![1, r + s]\!] \\
+ 	x & \longmapsto & 
 		\left\{\begin{array}{l l}
-			H(x) & ~\text{si}~ x \leqslant b \\
-			H(\pi(x)) & ~\text{si}~  b + 1 \leqslant x \leqslant a \times p + b ~\text{et}~ H(\pi(x)) \neq r + 1 \\
-			r + V \left(\left\lceil \dfrac{x - b}{a} \right\rceil\right) & ~\text{si}~ b + 1 \leqslant x \leqslant a \times p + b ~\text{et}~ H(\pi(x)) = r + 1 \\
-			F(x - a \times p - b) & ~\text{si}~ x \geqslant a \times p + b + 1
+			H(x) & ~\text{if}~ x \leqslant b \\
+			H(\pi(x)) & ~\text{if}~  b + 1 \leqslant x \leqslant a p + b ~\text{and}~ H(\pi(x)) \neq r + 1 \\
+			r + V \left(\left\lceil \dfrac{x - b}{a} \right\rceil\right) & ~\text{if}~ b + 1 \leqslant x \leqslant a p + b 
+				~\text{and}~ H(\pi(x)) = r + 1 \\
+			F(x - a p - b) & ~\text{if}~ x \geqslant a p + b + 1
 		\end{array}\right.
@@
 \begin{figure}[H]
-\caption{Exemple de construction avec \(b = 5\)}
-\renewcommand{\arraystretch}{1.7}
+\caption{Example of construction with \(b = 5\)}
+\renewcommand{\arraystretch}{1.6}
 \begin{center}
@@
 		\Body
-			couleur template
+			template color
 	\end{NiceTabular} \\
-	coloriage \(H\) \\
+	\(H\) coloring \\
 	\(
@@
 		\Body
-			\,\,1\,\, & \,\,2\,\, & \,\,3\,\, & \,\,4\,\, & \,\,5\,\, & \,\,6\,\, & \,\,7\,\, & \,\,8\,\, & \,\,9\,\, & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 \\
+			\,\,1\,\, & \,\,2\,\, & \,\,3\,\, & \,\,4\,\, & \,\,5\,\, & \,\,6\,\, & \,\,7\,\, & \,\,8\,\, & \,\,9\,\, & 10 & 
+				11 & 12 & 13 & 14 & 15 & 16 & 17 \\
 			\Block{1-5}{\underbrace{\hphantom{................................}}_{\textstyle I}} & & & & & \Block{1-12}{\underbrace{\hphantom{..................................................................................}}_{\textstyle P}}
@@
 	\begin{tabular}{c c}
-		coloriage \(V\) & coloriage \(F\) \\
+		\begin{tabular}{c}
+			\(V\) coloring \\
 			\(
@@
 					\,\,4\,\, \\
-			\end{NiceArray}\) &
-			\( \begin{NiceArray}{*{4}{c}}[hvlines]
+				\end{NiceArray}\)
+		\end{tabular} &
+		\begin{tabular}{c}
+			\(F\) coloring \\
+			\(
+				\begin{NiceArray}{*{4}{c}}[hvlines]
 				\CodeBefore
@@
 					\,\,1\,\, & \,\,2\,\, & \,\,3\,\, & \,\,4\,\,
-			\end{NiceArray}\) \\	
+				\end{NiceArray}\)
+		\end{tabular}
 	\end{tabular} \\
@@
 
-\begin{definition}[Compatibilité avec un \(b\)-template]
-Soit \(a \in \mathbb{N}^*\), soit \(b \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
-Soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, + \infty [\![}^r\).
-Soit \(T \in \mathcal{T}_b(k_1, ..., k_r; a)\) un \(b\)-template et soit \(A_1, ..., A_{r+1}\) la partition associée.
-Soit \(d \in [\![1, a]\!]\).
-Soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r +1\) couleurs et soit \(B_1, ..., B_{r + 1}\) la partition associée.
-Le coloriage \(F\)  est dit compatible avec le coloriage \(T\) si il vérifie :
+In some cases, it may be useful to use a specific coloring for the final coloring. However, a default coloring 
+associated to the horizontal coloring can be used instead.
+
+\begin{definition}[Default coloring]
+Let \(n \in \mathbb{N}^*\), \(b \in \mathbb{N}\) and \(r \in \mathbb{N}\). Let \(H\) be a coloring of \([\![1, n]\!]\) 
+with \(r +1\) colors. Set \(d = \min \left(H^{-1}(\{r + 1\}) \backslash [\![1, b]\!] \right) - b  - 1\). The default 
+coloring \(\coldef_b(H)\)  associated to \(H\) is defined as follows.
+\[\begin{array}{c c c c}
+	\coldef_b(H) : & [\![1, d]\!] & \longrightarrow & [\![1, r + 1]\!] \\
+	 & x & \longmapsto & H(x + b)
+\end{array}\]
+\end{definition}
+
+The construction described in \cite{RowleyRamsey} for sf-templates corresponds to the case \(b = 0\) and it uses the 
+default coloring. Contrary to sf-templates, \(b\)-templates are directly defined as particular colorings for which the 
+clique numbers remain unchanged in the construction. The rest of this section defines the \(b\)-templates as well as 
+the notion of compatibility for the final coloring.
+
+In order to describe the configurations in which a given tuple can induce a monochromatic clique when using the 
+construction, a tree is associated to every tuple.
+
+\begin{definition}
+A tree node has two components: the first one is the label and the second one is the set of descendants of this node. A 
+branch of a tree \(T\) is a tuple \((x_i)_{1 \leqslant i \leqslant k}\) such that there is a sequence of trees 
+\((t_i)_{1 \leqslant i \leqslant k}\) satisfying: \(t_1 = T\) and for all \(i \in [\![1, k]\!]\) \(x_i\) is the label 
+of \(t_i\) and for all \(i \in [\![1, k - 1]\!]\) \(t_{i + 1}\) is a descendant of \(t_i\).
+
+Let \(a \in \mathbb{N}^*\) and \(b \in \mathbb{N}\). The \(\tree_{a, b}\) application is recurssively defined as 
+follows.
+\[ \left\{
+\begin{array}{l}
+	\forall x \in \mathbb{Z}, \tree_{a, b}(x) = (x, \varnothing), \\
+	\forall k \in [\![2, +\infty[\![, \forall x \in \mathbb{Z}^k, \\
+	\mspace{30mu}
+		\left\{
+		\begin{array}{l l}
+			\tree_{a, b}(x) = (x_1, \{\tree_{a, b}(x_2, ..., x_k)\}) &  ~\text{if}~ x_2 - x_1 > b \\
+			\tree_{a, b}(x) = (x_1, \{\tree_{a, b}(x_2, ..., x_k), \tree_{a, b}(x_2 + a, ..., x_k)\}) &  ~\text{if}~ 0 \leqslant 
+				x_2 - x_1 \leqslant b \\
+			\tree_{a, b}(x) = \tree_{a, b} \left(x_1, x_2 + a \left \lceil \dfrac{x_1 - x_2}{a} \right \rceil, x_3, ..., x_k 
+				\right) & ~\text{if}~ x_2 < x_1
+		\end{array}
+		\right.
+\end{array}
+\right. \]
+Let \(x\) be a non-empty tuple of integers. The set of all the branches of the tree \(\tree_{a, b}(x)\) is denoted by 
+\(\treeset_{a, b}(x)\).
+\end{definition}
+
+Let \(A \subset \mathbb{N}^*\) and let \(k \in [\![2, +\infty]\!]\). When using the construction, not every tuple in 
+\(A^k\) have a tree which describes cliques that appear in the construction.
+
+\begin{definition}
+Let \(A \subset \mathbb{N}^*\), \(b \in \mathbb{N}\) and \(k \in [\![2, +\infty[\![\). The set of \(k\)-tuples of 
+\(A^k\) whose values are pariwise distinct is denoted by \(\mathfrak{S}_k(A)\). The set of \(k\)-tuples of 
+\(\mathfrak{S}_k(A)\) such that the elements of a tuple that are in \([\![1, b]\!]\) appear in increasing order at 
+begining of this tuple is denoted by \(S_{b,k}(A)\). That is 
+\(S_{b,k}(A) = \left\{ x \in \mathfrak{S}_k(A) ~:~ \forall i \in  [\![2, k]\!], x_i \leqslant b \implies x_i \geqslant 
+x_{i -1} \right\}\). The set of branches of trees of tuples in \(S_{b, k}(A)\) is denoted by \(\TS_{b,k}(A)\): 
+\(\TS_{b,k}(A) = \displaystyle \bigcup \limits_{x \in S_{b,k}(A)} \treeset(x)\).
+\end{definition}
+
+Most of the integers which appear in the tuples of \(\TS_{b,k}(A)\) (as well as the differences of these integers) are 
+not in \([\![1, a + b]\!]\). The role of the projection \(\pi_{a, b}\) is to project these integers onto 
+\([\![1, a + b]\!]\) in order to describe the constraints defning the \(b\)-templates.
+
+\begin{definition}
+Let \(a \in \mathbb{N}^*\) and \(b \in \mathbb{N}\).The projection \(\pi_{a, b}\) is defined as follows.
+\[ \begin{array}{c c c l}
+	\pi_{a, b} : & \mathbb{Z} & \longrightarrow & [\![1, a + b]\!] \\
+	 & x & \longmapsto & 
+		\left\{
+		\begin{array}{l l}
+			x & ~\text{if}~ 1 \leqslant x \leqslant b \\
+			(x \mod a) + a \mathds{1}_{[\![0, b]\!]}(x \mod a) & ~\text{if}~ x > b
+		\end{array}
+		\right.
+\end{array} \]
+\end{definition}
+
+The \(b\)-templates are designed to be used as the horizontal coloring in the construction.
+
+\begin{definition}[\(b\)-Templates]
+Let \(r \in \mathbb{N}\) and \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\). Let 
+\(a \in \mathbb{N}^*\) and \(b \in [\![0, a - 1]\!]\).  A \(b\)-template with width \(a\) and \(r + 1\) colors is 
+defined as a partition of \([\![1, a + b]\!]\) into \(r+1\) subsets \(A_1, ..., A_{r+1}\) such that:
 \begin{enumerate}[(i)]
-\item \(\forall (x,y) \in A_{r+1}^2, (x + y > b ~\text{et}~ \pi(x + y) \leqslant d) \implies \pi(x + y)  \notin B_{r+1}\)
+\item \(a \in A_{r+1}\),
+\item \(\forall (x, y) \in A_{r + 1}^2, x + y \notin [\![a + b + 1, 2 a + b]\!] \implies \pi_{a, b}(x + y) \notin 
+	A_{r + 1}\),
+\item \(\forall c \in [\![1, c]\!], \forall x \in \TS_{b, k_c - 1}(A_c), \exists (i, j) \in {[\![1, k_c - 1]\!]}^2, i < 
+	j ~\text{et}~ \pi_{a, b}(x_j - x_i) \notin A_c\).
+\end{enumerate}
+The set of these \(b\)-templates is denoted by \(\mathcal{T}_b(k_1, ..., k_r, t; a)\).  Color \(r + 1\) plays a special 
+role and is nammed "template color".
+\end{definition}
+
+Color \(r + 1\)  is not necessarily the last color by order of appearance, the designation of \(r+1\) as template color 
+symbolized by "\(t\)" is a convention that lightens notations and avoids writting 
+\(\mathcal{T}_b(k_1, ..., k_{i - 1}, t,  k_{i + 1}, ..., k_{r + 1}; n)\) for instance.
+
+If all the \(k_c\)'s are equal to 3, these \(b\)-templates can be used to produce sum-free partitions for Schur numbers.
+
+\(b\)-Templates are a particular case of linear colorings. In the template color, the corresponding clique number is 
+equal to 3. That is \(T_b(k_1, ..., k_r, t; a) \subset L(k_1, ..., k_r, 3; a + b)\).
+
+The notion of compatibility with a \(b\)-template illustrates the fact that the final coloring in the construction is 
+less constrained than the horizontal coloring, and that the constraints on this final coloring depends only on the 
+horizontal coloring.
+
+\begin{definition}[Compatibility with a \(b\)-template]
+For \(A \subset \mathbb{N}\) and \(k \in \mathbb{N}\), the set of increasing sequences of length \(k\) with values in 
+\(A\) is denoted by \(\mathfrak{I}_k(A)\).
+
+Let \(a \in \mathbb{N}^*\), \(b \in [\![0, a - 1]\!]\) and \(r \in \mathbb{N}\). Let 
+\((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, + \infty [\![}^r\). Let \(T \in \mathcal{T}_b(k_1, ..., k_r; a)\) and 
+denote by \(A_1, ..., A_{r+1}\) the associated partition. Let \(d \in [\![0, a]\!]\). Let \(F\) be a coloring of 
+\([\![1, d]\!]\) with \(r +1\) colors and denote by \(B_1, ..., B_{r + 1}\) the associated partition. The coloring 
+\(F\) is said to be compatible with the \(b\)-template \(T\) if it satisfies:
+\begin{enumerate}[(i)]
+\item \(a - b \notin B_{r + 1}\)
+\item \(\forall (x,y) \in A_{r+1}^2, (x + y > a + b ~\text{and}~ \pi_{a, b}(x + y) \leqslant d) \implies \pi_{a, b}
+	(x + y)  \notin B_{r+1}\)
 \item \(\forall (x,y) \in A_{r+1} \times B_{r+1}, x + y \leqslant d \implies x + y  \notin B_{r+1}\)
-\item \(\forall c \in [\![1, r]\!], \forall k \in [\![1, k_c-1]\!], \\
-	\left\{ \text{ou} 
+\item \(\forall c \in [\![1, r]\!], \forall k \in [\![1, k_c-1]\!], \forall x \in \TS_{b, k}(A_c), \forall y \in 
+	\mathfrak{I}_{k_c - k - 1}(B_c), \\
 	\begin{array}{l}
-		\exists (i, j) \in {[\![1, k]\!]}^2, |x_i - x_j| \notin A_c, \\
-		TODO \\
-		\exists (i, j) \in {[\![1, k_c - k - 1]\!]}^2, i < j ~\text{et}~ \pi(y_j - y_i) \notin A_c.
+		\mspace{30mu} 
+		\left\{ \text{or} 
+		\begin{array}{l}
+			\exists (i, j) \in {[\![1, k]\!]}^2, \pi_{a, b}(x_j - x_i) \notin A_c, \\
+			\exists (i, j) \in [\![1, k]\!] \times [\![1, k_c - k - 1]\!], \\
+			\mspace{30mu}
+				\left \{
+				\begin{array}{l l}
+					(y_j - x_i) \mod a \notin A_c & ~\text{if}~ (y_j - x_i) \mod a > b \\
+					(y_j - x_i) \mod a \notin A_c ~\text{and}~ \pi_{a, b}(y_j - x_i) \notin A_c & ~\text{if}~ (y_j - x_i) \mod a 
+						\leqslant b \\
 				\end{array}
-	\right.\)
+				\right. \\
+			\exists (i, j) \in {[\![1, k_c - k - 1]\!]}^2, i < j ~\text{and}~ \pi_{a, b}(y_j - y_i) \notin A_c.
+		\end{array}
+		\right.
+	\end{array}\)
 \end{enumerate}
@@
 \end{corollary}
+
+La construction présentée dans \cite{rowleyramseyabott} utilise des coloriages linéaires afin de construire des \(0\)-templates.
+La proposition suivante présente cette construction sous l'angle des \(b\)-templates.
+\begin{proposition}
+Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
+Soit \(n \in \mathbb{N}\) tel que \(\mathcal{L}(k_1, ..., k_r; n) \neq \varnothing\) et on se donne \(\gamma\) un tel coloriage.
+On définit un nouveau coloriage T de la manière suivante.
+\[\begin{array}{c c c l}
+	T : & [\![1, 2 n + 1]\!] & \longrightarrow & [\![1, r + 1]\!] \\
+	 & x & \longmapsto & \left\{
+		\begin{array}{l l}
+			\gamma(x) & ~\text{si}~ x \leqslant n \\
+			r + 1 & ~\text{si}~ x > n \\
+		\end{array}
+		\right.
+\end{array}\]
+Alors \(T \in \mathcal{T}_0(k_1, ..., k_r, t; 2 \, n + 1)\).
+\end{proposition}
 

### 2022-06-29 article_ramsey/template_improvement.tex
ineqs

@@
 results on \(b\)-templates and on the construction. Section \ref{sec:bounds} records the new inequalities and some new 
-lower bounds.
+lower bounds. The improved templates can be found in Appendix \ref{appendix}.
 
@@
 Let \(a \in \mathbb{N}^*\), \(b \in [\![0, a - 1]\!]\) and \(r \in \mathbb{N}\). Let 
-\((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, + \infty [\![}^r\). Let \(T \in \mathcal{T}_b(k_1, ..., k_r; a)\) and 
-denote by \(A_1, ..., A_{r+1}\) the associated partition. Let \(d \in [\![0, a]\!]\). Let \(F\) be a coloring of 
+\((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, + \infty [\![}^r\). Let \(T \in \mathcal{T}_b(k_1, ..., k_r, t; a)\) 
+and denote by \(A_1, ..., A_{r+1}\) the associated partition. Let \(d \in [\![0, a]\!]\). Let \(F\) be a coloring of 
 \([\![1, d]\!]\) with \(r +1\) colors and denote by \(B_1, ..., B_{r + 1}\) the associated partition. The coloring 
@@
 \begin{corollary}[Inégalités pour les nombres de Ramsey linéaires]
+\label{thm:ineq}
 Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, +\infty[\![}^r\).
@@
 
-\section{Nouvelles inégalités et bornes inférieures}
+\section{New inequalites and lower bounds}
 \label{sec:bounds}
 
-\subsection{Nombres de Schur}
+As in \cite{schurboyz} and \cite{rowleyramseysat}, the \(b\)-templates described in this article were found by encoding 
+the existence of the templates into a boolean formula and then using a SAT solver (here, the parallel version of the 
+Lingeling SAT solver \cite{Lingeling2017}).
 
-L'existence d'un 2-S-template de largeur 10 à 3 couleurs non exprimable en tant que S-template fournit une nouvelle inégalité. L'ancienne inégalité était \(S(n + 2) \geqslant 9 \, S(n) + 4\).
+\subsection{Multicolor Ramsey numbers}
+
+The templates in Appendix \ref{appendix} provide inequalities of the form 
+\(L(k_1, ..., k_r, k_{r+1}, ..., k_{r+s}) \geqslant a \, L(k_1, ..., k_r) - 2 + d\). In table \ref{tab:ineq},"added 
+\(k_i\)'s" denotes the \( k_{r+1}, ..., k_{r+s}\) in the previous inequality and "\(b\)-template" indicates a 
+\(b\)-template which cannot be expressed as a sf-template.
+
+\begin{table}[H]
+\begin{center}
+\caption{Summarizing table of the new inequalities}
+\begin{tabular}{| c | c | c | c | c |}
+	\hline
+	added \(k_i\)'s & former (a, d) & new (a, d) & template type & final coloring \\
+	\hline
+	3, 3 & 9, 4 \cite{AbbottHanson} & 10, 2 & \(b\)-template & default \\
+	\hline
+	3, 4 & 18, 7 \cite{rowleyramseysat} & 19, 2 & \(b\)-template & default \\
+	\hline
+	3, 5 & 30, 12 \cite{rowleyramseysat} & 31, 3 & \(b\)-template & specific \\
+	\hline
+	4, 5 & 51, 21 \cite{rowleyramseysat} & 55, 23 & sf-template & default \\
+	\hline
+\end{tabular}
+\end{center}
+\label{tab:ineq}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\caption{Summarizing table of the new lower bounds for small Ramsey numbers}
+\begin{tabular}{| c | c | c |}
+	\hline
+	Ramsey number & former lower bound & new lower bound \\
+	\hline
+	\(R_8(3)\) & \(5\,288\) \cite{RowleyRamsey} & \(5\,364\)  \\
+	\hline
+	\(R_{13}(3)\) & \(2\,011\,292\) \cite{schurboyz} & \(2\,038\,284\) \\
+	\hline
+	\(R(3 , 4 , 5 , 5)\) & 729 \cite{rowleyramseysat} & 764 \\
+	\hline
+\end{tabular}
+\end{center}
+\label{tab:bounds}
+\end{table}
+The template in \(\mathcal{L}_2(3, 3, t; 10)\) induces an inequality which improves the lower bounds for 
+\(R_{5 n + 3}(3)\) for all \(n \in \mathbb{N}^*\).
+
+\subsection{Schur numbers}
+
+The existence of a 2-template with width 10 and 3 colors which cannot be expressed as a sf-template provides an improved 
+inequality. The former corresponding inequality is \(S(n + 2) \geqslant 9 \, S(n) + 4\) \cite{AbbottHanson}.
 
 \begin{proposition}
-	\[\forall n \in \mathbb{N}^*, S(n + 2) \geqslant 10 \, S(n) + 2\]
+	\[\forall n \in \mathbb{N}, S(n + 2) \geqslant 10 \, S(n) + 2\]
 \end{proposition}
 
-Cette inégalité fournit les nouvelles bornes inférieures suivantes : \(S(8) \geqslant 5\,362\) et \(S(13) \geqslant 2\,038\,282\) (contre respectivement \(5\,286\) dans \cite{RowleyRamsey} et \(2\,011\,290\) dans \cite{schurboyz}).
-Plus généralement, cette inégalité améliore les bornes inférieures des \(S(5 k + 3), \forall k \in \mathbb{N}^*\).
+This inequality provides the following improved lower bounds: \(S(8) \geqslant 5\,362\) and 
+\(S(13) \geqslant 2\,038\,282\) (the former lower bounds were respectively \(5\,286\) \cite{RowleyRamsey} and 
+\(2\,011\,290\) \cite{schurboyz}). More generally, this inequality improves the lower bounds for \(S(5 n + 3)\) for all 
+\(n \in \mathbb{N}^*\).
 
-\subsection{Nombres de Ramsey}
+\section{Acknowledgements}
 
-On obtient des ingégalités de la forme \(L(k_1, ..., k_r, k_{r+1}, ..., k_{r+s}) - 2 \geqslant a \, (L(k_1, ..., k_r) - 2) + d\).
-Les "\(k_i\) ajoutés" désignent \( k_{r+1}, ..., k_{r+s}\).
-Dans le tableau ci-dessous, \(b\)-template désigne un \(b\)-template non exprimable en tant que template.
-Les anciennes valeurs viennent de \cite{rowleyramseysat}.
-\begin{table}[H]\begin{center}
-\begin{tabular}{| c | c | c | c | c |}
-	\hline
-	\(k_i\) ajoutés & ancien (a, d) & nouveau (a, d) & type de template & coloriage final \\
-	\hline
-	3, 3 & 9, 4 & 10, 2 & \(b\)-template & défaut \\
-	\hline
-	3, 4 & 18, 7 & 19, 2 & \(b\)-template & défaut \\
-	\hline
-	3, 5 & 30, 12 & 31, 3 & \(b\)-template & spécifique \\
-	\hline
-	4, 5 & 51, 21 & 55, 23 & template & défaut \\
-	\hline
-\end{tabular}
-\end{center}\end{table}
-
-En ce qui concerne les bornes inférieures, on a  \(R_8(3) \geqslant 5\,364\) et \(R_{13}(3)\geqslant 2\,038\,284\) (contre respectivement \(5\,288\) dans \cite{RowleyRamsey} et \(2\,011\,292\) dans \cite{schurboyz}), et plus généralement une amélioration pour les \(R_{5 k + 3}(3), \forall k \in \mathbb{N}^*\).
-On a aussi \(R(3 , 4 , 5 , 5) \geqslant 764\) (contre 729 dans \cite{rowleyramseysat}).
-Il existe de nombreuses inégalités récursives et constructions pour les nombres de Ramsey.
-Afin de savoir quelles bornes précisément ont été améliorées, il faudrait recenser chacunes des bornes inférieures et des méthodes existantes puis calculer toutes les bornes et voir si cetaines sont améliorées.
-Il est probable que les inégalités de cette section permettent d'améliorer les bornes inférieures pour d'autres nombres de Ramsey mais je n'ai pas effectué cette vérification.
+This study results from a long-term project performed within the framework of the Project Cluster "Training for 
+Research" of CentraleSupélec. I also would like to address warm thanks to Paul Casteras, Thibaut Pellerin and Yann 
+Portella with whom I started working on Schur and weak Schur numbers.
 
@@
 
+\appendix
+
+\section{\(b\)-Templates}
+\label{appendix}
+
+\begin{table}[H]
+\caption{\(T \in \mathcal{T}_2(3, 3, t; 10)\)}
+\begin{center}
+\begin{tabular}{c}
+	\begin{tabular}{| c | c |}
+		\hline
+		1 & 1, 5, 8, 12 \\
+		\hline
+		2 & 2, 6, 7 \\
+		\hline
+		3 & 3, 4, 9, 10, 11 \\
+		\hline
+	\end{tabular} \\ \\
+	 Final coloring: \(\varnothing\)
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\caption{\(T \in \mathcal{T}_2(3, 4, t; 19)\)}
+\begin{center}
+\begin{tabular}{c}
+	\begin{tabular}{| c | c |}
+		\hline
+		1 & 1, 6, 9, 13, 17, 21 \\
+		\hline
+		2 & 2, 7, 8, 10, 14, 15, 16 \\
+		\hline
+		3 & 3, 4, 5, 11, 12, 18, 19, 20 \\
+		\hline
+	\end{tabular} \\ \\
+	 Final coloring: \(\varnothing\)
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\caption{\(T \in \mathcal{T}_2(3, 5, t; 31)\)}
+\begin{center}
+\begin{tabular}{c}
+	\begin{tabular}{| c | c |}
+		\hline
+		1 & 1, 5, 9, 12, 16, 19, 23, 26, 30 \\
+		\hline
+		2 & 2, 6, 7, 8, 10, 11, 17, 18, 24, 25, 27, 28, 29, 33 \\
+		\hline
+		3 & 3, 4, 13, 14, 15, 20, 21, 22, 31, 32 \\
+		\hline
+	\end{tabular} \\ \\
+	 Final coloring: \(F(1) = 1\)
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[H]
+\caption{\(T \in \mathcal{T}_0(5, 4, t; 55)\)}
+\begin{center}
+\begin{tabular}{c}
+	\begin{tabular}{| c | c |}
+		\hline
+		1 & 1, 5, 6, 7, 9, 10, 12, 14, 15, 17, 18, 19, 23, 25, 31, 48, 54 \\
+		\hline
+		2 & 2, 3, 4, 8, 11, 13, 16, 20, 21, 22, 26, 28, 51, 52, 53 \\
+		\hline
+		3 & 24, 27, 29, 30, 32, 33, 34, 35, 36, 37, 38, 39 \\
+		 & 40, 41, 42, 43, 44, 45, 46, 47, 49, 50, 55 \\
+		\hline
+	\end{tabular} \\ \\
+	 Final coloring: \(\coldef_0(T)\)
+\end{tabular}
+\end{center}
+\end{table}
+
 \end{document}

### 2022-07-02 article_ramsey/template_improvement.tex
typos + strong / regular / weak compat

@@
 \usepackage{hyperref}
+
+\hypersetup{hidelinks}
+
 \usepackage[utf8]{inputenc}
@@
 "final") be a coloring of \([\![1, d]\!]\) with \(r + 1\) colors. The empty coloring (i.e. \(d = 0\)) is denoted by 
-\(F = \varnothing\). The construction produces a coloring \(\cons_b(H, V, F)\) of \([\![1, a p + b + d]\!]\) with 
-\(r + s\) colors.
+\(F = \varnothing\). If \(s \geqslant 3\) or \(s = 2\) and \(V(p) \neq 2\), set \(c = \max ([\![2, s]\!] \backslash 
+\{V(p)\})\). Otherwise, set \(c = s\). The construction produces a coloring \(\cons_b(H, V, F)\) of 
+\([\![1, a p + b + d]\!]\) with \(r + s\) colors.
 
@@
 pattern \(P \defeq H_{| \, [\![b + 1, a + b]\!]}\) while replacing at the \(i\)\textsuperscript{th} iteration the color 
-\(r + 1\) by \(r + \mathcal{V}(i)\), and eventually appends the coloring \(\mathcal{F}\). Formally:
+\(r + 1\) by \(r + \mathcal{V}(i)\), and eventually appends the coloring \(\mathcal{F}\) in which color \(r + 1\) is 
+replaced by \(r + c\). Formally:
 \[\begin{array}{ccl}
@@
 				~\text{and}~ H(\pi(x)) = r + 1 \\
-			F(x - a p - b) & ~\text{if}~ x \geqslant a p + b + 1
+			F(x - a p - b) & ~\text{if}~ x \geqslant a p + b + 1 ~\text{and}~ F(x - a p - b) \neq r + 1 \\
+			r + c & ~\text{if}~ x \geqslant a p + b + 1 ~\text{and}~ F(x - a p - b) = r + 1 \\
 		\end{array}\right.
@@
 \renewcommand{\arraystretch}{1.6}
+\small
 \begin{center}
@@
 			\cellcolor{red}{6-1}
-			\cellcolor{cyan}{6-2}
+			\cellcolor{yellow}{6-2}
 			\cellcolor{green}{6-3}
@@
 \([\![1, d]\!]\) with \(r +1\) colors and denote by \(B_1, ..., B_{r + 1}\) the associated partition. The coloring 
-\(F\) is said to be compatible with the \(b\)-template \(T\) if it satisfies:
+\(F\) is said to be strongly compatible with the \(b\)-template \(T\) if it satisfies:
 \begin{enumerate}[(i)]
-\item \(a - b \notin B_{r + 1}\)
-\item \(\forall (x,y) \in A_{r+1}^2, (x + y > a + b ~\text{and}~ \pi_{a, b}(x + y) \leqslant d) \implies \pi_{a, b}
-	(x + y)  \notin B_{r+1}\)
-\item \(\forall (x,y) \in A_{r+1} \times B_{r+1}, x + y \leqslant d \implies x + y  \notin B_{r+1}\)
-\item \(\forall c \in [\![1, r]\!], \forall k \in [\![1, k_c-1]\!], \forall x \in \TS_{b, k}(A_c), \forall y \in 
-	\mathfrak{I}_{k_c - k - 1}(B_c), \\
+\item \label{cond:nocol} \(a - b \notin B_{r + 1}\)
+\item \label{cond:noover} \(\forall (x,y) \in A_{r+1}^2, (x + y > a + b ~\text{and}~ \pi_{a, b}(x + y) - b \leqslant d) 
+	\implies \pi_{a, b}(x + y) - b \notin B_{r+1}\)
+\item \label{cond:nolin} \(\forall (x,y) \in A_{r+1} \times B_{r+1}, x + y \leqslant d \implies x + y  \notin B_{r+1}\)
+\item \label{cond:notree} \(\forall c \in [\![1, r]\!], \forall k \in [\![1, k_c-1]\!], \forall x \in \TS_{b, k}(A_c), 
+	\forall y \in \mathfrak{I}_{k_c - k - 1}(B_c), \\
 	\begin{array}{l}
-		\mspace{30mu} 
 		\left\{ \text{or} 
@@
 			\exists (i, j) \in [\![1, k]\!] \times [\![1, k_c - k - 1]\!], \\
-			\mspace{30mu}
+			\mspace{15mu}
 				\left \{
 				\begin{array}{l l}
-					(y_j - x_i) \mod a \notin A_c & ~\text{if}~ (y_j - x_i) \mod a > b \\
-					(y_j - x_i) \mod a \notin A_c ~\text{and}~ \pi_{a, b}(y_j - x_i) \notin A_c & ~\text{if}~ (y_j - x_i) \mod a 
-						\leqslant b \\
+					(y_j + b - x_i) \mod a \notin A_c & ~\text{if}~ (y_j + b - x_i) \mod a > b \\
+					(y_j + b - x_i) \mod a \notin A_c ~\text{and}~ \pi_{a, b}(y_j + b - x_i) \notin A_c & ~\text{if}~ (y_j + b - x_i) 
+						\mod a \leqslant b \\
 				\end{array}
@@
 \end{enumerate}
+
+In practice, conditions (\ref{cond:noover}) and (\ref{cond:nolin}) can be weakened by replacing \(A_{r + 1}\) by 
+\(A_{r + 1} \backslash [\![1, b]\!]\); those modified conditions are respectively denoted by 
+(\(\widetilde{\ref{cond:noover}}\)) and (\(\widetilde{\ref{cond:nolin}}\)). The coloring \(F\) is said to be compatible 
+with the \(b\)-template \(T\) if it satisfies conditions (\ref{cond:nocol}), (\(\widetilde{\ref{cond:noover}}\)), 
+(\(\widetilde{\ref{cond:nolin}}\)) and (\ref{cond:notree}). The coloring \(F\) is said to be weakly compatible with the
+ \(b\)-template \(T\) if it satisfies conditions (\ref{cond:nocol}), (\(\widetilde{\ref{cond:noover}}\)) and 
+(\ref{cond:notree}). 
 \end{definition}

### 2022-07-07 article_ramsey/template_improvement.tex
debut thms

@@
 
-On a une cractérisation similaire à celle donnée dans \cite{RowleyRamsey} pour les sf-templates.
-\begin{proposition}[Condition suffisante pour les templates]
-Soit \(a \in \mathbb{N}^*\), soit \(b \in \mathbb{N}\) et soit \(r \in \mathbb{N}\).
-Soit \((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, + \infty [\![}^r\).
-Soit \(T\) un coloriage de \([\![1,  a + b]\!]\) à \(r + 1\) couleurs.
-Soit \(d \in [\![1, a - 1 ]\!]\) et soit \(F\) un coloriage de \([\![1, d]\!]\) à \(r + 1\) couleurs.
-Soit \(n \in [\![3, + \infty [\![\) tel que \(n \geqslant \max_{1 \leqslant c \leqslant r} k_c - 1\).
-Soit \(s \in \mathbb{N}^*\) et soit \((l_c)_{1 \leqslant c \leqslant s} \in {[\![3, + \infty [\![}^s\).
-Soit enfin \(\gamma \in \mathcal{L}(l_1, ..., l_s; n)\) tel qu'il existe une couleur \(c \in [\![1, s]\!]\) et un sous-ensemble \(S\) de \([\![1, n]\!]\) monochromatique de couleur \(c\) et de cardinal \(k_c - 2\) vérifiant pour tous \(x, y \in S\) distincts, \(\gamma(|x - y|) = c\).
-Supposons que \(\cons_b(T, \gamma, F) \in \mathcal{L}(k_1, ..., k_r, l_1, ..., l_s; a n + b + d)\).
-Alors \(T \in \mathcal{T}_b(k_1, ..., k_r, t; a)\) et \(F\) est compatible avec \(T\).
+\begin{proposition}
+Let \(r \in \mathbb{N}\) and let \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\). Let 
+\(a \in \mathbb{N}^*\) and let \(b \in [\![0, a - 1]\!]\). Let \(T \in \mathcal{T}_b(k_1, ..., k_r, t; a)\). Then 
+\(\coldef_b(T)\) is strongly compatible with \(T\).
 \end{proposition}
 
-\begin{proposition}[Compatibilité de la valeur par défaut]
-Soit \(r \in \mathbb{N}\) et soit \((k_c)_{1 \leqslant c \leqslant r}  \in {[\![3, +\infty[\![}^r\).
-Soit \(a \in \mathbb{N}^*\) et soit \(b \in \mathbb{N}\).
-Soit \(T \in \mathcal{T}_b(k_1, ..., k_r, t; a)\) un \(b\)-template.
-Alors \(T\) et \(\coldef_b(T)\) sont compatibles.
-\end{proposition}
+\begin{proof}
+TODO
+\end{proof}
 
-\begin{theorem}[Construction de coloriages linéaires]
+\begin{lemma}
+Let \(a \in \mathbb{N}^*\), \(b \in [\![0, a - 1 ]\!]\) and \(r \in \mathbb{N}^*\). Let 
+\((k_c)_{1 \leqslant c \leqslant r} \in {[\![3, + \infty [\![}^r\). Let \(T\) be a coloring of \([\![1,  a + b]\!]\) 
+with \(r + 1\) colors. Let \(d \in [\![0, a]\!]\) and let \(F\) be a coloring of \([\![1, d]\!]\) with \(r + 1\) 
+colors. Set \(k = \max_{1 \leqslant c \leqslant r} k_c - 1\).
+
+Define the following three colorings.
+\[\begin{array}{l c c c l}
+	V_\mathit{strong} : & [\![1, k - 2]\!] & \longrightarrow & \{1\} & \\
+	 & x & \longmapsto & 1 & \\
+	 & & & & \\
+	V_\mathit{reg} : & [\![1, k - 2]\!] & \longrightarrow & \{1\} & \\
+	 & x & \longmapsto & 1 & \\
+	 & & & & \\
+	V_\mathit{weak} : & [\![1, k - 2]\!] & \longrightarrow & \{1\} & \\
+	 & x & \longmapsto & 1 & \\
+\end{array}\]
+\end{lemma}
+
+\begin{theorem}[Construction of linear colorings]
 \label{thm:b-temp}
